### 2022-11-16 1st_Manuscript/ManuscriptDraft.Rmd
Rmarkdown & Zotero library

---
title: "The complex network of trophic interactions in the Marine Protected Area Namuncurá-Banco Burdwood"
author: "Tomás I. Marina, Irene R. Schloss and Luciana Riccialdelli"
output: pdf_document
bibliography: "AMPBancoBurdwood.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
@Schejter2016

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## References

### 2022-11-23 1st_Manuscript/ManuscriptDraft.Rmd
Added Obj, main Res & Disc

@@
 ```{r setup, include=FALSE} 
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
 ```
 
-## R Markdown
-@Schejter2016
+## Abstract
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+## Introduction
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+The objective of the present work was to build the network of predator-prey interactions (food web) for the Marine Protected Area Namuncurá - Banco Burdwood I, and characterize it in terms of complexity and structure.
 
-```{r cars}
-summary(cars)
-```
+## Methodology
 
-## Including Plots
+### Study area
 
-You can also embed plots, for example:
+### Food web construction
 
-```{r pressure, echo=FALSE}
-plot(pressure)
-```
+### Food web analysis
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+We analyzed the MPA food web at 2 levels: 1) global, network-level properties (considers all species and interactions), and 2) species, species-level properties (considers the species’ role in the food web).
+GLOBAL
+Complexity: # trophic species, # interactions, link density, connectance
+Degree distribution
+Mean shortest path length
+Omnivory
+Distribution of prey and predator
+Distribution of interactions by functional group
+
+SPECIES
+Centrality indices (betweenness, closeness)
+Trophic similarity
+Topological role
+
+## Results
+
+### Network-level properties
+
+Most Functional groups show an asymmetric distribution of interactions: few species are relatively more connected than the rest.
+
+Most consumers have a narrow potential diet, few have a broad diet.
+Few prey are consumed by many predators, most prey have few predators.
+Consumers w/ broad diet: Patagonotothen guntheri, P. ramsayi, Dissostichus eleginoides, Bathyraja brachyurops, B. griseocauda.
+Prey w/ many predators: Detritus, Diatoms (benthic, centric, pennate), Euphausia spp., Foraminifera.
+
+### Species-level properties
+
+‘Network connector’ and ‘module connector’ species are responsible for linking modules and maintaining the connectivity of the food web. TL range for these species: 1 - 3.86.
+
+Betweenness = Species at mid-trophic levels (3-4) present more shortest paths between species than any other species: ‘bridge’ role.
+Closeness = Low-trophic level species are relatively closer to other species in the food web.
+
+Trophic similarity: Species are more similar at mid-trophic levels (2-3) than in lower or higher ones. Basal and top species present a higher uniqueness in terms of trophic role.
+
+## Discussion
+
+The distribution of the interactions is asymmetric, where few species concentrate most of the interactions: Detritus, Diatoms (x3), Patagonotothen ramsayi & P.
+guntheri, Euphausia spp.
+The same happens within each functional group.
+
+The most demanded food sources are: Detritus, Diatoms (x3), Euphausia spp., & Foraminifera.
+Almost half of the consumers (47.64 %) are omnivores. Those with the broadest diets are: Patagonotothen ramsayi, P. guntheri, Dissostichus eleginoides, Bathyraja brachyurops, B. griseocauda.
+
+Low and mid-trophic level species are responsible for maintaining the connectivity of the food web.
+The functional groups represented are: Amphipoda, Bivalvia, Bryozoa, Cnidaria, Cumacea, Decapoda, Detritus, Diatoms, Echinodermata, Fish (bentho-pelagic, demersal, chondrichthyes), Foraminifera, Polychaeta, Porifera, Zooplankton.
+
+Low and mid-trophic level species present the highest betweenness and closeness values. These species have an important ‘bridge’ role and are close to other species.
+Mid-trophic level species are more redundant than those at low and high trophic levels.
 

### 2022-11-24 1st_Manuscript/ManuscriptDraft.Rmd
Started w/ M&M

@@
 
-The objective of the present work was to build the network of predator-prey interactions (food web) for the Marine Protected Area Namuncurá - Banco Burdwood I, and characterize it in terms of complexity and structure.
+The objective of the present work was to build the network of predator-prey interactions (food web) for the Marine Protected Area Namuncurá - Banco Burdwood I (MPAN-BB), and characterize it in terms of complexity and structure.
 
@@
 ### Study area
+
+The MPAN-BB is a shallow submarine plateau called Burdwood Bank (BB) located 150 km east of Isla de los Estados and 200 km south from Malvinas/Falkland Islands (Figure 1).
+It comprises nearly 34.000 km^2 circumscribed by the 200 m isobath, between 54º–55ºS and 56º–62ºW, with a slight slope extended nearly 370 km east–west.
+The BB is surrounded by steep flanks of more than 3000 m depth through which strong currents circulate [@Piola1989; @Reta2014; @Matano2019].
+Intense upwelling and mixing occur over it, entraining deep nutrient rich waters into the photic layer [@Piola2009; @Matano2019] and resulting in a fairly homogeneous water column both spatially and temporally [@Glorioso1995; @Guerrero1999; @Matano2019].
+Physical features in the MPAN-BB are fairly stable, with salinity averaging 34 all year round and temperature ranging between 4 and 8 ºC overall [@Guerrero1999; @Acha2004; @Piola2009].
 

### 2023-01-13 1st_Manuscript/ManuscriptDraft.Rmd
Update January 2023

@@
 ---
-title: "The complex network of trophic interactions in the Marine Protected Area Namuncurá-Banco Burdwood"
+title: "The complex network of trophic interactions in a subAntarctic Marine Protected Area"
 author: "Tomás I. Marina, Irene R. Schloss and Luciana Riccialdelli"
@@
 
-The objective of the present work was to build the network of predator-prey interactions (food web) for the Marine Protected Area Namuncurá - Banco Burdwood I (MPAN-BB), and characterize it in terms of complexity and structure.
+The objective of the present work was to build the network of trophic (predator-prey) interactions for the Marine Protected Area Namuncurá - Banco Burdwood I (MPAN-BB), and characterize it in terms of complexity and structure using a network approach.
 
@@
 The BB is surrounded by steep flanks of more than 3000 m depth through which strong currents circulate [@Piola1989; @Reta2014; @Matano2019].
-Intense upwelling and mixing occur over it, entraining deep nutrient rich waters into the photic layer [@Piola2009; @Matano2019] and resulting in a fairly homogeneous water column both spatially and temporally [@Glorioso1995; @Guerrero1999; @Matano2019].
-Physical features in the MPAN-BB are fairly stable, with salinity averaging 34 all year round and temperature ranging between 4 and 8 ºC overall [@Guerrero1999; @Acha2004; @Piola2009].
+Intense upwelling and mixing occur over it, entraining deep nutrient rich waters into the photic layer [@Piola2009; @Matano2019], and resulting in a fairly homogeneous water column both spatially and temporally [@Glorioso1995; @Guerrero1999; @Matano2019].
+Physical features in the MPAN-BB are fairly stable, with salinity averaging 34 all year round and temperature ranging between 4 and 8ºC overall [@Guerrero1999; @Acha2004; @Piola2009].
 
-### Food web construction
+### Network construction
 
-### Food web analysis
+In order to build the network of predator-prey interactions we reviewed more than 150 references considering published articles, databases and doctoral theses.
+Furthermore, we took into account personal communications from experts belonging to the working group of the study area (https://www.pampazul.gob.ar/tag/banco-burdwood/).
+The diversity of the expertise of the authors contributing to the present study was a key factor in generating the quality of the network, and inherently improved the network representation of the MPAN-BB ecosystem.
+A list of the bibliography used to build the network is presented in Supplementary Material (Table S1).
+
+Due to a lack of trophic data resolution for some species inhabiting the MPAN-BB, we follow the concept of trophospecies, here defined as aggregated groups of taxa.
+In most cases we followed this when data on specific biological species were not available, but for some cases we collapsed species when taxa shared the same set of predators and prey (trophic similarity criteria).
+Details about this can be found in Supplementary Material (Table S2).
+
+### Network analysis
 
@@
 Topological role
+
+All analyses and graphs were performed in R version 4.2.2 [@RCoreTeam2022], mainly using 'igraph' [@Csardi2006] and ‘multiweb’ [@Saravia2022a] packages.
+
+```{r table1, echo=FALSE, results='asis'}
+
+# Load packages
+library(knitr)
+library(tidyverse)
+library(pander)
+
+# Build Table 1. Network metrics
+ti_des <- tibble(Name="Connectance",
+                 Description="Directed connectance describes the proportion of directed links realized out of the maximum number of possible links.",
+                 Implications = "It measures the probability of interactions, it is a fundamental measure of network complexity.
+Connectance can be negatively or positively associated with food-web robustness, depending on the network structure (random vs non-random) or how the strength of the interactions are distributed.",
+                 Reference = "")
+
+ti_des <- add_row(ti_des, Name="Link density", Description="Number of trophic interactions (links) per species.", Implications = "The average number of links per species informs about how connected species are in the food-web", Reference = "")
+
+ti_des <- add_row(ti_des, Name="Proportion of basal species", Description="Proportion of taxa with no prey.", Implications = "The proportion of basal species is often under-represented in marine food webs.
+The few basal species impart a funnel shape at the base of the food web.", Reference = "")
+
+ti_des <- add_row(ti_des, Name="Proportion of intermediate species", Description="Proportion of taxa that are both prey and predators to other species.", Implications = "The proportion of intermediate species influence the connectivity of a food web between lower and upper trophic levels.
+The proportion of intermediate species is positively associated with connectance and level of omnivory.", Reference = "")
+
+ti_des <- add_row(ti_des, Name="Proportion of top species", Description="Proportion of taxa with no predators.", Implications = "Top predators may induce indirect, top down effects such as trophic cascades through lower trophic", Reference = "")
+
+ti_des <- add_row(ti_des, Name="Trophic Level", Description="Mean of all short-weighted paths from base to each species.", 
+                  Implications = "The number of trophic levels is a central feature of the vertical structure of food webs and is related to the length of food chains.
+The height of trophic levels reflects ecological processes that sustain top predators.", Reference = "")
+
+ti_des <- add_row(ti_des, Name="Omnivory", Description="Level of omnivory of each species is the standard deviation of the short-weighted trophic level of its resources.", Implications = "Omnivory can negatively or positively influence the stability of communities, depending on the interaction strength.
+Intermediate levels of omnivory may stabilize communities, and may diffuse top-down influences through the food webs and thereby reduce the probability of trophic cascades.", Reference = "")
+
+ti_des <- add_row(ti_des, Name="Modularity", Description="Modularity describes how densely sub-groups of species interact with one another compared to species from other sub-groups.", Implications = "Modularity is positively associated with robustness, because perturbations can be retained within modules, preventing them to spread to the whole network.", Reference = "")
+
+ti_des <- add_row(ti_des, Name="Mean maximum eingenvalue", Description="The mean of the maximum eigenvalue of the community matrix.
+This matrix is based on the adjacency matrix of the food web with the magnitudes randomized.", Implications = "This metric is directly related with network local stability, which can reveal the amplification of small perturbations near the equilibrium point; values closer to zero indicate a more stable food web.", Reference = "")
+
+pandoc.table(ti_des, digits = 4, colnames("Metric","Definition","Implication","Reference"), style="multiline", split.tables = Inf, justify = c('left','left','left','right'),
+             caption = "List of network metrics analyzed, definitions, and relevant ecological implication related to food web complexity and structure.")
+
+```
 

### 2023-01-13 1st_Manuscript/SupMaterial.Rmd
Update January 2023

---
title: "Supplementary material for 'The complex network of trophic interactions in a subAntarctic Marine Protected Area'"
author: "Tomás I. Marina, Irene R. Schloss and Luciana Riccialdelli"
output: pdf_document
bibliography: "AMPBancoBurdwood.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

## Food web construction

The following figure and tables summarize the data we used to build the network of trophic (predator-prey) interactions for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).
Figure 1 resumes the type and number of references reviewed. Table 1 is the complete list of trophic interactions and the references that confirm each of them. Table 2 is the species list with details on trophospecies cases (aggregated taxa).

```{r ref-plot, echo=FALSE, fig.cap="Summary of the references used to build the network of trophic (predator-prey) interactions for the MPAN-BB ecosystem."}

# Load packages
library(tidyverse)
library(ggplot2)

# Load data
load("../data/cleaned-data_sep22.rda")

# Discard low resolution interactions
int_good_res <- int_raw %>% 
  filter(!str_detect(Prey, "\\*$")) %>% 
  filter(!str_detect(Predator, "\\*$")) %>% 
  dplyr::select(Prey, Predator, PreyGroup, PredGroup, Reference) %>% 
  distinct(Prey, Predator, .keep_all = TRUE)

# Figure 1. Plot resuming references
biblio <- data.frame(unique(int_good_res$Reference))
colnames(biblio) <- "Reference"
biblio <- biblio %>% 
  mutate(Type = case_when(str_detect(Reference, "pers.com.") ~ "PersComm",
                          str_detect(Reference, "etal") ~ "Article",
                          str_detect(Reference, "&") ~ "Article",
                          str_detect(Reference, "Encyclopedia of Life") ~ "DataBase",
                          str_detect(Reference, "GloBI") ~ "DataBase",
                          str_detect(Reference, "GATEWAy") ~ "DataBase",
                          str_detect(Reference, "PhDTesis") ~ "Thesis",
                          TRUE ~ "Article"))
ggplot(biblio) +
  geom_bar(aes(x = Type, fill = Type)) +
  theme_bw() +
  labs(x = "Reference", y = "Count") +
  annotate("text", x = Inf, y = Inf, label = paste("Total = ", nrow(biblio), sep = ""), vjust=1, hjust=1)

```

\newpage

```{r echo=FALSE, results='asis'}

# Load packages
library(knitr)
library(dplyr)
library(kableExtra)

# Load data
load("../data/cleaned-data_sep22.rda")

# Discard low resolution interactions
int_good_res <- int_raw %>% 
  filter(!str_detect(Prey, "\\*$")) %>% 
  filter(!str_detect(Predator, "\\*$")) %>% 
  dplyr::select(Prey, Predator, PreyGroup, PredGroup, Reference) %>% 
  distinct(Prey, Predator, .keep_all = TRUE)

# Table 1. List of interactions
knitr::kable(int_good_res %>% arrange(., (Predator)), format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE,
             caption = "List of predator-prey (trophic) interactions used to build the network for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).") %>%
  column_spec(5, width = "0.5in") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 6)

```

\newpage

```{r echo=FALSE, results='asis'}

# Load packages
library(knitr)
library(dplyr)
library(kableExtra)

# Load data
load("../data/cleaned-data_sep22.rda")
load("../data/foodweb-data_jan23.rda")

# Tidy data
df_g <- igraph::as_data_frame(g, 'both')
sp_list <- df_g[["vertices"]] %>% 
  rename("TrophicSpecies" = "name") %>% 
  left_join(sp_raw) %>% 
  dplyr::select(TrophicSpecies, FunctionalGroup, Reference_pres, Observation) %>% 
  rename("Species" = "TrophicSpecies", "Reference" = "Reference_pres") %>% 
  mutate(Observation = case_when(Observation %in% c("Registrado Psolus_sp; Martinez sugiere presencia de P. segregatus", "Registrado Psolus_sp; Martinez sugiere presencia de P. patagonicus", "Registrado Psolus_sp; Martinez sugiere presencia de P. antarcticus", "Lista de sp no publicada provista por Díaz de Astarloa", "Info from Sup Info (Teso_etal_2019)", "AMPNBB-II", "Abundance data available ?", "Esquema trófico", "Depredadores tope", "Copepoda", "Benthic. Not recorded", "Cirripedia") ~ "", 
                                 Species == "Campylaspis_spp" ~ "Aggregated: Campylaspis_frigida y Campylaspis_bacescui",
                                 Species == "Ophiactis_sp" ~ "Aggregated: Ophiactis_asperula y Ophiactis_spp",
                                 Species == "Brachiopoda_spp" ~ "Aggregated: Magellania_venosa, Liothyrella_uva y Terebratella_dorsata",
                                 TRUE ~ Observation),
         Reference = case_when(Species == "Bacteria" ~ "Guinder_etal_2020",
                               Species == "Necromass" ~ "Riccialdelli_etal_2017", 
                               Species == "Syllidae" ~ "Schejter_etal_2016; Bremec_etal_2019",
                               Species == "Sabellidae" ~ "Schejter_etal_2016; Bremec_etal_2019; Spinelli_etal_2020",
                               Species == "Ophiactis_sp" ~ "Schejter_etal_2016; 2020a; Brogger_pers.com.",
                               Species == "Campylaspis_spp" ~ "Doti_etal_2020",
                               Species == "Brachiopoda_spp" ~ "Schejter_etal_2016", TRUE ~ Reference),
         FunctionalGroup = case_when(Species == "Campylaspis_spp" ~ "Cumacea",
                                     Species == "Brachiopoda_spp" ~ "Brachiopoda", TRUE ~ FunctionalGroup)) %>% 
  arrange(., (Species))

# Table 2. List of species
knitr::kable(sp_list, format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE,
             caption = "List of species for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).") %>%
  column_spec(4, width = "0.5in") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 6)

```

### 2023-01-13 R/3_foodwebexploring.R

@@ -32,8 +32,29 @@ int_need_res <- int_raw %>% filter_at(.vars = vars(Prey, Predator),
 int_good_res <- int_raw %>% 
   filter(!str_detect(Prey, "\\*$")) %>% 
   filter(!str_detect(Predator, "\\*$")) %>% 
-  dplyr::select(Prey, Predator, PreyGroup, PredGroup, PredStrategy, FoodSource) %>% 
+  dplyr::select(Prey, Predator, PreyGroup, PredGroup, PredStrategy, FoodSource, Reference) %>% 
   distinct(Prey, Predator, .keep_all = TRUE)
+
+## Referencias ----
+
+## Revision bibliografica ----
+
+biblio <- data.frame(unique(int_good_res$Reference))
+colnames(biblio) <- "Reference"
+biblio <- biblio %>% 
+  mutate(Type = case_when(str_detect(Reference, "pers.com.") ~ "PersComm",
+                          str_detect(Reference, "etal") ~ "Article",
+                          str_detect(Reference, "&") ~ "Article",
+                          str_detect(Reference, "Encyclopedia of Life") ~ "DataBase",
+                          str_detect(Reference, "GloBI") ~ "DataBase",
+                          str_detect(Reference, "GATEWAy") ~ "DataBase",
+                          str_detect(Reference, "PhDTesis") ~ "Thesis",
+                          TRUE ~ "Article"))
+ggplot(biblio) +
+  geom_bar(aes(x = Type, fill = Type)) +
+  theme_bw() +
+  labs(x = "Bibliography", y = "Count") +
+  annotate("text", x = Inf, y = Inf, label = paste("Total = ", nrow(biblio), sep = ""), vjust=1, hjust=1)
 
 
 ## Objeto igraph ----
@@ -90,4 +111,4 @@ plotTrophLevel(g, ylab = "Trophic level")
 # Save data ----
 
 save(g, int_need_res, int_good_res,
-     file = "data/foodweb-data_sep22.rda")
+     file = "data/foodweb-data_jan23.rda")

### 2023-01-17 1st_Manuscript/ManuscriptDraft.Rmd
January 2023 updates

@@
 
-The objective of the present work was to build the network of trophic (predator-prey) interactions for the Marine Protected Area Namuncurá - Banco Burdwood I (MPAN-BB), and characterize it in terms of complexity and structure using a network approach.
+The objective of the present work was to characterize the trophic (predator-prey) interactions of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB) in terms of complexity and structure using a network approach.
 

### 2023-01-17 1st_Manuscript/SupMaterial.Rmd
January 2023 updates

@@
 # Load data
-load("../data/cleaned-data_sep22.rda")
+load("../data/cleaned-data_jan23.rda")
 
@@
 library(kableExtra)
+library(pander)
 
 # Load data
-load("../data/cleaned-data_sep22.rda")
+load("../data/cleaned-data_jan23.rda")
 
@@
   filter(!str_detect(Predator, "\\*$")) %>% 
-  dplyr::select(Prey, Predator, PreyGroup, PredGroup, Reference) %>% 
+  dplyr::select(Prey, Predator, Reference, Reference_link) %>% 
   distinct(Prey, Predator, .keep_all = TRUE)
@@
 # Table 1. List of interactions
-knitr::kable(int_good_res %>% arrange(., (Predator)), format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE,
-             caption = "List of predator-prey (trophic) interactions used to build the network for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).") %>%
-  column_spec(5, width = "0.5in") %>%
-  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 6)
+knitr::kable(int_good_res %>% arrange(., (Predator)), booktabs = TRUE, format = "latex", longtable = T, col.names = c("Prey","Predator","Reference", "Link"), caption = "List of predator-prey (trophic) interactions used to build the network for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).") %>%
+  column_spec(1:3, width="2cm") %>% 
+  column_spec(4, width="14cm") %>% 
+  kable_styling(latex_options = c("hold_position","repeat_header"), font_size = 4) %>% 
+  landscape()
+
+# pandoc.table(int_good_res %>% arrange(., (Predator)) %>% mutate(Reference_link = paste('\\tiny', Reference_link)) %>% rename("Link"="Reference_link"), style="multiline", split.tables = Inf, justify = c("left","left","left","right"),
+#              caption = "List of predator-prey (trophic) interactions used to build the network for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).")
 
@@
 # Load data
-load("../data/cleaned-data_sep22.rda")
+load("../data/cleaned-data_jan23.rda")
 load("../data/foodweb-data_jan23.rda")
@@
   left_join(sp_raw) %>% 
-  dplyr::select(TrophicSpecies, FunctionalGroup, Reference_pres, Observation) %>% 
+  dplyr::select(TrophicSpecies, FunctionalGroup, Reference_pres, Reference_pres_link, Observation) %>% 
   rename("Species" = "TrophicSpecies", "Reference" = "Reference_pres") %>% 
@@
 # Table 2. List of species
-knitr::kable(sp_list, format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE,
-             caption = "List of species for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).") %>%
-  column_spec(4, width = "0.5in") %>%
-  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 6)
+knitr::kable(sp_list, format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Group","Reference","Link","Observation"), caption = "List of species for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).") %>%
+  column_spec(1:3, width="3cm") %>%
+  column_spec(4:5, width="5cm") %>% 
+  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 4) %>% 
+  landscape()
 

### 2023-01-17 R/1_datawrangling.R

@@ -26,7 +26,7 @@ sp_raw <- sp_raw %>%
 
 ## Lista de Interacciones ----
 
-int_raw <- read.csv("data/ListaInteracciones_AMPNBB_sep_22.csv")
+int_raw <- read.csv("data/ListaInteracciones_AMPNBB_jan23.csv")
 
 int_raw <- int_raw %>% 
   # low-resolved Phytoplankton
@@ -145,4 +145,4 @@ spp_tl_1 <- spp_db %>%
 ## Save data ----
 
 save(sp_raw, int_raw,
-     file = "data/cleaned-data_sep22.rda")
+     file = "data/cleaned-data_jan23.rda")

### 2023-01-17 R/2_dataexploring.R

@@ -17,7 +17,7 @@ ipak(packages)
 
 # Cargar datos ----
 
-load("data/cleaned-data_sep22.rda")
+load("data/cleaned-data_jan23.rda")
 
 
 # Lista de Especies ----

### 2023-01-17 R/3_foodwebexploring.R

@@ -17,7 +17,7 @@ ipak(packages)
 
 # Cargar datos ----
 
-load("data/cleaned-data_sep22.rda")
+load("data/cleaned-data_jan23.rda")
 
 
 # Red trófica ----
@@ -87,7 +87,10 @@ g_dec
 
 group_sp <- as.data.frame((V(g)$name)) %>% 
   mutate(as.data.frame(V(g)$FunctionalGroup)) %>%
-  rename("TrophicSpecies" = 1, "FunctionalGroup" = 2)
+  rename("TrophicSpecies" = 1, "FunctionalGroup" = 2) %>% 
+  mutate(FunctionalGroup = case_when(TrophicSpecies == "Brachiopoda_spp" ~ "Brachiopoda",
+                                     TrophicSpecies == "Campylaspis_spp" ~ "Cumacea",
+                                     TRUE ~ FunctionalGroup))
 
 group_sp <- group_sp %>%
   count(FunctionalGroup) %>%

### 2023-01-17 R/1_datawrangling.R
January updates

@@ -17,7 +17,7 @@ ipak(packages)
 
 ## Lista de Especies ----
 
-sp_raw <- read.csv("data/ListaEspecies_AMPNBB_sep_22.csv")
+sp_raw <- read.csv("data/ListaEspecies_AMPNBB_jan23.csv")
 colnames(sp_raw)
 sp_raw <- sp_raw %>% 
   add_count(FunctionalGroup, name = "Richness") %>% 

### 2023-01-18 1st_Manuscript/ManuscriptDraft.Rmd
Finished M&M, starting Results

--- 2022-11-24 1st_Manuscript/ManuscriptDraft.Rmd
@@
 
-```{r setup, include=FALSE} 
+```{r setup, include=FALSE, echo=FALSE} 
 knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
+library(knitr)
+library(tidyverse)
+library(pander)
+library(ggplot2)
+library(kableExtra)
+
 ```
@@
 
-The objective of the present work was to build the network of predator-prey interactions (food web) for the Marine Protected Area Namuncurá - Banco Burdwood I (MPAN-BB), and characterize it in terms of complexity and structure.
+The objective of the present work was twofold: characterize the network of trophic interactions in terms of complexity and structure for the MPAN-BB ecosystem, and describe the species' role in such network framework.
 
@@
 The BB is surrounded by steep flanks of more than 3000 m depth through which strong currents circulate [@Piola1989; @Reta2014; @Matano2019].
-Intense upwelling and mixing occur over it, entraining deep nutrient rich waters into the photic layer [@Piola2009; @Matano2019] and resulting in a fairly homogeneous water column both spatially and temporally [@Glorioso1995; @Guerrero1999; @Matano2019].
-Physical features in the MPAN-BB are fairly stable, with salinity averaging 34 all year round and temperature ranging between 4 and 8 ºC overall [@Guerrero1999; @Acha2004; @Piola2009].
+Intense upwelling and mixing occur over it, entraining deep nutrient rich waters into the photic layer [@Piola2009; @Matano2019], and resulting in a fairly homogeneous water column both spatially and temporally [@Glorioso1995; @Guerrero1999; @Matano2019].
+Physical features in the MPAN-BB are fairly stable, with salinity averaging 34 all year round and temperature ranging between 4 and 8ºC overall [@Guerrero1999; @Acha2004; @Piola2009].
 
-### Food web construction
+```{r figure1}
+# Map of MPAN-BB provided by Lu R. (?)
 
-### Food web analysis
+```
 
-We analyzed the MPA food web at 2 levels: 1) global, network-level properties (considers all species and interactions), and 2) species, species-level properties (considers the species’ role in the food web).
-GLOBAL
-Complexity: # trophic species, # interactions, link density, connectance
-Degree distribution
-Mean shortest path length
-Omnivory
-Distribution of prey and predator
-Distribution of interactions by functional group
+### Network construction
 
-SPECIES
-Centrality indices (betweenness, closeness)
-Trophic similarity
-Topological role
+In order to build the network of predator-prey interactions we reviewed more than 150 references considering published articles, databases and doctoral theses.
+Furthermore, we took into account personal communications from experts belonging to the working group of the study area (https://www.pampazul.gob.ar/tag/banco-burdwood/).
+The diversity of the expertise of the authors contributing to the present study was a key factor in generating the quality of the network, and inherently improved the network representation of the MPAN-BB ecosystem.
+A list of the bibliography used to build the network is presented in Supplementary Material (Table S1).
+
+Due to a lack of trophic data resolution for some species inhabiting the MPAN-BB, we follow the concept of trophic species, here defined as aggregated groups of taxa.
+In most cases we followed this when data on specific biological species were not available, but for some cases we collapsed species when taxa shared the same set of predators and prey (trophic similarity criteria).
+Details about this can be found in Supplementary Material (Table S2).
+
+With the gathered trophic data we constructed an interaction matrix of pairwise interactions; a value of 1 or 0 was assigned to each element a_ij of the matrix depending on whether the j-species preyed or not on the i-species.
+Then we transformed such matrix into an oriented graph with L trophic interactions between S nodes or species.
+The orientation or direction of the graph follows the flow of energy and matter in the network, from prey to predator.
+
+### Network analysis
+
+We analyzed the MPAN-BB network of trophic interactions, hereafter food web, at two levels: 1) global, considering species and interactions of the entire network; and 2) species, considering interactions and species related to a particular species.
+For the global-level analysis we calculated several network properties commonly used to describe the complexity and structure in food webs [@Pascual2005]: (1) number of species S; (2) number of interactions or links L; (3) link density L/S; (4) Connectance L/S^2; (5) omnivory Omn; and (6) shortest path length SPL.
+Also, we estimated the (7) degree distributions for the entire network, for each functional group (e.g.
+Amphipoda, Ascidiacea, Bivalvia, Fish, Marine mammals, Seabirds, etc.), and for prey and predators (Table 1).
+The functional group's degree distributions show the most-connected species; the prey's distribution indicates the amount of predators per prey; and the predator's distribution represents the amount of prey per predator.
+For the species-level analysis we considered the following properties: (1) betweenness Btw; (2) closeness Cl; (3) trophic level TL; (4) trophic similarity TS; and (5) topological role TR (Table 1).
+These properties provide a general appropriate description of species' role in food webs [@Cirtwill2018].
+
+All network analyses and graphs were performed in R version 4.2.2 [@RCoreTeam2022], mainly using 'igraph' [@Csardi2006] and ‘multiweb’ [@Saravia2022a] packages.
+The source code and data are available at https://github.com/TomasMarina/Banco-Burdwood.
+
+```{r table1, results='asis'}
+
+# Table 1. Network metrics
+table1 <- tibble(Name="Number of species", Definition="Number of trophic species in a food web.", Implications="It represents the species diversity and has implications for the persistence of the ecosystem.", Reference = "May 1973, Tilman 1996")
+
+table1 <- add_row(table1, Name="Number of interactions", Definition="Total number of trophic interactions in a food web.", Implications="It represents the number of pathways along which matter and energy can flow.", Reference="Dunne et al.
+2002")
+
+table1 <- add_row(table1, Name="Link density", Definition="Ratio of interactions to species in a food web", Implications="It represents the average number of interactions per species; informs about how connected species are in the food-web.", Reference="Dunne et al.
+2002")
+
+table1 <- add_row(table1, Name="Connectance", Definition="Proportion of potential links among species that are actually realized.", Implications="It measures the probability of interactions; it is a fundamental measure of network complexity.
+Connectance can be negatively or positively associated with food web robustness, depending on the network structure (random vs non-random) or how the strength of the interactions are distributed.", Reference = "Martinez 1991")
+
+table1 <- add_row(table1, Name="Degree distribution", Definition="Probability of trophic species P(k) that have k or more interactions (both predator and prey links).", Implications="It suggests on the vulnerability of complex food webs against random failures and intentional attacks (i.e.
+species extinctions).", Reference="Albert & Barabási 2002")
+
+table1 <- add_row(table1, Name="Omnivory", Definition="Species feeding on prey from more than one trophic level.", Implications="It influences food web's stability; intermediate levels of omnivory may stabilize it and may diffuse top-down effects thus reduce the probability of trophic cascades.", Reference = "McCann & Hastings 1997")
+
+table1 <- add_row(table1, Name="Shortest path length", Definition="Average shortest path length between all pairs of species.", Implications="A short path length imply a rapid spread of an impact (e.g.
+invasion, population fluctuation, local extinction) throughout the food web.", Reference="Watts & Strogatz 1998")
+
+table1 <- add_row(table1, Name="Betweenness", Definition="Number of shortest paths going through a species.", Implications=" Species with high betweenness act as “bridges”; if removed, would have rapidly spreading effects in the food web.", Reference="Freeman 1979")
+
+table1 <- add_row(table1, Name="Closeness", Definition="Number of steps required to reach every other species from a given species.", Implications="The removal of a species with high closeness will affect the most other species in the food web.", Reference="Freeman 1979")
+
+tabble1 <- add_row(table1, Name="Trophic level", Definition="It represents the number of interactions that separates a species from the base of the food web.", Implications="It indicates the position the species occupies in the food web; commonly categorized as producer, intermediate consumer and top predator.", Reference="Borelli & Ginzburg 2014")
+
+table1 <- add_row(table1, Name="Trophic similarity", Definition="Trophic overlap based on shared and unique resources (prey) and consumers (predators).", Implications="It measures one of the most important aspects of species’ niches, the trophic niche, and functional aspects of biodiversity.", Reference="Martinez 1991")
+
+table1 <- add_row(table1, Name="Topological role", Definition="Species role according to interactions within and across modules (subgroups of species).", Implications="Four roles are defined: module hub, module specialist, module connector and network connector.
+Species with the same role are expected to have similar topological properties.", Reference="Guimera 2005")
+
+pandoc.table(table1, digits = 4, colnames("Property","Definition","Implication","Reference"), style="multiline", split.tables = Inf, justify = c('left','left','left','right'),
+             caption = "List of network properties analyzed, definitions, and relevant ecological implications related to food web complexity and structure.")
+
+```
 
@@
 ### Network-level properties
+
+```{r figure2&table2}
+# Food web graph and table
+
+load()
+
+plot_troph_level(vertexLabel = F, modules = F, ylab = "Trophic level")
+
+knitr::kable(prop_topol %>% select())
+
+```
+
+```{r figure3}
+# Degree distributions: network, prey, predator & group
+# above row (network, prey, predator), below row (group)
+
+```
 
@@
 
+```{r figure4}
+# Betweenness, Closeness & Trophic similarity by Trophic level
+
+```
+
+```{r figure5}
+# Topological roles
+
+```
+
 ‘Network connector’ and ‘module connector’ species are responsible for linking modules and maintaining the connectivity of the food web. TL range for these species: 1 - 3.86.
@@
 ## Discussion
+
+### Food web complexity and structure
+
+### Species' role
 

### 2023-01-19 R/4_foodwebanalysis.R
January 2023 updates

@@ -18,8 +18,8 @@ ipak(packages)
 
 # Cargar datos ----
 
-load("data/cleaned-data_sep22.rda")
-load("data/foodweb-data_sep22.rda")
+load("data/cleaned-data_jan23.rda")
+load("data/foodweb-data_jan23.rda")
 
 
 # Análisis ----
@@ -27,11 +27,11 @@ load("data/foodweb-data_sep22.rda")
 ## Escala global ----
 
 # Propiedades topológicas
-prop.topol <- multiweb::calc_topological_indices(g)
+prop_topol <- multiweb::calc_topological_indices(g)
 
 # Prop. sp B, I y T
-prop.bas <- prop.topol$Basal/prop.topol$Size
-prop.top <- prop.topol$Top/prop.topol$Size
+prop.bas <- prop_topol$Basal/prop_topol$Size
+prop.top <- prop_topol$Top/prop_topol$Size
 prop.int <- 1 - (prop.bas + prop.top)
 prop.bas+prop.top+prop.int  # chequear sum(prop)=1
 
@@ -123,7 +123,7 @@ ts <- TrophicSimilarity(cc)
 mts <- tibble(TrophicSpecies = rownames(ts), meanTrophicSimil = colMeans(ts))  # data frame
 
 # Guardar como data frame y .csv
-spp_id <- as.data.frame(1:prop.topol$Size)
+spp_id <- as.data.frame(1:prop_topol$Size)
 spp_name <- as.data.frame(V(g)$name)
 spp_fg <- as.data.frame(V(g)$FunctionalGroup)
 spp_totdegree <- as.data.frame(V(g)$TotalDegree)
@@ -159,7 +159,7 @@ spp_total <- spp_total %>%
                              FunctionalGroup %in% c("Fish_Demersal") ~ "Demersal"))
 
 
-write_csv(spp_total, file = "results/spp_prop_sep22.csv")
+write_csv(spp_total, file = "results/spp_prop_jan23.csv")
 
 
 # Resolución de la red ----
@@ -173,5 +173,5 @@ sp_prop <- sp_count/vcount(g_up)
 
 # Guardar datos ----
 
-save(g_up, deg_dist_fit, prop.topol, spp_total, top.role, top.role.df,
-     file = "results/summary_results_sep22.rda")
+save(g_up, g, deg_dist_fit, prop_topol, spp_total, top.role, top.role.df,
+     file = "results/summary_results_jan23.rda")

### 2023-01-19 1st_Manuscript/ManuscriptDraft.Rmd
Add figures & tables

@@
 bibliography: "AMPBancoBurdwood.bib"
+header-includes:
+  - \usepackage[left]{lineno}
+  - \linenumbers
 ---
@@
 library(kableExtra)
+library(multiweb)
+library(ggjoy)
+library(ggpubr)
+library(igraph)
+library(gridExtra)
+library(grid)
 
@@
 
-The objective of the present work was twofold: characterize the network of trophic interactions in terms of complexity and structure for the MPAN-BB ecosystem, and describe the species' role in such network framework.
+Brief description and ecological importance of MPAN-BB
+
+The objective of the present work was twofold: characterize the network of trophic interactions in terms of complexity and structure for the MPA Namuncurá-Banco Burdwood ecosystem, and describe the species' role in such network framework.
 
@@
 
-The MPAN-BB is a shallow submarine plateau called Burdwood Bank (BB) located 150 km east of Isla de los Estados and 200 km south from Malvinas/Falkland Islands (Figure 1).
+The MPA Namuncurá-Banco Burdwood is a shallow submarine plateau called Burdwood Bank (BB) located 150 km east of Isla de los Estados and 200 km south from Malvinas/Falkland Islands (Figure 1).
 It comprises nearly 34.000 km^2 circumscribed by the 200 m isobath, between 54º–55ºS and 56º–62ºW, with a slight slope extended nearly 370 km east–west.
@@
 
-```{r figure1}
+```{r figure1, echo=FALSE}
 # Map of MPAN-BB provided by Lu R. (?)
@@
 Furthermore, we took into account personal communications from experts belonging to the working group of the study area (https://www.pampazul.gob.ar/tag/banco-burdwood/).
-The diversity of the expertise of the authors contributing to the present study was a key factor in generating the quality of the network, and inherently improved the network representation of the MPAN-BB ecosystem.
+The diversity of the expertise of the authors contributing to the present study was a key factor in generating the quality of the network, and inherently improved the network representation of the MPA Namuncurá-Banco Burdwood ecosystem.
 A list of the bibliography used to build the network is presented in Supplementary Material (Table S1).
 
-Due to a lack of trophic data resolution for some species inhabiting the MPAN-BB, we follow the concept of trophic species, here defined as aggregated groups of taxa.
+Due to a lack of trophic data resolution for some species inhabiting the MPA Namuncurá-Banco Burdwood, we follow the concept of trophic species, here defined as aggregated groups of taxa.
 In most cases we followed this when data on specific biological species were not available, but for some cases we collapsed species when taxa shared the same set of predators and prey (trophic similarity criteria).
@@
 
-We analyzed the MPAN-BB network of trophic interactions, hereafter food web, at two levels: 1) global, considering species and interactions of the entire network; and 2) species, considering interactions and species related to a particular species.
+We analyzed the MPA Namuncurá-Banco Burdwood network of trophic interactions, hereafter food web, at two levels: 1) global, considering species and interactions of the entire network; and 2) species, considering interactions and species related to a particular species.
 For the global-level analysis we calculated several network properties commonly used to describe the complexity and structure in food webs [@Pascual2005]: (1) number of species S; (2) number of interactions or links L; (3) link density L/S; (4) Connectance L/S^2; (5) omnivory Omn; and (6) shortest path length SPL.
-Also, we estimated the (7) degree distributions for the entire network, for each functional group (e.g.
-Amphipoda, Ascidiacea, Bivalvia, Fish, Marine mammals, Seabirds, etc.), and for prey and predators (Table 1).
-The functional group's degree distributions show the most-connected species; the prey's distribution indicates the amount of predators per prey; and the predator's distribution represents the amount of prey per predator.
+Also, we estimated the (7) degree distributions for the food web, for prey and predators, and for each functional group (e.g.
+Amphipoda, Ascidiacea, Bivalvia, Fish, Marine mammals, Seabirds, etc.) (Table 1).
+The prey and predator distributions indicate the frequency of prey among predators, and viceversa; the functional group's degree shows the distribution of interactions within groups.
 For the species-level analysis we considered the following properties: (1) betweenness Btw; (2) closeness Cl; (3) trophic level TL; (4) trophic similarity TS; and (5) topological role TR (Table 1).
-These properties provide a general appropriate description of species' role in food webs [@Cirtwill2018].
+These properties provide a general appropriate description of species' role in empirical complex food webs [@Cirtwill2018].
 
@@
 
-```{r table1, results='asis'}
+```{r table1, echo=FALSE, results='asis'}
 
@@
 
-```{r figure2&table2}
-# Food web graph and table
+```{r figure2, echo=FALSE, fig.align='center', fig.cap="Graph of the food web of MPA Namuncurá-Banco Burdwood.
+Circles represent the species and arrows the trophic interactions.
+Colour gradient indicate the trophic level.
+Circle diameter is relative to the number of interactions."}
+# Food web graph
 
-load()
+load("../results/summary_results_jan23.rda")
 
-plot_troph_level(vertexLabel = F, modules = F, ylab = "Trophic level")
-
-knitr::kable(prop_topol %>% select())
+plot <- plot_troph_level(g, vertexLabel = F, modules = F, ylab = "Trophic level")
 
@@
 
-```{r figure3}
-# Degree distributions: network, prey, predator & group
+```{r table2, echo=FALSE}
+
+load("../results/summary_results_jan23.rda")
+
+knitr::kable(round(prop_topol,2) %>% dplyr::select(Size, Links, LD, Connectance, Omnivory, PathLength), col.names = c("Species","Interactions","Density","Connectance","Omnivory","Path length"),
+                      caption = "Global-level properties of the food web of MPA Namuncurá-Banco Burdwood. See table 1 for definitions and ecological relevance.")
+
+```
+
+```{r figure3, echo=FALSE, fig.height = 28, fig.width = 20, fig.cap="Degree distributions for the (A) food web, for (B) prey among predators, (C) predators among prey, and (D) for each functional group."}
+# Degree distributions: network, predator, prey & group
 # above row (network, prey, predator), below row (group)
+
+load("../data/foodweb-data_jan23.rda")
+load("../results/summary_results_jan23.rda")
+
+# Network Degree
+degree <- as.data.frame(degree(g, mode = "total"))
+plot_totdeg <- ggplot(degree, aes(degree[,1])) +
+    geom_histogram(bins = 100, alpha = 0.3, color = "black") +
+    labs(x = "Number of interactions (Degree)", y = "Frequency") +
+    theme_bw() +
+    theme(legend.position = "none",
+          axis.text.x = element_text(size = 26),
+          axis.text.y = element_text(size = 26),
+          axis.title.x = element_text(face = "bold", size = 26),
+          axis.title.y = element_text(face = "bold", size = 26))
+
+# Predator Degree
+# Generality (generalistas vs especialistas)
+plot_preddeg <- spp_total %>% 
+    filter(NumPrey != 0) %>% 
+    ggplot(., aes(x = NumPrey)) +
+    geom_histogram(stat = "count") +
+    labs(x = "Predators", y = "Number of prey") +
+    theme_bw() +
+    theme(legend.position = "none",
+          axis.text.x = element_text(size = 26),
+          axis.text.y = element_text(size = 26),
+          axis.title.x = element_text(face = "bold", size = 26),
+          axis.title.y = element_text(face = "bold", size = 26)) #+
+# annotate("text", x = Inf, y = Inf, label = paste("Prey per predator = ", round(prop_topol$Generality, 2), sep = ""),
+#          size = 5, vjust=1, hjust=1))
+
+# Prey Degree
+# Vulnerability (energy flows)
+plot_preydeg <- spp_total %>% 
+    filter(NumPred != 0) %>% 
+    ggplot(., aes(x = NumPred)) +
+    geom_histogram(stat = "count") +
+    labs(x = "Prey", y = "Number of predators") +
+    theme_bw() +
+    theme(legend.position = "none",
+          axis.text.x = element_text(size = 26),
+          axis.text.y = element_text(size = 26),
+          axis.title.x = element_text(face = "bold", size = 26),
+          axis.title.y = element_text(face = "bold", size = 26)) #+
+# annotate("text", x = Inf, y = Inf, label = paste("Predators per prey = ", round(prop_topol$Vulnerability, 2), sep = ""),
+#          size = 5, vjust=1, hjust=1))
+
+# Group Degree
+un.prey <- as.data.frame(unique(int_good_res$PreyGroup))  # prey groups
+un.pred <- as.data.frame(unique(int_good_res$PredGroup))  # pred groups
+colnames(un.prey) <- "Group"
+colnames(un.pred) <- "Group"
+unique_FG <- unique(bind_rows(un.pred, un.prey))  # 35 groups
+
+col_palette <- scales::hue_pal()(nrow(unique_FG))
+FGColors <- setNames(col_palette, levels(unique_FG$Group))
+unique_FG <- cbind(unique_FG, as.data.frame(FGColors))
+colnames(unique_FG) <- c("FunctionalGroup", "FGColor")
+
+plot_grpdeg <- spp_total %>% 
+    add_count(FunctionalGroup) %>% 
+    filter(n > 2) %>% 
+    group_by(FunctionalGroup) %>% 
+    mutate(TL_fg = mean(TL)) %>% 
+    ggplot(., aes(x = TotalDegree, y = reorder(FunctionalGroup, TL_fg), fill = FunctionalGroup)) + 
+    geom_joy(scale = 3.75) +
+    scale_fill_manual(values = FGColors) +
+    labs(x = "Number of interactions", y = "Functional group", tag="D") +
+    theme_joy(grid = FALSE) +
+    theme(legend.position = "none",
+          axis.text.x = element_text(size = 26),
+          axis.text.y = element_text(size = 20),
+          axis.title.x = element_text(face = "bold", size = 26),
+          axis.title.y = element_text(face = "bold", size = 26),
+          plot.tag = element_text(face = "bold", size = 32),
+          plot.tag.position = c(0.05, 1))
+
+# Figure
+a <- plot_totdeg
+b <- plot_preddeg
+c <- plot_preydeg
+d <- plot_grpdeg
+
+# Move to a new page
+grid.newpage()
+# Nested ggarrange
+ggarrange(a,                                                                                         # First row
+          ggarrange(b, c, ncol = 2, labels = c("B", "C"), font.label=list(color="black",size=30)),   # Second row
+          ggarrange(d, ncol = 1),                                                                    # Third row
+          nrow = 3, labels = "A",
+          font.label=list(color="black",size=30))
+
+# # Create layout : nrow = 2, ncol = 2
+# pushViewport(viewport(layout = grid.layout(3, 2)))
+# # A helper function to define a region on the layout
+# define_region <- function(row, col){
+#   viewport(layout.pos.row = row, layout.pos.col = col)
+# } 
+# # Arrange the plots
+# print(a, vp = define_region(1, 1:2))
+# print(b, vp = define_region(2, 1))
+# print(c, vp = define_region(2, 2))
+# print(d, vp = define_region(3, 1:2))
 
@@
 
-```{r figure4}
+```{r figure4, echo=FALSE}
 # Betweenness, Closeness & Trophic similarity by Trophic level
@@
 
-```{r figure5}
+```{r figure5, echo=FALSE}
 # Topological roles

### 2023-01-20 1st_Manuscript/ManuscriptDraft.Rmd
Figures 4 & 5

@@
 
-# Figure
+# Arrange figure
 a <- plot_totdeg
@@
 # Nested ggarrange
-ggarrange(a,                                                                                         # First row
+figure_3 <- ggarrange(a,                                                                                         # First row
           ggarrange(b, c, ncol = 2, labels = c("B", "C"), font.label=list(color="black",size=30)),   # Second row
@@
           font.label=list(color="black",size=30))
+figure_3
 
@@
 
-```{r figure4, echo=FALSE}
-# Betweenness, Closeness & Trophic similarity by Trophic level
+```{r figure4, echo=FALSE, fig.width = 20, fig.height=20, fig.cap="Species-level properties (A) betwenness, (B) closeness, and (C) trophic similarity by trophic level (equal or greater than 2).
+See table 1 for definitions and ecological relevance."}
+# Betweenness, Closeness & Trophic similarity by Trophic level (>= 2)
+
+# Betweenness
+plot_sp_bt <- spp_total %>% 
+  filter(TL >= 2) %>% 
+  ggplot(., aes(x = TL, y = Between)) +
+  geom_point() +
+  #geom_vline(xintercept = c(spp_nt_12+1, spp_nt_12+spp_nt_13+1, spp_nt_14+1), linetype = "longdash", colour = "red") +
+  labs(x = "Trophic level", y = "Betweenness") +
+  theme_bw() +
+  theme(panel.grid = element_blank(),
+        axis.text.x = element_text(size = 26),
+        axis.text.y = element_text(size = 26),
+        axis.title = element_text(size = 26, face = "bold"))
+
+# Closeness
+plot_sp_cl <- spp_total %>% 
+  filter(TL >= 2) %>%
+  ggplot(., aes(x = TL, y = Close)) +
+  geom_point() +
+  #geom_vline(xintercept = c(spp_nt_12+1, spp_nt_12+spp_nt_13+1, spp_nt_14+1), linetype = "longdash", colour = "red") +
+  labs(x = "Trophic level", y = "Closeness") +
+  theme_bw() +
+  theme(panel.grid = element_blank(),
+        axis.text.x = element_text(size = 26),
+        axis.text.y = element_text(size = 26),
+        axis.title = element_text(size = 26, face = "bold"))
+
+# Trophic similarity
+plot_sp_ts <- spp_total %>% 
+  filter(TL >= 2) %>%
+  ggplot(., aes(x = TL, y = meanTrophicSimil)) +
+  geom_point() +
+  #geom_vline(xintercept = c(spp_nt_12+1, spp_nt_12+spp_nt_13+1, spp_nt_14+1), linetype = "longdash", colour = "red") +
+  labs(x = "Trophic level", y = "Trophic similarity") +
+  theme_bw() +
+  theme(panel.grid = element_blank(),
+        axis.text.x = element_text(size = 26),
+        axis.text.y = element_text(size = 26),
+        axis.title = element_text(size = 26, face = "bold"))
+
+# Move to a new page
+grid.newpage()
+# Arrange figure
+figure_4 <- ggarrange(plot_sp_bt + rremove("xlab"), plot_sp_cl + rremove("xlab"), plot_sp_ts + rremove("xlab"),
+                      labels = c("A","B","C"), ncol=2, nrow=2,
+                      font.label = list(size = 30, color = "black"))
+annotate_figure(figure_4, bottom = textGrob("Trophic level", gp = gpar(fontface="bold", col="black", fontsize=26)))
 
@@
 # Topological roles
+
+top.role.col <- hcl.colors(4, palette = "Purple-Green")
+TRColor <- setNames(top.role.col, levels(as.factor(V(g_up)$TopRole)))
+TRColor <- as.data.frame(TRColor) %>% 
+  mutate(TopRole = c("hubcon", "modcon", "modhub", "modspe"))
+#show_col(top.role.col)  # shows color & code
+data_TRColor <- spp_total %>% 
+  dplyr::select(TopRole, everything()) %>% 
+  left_join(TRColor)
+g_up_c <- g_up %>% 
+  set_vertex_attr("TRColor", value = data_TRColor$TRColor)
+
+# Filter network connectors ('hubcon') & module connectors ('modcon'). Violet & pink respectively
+sp_con <- spp_total %>% 
+  filter(TopRole == "hubcon" | TopRole == "modcon")
+
+# Move to a new page
+grid.newpage()
+# Arrange figure
+figure_5 <- plot_troph_level(g_up_c, vertexLabel = F, modules = F, ylab = "Trophic level", vertex.color = V(g_up_c)$TRColor)
 

### 2023-01-23 1st_Manuscript/ManuscriptDraft.Rmd
Page breaks

@@
 
+\newpage
+
 ## Introduction
@@
 The objective of the present work was twofold: characterize the network of trophic interactions in terms of complexity and structure for the MPA Namuncurá-Banco Burdwood ecosystem, and describe the species' role in such network framework.
+
+\newpage
 
@@
 
+\newpage
+
 ## Results
@@
 
-```{r figure2, echo=FALSE, fig.align='center', fig.cap="Graph of the food web of MPA Namuncurá-Banco Burdwood.
+```{r figure2, echo=FALSE, fig.align='center', fig.width = 20, fig.height=20, fig.cap="Graph of the food web of MPA Namuncurá-Banco Burdwood.
 Circles represent the species and arrows the trophic interactions.
@@
 
+par(cex.axis=1.5, cex.lab=1.5)
 plot <- plot_troph_level(g, vertexLabel = F, modules = F, ylab = "Trophic level")
@@
 
-```{r figure3, echo=FALSE, fig.height = 28, fig.width = 20, fig.cap="Degree distributions for the (A) food web, for (B) prey among predators, (C) predators among prey, and (D) for each functional group."}
+\newpage
+
+```{r figure3, echo=FALSE, fig.height = 28, fig.width = 20, fig.cap="Degree distributions for the (A) food web, for (B) prey among predators, (C) predators among prey, and (D) for each functional group.
+Groups are vertically ordered by trophic level."}
 # Degree distributions: network, predator, prey & group
@@
 
+\newpage
+
 ```{r figure4, echo=FALSE, fig.width = 20, fig.height=20, fig.cap="Species-level properties (A) betwenness, (B) closeness, and (C) trophic similarity by trophic level (equal or greater than 2).
@@
 
-```{r figure5, echo=FALSE}
-# Topological roles
-
-top.role.col <- hcl.colors(4, palette = "Purple-Green")
-TRColor <- setNames(top.role.col, levels(as.factor(V(g_up)$TopRole)))
-TRColor <- as.data.frame(TRColor) %>% 
-  mutate(TopRole = c("hubcon", "modcon", "modhub", "modspe"))
-#show_col(top.role.col)  # shows color & code
-data_TRColor <- spp_total %>% 
-  dplyr::select(TopRole, everything()) %>% 
-  left_join(TRColor)
-g_up_c <- g_up %>% 
-  set_vertex_attr("TRColor", value = data_TRColor$TRColor)
-
-# Filter network connectors ('hubcon') & module connectors ('modcon'). Violet & pink respectively
-sp_con <- spp_total %>% 
-  filter(TopRole == "hubcon" | TopRole == "modcon")
-
-# Move to a new page
-grid.newpage()
-# Arrange figure
-figure_5 <- plot_troph_level(g_up_c, vertexLabel = F, modules = F, ylab = "Trophic level", vertex.color = V(g_up_c)$TRColor)
-
-```
-
 ‘Network connector’ and ‘module connector’ species are responsible for linking modules and maintaining the connectivity of the food web. TL range for these species: 1 - 3.86.
@@
 
+\newpage
+
 ## References

### 2023-01-23 1st_Manuscript/SupMaterial.Rmd
Add topological roles graph

@@
 
-## Food web construction
+## Methodology
 
-The following figure and tables summarize the data we used to build the network of trophic (predator-prey) interactions for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).
+### Food web construction
+
+The following figure and tables summarize the data we used to build the network of trophic (predator-prey) interactions for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
 Figure 1 resumes the type and number of references reviewed.
@@
 ```
+
+\newpage
+
+## Results
+
+### Species-level properties
+
+Figure 2 shows the species topological roles of the food web for the MPA Namuncurá-Banco Burdwood ecosystem.
+Species, represented by circles, are coloured by role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green).
+Network connector = 5 species; module connector = 35 species; module hub = 7 species; and module specialist = 332 species.
+
+```{r toprole, echo=FALSE, fig.width = 20, fig.height=20, fig.cap="Graph of the food web showing species coloured by topological role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green)."}
+
+# Load packages
+library(igraph)
+library(multiweb)
+library(grid)
+library(dplyr)
+library(ggplot2)
+
+# Load data
+load("../results/summary_results_jan23.rda")
+
+# Topological roles
+top.role.col <- hcl.colors(4, palette = "Purple-Green")
+TRColor <- setNames(top.role.col, levels(as.factor(V(g_up)$TopRole)))
+TRColor <- as.data.frame(TRColor) %>% 
+  mutate(TopRole = c("hubcon", "modcon", "modhub", "modspe"))
+#show_col(top.role.col)  # shows color & code
+data_TRColor <- spp_total %>% 
+  dplyr::select(TopRole, everything()) %>% 
+  left_join(TRColor)
+g_up_c <- g_up %>% 
+  set_vertex_attr("TRColor", value = data_TRColor$TRColor)
+
+# Number of species by Role
+TR_table <- spp_total %>% 
+  group_by(TopRole) %>% 
+  summarise(n = n()) %>%
+  mutate(freq = n / sum(n)) %>% 
+  mutate(TopRole = case_when(TopRole == "hubcon" ~ "Network connector",
+                             TopRole == "modcon" ~ "Module connector",
+                             TopRole == "modhub" ~ "Module hub",
+                             TopRole == "modspe" ~ "Module specialist"))
+
+# Filter network connectors ('hubcon') & module connectors ('modcon'). Violet & pink respectively
+sp_con <- spp_total %>% 
+  filter(TopRole == "hubcon" | TopRole == "modcon")
+
+# Move to a new page
+grid.newpage()
+# Arrange figure
+par(cex.axis=1.5, cex.lab=1.5)
+plot_troph_level(g_up_c, vertexLabel = F, modules = F, vertex.color = V(g_up_c)$TRColor, ylab = "Trophic level")
+
+```

### 2023-01-23 1st_Manuscript/ManuscriptDraft.Rmd
Continue w/ Results

@@
 
-We analyzed the MPA Namuncurá-Banco Burdwood network of trophic interactions, hereafter food web, at two levels: 1) global, considering species and interactions of the entire network; and 2) species, considering interactions and species related to a particular species.
+We analyzed the MPA Namuncurá-Banco Burdwood network of trophic interactions, hereafter food web, at two levels: 1) global, considering species and interactions of the whole network; and 2) species, considering interactions and species related to a particular species.
 For the global-level analysis we calculated several network properties commonly used to describe the complexity and structure in food webs [@Pascual2005]: (1) number of species S; (2) number of interactions or links L; (3) link density L/S; (4) Connectance L/S^2; (5) omnivory Omn; and (6) shortest path length SPL.
@@
 
+In terms of complexity, the MPA Namuncurá-Banco Burdwood food web consisted of 379 species and 1778 predator-prey interactions (Figure 2).
+The food web presents a link density of 4.69, meaning the average number of interactions per species, and a connectance of 0.01 (Table 1).
+Almost half of the consumers are omnivores, feeding on sources of different trophic levels.
+The food web shows a path length of 2.99, which implies that nearly three interactions are needed to connect any pair of species of the network.
+
 ```{r figure2, echo=FALSE, fig.align='center', fig.width = 20, fig.height=20, fig.cap="Graph of the food web of MPA Namuncurá-Banco Burdwood.
@@
 ```
+
+The degree distribution of the food web shows an asymmetric frequency in the number of interactions, where most of the species have relatively low interactions and few species concentrate the majority of them (Figure 2A).
+If we consider the distribution of prey among predators, most of the consumers feed on a low number of prey whereas few of them have multiple preys (Figure 2B).
+These are the top-five predators in number of prey: *Patagonotothen guntheri* (Notothenioid fish, 52 prey), *Patagonotothen ramsayi* (Notothenioid fish, 50 prey), *Dissostichus eleginoides* (Notothenioid fish, 30 prey), *Bathyraja brachyurops* (Chondrichthyan, 30 prey), and *Bathyraja griseocauda* (Chondrichthyan, 28 prey).
+Following the same distribution pattern, few prey are fed by multiple predators (Figure 2C).
+These are the top-five prey in number of predators:...
+Finally, if we take into account the interactions within each functional group, the situation is the same as in the whole food web (Figure 2D).
+Overall, there is an evident asymmetry in the distribution of interactions among species in the MPA Namuncurá-Banco Burdwood food web.
+
+Most Functional groups show an asymmetric distribution of interactions: few species are relatively more connected than the rest.
+Most consumers have a narrow potential diet, few have a broad diet.
+Few prey are consumed by many predators, most prey have few predators.
+Consumers w/ broad diet: Patagonotothen guntheri, P. ramsayi, Dissostichus eleginoides, Bathyraja brachyurops, B. griseocauda.
+Prey w/ many predators: Detritus, Diatoms (benthic, centric, pennate), Euphausia spp., Foraminifera.
 
@@
 
-Most Functional groups show an asymmetric distribution of interactions: few species are relatively more connected than the rest.
+### Species-level properties
 
-Most consumers have a narrow potential diet, few have a broad diet.
-Few prey are consumed by many predators, most prey have few predators.
-Consumers w/ broad diet: Patagonotothen guntheri, P. ramsayi, Dissostichus eleginoides, Bathyraja brachyurops, B. griseocauda.
-Prey w/ many predators: Detritus, Diatoms (benthic, centric, pennate), Euphausia spp., Foraminifera.
-
-### Species-level properties
+The majority of the species of the food web are consumers, 336 out of 379; the rest are primary producers, such as phytoplankton, and non-living food sources like detritus and necromass.
 
@@
 
-### Food web complexity and structure
+### The MPA Namuncurá-Banco Burdwood food web
 
@@
 
+### Caveats and future perspectives
+
 \newpage

### 2023-01-24 1st_Manuscript/ManuscriptDraft.Rmd
Results finished

--- 2023-01-23 1st_Manuscript/ManuscriptDraft.Rmd
@@
 The MPA Namuncurá-Banco Burdwood is a shallow submarine plateau called Burdwood Bank (BB) located 150 km east of Isla de los Estados and 200 km south from Malvinas/Falkland Islands (Figure 1).
-It comprises nearly 34.000 km^2 circumscribed by the 200 m isobath, between 54º–55ºS and 56º–62ºW, with a slight slope extended nearly 370 km east–west.
+It comprises nearly 34.000 km^2^ circumscribed by the 200 m isobath, between 54º–55ºS and 56º–62ºW, with a slight slope extended nearly 370 km east–west.
 The BB is surrounded by steep flanks of more than 3000 m depth through which strong currents circulate [@Piola1989; @Reta2014; @Matano2019].
@@
 
-```{r figure1, echo=FALSE}
+```{r figure1, echo=FALSE, out.width = '100%', fig.cap="Map of the Marine Protected Area Namuncurá-Banco Burdwood.
+Taken from https://www.argentina.gob.ar/parquesnacionales/areasmarinas/namuncura-burdwood."}
 # Map of MPAN-BB provided by Lu R. (?)
+knitr::include_graphics("MPABurdwood_map.jpeg")
 
@@
 
-We analyzed the MPA Namuncurá-Banco Burdwood network of trophic interactions, hereafter food web, at two levels: 1) global, considering species and interactions of the entire network; and 2) species, considering interactions and species related to a particular species.
-For the global-level analysis we calculated several network properties commonly used to describe the complexity and structure in food webs [@Pascual2005]: (1) number of species S; (2) number of interactions or links L; (3) link density L/S; (4) Connectance L/S^2; (5) omnivory Omn; and (6) shortest path length SPL.
+We analysed the MPA Namuncurá-Banco Burdwood network of trophic interactions, hereafter food web, at two levels: 1) global, considering species and interactions of the whole network; and 2) species, considering interactions and species related to a particular species.
+The global-level analysis aims to characterize the network of trophic interactions in terms of complexity and structure.
+For this we calculated several network properties commonly used to describe empirical food webs [@Pascual2005]: (1) number of species S; (2) number of interactions or links L; (3) link density L/S; (4) Connectance L/S^2; (5) omnivory Omn; and (6) shortest path length SPL.
 Also, we estimated the (7) degree distributions for the food web, for prey and predators, and for each functional group (e.g.
@@
 The prey and predator distributions indicate the frequency of prey among predators, and viceversa; the functional group's degree shows the distribution of interactions within groups.
-For the species-level analysis we considered the following properties: (1) betweenness Btw; (2) closeness Cl; (3) trophic level TL; (4) trophic similarity TS; and (5) topological role TR (Table 1).
+The species-level analysis aims to describe the species' role in the food web.
+For this we considered the following properties: (1) betweenness Btw; (2) closeness Cl; (3) trophic similarity TS; (4) topological role TR; and (5) trophic level TL (Table 1).
+We also studied the relationship between species trophic level and the other species properties by performing linear regression analyses.
+Thus, we considered the IS as the dependent variable and the given unweighted property as the independent variable, and obtained the coefficients (slope and intercept) for the linear model.
+Models were fitted using the least squares approach.
+We also explored the mean IS distribution with the species habitat.
 These properties provide a general appropriate description of species' role in empirical complex food webs [@Cirtwill2018].
@@
 pandoc.table(table1, digits = 4, colnames("Property","Definition","Implication","Reference"), style="multiline", split.tables = Inf, justify = c('left','left','left','right'),
-             caption = "List of network properties analyzed, definitions, and relevant ecological implications related to food web complexity and structure.")
+             caption = "List of network properties analysed, definitions, and relevant ecological implications related to food web complexity and structure.")
 
@@
 
+In terms of complexity, the MPA Namuncurá-Banco Burdwood food web consisted of 379 species and 1778 predator-prey interactions (Figure 2).
+The food web presented a link density of 4.69, meaning the average number of interactions per species, and a connectance of 0.01.
+Almost half of the consumers were omnivores, feeding on sources at different trophic levels.
+The food web showed a path length of 2.99, which implies that nearly three interactions are needed to connect any pair of species of the network (Table 1).
+
 ```{r figure2, echo=FALSE, fig.align='center', fig.width = 20, fig.height=20, fig.cap="Graph of the food web of MPA Namuncurá-Banco Burdwood.
-Circles represent the species and arrows the trophic interactions.
+Circles represent species and arrows trophic interactions.
 Colour gradient indicate the trophic level.
@@
 par(cex.axis=1.5, cex.lab=1.5)
-plot <- plot_troph_level(g, vertexLabel = F, modules = F, ylab = "Trophic level")
+figure_2 <- plot_troph_level(g, vertexLabel = F, modules = F, ylab = "Trophic level")
 
@@
 knitr::kable(round(prop_topol,2) %>% dplyr::select(Size, Links, LD, Connectance, Omnivory, PathLength), col.names = c("Species","Interactions","Density","Connectance","Omnivory","Path length"),
-                      caption = "Global-level properties of the food web of MPA Namuncurá-Banco Burdwood. See table 1 for definitions and ecological relevance.")
+                      caption = "Global-level properties of the MPA Namuncurá-Banco Burdwood food web. See table 1 for definitions and ecological relevance.")
 
@@
 
-\newpage
+The degree distribution of the food web showed an asymmetric frequency in the number of interactions, where most of the species had a relatively low number of interactions and few species concentrated the majority of them (Figure 3A).
+If we consider the distribution of prey among predators, most of the consumers fed on a low number of prey whereas few of them had multiple preys (Figure 3B).
+These were the top-five predators in terms of prey: *Patagonotothen guntheri* (Notothenioid fish, 52 prey), *Patagonotothen ramsayi* (Notothenioid fish, 50 prey), *Dissostichus eleginoides* (Notothenioid fish, 30 prey), *Bathyraja brachyurops* (Chondrichthyan, 30 prey), and *Bathyraja griseocauda* (Chondrichthyan, 28 prey).
+Following the same distribution pattern, few prey presented multiple predators (Figure 3C).
+These were the top-five prey in number of predators: Detritus (Non-living, predators), the three categories of Diatoms considered (benthic, centric and pennate, 72 predators on average), and species of genus *Euphausia* (Zooplankton, 46 predators).
+Finally, taking into account the interactions within each functional group, the situation is the same as in the whole food web (Figure 3D).
+Overall, there is an evident asymmetry in the distribution of interactions among species in the MPA Namuncurá-Banco Burdwood food web.
 
-```{r figure3, echo=FALSE, fig.height = 28, fig.width = 20, fig.cap="Degree distributions for the (A) food web, for (B) prey among predators, (C) predators among prey, and (D) for each functional group.
-Groups are vertically ordered by trophic level."}
+A list of the distribution of interactions per species is presented in Supplementary Material (Table S3).
+
+```{r figure3, echo=FALSE, fig.height = 25, fig.width = 20, fig.cap="Degree distributions for the (A) food web, for (B) prey among predators, (C) predators among prey, and (D) for each functional group.
+Groups are vertically ordered by increasing trophic level."}
 # Degree distributions: network, predator, prey & group
@@
 
-Most Functional groups show an asymmetric distribution of interactions: few species are relatively more connected than the rest.
-
-Most consumers have a narrow potential diet, few have a broad diet.
-Few prey are consumed by many predators, most prey have few predators.
-Consumers w/ broad diet: Patagonotothen guntheri, P. ramsayi, Dissostichus eleginoides, Bathyraja brachyurops, B. griseocauda.
-Prey w/ many predators: Detritus, Diatoms (benthic, centric, pennate), Euphausia spp., Foraminifera.
+\newpage
 
@@
 
-\newpage
+The majority of the species of the food web were consumers, 336 out of 379; the rest were primary producers, such as diatoms (phytoplankton), and non-living food sources like detritus and necromass.
 
-```{r figure4, echo=FALSE, fig.width = 20, fig.height=20, fig.cap="Species-level properties (A) betwenness, (B) closeness, and (C) trophic similarity by trophic level (equal or greater than 2).
-See table 1 for definitions and ecological relevance."}
-# Betweenness, Closeness & Trophic similarity by Trophic level (>= 2)
+We found different relationships between the species trophic level (TL) and the rest of the analysed species-level properties (Figure 4A-D).
+In this regard, the most evident significant relationship was with trophic similarity, i.e.
+the higher the species' TL, the lower the trophic similarity or the higher the uniqueness in terms of trophic role (Figure 4C).
+There was also a negative significant relationship with closeness, however less strong: low-TL species were relatively closer to any other species in the food web than high-TL ones (Figure 4B).
+It's noteworthy that betweenness highest values were presented in species of mid-TLs (3-4), meaning that those species participated in the highest number of shortest paths between species: ‘bridge’ role (Figure 4A).
+Taking into account the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.77); 'module hub' was constrained to mid-TL species (2.48 - 3.92); 'module connector' from low to mid-TLs (1 - 3.86); and 'network connector', the least frequent, had all of its species in TL = 1, except for one with TL = 3.47 (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework).
+Here it's important to highlight species of the latter two topological roles, because they are responsible for linking modules and maintaining the connectivity of the food web: 40 species (5 network connectors + 35 module connectors) from 20 different functional groups with a TL range = 1 - 3.86.
+
+An exhaustive list of the species-level properties is presented in Supplementary Material (Table S3).
+
+```{r figure4, echo=FALSE, fig.width = 20, fig.height=20, fig.cap="Species-level properties (A) betweenness, (B) closeness, (C) trophic similarity, and (D) topological role by trophic level.
+Linear regressions for betweenness ($y = 72.48x - 111.98, R^2 = 0.04, p-value < 3.38e-05$), closeness ($y = 5.78e-06x - 9.37e-04, R^2 = -0.0005, p-value = 0.37$) and trophic similarity ($y = -0.01x - 0.11, R^2 = 0.07, p-value = 6.76e-08$).
+Note that for A, B and C panels only species with TLs equal or greater than 2 were considered."}
+# Betweenness, Closeness, Trophic similarity & Topological role by Trophic level
 
@@
   geom_point() +
-  #geom_vline(xintercept = c(spp_nt_12+1, spp_nt_12+spp_nt_13+1, spp_nt_14+1), linetype = "longdash", colour = "red") +
+  geom_smooth(method = "lm") +
   labs(x = "Trophic level", y = "Betweenness") +
@@
   geom_point() +
-  #geom_vline(xintercept = c(spp_nt_12+1, spp_nt_12+spp_nt_13+1, spp_nt_14+1), linetype = "longdash", colour = "red") +
+  geom_smooth(method = "lm") +
   labs(x = "Trophic level", y = "Closeness") +
@@
   geom_point() +
-  #geom_vline(xintercept = c(spp_nt_12+1, spp_nt_12+spp_nt_13+1, spp_nt_14+1), linetype = "longdash", colour = "red") +
+  geom_smooth(method = "lm") +
   labs(x = "Trophic level", y = "Trophic similarity") +
@@
 
+# Topological role
+top.role.col <- hcl.colors(4, palette = "Purple-Green")
+TRColor <- setNames(top.role.col, levels(as.factor(V(g_up)$TopRole)))
+TRColor <- as.data.frame(TRColor) %>% 
+  mutate(TopRole = c("hubcon", "modcon", "modhub", "modspe"))
+data_TRColor <- spp_total %>% 
+  dplyr::select(TopRole, everything()) %>% 
+  left_join(TRColor)
+
+plot_sp_tr <- data_TRColor %>% 
+  mutate(TopRole = case_when(TopRole == "hubcon" ~ "netcon", TRUE ~ TopRole)) %>% 
+  ggplot(., aes(x = TopRole, y = TL)) +
+  geom_violin(fill = "grey90") +
+  geom_point(size=3, aes(color=TRColor)) +
+  labs(x = "Topological role", y = "Trophic level") +
+  theme_bw() +
+  theme(panel.grid = element_blank(),
+        axis.text.x = element_text(size = 26),
+        axis.text.y = element_text(size = 26),
+        axis.title = element_text(size = 26, face = "bold"),
+        legend.position = "none")
+
 # Move to a new page
@@
 # Arrange figure
-figure_4 <- ggarrange(plot_sp_bt + rremove("xlab"), plot_sp_cl + rremove("xlab"), plot_sp_ts + rremove("xlab"),
-                      labels = c("A","B","C"), ncol=2, nrow=2,
+figure_ab <- ggarrange(plot_sp_bt + rremove("xlab"), plot_sp_cl + rremove("xlab"),
+                      labels = c("A","B"), ncol=2,
                       font.label = list(size = 30, color = "black"))
-annotate_figure(figure_4, bottom = textGrob("Trophic level", gp = gpar(fontface="bold", col="black", fontsize=26)))
+figure_ab <- annotate_figure(figure_ab, bottom = textGrob("Trophic level", gp = gpar(fontface="bold", col="black", fontsize=26)))
+figure_4 <- ggarrange(figure_ab,                                                                                         # First row
+          ggarrange(plot_sp_ts, plot_sp_tr, ncol = 2, labels = c("C", "D"), font.label=list(color="black",size=30)),                                            
+          nrow = 2)
+figure_4
 
@@
 
-‘Network connector’ and ‘module connector’ species are responsible for linking modules and maintaining the connectivity of the food web. TL range for these species: 1 - 3.86.
-
-Betweenness = Species at mid-trophic levels (3-4) present more shortest paths between species than any other species: ‘bridge’ role.
-Closeness = Low-trophic level species are relatively closer to other species in the food web.
-
-Trophic similarity: Species are more similar at mid-trophic levels (2-3) than in lower or higher ones. Basal and top species present a higher uniqueness in terms of trophic role.
+\newpage
 
@@
 
-### Food web complexity and structure
+### The MPA Namuncurá-Banco Burdwood food web
+
+Most Functional groups show an asymmetric distribution of interactions: few species are relatively more connected than the rest. This coincides w/ previous studies on empirical complex food webs.
+Most consumers have a narrow potential diet, few have a broad diet.
+Few prey are consumed by many predators, most prey have few predators.
+Consumers w/ broad diet: Patagonotothen guntheri, P. ramsayi, Dissostichus eleginoides, Bathyraja brachyurops, B. griseocauda.
+Prey w/ many predators: Detritus, Diatoms (benthic, centric, pennate), Euphausia spp., Foraminifera.
 
@@
 
+‘Network connector’ (netcon) and ‘module connector’ (modcon) species are responsible for linking modules and maintaining the connectivity of the food web. TL range for these species: 1 - 3.86.
+
+Betweenness = Species at mid-trophic levels (3-4) present more shortest paths between species than any other species: ‘bridge’ role.
+Closeness = Low-trophic level species are relatively closer to other species in the food web.
+
+Trophic similarity: Species are more similar at mid-trophic levels (2-3) than in lower or higher ones. Basal and top species present a higher uniqueness in terms of trophic role.
+
 Low and mid-trophic level species are responsible for maintaining the connectivity of the food web.

### 2023-01-24 1st_Manuscript/SupMaterial.Rmd
minor changes

@@
 Figure 1 resumes the type and number of references reviewed.
-Table 1 is the complete list of trophic interactions and the references that confirm each of them.
-Table 2 is the species list with details on trophospecies cases (aggregated taxa).
+Table 1 is the complete list of trophic interactions and references that confirm each of them.
+Table 2 is the species list with details on trophic species cases (aggregated taxa).
 
-```{r ref-plot, echo=FALSE, fig.cap="Summary of the references used to build the network of trophic (predator-prey) interactions for the MPAN-BB ecosystem."}
+```{r ref_plot, echo=FALSE, fig.cap="Summary of references used to build the network of trophic (predator-prey) interactions for the MPAN-BB ecosystem."}
 
@@
 
-```{r echo=FALSE, results='asis'}
+```{r tableS1, echo=FALSE, results='asis'}
 
@@
 # Table 1. List of interactions
-knitr::kable(int_good_res %>% arrange(., (Predator)), booktabs = TRUE, format = "latex", longtable = T, col.names = c("Prey","Predator","Reference", "Link"), caption = "List of predator-prey (trophic) interactions used to build the network for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).") %>%
+knitr::kable(int_good_res %>% arrange(., (Predator)), booktabs = TRUE, format = "latex", longtable = T, col.names = c("Prey","Predator","Reference", "Link"), caption = "List of predator-prey (trophic) interactions for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.") %>%
   column_spec(1:3, width="2cm") %>% 
@@
 
-```{r echo=FALSE, results='asis'}
+```{r tableS2, echo=FALSE, results='asis'}
 
@@
 # Table 2. List of species
-knitr::kable(sp_list, format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Group","Reference","Link","Observation"), caption = "List of species for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).") %>%
+knitr::kable(sp_list, format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Group","Reference","Link","Observation"), caption = "List of species for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.") %>%
   column_spec(1:3, width="3cm") %>%
@@
 
-### Species-level properties
+Table 3 presents an exhaustive list of the species-level properties for the food web of the MPA Namuncurá - Banco Burdwood I ecosystem.
 
-Figure 2 shows the species topological roles of the food web for the MPA Namuncurá-Banco Burdwood ecosystem.
+```{r tableS3, echo=FALSE}
+
+load("../results/summary_results_jan23.rda")
+
+# Table 2. List of species
+knitr::kable(spp_total %>% 
+               mutate(TopRole = case_when(TopRole == "hubcon" ~ "netcon",
+                                          TRUE ~ TopRole)) %>% 
+               dplyr::select(TrophicSpecies, FunctionalGroup, TotalDegree, NumPrey, NumPred, Between, Close, TL, meanTrophicSimil, TopRole) %>% 
+               arrange(., desc(TotalDegree)) %>% 
+               mutate(across(where(is.numeric), round, 4)), 
+             format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Group","Degree","NumPrey","NumPred","Between","Close","TL","TS","TR"), align = "llcccccccc", caption = "Species-level properties for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
+Degree: total number of interactions; Between: betweenness; Close: closeness; TL: trophic level; TS: trophic similarity; TR: topological role (netcon = network connector, modcon = module connector, modhub = module hub, modspe = module specialist).") %>%
+  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 4.5)
+
+```
+
+\newpage
+
+Figure 2 shows the species' topological roles in the food web graph.
 Species, represented by circles, are coloured by role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green).
@@
 
-```{r toprole, echo=FALSE, fig.width = 20, fig.height=20, fig.cap="Graph of the food web showing species coloured by topological role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green)."}
+```{r toprole_graph, echo=FALSE, fig.width = 20, fig.height=20, fig.cap="Graph of the food web showing species coloured by topological role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green)."}
 

### 2023-01-24 R/5_regressionanalyses.R
Linear regressions with TL

@@ -1,0 +1,83 @@
+## FOOD WEB ANALYSIS: RED TRÓFICA AMP NAMUNCURÁ-BANCO BURDWOOD
+# Autor: Tomás Ignacio Marina
+# Fecha: 24/01/2023
+
+
+# Paquetes ----
+
+packages <- c("dplyr", "ggplot2", "olsrr")
+ipak <- function(pkg){
+  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
+  if (length(new.pkg))
+    install.packages(new.pkg, dependencies = TRUE)
+  sapply(pkg, require, character.only = TRUE)
+}
+ipak(packages)
+
+
+# Datos ----
+load("results/summary_results_jan23.rda")
+
+
+# Linear Regression ----
+
+## Betweenness ----
+plot_sp_bt <- spp_total %>% 
+  filter(TL >= 2) %>% 
+  ggplot(., aes(x = TL, y = Between)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  #geom_vline(xintercept = c(spp_nt_12+1, spp_nt_12+spp_nt_13+1, spp_nt_14+1), linetype = "longdash", colour = "red") +
+  labs(x = "Trophic level", y = "Betweenness") +
+  theme_bw() +
+  theme(panel.grid = element_blank(),
+        axis.text.x = element_text(size = 26),
+        axis.text.y = element_text(size = 26),
+        axis.title = element_text(size = 26, face = "bold"))
+
+# Test regression significance
+btw_reg <- lm(Between ~ TL, data = spp_total)
+summary(btw_reg)
+ols_test_normality(btw_reg)  # check normality of residuals
+ols_plot_resid_qq(btw_reg)  # Q-Q plot
+
+
+## Closeness ----
+plot_sp_cl <- spp_total %>% 
+  filter(TL >= 2) %>%
+  ggplot(., aes(x = TL, y = Close)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  labs(x = "Trophic level", y = "Closeness") +
+  theme_bw() +
+  theme(panel.grid = element_blank(),
+        axis.text.x = element_text(size = 26),
+        axis.text.y = element_text(size = 26),
+        axis.title = element_text(size = 26, face = "bold"))
+
+# Test regression significance
+clo_reg <- lm(Close ~ TL, data = spp_total)
+summary(clo_reg)
[…]

### 2023-01-24 R/6_figures.R
Tidy figures

@@ -1,0 +1,258 @@
+## FIGURES: RED TRÓFICA AMP NAMUNCURÁ-BANCO BURDWOOD
+# Autor: Tomás Ignacio Marina
+# Fecha: 18/08/2022
+
+
+# Paquetes ----
+
+packages <- c("tidyverse", "ggplot2", "ggjoy", "ggpubr", "scales", 
+              "multiweb", "igraph")
+ipak <- function(pkg){
+  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
+  if (length(new.pkg))
+    install.packages(new.pkg, dependencies = TRUE)
+  sapply(pkg, require, character.only = TRUE)
+}
+ipak(packages)
+
+
+# Cargar datos ----
+
+load("results/summary_results_jan23.rda")
+
+
+# Figuras ----
+
+## Escala global ----
+
+# Red trófica por degree
+plot_troph_level(g_up, ylab = "Trophic level")
+
+# Distribución de grado
+# Histograma
+degree <- as.data.frame(degree(g, mode = "total"))
+(plot_distdegree <- ggplot(degree, aes(degree[,1])) +
+    geom_histogram(bins = 100, alpha = 0.3, color = "black") +
+    labs(x = "Degree", y = "Frequency") +
+    theme_bw() +
+    theme(legend.position = "none",
+          axis.text.x = element_text(size = 14),
+          axis.text.y = element_text(size = 14),
+          axis.title.x = element_text(face = "bold", size = 16),
+          axis.title.y = element_text(face = "bold", size = 16)))
+
+# Generality (generalistas vs especialistas)
+plot_indeg <- spp_total %>% 
+    filter(NumPrey != 0) %>% 
+    ggplot(., aes(x = NumPrey)) +
+    geom_histogram(stat = "count") +
+    labs(x = "Predators", y = "Number of prey") +
+    theme_bw() +
+    theme(legend.position = "none",
+          axis.text.x = element_text(size = 14),
+          axis.text.y = element_text(size = 14),
+          axis.title.x = element_text(face = "bold", size = 16),
+          axis.title.y = element_text(face = "bold", size = 16)) #+
+# annotate("text", x = Inf, y = Inf, label = paste("Prey per predator = ", round(prop.topol$Generality, 2), sep = ""),
+#          size = 5, vjust=1, hjust=1))
[…]

### 2023-01-24 R/5_figures.R
Delete 5_figures.R

@@ -1,244 +1,0 @@
-## FIGURES: RED TRÓFICA AMP NAMUNCURÁ-BANCO BURDWOOD
-# Autor: Tomás Ignacio Marina
-# Fecha: 18/08/2022
-
-
-# Paquetes ----
-
-packages <- c("tidyverse", "ggplot2", "ggjoy", "ggpubr", "scales", 
-              "multiweb", "igraph")
-ipak <- function(pkg){
-  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
-  if (length(new.pkg))
-    install.packages(new.pkg, dependencies = TRUE)
-  sapply(pkg, require, character.only = TRUE)
-}
-ipak(packages)
-
-
-# Cargar datos ----
-
-load("results/summary_results_sep22.rda")
-
-
-# Figuras ----
-
-## Escala global ----
-
-# Red trófica por degree
-plot_troph_level(g_up, ylab = "Trophic level")
-
-# Distribución de grado
-# Histograma
-degree <- as.data.frame(degree(g, mode = "total"))
-(plot_distdegree <- ggplot(degree, aes(degree[,1])) +
-    geom_histogram(bins = 100, alpha = 0.3, color = "black") +
-    labs(x = "Degree", y = "Frequency") +
-    theme_bw() +
-    theme(legend.position = "none",
-          axis.text.x = element_text(size = 14),
-          axis.text.y = element_text(size = 14),
-          axis.title.x = element_text(face = "bold", size = 16),
-          axis.title.y = element_text(face = "bold", size = 16)))
-
-# Generality (generalistas vs especialistas)
-plot_indeg <- spp_total %>% 
-    filter(NumPrey != 0) %>% 
-    ggplot(., aes(x = NumPrey)) +
-    geom_histogram(stat = "count") +
-    labs(x = "Predators", y = "Number of prey") +
-    theme_bw() +
-    theme(legend.position = "none",
-          axis.text.x = element_text(size = 14),
-          axis.text.y = element_text(size = 14),
-          axis.title.x = element_text(face = "bold", size = 16),
-          axis.title.y = element_text(face = "bold", size = 16)) #+
-# annotate("text", x = Inf, y = Inf, label = paste("Prey per predator = ", round(prop.topol$Generality, 2), sep = ""),
-#          size = 5, vjust=1, hjust=1))
[…]

### 2023-01-25 1st_Manuscript/ManuscriptDraft.Rmd
Finished Results

@@
 ---
-title: "The complex network of trophic interactions in a subAntarctic Marine Protected Area"
+title: The complex network of trophic interactions in a subAntarctic Marine Protected
+  Area
 author: "Tomás I. Marina, Irene R. Schloss and Luciana Riccialdelli"
-output: pdf_document
-bibliography: "AMPBancoBurdwood.bib"
+output:
+  pdf_document: default
+  word_document: default
+bibliography: AMPBancoBurdwood.bib
+csl: "marine-ecology-progress-series.csl"
+nocite: '@*'
 header-includes:
@@
 
-The objective of the present work was twofold: characterize the network of trophic interactions in terms of complexity and structure for the MPA Namuncurá-Banco Burdwood ecosystem, and describe the species' role in such network framework.
+Trophic ecology & keystone spp knowledge of B Burdwood
+
+Benefits of studying complex ecosystems using network approach
+
+Objective
+In the present work we present the first, detailed analysis of the food web for the MPA Namuncurá - Banco Burdwood ecosystem.
+For this we applied a network approach to a highly-resolved food web.
+The objective was twofold: characterise the food web in terms of complexity and structure, and describe the species' role in such network framework.
 
@@
 table1 <- add_row(table1, Name="Connectance", Definition="Proportion of potential links among species that are actually realized.", Implications="It measures the probability of interactions; it is a fundamental measure of network complexity.
-Connectance can be negatively or positively associated with food web robustness, depending on the network structure (random vs non-random) or how the strength of the interactions are distributed.", Reference = "Martinez 1991")
+Connectance can be negatively or positively associated with food web robustness, depending on the network structure (random vs non-random) or how the strength of the interactions are distributed.", Reference = "Martinez 1992")
 
@@
 
-table1 <- add_row(table1, Name="Betweenness", Definition="Number of shortest paths going through a species.", Implications=" Species with high betweenness act as “bridges”; if removed, would have rapidly spreading effects in the food web.", Reference="Freeman 1979")
+table1 <- add_row(table1, Name="Betweenness", Definition="Number of shortest paths going through a species.", Implications=" Species with high betweenness act as “bridges”; if removed, would have rapidly spreading effects in the food web.", Reference="Freeman 1978, Lai et al.
+2012")
 
-table1 <- add_row(table1, Name="Closeness", Definition="Number of steps required to reach every other species from a given species.", Implications="The removal of a species with high closeness will affect the most other species in the food web.", Reference="Freeman 1979")
+table1 <- add_row(table1, Name="Closeness", Definition="Number of steps required to reach every other species from a given species.", Implications="The removal of a species with high closeness will affect the most other species in the food web.", Reference="Freeman 1978, Lai et al.
+2012")
 
@@
 
-table1 <- add_row(table1, Name="Trophic similarity", Definition="Trophic overlap based on shared and unique resources (prey) and consumers (predators).", Implications="It measures one of the most important aspects of species’ niches, the trophic niche, and functional aspects of biodiversity.", Reference="Martinez 1991")
+table1 <- add_row(table1, Name="Trophic similarity", Definition="Trophic overlap based on shared and unique resources (prey) and consumers (predators).", Implications="It measures one of the most important aspects of species’ niches, the trophic niche, and functional aspects of biodiversity.", Reference="Martinez 1992")
 
 table1 <- add_row(table1, Name="Topological role", Definition="Species role according to interactions within and across modules (subgroups of species).", Implications="Four roles are defined: module hub, module specialist, module connector and network connector.
-Species with the same role are expected to have similar topological properties.", Reference="Guimera 2005")
+Species with the same role are expected to have similar topological properties.", Reference="Guimera & Nunes Amaral 2005")
 
-pandoc.table(table1, digits = 4, colnames("Property","Definition","Implication","Reference"), style="multiline", split.tables = Inf, justify = c('left','left','left','right'),
+names(table1) <- pandoc.strong.return(names(table1))
+pandoc.table(table1, digits = 4, colnames("Property","Definition","Implication","Reference"), style="multiline", split.tables = Inf, justify = c('left','left','left','right'), emphasize.strong.cols = 1, emphasize.rownames = 1,
              caption = "List of network properties analysed, definitions, and relevant ecological implications related to food web complexity and structure.")
@@
 knitr::kable(round(prop_topol,2) %>% dplyr::select(Size, Links, LD, Connectance, Omnivory, PathLength), col.names = c("Species","Interactions","Density","Connectance","Omnivory","Path length"),
-                      caption = "Global-level properties of the MPA Namuncurá-Banco Burdwood food web. See table 1 for definitions and ecological relevance.")
+                      caption = "Global-level properties of the MPA Namuncurá-Banco Burdwood food web. See table 1 for definitions and ecological relevance.") %>% row_spec(0,bold=TRUE)
 
@@
 ```{r figure4, echo=FALSE, fig.width = 20, fig.height=20, fig.cap="Species-level properties (A) betweenness, (B) closeness, (C) trophic similarity, and (D) topological role by trophic level.
+Each point represents a species.
 Linear regressions for betweenness ($y = 72.48x - 111.98, R^2 = 0.04, p-value < 3.38e-05$), closeness ($y = 5.78e-06x - 9.37e-04, R^2 = -0.0005, p-value = 0.37$) and trophic similarity ($y = -0.01x - 0.11, R^2 = 0.07, p-value = 6.76e-08$).
@@
 # Betweenness, Closeness, Trophic similarity & Topological role by Trophic level
+
+load("../results/summary_results_jan23.rda")
 
@@
 
-plot_sp_tr <- data_TRColor %>% 
+cols <- c("netcon"="#492050", "modspe"="#023903", "modhub"="#A5CEA5", "modcon"="#DAB8E2")
+plot_sp_tr <- spp_total %>% 
   mutate(TopRole = case_when(TopRole == "hubcon" ~ "netcon", TRUE ~ TopRole)) %>% 
   ggplot(., aes(x = TopRole, y = TL)) +
-  geom_violin(fill = "grey90") +
-  geom_point(size=3, aes(color=TRColor)) +
+  geom_boxplot(aes(color = factor(TopRole), fill = factor(TopRole)), alpha=0.9) +
+  geom_jitter(aes(color = factor(TopRole), fill = factor(TopRole))) +
+  scale_fill_manual(values=cols) +
   labs(x = "Topological role", y = "Trophic level") +

### 2023-01-25 1st_Manuscript/ManuscriptDraft.Rmd
Added species' role results

@@
 Furthermore, we took into account personal communications from experts belonging to the working group of the study area (https://www.pampazul.gob.ar/tag/banco-burdwood/).
-The diversity of the expertise of the authors contributing to the present study was a key factor in generating the quality of the network, and inherently improved the network representation of the MPA Namuncurá-Banco Burdwood ecosystem.
-A list of the bibliography used to build the network is presented in Supplementary Material (Table S1).
+The diversity of the expertise of the authors contributing to the present study was a key factor in enhancing the quality of the network, and inherently improved the network representation of the MPA Namuncurá-Banco Burdwood ecosystem.
+A list of the references used to build the network is presented in Supplementary Material (Table S1).
 
-Due to a lack of trophic data resolution for some species inhabiting the MPA Namuncurá-Banco Burdwood, we follow the concept of trophic species, here defined as aggregated groups of taxa.
+Due to a lack of trophic data resolution for some species inhabiting the MPA Namuncurá-Banco Burdwood, we followed the concept of trophic species, here defined as aggregated groups of taxa.
 In most cases we followed this when data on specific biological species were not available, but for some cases we collapsed species when taxa shared the same set of predators and prey (trophic similarity criteria).
@@
 
-In terms of complexity, the MPA Namuncurá-Banco Burdwood food web consisted of 379 species and 1778 predator-prey interactions (Figure 2).
+In terms of complexity, the MPA Namuncurá - Banco Burdwood food web consisted of 1778 predator-prey interactions and 379 species, where 93% of them were defined at the species taxonomical level (Figure 2, Table S2).
 The food web presented a link density of 4.69, meaning the average number of interactions per species, and a connectance of 0.01.
@@
 the higher the species' TL, the lower the trophic similarity or the higher the uniqueness in terms of trophic role (Figure 4C).
+Here we highlight the following high-trophic level species of fishes (*Bathyraja macloviana*, *Squalus acanthias*), echinoderms (*Diplopteraster clarki*, *Pteraster sp*), seabirds (*Phalacrocorax_atriceps*, *Eudyptes chrysocome*), and marine mammals (*Lagenorhynchus_cruciger*, *Mesoplodon_bowdoini*) (Table S3).
 There was also a negative significant relationship with closeness, however less strong: low-TL species were relatively closer to any other species in the food web than high-TL ones (Figure 4B).
-It's noteworthy that betweenness highest values were presented in species of mid-TLs (3-4), meaning that those species participated in the highest number of shortest paths between species: ‘bridge’ role (Figure 4A).
+Species of genera *Calanus* and *Euphausia*, and Brachiopoda trophic species, all of them with TL < 3, registered the highest values (Table S3).
+It's noteworthy that the highest values of betweenness were shown by species of mid-TLs (3-4), meaning that those species participated in the highest number of shortest paths between species (Figure 4A).
+These were the species with the highest values: *Patagonotothen ramsayi*, *Dissostichus eleginoides*, *Salilota australis* (fish), *Doryteuthis gahi* (Cephalopoda), and *Patagonotothen guntheri* (Table S3).
 Taking into account the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.77); 'module hub' was constrained to mid-TL species (2.48 - 3.92); 'module connector' from low to mid-TLs (1 - 3.86); and 'network connector', the least frequent, had all of its species in TL = 1, except for one with TL = 3.47 (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework).
@@
 
-### The MPA Namuncurá-Banco Burdwood food web
+### The MPA Namuncurá - Banco Burdwood food web
 
-Most Functional groups show an asymmetric distribution of interactions: few species are relatively more connected than the rest. This coincides w/ previous studies on empirical complex food webs.
-Most consumers have a narrow potential diet, few have a broad diet.
-Few prey are consumed by many predators, most prey have few predators.
-Consumers w/ broad diet: Patagonotothen guntheri, P. ramsayi, Dissostichus eleginoides, Bathyraja brachyurops, B. griseocauda.
-Prey w/ many predators: Detritus, Diatoms (benthic, centric, pennate), Euphausia spp., Foraminifera.
+* The MPA Namuncurá - Banco Burdwood food web is one of the most highly-resolved network of trophic interactions described for subpolar and polar regions.
+Compare with other subpolar and polar food webs.
+
+* The food web shows an asymmetry in the distribution of interactions at several levels: food web, functional group, prey and predators. In all of them interactions are concentrated in a few species.
+On one hand, this asymmetry indicates that most consumers have a narrow diet, few present flexible diets (Patagonotothen guntheri, P.
+ramsayi, Dissostichus eleginoides, Bathyraja brachyurops, B.
+griseocauda).
+On the other hand few prey are consumed by many predators, meaning that there are dominant food sources from which most consumers depend on: detritus, diatoms (benthic, centric, pennate), and species of *Euphausia*.
 
@@
 
-The distribution of the interactions is asymmetric, where few species concentrate most of the interactions: Detritus, Diatoms (x3), Patagonotothen ramsayi & P.
-guntheri, Euphausia spp.
-The same happens within each functional group.
+Our results state that certain species play particular roles in the structure of the food web.
 
-The most demanded food sources are: Detritus, Diatoms (x3), Euphausia spp., & Foraminifera.
-Almost half of the consumers (47.64 %) are omnivores. Those with the broadest diets are: Patagonotothen ramsayi, P. guntheri, Dissostichus eleginoides, Bathyraja brachyurops, B. griseocauda.
+* Betweenness.
+Species at mid-trophic levels (3-4) lie in more shortest paths between species than any other species: ‘bridge’ role.
+Implications for spread of perturbations like mercury, microplastics.
 
-‘Network connector’ (netcon) and ‘module connector’ (modcon) species are responsible for linking modules and maintaining the connectivity of the food web. TL range for these species: 1 - 3.86.
+* Closeness. Low-trophic level species are relatively closer to other species in the food web.
 
-Betweenness = Species at mid-trophic levels (3-4) present more shortest paths between species than any other species: ‘bridge’ role.
-Closeness = Low-trophic level species are relatively closer to other species in the food web.
+* Trophic similarity.
+Species are more similar at low and mid-trophic levels (2-4).
+There is a functional redundancy at these levels of the food web.
+On the other hand, less trophic similarity at high levels indicate uniqueness in terms of trophic role.
+This highlights the importance of top predators.
 
-Trophic similarity: Species are more similar at mid-trophic levels (2-3) than in lower or higher ones. Basal and top species present a higher uniqueness in terms of trophic role.
-
+* Topological role.
+network connector and module connector species are responsible for linking modules and maintaining the connectivity of the food web.
+TL range for these species: 1 - 3.86.
 Low and mid-trophic level species are responsible for maintaining the connectivity of the food web.
@@
 
-Low and mid-trophic level species present the highest betweenness and closeness values. These species have an important ‘bridge’ role and are close to other species.
+* Overall, low and mid-trophic level species present the highest betweenness and closeness values, and the most important topological roles.
 Mid-trophic level species are more redundant than those at low and high trophic levels.
@@
 
+Caveats:
+
+* Seasonal variation in predators' diet due to food source availability.
+
+* Spatial variation of study area: Banco Burdwood west-east gradient.
+
+Perspectives:
+
+* Estimation of interaction strength to gain insights into food web stability and response to anthropogenic and environmental perturbations.
+
+* Simulate perturbations on food web and target species: mercury transfer, microplastic pollution, fisheries.
+
 \newpage

### 2023-01-25 1st_Manuscript/SupMaterial.Rmd
Taxa resolution

@@
 # Table 1. List of interactions
-knitr::kable(int_good_res %>% arrange(., (Predator)), booktabs = TRUE, format = "latex", longtable = T, col.names = c("Prey","Predator","Reference", "Link"), caption = "List of predator-prey (trophic) interactions for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.") %>%
+knitr::kable(int_good_res %>% arrange(., (Predator)), booktabs = TRUE, format = "latex", longtable = T, col.names = c("Prey","Predator","Reference", "Link"), caption = "List of predator-prey (trophic) interactions for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
+Alphabetically ordered by predator.") %>%
   column_spec(1:3, width="2cm") %>% 
@@
                                      Species == "Brachiopoda_spp" ~ "Brachiopoda", TRUE ~ FunctionalGroup)) %>% 
+  mutate(TaxLevel = case_when(str_detect(Species, "_") | str_detect(Species, "_spp") ~ "Species",
+                              str_detect(Species, "_sp") ~ "Genus",
+                              str_detect(Species, "dae$") ~ "Family",
+                              Species %in% c("Detritus","Necromass") ~ "NA",
+                              Species %in% c("Bacteria","Foraminifera") ~ "Phylum",
+                              Species %in% c("Calcarea","Copepodite","Hexactinellida") ~ "Class",
+                              Species %in% c("Halichondrida","Haplosclerida","Poecilosclerida","Tetractinellida") ~ "Order",
+                              TRUE ~ "Other")) %>% 
+  dplyr::select(Species, TaxLevel, FunctionalGroup, Reference, Reference_pres_link, Observation) %>% 
   arrange(., (Species))
 
+# Food web resolution
+res_sp <- sum(sp_list$TaxLevel == "Species") / nrow(sp_list)
+
 # Table 2. List of species
-knitr::kable(sp_list, format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Group","Reference","Link","Observation"), caption = "List of species for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.") %>%
-  column_spec(1:3, width="3cm") %>%
-  column_spec(4:5, width="5cm") %>% 
+knitr::kable(sp_list, format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Taxonomy","Group","Reference","Link","Observation"), caption = "List of species for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
+Alphabetically ordered by species.") %>%
+  column_spec(1:3, width="2cm") %>%
+  column_spec(4, width="3cm") %>% 
+  column_spec(5:6, width="5cm") %>% 
   kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 4) %>% 
@@
              format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Group","Degree","NumPrey","NumPred","Between","Close","TL","TS","TR"), align = "llcccccccc", caption = "Species-level properties for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
-Degree: total number of interactions; Between: betweenness; Close: closeness; TL: trophic level; TS: trophic similarity; TR: topological role (netcon = network connector, modcon = module connector, modhub = module hub, modspe = module specialist).") %>%
+Ordered by degree (total number of interactions).
+Between: betweenness; Close: closeness; TL: trophic level; TS: trophic similarity; TR: topological role (netcon = network connector, modcon = module connector, modhub = module hub, modspe = module specialist).") %>%
   kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 4.5)

### 2023-01-26 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Submission formatting

--- 2023-01-25 1st_Manuscript/ManuscriptDraft.Rmd
@@
   Area
-author: "Tomás I. Marina, Irene R. Schloss and Luciana Riccialdelli"
+author:
+  - name: Tomás I. Marina^a^
+    email: tomasimarina@gmail.com
+  - name: Irene R. Schloss^a^^,^^b^
+  - name: Luciana Riccialdelli^a^
+address:
+  - code: 1
+    address: Centro Austral de Investigaciones Cientificas (CADIC-CONICET), Argentina
+  - code: 2
+    address: Instituto Antartico Argentino (IAA), Argentina
+abstract: |
+  The abstract goes here.
+
+keywords: 
+  - Food web
+  - Complexity
+  - Structure
+  - Marine Protected Area
+  - Southwest Atlantic
+journal: "MEPS, Oikos, Polar Biology (?)"
+date: "`r Sys.Date()`"
+classoption: preprint, 3p, authoryear
+bibliography: AMPBancoBurdwood.bib
+nocite: '@*'
+linenumbers: true
+numbersections: true
+# Use a CSL with `citation_package = "default"`
+csl: "apa-old-doi-prefix.csl"
 output: 
-  pdf_document: default
-  word_document: default
-bibliography: AMPBancoBurdwood.bib
-csl: "marine-ecology-progress-series.csl"
-nocite: '@*'
-header-includes:
-- \usepackage[left]{lineno}
-- \linenumbers
+  rticles::elsevier_article:
+    keep_tex: true
+    citation_package: "default"
 ---
@@
 
-## Abstract
+# Introduction
 
-\newpage
+Introduction to MPAs and MPA N-BB
 
-## Introduction
-
-Brief description and ecological importance of MPAN-BB
+Ecological importance of MPA N-BB to the region
 
@@
 
-Benefits of studying complex ecosystems using network approach
+Why using a network approach
 
-Objective
 In the present work we present the first, detailed analysis of the food web for the MPA Namuncurá - Banco Burdwood ecosystem.
@@
 
-\newpage
+# Methodology
 
-## Methodology
+## Study area
 
-### Study area
-
-The MPA Namuncurá-Banco Burdwood is a shallow submarine plateau called Burdwood Bank (BB) located 150 km east of Isla de los Estados and 200 km south from Malvinas/Falkland Islands (Figure 1).
+The MPA Namuncurá - Banco Burdwood is a shallow submarine plateau called Burdwood Bank (BB) located 150 km east of Isla de los Estados and 200 km south from Malvinas/Falkland Islands (Figure 1).
 It comprises nearly 34.000 km^2^ circumscribed by the 200 m isobath, between 54º–55ºS and 56º–62ºW, with a slight slope extended nearly 370 km east–west.
@@
 
-```{r figure1, echo=FALSE, out.width = '100%', fig.cap="Map of the Marine Protected Area Namuncurá-Banco Burdwood.
+```{r figure1, echo=FALSE, fig.width = 5, fig.height = 10, out.width = '100%', fig.cap="Map of the Marine Protected Area Namuncurá - Banco Burdwood.
 Taken from https://www.argentina.gob.ar/parquesnacionales/areasmarinas/namuncura-burdwood."}
@@
 
-### Network construction
+## Network construction
 
@@
 
-### Network analysis
+## Network analysis
 
-We analysed the MPA Namuncurá-Banco Burdwood network of trophic interactions, hereafter food web, at two levels: 1) global, considering species and interactions of the whole network; and 2) species, considering interactions and species related to a particular species.
-The global-level analysis aims to characterize the network of trophic interactions in terms of complexity and structure.
+We analysed the MPA Namuncurá - Banco Burdwood network of trophic interactions, hereafter food web, at two levels: 1) network, considering species and interactions of the whole network; and 2) species, considering interactions and species related to a particular species.
+The network-level analysis aims to characterize the network of trophic interactions in terms of complexity and structure.
 For this we calculated several network properties commonly used to describe empirical food webs [@Pascual2005]: (1) number of species S; (2) number of interactions or links L; (3) link density L/S; (4) Connectance L/S^2; (5) omnivory Omn; and (6) shortest path length SPL.
 Also, we estimated the (7) degree distributions for the food web, for prey and predators, and for each functional group (e.g.
-Amphipoda, Ascidiacea, Bivalvia, Fish, Marine mammals, Seabirds, etc.) (Table 1).
+Amphipoda, Ascidiacea, Bivalvia, Fish, Marine mammals, Sea birds, etc.) (Table 1).
 The prey and predator distributions indicate the frequency of prey among predators, and viceversa; the functional group's degree shows the distribution of interactions within groups.
@@
 
-table1 <- add_row(table1, Name="Degree distribution", Definition="Probability of trophic species P(k) that have k or more interactions (both predator and prey links).", Implications="It suggests on the vulnerability of complex food webs against random failures and intentional attacks (i.e.
+table1 <- add_row(table1, Name="Degree distribution", Definition="Frequency of trophic species that have k or more interactions.", Implications="It suggests on the vulnerability of complex food webs against random failures and intentional attacks (i.e.
 species extinctions).", Reference="Albert & Barabási 2002")
@@
 pandoc.table(table1, digits = 4, colnames("Property","Definition","Implication","Reference"), style="multiline", split.tables = Inf, justify = c('left','left','left','right'), emphasize.strong.cols = 1, emphasize.rownames = 1,
-             caption = "List of network properties analysed, definitions, and relevant ecological implications related to food web complexity and structure.")
+             caption = "List of network and species-level properties analysed, definitions, and relevant ecological implications related to food web complexity and structure.")
 
@@
 
-\newpage
+# Results
 
-## Results
-
-### Network-level properties
+## Network-level properties
 
@@
 
-```{r figure2, echo=FALSE, fig.align='center', fig.width = 20, fig.height=20, fig.cap="Graph of the food web of MPA Namuncurá-Banco Burdwood.
+\newpage
+
+```{r figure2, echo=FALSE, fig.width = 5.5, fig.height = 10, fig.align='center', fig.cap="Graph of the food web for the MPA Namuncurá - Banco Burdwood.
 Circles represent species and arrows trophic interactions.
-Colour gradient indicate the trophic level.
-Circle diameter is relative to the number of interactions."}
+Circle diameter is relative to the number of interactions.
+Colour gradient indicate the trophic level."}
 # Food web graph
@@
 
-par(cex.axis=1.5, cex.lab=1.5)
+par(cex.axis=0.8, cex.lab=0.8)
 figure_2 <- plot_troph_level(g, vertexLabel = F, modules = F, ylab = "Trophic level")
@@
 knitr::kable(round(prop_topol,2) %>% dplyr::select(Size, Links, LD, Connectance, Omnivory, PathLength), col.names = c("Species","Interactions","Density","Connectance","Omnivory","Path length"),
-                      caption = "Global-level properties of the MPA Namuncurá-Banco Burdwood food web. See table 1 for definitions and ecological relevance.") %>% row_spec(0,bold=TRUE)
+                      caption = "Network-level properties of the MPA Namuncurá - Banco Burdwood food web. See table 1 for definitions and ecological relevance.") %>% row_spec(0,bold=TRUE)
 
@@
 The degree distribution of the food web showed an asymmetric frequency in the number of interactions, where most of the species had a relatively low number of interactions and few species concentrated the majority of them (Figure 3A).
-If we consider the distribution of prey among predators, most of the consumers fed on a low number of prey whereas few of them had multiple preys (Figure 3B).
-These were the top-five predators in terms of prey: *Patagonotothen guntheri* (Notothenioid fish, 52 prey), *Patagonotothen ramsayi* (Notothenioid fish, 50 prey), *Dissostichus eleginoides* (Notothenioid fish, 30 prey), *Bathyraja brachyurops* (Chondrichthyan, 30 prey), and *Bathyraja griseocauda* (Chondrichthyan, 28 prey).
+The distribution of prey among predators showed that most of the consumers fed on a low number of prey whereas few of them had multiple preys (Figure 3B).
+These were the top-five predators in number of prey: *Patagonotothen guntheri* (Notothenioid fish, 52 prey), *Patagonotothen ramsayi* (Notothenioid fish, 50 prey), *Dissostichus eleginoides* (Notothenioid fish, 30 prey), *Bathyraja brachyurops* (Chondrichthyan, 30 prey), and *Bathyraja griseocauda* (Chondrichthyan, 28 prey).
 Following the same distribution pattern, few prey presented multiple predators (Figure 3C).
-These were the top-five prey in number of predators: Detritus (Non-living, predators), the three categories of Diatoms considered (benthic, centric and pennate, 72 predators on average), and species of genus *Euphausia* (Zooplankton, 46 predators).
-Finally, taking into account the interactions within each functional group, the situation is the same as in the whole food web (Figure 3D).
-Overall, there is an evident asymmetry in the distribution of interactions among species in the MPA Namuncurá-Banco Burdwood food web.
+These were the top-five prey in number of predators: Detritus (Non-living, 153 predators), the three categories of Diatoms considered (benthic, centric and pennate, 72 predators on average), and species of the genus *Euphausia* (Zooplankton, 46 predators).
+Finally, taking into account the interactions within each functional group, again the majority of the interactions were concentrated in few species (Figure 3D).
+The most evident species were: *Themisto gaudichaudii* (Amphipoda), *Zygochlamys patagonica* (Bivalvia), *Aspidostoma giganteum* (Bryozoa), *Munida gregaria* (Decapoda), *Patagonotothen ramsayi* and *Patagonotothen guntheri* (bentho-pelagic fish), *Psychrolutes marmoratus* (demersal fish), and species of *Euphausia* (Zooplankton).
+Overall, there is an evident asymmetry in the distribution of interactions among species at different levels in the MPA Namuncurá - Banco Burdwood food web.
 
@@
 
-```{r figure3, echo=FALSE, fig.height = 25, fig.width = 20, fig.cap="Degree distributions for the (A) food web, for (B) prey among predators, (C) predators among prey, and (D) for each functional group.
-Groups are vertically ordered by increasing trophic level."}
+```{r figure3, echo=FALSE, fig.width = 6.5, fig.height = 9, fig.align='center', fig.cap="Degree distributions for the (A) food web, for (B) prey among predators, (C) predators among prey, and (D) for each functional group.
+Groups are vertically ordered by increasing trophic level; groups with less than 3 species were not plotted (e.g.
+pelagic fish)."}
 # Degree distributions: network, predator, prey & group
@@
     geom_histogram(bins = 100, alpha = 0.3, color = "black") +
-    labs(x = "Number of interactions (Degree)", y = "Frequency") +
+    labs(x = "Degree (total interactions)", y = "Frequency") +
     theme_bw() +
     theme(legend.position = "none",
-          axis.text.x = element_text(size = 26),
-          axis.text.y = element_text(size = 26),
-          axis.title.x = element_text(face = "bold", size = 26),
-          axis.title.y = element_text(face = "bold", size = 26))
+          axis.text.x = element_text(size = 10),
+          axis.text.y = element_text(size = 10),
+          axis.title.x = element_text(face = "bold", size = 10),
+          axis.title.y = element_text(face = "bold", size = 10))
 
@@
     theme(legend.position = "none",
-          axis.text.x = element_text(size = 26),
-          axis.text.y = element_text(size = 26),
-          axis.title.x = element_text(face = "bold", size = 26),
-          axis.title.y = element_text(face = "bold", size = 26)) #+
+          axis.text.x = element_text(size = 10),
+          axis.text.y = element_text(size = 10),
+          axis.title.x = element_text(face = "bold", size = 10),
+          axis.title.y = element_text(face = "bold", size = 10)) #+
 # annotate("text", x = Inf, y = Inf, label = paste("Prey per predator = ", round(prop_topol$Generality, 2), sep = ""),
@@
     theme(legend.position = "none",
-          axis.text.x = element_text(size = 26),
-          axis.text.y = element_text(size = 26),
-          axis.title.x = element_text(face = "bold", size = 26),
-          axis.title.y = element_text(face = "bold", size = 26)) #+
+          axis.text.x = element_text(size = 10),
+          axis.text.y = element_text(size = 10),
+          axis.title.x = element_text(face = "bold", size = 10),
+          axis.title.y = element_text(face = "bold", size = 10)) #+
 # annotate("text", x = Inf, y = Inf, label = paste("Predators per prey = ", round(prop_topol$Vulnerability, 2), sep = ""),
@@
     theme(legend.position = "none",
-          axis.text.x = element_text(size = 26),
-          axis.text.y = element_text(size = 20),
-          axis.title.x = element_text(face = "bold", size = 26),
-          axis.title.y = element_text(face = "bold", size = 26),
-          plot.tag = element_text(face = "bold", size = 32),
+          axis.text.x = element_text(size = 10),
+          axis.text.y = element_text(size = 6),
+          axis.title.x = element_text(face = "bold", size = 10),
+          axis.title.y = element_text(face = "bold", size = 10),
+          plot.tag = element_text(face = "bold", size = 10),
           plot.tag.position = c(0.05, 1))
@@
 figure_3 <- ggarrange(a,                                                                                         # First row
-          ggarrange(b, c, ncol = 2, labels = c("B", "C"), font.label=list(color="black",size=30)),   # Second row
+          ggarrange(b, c, ncol = 2, labels = c("B", "C"), font.label=list(color="black",size=10)),   # Second row
           ggarrange(d, ncol = 1),                                                                    # Third row
           nrow = 3, labels = "A",
-          font.label=list(color="black",size=30))
+          font.label=list(color="black",size=10))
 figure_3
@@
 
-\newpage
-
-### Species-level properties
+## Species-level properties
 
@@
 the higher the species' TL, the lower the trophic similarity or the higher the uniqueness in terms of trophic role (Figure 4C).
-Here we highlight the following high-trophic level species of fishes (*Bathyraja macloviana*, *Squalus acanthias*), echinoderms (*Diplopteraster clarki*, *Pteraster sp*), seabirds (*Phalacrocorax_atriceps*, *Eudyptes chrysocome*), and marine mammals (*Lagenorhynchus_cruciger*, *Mesoplodon_bowdoini*) (Table S3).
-There was also a negative significant relationship with closeness, however less strong: low-TL species were relatively closer to any other species in the food web than high-TL ones (Figure 4B).
-Species of genera *Calanus* and *Euphausia*, and Brachiopoda trophic species, all of them with TL < 3, registered the highest values (Table S3).
+Here it's noteworthy to highlight high-trophic level species with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster sp* (echinoderms), *Phalacrocorax_atriceps* and *Eudyptes chrysocome* (sea birds), and *Lagenorhynchus cruciger* and *Mesoplodon bowdoini* (marine mammals) (Table S3).
+
+We also found a negative significant relationship with closeness, however less evident, meaning that low-TL species are relatively closer to any other species in the food web (Figure 4B).
+Species of genera *Calanus* and *Euphausia*, and species of Brachiopoda, all of them with TL < 3, registered the highest values of closeness (Table S3).
+
 It's noteworthy that the highest values of betweenness were shown by species of mid-TLs (3-4), meaning that those species participated in the highest number of shortest paths between species (Figure 4A).
-These were the species with the highest values: *Patagonotothen ramsayi*, *Dissostichus eleginoides*, *Salilota australis* (fish), *Doryteuthis gahi* (Cephalopoda), and *Patagonotothen guntheri* (Table S3).
+These were the species with the highest values: *Patagonotothen ramsayi*, *Dissostichus eleginoides*, *Salilota australis* (fishes), *Doryteuthis gahi* (Cephalopoda), and *Patagonotothen guntheri* (Notothenioid fish) (Table S3).
+
 Taking into account the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.77); 'module hub' was constrained to mid-TL species (2.48 - 3.92); 'module connector' from low to mid-TLs (1 - 3.86); and 'network connector', the least frequent, had all of its species in TL = 1, except for one with TL = 3.47 (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework).
-Here it's important to highlight species of the latter two topological roles, because they are responsible for linking modules and maintaining the connectivity of the food web: 40 species (5 network connectors + 35 module connectors) from 20 different functional groups with a TL range = 1 - 3.86.
+Here it's important to highlight species of the two latter topological roles, because they are responsible for linking modules and maintaining the connectivity of the food web: 40 species (5 network connectors + 35 module connectors) from 20 different functional groups with a TL range = 1 - 3.86.
 
@@
 
-```{r figure4, echo=FALSE, fig.width = 20, fig.height=20, fig.cap="Species-level properties (A) betweenness, (B) closeness, (C) trophic similarity, and (D) topological role by trophic level.
+```{r figure4, echo=FALSE, fig.width = 6.5, fig.height = 6.5, fig.align='center', fig.cap="Species-level properties by trophic level: (A) betweenness, (B) closeness, (C) trophic similarity, and (D) topological role.
 Each point represents a species.
@@
   ggplot(., aes(x = TL, y = Between)) +
-  geom_point() +
+  geom_point(size=0.3) +
   geom_smooth(method = "lm") +
@@
   theme(panel.grid = element_blank(),
-        axis.text.x = element_text(size = 26),
-        axis.text.y = element_text(size = 26),
-        axis.title = element_text(size = 26, face = "bold"))
+        axis.text.x = element_text(size = 10),
+        axis.text.y = element_text(size = 10),
+        axis.title = element_text(size = 10, face = "bold"))
 
@@
   ggplot(., aes(x = TL, y = Close)) +
-  geom_point() +
+  geom_point(size=0.3) +
   geom_smooth(method = "lm") +
@@
   ggplot(., aes(x = TL, y = meanTrophicSimil)) +
-  geom_point() +
+  geom_point(size=0.3) +
   geom_smooth(method = "lm") +
@@
   geom_boxplot(aes(color = factor(TopRole), fill = factor(TopRole)), alpha=0.9) +
-  geom_jitter(aes(color = factor(TopRole), fill = factor(TopRole))) +
+  geom_jitter(size=0.3, aes(color = factor(TopRole), fill = factor(TopRole))) +
   scale_fill_manual(values=cols) +
@@
   theme(panel.grid = element_blank(),
-        axis.text.x = element_text(size = 26),
-        axis.text.y = element_text(size = 26),
-        axis.title = element_text(size = 26, face = "bold"),
+        axis.text.x = element_text(size = 10),
+        axis.text.y = element_text(size = 10),
+        axis.title = element_text(size = 10, face = "bold"),
         legend.position = "none")
@@
                       labels = c("A","B"), ncol=2,
-                      font.label = list(size = 30, color = "black"))
-figure_ab <- annotate_figure(figure_ab, bottom = textGrob("Trophic level", gp = gpar(fontface="bold", col="black", fontsize=26)))
+                      font.label = list(size = 10, color = "black"))
+figure_ab <- annotate_figure(figure_ab, bottom = textGrob("Trophic level", gp = gpar(fontface="bold", col="black", fontsize=10)))
 figure_4 <- ggarrange(figure_ab,                                                                                         # First row
-          ggarrange(plot_sp_ts, plot_sp_tr, ncol = 2, labels = c("C", "D"), font.label=list(color="black",size=30)),                                            
+          ggarrange(plot_sp_ts, plot_sp_tr, ncol = 2, labels = c("C", "D"), font.label=list(color="black",size=10)),                                            
           nrow = 2)
@@
 
-\newpage
+# Discussion
 
-## Discussion
+## The MPA Namuncurá - Banco Burdwood food web
 
-### The MPA Namuncurá - Banco Burdwood food web
-
-* The MPA Namuncurá - Banco Burdwood food web is one of the most highly-resolved network of trophic interactions described for subpolar and polar regions.
-Compare with other subpolar and polar food webs.
+* The MPA Namuncurá - Banco Burdwood food web is one of the most highly-resolved networks of trophic interactions described for subpolar and polar regions.
+Compare network-level properties with other subpolar and polar food webs.
 
 * The food web shows an asymmetry in the distribution of interactions at several levels: food web, functional group, prey and predators. In all of them interactions are concentrated in a few species.
-On one hand, this asymmetry indicates that most consumers have a narrow diet, few present flexible diets (Patagonotothen guntheri, P.
-ramsayi, Dissostichus eleginoides, Bathyraja brachyurops, B.
-griseocauda).
+On one hand, this asymmetry indicates that most consumers have a narrow diet, and few present flexible diets (*Patagonotothen guntheri*, *P.
+ramsayi*, *Dissostichus eleginoides*, *Bathyraja brachyurops*, *B.
+griseocauda*).
 On the other hand few prey are consumed by many predators, meaning that there are dominant food sources from which most consumers depend on: detritus, diatoms (benthic, centric, pennate), and species of *Euphausia*.
 
-### Species' role
+## Species' role
 
@@
 Species at mid-trophic levels (3-4) lie in more shortest paths between species than any other species: ‘bridge’ role.
-Implications for spread of perturbations like mercury, microplastics.
+Implications for spread of perturbations like mercury [@Fioramonti2022], microplastics [@Cossi2021].
 
-* Closeness. Low-trophic level species are relatively closer to other species in the food web.
+* Closeness.
+Low-trophic level species are relatively closer to other species in the food web.
+Apart from the most demanded food sources (i.e.
+detritus), which are logically closer to many species, unexpected consumers arise as important in this regard.
+Species of the zooplankton community like *Calanus* and *Euphausia* are crucial for the food web functioning, since they can affect others more quickly.
 
@@
 There is a functional redundancy at these levels of the food web.
-On the other hand, less trophic similarity at high levels indicate uniqueness in terms of trophic role.
-This highlights the importance of top predators.
+On the other hand, less trophic similarity at high TLs indicate uniqueness in terms of trophic role.
+This highlights the importance of top predators in the sense that they play a role that cannot be played by any other species.
 
 * Topological role.
-network connector and module connector species are responsible for linking modules and maintaining the connectivity of the food web.
-TL range for these species: 1 - 3.86.
-Low and mid-trophic level species are responsible for maintaining the connectivity of the food web.
+Low and mid-trophic level species (TL = 1 - 3.86) are responsible for maintaining the connectivity of the food web (network connector and module connector).
 The functional groups represented are: Amphipoda, Bivalvia, Bryozoa, Cnidaria, Cumacea, Decapoda, Detritus, Diatoms, Echinodermata, Fish (bentho-pelagic, demersal, chondrichthyes), Foraminifera, Polychaeta, Porifera, Zooplankton.
+This shows that the structure of the food web depends on a diversity of species, which at the end comprise the ecosystem's diversity.
 
-* Overall, low and mid-trophic level species present the highest betweenness and closeness values, and the most important topological roles.
-Mid-trophic level species are more redundant than those at low and high trophic levels.
+* Overall, low and mid-trophic level species arise as crucial in the structure of the MPA Namuncurá - Banco Burdwood food web, since they present the highest betweenness and closeness values, and the most important topological roles.
+This coincides with a recent study that suggest a wasp-waist trophic structure for the region [@Riccialdelli2020].
+However, we also suggest that there exists functional redundancy at mid-trophic levels.
+Furthermore, our study points out species of high-trophic levels due to its uniqueness role.
 
-### Caveats and future perspectives
+## Caveats and future perspectives
 
@@
 
+* The lack of density or biomass data might have neglected well-known important species for the structure of the food web: *Sprattus fuegensis*.
+
 Perspectives:
@@
 
-\newpage
+# Conclusion
 
-## References
+# References

### 2023-01-26 MS_ToSubmit/MS_Burdwood_foodweb.tex
Submission formatting

\documentclass[preprint, 3p,
authoryear]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%

\usepackage[hyphens]{url}

  \journal{MEPS, Oikos, Polar Biology (?)} % Sets Journal name

\usepackage{lineno} % add
  \linenumbers % turns line numbering on

\usepackage{graphicx}
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={The complex network of trophic interactions in a subAntarctic Marine Protected Area},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}

\setcounter{secnumdepth}{5}
% Pandoc toggle for numbering sections (defaults to be off)

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% From pandoc table feature
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

% Pandoc citation processing
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\begin{document}

\begin{frontmatter}

  \title{The complex network of trophic interactions in a subAntarctic
Marine Protected Area}
    \author[]{Tomás I. Marina\textsuperscript{a}%
  %
  }
   \ead{tomasimarina@gmail.com} 
    \author[]{Irene R. Schloss\textsuperscript{a,b}%
  %
  }

    \author[]{Luciana Riccialdelli\textsuperscript{a}%
  %
  }

      \affiliation[1]{Centro Austral de Investigaciones Cientificas
(CADIC-CONICET), Argentina}
    \affiliation[2]{Instituto Antartico Argentino (IAA), Argentina}
    \cortext[cor1]{Corresponding author}

  \begin{abstract}
  The abstract goes here.
  \end{abstract}
    \begin{keyword}
    Food web \sep Complexity \sep Structure \sep Marine Protected
Area \sep 
    Southwest Atlantic
  \end{keyword}

 \end{frontmatter}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Introduction to MPAs and MPA N-BB

Ecological importance of MPA N-BB to the region

Trophic ecology \& keystone spp knowledge of B Burdwood

Why using a network approach

In the present work we present the first, detailed analysis of the food
web for the MPA Namuncurá - Banco Burdwood ecosystem. For this we
applied a network approach to a highly-resolved food web. The objective
was twofold: characterise the food web in terms of complexity and
structure, and describe the species' role in such network framework.

\hypertarget{methodology}{%
\section{Methodology}\label{methodology}}

\hypertarget{study-area}{%
\subsection{Study area}\label{study-area}}

The MPA Namuncurá - Banco Burdwood is a shallow submarine plateau called
Burdwood Bank (BB) located 150 km east of Isla de los Estados and 200 km
south from Malvinas/Falkland Islands (Figure 1). It comprises nearly
34.000 km\textsuperscript{2} circumscribed by the 200 m isobath, between
54º--55ºS and 56º--62ºW, with a slight slope extended nearly 370 km
east--west. The BB is surrounded by steep flanks of more than 3000 m
depth through which strong currents circulate (Matano, Palma, \& Combes,
2019; A. R. Piola \& Gordon, 1989; Reta, 2014). Intense upwelling and
mixing occur over it, entraining deep nutrient rich waters into the
photic layer (Matano et al., 2019; A. Piola \& Falabella, 2009), and
resulting in a fairly homogeneous water column both spatially and
temporally (Glorioso \& Flather, 1995; Guerrero, Baldoni, \& Benavides,
1999; Matano et al., 2019). Physical features in the MPAN-BB are fairly
stable, with salinity averaging 34 all year round and temperature
ranging between 4 and 8ºC overall (Acha, Mianzan, Guerrero, Favero, \&
Bava, 2004; Guerrero et al., 1999; A. Piola \& Falabella, 2009).

\begin{figure}
\includegraphics[width=1\linewidth]{MPABurdwood_map} \caption{Map of the Marine Protected Area Namuncurá - Banco Burdwood. Taken from https://www.argentina.gob.ar/parquesnacionales/areasmarinas/namuncura-burdwood.}\label{fig:figure1}
\end{figure}

\hypertarget{network-construction}{%
\subsection{Network construction}\label{network-construction}}

In order to build the network of predator-prey interactions we reviewed
more than 150 references considering published articles, databases and
doctoral theses. Furthermore, we took into account personal
communications from experts belonging to the working group of the study
area (https://www.pampazul.gob.ar/tag/banco-burdwood/). The diversity of
the expertise of the authors contributing to the present study was a key
factor in enhancing the quality of the network, and inherently improved
the network representation of the MPA Namuncurá-Banco Burdwood
ecosystem. A list of the references used to build the network is
presented in Supplementary Material (Table S1).

Due to a lack of trophic data resolution for some species inhabiting the
MPA Namuncurá-Banco Burdwood, we followed the concept of trophic
species, here defined as aggregated groups of taxa. In most cases we
followed this when data on specific biological species were not
available, but for some cases we collapsed species when taxa shared the
same set of predators and prey (trophic similarity criteria). Details
about this can be found in Supplementary Material (Table S2).

With the gathered trophic data we constructed an interaction matrix of
pairwise interactions; a value of 1 or 0 was assigned to each element
a\_ij of the matrix depending on whether the j-species preyed or not on
the i-species. Then we transformed such matrix into an oriented graph
with L trophic interactions between S nodes or species. The orientation
or direction of the graph follows the flow of energy and matter in the
network, from prey to predator.

\hypertarget{network-analysis}{%
\subsection{Network analysis}\label{network-analysis}}

We analysed the MPA Namuncurá - Banco Burdwood network of trophic
interactions, hereafter food web, at two levels: 1) network, considering
species and interactions of the whole network; and 2) species,
considering interactions and species related to a particular species.
The network-level analysis aims to characterize the network of trophic
interactions in terms of complexity and structure. For this we
calculated several network properties commonly used to describe
empirical food webs (Pascual \& Dunne, 2005): (1) number of species S;
(2) number of interactions or links L; (3) link density L/S; (4)
Connectance L/S\^{}2; (5) omnivory Omn; and (6) shortest path length
SPL. Also, we estimated the (7) degree distributions for the food web,
for prey and predators, and for each functional group (e.g.~Amphipoda,
Ascidiacea, Bivalvia, Fish, Marine mammals, Sea birds, etc.) (Table 1).
The prey and predator distributions indicate the frequency of prey among
predators, and viceversa; the functional group's degree shows the
distribution of interactions within groups. The species-level analysis
aims to describe the species' role in the food web. For this we
considered the following properties: (1) betweenness Btw; (2) closeness
Cl; (3) trophic similarity TS; (4) topological role TR; and (5) trophic
level TL (Table 1). We also studied the relationship between species
trophic level and the other species properties by performing linear
regression analyses. Thus, we considered the IS as the dependent
variable and the given unweighted property as the independent variable,
and obtained the coefficients (slope and intercept) for the linear
model. Models were fitted using the least squares approach. We also
explored the mean IS distribution with the species habitat. These
properties provide a general appropriate description of species' role in
empirical complex food webs (Cirtwill et al., 2018).

All network analyses and graphs were performed in R version 4.2.2 (Team,
2022), mainly using `igraph' (Csardi \& Nepusz, 2006) and `multiweb'
(Saravia, 2022) packages. The source code and data are available at
https://github.com/TomasMarina/Banco-Burdwood.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2266}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2578}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2578}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2578}}@{}}
\caption{List of network and species-level properties analysed,
definitions, and relevant ecological implications related to food web
complexity and structure.}\tabularnewline
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Name}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Definition}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Implications}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
\textbf{Reference}
\end{minipage} \\
\midrule()
\endfirsthead
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Name}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Definition}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Implications}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
\textbf{Reference}
\end{minipage} \\
\midrule()
\endhead
\textbf{Number of species} & Number of trophic species in a food web. &
It represents the species diversity and has implications for the
persistence of the ecosystem. & May 1973, Tilman 1996 \\
\textbf{Number of interactions} & Total number of trophic interactions
in a food web. & It represents the number of pathways along which matter
and energy can flow. & Dunne et al.~2002 \\
\textbf{Link density} & Ratio of interactions to species in a food web &
It represents the average number of interactions per species; informs
about how connected species are in the food-web. & Dunne et al.~2002 \\
\textbf{Connectance} & Proportion of potential links among species that
are actually realized. & It measures the probability of interactions; it
is a fundamental measure of network complexity. Connectance can be
negatively or positively associated with food web robustness, depending
on the network structure (random vs non-random) or how the strength of
the interactions are distributed. & Martinez 1992 \\
\textbf{Degree distribution} & Frequency of trophic species that have k
or more interactions. & It suggests on the vulnerability of complex food
webs against random failures and intentional attacks (i.e. species
extinctions). & Albert \& Barabási 2002 \\
\textbf{Omnivory} & Species feeding on prey from more than one trophic
level. & It influences food web's stability; intermediate levels of
omnivory may stabilize it and may diffuse top-down effects thus reduce
the probability of trophic cascades. & McCann \& Hastings 1997 \\
\textbf{Shortest path length} & Average shortest path length between all
pairs of species. & A short path length imply a rapid spread of an
impact (e.g.~invasion, population fluctuation, local extinction)
throughout the food web. & Watts \& Strogatz 1998 \\
\textbf{Betweenness} & Number of shortest paths going through a species.
& Species with high betweenness act as ``bridges''; if removed, would
have rapidly spreading effects in the food web. & Freeman 1978, Lai et
al.~2012 \\
\textbf{Closeness} & Number of steps required to reach every other
species from a given species. & The removal of a species with high
closeness will affect the most other species in the food web. & Freeman
1978, Lai et al.~2012 \\
\textbf{Trophic similarity} & Trophic overlap based on shared and unique
resources (prey) and consumers (predators). & It measures one of the
most important aspects of species' niches, the trophic niche, and
functional aspects of biodiversity. & Martinez 1992 \\
\textbf{Topological role} & Species role according to interactions
within and across modules (subgroups of species). & Four roles are
defined: module hub, module specialist, module connector and network
connector. Species with the same role are expected to have similar
topological properties. & Guimera \& Nunes Amaral 2005 \\
\bottomrule()
\end{longtable}

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{network-level-properties}{%
\subsection{Network-level properties}\label{network-level-properties}}

In terms of complexity, the MPA Namuncurá - Banco Burdwood food web
consisted of 1778 predator-prey interactions and 379 species, where 93\%
of them were defined at the species taxonomical level (Figure 2, Table
S2). The food web presented a link density of 4.69, meaning the average
number of interactions per species, and a connectance of 0.01. Almost
half of the consumers were omnivores, feeding on sources at different
trophic levels. The food web showed a path length of 2.99, which implies
that nearly three interactions are needed to connect any pair of species
of the network (Table 1).

\newpage

\begin{figure}

{\centering \includegraphics{MS_Burdwood_foodweb_files/figure-latex/figure2-1}

}

\caption{Graph of the food web for the MPA Namuncurá - Banco Burdwood. Circles represent species and arrows trophic interactions. Circle diameter is relative to the number of interactions. Colour gradient indicate the trophic level.}\label{fig:figure2}
\end{figure}

\begin{table}

\caption{\label{tab:table2}Network-level properties of the MPA Namuncurá - Banco Burdwood food web. See table 1 for definitions and ecological relevance.}
\centering
\begin{tabular}[t]{r|r|r|r|r|r}
\hline
\textbf{Species} & \textbf{Interactions} & \textbf{Density} & \textbf{Connectance} & \textbf{Omnivory} & \textbf{Path length}\\
\hline
379 & 1778 & 4.69 & 0.01 & 0.48 & 2.99\\
\hline
\end{tabular}
\end{table}

The degree distribution of the food web showed an asymmetric frequency
in the number of interactions, where most of the species had a
relatively low number of interactions and few species concentrated the
majority of them (Figure 3A). The distribution of prey among predators
showed that most of the consumers fed on a low number of prey whereas
few of them had multiple preys (Figure 3B). These were the top-five
predators in number of prey: \emph{Patagonotothen guntheri}
(Notothenioid fish, 52 prey), \emph{Patagonotothen ramsayi}
(Notothenioid fish, 50 prey), \emph{Dissostichus eleginoides}
(Notothenioid fish, 30 prey), \emph{Bathyraja brachyurops}
(Chondrichthyan, 30 prey), and \emph{Bathyraja griseocauda}
(Chondrichthyan, 28 prey). Following the same distribution pattern, few
prey presented multiple predators (Figure 3C). These were the top-five
prey in number of predators: Detritus (Non-living, 153 predators), the
three categories of Diatoms considered (benthic, centric and pennate, 72
predators on average), and species of the genus \emph{Euphausia}
(Zooplankton, 46 predators). Finally, taking into account the
interactions within each functional group, again the majority of the
interactions were concentrated in few species (Figure 3D). The most
evident species were: \emph{Themisto gaudichaudii} (Amphipoda),
\emph{Zygochlamys patagonica} (Bivalvia), \emph{Aspidostoma giganteum}
(Bryozoa), \emph{Munida gregaria} (Decapoda), \emph{Patagonotothen
ramsayi} and \emph{Patagonotothen guntheri} (bentho-pelagic fish),
\emph{Psychrolutes marmoratus} (demersal fish), and species of
\emph{Euphausia} (Zooplankton). Overall, there is an evident asymmetry
in the distribution of interactions among species at different levels in
the MPA Namuncurá - Banco Burdwood food web.

A list of the distribution of interactions per species is presented in
Supplementary Material (Table S3).

\begin{figure}

{\centering \includegraphics{MS_Burdwood_foodweb_files/figure-latex/figure3-1}

}

\caption{Degree distributions for the (A) food web, for (B) prey among predators, (C) predators among prey, and (D) for each functional group. Groups are vertically ordered by increasing trophic level; groups with less than 3 species were not plotted (e.g. pelagic fish).}\label{fig:figure3}
\end{figure}

\hypertarget{species-level-properties}{%
\subsection{Species-level properties}\label{species-level-properties}}

The majority of the species of the food web were consumers, 336 out of
379; the rest were primary producers, such as diatoms (phytoplankton),
and non-living food sources like detritus and necromass.

We found different relationships between the species trophic level (TL)
and the rest of the analysed species-level properties (Figure 4A-D). In
this regard, the most evident significant relationship was with trophic
similarity, i.e.~the higher the species' TL, the lower the trophic
similarity or the higher the uniqueness in terms of trophic role (Figure
4C). Here it's noteworthy to highlight high-trophic level species with
low values of trophic similarity: \emph{Bathyraja macloviana} and
\emph{Squalus acanthias} (Chondrichthyans), \emph{Diplopteraster clarki}
and \emph{Pteraster sp} (echinoderms), \emph{Phalacrocorax\_atriceps}
and \emph{Eudyptes chrysocome} (sea birds), and \emph{Lagenorhynchus
cruciger} and \emph{Mesoplodon bowdoini} (marine mammals) (Table S3).

We also found a negative significant relationship with closeness,
however less evident, meaning that low-TL species are relatively closer
to any other species in the food web (Figure 4B). Species of genera
\emph{Calanus} and \emph{Euphausia}, and species of Brachiopoda, all of
them with TL \textless{} 3, registered the highest values of closeness
(Table S3).

It's noteworthy that the highest values of betweenness were shown by
species of mid-TLs (3-4), meaning that those species participated in the
highest number of shortest paths between species (Figure 4A). These were
the species with the highest values: \emph{Patagonotothen ramsayi},
\emph{Dissostichus eleginoides}, \emph{Salilota australis} (fishes),
\emph{Doryteuthis gahi} (Cephalopoda), and \emph{Patagonotothen
guntheri} (Notothenioid fish) (Table S3).

Taking into account the topological role, `module specialist' species
were the most frequent and presented a wide TL range (1 - 4.77); `module
hub' was constrained to mid-TL species (2.48 - 3.92); `module connector'
from low to mid-TLs (1 - 3.86); and `network connector', the least
frequent, had all of its species in TL = 1, except for one with TL =
3.47 (Figure 4D, see Figure S2 for species' topological roles in a food
web graph framework). Here it's important to highlight species of the
two latter topological roles, because they are responsible for linking
modules and maintaining the connectivity of the food web: 40 species (5
network connectors + 35 module connectors) from 20 different functional
groups with a TL range = 1 - 3.86.

An exhaustive list of the species-level properties is presented in
Supplementary Material (Table S3).

\begin{figure}

{\centering \includegraphics{MS_Burdwood_foodweb_files/figure-latex/figure4-1}

}

\caption{Species-level properties by trophic level: (A) betweenness, (B) closeness, (C) trophic similarity, and (D) topological role. Each point represents a species. Linear regressions for betweenness ($y = 72.48x - 111.98, R^2 = 0.04, p-value < 3.38e-05$), closeness ($y = 5.78e-06x - 9.37e-04, R^2 = -0.0005, p-value = 0.37$) and trophic similarity ($y = -0.01x - 0.11, R^2 = 0.07, p-value = 6.76e-08$). Note that for A, B and C panels only species with TLs equal or greater than 2 were considered.}\label{fig:figure4}
\end{figure}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{the-mpa-namuncuruxe1---banco-burdwood-food-web}{%
\subsection{The MPA Namuncurá - Banco Burdwood food
web}\label{the-mpa-namuncuruxe1---banco-burdwood-food-web}}

\begin{itemize}
\item
  The MPA Namuncurá - Banco Burdwood food web is one of the most
  highly-resolved networks of trophic interactions described for
  subpolar and polar regions. Compare network-level properties with
  other subpolar and polar food webs.
\item
  The food web shows an asymmetry in the distribution of interactions at
  several levels: food web, functional group, prey and predators. In all
  of them interactions are concentrated in a few species. On one hand,
  this asymmetry indicates that most consumers have a narrow diet, and
  few present flexible diets (\emph{Patagonotothen guntheri}, \emph{P.
  ramsayi}, \emph{Dissostichus eleginoides}, \emph{Bathyraja
  brachyurops}, \emph{B. griseocauda}). On the other hand few prey are
  consumed by many predators, meaning that there are dominant food
  sources from which most consumers depend on: detritus, diatoms
  (benthic, centric, pennate), and species of \emph{Euphausia}.
\end{itemize}

\hypertarget{species-role}{%
\subsection{Species' role}\label{species-role}}

Our results state that certain species play particular roles in the
structure of the food web.

\begin{itemize}
\item
  Betweenness. Species at mid-trophic levels (3-4) lie in more shortest
  paths between species than any other species: `bridge' role.
  Implications for spread of perturbations like mercury (Fioramonti,
  Ribeiro Guevara, Becker, \& Riccialdelli, 2022), microplastics (Cossi
  et al., 2021).
\item
  Closeness. Low-trophic level species are relatively closer to other
  species in the food web. Apart from the most demanded food sources
  (i.e.~detritus), which are logically closer to many species,
  unexpected consumers arise as important in this regard. Species of the
  zooplankton community like \emph{Calanus} and \emph{Euphausia} are
  crucial for the food web functioning, since they can affect others
  more quickly.
\item
  Trophic similarity. Species are more similar at low and mid-trophic
  levels (2-4). There is a functional redundancy at these levels of the
  food web. On the other hand, less trophic similarity at high TLs
  indicate uniqueness in terms of trophic role. This highlights the
  importance of top predators in the sense that they play a role that
  cannot be played by any other species.
\item
  Topological role. Low and mid-trophic level species (TL = 1 - 3.86)
  are responsible for maintaining the connectivity of the food web
  (network connector and module connector). The functional groups
  represented are: Amphipoda, Bivalvia, Bryozoa, Cnidaria, Cumacea,
  Decapoda, Detritus, Diatoms, Echinodermata, Fish (bentho-pelagic,
  demersal, chondrichthyes), Foraminifera, Polychaeta, Porifera,
  Zooplankton. This shows that the structure of the food web depends on
  a diversity of species, which at the end comprise the ecosystem's
  diversity.
\item
  Overall, low and mid-trophic level species arise as crucial in the
  structure of the MPA Namuncurá - Banco Burdwood food web, since they
  present the highest betweenness and closeness values, and the most
  important topological roles. This coincides with a recent study that
  suggest a wasp-waist trophic structure for the region (Riccialdelli et
  al., 2020). However, we also suggest that there exists functional
  redundancy at mid-trophic levels. Furthermore, our study points out
  species of high-trophic levels due to its uniqueness role.
\end{itemize}

\hypertarget{caveats-and-future-perspectives}{%
\subsection{Caveats and future
perspectives}\label{caveats-and-future-perspectives}}

Caveats:

\begin{itemize}
\item
  Seasonal variation in predators' diet due to food source availability.
\item
  Spatial variation of study area: Banco Burdwood west-east gradient.
\item
  The lack of density or biomass data might have neglected well-known
  important species for the structure of the food web: \emph{Sprattus
  fuegensis}.
\end{itemize}

Perspectives:

\begin{itemize}
\item
  Estimation of interaction strength to gain insights into food web
  stability and response to anthropogenic and environmental
  perturbations.
\item
  Simulate perturbations on food web and target species: mercury
  transfer, microplastic pollution, fisheries.
\end{itemize}

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Acha2004}{}}%
Acha, E. M., Mianzan, H. W., Guerrero, R. A., Favero, M., \& Bava, J.
(2004). Marine fronts at the continental shelves of austral {South
America}: {Physical} and ecological processes. \emph{Journal of Marine
Systems}, \emph{44}(1), 83--105. doi:
\href{https://doi.org/10.1016/j.jmarsys.2003.09.005}{10.1016/j.jmarsys.2003.09.005}

\leavevmode\vadjust pre{\hypertarget{ref-Albert2002}{}}%
Albert, R., \& Barabási, A.-L. (2002). Statistical mechanics of complex
networks. \emph{Reviews of Modern Physics}, \emph{74}(1), 47--97. doi:
\href{https://doi.org/10.1103/RevModPhys.74.47}{10.1103/RevModPhys.74.47}

\leavevmode\vadjust pre{\hypertarget{ref-APN2022}{}}%
APN. (2022). \emph{Plan de gestión {AMP Namuncurá Banco Burdwood}}.

\leavevmode\vadjust pre{\hypertarget{ref-Borrelli2014}{}}%
Borrelli, J. J., \& Ginzburg, L. R. (2014). Why there are so few trophic
levels: {Selection} against instability explains the pattern. \emph{Food
Webs}, \emph{1}(1), 10--17. doi:
\href{https://doi.org/10.1016/j.fooweb.2014.11.002}{10.1016/j.fooweb.2014.11.002}

\leavevmode\vadjust pre{\hypertarget{ref-Cirtwill2018}{}}%
Cirtwill, A. R., Dalla Riva, G. V., Gaiarsa, M. P., Bimler, M. D.,
Cagua, E. F., Coux, C., \& Dehling, D. M. (2018). A review of species
role concepts in food webs. \emph{Food Webs}, \emph{16}, e00093. doi:
\href{https://doi.org/10.1016/j.fooweb.2018.e00093}{10.1016/j.fooweb.2018.e00093}

\leavevmode\vadjust pre{\hypertarget{ref-Cossi2021}{}}%
Cossi, P. F., Ojeda, M., Chiesa, I. L., Rimondino, G. N., Fraysse, C.,
Calcagno, J., \& Pérez, A. F. (2021). First evidence of microplastics in
the {Marine Protected Area Namuncurá} at {Burdwood Bank}, {Argentina}: A
study on {Henricia} obesa and {Odontaster} penicillatus
({Echinodermata}: {Asteroidea}). \emph{Polar Biology}, \emph{44}(12),
2277--2287. doi:
\href{https://doi.org/10.1007/s00300-021-02959-5}{10.1007/s00300-021-02959-5}

\leavevmode\vadjust pre{\hypertarget{ref-Csardi2006}{}}%
Csardi, \& Nepusz. (2006). \emph{The igraph software package for complex
network research}.

\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002}{}}%
Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002). Network
structure and biodiversity loss in food webs: Robustness increases with
connectance. \emph{Ecology Letters}, \emph{5}(4), 558--567. doi:
\href{https://doi.org/10.1046/j.1461-0248.2002.00354.x}{10.1046/j.1461-0248.2002.00354.x}

\leavevmode\vadjust pre{\hypertarget{ref-Fioramonti2022}{}}%
Fioramonti, N. E., Ribeiro Guevara, S., Becker, Y. A., \& Riccialdelli,
L. (2022). Mercury transfer in coastal and oceanic food webs from the
{Southwest Atlantic Ocean}. \emph{Marine Pollution Bulletin},
\emph{175}, 113365. doi:
\href{https://doi.org/10.1016/j.marpolbul.2022.113365}{10.1016/j.marpolbul.2022.113365}

\leavevmode\vadjust pre{\hypertarget{ref-Freeman1978}{}}%
Freeman, L. C. (1978). Centrality in social networks conceptual
clarification. \emph{Social Networks}, \emph{1}(3), 215--239. doi:
\href{https://doi.org/10.1016/0378-8733(78)90021-7}{10.1016/0378-8733(78)90021-7}

\leavevmode\vadjust pre{\hypertarget{ref-Glorioso1995}{}}%
Glorioso, P. D., \& Flather, R. A. (1995). A barotropic model of the
currents off {SE South America}. \emph{Journal of Geophysical Research:
Oceans}, \emph{100}(C7), 13427--13440. doi:
\href{https://doi.org/10.1029/95JC00942}{10.1029/95JC00942}

\leavevmode\vadjust pre{\hypertarget{ref-Guerrero1999}{}}%
Guerrero, R. A., Baldoni, A. G., \& Benavides, H. R. (1999).
\emph{Oceanographic conditions at the southern end of the argentine
continental slope}. doi: \url{http://10.0.64.26/handle/inidep/247}

\leavevmode\vadjust pre{\hypertarget{ref-Guimera2005}{}}%
Guimerà, R., \& Nunes Amaral, L. A. (2005). Functional cartography of
complex metabolic networks. \emph{Nature}, \emph{433}(7028), 895--900.
doi: \href{https://doi.org/10.1038/nature03288}{10.1038/nature03288}

\leavevmode\vadjust pre{\hypertarget{ref-Lai2012}{}}%
Lai, S.-M., Liu, W.-C., \& Jordán, F. (2012). On the centrality and
uniqueness of species from the network perspective. \emph{Biology
Letters}, \emph{8}(4), 570--573. doi:
\href{https://doi.org/10.1098/rsbl.2011.1167}{10.1098/rsbl.2011.1167}

\leavevmode\vadjust pre{\hypertarget{ref-Lopez-Gappa2018}{}}%
López-Gappa, J., Liuzzi, M. G., \& Zelaya, D. G. (2018). A new genus and
species of cheilostome bryozoan associated with hermit crabs in the
subantarctic {Southwest Atlantic}. \emph{Polar Biology}, \emph{41}(4),
733--741. doi:
\href{https://doi.org/10.1007/s00300-017-2234-9}{10.1007/s00300-017-2234-9}

\leavevmode\vadjust pre{\hypertarget{ref-Martinez1992}{}}%
Martinez, N. D. (1992). Constant {Connectance} in {Community Food Webs}.
\emph{The American Naturalist}, \emph{139}(6), 1208--1218. doi:
\href{https://doi.org/10.1086/285382}{10.1086/285382}

\leavevmode\vadjust pre{\hypertarget{ref-Matano2019}{}}%
Matano, R. P., Palma, E. D., \& Combes, V. (2019). The {Burdwood Bank
Circulation}. \emph{Journal of Geophysical Research: Oceans},
\emph{124}(10), 6904--6926. doi:
\href{https://doi.org/10.1029/2019JC015001}{10.1029/2019JC015001}

\leavevmode\vadjust pre{\hypertarget{ref-Matusevich2022}{}}%
Matusevich. (2022). \emph{Chondrichthyan fauna from the {Marine
Protected Area Namuncurá} at {Burdwood Bank}: Exploring egg nursery
grounds}. https://www.researchsquare.com. doi:
\href{https://doi.org/10.21203/rs.3.rs-2247873/v1}{10.21203/rs.3.rs-2247873/v1}

\leavevmode\vadjust pre{\hypertarget{ref-May1973}{}}%
May, R. (1973). \emph{Stability and complexity in model ecosystems}.
{Princeton University Press}.

\leavevmode\vadjust pre{\hypertarget{ref-McCann1997}{}}%
McCann, K., \& Hastings, A. (1997). Re\textendash evaluating the
omnivory\textendash stability relationship in food webs.
\emph{Proceedings of the Royal Society of London. Series B: Biological
Sciences}, \emph{264}(1385), 1249--1254. doi:
\href{https://doi.org/10.1098/rspb.1997.0172}{10.1098/rspb.1997.0172}

\leavevmode\vadjust pre{\hypertarget{ref-Pascual2005}{}}%
Pascual, M., \& Dunne, J. A. (2005). \emph{Ecological {Networks}:
{Linking Structure} to {Dynamics} in {Food Webs}}. {Oxford University
Press}.

\leavevmode\vadjust pre{\hypertarget{ref-Pastorino2019}{}}%
Pastorino, G. (2019). A new deep water gastropod of the genus
{Parabuccinum} ({Neogastropoda}: {Buccinulidae}) from southwestern
{Atlantic} waters with new data on the distribution of all species.
\emph{Marine Biodiversity}, \emph{49}(2), 913--922. doi:
\href{https://doi.org/10.1007/s12526-018-0876-7}{10.1007/s12526-018-0876-7}

\leavevmode\vadjust pre{\hypertarget{ref-Piola1989}{}}%
Piola, A. R., \& Gordon, A. L. (1989). Intermediate waters in the
southwest {South Atlantic}. \emph{Deep Sea Research Part A.
Oceanographic Research Papers}, \emph{36}(1), 1--16. doi:
\href{https://doi.org/10.1016/0198-0149(89)90015-0}{10.1016/0198-0149(89)90015-0}

\leavevmode\vadjust pre{\hypertarget{ref-Piola2009}{}}%
Piola, A., \& Falabella, V. (2009). \emph{El mar {Patagónico}}.
{Wildlife Conservation Society y Birdlife Internacional}.

\leavevmode\vadjust pre{\hypertarget{ref-Reta2014}{}}%
Reta, R. (2014). \emph{Oceanografía del {Banco Burdwood}: {Estado
Actual} del {Conocimiento} y {Perspectivas}}. {INIDEP}.

\leavevmode\vadjust pre{\hypertarget{ref-Riccialdelli2020}{}}%
Riccialdelli, L., Becker, Y. A., Fioramonti, N. E., Torres, M., Bruno,
D. O., Rey, A. R., \& Fernández, D. A. (2020). Trophic structure of
southern marine ecosystems: A comparative isotopic analysis from the
{Beagle Channel} to the oceanic {Burdwood Bank} area under a wasp-waist
assumption. \emph{Marine Ecology Progress Series}, \emph{655}, 1--27.
doi: \href{https://doi.org/10.3354/meps13524}{10.3354/meps13524}

\leavevmode\vadjust pre{\hypertarget{ref-Saravia2022a}{}}%
Saravia, L. A. (2022). \emph{Multiweb: {Ecological} network analyses
including multiplex networks}.

\leavevmode\vadjust pre{\hypertarget{ref-Schejter2016}{}}%
Schejter, L., Rimondino, C., Chiesa, I., Díaz de Astarloa, J. M., Doti,
B., Elías, R., \ldots{} Bremec, C. S. (2016). Namuncurá {Marine
Protected Area}: An oceanic hot spot of benthic biodiversity at
{Burdwood Bank}, {Argentina}. \emph{Polar Biology}, \emph{39}(12),
2373--2386. doi:
\href{https://doi.org/10.1007/s00300-016-1913-2}{10.1007/s00300-016-1913-2}

\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam2022}{}}%
Team, R. C. (2022). \emph{R: {A Language} and {Environment} for
{Statistical Computing}}. {Vienna, Austria}: R Foundation for
Statistical Computing.

\leavevmode\vadjust pre{\hypertarget{ref-Tilman1996}{}}%
Tilman, D. (1996). Biodiversity: {Population Versus Ecosystem
Stability}. \emph{Ecology}, \emph{77}(2), 350--363. doi:
\href{https://doi.org/10.2307/2265614}{10.2307/2265614}

\leavevmode\vadjust pre{\hypertarget{ref-Watts1998}{}}%
Watts, D. J., \& Strogatz, S. H. (1998). Collective dynamics of
{``small-world''} networks. \emph{Nature}, \emph{393}(6684), 440--442.
doi: \href{https://doi.org/10.1038/30918}{10.1038/30918}

\end{CSLReferences}

\end{document}

### 2023-01-26 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Finish M&M, Results

@@
 
-We analysed the MPA Namuncurá - Banco Burdwood network of trophic interactions, hereafter food web, at two levels: 1) network, considering species and interactions of the whole network; and 2) species, considering interactions and species related to a particular species.
-The network-level analysis aims to characterize the network of trophic interactions in terms of complexity and structure.
+We analysed the MPA Namuncurá - Banco Burdwood network of trophic interactions, hereafter food web, at two levels: A) network, considering species and interactions of the whole network; and B) species, considering interactions and species related to a particular species.
+The network-level analysis aims to characterise the network of trophic interactions in terms of complexity and structure.
 For this we calculated several network properties commonly used to describe empirical food webs [@Pascual2005]: (1) number of species S; (2) number of interactions or links L; (3) link density L/S; (4) Connectance L/S^2; (5) omnivory Omn; and (6) shortest path length SPL.
@@
 For this we considered the following properties: (1) betweenness Btw; (2) closeness Cl; (3) trophic similarity TS; (4) topological role TR; and (5) trophic level TL (Table 1).
-We also studied the relationship between species trophic level and the other species properties by performing linear regression analyses.
-Thus, we considered the IS as the dependent variable and the given unweighted property as the independent variable, and obtained the coefficients (slope and intercept) for the linear model.
+We also studied the relationship between species TL and the other species properties by performing linear regression analyses.
+Thus, we considered the TL as the dependent variable and the given property as the independent variable, and obtained the coefficients (slope and intercept) for the linear model.
 Models were fitted using the least squares approach.
-We also explored the mean IS distribution with the species habitat.
-These properties provide a general appropriate description of species' role in empirical complex food webs [@Cirtwill2018].
+We also explored the topological role categories with the species TL.
+These species-level properties provide a general appropriate description of species' role in empirical complex food webs [@Cirtwill2018].
 

### 2023-01-26 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Starting w/ Intro

@@
 
-Introduction to MPAs and MPA N-BB
+* Introduction to MPAs and MPA N-BB
 
-Ecological importance of MPA N-BB to the region
+Globally, the total area of the world ocean designated under marine protection adds up to nearly 29,600,000 km^2^, distributed across nearly 18,444 Marine Protected Areas (MPAs) and covering 8.16% of the ocean’s surface [@IUCN2023], and therefore approaching the 10% goal of the Convention of Biological Diversity [@ConventiononBiologicalDiversity2004].
+Latin America & Polar region status and growth.
 
-Trophic ecology & keystone spp knowledge of B Burdwood
+Approximately 42 countries with marine territories (27.3%) have above the global average of ocean area designated under protected areas, and 36 countries (23.4%; UNEP-WCMC, 2020; www.protectedplanet.net) exceed the 10% international commitment.
+Despite this progress, recent reports have shown that effective protection has been overestimated because it includes areas that are not yet effectively protected (only declared) as well as areas that allow significant extractive activities, such as fishing (Lubchenco & Grorud-Colvert, 2015; Sala et al., 2018).
+According to Sala et al.
+(2018), only 3.6% of the ocean should be currently considered as protected by implemented MPAs, and only 2% is strongly or fully protected by MPAs.
 
-Why using a network approach
+* Ecological importance of MPA N-BB to the region
+
+* Trophic ecology & keystone spp knowledge of B Burdwood
+
+* Why using a network approach
 
@@
 The MPA Namuncurá - Banco Burdwood is a shallow submarine plateau called Burdwood Bank (BB) located 150 km east of Isla de los Estados and 200 km south from Malvinas/Falkland Islands (Figure 1).
-It comprises nearly 34.000 km^2^ circumscribed by the 200 m isobath, between 54º–55ºS and 56º–62ºW, with a slight slope extended nearly 370 km east–west.
+It comprises nearly 34,000 km^2^ circumscribed by the 200 m isobath, between 54º–55ºS and 56º–62ºW, with a slight slope extended nearly 370 km east–west.
 The BB is surrounded by steep flanks of more than 3000 m depth through which strong currents circulate [@Piola1989; @Reta2014; @Matano2019].

### 2023-01-27 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Intro advance

--- 2023-01-26 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
@@
 
-Introduction to MPAs and MPA N-BB
+* Introduction to MPAs and MPA N-BB
 
-Ecological importance of MPA N-BB to the region
+The evidence of benefits provided by Marine Protected Areas (MPAs) as well as the urgent need for ocean protection have driven an unprecedented increase in the number of MPAs worldwide in recent years [@Roberts2017; @Sala2018].
+Globally, the total area of the world ocean designated under marine protection adds up to nearly 29,600,000 km^2^, distributed across nearly 18,444 MPAs and covering 8.16% of the ocean’s surface [@IUCN2023], and therefore approaching the 10% goal of the Convention of Biological Diversity [@CBD2004].
+Despite this progress, recent reports have shown that effective protection has been overestimated because it includes areas that are not yet effectively protected (only declared) as well as areas that allow significant extractive activities [@Sala2018].
 
-Trophic ecology & keystone spp knowledge of B Burdwood
+In the subAntarctic region, the level of protection is mainly associated to islands, such as South Georgia and the South Sandwich, Bouvet, Prince Edward, and Macquarie [@IUCN2023].
+Interestingly, the case of the MPA Namuncurá - Banco Burdwood I (MPA N-BB), which forms the focus of this work, is unique since it is associated to a submarine plateau [@Reta2014].
+Here it's noteworthy to mark that this MPA is part of a network of protected areas in the subAntarctic (i.e MPA Namuncurá - Banco Burdwood II and Yaganes), that contribute to protect and strengthen the functioning of this southern region to maintain global ocean health.
 
-Why using a network approach
+* Ecological importance of MPA N-BB to the region
 
-In the present work we present the first, detailed analysis of the food web for the MPA Namuncurá - Banco Burdwood ecosystem.
+Many of these MPAs centre on the presence of particularly vulnerable, keystone, or charismatic species; the presence of large numbers (or proportions) of endemic species; and the presence of high biodiversity across taxonomic levels [@Hogg2016].
+Indeed, the MPA N-BB has been created because it is considered a biodiversity hotspot, mostly of its benthic community [@Schejter2016; @Falabella2017].
+This community is characterized by a high biomass of vulnerable and fragile species (mainly Porifera and Cnidaria) that meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResources2009].
+Also, it provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge, or nursery area [@GarciaAlonso2018; @Delpiani2020; @Troccoli2020].
+The maintenance of this singular community is related to the oceanographic processes, including the circulation of the rich Malvinas (Falkland) current in the area [@Piola1989; @Guerrero1999] and the upwelling and mixing phenomena [@Matano2019].
+The input of nutrients coming from the Malvinas (Falkland) current supports the plankton community [@Guinder2020].
+Overall, at the ecosystem level the MPA N-BB is ascribed as a carbon-sinker [@Bergagna2019].
+
+* Trophic ecology & keystone spp knowledge of B Burdwood
+
+We found that BC and BB have a more pronounced WW structure compared to CA.
+We identified species at mid to low trophic positions that play a key role in the trophodynamics of each marine area (e.g.
+Fuegian sprat Sprattus fuegensis, longtail southern cod Patagonotothen ramsayi and squat lobster Munida gregaria) and considered them as the most plausible WW species.
+The identification of the most influential species within food webs has become a crucial task for conservation purposes in local and regional contexts to maintain ecosystem integrity and the supply of ecosystem services for the southwestern South Atlantic Ocean.
+[@Riccialdelli2020]
+
+* Why using a network approach
+
+Anthropogenic and climate-induced impacts are known to affect individual species, but they can also change the interactions that each species has with its prey and predators (Constable et al.
+2014, Lynam et al.
+2017).
+
+* Objective
+In the present work we present the first, detailed analysis of the food web for the MPA N-BB ecosystem.
 For this we applied a network approach to a highly-resolved food web.
@@
 
-The MPA Namuncurá - Banco Burdwood is a shallow submarine plateau called Burdwood Bank (BB) located 150 km east of Isla de los Estados and 200 km south from Malvinas/Falkland Islands (Figure 1).
-It comprises nearly 34.000 km^2^ circumscribed by the 200 m isobath, between 54º–55ºS and 56º–62ºW, with a slight slope extended nearly 370 km east–west.
+The MPA Namuncurá - Banco Burdwood I is a shallow submarine plateau called Burdwood Bank (BB) located 150 km east of Isla de los Estados and 200 km south from Malvinas/Falkland Islands (Figure 1).
+It comprises nearly 34,000 km^2^ circumscribed by the 200 m isobath, between 54º–55ºS and 56º–62ºW, with a slight slope extended nearly 370 km east–west.
 The BB is surrounded by steep flanks of more than 3000 m depth through which strong currents circulate [@Piola1989; @Reta2014; @Matano2019].

### 2023-01-27 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Continue w/ Intro

@@
 
-In the subAntarctic region, the level of protection is mainly associated to islands, such as South Georgia and the South Sandwich, Bouvet, Prince Edward, and Macquarie [@IUCN2023].
+In the subAntarctic region, the level of protection is mainly associated to oceanic islands, such as South Georgia and the South Sandwich, Bouvet, Prince Edward, and Macquarie [@IUCN2023].
 Interestingly, the case of the MPA Namuncurá - Banco Burdwood I (MPA N-BB), which forms the focus of this work, is unique since it is associated to a submarine plateau [@Reta2014].
-Here it's noteworthy to mark that this MPA is part of a network of protected areas in the subAntarctic (i.e MPA Namuncurá - Banco Burdwood II and Yaganes), that contribute to protect and strengthen the functioning of this southern region to maintain global ocean health.
+Added to this, such MPA is part of a network of protected areas in the subAntarctic (i.e joining MPAs Namuncurá - Banco Burdwood II and Yaganes), that contribute to protect and strengthen the functioning of this southern region to maintain global ocean health.
 
@@
 Indeed, the MPA N-BB has been created because it is considered a biodiversity hotspot, mostly of its benthic community [@Schejter2016; @Falabella2017].
-This community is characterized by a high biomass of vulnerable and fragile species (mainly Porifera and Cnidaria) that meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResources2009].
-Also, it provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge, or nursery area [@GarciaAlonso2018; @Delpiani2020; @Troccoli2020].
+It is characterized by a high biomass of vulnerable and fragile species (mainly Porifera and Cnidaria) that meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResources2009].
+Also, the benthic community provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge, or nursery area [@GarciaAlonso2018; @Delpiani2020; @Troccoli2020].
 The maintenance of this singular community is related to the oceanographic processes, including the circulation of the rich Malvinas (Falkland) current in the area [@Piola1989; @Guerrero1999] and the upwelling and mixing phenomena [@Matano2019].
-The input of nutrients coming from the Malvinas (Falkland) current supports the plankton community [@Guinder2020].
-Overall, at the ecosystem level the MPA N-BB is ascribed as a carbon-sinker [@Bergagna2019].
+The input of nutrients coming from the Malvinas (Falkland) current also supports a diverse plankton community [@Guinder2020].
+Overall, 811 benthic and planktonic species have been identified for the MPA N-BB ecosystem, where 349 were reported for the first time for the MPA [@APN2022].
+At the ecosystem level the MPA N-BB is ascribed as a carbon-sinker [@Bergagna2019].
 
@@
 
-We found that BC and BB have a more pronounced WW structure compared to CA.
-We identified species at mid to low trophic positions that play a key role in the trophodynamics of each marine area (e.g.
-Fuegian sprat Sprattus fuegensis, longtail southern cod Patagonotothen ramsayi and squat lobster Munida gregaria) and considered them as the most plausible WW species.
-The identification of the most influential species within food webs has become a crucial task for conservation purposes in local and regional contexts to maintain ecosystem integrity and the supply of ecosystem services for the southwestern South Atlantic Ocean.
-[@Riccialdelli2020]
+The structure and functioning of ecosystems can be successfully described by studying one of the most-frequent interactions occurring between species: the predator-prey relationship [@Bascompte2009].
+The predator-prey or trophic interactions of a particular region are commonly referred as the food web, that represents the roadmap for matter and energy flow in an ecosystem.
+The trophic structure of the southwestern South Atlantic Ocean has been proposed to be under a 'wasp-waist' control, meaning that the structure and dynamics of the ecosystem is regulated primarily by mid-trophic level species (e.g.
+fishes, crustaceans) [@Padovani2012; @Saporiti2015; @Riccialdelli2020].
+In particular, the ecosystem of the MPA N-BB shows a more pronounced 'wasp-waist' structure than other subAntarctic areas, like the Atlantic coast of Tierra del Fuego, where the Fuegian sprat *Sprattus fuegensis* and longtail southern cod *Patagonotothen ramsayi* are considered the most plausible 'wasp-waist' species [@Riccialdelli2020].
+Recently, the identification of the most influential species within food webs has become a crucial task for conservation purposes in local and regional contexts to maintain ecosystem integrity and the supply of ecosystem services for the southwestern South Atlantic Ocean [@Franco2020; @Bergagna2020; @Riccialdelli2020].
 
 * Why using a network approach
+
+In the past decades, several researches have shown that high-latitude marine ecosystems, such as the MPA N-BB, are characterised by an unexpected complexity in terms of biodiversity and ecological interactions [@Day2013; @Kortsch2019; @Cordone2020; @Trathan2021].
 
@@
 * Objective
+
 In the present work we present the first, detailed analysis of the food web for the MPA N-BB ecosystem.
@@
 
+# Acknowledgements
+
+This study was funded by Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617).
+This work is contribution no.
+XX of the MPA Namuncurá (Law 26875).
+
 # References

### 2023-01-30 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Finish Intro

@@
   - Southwest Atlantic
-journal: "MEPS, Oikos, Polar Biology (?)"
+journal: "MEPS, Oikos, Ecological Applications, J of Applied Ecology (?)"
 date: "`r Sys.Date()`"
@@
 
-* Introduction to MPAs and MPA N-BB
-
 The evidence of benefits provided by Marine Protected Areas (MPAs) as well as the urgent need for ocean protection have driven an unprecedented increase in the number of MPAs worldwide in recent years [@Roberts2017; @Sala2018].
@@
 
-* Ecological importance of MPA N-BB to the region
-
 Many of these MPAs centre on the presence of particularly vulnerable, keystone, or charismatic species; the presence of large numbers (or proportions) of endemic species; and the presence of high biodiversity across taxonomic levels [@Hogg2016].
-Indeed, the MPA N-BB has been created because it is considered a biodiversity hotspot, mostly of its benthic community [@Schejter2016; @Falabella2017].
-It is characterized by a high biomass of vulnerable and fragile species (mainly Porifera and Cnidaria) that meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResources2009].
-Also, the benthic community provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge, or nursery area [@GarciaAlonso2018; @Delpiani2020; @Troccoli2020].
+Indeed, the MPA N-BB was created because it is considered a biodiversity hotspot, mostly of its benthic community [@Schejter2016; @Falabella2017].
+This community is featured by a high biomass of vulnerable and fragile species (mainly Porifera and Cnidaria) that meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResources2009].
+Also, it provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge, or nursery area [@GarciaAlonso2018; @Delpiani2020; @Troccoli2020].
 The maintenance of this singular community is related to the oceanographic processes, including the circulation of the rich Malvinas (Falkland) current in the area [@Piola1989; @Guerrero1999] and the upwelling and mixing phenomena [@Matano2019].
 The input of nutrients coming from the Malvinas (Falkland) current also supports a diverse plankton community [@Guinder2020].
-Overall, 811 benthic and planktonic species have been identified for the MPA N-BB ecosystem, where 349 were reported for the first time for the MPA [@APN2022].
-At the ecosystem level the MPA N-BB is ascribed as a carbon-sinker [@Bergagna2019].
+Overall, 811 benthic and plankton species have been identified for the MPA N-BB ecosystem, where 349 were reported for the first time for the area [@APN2022].
 
-* Trophic ecology & keystone spp knowledge of B Burdwood
-
-The structure and functioning of ecosystems can be successfully described by studying one of the most-frequent interactions occurring between species: the predator-prey relationship [@Bascompte2009].
-The predator-prey or trophic interactions of a particular region are commonly referred as the food web, that represents the roadmap for matter and energy flow in an ecosystem.
-The trophic structure of the southwestern South Atlantic Ocean has been proposed to be under a 'wasp-waist' control, meaning that the structure and dynamics of the ecosystem is regulated primarily by mid-trophic level species (e.g.
+Recently, the identification of the most influential species has become a crucial task for conservation purposes in local and regional contexts to maintain ecosystem integrity and the supply of ecosystem services for the southwestern South Atlantic Ocean [@Franco2020; @Bergagna2020; @Riccialdelli2020].
+In this regard, the structure of the southwestern South Atlantic Ocean has been proposed to be under a 'wasp-waist' control, meaning that the structure and dynamics of the ecosystem is regulated primarily by mid-trophic level species (e.g.
 fishes, crustaceans) [@Padovani2012; @Saporiti2015; @Riccialdelli2020].
 In particular, the ecosystem of the MPA N-BB shows a more pronounced 'wasp-waist' structure than other subAntarctic areas, like the Atlantic coast of Tierra del Fuego, where the Fuegian sprat *Sprattus fuegensis* and longtail southern cod *Patagonotothen ramsayi* are considered the most plausible 'wasp-waist' species [@Riccialdelli2020].
-Recently, the identification of the most influential species within food webs has become a crucial task for conservation purposes in local and regional contexts to maintain ecosystem integrity and the supply of ecosystem services for the southwestern South Atlantic Ocean [@Franco2020; @Bergagna2020; @Riccialdelli2020].
 
-* Why using a network approach
+High-latitude marine ecosystems, such as the MPA N-BB, are characterised by an unexpected complexity in terms of biodiversity and ecological interactions [@Day2013; @Kortsch2019; @Cordone2020; @Trathan2021].
+Although there is a robust knowledge about the complexity considering the richness of the benthic and plankton communities in the MPA N-BB ecosystem [e.g.
+@Schejter2016; @Guinder2020; @APN2022], there is a need for a better understanding of species interactions' complexity and structure.
+This aspect can be tackled by analysing one of the most-frequent relationships occurring between species: the predator-prey interaction [@Bascompte2009].
+The sum of predator-prey or trophic interactions of a particular region is referred to as a food web, which represents the roadmap for matter and energy flow in an ecosystem.
+In recent years, network approaches have been successfully applied to study complex high-latitude marine ecosystems, improving our knowledge on structure, functioning, and respond to environmental/anthropogenic changes [e.g.
+@Kortsch2015; @Cordone2018; @Funes2022; @Marina2023].
+Here it is worth mentioning that anthropogenic threats have been recently reported for the MPA N-BB region [@Cossi2021; @Fioramonti2022].
 
-In the past decades, several researches have shown that high-latitude marine ecosystems, such as the MPA N-BB, are characterised by an unexpected complexity in terms of biodiversity and ecological interactions [@Day2013; @Kortsch2019; @Cordone2020; @Trathan2021].
-
-Anthropogenic and climate-induced impacts are known to affect individual species, but they can also change the interactions that each species has with its prey and predators (Constable et al.
-2014, Lynam et al.
-2017).
-
-* Objective
-
-In the present work we present the first, detailed analysis of the food web for the MPA N-BB ecosystem.
+In the present work we present the first, detailed analysis of the network of predator-prey interactions, hereafter food web, for the MPA N-BB ecosystem.
 For this we applied a network approach to a highly-resolved food web.
-The objective was twofold: characterise the food web in terms of complexity and structure, and describe the species' role in such network framework.
+The objective was twofold: characterise the food web in terms of complexity and structure, and identify the species' role in such network framework.
 
@@
 the higher the species' TL, the lower the trophic similarity or the higher the uniqueness in terms of trophic role (Figure 4C).
-Here it's noteworthy to highlight high-trophic level species with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster sp* (echinoderms), *Phalacrocorax_atriceps* and *Eudyptes chrysocome* (sea birds), and *Lagenorhynchus cruciger* and *Mesoplodon bowdoini* (marine mammals) (Table S3).
+Here it is noteworthy to highlight high-trophic level species with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster sp* (echinoderms), *Phalacrocorax_atriceps* and *Eudyptes chrysocome* (sea birds), and *Lagenorhynchus cruciger* and *Mesoplodon bowdoini* (marine mammals) (Table S3).
 
@@
 
-It's noteworthy that the highest values of betweenness were shown by species of mid-TLs (3-4), meaning that those species participated in the highest number of shortest paths between species (Figure 4A).
+It is noteworthy that the highest values of betweenness were shown by species of mid-TLs (3-4), meaning that those species participated in the highest number of shortest paths between species (Figure 4A).
 These were the species with the highest values: *Patagonotothen ramsayi*, *Dissostichus eleginoides*, *Salilota australis* (fishes), *Doryteuthis gahi* (Cephalopoda), and *Patagonotothen guntheri* (Notothenioid fish) (Table S3).
@@
 
-This study was funded by Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617).
+This study was funded by Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617), Argentina.
 This work is contribution no.

### 2023-01-30 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Start Discussion

@@
 # Use a CSL with `citation_package = "default"`
-csl: "apa-old-doi-prefix.csl"
+csl: "apa.csl"
 output: 
@@
 High-latitude marine ecosystems, such as the MPA N-BB, are characterised by an unexpected complexity in terms of biodiversity and ecological interactions [@Day2013; @Kortsch2019; @Cordone2020; @Trathan2021].
-Although there is a robust knowledge about the complexity considering the richness of the benthic and plankton communities in the MPA N-BB ecosystem [e.g.
-@Schejter2016; @Guinder2020; @APN2022], there is a need for a better understanding of species interactions' complexity and structure.
+Although there is a robust knowledge about the complexity considering the richness of the benthic and plankton communities in the MPA N-BB ecosystem [@Schejter2016; @Guinder2020; @APN2022], there is a need for a better understanding of species interactions' complexity and structure.
 This aspect can be tackled by analysing one of the most-frequent relationships occurring between species: the predator-prey interaction [@Bascompte2009].
 The sum of predator-prey or trophic interactions of a particular region is referred to as a food web, which represents the roadmap for matter and energy flow in an ecosystem.
-In recent years, network approaches have been successfully applied to study complex high-latitude marine ecosystems, improving our knowledge on structure, functioning, and respond to environmental/anthropogenic changes [e.g.
-@Kortsch2015; @Cordone2018; @Funes2022; @Marina2023].
+In recent years, network approaches have been successfully applied to study complex high-latitude marine ecosystems, improving our knowledge on structure, functioning, and respond to environmental/anthropogenic changes [@Kortsch2015; @Cordone2018; @Funes2022; @Marina2023].
 Here it is worth mentioning that anthropogenic threats have been recently reported for the MPA N-BB region [@Cossi2021; @Fioramonti2022].
@@
 
+The food web for the MPA Namuncurá - Banco Burdwood is one of the most highly-resolved networks of trophic interactions not only for high-latitude marine ecosystems but also for marine protected areas.
+It is of paramount importance to consider the complexity of species interactions in order to gain insights into the structure of the ecosystem, since the aggregation of species might mask food web properties and/or generate artifacts [@Martinez1993; @Gauzens2013].
+
+Compare network-level properties with other subpolar and polar food webs
+Complexity, connectance
+
+The structure of species interactions influences the opportunities for multiple species to persist in the long term and, therefore, their coexistence [@Godoy2018].
+The food web for the MPA N-BB ecosystem, as we showed in this study, presents an asymmetric degree (interaction) distribution.
+This is a pattern that we have identified at different levels of analysis: food web, predator, prey, and functional group.
+Such asymmetry is a well-known feature in empirical complex food webs in particular [@Dunne2002a; @Montoya2003; @Stouffer2005], and has received great attention in complex networks in general [@Albert2002; @Newman2003].
+The degree distribution pattern affects the resilience of complex food webs against random failures and intentional attacks: more-skewed distributions, like the one described in this study, are more vulnerable to the removal of the most-connected species or hubs with the potential of producing a catastrophic fragmentation of the network [@Albert2000; @Dunne2002].
+
+Considering the relevance of DD in network robustness we have considered this parameter in our analysis of food webs vulnerability to species loss.
+In particular we are interested in the intentional removal of certain species in the food web more than in the random extinction of species.
+As Dunne et al.
+(2002b) have correctly pointed out the anthropogenically caused species and population extinctions are far from being random as human have historically tended to impact higher trophic levels in the ecosystems.
+
 * The MPA Namuncurá - Banco Burdwood food web is one of the most highly-resolved networks of trophic interactions described for subpolar and polar regions.
@@
 
-* Seasonal variation in predators' diet due to food source availability.
+Seasonal variation in predators' diet due to food source availability.
+@Brose2019
 
-* Spatial variation of study area: Banco Burdwood west-east gradient.
+Spatial variation of study area: Banco Burdwood west-east gradient.
+@Kortsch2019
 
-* The lack of density or biomass data might have neglected well-known important species for the structure of the food web: *Sprattus fuegensis*.
+The lack of density or biomass data might have neglected well-known important species for the structure of the food web: *Sprattus fuegensis*.
 
@@
 
-* Estimation of interaction strength to gain insights into food web stability and response to anthropogenic and environmental perturbations.
+Estimation of interaction strength considering species and interaction traits (i.e.
+body size, body mass, dimensionality) to gain insights into food web stability and response to anthropogenic and environmental perturbations.
+@Nilsson2016; @Cirtwill2018; @Kortsch2021
 
-* Simulate perturbations on food web and target species: mercury transfer, microplastic pollution, fisheries.
+Simulate perturbations on food web and target species: mercury transfer, microplastic pollution, fisheries.
+@Cossi2021; @Fioramonti2022
 

### 2023-01-31 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Add Discussion

@@
 In the subAntarctic region, the level of protection is mainly associated to oceanic islands, such as South Georgia and the South Sandwich, Bouvet, Prince Edward, and Macquarie [@IUCN2023].
-Interestingly, the case of the MPA Namuncurá - Banco Burdwood I (MPA N-BB), which forms the focus of this work, is unique since it is associated to a submarine plateau [@Reta2014].
-Added to this, such MPA is part of a network of protected areas in the subAntarctic (i.e joining MPAs Namuncurá - Banco Burdwood II and Yaganes), that contribute to protect and strengthen the functioning of this southern region to maintain global ocean health.
+Interestingly, the case of the MPAs Namuncurá - Banco Burdwood I and II (MPA N-BB), which forms the focus of this work, is unique since they are associated to a submarine plateau and the southern adjacent deep slope region, respectively [@Falabella2017].
+Added to this, such MPAs are part of a network of protected areas in the subAntarctic (jointly with MPA Yaganes), that contributes to protect and strengthen the functioning of this southern region to maintain global ocean health.
 
 Many of these MPAs centre on the presence of particularly vulnerable, keystone, or charismatic species; the presence of large numbers (or proportions) of endemic species; and the presence of high biodiversity across taxonomic levels [@Hogg2016].
-Indeed, the MPA N-BB was created because it is considered a biodiversity hotspot, mostly of its benthic community [@Schejter2016; @Falabella2017].
-This community is featured by a high biomass of vulnerable and fragile species (mainly Porifera and Cnidaria) that meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResources2009].
+Indeed, the MPA N-BB was created to protect a sensitive and biodiverse benthic habitat that was barely known [@Schejter2016; @Falabella2017].
+The benthic community is featured by a high biomass of vulnerable and fragile species (mainly Porifera and Cnidaria) that meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResources2009].
 Also, it provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge, or nursery area [@GarciaAlonso2018; @Delpiani2020; @Troccoli2020].
@@
 fishes, crustaceans) [@Padovani2012; @Saporiti2015; @Riccialdelli2020].
-In particular, the ecosystem of the MPA N-BB shows a more pronounced 'wasp-waist' structure than other subAntarctic areas, like the Atlantic coast of Tierra del Fuego, where the Fuegian sprat *Sprattus fuegensis* and longtail southern cod *Patagonotothen ramsayi* are considered the most plausible 'wasp-waist' species [@Riccialdelli2020].
+In particular, the ecosystem of the MPA N-BB shows a more pronounced 'wasp-waist' structure than other subAntarctic areas, like the Atlantic coast of Tierra del Fuego.
+The Fuegian sprat *Sprattus fuegensis* and longtail southern cod *Patagonotothen ramsayi* are considered the most plausible 'wasp-waist' species [@Riccialdelli2020].
 
 High-latitude marine ecosystems, such as the MPA N-BB, are characterised by an unexpected complexity in terms of biodiversity and ecological interactions [@Day2013; @Kortsch2019; @Cordone2020; @Trathan2021].
-Although there is a robust knowledge about the complexity considering the richness of the benthic and plankton communities in the MPA N-BB ecosystem [@Schejter2016; @Guinder2020; @APN2022], there is a need for a better understanding of species interactions' complexity and structure.
+Although there is a robust knowledge about the complexity considering the richness of the benthic and plankton communities in the MPA N-BB ecosystem [@Schejter2016; @Guinder2020; @Schejter2020; @APN2022], there is a need for a better understanding of species interactions' complexity and structure.
 This aspect can be tackled by analysing one of the most-frequent relationships occurring between species: the predator-prey interaction [@Bascompte2009].
@@
 
-The MPA Namuncurá - Banco Burdwood I is a shallow submarine plateau called Burdwood Bank (BB) located 150 km east of Isla de los Estados and 200 km south from Malvinas/Falkland Islands (Figure 1).
-It comprises nearly 34,000 km^2^ circumscribed by the 200 m isobath, between 54º–55ºS and 56º–62ºW, with a slight slope extended nearly 370 km east–west.
-The BB is surrounded by steep flanks of more than 3000 m depth through which strong currents circulate [@Piola1989; @Reta2014; @Matano2019].
+The MPAs Namuncurá - Banco Burdwood I and II, created by National Laws 26875 and 27490, comprise a shallow submarine plateau called Burdwood Bank (BB) and a deep slope that reaches 4000 m in depth, respectively [@APN2023].
+They are located 150 km east of Isla de los Estados and 200 km south from Malvinas/Falkland Islands (Figure 1).
+The MPA Namuncurá - Banco Burdwood I comprises nearly 34,000 km^2^ circumscribed by the 200 m isobath, between 54º–55ºS and 56º–62ºW, with a slight slope extended nearly 370 km east–west.
+Physical features in the BB are fairly stable, with salinity averaging 34 all year round and temperature ranging between 4 and 8ºC overall [@Guerrero1999; @Acha2004; @Piola2009].
+The BB is surrounded by steep flanks of up to 4000 m depth through which strong currents circulate [@Piola1989; @Reta2014; @Matano2019].
+Such deep slope form the basis of the MPA Namuncurá - Banco Burdwood II that protects about 32,000 km^2^.
 Intense upwelling and mixing occur over it, entraining deep nutrient rich waters into the photic layer [@Piola2009; @Matano2019], and resulting in a fairly homogeneous water column both spatially and temporally [@Glorioso1995; @Guerrero1999; @Matano2019].
-Physical features in the MPAN-BB are fairly stable, with salinity averaging 34 all year round and temperature ranging between 4 and 8ºC overall [@Guerrero1999; @Acha2004; @Piola2009].
 
-```{r figure1, echo=FALSE, fig.width = 5, fig.height = 10, out.width = '100%', fig.cap="Map of the Marine Protected Area Namuncurá - Banco Burdwood.
-Taken from https://www.argentina.gob.ar/parquesnacionales/areasmarinas/namuncura-burdwood."}
+Given the evidence collected during several research cruises about the oceanographic and ecological processes connecting MPAs Namuncurá - Banco Burdwood I and II [references in @APN2022], a joint management plan was recently proposed [@APN2022].
+Three categories were defined according to the authorized activities: 1) Marine National Reserve (MNR), an area with the objective of conserving marine biodiversity, landscape quality and large-scale ecological processes, allowing scientific, educational, recreational uses and the sustainable use of one or more of its natural resources; 2) Marine National Park, an area with the objective of conserving marine biodiversity, landscape quality and large-scale ecological processes (MNP); and 3) Restricted Marine National Reserve (RMNR), an area of maximum permanent or temporary protection with the objective to preserve marine biodiversity and ecological processes in the long term, minimizing anthropogenic impact, and allowing scientific research and monitoring, as well as control and surveillance activities.
+Figure 1 shows the geographic location of these categories within MPAs Namuncurá - Banco Burdwood I and II.
+
+```{r figure1, echo=FALSE, fig.width = 5, fig.height = 10, out.width = '100%', fig.cap="Map of the Marine Protected Areas Namuncurá - Banco Burdwood I (MNR and MNP, northern section) and II (MNR and SMNR, southern section).
+Acronyms indicate categories according to the management plan: MNR - Marine National Reserve, MNP - Marine National Park and RMNR - Restricted Marine National Reserve."}
 # Map of MPAN-BB provided by Lu R. (?)
@@
 Furthermore, we took into account personal communications from experts belonging to the working group of the study area (https://www.pampazul.gob.ar/tag/banco-burdwood/).
-The diversity of the expertise of the authors contributing to the present study was a key factor in enhancing the quality of the network, and inherently improved the network representation of the MPA Namuncurá-Banco Burdwood ecosystem.
+The diversity of the expertise of the authors contributing to the present study was a key factor in enhancing the quality of the network, and inherently improved the network representation.
 A list of the references used to build the network is presented in Supplementary Material (Table S1).
 
-Due to a lack of trophic data resolution for some species inhabiting the MPA Namuncurá-Banco Burdwood, we followed the concept of trophic species, here defined as aggregated groups of taxa.
-In most cases we followed this when data on specific biological species were not available, but for some cases we collapsed species when taxa shared the same set of predators and prey (trophic similarity criteria).
+Due to a lack of trophic data resolution for some species inhabiting the study area, we followed the concept of trophic species, here defined as aggregated groups of taxa.
+In most cases we followed it when specific data on biological species were not available, but for some cases we collapsed species when taxa shared the same set of predators and prey (trophic similarity criterion, @Martinez1991).
 Details about this can be found in Supplementary Material (Table S2).
@@
 table1 <- add_row(table1, Name="Topological role", Definition="Species role according to interactions within and across modules (subgroups of species).", Implications="Four roles are defined: module hub, module specialist, module connector and network connector.
-Species with the same role are expected to have similar topological properties.", Reference="Guimera & Nunes Amaral 2005")
+Network connector and module connector roles maintain the connectivity of the food web.", Reference="Guimera & Nunes Amaral 2005")
 
@@
 
-The food web for the MPA Namuncurá - Banco Burdwood is one of the most highly-resolved networks of trophic interactions not only for high-latitude marine ecosystems but also for marine protected areas.
-It is of paramount importance to consider the complexity of species interactions in order to gain insights into the structure of the ecosystem, since the aggregation of species might mask food web properties and/or generate artifacts [@Martinez1993; @Gauzens2013].
+The food web for the MPA Namuncurá - Banco Burdwood, analysed in this study, is one of the most highly-resolved networks of trophic interactions not only for a high-latitude marine ecosystem but also for a marine protected area worldwide.
+It is of paramount importance to consider the complexity of species interactions in order to gain insights into the structure and functioning of the ecosystem, since the aggregation of species might mask food web properties and/or generate artifacts [@Martinez1993; @Gauzens2013].
+Connectance, a property that resumes the complexity of a food web,
 
@@
 The degree distribution pattern affects the resilience of complex food webs against random failures and intentional attacks: more-skewed distributions, like the one described in this study, are more vulnerable to the removal of the most-connected species or hubs with the potential of producing a catastrophic fragmentation of the network [@Albert2000; @Dunne2002].
+Important to attacks like anthropogenic perturbations: mercury, microplastics
+As Dunne et al.
+(2002b) have correctly pointed out the anthropogenically caused species and population extinctions are far from being random as human have historically tended to impact higher trophic levels in the ecosystems.
+
+The degree distribution allows identification of important species, such as potential keystone species [@Sole2001; @Dunne2002], generalists, and specialist species [@Kondoh2010].
 
@@
 In particular we are interested in the intentional removal of certain species in the food web more than in the random extinction of species.
-As Dunne et al.
-(2002b) have correctly pointed out the anthropogenically caused species and population extinctions are far from being random as human have historically tended to impact higher trophic levels in the ecosystems.
 
@@
 
+Incorporate habitat heterogeneity, since benthic community in the BB and deep flanks is different [@Schejter2021].
+This might lead to distinct food web properties, hence differences in ecosystem functioning and response to anthropogenic and environmental perturbations.
+@Cordone2020
+
 Estimation of interaction strength considering species and interaction traits (i.e.

### 2023-02-01 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Add small-world

@@
 Acronyms indicate categories according to the management plan: MNR - Marine National Reserve, MNP - Marine National Park and RMNR - Restricted Marine National Reserve."}
-# Map of MPAN-BB provided by Lu R. (?)
-knitr::include_graphics("MPABurdwood_map.jpeg")
+
+knitr::include_graphics("MPABurdwood_map.jpg")
 
@@
 Due to a lack of trophic data resolution for some species inhabiting the study area, we followed the concept of trophic species, here defined as aggregated groups of taxa.
-In most cases we followed it when specific data on biological species were not available, but for some cases we collapsed species when taxa shared the same set of predators and prey (trophic similarity criterion, @Martinez1991).
+In most cases we followed it when specific data on species, in the taxonomic sense, were not available.
+In some cases we collapsed species when taxa shared the same set of predators and prey (trophic similarity, @Martinez1991), one of the aggregation methods that better preserves food web functional properties [@Gauzens2013].
 Details about this can be found in Supplementary Material (Table S2).
@@
 The network-level analysis aims to characterise the network of trophic interactions in terms of complexity and structure.
-For this we calculated several network properties commonly used to describe empirical food webs [@Pascual2005]: (1) number of species S; (2) number of interactions or links L; (3) link density L/S; (4) Connectance L/S^2; (5) omnivory Omn; and (6) shortest path length SPL.
+For this we calculated several network properties commonly used to describe empirical food webs [@Pascual2005]: (1) number of species S; (2) number of interactions or links L; (3) link density L/S; (4) Connectance L/S^2; (5) omnivory Omn; and (6) small-world pattern.
+For the latter property, we calculated the characteristic path length and the clustering coefficient of the network, and we compared it to 1000 random networks generated with the same number of species and interactions [@Marina2018a].
 Also, we estimated the (7) degree distributions for the food web, for prey and predators, and for each functional group (e.g.
@@
 
-table1 <- add_row(table1, Name="Connectance", Definition="Proportion of potential links among species that are actually realized.", Implications="It measures the probability of interactions; it is a fundamental measure of network complexity.
+table1 <- add_row(table1, Name="Connectance", Definition="Proportion of potential links among species that are actually realized.
+Range = 0 - 1.", Implications="It measures the probability of interactions and is a fundamental measure of network complexity.
 Connectance can be negatively or positively associated with food web robustness, depending on the network structure (random vs non-random) or how the strength of the interactions are distributed.", Reference = "Martinez 1992")
@@
 
-table1 <- add_row(table1, Name="Shortest path length", Definition="Average shortest path length between all pairs of species.", Implications="A short path length imply a rapid spread of an impact (e.g.
-invasion, population fluctuation, local extinction) throughout the food web.", Reference="Watts & Strogatz 1998")
+table1 <- add_row(table1, Name="Small-world pattern", Definition="A network with short path length (distance between nodes) and high clustering coefficient (formation of compartments) compared to random networks.", Implications="Consequences of this structural pattern in food webs are of great importance in recognizing evolutionary paths and the vulnerability to perturbations.", Reference="Watts & Strogatz 1998, Montoya & Solé 2002")
 
@@
 Almost half of the consumers were omnivores, feeding on sources at different trophic levels.
-The food web showed a path length of 2.99, which implies that nearly three interactions are needed to connect any pair of species of the network (Table 1).
+The food web displayed a small-world pattern, meaning that the path length was lower and the clustering coefficient was higher than the random networks (Table 1).
 
@@
 
-knitr::kable(round(prop_topol,2) %>% dplyr::select(Size, Links, LD, Connectance, Omnivory, PathLength), col.names = c("Species","Interactions","Density","Connectance","Omnivory","Path length"),
-                      caption = "Network-level properties of the MPA Namuncurá - Banco Burdwood food web. See table 1 for definitions and ecological relevance.") %>% row_spec(0,bold=TRUE)
+knitr::kable(round(prop_topol,2) %>% dplyr::select(Size, Links, LD, Connectance, Omnivory, PathLength, Clustering) %>% mutate(SW = "True"), col.names = c("Species","Interactions","Density","Connectance","Omnivory","Path length", "Clustering", "SW"),
+                      caption = "Network-level properties of the MPA Namuncurá - Banco Burdwood food web.
+SW: small-world pattern.
+See table 1 for definitions and ecological relevance.") %>% row_spec(0,bold=TRUE)
 
@@
 
-## The MPA Namuncurá - Banco Burdwood food web
+## The food web of the MPA Namuncurá - Banco Burdwood ecosystem
 
-The food web for the MPA Namuncurá - Banco Burdwood, analysed in this study, is one of the most highly-resolved networks of trophic interactions not only for a high-latitude marine ecosystem but also for a marine protected area worldwide.
-It is of paramount importance to consider the complexity of species interactions in order to gain insights into the structure and functioning of the ecosystem, since the aggregation of species might mask food web properties and/or generate artifacts [@Martinez1993; @Gauzens2013].
-Connectance, a property that resumes the complexity of a food web,
+The food web of the MPA Namuncurá - Banco Burdwood ecosystem, analysed in this study, is one of the most highly-resolved networks of trophic interactions not only for a high-latitude marine ecosystem but also for a marine protected area worldwide.
+It is of paramount importance to consider the complexity of species interactions in order to gain insights into the structure and functioning of the ecosystem, since the aggregation of species might mask food web properties and/or produce type II errors (false positive) [@Martinez1993; @Gauzens2013].
 
-Compare network-level properties with other subpolar and polar food webs
-Complexity, connectance
+Food web connectance is a property that resumes the complexity of the network.
+It contains important information regarding how interactions within an ecological network are distributed, and predicts reasonably well key dynamical properties of ecological networks  also many structural [@Dunne2002a].
+More importantly, it is an emergent property of pairwise species interactions [@Poisot2014].
+Complex marine food webs (i.e.
+with more than 25 trophic species) show connectance values ranging from 0.01 - 0.27 [@Marina2018a].
+In particular, food webs from high-latitude regions tend to exhibit a connectance closer to the minimum (between 0.01 and 0.05) [@Santana2013; @Kortsch2015; @Rodriguez2022].
+Whether food webs display low or high connectance values helps to better comprehend ecosystem's synthetic properties like robustness.
+In this sense, empirical analyses support the notion that the robustness of a food web increases with connectance [@Dunne2002; @Montoya2003].
+The connectance of the food web of the MPA Namuncurá - Banco Burdwood (0.01) is one of the lowest reported so far for these regions; five times lower than that of Beagle Channel [@Rodriguez2022].
 
-The structure of species interactions influences the opportunities for multiple species to persist in the long term and, therefore, their coexistence [@Godoy2018].
-The food web for the MPA N-BB ecosystem, as we showed in this study, presents an asymmetric degree (interaction) distribution.
+The degree distribution or the distribution of number of interactions per species is the core for the structure of species interactions, which influences the opportunities for multiple species to persist in the long term and, therefore, their coexistence [@Godoy2018].
+The food web for the MPA N-BB presents an asymmetric degree (interaction) distribution.
 This is a pattern that we have identified at different levels of analysis: food web, predator, prey, and functional group.
 Such asymmetry is a well-known feature in empirical complex food webs in particular [@Dunne2002a; @Montoya2003; @Stouffer2005], and has received great attention in complex networks in general [@Albert2002; @Newman2003].
-The degree distribution pattern affects the resilience of complex food webs against random failures and intentional attacks: more-skewed distributions, like the one described in this study, are more vulnerable to the removal of the most-connected species or hubs with the potential of producing a catastrophic fragmentation of the network [@Albert2000; @Dunne2002].
-Important to attacks like anthropogenic perturbations: mercury, microplastics
-As Dunne et al.
-(2002b) have correctly pointed out the anthropogenically caused species and population extinctions are far from being random as human have historically tended to impact higher trophic levels in the ecosystems.
+The degree distribution pattern affects the resilience of complex food webs against random failures and intentional attacks: right-skewed distributions, like the one described in this study, are more vulnerable to the removal of the most-connected species or hubs with the potential of producing a catastrophic fragmentation of the network [@Albert2000; @Dunne2002].
+
+Small-world
+The path length, another network-level property we analysed, refers to the average shortest distance between pairs of species in the food web.
+A short path length implies a rapid spread of an impact (e.g.
+contaminant, population fluctuation, local extinction) throughout the network [@Williams2002].
+In comparison to complex and empirical marine food webs, the food web of the MPA Namuncurá - Banco Burdwood has a long path length (4th longest among 29 food webs) [@Marina2018a].
+
+Omnivory
+
+Low connectance, 
+Right-skewed degree distribution
+
+combined with vulnerable and fragile species and ongoing anthropogenic impacts [@Cossi2021; @Fioramonti2022], suggest potential ecosystem fragility which need to be addressed.
 

### 2023-02-01 R/4_foodwebanalysis.R
Add small-world analysis

@@ -69,6 +69,18 @@ ggplot(data = degree) +
         axis.title.x = element_text(face = "bold", size = 16),
         axis.title.y = element_text(face = "bold", size = 16))
 
+# Small-world
+rnd_g <- lapply(1:100, function (x) {
+  e <- sample_gnm(prop_topol$Size, prop_topol$Links, directed = TRUE)
+  
+  # Check that the ER networks has only one connected component
+  while(components(e)$no > 1)
+    e <- erdos.renyi.game(prop_topol$Size, prop_topol$Links, type = "gnm", 
+                          directed = TRUE)
+  return(e) 
+})
+multiweb::calc_swness_zscore(g, nullDist = rnd_g, weights = NA, ncores = 4)
+
 
 ## Escala subgrupos ----
 

### 2023-02-01 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Continue Discussion

@@
 
-Food web connectance is a property that resumes the complexity of the network.
-It contains important information regarding how interactions within an ecological network are distributed, and predicts reasonably well key dynamical properties of ecological networks  also many structural [@Dunne2002a].
-More importantly, it is an emergent property of pairwise species interactions [@Poisot2014].
+Food web connectance is a feature that resumes the complexity of the network, but more importantly it is an emergent property of pairwise species interactions [@Poisot2014].
+It contains information regarding how interactions within an ecological network are distributed, and predicts reasonably well key dynamical properties of ecological networks [@Dunne2002a].
 Complex marine food webs (i.e.
@@
 In particular, food webs from high-latitude regions tend to exhibit a connectance closer to the minimum (between 0.01 and 0.05) [@Santana2013; @Kortsch2015; @Rodriguez2022].
-Whether food webs display low or high connectance values helps to better comprehend ecosystem's synthetic properties like robustness.
+Whether food webs display a low or a high connectance helps to better comprehend ecosystem's synthetic properties like robustness.
 In this sense, empirical analyses support the notion that the robustness of a food web increases with connectance [@Dunne2002; @Montoya2003].
@@
 Such asymmetry is a well-known feature in empirical complex food webs in particular [@Dunne2002a; @Montoya2003; @Stouffer2005], and has received great attention in complex networks in general [@Albert2002; @Newman2003].
-The degree distribution pattern affects the resilience of complex food webs against random failures and intentional attacks: right-skewed distributions, like the one described in this study, are more vulnerable to the removal of the most-connected species or hubs with the potential of producing a catastrophic fragmentation of the network [@Albert2000; @Dunne2002].
+The degree distribution pattern affects the resilience of complex food webs against random failures and intentional attacks: right-skewed distributions, like the one described in this study, are more vulnerable to the removal of the most-connected species or hubs with the potential of producing secondary extinctions and a catastrophic fragmentation of the network [@Albert2000; @Dunne2002; @Eklof2006].
 
-Small-world
+The small-world pattern is a property that has implications for network functioning [@Strogatz2001].
+
 The path length, another network-level property we analysed, refers to the average shortest distance between pairs of species in the food web.

### 2023-02-02 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Continue Discussion

@@
 Recently, the identification of the most influential species has become a crucial task for conservation purposes in local and regional contexts to maintain ecosystem integrity and the supply of ecosystem services for the southwestern South Atlantic Ocean [@Franco2020; @Bergagna2020; @Riccialdelli2020].
-In this regard, the structure of the southwestern South Atlantic Ocean has been proposed to be under a 'wasp-waist' control, meaning that the structure and dynamics of the ecosystem is regulated primarily by mid-trophic level species (e.g.
-fishes, crustaceans) [@Padovani2012; @Saporiti2015; @Riccialdelli2020].
+In this regard, the structure of the southwestern South Atlantic Ocean has been proposed to be under a 'wasp-waist' control, meaning that the structure and dynamics of the ecosystem is regulated primarily by mid-trophic level species (e.g., fishes, crustaceans) [@Padovani2012; @Saporiti2015; @Riccialdelli2020].
 In particular, the ecosystem of the MPA N-BB shows a more pronounced 'wasp-waist' structure than other subAntarctic areas, like the Atlantic coast of Tierra del Fuego.
@@
 
-We analysed the MPA Namuncurá - Banco Burdwood network of trophic interactions, hereafter food web, at two levels: A) network, considering species and interactions of the whole network; and B) species, considering interactions and species related to a particular species.
+We analysed the MPA Namuncurá - Banco Burdwood network of trophic interactions, hereafter food web, at two levels: A) network, considering species and interactions of the whole network; and B) species, considering interactions and species related to a particular species (Table 1).
+
 The network-level analysis aims to characterise the network of trophic interactions in terms of complexity and structure.
 For this we calculated several network properties commonly used to describe empirical food webs [@Pascual2005]: (1) number of species S; (2) number of interactions or links L; (3) link density L/S; (4) Connectance L/S^2; (5) omnivory Omn; and (6) small-world pattern.
-For the latter property, we calculated the characteristic path length and the clustering coefficient of the network, and we compared it to 1000 random networks generated with the same number of species and interactions [@Marina2018a].
-Also, we estimated the (7) degree distributions for the food web, for prey and predators, and for each functional group (e.g.
-Amphipoda, Ascidiacea, Bivalvia, Fish, Marine mammals, Sea birds, etc.) (Table 1).
+In order to explore the small-world phenomenon we analysed the properties of interest: characteristic path length (CPL) and clustering coefficient (CC).
+The CPL is defined as the average shortest path length between all pairs of nodes [@Watts1998].
+Here, CPL was calculated as the average number of nodes in the shortest path $CPL_{Min} (i,j)$ between all pairs of nodes $S(i,j)$ in a network averaged over $S(S-1)/2$ nodes:
+
+$$
+CPL = \frac{2}{S(S-1)} \sum_{i = 1}^{S} \sum_{i = 1}^{S} {CPL_{Min}(i,j)}
+$$
+The CC quantifies the local interconnectedness of the network and it is defined as the fraction of the number of existing links between neighbours of node $i$ among all possible links between these neighbours.
+In this study, the CC was determined as the average of the individual clustering coefficients $CC_i$ of all the nodes in the network.
+Individual $CC_i$ were determined as follows:
+
+$$
+CC_i = \frac{2E_i}{K_i(K_i-1)}
+$$
+where $E_i$ is the effective number of interactions between $K_i$ nearest-neighbor nodes of node $i$ and the maximal possible number of such interactions [@Newman2003].
+With the aim of testing whether the food web presented the small-world pattern, we compared the empirical values of CPL and CC with those resulted from 1000 randomly generated networks with the same size (S) and number of interactions (L), following the method proposed by @Marina2018a.
+
+Also, we estimated the (7) degree distributions for the food web, for prey and predators, and for each functional group (e.g., Amphipoda, Ascidiacea, Bivalvia, Fish, Marine mammals, Sea birds, etc.).
 The prey and predator distributions indicate the frequency of prey among predators, and viceversa; the functional group's degree shows the distribution of interactions within groups.
+
 The species-level analysis aims to describe the species' role in the food web.
@@
 The food web presented a link density of 4.69, meaning the average number of interactions per species, and a connectance of 0.01.
-Almost half of the consumers were omnivores, feeding on sources at different trophic levels.
-The food web displayed a small-world pattern, meaning that the path length was lower and the clustering coefficient was higher than the random networks (Table 1).
+Almost half of the consumers were omnivores (0.48), feeding on sources at different trophic levels.
+The food web displayed a small-world pattern, meaning that the path length was lower and the clustering coefficient was higher than the random networks (Table 2).
 
@@
 
-knitr::kable(round(prop_topol,2) %>% dplyr::select(Size, Links, LD, Connectance, Omnivory, PathLength, Clustering) %>% mutate(SW = "True"), col.names = c("Species","Interactions","Density","Connectance","Omnivory","Path length", "Clustering", "SW"),
+knitr::kable(round(prop_topol,2) %>% dplyr::select(Size, Links, LD, Connectance, Omnivory, PathLength, Clustering) %>% mutate(SW = "True"), col.names = c("Species","Interactions","Density","Connectance","Omnivory","CPL", "CC", "SW"),
                       caption = "Network-level properties of the MPA Namuncurá - Banco Burdwood food web.
-SW: small-world pattern.
+CPL: Characteristic Path Length; CC: Clustering Coefficient; SW: Small-World pattern.
 See table 1 for definitions and ecological relevance.") %>% row_spec(0,bold=TRUE)
@@
 ```{r figure3, echo=FALSE, fig.width = 6.5, fig.height = 9, fig.align='center', fig.cap="Degree distributions for the (A) food web, for (B) prey among predators, (C) predators among prey, and (D) for each functional group.
-Groups are vertically ordered by increasing trophic level; groups with less than 3 species were not plotted (e.g.
-pelagic fish)."}
+Groups are vertically ordered by increasing trophic level; groups with less than 3 species were not plotted (e.g., pelagic fish)."}
 # Degree distributions: network, predator, prey & group
@@
 
-The food web of the MPA Namuncurá - Banco Burdwood ecosystem, analysed in this study, is one of the most highly-resolved networks of trophic interactions not only for a high-latitude marine ecosystem but also for a marine protected area worldwide.
+The food web of the MPA Namuncurá - Banco Burdwood ecosystem, analysed in this study, is one of the most highly-resolved networks of trophic interactions ever studied not only for a high-latitude marine ecosystem but also for a marine protected area worldwide.
 It is of paramount importance to consider the complexity of species interactions in order to gain insights into the structure and functioning of the ecosystem, since the aggregation of species might mask food web properties and/or produce type II errors (false positive) [@Martinez1993; @Gauzens2013].
@@
 Whether food webs display a low or a high connectance helps to better comprehend ecosystem's synthetic properties like robustness.
-In this sense, empirical analyses support the notion that the robustness of a food web increases with connectance [@Dunne2002; @Montoya2003].
+In this sense, empirical analyses support the notion that highly-connected ecological networks are robust against external perturbations such as the introduction of new (e.g., invasive) species [@Smith-Ramesh2017] as well as species removal (e.g., local extinction) [@Dunne2002; @Montoya2003].
 The connectance of the food web of the MPA Namuncurá - Banco Burdwood (0.01) is one of the lowest reported so far for these regions; five times lower than that of Beagle Channel [@Rodriguez2022].
@@
 Such asymmetry is a well-known feature in empirical complex food webs in particular [@Dunne2002a; @Montoya2003; @Stouffer2005], and has received great attention in complex networks in general [@Albert2002; @Newman2003].
-The degree distribution pattern affects the resilience of complex food webs against random failures and intentional attacks: right-skewed distributions, like the one described in this study, are more vulnerable to the removal of the most-connected species or hubs with the potential of producing secondary extinctions and a catastrophic fragmentation of the network [@Albert2000; @Dunne2002; @Eklof2006].
+The degree distribution affects the resilience of complex food webs against random failures and intentional attacks: right-skewed distributions, like the one described in this study, are more vulnerable to the removal of the most-connected species or hubs with the potential of producing secondary extinctions and a catastrophic fragmentation of the network [@Albert2000; @Dunne2002; @Eklof2006].
 
-The small-world pattern is a property that has implications for network functioning [@Strogatz2001].
+It is suggested that the small-world pattern is not frequent in complex marine food webs, mainly due to a low clustering coefficient compared to random networks [@Dunne2002b; @Marina2018a].
+However, the food web of the MPA N-BB does display a small-world pattern, characterizing a network with short path length and high clustering coefficient.
+Consequences of the small-world pattern in food webs are of great importance in recognizing evolutionary paths and the vulnerability to perturbations [@Montoya2002].
+On the one hand, a short path length implies a rapid spread of an impact (e.g., contaminant, population fluctuation, local extinction) throughout the network and, at the same time, a more potentially adaptive dynamics in face of external perturbations [@Montoya2002; @Williams2002].
+On the other hand, a high clustering coefficient indicates the formation of subnetworks composed only by the neighbors of particular species.
+This translates into a greater resistance of the network due to the confinement of perturbations mainly within subnetworks and not between them [@Kortsch2019; @Heer2020].
+Overall, a small-world topology provides ecological networks with a greater resilience and resistance [@Bornatowski2017; @Dormann2017].
 
-The path length, another network-level property we analysed, refers to the average shortest distance between pairs of species in the food web.
-A short path length implies a rapid spread of an impact (e.g.
-contaminant, population fluctuation, local extinction) throughout the network [@Williams2002].
-In comparison to complex and empirical marine food webs, the food web of the MPA Namuncurá - Banco Burdwood has a long path length (4th longest among 29 food webs) [@Marina2018a].
+Omnivory acts as a buffer to changes as the ecosystem presents alternative energy pathways in the face of perturbations; i.e., reducing the risk of cascading extinctions following primary loss of species [@Borrvall2000].
+This is based in the fact that omnivores are species able to adapt faster and at a wider range of environmental conditions by changing their foraging habits to feed on the most abundant prey [@Fagan1997].
+Furthermore, omnivory can be analysed from the interaction point of view: theoretical studies have identified omnivorous interactions as a possible candidate for a keystone interaction, sensu @Kadoya2018, highlighting the importance on stabilizing food web dynamics [@McCann1997; @Neutel2002].
+The high proportion of omnivory in the food web of the MPA N-BB suggests that the network might be robust to variations in prey abundances, which could increase food web's persistence and stability [@Stouffer2010].
 
-Omnivory
+Overall, the food web of the MPA Namuncurá - Banco Burdwood presents a combination of network properties that make it unique in terms of network resolution, complexity, and structural pattern.
+This suggests that the ecosystem might be fragile to external perturbations targeting high connected species.
+However, structural properties might provide resilience and resistance with the final outcome of a rearrange structure maintaining their functions.
 
-Low connectance, 
-Right-skewed degree distribution
+## Species' role
 
-combined with vulnerable and fragile species and ongoing anthropogenic impacts [@Cossi2021; @Fioramonti2022], suggest potential ecosystem fragility which need to be addressed.
+* The food web shows an asymmetry in the distribution of interactions at several levels: food web, functional group, prey and predators. In all of them interactions are concentrated in a few species.
 
 The degree distribution allows identification of important species, such as potential keystone species [@Sole2001; @Dunne2002], generalists, and specialist species [@Kondoh2010].
-
-Considering the relevance of DD in network robustness we have considered this parameter in our analysis of food webs vulnerability to species loss.
-In particular we are interested in the intentional removal of certain species in the food web more than in the random extinction of species.
-
-* The MPA Namuncurá - Banco Burdwood food web is one of the most highly-resolved networks of trophic interactions described for subpolar and polar regions.
-Compare network-level properties with other subpolar and polar food webs.
-
-* The food web shows an asymmetry in the distribution of interactions at several levels: food web, functional group, prey and predators. In all of them interactions are concentrated in a few species.
 On one hand, this asymmetry indicates that most consumers have a narrow diet, and few present flexible diets (*Patagonotothen guntheri*, *P.
@@
 On the other hand few prey are consumed by many predators, meaning that there are dominant food sources from which most consumers depend on: detritus, diatoms (benthic, centric, pennate), and species of *Euphausia*.
-
-## Species' role
 

### 2023-02-02 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Continue Discussion

@@
 
-* The food web shows an asymmetry in the distribution of interactions at several levels: food web, functional group, prey and predators. In all of them interactions are concentrated in a few species.
+The degree distribution, a network-level property as defined in this study, also allows to identify important species, such as potential keystone species [@Sole2001; @Dunne2002], generalists/specialist species, and dominant food sources [@Kondoh2010].
 
-The degree distribution allows identification of important species, such as potential keystone species [@Sole2001; @Dunne2002], generalists, and specialist species [@Kondoh2010].
-On one hand, this asymmetry indicates that most consumers have a narrow diet, and few present flexible diets (*Patagonotothen guntheri*, *P.
-ramsayi*, *Dissostichus eleginoides*, *Bathyraja brachyurops*, *B.
-griseocauda*).
-On the other hand few prey are consumed by many predators, meaning that there are dominant food sources from which most consumers depend on: detritus, diatoms (benthic, centric, pennate), and species of *Euphausia*.
+We have identified that the majority of the consumers in the food web of the MPA N-BB have a narrow diet or are specialists, while few present a broad diet.
+*Patagonotothen guntheri*, *P.
+ramsayi*, *Dissostichus eleginoides*, *Bathyraja brachyurops*, and *B.
+griseocauda* are the most evident generalist species, with more than 25 potential prey.
+Since these species present mid-trophic positions in the food web (3-4), acting as predator and prey, they might be important links between lower and higher trophic levels.
+This is in agreement with the sole analysis, using stable isotopes, that exists so far for the trophic structure of the MPA N-BB [@Riccialdelli2020], and resembles other high-latitude marine systems of the Southwest Atlantic and Arctic regions [@Arkhipkin2013; @Kortsch2019].
+The importance of these generalist species also arises since they feed on the benthic and pelagic habitats [@Troccoli2020; @CovattiAle2022; @Fischer2022], linking these realms and contributing to the vertical carbon flow.
+
+On the other hand, few prey are consumed by many predators, suggesting that there are dominant food sources from which most consumers depend on, and from where the ecosystem energy is being transferred to the upper trophic levels.
+Food sources identified in Riccialdelli et al. 2020, Bertola et al ?
+detritus, diatoms (benthic, centric, pennate), and species of *Euphausia*.
 

### 2023-02-03 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Continue Discussion

@@
 We found different relationships between the species trophic level (TL) and the rest of the analysed species-level properties (Figure 4A-D).
-In this regard, the most evident significant relationship was with trophic similarity, i.e.
+The most evident significant relationship was with trophic similarity, i.e.
 the higher the species' TL, the lower the trophic similarity or the higher the uniqueness in terms of trophic role (Figure 4C).
@@
 It is noteworthy that the highest values of betweenness were shown by species of mid-TLs (3-4), meaning that those species participated in the highest number of shortest paths between species (Figure 4A).
-These were the species with the highest values: *Patagonotothen ramsayi*, *Dissostichus eleginoides*, *Salilota australis* (fishes), *Doryteuthis gahi* (Cephalopoda), and *Patagonotothen guntheri* (Notothenioid fish) (Table S3).
+The following are the species with the highest values: *Patagonotothen ramsayi*, *Dissostichus eleginoides*, *Salilota australis* (fishes), *Doryteuthis gahi* (Cephalopoda), and *Patagonotothen guntheri* (Notothenioid fish) (Table S3).
 
 Taking into account the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.77); 'module hub' was constrained to mid-TL species (2.48 - 3.92); 'module connector' from low to mid-TLs (1 - 3.86); and 'network connector', the least frequent, had all of its species in TL = 1, except for one with TL = 3.47 (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework).
-Here it's important to highlight species of the two latter topological roles, because they are responsible for linking modules and maintaining the connectivity of the food web: 40 species (5 network connectors + 35 module connectors) from 20 different functional groups with a TL range = 1 - 3.86.
+Here it is important to highlight species of the two latter topological roles, because they are responsible for linking modules and maintaining the connectivity of the food web: 40 species (5 network connectors + 35 module connectors) from 20 different functional groups with a TL range = 1 - 3.86.
 
@@
 
-## Species' role
+## Dominant consumers and food sources
 
@@
 
-On the other hand, few prey are consumed by many predators, suggesting that there are dominant food sources from which most consumers depend on, and from where the ecosystem energy is being transferred to the upper trophic levels.
-Food sources identified in Riccialdelli et al. 2020, Bertola et al ?
-detritus, diatoms (benthic, centric, pennate), and species of *Euphausia*.
+On the other hand, few prey are consumed by many predators in the food web of the MPA N-BB.
+This suggests that there are dominant food sources from which most consumers depend on, and from where the ecosystem energy is being transferred to the upper trophic levels.
+The most demanded source we identified in this study (i.e.
+detritus) supports the abundant benthic community of filter-feeders [@Schejter2016].
+Furthermore, we found that the second and third-most consumed prey were diatoms and species of *Euphausia*, which are essential sources for the diverse zooplankton community on one hand [@Spinelli2020], mid-TL consumers like the Fuegian sprat *Sprattus fuegensis* [@Padovani2021] and *Patagonotothen ramsayi* [@Fischer2022], and top predators on the other hand [@RayaRey2022; @Riccialdelli2022].
 
-Our results state that certain species play particular roles in the structure of the food web.
+## Species' role related to their trophic level
 
-* Betweenness.
-Species at mid-trophic levels (3-4) lie in more shortest paths between species than any other species: ‘bridge’ role.
-Implications for spread of perturbations like mercury [@Fioramonti2022], microplastics [@Cossi2021].
+Describing species’ roles in food webs provides a toolbox with which to assess the significance of species in terms of community's functioning and overall stability [@Thebault2010; @Cirtwill2018].
+We employed a range of descriptors to characterise the dynamic and multifaceted nature of the species comprising the MPA N-BB food web.
 
-* Closeness.
-Low-trophic level species are relatively closer to other species in the food web.
-Apart from the most demanded food sources (i.e.
-detritus), which are logically closer to many species, unexpected consumers arise as important in this regard.
-Species of the zooplankton community like *Calanus* and *Euphausia* are crucial for the food web functioning, since they can affect others more quickly.
+Closeness and betweenness are defined as "meso-scale" properties because they consider direct and indirect interactions, therefore describing the focal species’ ability to influence the rest of the species of the food web [@Lai2012].
+Closeness quantifies how many steps away species $i$ is from all others in the food web, and is proportional to how rapidly the indirect effects of the focal species can spread to other species in the network [@Scotti2010].
+Low-TL consumers arise as important in this regard: species of the zooplankton community, *Calanus* and *Euphausia*, and Brachiopoda.
+Any perturbation affecting these species, such as mercury [@Fioramonti2022] and microplastics [@Cossi2021], might reach many other species in the food web.
+Otherwise, betweenness measures the number of shortest paths between species, providing information on the importance of species as “bridges” for energy transfer: a species with high betweenness takes part in more food chains and therefore affects more energy flows [@Scotti2010].
+We have identified the longtail southern cod *Patagonotothen ramsayi* as the most important species in this sense.
+Moreover, according to our analysis, other species like the Patagonian toothfish *Dissostichus eleginoides*, the Patagonian cod *Salilota australis*, the yellowfin notothen *Patagonotothen guntheri*, and the Patagonian longfin squid *Doryteuthis gahi* should be consider as relevant energy transfers for the ecosystem.
+All these species have a mid-trophic position in the food web, supporting the 'wasp-waist' control hypothesis for the MPA N-BB [@Riccialdelli2020].
 
-* Trophic similarity.
-Species are more similar at low and mid-trophic levels (2-4).
-There is a functional redundancy at these levels of the food web.
-On the other hand, less trophic similarity at high TLs indicate uniqueness in terms of trophic role.
-This highlights the importance of top predators in the sense that they play a role that cannot be played by any other species.
+Ecosystems with a pronounced 'wasp-waist' structure are suggested to present a high trophic redundancy, since a large proportion of species would show similar trophic habits [@Cury2000].
+The significant negative relationship we found between trophic similarity and trophic level enhances the hypothesis of functional redundancy at low and mid-TL species compared to higher TL species for the MPA N-BB food web [@Riccialdelli2020].
+At the same time, our results highlight the uniqueness in terms of trophic role for high-TL predators.
+Here, not only the expected pelagic animals as marine mammals and sea birds arise as relevant, but also benthic vertebrate (chondrichthyans *Bathyraja macloviana* and *Squalus acanthias*) and invertebrate species (echinoderms *Diplopteraster clarki* and *Pteraster sp*) are noteworthy.
+The role that such species play in the MPA N-BB ecosystem is unique and perturbations on them might result in unprecedented changes at the trophic structure and functioning.
+
+Species' role can be also assessed in a module-based context, where modules are defined as a group of species that interact more frequently among themselves than with species that are not members of the module [@Guimera2005].
+
+Taking into account the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.77); 'module hub' was constrained to mid-TL species (2.48 - 3.92); 'module connector' from low to mid-TLs (1 - 3.86); and 'network connector', the least frequent, had all of its species in TL = 1, except for one with TL = 3.47 (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework).
+Here it is important to highlight species of the two latter topological roles, because they are responsible for linking modules and maintaining the connectivity of the food web: 40 species (5 network connectors + 35 module connectors) from 20 different functional groups with a TL range = 1 - 3.86.
 
@@
 Spatial variation of study area: Banco Burdwood west-east gradient.
+In the oceanic BB area, complex oceanographic conditions generate an internal spatial heterogeneity, mainly along its longitudinal axis [@Matano2019], and consequently plankton communities respond with different spatial distributions [@Spinelli2020].
 @Kortsch2019
@@
 Simulate perturbations on food web and target species: mercury transfer, microplastic pollution, fisheries.
-@Cossi2021; @Fioramonti2022
+@Cossi2021; @DiMauro2022; @Fioramonti2022
 

### 2023-02-04 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Finish Discussion

@@
 For this we considered the following properties: (1) betweenness Btw; (2) closeness Cl; (3) trophic similarity TS; (4) topological role TR; and (5) trophic level TL (Table 1).
+Topological roles refers to the fact that food webs tend to naturally organize in non-random, modular patterns [@Grilli2016].
+Species can play different roles in this respect, according to the pattern of interactions they have within their own module and/or across modules.
+We computed the topological role for each species, classified as: module hub, species with a relatively high number of interactions, but most within its own module; module specialist, species with relatively few interactions and most within its own module; module connector, species with relatively few interactions mainly between modules; and network connector, species with high connectivity between and within modules [@Guimera2005].
+
 We also studied the relationship between species TL and the other species properties by performing linear regression analyses.
-Thus, we considered the TL as the dependent variable and the given property as the independent variable, and obtained the coefficients (slope and intercept) for the linear model.
+Thus, we considered the TL as the dependent variable and the given property (i.e.
+betweenness, closeness, trophic similarity) as the independent variable, and obtained the coefficients (slope and intercept) for the linear model.
 Models were fitted using the least squares approach.
@@
 Taking into account the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.77); 'module hub' was constrained to mid-TL species (2.48 - 3.92); 'module connector' from low to mid-TLs (1 - 3.86); and 'network connector', the least frequent, had all of its species in TL = 1, except for one with TL = 3.47 (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework).
-Here it is important to highlight species of the two latter topological roles, because they are responsible for linking modules and maintaining the connectivity of the food web: 40 species (5 network connectors + 35 module connectors) from 20 different functional groups with a TL range = 1 - 3.86.
+Here it is important to highlight the two latter topological roles, because they are responsible for linking modules and maintaining the connectivity of the food web: 40 species (5 network connectors + 35 module connectors) from 20 different functional groups with a TL range = 1 - 3.86.
+The following were the 5 species with a network connector role: Detritus, Diatoms (benthic, centric and pennate), and *Patagonotothen ramsayi*.
+The 35 species with a module connector role represent these functional groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Cnidaria, Cumacea, Decapoda, Detritus, Diatoms, Dinoflagellates, Echinodermata, Fish (bentho-pelagic, demersal, chondrichthyes), Foraminifera, Polychaeta, Porifera, Pycnogonida, Sea birds, and Zooplankton (see Supplementary Material Table S3 for the identity of the species).
 
@@
 Closeness quantifies how many steps away species $i$ is from all others in the food web, and is proportional to how rapidly the indirect effects of the focal species can spread to other species in the network [@Scotti2010].
-Low-TL consumers arise as important in this regard: species of the zooplankton community, *Calanus* and *Euphausia*, and Brachiopoda.
-Any perturbation affecting these species, such as mercury [@Fioramonti2022] and microplastics [@Cossi2021], might reach many other species in the food web.
+In the food web of the MPA N-BB, low-TL consumers arise as important in this regard: species of the zooplankton community, *Calanus* and *Euphausia*, and Brachiopoda.
+Any perturbation affecting these species, such as the already confirmed contaminants mercury [@Fioramonti2022] and microplastics [@Cossi2021; @DiMauro2022] for the area, should be of concern since it might reach many other species in the food web.
 Otherwise, betweenness measures the number of shortest paths between species, providing information on the importance of species as “bridges” for energy transfer: a species with high betweenness takes part in more food chains and therefore affects more energy flows [@Scotti2010].
@@
 Species' role can be also assessed in a module-based context, where modules are defined as a group of species that interact more frequently among themselves than with species that are not members of the module [@Guimera2005].
-
-Taking into account the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.77); 'module hub' was constrained to mid-TL species (2.48 - 3.92); 'module connector' from low to mid-TLs (1 - 3.86); and 'network connector', the least frequent, had all of its species in TL = 1, except for one with TL = 3.47 (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework).
-Here it is important to highlight species of the two latter topological roles, because they are responsible for linking modules and maintaining the connectivity of the food web: 40 species (5 network connectors + 35 module connectors) from 20 different functional groups with a TL range = 1 - 3.86.
-
-* Topological role.
-Low and mid-trophic level species (TL = 1 - 3.86) are responsible for maintaining the connectivity of the food web (network connector and module connector).
-The functional groups represented are: Amphipoda, Bivalvia, Bryozoa, Cnidaria, Cumacea, Decapoda, Detritus, Diatoms, Echinodermata, Fish (bentho-pelagic, demersal, chondrichthyes), Foraminifera, Polychaeta, Porifera, Zooplankton.
-This shows that the structure of the food web depends on a diversity of species, which at the end comprise the ecosystem's diversity.
-
-* Overall, low and mid-trophic level species arise as crucial in the structure of the MPA Namuncurá - Banco Burdwood food web, since they present the highest betweenness and closeness values, and the most important topological roles.
-This coincides with a recent study that suggest a wasp-waist trophic structure for the region [@Riccialdelli2020].
-However, we also suggest that there exists functional redundancy at mid-trophic levels.
-Furthermore, our study points out species of high-trophic levels due to its uniqueness role.
+Among the varying numbers of topological roles in which species can be divided, two are remarkable: 'module connector' and 'network connector'.
+Here again the longtail southern cod *Patagonotothen ramsayi* is emphasized as an influential species for the connectivity of the food web, which agrees with the suggested 'wasp-waist' control for the MPA N-BB ecosystem [@Riccialdelli2020].
+But most importantly, our analysis broadens this issue by pointing out that there are actually other species from a wide range of trophic positions (1 to 3.86), representing 20 different functional groups, that should be considered.
+Thus, we propose that it is the diversity of species (benthic and pelagic) what maintains the connectivity of the food web, therefore contributing to the trophic structure and ecosystem's stability.
 

### 2023-02-04 MS_ToSubmit/SupMaterial.Rmd
Fix NA in Table S3

--- 2023-01-25 1st_Manuscript/SupMaterial.Rmd
@@
                arrange(., desc(TotalDegree)) %>% 
-               mutate(across(where(is.numeric), round, 4)), 
+               mutate(across(where(is.numeric), round, 4),
+                      FunctionalGroup = case_when(TrophicSpecies == "Brachiopoda_spp" ~ "Brachiopoda",
+                                                  TrophicSpecies == "Campylaspis_spp" ~ "Cumacea",
+                                                  TRUE ~ FunctionalGroup)), 
              format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Group","Degree","NumPrey","NumPred","Between","Close","TL","TS","TR"), align = "llcccccccc", caption = "Species-level properties for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.

### 2023-02-06 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Finish 1st draft

@@
 In this sense, empirical analyses support the notion that highly-connected ecological networks are robust against external perturbations such as the introduction of new (e.g., invasive) species [@Smith-Ramesh2017] as well as species removal (e.g., local extinction) [@Dunne2002; @Montoya2003].
-The connectance of the food web of the MPA Namuncurá - Banco Burdwood (0.01) is one of the lowest reported so far for these regions; five times lower than that of Beagle Channel [@Rodriguez2022].
+The connectance of the food web of the MPA Namuncurá - Banco Burdwood (0.01) is one of the lowest reported so far for these regions; five times lower than that of Beagle Channel, an adjacent area [@Rodriguez2022].
 
 The degree distribution or the distribution of number of interactions per species is the core for the structure of species interactions, which influences the opportunities for multiple species to persist in the long term and, therefore, their coexistence [@Godoy2018].
-The food web for the MPA N-BB presents an asymmetric degree (interaction) distribution.
+The food web for the MPA N-BB presents an asymmetric degree distribution.
 This is a pattern that we have identified at different levels of analysis: food web, predator, prey, and functional group.
@@
 On the one hand, a short path length implies a rapid spread of an impact (e.g., contaminant, population fluctuation, local extinction) throughout the network and, at the same time, a more potentially adaptive dynamics in face of external perturbations [@Montoya2002; @Williams2002].
-On the other hand, a high clustering coefficient indicates the formation of subnetworks composed only by the neighbors of particular species.
+On the other hand, a high clustering coefficient indicates the formation of subnetworks composed only by the neighbours of particular species.
 This translates into a greater resistance of the network due to the confinement of perturbations mainly within subnetworks and not between them [@Kortsch2019; @Heer2020].
@@
 
-Overall, the food web of the MPA Namuncurá - Banco Burdwood presents a combination of network properties that make it unique in terms of network resolution, complexity, and structural pattern.
-This suggests that the ecosystem might be fragile to external perturbations targeting high connected species.
+To resume, the food web of the MPA Namuncurá - Banco Burdwood presents a combination of network properties that make it unique in terms of network resolution, complexity, and structural pattern.
+All this suggest that the ecosystem might be fragile to external perturbations targeting high connected species.
 However, structural properties might provide resilience and resistance with the final outcome of a rearrange structure maintaining their functions.
@@
 
-The degree distribution, a network-level property as defined in this study, also allows to identify important species, such as potential keystone species [@Sole2001; @Dunne2002], generalists/specialist species, and dominant food sources [@Kondoh2010].
+The degree distribution allows to identify important species, such as potential keystone species [@Sole2001; @Dunne2002], generalist/specialist species, and dominant food sources [@Kondoh2010].
 
-We have identified that the majority of the consumers in the food web of the MPA N-BB have a narrow diet or are specialists, while few present a broad diet.
-*Patagonotothen guntheri*, *P.
+We have identified that the majority of the consumers in the food web of the MPA N-BB has a narrow diet or are specialists, while few present a broad diet.
+The most evident generalist species are *Patagonotothen guntheri*, *P.
 ramsayi*, *Dissostichus eleginoides*, *Bathyraja brachyurops*, and *B.
-griseocauda* are the most evident generalist species, with more than 25 potential prey.
+griseocauda*, with more than 25 potential prey.
 Since these species present mid-trophic positions in the food web (3-4), acting as predator and prey, they might be important links between lower and higher trophic levels.
 This is in agreement with the sole analysis, using stable isotopes, that exists so far for the trophic structure of the MPA N-BB [@Riccialdelli2020], and resembles other high-latitude marine systems of the Southwest Atlantic and Arctic regions [@Arkhipkin2013; @Kortsch2019].
-The importance of these generalist species also arises since they feed on the benthic and pelagic habitats [@Troccoli2020; @CovattiAle2022; @Fischer2022], linking these realms and contributing to the vertical carbon flow.
+The importance of these particular generalist species also arises since they feed on the benthic and pelagic habitats [@Troccoli2020; @CovattiAle2022; @Fischer2022], linking these realms and contributing to the vertical carbon flow.
 
@@
 detritus) supports the abundant benthic community of filter-feeders [@Schejter2016].
-Furthermore, we found that the second and third-most consumed prey were diatoms and species of *Euphausia*, which are essential sources for the diverse zooplankton community on one hand [@Spinelli2020], mid-TL consumers like the Fuegian sprat *Sprattus fuegensis* [@Padovani2021] and *Patagonotothen ramsayi* [@Fischer2022], and top predators on the other hand [@RayaRey2022; @Riccialdelli2022].
+Furthermore, we found that the second and third-most consumed prey were diatoms and species of *Euphausia*, respectively, which are essential sources for the diverse zooplankton community [@Spinelli2020], mid-TL consumers like the Fuegian sprat *Sprattus fuegensis* [@Padovani2021] and *Patagonotothen ramsayi* [@Fischer2022], and top predators [@RayaRey2022; @Riccialdelli2022].
 
@@
 In the food web of the MPA N-BB, low-TL consumers arise as important in this regard: species of the zooplankton community, *Calanus* and *Euphausia*, and Brachiopoda.
-Any perturbation affecting these species, such as the already confirmed contaminants mercury [@Fioramonti2022] and microplastics [@Cossi2021; @DiMauro2022] for the area, should be of concern since it might reach many other species in the food web.
+Any perturbation affecting these species, such as the recently confirmed contaminants mercury [@Fioramonti2022] and microplastics [@Cossi2021; @DiMauro2022] for the area, should be of concern since it might reach many other species in the food web.
 Otherwise, betweenness measures the number of shortest paths between species, providing information on the importance of species as “bridges” for energy transfer: a species with high betweenness takes part in more food chains and therefore affects more energy flows [@Scotti2010].
 We have identified the longtail southern cod *Patagonotothen ramsayi* as the most important species in this sense.
-Moreover, according to our analysis, other species like the Patagonian toothfish *Dissostichus eleginoides*, the Patagonian cod *Salilota australis*, the yellowfin notothen *Patagonotothen guntheri*, and the Patagonian longfin squid *Doryteuthis gahi* should be consider as relevant energy transfers for the ecosystem.
+Moreover, in light of our analysis, other species like the Patagonian toothfish *Dissostichus eleginoides*, the Patagonian cod *Salilota australis*, the yellowfin notothen *Patagonotothen guntheri*, and the Patagonian longfin squid *Doryteuthis gahi* should be consider as relevant energy transfers for the ecosystem.
 All these species have a mid-trophic position in the food web, supporting the 'wasp-waist' control hypothesis for the MPA N-BB [@Riccialdelli2020].
@@
 At the same time, our results highlight the uniqueness in terms of trophic role for high-TL predators.
-Here, not only the expected pelagic animals as marine mammals and sea birds arise as relevant, but also benthic vertebrate (chondrichthyans *Bathyraja macloviana* and *Squalus acanthias*) and invertebrate species (echinoderms *Diplopteraster clarki* and *Pteraster sp*) are noteworthy.
+Here, not only the expected pelagic animals such as marine mammals and sea birds arise as relevant, but also benthic vertebrate (chondrichthyans *Bathyraja macloviana* and *Squalus acanthias*) and invertebrate species (echinoderms *Diplopteraster clarki* and *Pteraster sp*) are noteworthy.
 The role that such species play in the MPA N-BB ecosystem is unique and perturbations on them might result in unprecedented changes at the trophic structure and functioning.
@@
 Here again the longtail southern cod *Patagonotothen ramsayi* is emphasized as an influential species for the connectivity of the food web, which agrees with the suggested 'wasp-waist' control for the MPA N-BB ecosystem [@Riccialdelli2020].
-But most importantly, our analysis broadens this issue by pointing out that there are actually other species from a wide range of trophic positions (1 to 3.86), representing 20 different functional groups, that should be considered.
+But most importantly, our results broadens this issue by pointing out that there are other species, belonging to a wide range of trophic positions (1 to 3.86) and representing 20 different functional groups, that should be considered.
 Thus, we propose that it is the diversity of species (benthic and pelagic) what maintains the connectivity of the food web, therefore contributing to the trophic structure and ecosystem's stability.
 
-## Caveats and future perspectives
+<!-- ## Caveats and future perspectives -->
 
-Caveats:
+<!-- Caveats: -->
 
-Seasonal variation in predators' diet due to food source availability.
-@Brose2019
+<!-- Seasonal variation in predators' diet due to food source availability. -->
+<!-- @Brose2019 -->
 
-Spatial variation of study area: Banco Burdwood west-east gradient.
-In the oceanic BB area, complex oceanographic conditions generate an internal spatial heterogeneity, mainly along its longitudinal axis [@Matano2019], and consequently plankton communities respond with different spatial distributions [@Spinelli2020].
-@Kortsch2019
+<!-- Spatial variation of study area: Banco Burdwood west-east gradient. -->
+<!-- In the oceanic BB area, complex oceanographic conditions generate an internal spatial heterogeneity, mainly along its longitudinal axis [@Matano2019], and consequently plankton communities respond with different spatial distributions [@Spinelli2020].
+-->
+<!-- @Kortsch2019 -->
 
-The lack of density or biomass data might have neglected well-known important species for the structure of the food web: *Sprattus fuegensis*.
+<!-- Perspectives: -->
 
-Perspectives:
+<!-- Incorporate habitat heterogeneity, since benthic community in the BB and deep flanks is different [@Schejter2021].
+This might lead to distinct food web properties, hence differences in ecosystem functioning and response to anthropogenic and environmental perturbations.
+-->
+<!-- @Cordone2020 -->
 
-Incorporate habitat heterogeneity, since benthic community in the BB and deep flanks is different [@Schejter2021].
-This might lead to distinct food web properties, hence differences in ecosystem functioning and response to anthropogenic and environmental perturbations.
-@Cordone2020
+<!-- Simulate perturbations on food web and target species: mercury transfer, microplastic pollution, fisheries. -->
+<!-- @Cossi2021; @DiMauro2022; @Fioramonti2022 -->
 
-Estimation of interaction strength considering species and interaction traits (i.e.
+<!-- Estimation of interaction strength considering species and interaction traits (i.e.
 body size, body mass, dimensionality) to gain insights into food web stability and response to anthropogenic and environmental perturbations.
-@Nilsson2016; @Cirtwill2018; @Kortsch2021
-
-Simulate perturbations on food web and target species: mercury transfer, microplastic pollution, fisheries.
-@Cossi2021; @DiMauro2022; @Fioramonti2022
+-->
+<!-- @Nilsson2016; @Cirtwill2018; @Kortsch2021 -->
 
@@
 
+We compiled information on the species and trophic diversity of the Marine Protected Area Namuncurá - Banco Burdwood, generating an unprecedented well-resolved network of trophic interactions for a subAntarctic ecosystem.
+Particular properties at the network level might reflect ecosystem's vulnerability to perturbations of highly-connected species, with a rearrange structure maintaining their functions due to its potential resilience and resistance.
+
+We identified several species as important in terms of different aspects of trophic structure and functioning, and response to perturbations (i.e.
+environmental/anthropogenic changes).
+On one hand, we suggest that generalist species, mostly fishes, play a crucial role in the ecosystem's bentho-pelagic coupling process.
+At the same time, we propose that other species rather than the longtail southern cod *Patagonotothen ramsayi* and the Fueguian sprat *Sprattus fuegensis* should be consider as relevant energy transfers for the ecosystem.
+Finally, we argue that it is the diversity of species, representing the benthic and pelagic habitats, what maintains the connectivity of the food web against perturbations, therefore contributing to the structure and stability of the ecosystem.
+
 # Acknowledgements
 
+We are indebted to all those experts of the working group 'Banco Burdwood / Área Protegida Namuncurá' who humbly provided their knowledge to enhance the quality of the present research.
 This study was funded by Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617), Argentina.

### 2023-03-28 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Add LS & IR minor comments

@@
   - name: Luciana Riccialdelli^a^
+  - name: To be continued(?)^c^
 address:
@@
     address: Instituto Antartico Argentino (IAA), Argentina
+  - code: 3
+    address: INIDEP, UBA-CONICET, IIMyC-CONICET, MACN-CONICET, UNC-CONICET
 abstract: |
@@
 Globally, the total area of the world ocean designated under marine protection adds up to nearly 29,600,000 km^2^, distributed across nearly 18,444 MPAs and covering 8.16% of the ocean’s surface [@IUCN2023], and therefore approaching the 10% goal of the Convention of Biological Diversity [@CBD2004].
-Despite this progress, recent reports have shown that effective protection has been overestimated because it includes areas that are not yet effectively protected (only declared) as well as areas that allow significant extractive activities [@Sala2018].
+Despite this progress, recent reports have shown that actual protection has been overestimated because it includes areas that are not yet effectively protected (only declared) as well as areas that allow significant extractive activities [@Sala2018].
 
-In the subAntarctic region, the level of protection is mainly associated to oceanic islands, such as South Georgia and the South Sandwich, Bouvet, Prince Edward, and Macquarie [@IUCN2023].
-Interestingly, the case of the MPAs Namuncurá - Banco Burdwood I and II (MPA N-BB), which forms the focus of this work, is unique since they are associated to a submarine plateau and the southern adjacent deep slope region, respectively [@Falabella2017].
-Added to this, such MPAs are part of a network of protected areas in the subAntarctic (jointly with MPA Yaganes), that contributes to protect and strengthen the functioning of this southern region to maintain global ocean health.
+In the sub-Antarctic region, the level of ocean protection is mainly associated to oceanic islands, such as the South Georgia and South Sandwich, Bouvet, Prince Edward, and Macquarie islands [@IUCN2023].
+Interestingly, the case of the MPAs Namuncurá - Banco Burdwood I and II (MPA N-BB), which is the focus of this work, is unique since these MPAs are associated to a submarine plateau and its southern adjacent deep slope region, respectively [@Falabella2017].
+Added to this, such MPAs are part of a network of protected areas in the sub-Antarctic (jointly with MPA Yaganes), that aims to protect and strengthen the functioning of this southern region to maintain global ocean health.
 
-Many of these MPAs centre on the presence of particularly vulnerable, keystone, or charismatic species; the presence of large numbers (or proportions) of endemic species; and the presence of high biodiversity across taxonomic levels [@Hogg2016].
+Many of these MPAs focus on the presence of particularly vulnerable, keystone, or charismatic species, the presence of large numbers (or proportions) of endemic species, and/or the presence of high biodiversity across taxonomic levels [@Hogg2016].
 Indeed, the MPA N-BB was created to protect a sensitive and biodiverse benthic habitat that was barely known [@Schejter2016; @Falabella2017].
-The benthic community is featured by a high biomass of vulnerable and fragile species (mainly Porifera and Cnidaria) that meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResources2009].
-Also, it provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge, or nursery area [@GarciaAlonso2018; @Delpiani2020; @Troccoli2020].
-The maintenance of this singular community is related to the oceanographic processes, including the circulation of the rich Malvinas (Falkland) current in the area [@Piola1989; @Guerrero1999] and the upwelling and mixing phenomena [@Matano2019].
+The benthic community is featured by a high biomass of vulnerable and fragile species (mainly Poriferaand Cnidaria) that meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResources2009].
+Also, it provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge and nursery area [@GarciaAlonso2018; @Delpiani2020; @Troccoli2020].
+The maintenance of this singular community is related to local and regional oceanographic processes, including the circulation of the rich Malvinas (Falkland) current in the area [@Piola1989; @Guerrero1999] and the upwelling and mixing phenomena [@Matano2019].
 The input of nutrients coming from the Malvinas (Falkland) current also supports a diverse plankton community [@Guinder2020].
 Overall, 811 benthic and plankton species have been identified for the MPA N-BB ecosystem, where 349 were reported for the first time for the area [@APN2022].
+However, identifying the main species for maintenance of ecosystem services and health as well as for management and conservation is essential.
 
-Recently, the identification of the most influential species has become a crucial task for conservation purposes in local and regional contexts to maintain ecosystem integrity and the supply of ecosystem services for the southwestern South Atlantic Ocean [@Franco2020; @Bergagna2020; @Riccialdelli2020].
-In this regard, the structure of the southwestern South Atlantic Ocean has been proposed to be under a 'wasp-waist' control, meaning that the structure and dynamics of the ecosystem is regulated primarily by mid-trophic level species (e.g., fishes, crustaceans) [@Padovani2012; @Saporiti2015; @Riccialdelli2020].
-In particular, the ecosystem of the MPA N-BB shows a more pronounced 'wasp-waist' structure than other subAntarctic areas, like the Atlantic coast of Tierra del Fuego.
+Recently, the structure of the southwestern South Atlantic Ocean has been proposed to be under a 'wasp-waist' control, meaning that the structure and dynamics of the ecosystem is regulated primarily by mid-trophic level species (e.g., fishes, crustaceans) [@Padovani2012; @Saporiti2015; @Riccialdelli2020].
+In particular, the ecosystem of the MPA N-BB shows a more pronounced 'wasp-waist' structure than other sub-Antarctic areas, such as the Atlantic coast of Tierra del Fuego.
 The Fuegian sprat *Sprattus fuegensis* and longtail southern cod *Patagonotothen ramsayi* are considered the most plausible 'wasp-waist' species [@Riccialdelli2020].
 
-High-latitude marine ecosystems, such as the MPA N-BB, are characterised by an unexpected complexity in terms of biodiversity and ecological interactions [@Day2013; @Kortsch2019; @Cordone2020; @Trathan2021].
+High-latitude marine ecosystems, such as the MPA N-BB, are characterized by an unexpected complexity in terms of biodiversity and ecological interactions [@Day2013; @Kortsch2019; @Cordone2020; @Trathan2021].
 Although there is a robust knowledge about the complexity considering the richness of the benthic and plankton communities in the MPA N-BB ecosystem [@Schejter2016; @Guinder2020; @Schejter2020; @APN2022], there is a need for a better understanding of species interactions' complexity and structure.
-This aspect can be tackled by analysing one of the most-frequent relationships occurring between species: the predator-prey interaction [@Bascompte2009].
+This aspect can be tackled by analyzing one of the most-frequent relationships occurring between species: the predator-prey interaction [@Bascompte2009].
 The sum of predator-prey or trophic interactions of a particular region is referred to as a food web, which represents the roadmap for matter and energy flow in an ecosystem.
-In recent years, network approaches have been successfully applied to study complex high-latitude marine ecosystems, improving our knowledge on structure, functioning, and respond to environmental/anthropogenic changes [@Kortsch2015; @Cordone2018; @Funes2022; @Marina2023].
-Here it is worth mentioning that anthropogenic threats have been recently reported for the MPA N-BB region [@Cossi2021; @Fioramonti2022].
+In recent years, network approaches have been successfully applied to study complex high-latitude marine ecosystems, improving our knowledge on structure, functioning, and response to environmental/anthropogenic changes [@Kortsch2015; @Cordone2018; @Funes2022; @Marina2023].
+Among anthropogenic threats, it is worth mentioning that contaminants like mercury and microplastics have been recently reported as important threats for the MPA N-BB region [@Cossi2021; @DiMauro2022; @Fioramonti2022].
 
-In the present work we present the first, detailed analysis of the network of predator-prey interactions, hereafter food web, for the MPA N-BB ecosystem.
-For this we applied a network approach to a highly-resolved food web.
-The objective was twofold: characterise the food web in terms of complexity and structure, and identify the species' role in such network framework.
+In the present work, we present the first, detailed analysis of the network of predator-prey interactions, hereafter food web, for the MPA N-BB ecosystem.
+For this, we applied a network approach to a highly resolved food web.
+The objective was twofold: characterize the food web in terms of complexity and structure, and identify the species' role in such network framework.
 
@@
 
-The MPAs Namuncurá - Banco Burdwood I and II, created by National Laws 26875 and 27490, comprise a shallow submarine plateau called Burdwood Bank (BB) and a deep slope that reaches 4000 m in depth, respectively [@APN2023].
-They are located 150 km east of Isla de los Estados and 200 km south from Malvinas/Falkland Islands (Figure 1).
-The MPA Namuncurá - Banco Burdwood I comprises nearly 34,000 km^2^ circumscribed by the 200 m isobath, between 54º–55ºS and 56º–62ºW, with a slight slope extended nearly 370 km east–west.
-Physical features in the BB are fairly stable, with salinity averaging 34 all year round and temperature ranging between 4 and 8ºC overall [@Guerrero1999; @Acha2004; @Piola2009].
+The MPAs Namuncurá - Banco Burdwood I and II, created by National Laws 26.875 and 27.490, comprise a shallow submarine plateau called Burdwood Bank (BB) and a deep slope that reaches 4000 m in depth, N-BB I and N-BB II, respectively [@APN2023].
+They are located 150 km east of isla de los Estados and 200 km south from Malvinas/Falkland Islands (Figure 1).
+The MPA N-BB I comprises nearly 34,000 km^2^ circumscribed by the 200 m isobath, between 54º–55ºS and 56º–62ºW, with a slight slope extended nearly 370 km east–west.
+Physical features in the BB are fairly stable, with salinity averaging 34 all year round and temperature ranging between 4 and 8ºC [@Guerrero1999; @Acha2004; @Piola2009].
 The BB is surrounded by steep flanks of up to 4000 m depth through which strong currents circulate [@Piola1989; @Reta2014; @Matano2019].
-Such deep slope form the basis of the MPA Namuncurá - Banco Burdwood II that protects about 32,000 km^2^.
-Intense upwelling and mixing occur over it, entraining deep nutrient rich waters into the photic layer [@Piola2009; @Matano2019], and resulting in a fairly homogeneous water column both spatially and temporally [@Glorioso1995; @Guerrero1999; @Matano2019].
+Such deep slope form the basis of N-BB II that protects about 32,000 km^2^.
+Intense upwelling and mixing occur over it, entraining deep nutrient-rich waters into the photic layer [@Piola2009; @Matano2019], and resulting in a fairly homogeneous water column both spatially and temporally [@Glorioso1995; @Guerrero1999; @Matano2019].
 
-Given the evidence collected during several research cruises about the oceanographic and ecological processes connecting MPAs Namuncurá - Banco Burdwood I and II [references in @APN2022], a joint management plan was recently proposed [@APN2022].
-Three categories were defined according to the authorized activities: 1) Marine National Reserve (MNR), an area with the objective of conserving marine biodiversity, landscape quality and large-scale ecological processes, allowing scientific, educational, recreational uses and the sustainable use of one or more of its natural resources; 2) Marine National Park, an area with the objective of conserving marine biodiversity, landscape quality and large-scale ecological processes (MNP); and 3) Restricted Marine National Reserve (RMNR), an area of maximum permanent or temporary protection with the objective to preserve marine biodiversity and ecological processes in the long term, minimizing anthropogenic impact, and allowing scientific research and monitoring, as well as control and surveillance activities.
-Figure 1 shows the geographic location of these categories within MPAs Namuncurá - Banco Burdwood I and II.
+Given the evidence collected during several research cruises about the oceanographic and ecological processes connecting MPAs N-BB I and II [references in @APN2022], a joint management plan was recently proposed [@APN2022].
 
-```{r figure1, echo=FALSE, fig.width = 5, fig.height = 10, out.width = '100%', fig.cap="Map of the Marine Protected Areas Namuncurá - Banco Burdwood I (MNR and MNP, northern section) and II (MNR and SMNR, southern section).
+```{r figure1, echo=FALSE, fig.width = 5, fig.height = 10, out.width = '100%', fig.cap="Marine Protected Areas Namuncurá - Banco Burdwood I (MNR and MNP, northern section) and II (MNR and SMNR, southern section).
 Acronyms indicate categories according to the management plan: MNR - Marine National Reserve, MNP - Marine National Park and RMNR - Restricted Marine National Reserve."}
@@
 Due to a lack of trophic data resolution for some species inhabiting the study area, we followed the concept of trophic species, here defined as aggregated groups of taxa.
-In most cases we followed it when specific data on species, in the taxonomic sense, were not available.
-In some cases we collapsed species when taxa shared the same set of predators and prey (trophic similarity, @Martinez1991), one of the aggregation methods that better preserves food web functional properties [@Gauzens2013].
+In most cases, we followed it when specific data on species, in the taxonomic sense, were not available.
+In some cases, we collapsed species when taxa shared the same set of predators and prey (trophic similarity, @Martinez1991), one of the aggregation methods that better preserves food web functional properties [@Gauzens2013].
 Details about this can be found in Supplementary Material (Table S2).
 
-With the gathered trophic data we constructed an interaction matrix of pairwise interactions; a value of 1 or 0 was assigned to each element a_ij of the matrix depending on whether the j-species preyed or not on the i-species.
+With the gathered trophic data we constructed a matrix of pairwise interactions; a value of 1 or 0 was assigned to each element a_ij of the matrix depending on whether the j-species preyed or not on the i-species.
 Then we transformed such matrix into an oriented graph with L trophic interactions between S nodes or species.
@@
 
-We analysed the MPA Namuncurá - Banco Burdwood network of trophic interactions, hereafter food web, at two levels: A) network, considering species and interactions of the whole network; and B) species, considering interactions and species related to a particular species (Table 1).
+We analyzed the MPA N-BB network of trophic interactions, or food web, at two levels: A) network, considering species and interactions of the whole network; and B) species, considering interactions and species related to a particular species (Table 1).
 
-The network-level analysis aims to characterise the network of trophic interactions in terms of complexity and structure.
-For this we calculated several network properties commonly used to describe empirical food webs [@Pascual2005]: (1) number of species S; (2) number of interactions or links L; (3) link density L/S; (4) Connectance L/S^2; (5) omnivory Omn; and (6) small-world pattern.
-In order to explore the small-world phenomenon we analysed the properties of interest: characteristic path length (CPL) and clustering coefficient (CC).
+The network-level analysis aims to characterizee the food web in terms of complexity and structure.
+For this we calculated several network properties commonly used to describe empirical food webs [@Pascual2005]: (1) number of species S; (2) number of interactions or links L; (3) link density L/S; (4) connectance L/S^2; (5) omnivory Omn; and (6) small-world pattern.
+In order to explore the small-world phenomenon we analyzed the  characteristic path length (CPL) and the clustering coefficient (CC).
 The CPL is defined as the average shortest path length between all pairs of nodes [@Watts1998].
@@
 where $E_i$ is the effective number of interactions between $K_i$ nearest-neighbor nodes of node $i$ and the maximal possible number of such interactions [@Newman2003].
-With the aim of testing whether the food web presented the small-world pattern, we compared the empirical values of CPL and CC with those resulted from 1000 randomly generated networks with the same size (S) and number of interactions (L), following the method proposed by @Marina2018a.
+With the aim of testing whether the food web presented the small-world pattern, we compared the empirical values of CPL and CC with those resulting from 1000 randomly generated networks with the same size (S) and number of interactions (L), following the method proposed by @Marina2018a.
 
@@
 The species-level analysis aims to describe the species' role in the food web.
-For this we considered the following properties: (1) betweenness Btw; (2) closeness Cl; (3) trophic similarity TS; (4) topological role TR; and (5) trophic level TL (Table 1).
-Topological roles refers to the fact that food webs tend to naturally organize in non-random, modular patterns [@Grilli2016].
+For this, we considered the following properties: (1) betweenness Btw; (2) closeness Cl; (3) trophic similarity TS; (4) topological role TR; and (5) trophic level TL (Table 1).
+Topological roles refers to the fact that food webs tend to naturally organize in non-random, modular patterns, where modules are defined as a group of species that interact more frequently among themselves than with species that are not members of the module [@Guimera2005].
 Species can play different roles in this respect, according to the pattern of interactions they have within their own module and/or across modules.
@@
 
-In terms of complexity, the MPA Namuncurá - Banco Burdwood food web consisted of 1778 predator-prey interactions and 379 species, where 93% of them were defined at the species taxonomical level (Figure 2, Table S2).
-The food web presented a link density of 4.69, meaning the average number of interactions per species, and a connectance of 0.01.
+In terms of complexity, the MPA Namuncurá - Banco Burdwood food web (N-BB I and II) consisted of 1778 predator-prey interactions and 379 species, where 93% of them were defined at the species taxonomical level (Figure 2, Table S2).
+The food web presented a link density (e.g., the average number of interactions per species) of 4.69, and a connectance of 0.01.
 Almost half of the consumers were omnivores (0.48), feeding on sources at different trophic levels.
-The food web displayed a small-world pattern, meaning that the path length was lower and the clustering coefficient was higher than the random networks (Table 2).
+The food web displayed a small-world pattern, meaning that the path length was lower and the clustering coefficient higher than the random networks (Table 2).
 
@@
 Circle diameter is relative to the number of interactions.
-Colour gradient indicate the trophic level."}
+Colour gradient indicates the trophic level."}
 # Food web graph
@@
 
-The majority of the species of the food web were consumers, 336 out of 379; the rest were primary producers, such as diatoms (phytoplankton), and non-living food sources like detritus and necromass.
+The majority of the species in the food web were consumers, 336 out of 379; the rest were primary producers, such as diatoms (phytoplankton), and non-living food sources like detritus and necromass.
 
@@
 the higher the species' TL, the lower the trophic similarity or the higher the uniqueness in terms of trophic role (Figure 4C).
-Here it is noteworthy to highlight high-trophic level species with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster sp* (echinoderms), *Phalacrocorax_atriceps* and *Eudyptes chrysocome* (sea birds), and *Lagenorhynchus cruciger* and *Mesoplodon bowdoini* (marine mammals) (Table S3).
+Here it is noteworthy to highlight those high-trophic level species with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster sp* (echinoderms), *Phalacrocorax_atriceps* and *Eudyptes chrysocome* (sea birds), and *Lagenorhynchus cruciger* and *Mesoplodon bowdoini* (marine mammals) (Table S3).
 
-We also found a negative significant relationship with closeness, however less evident, meaning that low-TL species are relatively closer to any other species in the food web (Figure 4B).
+We also found a negative significant relationship between TL and closeness, however less evident, meaning that low-TL species are relatively closer to any other species in the food web (Figure 4B).
 Species of genera *Calanus* and *Euphausia*, and species of Brachiopoda, all of them with TL < 3, registered the highest values of closeness (Table S3).
@@
 
-Taking into account the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.77); 'module hub' was constrained to mid-TL species (2.48 - 3.92); 'module connector' from low to mid-TLs (1 - 3.86); and 'network connector', the least frequent, had all of its species in TL = 1, except for one with TL = 3.47 (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework).
+Considering the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.77); 'module hub' was constrained to mid-TL species (2.48 - 3.92); 'module connector' from low to mid-TLs (1 - 3.86); and 'network connector', the least frequent, had all of its species in TL = 1, except for one with TL = 3.47 (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework).
 Here it is important to highlight the two latter topological roles, because they are responsible for linking modules and maintaining the connectivity of the food web: 40 species (5 network connectors + 35 module connectors) from 20 different functional groups with a TL range = 1 - 3.86.
-The following were the 5 species with a network connector role: Detritus, Diatoms (benthic, centric and pennate), and *Patagonotothen ramsayi*.
+The following were the five species with a network connector role: Detritus, Diatoms (benthic, centric and pennate), and *Patagonotothen ramsayi*.
 The 35 species with a module connector role represent these functional groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Cnidaria, Cumacea, Decapoda, Detritus, Diatoms, Dinoflagellates, Echinodermata, Fish (bentho-pelagic, demersal, chondrichthyes), Foraminifera, Polychaeta, Porifera, Pycnogonida, Sea birds, and Zooplankton (see Supplementary Material Table S3 for the identity of the species).
@@
 
-The food web of the MPA Namuncurá - Banco Burdwood ecosystem, analysed in this study, is one of the most highly-resolved networks of trophic interactions ever studied not only for a high-latitude marine ecosystem but also for a marine protected area worldwide.
+The food web of the MPA Namuncurá - Banco Burdwood ecosystem analysed in this study is one of the most highly-resolved networks of trophic interactions ever studied not only for a high-latitude marine ecosystem but also for a marine protected area worldwide.
 It is of paramount importance to consider the complexity of species interactions in order to gain insights into the structure and functioning of the ecosystem, since the aggregation of species might mask food web properties and/or produce type II errors (false positive) [@Martinez1993; @Gauzens2013].
 
-Food web connectance is a feature that resumes the complexity of the network, but more importantly it is an emergent property of pairwise species interactions [@Poisot2014].
+Food web connectance is a feature that resumes the complexity of the network, but more importantly, it is an emergent property of pairwise species interactions [@Poisot2014].
 It contains information regarding how interactions within an ecological network are distributed, and predicts reasonably well key dynamical properties of ecological networks [@Dunne2002a].
@@
 In this sense, empirical analyses support the notion that highly-connected ecological networks are robust against external perturbations such as the introduction of new (e.g., invasive) species [@Smith-Ramesh2017] as well as species removal (e.g., local extinction) [@Dunne2002; @Montoya2003].
-The connectance of the food web of the MPA Namuncurá - Banco Burdwood (0.01) is one of the lowest reported so far for these regions; five times lower than that of Beagle Channel, an adjacent area [@Rodriguez2022].
+The connectance of the food web of the MPA Namuncurá - Banco Burdwood (0.01) is one of the lowest reported so far for these regions; in particular, it appears to be five times lower than that of Beagle Channel, an adjacent area [@Rodriguez2022].
 
@@
 The food web for the MPA N-BB presents an asymmetric degree distribution.
-This is a pattern that we have identified at different levels of analysis: food web, predator, prey, and functional group.
+This pattern was identified at different levels of analysis: food web, predator, prey, and functional group.
 Such asymmetry is a well-known feature in empirical complex food webs in particular [@Dunne2002a; @Montoya2003; @Stouffer2005], and has received great attention in complex networks in general [@Albert2002; @Newman2003].
-The degree distribution affects the resilience of complex food webs against random failures and intentional attacks: right-skewed distributions, like the one described in this study, are more vulnerable to the removal of the most-connected species or hubs with the potential of producing secondary extinctions and a catastrophic fragmentation of the network [@Albert2000; @Dunne2002; @Eklof2006].
+The degree distribution affects the resilience of complex food webs against random failures and intentional attacks: food webs showing right-skewed distributions, like the one described in this study, are more vulnerable to the removal of the most connected species or hubs, with the potential of producing secondary extinctions and a catastrophic fragmentation of the network [@Albert2000; @Dunne2002; @Eklof2006].
 
-It is suggested that the small-world pattern is not frequent in complex marine food webs, mainly due to a low clustering coefficient compared to random networks [@Dunne2002b; @Marina2018a].
-However, the food web of the MPA N-BB does display a small-world pattern, characterizing a network with short path length and high clustering coefficient.
-Consequences of the small-world pattern in food webs are of great importance in recognizing evolutionary paths and the vulnerability to perturbations [@Montoya2002].
+It is suggested that the small-world pattern, i.e., a network with short path length and high clustering coefficient is not frequent in complex marine food webs, mainly due to a low clustering coefficient compared to random networks [@Dunne2002b; @Marina2018a].
+However, the food web of the MPA N-BB does display a small-world pattern.
+Consequences of this could be of great importance in recognizing evolutionary paths and the vulnerability to perturbations [@Montoya2002].
 On the one hand, a short path length implies a rapid spread of an impact (e.g., contaminant, population fluctuation, local extinction) throughout the network and, at the same time, a more potentially adaptive dynamics in face of external perturbations [@Montoya2002; @Williams2002].
 On the other hand, a high clustering coefficient indicates the formation of subnetworks composed only by the neighbours of particular species.
-This translates into a greater resistance of the network due to the confinement of perturbations mainly within subnetworks and not between them [@Kortsch2019; @Heer2020].
+This translates into a greater resistance of the network due to the confinement of perturbations mainly within subnetworks and not spreading between them [@Kortsch2019; @Heer2020].
 Overall, a small-world topology provides ecological networks with a greater resilience and resistance [@Bornatowski2017; @Dormann2017].
@@
 Omnivory acts as a buffer to changes as the ecosystem presents alternative energy pathways in the face of perturbations; i.e., reducing the risk of cascading extinctions following primary loss of species [@Borrvall2000].
-This is based in the fact that omnivores are species able to adapt faster and at a wider range of environmental conditions by changing their foraging habits to feed on the most abundant prey [@Fagan1997].
-Furthermore, omnivory can be analysed from the interaction point of view: theoretical studies have identified omnivorous interactions as a possible candidate for a keystone interaction, sensu @Kadoya2018, highlighting the importance on stabilizing food web dynamics [@McCann1997; @Neutel2002].
+This is based on the fact that omnivores are species able to adapt faster and to a wider range of environmental conditions by changing their foraging habits to feed on the most abundant prey [@Fagan1997].
+Furthermore, omnivory can be analysed from the interaction point of view: theoretical studies have identified omnivorous interactions as a possible candidate for a keystone interaction, sensu @Kadoya2018, highlighting the importance of omnivory inn stabilizing food web dynamics [@McCann1997; @Neutel2002].
 The high proportion of omnivory in the food web of the MPA N-BB suggests that the network might be robust to variations in prey abundances, which could increase food web's persistence and stability [@Stouffer2010].
@@
 To resume, the food web of the MPA Namuncurá - Banco Burdwood presents a combination of network properties that make it unique in terms of network resolution, complexity, and structural pattern.
-All this suggest that the ecosystem might be fragile to external perturbations targeting high connected species.
+All this suggest that the ecosystem might be fragile to external perturbations targeting highly connected species.
 However, structural properties might provide resilience and resistance with the final outcome of a rearrange structure maintaining their functions.
@@
 
-We have identified that the majority of the consumers in the food web of the MPA N-BB has a narrow diet or are specialists, while few present a broad diet.
+We have identified that the majority of the consumers in the food web of the MPA N-BB either has a narrow diet or are specialists, while few present a broad diet.
 The most evident generalist species are *Patagonotothen guntheri*, *P.
@@
 Describing species’ roles in food webs provides a toolbox with which to assess the significance of species in terms of community's functioning and overall stability [@Thebault2010; @Cirtwill2018].
-We employed a range of descriptors to characterise the dynamic and multifaceted nature of the species comprising the MPA N-BB food web.
+We used a range of descriptors to characterise the dynamic and multifaceted nature of the species forming the MPA N-BB food web.
 
 Closeness and betweenness are defined as "meso-scale" properties because they consider direct and indirect interactions, therefore describing the focal species’ ability to influence the rest of the species of the food web [@Lai2012].
-Closeness quantifies how many steps away species $i$ is from all others in the food web, and is proportional to how rapidly the indirect effects of the focal species can spread to other species in the network [@Scotti2010].
+Closeness quantifies how many steps away species $i$ is from all other species in the food web, and is proportional to how rapidly the indirect effects of the focal species can spread to other species in the network [@Scotti2010].
 In the food web of the MPA N-BB, low-TL consumers arise as important in this regard: species of the zooplankton community, *Calanus* and *Euphausia*, and Brachiopoda.
@@
 We have identified the longtail southern cod *Patagonotothen ramsayi* as the most important species in this sense.
-Moreover, in light of our analysis, other species like the Patagonian toothfish *Dissostichus eleginoides*, the Patagonian cod *Salilota australis*, the yellowfin notothen *Patagonotothen guntheri*, and the Patagonian longfin squid *Doryteuthis gahi* should be consider as relevant energy transfers for the ecosystem.
+Moreover, in light of our analysis, other species like the Patagonian toothfish *Dissostichus eleginoides*, the Patagonian cod *Salilota australis*, the yellowfin notothen *Patagonotothen guntheri*, and the Patagonian longfin squid *Doryteuthis gahi* should be considered as relevant in the energy transfer in the ecosystem.
 All these species have a mid-trophic position in the food web, supporting the 'wasp-waist' control hypothesis for the MPA N-BB [@Riccialdelli2020].
@@
 Here, not only the expected pelagic animals such as marine mammals and sea birds arise as relevant, but also benthic vertebrate (chondrichthyans *Bathyraja macloviana* and *Squalus acanthias*) and invertebrate species (echinoderms *Diplopteraster clarki* and *Pteraster sp*) are noteworthy.
-The role that such species play in the MPA N-BB ecosystem is unique and perturbations on them might result in unprecedented changes at the trophic structure and functioning.
+The role that such species play in the MPA N-BB ecosystem is unique and perturbations on them might result in unprecedented changes at the trophic structure and functioning level.
 
-Species' role can be also assessed in a module-based context, where modules are defined as a group of species that interact more frequently among themselves than with species that are not members of the module [@Guimera2005].
+Species' role can be also assessed in a module-based context.
 Among the varying numbers of topological roles in which species can be divided, two are remarkable: 'module connector' and 'network connector'.
@@
 
-<!-- ## Caveats and future perspectives -->
+## Caveats and future perspectives
 
-<!-- Caveats: -->
+In construction...
 
-<!-- Seasonal variation in predators' diet due to food source availability. -->
-<!-- @Brose2019 -->
+Caveats:
 
-<!-- Spatial variation of study area: Banco Burdwood west-east gradient. -->
-<!-- In the oceanic BB area, complex oceanographic conditions generate an internal spatial heterogeneity, mainly along its longitudinal axis [@Matano2019], and consequently plankton communities respond with different spatial distributions [@Spinelli2020].
--->
-<!-- @Kortsch2019 -->
+Seasonal variation in predators' diet due to food source availability.
+@Brose2019
 
-<!-- Perspectives: -->
+Spatial variation of study area: Banco Burdwood west-east gradient.
+In the oceanic BB area, complex oceanographic conditions generate an internal spatial heterogeneity, mainly along its longitudinal axis [@Matano2019], and consequently plankton communities respond with different spatial distributions [@Spinelli2020].
+@Kortsch2019
 
-<!-- Incorporate habitat heterogeneity, since benthic community in the BB and deep flanks is different [@Schejter2021].
+Perspectives:
+
+Incorporate habitat heterogeneity, since benthic community in the BB and deep flanks is different [@Schejter2021].
 This might lead to distinct food web properties, hence differences in ecosystem functioning and response to anthropogenic and environmental perturbations.
--->
-<!-- @Cordone2020 -->
+@Cordone2020
 
-<!-- Simulate perturbations on food web and target species: mercury transfer, microplastic pollution, fisheries. -->
-<!-- @Cossi2021; @DiMauro2022; @Fioramonti2022 -->
+Simulate perturbations on food web and target species: mercury transfer, microplastic pollution, fisheries.
+@Cossi2021; @DiMauro2022; @Fioramonti2022
 
-<!-- Estimation of interaction strength considering species and interaction traits (i.e.
-body size, body mass, dimensionality) to gain insights into food web stability and response to anthropogenic and environmental perturbations.
--->
-<!-- @Nilsson2016; @Cirtwill2018; @Kortsch2021 -->
+Estimation of interaction strength considering species and interaction traits (i.e.
+body size, body mass, interaction dimensionality) to gain insights into food web stability and response to anthropogenic and environmental perturbations.
+@Nilsson2016; @Cirtwill2018; @Kortsch2021
 
@@
 
-We compiled information on the species and trophic diversity of the Marine Protected Area Namuncurá - Banco Burdwood, generating an unprecedented well-resolved network of trophic interactions for a subAntarctic ecosystem.
-Particular properties at the network level might reflect ecosystem's vulnerability to perturbations of highly-connected species, with a rearrange structure maintaining their functions due to its potential resilience and resistance.
+We compiled information on the species and trophic diversity of the Marine Protected Area Namuncurá - Banco Burdwood, generating an unprecedented, well-resolved network of trophic interactions for a sub-Antarctic ecosystem, identifying the complexity and structure of the system, and the main species role in a network framework.
+Particular properties at the network level allowed us to identify ecosystem's vulnerability and potential response to perturbations in the presence of highly-connected species, with a rearrange structure maintaining their functions due to its potential resilience and resistance.
 
@@
 On one hand, we suggest that generalist species, mostly fishes, play a crucial role in the ecosystem's bentho-pelagic coupling process.
-At the same time, we propose that other species rather than the longtail southern cod *Patagonotothen ramsayi* and the Fueguian sprat *Sprattus fuegensis* should be consider as relevant energy transfers for the ecosystem.
+At the same time, we propose that other species rather than the longtail southern cod *Patagonotothen ramsayi* and the Fueguian sprat *Sprattus fuegensis* should be considered as relevant energy transfers for the ecosystem.
 Finally, we argue that it is the diversity of species, representing the benthic and pelagic habitats, what maintains the connectivity of the food web against perturbations, therefore contributing to the structure and stability of the ecosystem.
@@
 
-We are indebted to all those experts of the working group 'Banco Burdwood / Área Protegida Namuncurá' who humbly provided their knowledge to enhance the quality of the present research.
+We are indebted to all those experts of the working group 'Banco Burdwood' who humbly provided their knowledge to enhance the quality of the present research (add names if necessary), and special thanks to GA Lovrich the Scientific Coordinator of the MPA Namuncurá-Burdwood Bank and the MPA N-BB Administrators.
 This study was funded by Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617), Argentina.
 This work is contribution no.
-XX of the MPA Namuncurá (Law 26875).
+XX of the MPA Namuncurá (Law 26.875).
 

### 2023-03-28 MS_ToSubmit/MS_Burdwood_foodweb.tex
Add LS & IR minor comments

@@
 
-  \journal{MEPS, Oikos, Polar Biology (?)} % Sets Journal name
+  \journal{MEPS, Oikos, Ecological Applications, J of Applied Ecology
+(?)} % Sets Journal name
 
@@
 
+    \author[]{To be continued(?)\textsuperscript{c}%
+  %
+  }
+
       \affiliation[1]{Centro Austral de Investigaciones Cientificas
@@
     \affiliation[2]{Instituto Antartico Argentino (IAA), Argentina}
+    \affiliation[3]{INIDEP, UBA-CONICET, IIMyC-CONICET, MACN-CONICET,
+UNC-CONICET}
     \cortext[cor1]{Corresponding author}
@@
 
-Introduction to MPAs and MPA N-BB
-
-Ecological importance of MPA N-BB to the region
-
-Trophic ecology \& keystone spp knowledge of B Burdwood
-
-Why using a network approach
-
-In the present work we present the first, detailed analysis of the food
-web for the MPA Namuncurá - Banco Burdwood ecosystem. For this we
-applied a network approach to a highly-resolved food web. The objective
-was twofold: characterise the food web in terms of complexity and
-structure, and describe the species' role in such network framework.
+The evidence of benefits provided by Marine Protected Areas (MPAs) as
+well as the urgent need for ocean protection have driven an
+unprecedented increase in the number of MPAs worldwide in recent years
+(Roberts et al., 2017; Sala et al., 2018). Globally, the total area of
+the world ocean designated under marine protection adds up to nearly
+29,600,000 km\textsuperscript{2}, distributed across nearly 18,444 MPAs
+and covering 8.16\% of the ocean's surface (IUCN \& UNEP-WCMC, 2023),
+and therefore approaching the 10\% goal of the Convention of Biological
+Diversity (CBD, 2004). Despite this progress, recent reports have shown
+that actual protection has been overestimated because it includes areas
+that are not yet effectively protected (only declared) as well as areas
+that allow significant extractive activities (Sala et al., 2018).
+
+In the sub-Antarctic region, the level of ocean protection is mainly
+associated to oceanic islands, such as the South Georgia and South
+Sandwich, Bouvet, Prince Edward, and Macquarie islands (IUCN \&
+UNEP-WCMC, 2023). Interestingly, the case of the MPAs Namuncurá - Banco
+Burdwood I and II (MPA N-BB), which is the focus of this work, is unique
+since these MPAs are associated to a submarine plateau and its southern
+adjacent deep slope region, respectively (Falabella, 2017). Added to
+this, such MPAs are part of a network of protected areas in the
+sub-Antarctic (jointly with MPA Yaganes), that aims to protect and
+strengthen the functioning of this southern region to maintain global
+ocean health.
+
+Many of these MPAs focus on the presence of particularly vulnerable,
+keystone, or charismatic species, the presence of large numbers (or
+proportions) of endemic species, and/or the presence of high
+biodiversity across taxonomic levels (Hogg et al., 2016). Indeed, the
+MPA N-BB was created to protect a sensitive and biodiverse benthic
+habitat that was barely known (Falabella, 2017; L. Schejter et al.,
+2016). The benthic community is featured by a high biomass of vulnerable
+and fragile species (mainly Poriferaand Cnidaria) that meet the
+characteristics of vulnerable marine ecosystems (Schejter \& Albano,
+2021), here defined as sites that present taxa with a minimum biomass of
+10 kg per 1200 m\textsuperscript{2} (Commission for the Conservation of
+Antarctic Marine Living Resources, 2009). Also, it provides habitat to
+several small-sized species (López-Gappa et al., 2018; L. Schejter \&
+Bremec, 2019; Sirito, 2019), and has an important role in the life
+history of fishes as a food source, refuge and nursery area (Delpiani et
+al., 2020; García Alonso et al., 2018; Troccoli et al., 2020). The
+maintenance of this singular community is related to local and regional
+oceanographic processes, including the circulation of the rich Malvinas
+(Falkland) current in the area (Guerrero et al., 1999; A. R. Piola \&
+Gordon, 1989) and the upwelling and mixing phenomena (Matano et al.,
+2019). The input of nutrients coming from the Malvinas (Falkland)
+current also supports a diverse plankton community (Guinder et al.,
+2020). Overall, 811 benthic and plankton species have been identified
+for the MPA N-BB ecosystem, where 349 were reported for the first time
+for the area (APN, 2022). However, identifying the main species for
+maintenance of ecosystem services and health as well as for management
+and conservation is essential.
+
+Recently, the structure of the southwestern South Atlantic Ocean has
+been proposed to be under a `wasp-waist' control, meaning that the
+structure and dynamics of the ecosystem is regulated primarily by
+mid-trophic level species (e.g., fishes, crustaceans) (Padovani et al.,
+2012; Riccialdelli et al., 2020; Saporiti et al., 2015). In particular,
+the ecosystem of the MPA N-BB shows a more pronounced `wasp-waist'
+structure than other sub-Antarctic areas, such as the Atlantic coast of
+Tierra del Fuego. The Fuegian sprat \emph{Sprattus fuegensis} and
+longtail southern cod \emph{Patagonotothen ramsayi} are considered the
+most plausible `wasp-waist' species (Riccialdelli et al., 2020).
+
+High-latitude marine ecosystems, such as the MPA N-BB, are characterized
+by an unexpected complexity in terms of biodiversity and ecological
+interactions (Cordone et al., 2020; Day et al., 2013; Kortsch et al.,
+2019; Trathan et al., 2021). Although there is a robust knowledge about
+the complexity considering the richness of the benthic and plankton
+communities in the MPA N-BB ecosystem (APN, 2022; Guinder et al., 2020;
+L. Schejter et al., 2016, 2020), there is a need for a better
+understanding of species interactions' complexity and structure. This
+aspect can be tackled by analyzing one of the most-frequent
+relationships occurring between species: the predator-prey interaction
+(Bascompte, 2009). The sum of predator-prey or trophic interactions of a
+particular region is referred to as a food web, which represents the
+roadmap for matter and energy flow in an ecosystem. In recent years,
+network approaches have been successfully applied to study complex
+high-latitude marine ecosystems, improving our knowledge on structure,
+functioning, and response to environmental/anthropogenic changes
+(Cordone et al., 2018; Funes et al., 2022; Kortsch et al., 2015; Marina
+et al., 2023). Among anthropogenic threats, it is worth mentioning that
+contaminants like mercury and microplastics have been recently reported
+as important threats for the MPA N-BB region (Cossi et al., 2021; Di
+Mauro et al., 2022; Fioramonti et al., 2022).
+
+In the present work, we present the first, detailed analysis of the
+network of predator-prey interactions, hereafter food web, for the MPA
+N-BB ecosystem. For this, we applied a network approach to a highly
+resolved food web. The objective was twofold: characterize the food web
+in terms of complexity and structure, and identify the species' role in
+such network framework.
 
@@
 
-The MPA Namuncurá - Banco Burdwood is a shallow submarine plateau called
-Burdwood Bank (BB) located 150 km east of Isla de los Estados and 200 km
-south from Malvinas/Falkland Islands (Figure 1). It comprises nearly
-34.000 km\textsuperscript{2} circumscribed by the 200 m isobath, between
-54º--55ºS and 56º--62ºW, with a slight slope extended nearly 370 km
-east--west. The BB is surrounded by steep flanks of more than 3000 m
-depth through which strong currents circulate (Matano, Palma, \& Combes,
-2019; A. R. Piola \& Gordon, 1989; Reta, 2014). Intense upwelling and
-mixing occur over it, entraining deep nutrient rich waters into the
-photic layer (Matano et al., 2019; A. Piola \& Falabella, 2009), and
-resulting in a fairly homogeneous water column both spatially and
-temporally (Glorioso \& Flather, 1995; Guerrero, Baldoni, \& Benavides,
-1999; Matano et al., 2019). Physical features in the MPAN-BB are fairly
-stable, with salinity averaging 34 all year round and temperature
-ranging between 4 and 8ºC overall (Acha, Mianzan, Guerrero, Favero, \&
-Bava, 2004; Guerrero et al., 1999; A. Piola \& Falabella, 2009).
+The MPAs Namuncurá - Banco Burdwood I and II, created by National Laws
+26.875 and 27.490, comprise a shallow submarine plateau called Burdwood
+Bank (BB) and a deep slope that reaches 4000 m in depth, N-BB I and N-BB
+II, respectively (APN, 2023). They are located 150 km east of isla de
+los Estados and 200 km south from Malvinas/Falkland Islands (Figure 1).
+The MPA N-BB I comprises nearly 34,000 km\textsuperscript{2}
+circumscribed by the 200 m isobath, between 54º--55ºS and 56º--62ºW,
+with a slight slope extended nearly 370 km east--west. Physical features
+in the BB are fairly stable, with salinity averaging 34 all year round
+and temperature ranging between 4 and 8ºC (Acha et al., 2004; Guerrero
+et al., 1999; A. Piola \& Falabella, 2009). The BB is surrounded by
+steep flanks of up to 4000 m depth through which strong currents
+circulate (Matano et al., 2019; A. R. Piola \& Gordon, 1989; Reta,
+2014). Such deep slope form the basis of N-BB II that protects about
+32,000 km\textsuperscript{2}. Intense upwelling and mixing occur over
+it, entraining deep nutrient-rich waters into the photic layer (Matano
+et al., 2019; A. Piola \& Falabella, 2009), and resulting in a fairly
+homogeneous water column both spatially and temporally (Glorioso \&
+Flather, 1995; Guerrero et al., 1999; Matano et al., 2019).
+
+Given the evidence collected during several research cruises about the
+oceanographic and ecological processes connecting MPAs N-BB I and II
+(references in APN, 2022), a joint management plan was recently proposed
+(APN, 2022).
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{MPABurdwood_map} \caption{Map of the Marine Protected Area Namuncurá - Banco Burdwood.
-Taken from https://www.argentina.gob.ar/parquesnacionales/areasmarinas/namuncura-burdwood.}\label{fig:figure1}
+\includegraphics[width=1\linewidth]{MPABurdwood_map} \caption{Marine Protected Areas Namuncurá - Banco Burdwood I (MNR and MNP, northern section) and II (MNR and SMNR, southern section).
+Acronyms indicate categories according to the management plan: MNR - Marine National Reserve, MNP - Marine National Park and RMNR - Restricted Marine National Reserve.}\label{fig:figure1}
 \end{figure}
@@
 factor in enhancing the quality of the network, and inherently improved
-the network representation of the MPA Namuncurá-Banco Burdwood
-ecosystem. A list of the references used to build the network is
-presented in Supplementary Material (Table S1).
+the network representation. A list of the references used to build the
+network is presented in Supplementary Material (Table S1).
 
 Due to a lack of trophic data resolution for some species inhabiting the
-MPA Namuncurá-Banco Burdwood, we followed the concept of trophic
-species, here defined as aggregated groups of taxa. In most cases we
-followed this when data on specific biological species were not
-available, but for some cases we collapsed species when taxa shared the
-same set of predators and prey (trophic similarity criteria). Details
-about this can be found in Supplementary Material (Table S2).
-
-With the gathered trophic data we constructed an interaction matrix of
-pairwise interactions; a value of 1 or 0 was assigned to each element
-a\_ij of the matrix depending on whether the j-species preyed or not on
-the i-species. Then we transformed such matrix into an oriented graph
-with L trophic interactions between S nodes or species. The orientation
-or direction of the graph follows the flow of energy and matter in the
+study area, we followed the concept of trophic species, here defined as
+aggregated groups of taxa. In most cases, we followed it when specific
+data on species, in the taxonomic sense, were not available. In some
+cases, we collapsed species when taxa shared the same set of predators
+and prey (trophic similarity, Martinez (1991)), one of the aggregation
+methods that better preserves food web functional properties (Gauzens et
+al., 2013). Details about this can be found in Supplementary Material
+(Table S2).
+
+With the gathered trophic data we constructed a matrix of pairwise
+interactions; a value of 1 or 0 was assigned to each element a\_ij of
+the matrix depending on whether the j-species preyed or not on the
+i-species. Then we transformed such matrix into an oriented graph with L
+trophic interactions between S nodes or species. The orientation or
+direction of the graph follows the flow of energy and matter in the
 network, from prey to predator.
@@
 
-We analysed the MPA Namuncurá - Banco Burdwood network of trophic
-interactions, hereafter food web, at two levels: 1) network, considering
-species and interactions of the whole network; and 2) species,
-considering interactions and species related to a particular species.
-The network-level analysis aims to characterize the network of trophic
-interactions in terms of complexity and structure. For this we
-calculated several network properties commonly used to describe
-empirical food webs (Pascual \& Dunne, 2005): (1) number of species S;
-(2) number of interactions or links L; (3) link density L/S; (4)
-Connectance L/S\^{}2; (5) omnivory Omn; and (6) shortest path length
-SPL. Also, we estimated the (7) degree distributions for the food web,
-for prey and predators, and for each functional group (e.g.~Amphipoda,
-Ascidiacea, Bivalvia, Fish, Marine mammals, Sea birds, etc.) (Table 1).
-The prey and predator distributions indicate the frequency of prey among
+We analyzed the MPA N-BB network of trophic interactions, or food web,
+at two levels: A) network, considering species and interactions of the
+whole network; and B) species, considering interactions and species
+related to a particular species (Table 1).
+
+The network-level analysis aims to characterizee the food web in terms
+of complexity and structure. For this we calculated several network
+properties commonly used to describe empirical food webs (Pascual \&
+Dunne, 2005): (1) number of species S; (2) number of interactions or
+links L; (3) link density L/S; (4) connectance L/S\^{}2; (5) omnivory
+Omn; and (6) small-world pattern. In order to explore the small-world
+phenomenon we analyzed the characteristic path length (CPL) and the
+clustering coefficient (CC). The CPL is defined as the average shortest
+path length between all pairs of nodes (Watts \& Strogatz, 1998). Here,
+CPL was calculated as the average number of nodes in the shortest path
+\(CPL_{Min} (i,j)\) between all pairs of nodes \(S(i,j)\) in a network
+averaged over \(S(S-1)/2\) nodes:
+
+\[
+CPL = \frac{2}{S(S-1)} \sum_{i = 1}^{S} \sum_{i = 1}^{S} {CPL_{Min}(i,j)}
+\] The CC quantifies the local interconnectedness of the network and it
+is defined as the fraction of the number of existing links between
+neighbours of node \(i\) among all possible links between these
+neighbours. In this study, the CC was determined as the average of the
+individual clustering coefficients \(CC_i\) of all the nodes in the
+network. Individual \(CC_i\) were determined as follows:
+
+\[
+CC_i = \frac{2E_i}{K_i(K_i-1)}
+\] where \(E_i\) is the effective number of interactions between \(K_i\)
+nearest-neighbor nodes of node \(i\) and the maximal possible number of
+such interactions (Newman, 2003). With the aim of testing whether the
+food web presented the small-world pattern, we compared the empirical
+values of CPL and CC with those resulting from 1000 randomly generated
+networks with the same size (S) and number of interactions (L),
+following the method proposed by Marina et al. (2018).
+
+Also, we estimated the (7) degree distributions for the food web, for
+prey and predators, and for each functional group (e.g., Amphipoda,
+Ascidiacea, Bivalvia, Fish, Marine mammals, Sea birds, etc.). The prey
+and predator distributions indicate the frequency of prey among
 predators, and viceversa; the functional group's degree shows the
-distribution of interactions within groups. The species-level analysis
-aims to describe the species' role in the food web. For this we
-considered the following properties: (1) betweenness Btw; (2) closeness
-Cl; (3) trophic similarity TS; (4) topological role TR; and (5) trophic
-level TL (Table 1). We also studied the relationship between species
-trophic level and the other species properties by performing linear
-regression analyses. Thus, we considered the IS as the dependent
-variable and the given unweighted property as the independent variable,
-and obtained the coefficients (slope and intercept) for the linear
-model. Models were fitted using the least squares approach. We also
-explored the mean IS distribution with the species habitat. These
-properties provide a general appropriate description of species' role in
-empirical complex food webs (Cirtwill et al., 2018).
+distribution of interactions within groups.
+
+The species-level analysis aims to describe the species' role in the
+food web. For this, we considered the following properties: (1)
+betweenness Btw; (2) closeness Cl; (3) trophic similarity TS; (4)
+topological role TR; and (5) trophic level TL (Table 1). Topological
+roles refers to the fact that food webs tend to naturally organize in
+non-random, modular patterns, where modules are defined as a group of
+species that interact more frequently among themselves than with species
+that are not members of the module (Guimerà \& Nunes Amaral, 2005).
+Species can play different roles in this respect, according to the
+pattern of interactions they have within their own module and/or across
+modules. We computed the topological role for each species, classified
+as: module hub, species with a relatively high number of interactions,
+but most within its own module; module specialist, species with
+relatively few interactions and most within its own module; module
+connector, species with relatively few interactions mainly between
+modules; and network connector, species with high connectivity between
+and within modules (Guimerà \& Nunes Amaral, 2005).
+
+We also studied the relationship between species TL and the other
+species properties by performing linear regression analyses. Thus, we
+considered the TL as the dependent variable and the given property
+(i.e.~betweenness, closeness, trophic similarity) as the independent
+variable, and obtained the coefficients (slope and intercept) for the
+linear model. Models were fitted using the least squares approach. We
+also explored the topological role categories with the species TL. These
+species-level properties provide a general appropriate description of
+species' role in empirical complex food webs (Cirtwill et al., 2018).
 
@@
 \textbf{Connectance} & Proportion of potential links among species that
-are actually realized. & It measures the probability of interactions; it
-is a fundamental measure of network complexity. Connectance can be
-negatively or positively associated with food web robustness, depending
-on the network structure (random vs non-random) or how the strength of
-the interactions are distributed. & Martinez 1992 \\
+are actually realized. Range = 0 - 1. & It measures the probability of
+interactions and is a fundamental measure of network complexity.
+Connectance can be negatively or positively associated with food web
+robustness, depending on the network structure (random vs non-random) or
+how the strength of the interactions are distributed. & Martinez 1992 \\
 \textbf{Degree distribution} & Frequency of trophic species that have k
@@
 the probability of trophic cascades. & McCann \& Hastings 1997 \\
-\textbf{Shortest path length} & Average shortest path length between all
-pairs of species. & A short path length imply a rapid spread of an
-impact (e.g.~invasion, population fluctuation, local extinction)
-throughout the food web. & Watts \& Strogatz 1998 \\
+\textbf{Small-world pattern} & A network with short path length
+(distance between nodes) and high clustering coefficient (formation of
+compartments) compared to random networks. & Consequences of this
+structural pattern in food webs are of great importance in recognizing
+evolutionary paths and the vulnerability to perturbations. & Watts \&
+Strogatz 1998, Montoya \& Solé 2002 \\
 \textbf{Betweenness} & Number of shortest paths going through a species.
@@
 defined: module hub, module specialist, module connector and network
-connector. Species with the same role are expected to have similar
-topological properties. & Guimera \& Nunes Amaral 2005 \\
+connector. Network connector and module connector roles maintain the
+connectivity of the food web. & Guimera \& Nunes Amaral 2005 \\
 \bottomrule()
@@
 In terms of complexity, the MPA Namuncurá - Banco Burdwood food web
-consisted of 1778 predator-prey interactions and 379 species, where 93\%
-of them were defined at the species taxonomical level (Figure 2, Table
-S2). The food web presented a link density of 4.69, meaning the average
-number of interactions per species, and a connectance of 0.01. Almost
-half of the consumers were omnivores, feeding on sources at different
-trophic levels. The food web showed a path length of 2.99, which implies
-that nearly three interactions are needed to connect any pair of species
-of the network (Table 1).
+(N-BB I and II) consisted of 1778 predator-prey interactions and 379
+species, where 93\% of them were defined at the species taxonomical
+level (Figure 2, Table S2). The food web presented a link density (e.g.,
+the average number of interactions per species) of 4.69, and a
+connectance of 0.01. Almost half of the consumers were omnivores (0.48),
+feeding on sources at different trophic levels. The food web displayed a
+small-world pattern, meaning that the path length was lower and the
+clustering coefficient higher than the random networks (Table 2).
 
@@
 Circle diameter is relative to the number of interactions.
-Colour gradient indicate the trophic level.}\label{fig:figure2}
+Colour gradient indicates the trophic level.}\label{fig:figure2}
 \end{figure}
@@
 
-\caption{\label{tab:table2}Network-level properties of the MPA Namuncurá - Banco Burdwood food web. See table 1 for definitions and ecological relevance.}
+\caption{\label{tab:table2}Network-level properties of the MPA Namuncurá - Banco Burdwood food web.
+CPL: Characteristic Path Length; CC: Clustering Coefficient; SW: Small-World pattern.
+See table 1 for definitions and ecological relevance.}
 \centering
-\begin{tabular}[t]{r|r|r|r|r|r}
+\begin{tabular}[t]{r|r|r|r|r|r|r|l}
 \hline
-\textbf{Species} & \textbf{Interactions} & \textbf{Density} & \textbf{Connectance} & \textbf{Omnivory} & \textbf{Path length}\\
+\textbf{Species} & \textbf{Interactions} & \textbf{Density} & \textbf{Connectance} & \textbf{Omnivory} & \textbf{CPL} & \textbf{CC} & \textbf{SW}\\
 \hline
-379 & 1778 & 4.69 & 0.01 & 0.48 & 2.99\\
+379 & 1778 & 4.69 & 0.01 & 0.48 & 2.99 & 0.08 & True\\
 \hline
@@
 \caption{Degree distributions for the (A) food web, for (B) prey among predators, (C) predators among prey, and (D) for each functional group.
-Groups are vertically ordered by increasing trophic level; groups with less than 3 species were not plotted (e.g.
-pelagic fish).}\label{fig:figure3}
+Groups are vertically ordered by increasing trophic level; groups with less than 3 species were not plotted (e.g., pelagic fish).}\label{fig:figure3}
 \end{figure}
@@
 
-The majority of the species of the food web were consumers, 336 out of
+The majority of the species in the food web were consumers, 336 out of
 379; the rest were primary producers, such as diatoms (phytoplankton),
@@
 We found different relationships between the species trophic level (TL)
-and the rest of the analysed species-level properties (Figure 4A-D). In
-this regard, the most evident significant relationship was with trophic
-similarity, i.e.~the higher the species' TL, the lower the trophic
-similarity or the higher the uniqueness in terms of trophic role (Figure
-4C). Here it's noteworthy to highlight high-trophic level species with
-low values of trophic similarity: \emph{Bathyraja macloviana} and
-\emph{Squalus acanthias} (Chondrichthyans), \emph{Diplopteraster clarki}
-and \emph{Pteraster sp} (echinoderms), \emph{Phalacrocorax\_atriceps}
-and \emph{Eudyptes chrysocome} (sea birds), and \emph{Lagenorhynchus
+and the rest of the analysed species-level properties (Figure 4A-D). The
+most evident significant relationship was with trophic similarity,
+i.e.~the higher the species' TL, the lower the trophic similarity or the
+higher the uniqueness in terms of trophic role (Figure 4C). Here it is
+noteworthy to highlight those high-trophic level species with low values
+of trophic similarity: \emph{Bathyraja macloviana} and \emph{Squalus
+acanthias} (Chondrichthyans), \emph{Diplopteraster clarki} and
+\emph{Pteraster sp} (echinoderms), \emph{Phalacrocorax\_atriceps} and
+\emph{Eudyptes chrysocome} (sea birds), and \emph{Lagenorhynchus
 cruciger} and \emph{Mesoplodon bowdoini} (marine mammals) (Table S3).
 
-We also found a negative significant relationship with closeness,
-however less evident, meaning that low-TL species are relatively closer
-to any other species in the food web (Figure 4B). Species of genera
-\emph{Calanus} and \emph{Euphausia}, and species of Brachiopoda, all of
-them with TL \textless{} 3, registered the highest values of closeness
-(Table S3).
-
-It's noteworthy that the highest values of betweenness were shown by
+We also found a negative significant relationship between TL and
+closeness, however less evident, meaning that low-TL species are
+relatively closer to any other species in the food web (Figure 4B).
+Species of genera \emph{Calanus} and \emph{Euphausia}, and species of
+Brachiopoda, all of them with TL \textless{} 3, registered the highest
+values of closeness (Table S3).
+
+It is noteworthy that the highest values of betweenness were shown by
 species of mid-TLs (3-4), meaning that those species participated in the
-highest number of shortest paths between species (Figure 4A). These were
-the species with the highest values: \emph{Patagonotothen ramsayi},
-\emph{Dissostichus eleginoides}, \emph{Salilota australis} (fishes),
-\emph{Doryteuthis gahi} (Cephalopoda), and \emph{Patagonotothen
-guntheri} (Notothenioid fish) (Table S3).
-
-Taking into account the topological role, `module specialist' species
-were the most frequent and presented a wide TL range (1 - 4.77); `module
-hub' was constrained to mid-TL species (2.48 - 3.92); `module connector'
-from low to mid-TLs (1 - 3.86); and `network connector', the least
-frequent, had all of its species in TL = 1, except for one with TL =
-3.47 (Figure 4D, see Figure S2 for species' topological roles in a food
-web graph framework). Here it's important to highlight species of the
-two latter topological roles, because they are responsible for linking
-modules and maintaining the connectivity of the food web: 40 species (5
-network connectors + 35 module connectors) from 20 different functional
-groups with a TL range = 1 - 3.86.
+highest number of shortest paths between species (Figure 4A). The
+following are the species with the highest values: \emph{Patagonotothen
+ramsayi}, \emph{Dissostichus eleginoides}, \emph{Salilota australis}
+(fishes), \emph{Doryteuthis gahi} (Cephalopoda), and
+\emph{Patagonotothen guntheri} (Notothenioid fish) (Table S3).
+
+Considering the topological role, `module specialist' species were the
+most frequent and presented a wide TL range (1 - 4.77); `module hub' was
+constrained to mid-TL species (2.48 - 3.92); `module connector' from low
+to mid-TLs (1 - 3.86); and `network connector', the least frequent, had
+all of its species in TL = 1, except for one with TL = 3.47 (Figure 4D,
+see Figure S2 for species' topological roles in a food web graph
+framework). Here it is important to highlight the two latter topological
+roles, because they are responsible for linking modules and maintaining
+the connectivity of the food web: 40 species (5 network connectors + 35
+module connectors) from 20 different functional groups with a TL range =
+1 - 3.86. The following were the five species with a network connector
+role: Detritus, Diatoms (benthic, centric and pennate), and
+\emph{Patagonotothen ramsayi}. The 35 species with a module connector
+role represent these functional groups: Amphipoda, Bivalvia,
+Brachiopoda, Bryozoa, Cnidaria, Cumacea, Decapoda, Detritus, Diatoms,
+Dinoflagellates, Echinodermata, Fish (bentho-pelagic, demersal,
+chondrichthyes), Foraminifera, Polychaeta, Porifera, Pycnogonida, Sea
+birds, and Zooplankton (see Supplementary Material Table S3 for the
+identity of the species).
 
@@
 
-\hypertarget{the-mpa-namuncuruxe1---banco-burdwood-food-web}{%
-\subsection{The MPA Namuncurá - Banco Burdwood food
-web}\label{the-mpa-namuncuruxe1---banco-burdwood-food-web}}
-
-\begin{itemize}
-\item
-  The MPA Namuncurá - Banco Burdwood food web is one of the most
-  highly-resolved networks of trophic interactions described for
-  subpolar and polar regions. Compare network-level properties with
-  other subpolar and polar food webs.
-\item
-  The food web shows an asymmetry in the distribution of interactions at
-  several levels: food web, functional group, prey and predators. In all
-  of them interactions are concentrated in a few species. On one hand,
-  this asymmetry indicates that most consumers have a narrow diet, and
-  few present flexible diets (\emph{Patagonotothen guntheri}, \emph{P.
-  ramsayi}, \emph{Dissostichus eleginoides}, \emph{Bathyraja
-  brachyurops}, \emph{B. griseocauda}). On the other hand few prey are
-  consumed by many predators, meaning that there are dominant food
-  sources from which most consumers depend on: detritus, diatoms
-  (benthic, centric, pennate), and species of \emph{Euphausia}.
-\end{itemize}
-
-\hypertarget{species-role}{%
-\subsection{Species' role}\label{species-role}}
-
-Our results state that certain species play particular roles in the
-structure of the food web.
-
-\begin{itemize}
-\item
-  Betweenness. Species at mid-trophic levels (3-4) lie in more shortest
-  paths between species than any other species: `bridge' role.
-  Implications for spread of perturbations like mercury (Fioramonti,
-  Ribeiro Guevara, Becker, \& Riccialdelli, 2022), microplastics (Cossi
-  et al., 2021).
-\item
-  Closeness. Low-trophic level species are relatively closer to other
-  species in the food web. Apart from the most demanded food sources
-  (i.e.~detritus), which are logically closer to many species,
-  unexpected consumers arise as important in this regard. Species of the
-  zooplankton community like \emph{Calanus} and \emph{Euphausia} are
-  crucial for the food web functioning, since they can affect others
-  more quickly.
-\item
-  Trophic similarity. Species are more similar at low and mid-trophic
-  levels (2-4). There is a functional redundancy at these levels of the
-  food web. On the other hand, less trophic similarity at high TLs
-  indicate uniqueness in terms of trophic role. This highlights the
-  importance of top predators in the sense that they play a role that
-  cannot be played by any other species.
-\item
-  Topological role. Low and mid-trophic level species (TL = 1 - 3.86)
-  are responsible for maintaining the connectivity of the food web
-  (network connector and module connector). The functional groups
-  represented are: Amphipoda, Bivalvia, Bryozoa, Cnidaria, Cumacea,
-  Decapoda, Detritus, Diatoms, Echinodermata, Fish (bentho-pelagic,
-  demersal, chondrichthyes), Foraminifera, Polychaeta, Porifera,
-  Zooplankton. This shows that the structure of the food web depends on
-  a diversity of species, which at the end comprise the ecosystem's
-  diversity.
-\item
-  Overall, low and mid-trophic level species arise as crucial in the
-  structure of the MPA Namuncurá - Banco Burdwood food web, since they
-  present the highest betweenness and closeness values, and the most
-  important topological roles. This coincides with a recent study that
-  suggest a wasp-waist trophic structure for the region (Riccialdelli et
-  al., 2020). However, we also suggest that there exists functional
-  redundancy at mid-trophic levels. Furthermore, our study points out
-  species of high-trophic levels due to its uniqueness role.
-\end{itemize}
+\hypertarget{the-food-web-of-the-mpa-namuncuruxe1---banco-burdwood-ecosystem}{%
+\subsection{The food web of the MPA Namuncurá - Banco Burdwood
+ecosystem}\label{the-food-web-of-the-mpa-namuncuruxe1---banco-burdwood-ecosystem}}
+
+The food web of the MPA Namuncurá - Banco Burdwood ecosystem analysed in
+this study is one of the most highly-resolved networks of trophic
+interactions ever studied not only for a high-latitude marine ecosystem
+but also for a marine protected area worldwide. It is of paramount
+importance to consider the complexity of species interactions in order
+to gain insights into the structure and functioning of the ecosystem,
+since the aggregation of species might mask food web properties and/or
+produce type II errors (false positive) (Gauzens et al., 2013; Martinez,
+1993).
+
+Food web connectance is a feature that resumes the complexity of the
+network, but more importantly, it is an emergent property of pairwise
+species interactions (Poisot \& Gravel, 2014). It contains information
+regarding how interactions within an ecological network are distributed,
+and predicts reasonably well key dynamical properties of ecological
+networks (Dunne et al., 2002a). Complex marine food webs (i.e.~with more
+than 25 trophic species) show connectance values ranging from 0.01 -
+0.27 (Marina et al., 2018). In particular, food webs from high-latitude
+regions tend to exhibit a connectance closer to the minimum (between
+0.01 and 0.05) (Kortsch et al., 2015; Rodriguez et al., 2022; Santana et
+al., 2013). Whether food webs display a low or a high connectance helps
+to better comprehend ecosystem's synthetic properties like robustness.
+In this sense, empirical analyses support the notion that
+highly-connected ecological networks are robust against external
+perturbations such as the introduction of new (e.g., invasive) species
+(Smith-Ramesh et al., 2017) as well as species removal (e.g., local
+extinction) (Dunne et al., 2002b; Montoya \& Solé, 2003). The
+connectance of the food web of the MPA Namuncurá - Banco Burdwood (0.01)
+is one of the lowest reported so far for these regions; in particular,
+it appears to be five times lower than that of Beagle Channel, an
+adjacent area (Rodriguez et al., 2022).
+
+The degree distribution or the distribution of number of interactions
+per species is the core for the structure of species interactions, which
+influences the opportunities for multiple species to persist in the long
+term and, therefore, their coexistence (Godoy et al., 2018). The food
+web for the MPA N-BB presents an asymmetric degree distribution. This
+pattern was identified at different levels of analysis: food web,
+predator, prey, and functional group. Such asymmetry is a well-known
+feature in empirical complex food webs in particular (Dunne et al.,
+2002a; Montoya \& Solé, 2003; Stouffer et al., 2005), and has received
+great attention in complex networks in general (Albert \& Barabási,
+2002; Newman, 2003). The degree distribution affects the resilience of
+complex food webs against random failures and intentional attacks: food
+webs showing right-skewed distributions, like the one described in this
+study, are more vulnerable to the removal of the most connected species
+or hubs, with the potential of producing secondary extinctions and a
+catastrophic fragmentation of the network (Albert et al., 2000; Dunne et
+al., 2002b; Eklöf \& Ebenman, 2006).
+
+It is suggested that the small-world pattern, i.e., a network with short
+path length and high clustering coefficient is not frequent in complex
+marine food webs, mainly due to a low clustering coefficient compared to
+random networks (Dunne et al., 2002c; Marina et al., 2018). However, the
+food web of the MPA N-BB does display a small-world pattern.
+Consequences of this could be of great importance in recognizing
+evolutionary paths and the vulnerability to perturbations (Montoya \&
+Solé, 2002). On the one hand, a short path length implies a rapid spread
+of an impact (e.g., contaminant, population fluctuation, local
+extinction) throughout the network and, at the same time, a more
+potentially adaptive dynamics in face of external perturbations (Montoya
+\& Solé, 2002; Williams et al., 2002). On the other hand, a high
+clustering coefficient indicates the formation of subnetworks composed
+only by the neighbours of particular species. This translates into a
+greater resistance of the network due to the confinement of
+perturbations mainly within subnetworks and not spreading between them
+(Heer et al., 2020; Kortsch et al., 2019). Overall, a small-world
+topology provides ecological networks with a greater resilience and
+resistance (Bornatowski et al., 2017; Dormann et al., 2017).
+
+Omnivory acts as a buffer to changes as the ecosystem presents
+alternative energy pathways in the face of perturbations; i.e., reducing
+the risk of cascading extinctions following primary loss of species
+(Borrvall et al., 2000). This is based on the fact that omnivores are
+species able to adapt faster and to a wider range of environmental
+conditions by changing their foraging habits to feed on the most
+abundant prey (Fagan, 1997). Furthermore, omnivory can be analysed from
+the interaction point of view: theoretical studies have identified
+omnivorous interactions as a possible candidate for a keystone
+interaction, sensu Kadoya et al. (2018), highlighting the importance of
+omnivory inn stabilizing food web dynamics (McCann \& Hastings, 1997;
+Neutel et al., 2002). The high proportion of omnivory in the food web of
+the MPA N-BB suggests that the network might be robust to variations in
+prey abundances, which could increase food web's persistence and
+stability (Stouffer \& Bascompte, 2010).
+
+To resume, the food web of the MPA Namuncurá - Banco Burdwood presents a
+combination of network properties that make it unique in terms of
+network resolution, complexity, and structural pattern. All this suggest
+that the ecosystem might be fragile to external perturbations targeting
+highly connected species. However, structural properties might provide
+resilience and resistance with the final outcome of a rearrange
+structure maintaining their functions.
+
+\hypertarget{dominant-consumers-and-food-sources}{%
+\subsection{Dominant consumers and food
+sources}\label{dominant-consumers-and-food-sources}}
+
+The degree distribution allows to identify important species, such as
+potential keystone species (Dunne et al., 2002b; Solé \& Montoya, 2001),
+generalist/specialist species, and dominant food sources (Kondoh et al.,
+2010).
+
+We have identified that the majority of the consumers in the food web of
+the MPA N-BB either has a narrow diet or are specialists, while few
+present a broad diet. The most evident generalist species are
+\emph{Patagonotothen guntheri}, \emph{P. ramsayi}, \emph{Dissostichus
+eleginoides}, \emph{Bathyraja brachyurops}, and \emph{B. griseocauda},
+with more than 25 potential prey. Since these species present
+mid-trophic positions in the food web (3-4), acting as predator and
+prey, they might be important links between lower and higher trophic
+levels. This is in agreement with the sole analysis, using stable
+isotopes, that exists so far for the trophic structure of the MPA N-BB
+(Riccialdelli et al., 2020), and resembles other high-latitude marine
+systems of the Southwest Atlantic and Arctic regions (Arkhipkin \&
+Laptikhovsky, 2013; Kortsch et al., 2019). The importance of these
+particular generalist species also arises since they feed on the benthic
+and pelagic habitats (Covatti Ale et al., 2022; Fischer et al., 2022;
+Troccoli et al., 2020), linking these realms and contributing to the
+vertical carbon flow.
+
+On the other hand, few prey are consumed by many predators in the food
+web of the MPA N-BB. This suggests that there are dominant food sources
+from which most consumers depend on, and from where the ecosystem energy
+is being transferred to the upper trophic levels. The most demanded
+source we identified in this study (i.e.~detritus) supports the abundant
+benthic community of filter-feeders (L. Schejter et al., 2016).
+Furthermore, we found that the second and third-most consumed prey were
+diatoms and species of \emph{Euphausia}, respectively, which are
+essential sources for the diverse zooplankton community (Spinelli et
+al., 2020), mid-TL consumers like the Fuegian sprat \emph{Sprattus
+fuegensis} (Padovani et al., 2021) and \emph{Patagonotothen ramsayi}
+(Fischer et al., 2022), and top predators (Raya Rey, 2022; Riccialdelli,
+2022).
+
+\hypertarget{species-role-related-to-their-trophic-level}{%
+\subsection{Species' role related to their trophic
+level}\label{species-role-related-to-their-trophic-level}}
+
+Describing species' roles in food webs provides a toolbox with which to
+assess the significance of species in terms of community's functioning
+and overall stability (Cirtwill et al., 2018; Thébault \& Fontaine,
+2010). We used a range of descriptors to characterise the dynamic and
+multifaceted nature of the species forming the MPA N-BB food web.
+
+Closeness and betweenness are defined as ``meso-scale'' properties
+because they consider direct and indirect interactions, therefore
+describing the focal species' ability to influence the rest of the
+species of the food web (Lai et al., 2012). Closeness quantifies how
+many steps away species \(i\) is from all other species in the food web,
+and is proportional to how rapidly the indirect effects of the focal
+species can spread to other species in the network (Scotti \& Jordán,
+2010). In the food web of the MPA N-BB, low-TL consumers arise as
+important in this regard: species of the zooplankton community,
+\emph{Calanus} and \emph{Euphausia}, and Brachiopoda. Any perturbation
+affecting these species, such as the recently confirmed contaminants
+mercury (Fioramonti et al., 2022) and microplastics (Cossi et al., 2021;
+Di Mauro et al., 2022) for the area, should be of concern since it might
+reach many other species in the food web. Otherwise, betweenness
+measures the number of shortest paths between species, providing
+information on the importance of species as ``bridges'' for energy
+transfer: a species with high betweenness takes part in more food chains
+and therefore affects more energy flows (Scotti \& Jordán, 2010). We
+have identified the longtail southern cod \emph{Patagonotothen ramsayi}
+as the most important species in this sense. Moreover, in light of our
+analysis, other species like the Patagonian toothfish \emph{Dissostichus
+eleginoides}, the Patagonian cod \emph{Salilota australis}, the
+yellowfin notothen \emph{Patagonotothen guntheri}, and the Patagonian
+longfin squid \emph{Doryteuthis gahi} should be considered as relevant
+in the energy transfer in the ecosystem. All these species have a
+mid-trophic position in the food web, supporting the `wasp-waist'
+control hypothesis for the MPA N-BB (Riccialdelli et al., 2020).
+
+Ecosystems with a pronounced `wasp-waist' structure are suggested to
+present a high trophic redundancy, since a large proportion of species
+would show similar trophic habits (Cury et al., 2000). The significant
+negative relationship we found between trophic similarity and trophic
+level enhances the hypothesis of functional redundancy at low and mid-TL
+species compared to higher TL species for the MPA N-BB food web
+(Riccialdelli et al., 2020). At the same time, our results highlight the
+uniqueness in terms of trophic role for high-TL predators. Here, not
+only the expected pelagic animals such as marine mammals and sea birds
+arise as relevant, but also benthic vertebrate (chondrichthyans
+\emph{Bathyraja macloviana} and \emph{Squalus acanthias}) and
+invertebrate species (echinoderms \emph{Diplopteraster clarki} and
+\emph{Pteraster sp}) are noteworthy. The role that such species play in
+the MPA N-BB ecosystem is unique and perturbations on them might result
+in unprecedented changes at the trophic structure and functioning level.
+
+Species' role can be also assessed in a module-based context. Among the
+varying numbers of topological roles in which species can be divided,
+two are remarkable: `module connector' and `network connector'. Here
+again the longtail southern cod \emph{Patagonotothen ramsayi} is
+emphasized as an influential species for the connectivity of the food
+web, which agrees with the suggested `wasp-waist' control for the MPA
+N-BB ecosystem (Riccialdelli et al., 2020). But most importantly, our
+results broadens this issue by pointing out that there are other
+species, belonging to a wide range of trophic positions (1 to 3.86) and
+representing 20 different functional groups, that should be considered.
+Thus, we propose that it is the diversity of species (benthic and
+pelagic) what maintains the connectivity of the food web, therefore
+contributing to the trophic structure and ecosystem's stability.
 
@@
 
+In construction\ldots{}
+
 Caveats:
 
-\begin{itemize}
-\item
 Seasonal variation in predators' diet due to food source availability.
-\item
-  Spatial variation of study area: Banco Burdwood west-east gradient.
-\item
-  The lack of density or biomass data might have neglected well-known
-  important species for the structure of the food web: \emph{Sprattus
-  fuegensis}.
-\end{itemize}
+Brose et al. (2019)
+
+Spatial variation of study area: Banco Burdwood west-east gradient. In
+the oceanic BB area, complex oceanographic conditions generate an
+internal spatial heterogeneity, mainly along its longitudinal axis
+(Matano et al., 2019), and consequently plankton communities respond
+with different spatial distributions (Spinelli et al., 2020). Kortsch et
+al. (2019)
 
@@
 
-\begin{itemize}
-\item
-  Estimation of interaction strength to gain insights into food web
-  stability and response to anthropogenic and environmental
-  perturbations.
-\item
-  Simulate perturbations on food web and target species: mercury
-  transfer, microplastic pollution, fisheries.
-\end{itemize}
+Incorporate habitat heterogeneity, since benthic community in the BB and
+deep flanks is different (Schejter \& Albano, 2021). This might lead to
+distinct food web properties, hence differences in ecosystem functioning
+and response to anthropogenic and environmental perturbations. Cordone
+et al. (2020)
+
+Simulate perturbations on food web and target species: mercury transfer,
+microplastic pollution, fisheries. Cossi et al. (2021); Di Mauro et al.
+(2022); Fioramonti et al. (2022)
+
+Estimation of interaction strength considering species and interaction
+traits (i.e.~body size, body mass, interaction dimensionality) to gain
+insights into food web stability and response to anthropogenic and
+environmental perturbations. Nilsson \& McCann (2016); Cirtwill et al.
+(2018); Kortsch et al. (2021)
 
@@
 \section{Conclusion}\label{conclusion}}
+
+We compiled information on the species and trophic diversity of the
+Marine Protected Area Namuncurá - Banco Burdwood, generating an
+unprecedented, well-resolved network of trophic interactions for a
+sub-Antarctic ecosystem, identifying the complexity and structure of the
+system, and the main species role in a network framework. Particular
+properties at the network level allowed us to identify ecosystem's
+vulnerability and potential response to perturbations in the presence of
+highly-connected species, with a rearrange structure maintaining their
+functions due to its potential resilience and resistance.
+
+We identified several species as important in terms of different aspects
+of trophic structure and functioning, and response to perturbations
+(i.e.~environmental/anthropogenic changes). On one hand, we suggest that
+generalist species, mostly fishes, play a crucial role in the
+ecosystem's bentho-pelagic coupling process. At the same time, we
+propose that other species rather than the longtail southern cod
+\emph{Patagonotothen ramsayi} and the Fueguian sprat \emph{Sprattus
+fuegensis} should be considered as relevant energy transfers for the
+ecosystem. Finally, we argue that it is the diversity of species,
+representing the benthic and pelagic habitats, what maintains the
+connectivity of the food web against perturbations, therefore
+contributing to the structure and stability of the ecosystem.
+
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
+
+We are indebted to all those experts of the working group `Banco
+Burdwood' who humbly provided their knowledge to enhance the quality of
+the present research (add names if necessary), and special thanks to GA
+Lovrich the Scientific Coordinator of the MPA Namuncurá-Burdwood Bank
+and the MPA N-BB Administrators. This study was funded by Consejo
+Nacional de Investigaciones Científicas y Técnicas (CONICET) and Agencia
+Nacional de Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617),
+Argentina. This work is contribution no. XX of the MPA Namuncurá (Law
+26.875).
 
@@
 America}: {Physical} and ecological processes. \emph{Journal of Marine
-Systems}, \emph{44}(1), 83--105. doi:
-\href{https://doi.org/10.1016/j.jmarsys.2003.09.005}{10.1016/j.jmarsys.2003.09.005}
+Systems}, \emph{44}(1), 83--105.
+\url{https://doi.org/10.1016/j.jmarsys.2003.09.005}
 
@@
 Albert, R., \& Barabási, A.-L. (2002). Statistical mechanics of complex
-networks. \emph{Reviews of Modern Physics}, \emph{74}(1), 47--97. doi:
-\href{https://doi.org/10.1103/RevModPhys.74.47}{10.1103/RevModPhys.74.47}
+networks. \emph{Reviews of Modern Physics}, \emph{74}(1), 47--97.
+\url{https://doi.org/10.1103/RevModPhys.74.47}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Albert2000}{}}%
+Albert, R., Jeong, H., \& Barabási, A.-L. (2000). Error and attack
+tolerance of complex networks. \emph{Nature}, \emph{406}(6794),
+378--382. \url{https://doi.org/10.1038/35019019}
 
@@
 APN. (2022). \emph{Plan de gestión {AMP Namuncurá Banco Burdwood}}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-APN2023}{}}%
+APN. (2023). \emph{Área {Marina Protegida Namuncurá Banco Burdwood}}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Arkhipkin2013}{}}%
+Arkhipkin, A., \& Laptikhovsky, V. (2013). From gelatinous to muscle
+food chain: Rock cod {Patagonotothen} ramsayi recycles coelenterate and
+tunicate resources on the {Patagonian Shelf}. \emph{Journal of Fish
+Biology}, \emph{83}(5), 1210--1220.
+\url{https://doi.org/10.1111/jfb.12217}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bascompte2009}{}}%
+Bascompte, J. (2009). Disentangling the {Web} of {Life}. \emph{Science},
+\emph{325}(5939), 416--419.
+\url{https://doi.org/10.1126/science.1170749}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bergagna2019}{}}%
+Bergagna, L. (2019). \emph{{Descripción de los ensambles bentónicos del
+AMP Namuncurá-Banco Burdwood y estimación del contenido de carbono
+-orgánico e inorgánico- allí presente.}} {[}\{Bachelor Thesis\}{]}.
+Universidad Nacional de Córdoba.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bergagna2020}{}}%
+Bergagna, L., Chiesa, I., Álvarez, Y. P., Ceballos, S. G., Boy, C. C.,
+Riccialdelli, L., \& Lovrich, G. A. (2020). {En el fondo el Banco es
+bueno}. \emph{La Lupa. Colección Fueguina de Divulgación Científica},
+\emph{16}, 20--24.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bornatowski2017}{}}%
+Bornatowski, H., Barreto, R., Navia, A. F., \& de Amorim, A. F. (2017).
+Topological redundancy and {``small-world''} patterns in a food web in a
+subtropical ecosystem of {Brazil}. \emph{Marine Ecology}, \emph{38}(2),
+e12407. \url{https://doi.org/10.1111/maec.12407}
 
@@
 levels: {Selection} against instability explains the pattern. \emph{Food
-Webs}, \emph{1}(1), 10--17. doi:
-\href{https://doi.org/10.1016/j.fooweb.2014.11.002}{10.1016/j.fooweb.2014.11.002}
+Webs}, \emph{1}(1), 10--17.
+\url{https://doi.org/10.1016/j.fooweb.2014.11.002}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Borrvall2000}{}}%
+Borrvall, C., Ebenman, B., \& Tomas Jonsson, T. J. (2000). Biodiversity
+lessens the risk of cascading extinction in model food webs.
+\emph{Ecology Letters}, \emph{3}(2), 131--136.
+\url{https://doi.org/10.1046/j.1461-0248.2000.00130.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Brickle2009}{}}%
+Brickle, P., Arkhipkin, A. I., Laptikhovsky, V., Stocks, A., \& Taylor,
+A. (2009). Resource partitioning by two large planktivorous fishes
+{Micromesistius} australis and {Macruronus} magellanicus in the
+{Southwest Atlantic}. \emph{Estuarine, Coastal and Shelf Science},
+\emph{84}(1), 91--98. \url{https://doi.org/10.1016/j.ecss.2009.06.007}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Brose2019}{}}%
+Brose, U., Archambault, P., Barnes, A. D., Bersier, L.-F., Boy, T.,
+Canning-Clode, J., Conti, E., Dias, M., Digel, C., Dissanayake, A.,
+Flores, A. A. V., Fussmann, K., Gauzens, B., Gray, C., Häussler, J.,
+Hirt, M. R., Jacob, U., Jochum, M., Kéfi, S., \ldots{} Iles, A. C.
+(2019). Predator traits determine food-web architecture across
+ecosystems. \emph{Nature Ecology \& Evolution}, \emph{3}(6), 919--927.
+\url{https://doi.org/10.1038/s41559-019-0899-x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-CBD2004}{}}%
+CBD. (2004). \emph{Secretariat of the convention on biological
+diversity: {Technical} advice on the establishment and management of a
+national system of marine and coastal protected areas, {Technical
+Series} number 13.}
 
@@
 Cagua, E. F., Coux, C., \& Dehling, D. M. (2018). A review of species
-role concepts in food webs. \emph{Food Webs}, \emph{16}, e00093. doi:
-\href{https://doi.org/10.1016/j.fooweb.2018.e00093}{10.1016/j.fooweb.2018.e00093}
+role concepts in food webs. \emph{Food Webs}, \emph{16}, e00093.
+\url{https://doi.org/10.1016/j.fooweb.2018.e00093}
+
+\leavevmode\vadjust pre{\hypertarget{ref-CommissionfortheConservationofAntarcticMarineLivingResources2009}{}}%
+Commission for the Conservation of Antarctic Marine Living Resources.
+(2009). \emph{Vulnerable {Marine Ecosystem} taxa identification guide}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Cordone2018}{}}%
+Cordone, G., Marina, T. I., Salinas, V., Doyle, S. R., Saravia, L. A.,
+\& Momo, F. R. (2018). Effects of macroalgae loss in an {Antarctic}
+marine food web: Applying extinction thresholds to food web studies.
+\emph{PeerJ}, \emph{6}, e5531. \url{https://doi.org/10.7717/peerj.5531}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Cordone2020}{}}%
+Cordone, G., Salinas, V., Marina, T. I., Doyle, S. R., Pasotti, F.,
+Saravia, L. A., \& Momo, F. R. (2020). Green vs brown food web:
+{Effects} of habitat type on multidimensional stability proxies for a
+highly-resolved {Antarctic} food web. \emph{Food Webs}, \emph{25},
+e00166. \url{https://doi.org/10.1016/j.fooweb.2020.e00166}
 
@@
 ({Echinodermata}: {Asteroidea}). \emph{Polar Biology}, \emph{44}(12),
-2277--2287. doi:
-\href{https://doi.org/10.1007/s00300-021-02959-5}{10.1007/s00300-021-02959-5}
+2277--2287. \url{https://doi.org/10.1007/s00300-021-02959-5}
+
+\leavevmode\vadjust pre{\hypertarget{ref-CovattiAle2022}{}}%
+Covatti Ale, M., Fischer, L., Deli Antoni, M., Diaz de Astarloa, J. M.,
+\& Delpiani, G. (2022). Trophic ecology of the yellowfin notothen,
+{Patagonotothen} guntheri ({Norman}, 1937) at the {Marine Protected Area
+Namuncurá-Burdwood Bank}, {Argentina}. \emph{Polar Biology},
+\emph{45}(4), 549--558. \url{https://doi.org/10.1007/s00300-022-03011-w}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Cury2000}{}}%
+Cury, P., Bakun, A., Crawford, R. J. M., Jarre, A., Quiñones, R. A.,
+Shannon, L. J., \& Verheye, H. M. (2000). Small pelagics in upwelling
+systems: Patterns of interaction and structural changes in
+{``wasp-waist''} ecosystems. \emph{ICES Journal of Marine Science},
+\emph{57}(3), 603--618. \url{https://doi.org/10.1006/jmsc.2000.0712}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Day2013}{}}%
+Day, R. H., Weingartner, T. J., Hopcroft, R. R., Aerts, L. A. M.,
+Blanchard, A. L., Gall, A. E., Gallaway, B. J., Hannay, D. E., Holladay,
+B. A., Mathis, J. T., Norcross, B. L., Questel, J. M., \& Wisdom, S. S.
+(2013). The offshore northeastern {Chukchi Sea}, {Alaska}: {A} complex
+high-latitude ecosystem. \emph{Continental Shelf Research}, \emph{67},
+147--165. \url{https://doi.org/10.1016/j.csr.2013.02.002}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Delpiani2020}{}}%
+Delpiani, S. M., Bruno, D. O., Vazquez, D. M., Llompart, F., Delpiani,
+G. E., Fernández, D. A., Rosso, J. J., Mabragaña, E., \& Díaz de
+Astarloa, J. M. (2020). Structure and distribution of fish assemblages
+at {Burdwood Bank}, the first {Sub-Antarctic Marine Protected Area}
+{``{Namuncurá}''} in {Argentina} ({Southwestern Atlantic Ocean}).
+\emph{Polar Biology}, \emph{43}(11), 1783--1793.
+\url{https://doi.org/10.1007/s00300-020-02744-w}
+
+\leavevmode\vadjust pre{\hypertarget{ref-DiMauro2022}{}}%
+Di Mauro, R., Castillo, S., Pérez, A., Iachetti, C. M., Silva, L.,
+Tomba, J. P., \& Chiesa, I. L. (2022). Anthropogenic microfibers are
+highly abundant at the {Burdwood Bank} seamount, a protected
+sub-{Antarctic} environment in the {Southwestern Atlantic Ocean}.
+\emph{Environmental Pollution}, \emph{306}, 119364.
+\url{https://doi.org/10.1016/j.envpol.2022.119364}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Dormann2017}{}}%
+Dormann, C. F., Fründ, J., \& Schaefer, H. M. (2017). Identifying
+{Causes} of {Patterns} in {Ecological Networks}: {Opportunities} and
+{Limitations}. \emph{Annual Review of Ecology, Evolution, and
+Systematics}, \emph{48}, 559--584.
+\url{https://doi.org/10.1146/annurev-ecolsys-110316-022928}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002a}{}}%
+Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002a). Food-web
+structure and network theory: {The} role of connectance and size.
+\emph{Proceedings of the National Academy of Sciences}, \emph{99}(20),
+12917--12922. \url{https://doi.org/10.1073/pnas.192407699}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Dunne2002}{}}%
-Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002). Network
+Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002b). Network
 structure and biodiversity loss in food webs: Robustness increases with
-connectance. \emph{Ecology Letters}, \emph{5}(4), 558--567. doi:
-\href{https://doi.org/10.1046/j.1461-0248.2002.00354.x}{10.1046/j.1461-0248.2002.00354.x}
+connectance. \emph{Ecology Letters}, \emph{5}(4), 558--567.
+\url{https://doi.org/10.1046/j.1461-0248.2002.00354.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002b}{}}%
+Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002c). \emph{Small
+{Networks} but not {Small Worlds}: {Unique Aspects} of {Food Web
+Structure}}. {Santa Fe Institute}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Eklof2006}{}}%
+Eklöf, A., \& Ebenman, B. (2006). Species loss and secondary extinctions
+in simple and complex model communities. \emph{Journal of Animal
+Ecology}, \emph{75}(1), 239--246.
+\url{https://doi.org/10.1111/j.1365-2656.2006.01041.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Estrada2007}{}}%
+Estrada, E. (2007). Food webs robustness to biodiversity loss: {The}
+roles of connectance, expansibility and degree distribution.
+\emph{Journal of Theoretical Biology}, \emph{244}(2), 296--307.
+\url{https://doi.org/10.1016/j.jtbi.2006.08.002}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Fagan1997}{}}%
+Fagan, W. F. (1997). Omnivory as a {Stabilizing Feature} of {Natural
+Communities}. \emph{The American Naturalist}, \emph{150}(5), 554--567.
+\url{https://doi.org/10.1086/286081}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Falabella2017}{}}%
+Falabella, V. (2017). \emph{Área {Marina Protegida Namuncurá-Banco
+Burdwood}. {Contribuciones} para la línea de base y el plan de manejo}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Fernandez2021}{}}%
+Fernández, M., Rodríguez-Ruiz, M., Gelcich, S., Hiriart-Bertrand, L., \&
+Castilla, J. C. (2021). Advances and challenges in marine conservation
+in {Chile}: {A} regional and global comparison. \emph{Aquatic
+Conservation: Marine and Freshwater Ecosystems}, \emph{31}(7),
+1760--1771. \url{https://doi.org/10.1002/aqc.3570}
 
@@
 {Southwest Atlantic Ocean}. \emph{Marine Pollution Bulletin},
-\emph{175}, 113365. doi:
-\href{https://doi.org/10.1016/j.marpolbul.2022.113365}{10.1016/j.marpolbul.2022.113365}
+\emph{175}, 113365.
+\url{https://doi.org/10.1016/j.marpolbul.2022.113365}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Fischer2022}{}}%
+Fischer, L., Covatti Ale, M., Deli Antoni, M., Díaz de Astarloa, J. M.,
+\& Delpiani, G. (2022). Feeding ecology of the longtail southern cod,
+{Patagonotothen} ramsayi ({Regan}, 1913) ({Notothenioidei}) in the
+{Marine Protected Area Namuncurá-Burdwood Bank}, {Argentina}.
+\emph{Polar Biology}, \emph{45}(9), 1483--1494.
+\url{https://doi.org/10.1007/s00300-022-03082-9}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Franco2020}{}}%
+Franco, B. C., Defeo, O., Piola, A. R., Barreiro, M., Yang, H., Ortega,
+L., Gianelli, I., Castello, J. P., Vera, C., Buratti, C., Pájaro, M.,
+Pezzi, L. P., \& Möller, O. O. (2020). Climate change impacts on the
+atmospheric circulation, ocean, and fisheries in the southwest {South
+Atlantic Ocean}: A review. \emph{Climatic Change}, \emph{162}(4),
+2359--2377. \url{https://doi.org/10.1007/s10584-020-02783-6}
 
@@
 Freeman, L. C. (1978). Centrality in social networks conceptual
-clarification. \emph{Social Networks}, \emph{1}(3), 215--239. doi:
-\href{https://doi.org/10.1016/0378-8733(78)90021-7}{10.1016/0378-8733(78)90021-7}
+clarification. \emph{Social Networks}, \emph{1}(3), 215--239.
+\url{https://doi.org/10.1016/0378-8733(78)90021-7}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Funes2022}{}}%
+Funes, M., Saravia, L. A., Cordone, G., Iribarne, O. O., \& Galván, D.
+E. (2022). Network analysis suggests changes in food web stability
+produced by bottom trawl fishery in {Patagonia}. \emph{Scientific
+Reports}, \emph{12}(1), 10876.
+\url{https://doi.org/10.1038/s41598-022-14363-y}
+
+\leavevmode\vadjust pre{\hypertarget{ref-GarciaAlonso2018}{}}%
+García Alonso, V. A., Brown, D., Martín, J., Pájaro, M., \& Capitanio,
+F. L. (2018). Seasonal patterns of {Patagonian} sprat {Sprattus}
+fuegensis early life stages in an open sea {Sub-Antarctic Marine
+Protected Area}. \emph{Polar Biology}, \emph{41}(11), 2167--2179.
+\url{https://doi.org/10.1007/s00300-018-2352-z}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Gauzens2013}{}}%
+Gauzens, B., Legendre, S., Lazzaro, X., \& Lacroix, G. (2013). Food-web
+aggregation, methodological and functional issues. \emph{Oikos},
+\emph{122}(11), 1606--1615.
+\url{https://doi.org/10.1111/j.1600-0706.2013.00266.x}
 
@@
 currents off {SE South America}. \emph{Journal of Geophysical Research:
-Oceans}, \emph{100}(C7), 13427--13440. doi:
-\href{https://doi.org/10.1029/95JC00942}{10.1029/95JC00942}
+Oceans}, \emph{100}(C7), 13427--13440.
+\url{https://doi.org/10.1029/95JC00942}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Godoy2018}{}}%
+Godoy, O., Bartomeus, I., Rohr, R. P., \& Saavedra, S. (2018). Towards
+the {Integration} of {Niche} and {Network Theories}. \emph{Trends in
+Ecology \& Evolution}, \emph{33}(4), 287--300.
+\url{https://doi.org/10.1016/j.tree.2018.01.007}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Grilli2016}{}}%
+Grilli, J., Rogers, T., \& Allesina, S. (2016). Modularity and stability
+in ecological communities. \emph{Nature Communications}, \emph{7}(1),
+12031. \url{https://doi.org/10.1038/ncomms12031}
 
@@
 \emph{Oceanographic conditions at the southern end of the argentine
-continental slope}. doi: \url{http://10.0.64.26/handle/inidep/247}
+continental slope}.
+https://doi.org/\url{http://10.0.64.26/handle/inidep/247}
 
@@
 complex metabolic networks. \emph{Nature}, \emph{433}(7028), 895--900.
-doi: \href{https://doi.org/10.1038/nature03288}{10.1038/nature03288}
+\url{https://doi.org/10.1038/nature03288}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Guinder2020}{}}%
+Guinder, V. A., Malits, A., Ferronato, C., Krock, B., Garzón-Cardona,
+J., \& Martínez, A. (2020). Microbial plankton configuration in the
+epipelagic realm from the {Beagle Channel} to the {Burdwood Bank}, a
+{Marine Protected Area} in {Sub-Antarctic} waters. \emph{PLOS ONE},
+\emph{15}(5), e0233156.
+\url{https://doi.org/10.1371/journal.pone.0233156}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Heer2020}{}}%
+Heer, H., Streib, L., Schäfer, R. B., \& Ruzika, S. (2020). Maximising
+the clustering coefficient of networks and the effects on habitat
+network robustness. \emph{PLOS ONE}, \emph{15}(10), e0240940.
+\url{https://doi.org/10.1371/journal.pone.0240940}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Hogg2016}{}}%
+Hogg, O. T., Huvenne, V. A. I., Griffiths, H. J., Dorschel, B., \&
+Linse, K. (2016). Landscape mapping at sub-{Antarctic South Georgia}
+provides a protocol for underpinning large-scale marine protected areas.
+\emph{Scientific Reports}, \emph{6}(1), 33163.
+\url{https://doi.org/10.1038/srep33163}
+
+\leavevmode\vadjust pre{\hypertarget{ref-IUCN2023}{}}%
+IUCN, \& UNEP-WCMC. (2023). \emph{The world database on protected areas
+({WDPA})}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kadoya2018}{}}%
+Kadoya, T., Gellner, G., \& McCann, K. S. (2018). Potential oscillators
+and keystone modules in food webs. \emph{Ecology Letters}, \emph{21}(9),
+1330--1340. \url{https://doi.org/10.1111/ele.13099}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kondoh2010}{}}%
+Kondoh, M., Kato, S., \& Sakato, Y. (2010). Food webs are built up with
+nested subwebs. \emph{Ecology}, \emph{91}(11), 3123--3130.
+\url{https://doi.org/10.1890/09-2219.1}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kortsch2021}{}}%
+Kortsch, S., Frelat, R., Pecuchet, L., Olivier, P., Putnis, I.,
+Bonsdorff, E., Ojaveer, H., Jurgensone, I., Strāķe, S., Rubene, G.,
+Krūze, Ē., \& Nordström, M. C. (2021). Disentangling temporal food web
+dynamics facilitates understanding of ecosystem functioning.
+\emph{Journal of Animal Ecology}, \emph{90}(5), 1205--1216.
+\url{https://doi.org/10.1111/1365-2656.13447}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kortsch2019}{}}%
+Kortsch, S., Primicerio, R., Aschan, M., Lind, S., Dolgov, A. V., \&
+Planque, B. (2019). Food-web structure varies along environmental
+gradients in a high-latitude marine ecosystem. \emph{Ecography},
+\emph{42}(2), 295--308. \url{https://doi.org/10.1111/ecog.03443}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kortsch2015}{}}%
+Kortsch, S., Primicerio, R., Fossheim, M., Dolgov, A. V., \& Aschan, M.
+(2015). Climate change alters the structure of arctic marine food webs
+due to poleward shifts of boreal generalists. \emph{Proceedings of the
+Royal Society B: Biological Sciences}, \emph{282}(1814), 20151546.
+\url{https://doi.org/10.1098/rspb.2015.1546}
 
@@
 uniqueness of species from the network perspective. \emph{Biology
-Letters}, \emph{8}(4), 570--573. doi:
-\href{https://doi.org/10.1098/rsbl.2011.1167}{10.1098/rsbl.2011.1167}
+Letters}, \emph{8}(4), 570--573.
+\url{https://doi.org/10.1098/rsbl.2011.1167}
 
@@
 subantarctic {Southwest Atlantic}. \emph{Polar Biology}, \emph{41}(4),
-733--741. doi:
-\href{https://doi.org/10.1007/s00300-017-2234-9}{10.1007/s00300-017-2234-9}
+733--741. \url{https://doi.org/10.1007/s00300-017-2234-9}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Marina2018a}{}}%
+Marina, T. I., Saravia, L. A., Cordone, G., Salinas, V., Doyle, S. R.,
+\& Momo, F. R. (2018). Architecture of marine food webs: {To} be or not
+be a {``small-world.''} \emph{PLOS ONE}, \emph{13}(5), e0198217.
+\url{https://doi.org/10.1371/journal.pone.0198217}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Marina2023}{}}%
+Marina, T. I., Saravia, L. A., \& Kortsch, S. (2023). \emph{New insights
+into the {Weddell Sea} ecosystem applying a quantitative network
+approach}. {EGUsphere preprint}.
+\url{https://doi.org/10.5194/egusphere-2022-1518}
 
@@
 Martinez, N. D. (1992). Constant {Connectance} in {Community Food Webs}.
-\emph{The American Naturalist}, \emph{139}(6), 1208--1218. doi:
-\href{https://doi.org/10.1086/285382}{10.1086/285382}
+\emph{The American Naturalist}, \emph{139}(6), 1208--1218.
+\url{https://doi.org/10.1086/285382}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Martinez1991}{}}%
+Martinez, N. D. (1991). Artifacts or {Attributes}? {Effects} of
+{Resolution} on the {Little Rock Lake Food Web}. \emph{Ecological
+Monographs}, \emph{61}(4), 367--392.
+\url{https://doi.org/10.2307/2937047}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Martinez1993}{}}%
+Martinez, N. D. (1993). Effects of {Resolution} on {Food Web Structure}.
+\emph{Oikos}, \emph{66}(3), 403--412.
+\url{https://doi.org/10.2307/3544934}
 
@@
 Circulation}. \emph{Journal of Geophysical Research: Oceans},
-\emph{124}(10), 6904--6926. doi:
-\href{https://doi.org/10.1029/2019JC015001}{10.1029/2019JC015001}
+\emph{124}(10), 6904--6926. \url{https://doi.org/10.1029/2019JC015001}
 
@@
 Protected Area Namuncurá} at {Burdwood Bank}: Exploring egg nursery
-grounds}. https://www.researchsquare.com. doi:
-\href{https://doi.org/10.21203/rs.3.rs-2247873/v1}{10.21203/rs.3.rs-2247873/v1}
+grounds}. https://www.researchsquare.com.
+\url{https://doi.org/10.21203/rs.3.rs-2247873/v1}
 
@@
 \emph{Proceedings of the Royal Society of London. Series B: Biological
-Sciences}, \emph{264}(1385), 1249--1254. doi:
-\href{https://doi.org/10.1098/rspb.1997.0172}{10.1098/rspb.1997.0172}
+Sciences}, \emph{264}(1385), 1249--1254.
+\url{https://doi.org/10.1098/rspb.1997.0172}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Montoya2002}{}}%
+Montoya, J. M., \& Solé, R. V. (2002). Small {World Patterns} in {Food
+Webs}. \emph{Journal of Theoretical Biology}, \emph{214}(3), 405--412.
+\url{https://doi.org/10.1006/jtbi.2001.2460}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Montoya2003}{}}%
+Montoya, J. M., \& Solé, R. V. (2003). Topological properties of food
+webs: From real data to community assembly models. \emph{Oikos},
+\emph{102}(3), 614--622.
+\url{https://doi.org/10.1034/j.1600-0706.2003.12031.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Neutel2002}{}}%
+Neutel, A.-M., Heesterbeek, J. A. P., \& de Ruiter, P. C. (2002).
+Stability in {Real Food Webs}: {Weak Links} in {Long Loops}.
+\emph{Science}, \emph{296}(5570), 1120--1123.
+\url{https://doi.org/10.1126/science.1068326}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Newman2003}{}}%
+Newman, M. E. J. (2003). The {Structure} and {Function} of {Complex
+Networks}. \emph{SIAM Review}, \emph{45}(2), 167--256.
+\url{https://doi.org/10.1137/S003614450342480}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Nilsson2016}{}}%
+Nilsson, K. A., \& McCann, K. S. (2016). Interaction strength
+revisited\textemdash clarifying the role of energy flux for food web
+stability. \emph{Theoretical Ecology}, \emph{9}(1), 59--71.
+\url{https://doi.org/10.1007/s12080-015-0282-8}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Padovani2021}{}}%
+Padovani, L. N., Álvarez, N., \& Farías, A. (2021). \emph{Alimentación
+de la sardina fueguina ({Sprattus} fuegensis) en la región patagónica
+austral durante la época reproductiva}. {INIDEP}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Padovani2012}{}}%
+Padovani, L. N., Viñas, M. D., Sánchez, F., \& Mianzan, H. (2012).
+Amphipod-supported food web: {Themisto} gaudichaudii, a key food
+resource for fishes in the southern {Patagonian Shelf}. \emph{Journal of
+Sea Research}, \emph{67}(1), 85--90.
+\url{https://doi.org/10.1016/j.seares.2011.10.007}
 
@@
 {Atlantic} waters with new data on the distribution of all species.
-\emph{Marine Biodiversity}, \emph{49}(2), 913--922. doi:
-\href{https://doi.org/10.1007/s12526-018-0876-7}{10.1007/s12526-018-0876-7}
+\emph{Marine Biodiversity}, \emph{49}(2), 913--922.
+\url{https://doi.org/10.1007/s12526-018-0876-7}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Pawar2012}{}}%
+Pawar, S., Dell, A. I., \& Van M. Savage. (2012). Dimensionality of
+consumer search space drives trophic interaction strengths.
+\emph{Nature}, \emph{486}, 485.
+\url{https://doi.org/10.1038/nature11131}
 
@@
 southwest {South Atlantic}. \emph{Deep Sea Research Part A.
-Oceanographic Research Papers}, \emph{36}(1), 1--16. doi:
-\href{https://doi.org/10.1016/0198-0149(89)90015-0}{10.1016/0198-0149(89)90015-0}
+Oceanographic Research Papers}, \emph{36}(1), 1--16.
+\url{https://doi.org/10.1016/0198-0149(89)90015-0}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Poisot2014}{}}%
+Poisot, T., \& Gravel, D. (2014). When is an ecological network complex?
+{Connectance} drives degree distribution and emerging network
+properties. \emph{PeerJ}, \emph{2}, e251.
+\url{https://doi.org/10.7717/peerj.251}
+
+\leavevmode\vadjust pre{\hypertarget{ref-RayaRey2022}{}}%
+Raya Rey, A. (2022). \emph{Food items of sea birds of the {Marine
+Protected Area Namuncurá} - {Banco Burdwood}}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Reta2014}{}}%
@@
 Actual} del {Conocimiento} y {Perspectivas}}. {INIDEP}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Riccialdelli2022}{}}%
+Riccialdelli, L. (2022). \emph{Feeding items of marine mammals of the
+{Marine Protected Area Namuncurá} - {Banco Burdwood}}.
 
@@
 assumption. \emph{Marine Ecology Progress Series}, \emph{655}, 1--27.
-doi: \href{https://doi.org/10.3354/meps13524}{10.3354/meps13524}
+\url{https://doi.org/10.3354/meps13524}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Roberts2017}{}}%
+Roberts, C. M., O'Leary, B. C., McCauley, D. J., Cury, P. M., Duarte, C.
+M., Lubchenco, J., Pauly, D., Sáenz-Arroyo, A., Sumaila, U. R., Wilson,
+R. W., Worm, B., \& Castilla, J. C. (2017). Marine reserves can mitigate
+and promote adaptation to climate change. \emph{Proceedings of the
+National Academy of Sciences}, \emph{114}(24), 6167--6175.
+\url{https://doi.org/10.1073/pnas.1701262114}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Rodriguez2022}{}}%
+Rodriguez, I. D., Marina, T. I., Schloss, I. R., \& Saravia, L. A.
+(2022). Marine food webs are more complex but less stable in
+sub-{Antarctic} ({Beagle Channel}, {Argentina}) than in {Antarctic}
+({Potter Cove}, {Antarctic Peninsula}) regions. \emph{Marine
+Environmental Research}, \emph{174}, 105561.
+\url{https://doi.org/10.1016/j.marenvres.2022.105561}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sala2018}{}}%
+Sala, E., Lubchenco, J., Grorud-Colvert, K., Novelli, C., Roberts, C.,
+\& Sumaila, U. R. (2018). Assessing real progress towards effective
+ocean protection. \emph{Marine Policy}, \emph{91}, 11--13.
+\url{https://doi.org/10.1016/j.marpol.2018.02.004}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Santana2013}{}}%
+Santana, C. N. de, Rozenfeld, A. F., Marquet, P. A., \& Duarte, C. M.
+(2013). Topological properties of polar food webs. \emph{Marine Ecology
+Progress Series}, \emph{474}, 15--26.
+\url{https://doi.org/10.3354/meps10073}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Saporiti2015}{}}%
+Saporiti, F., Bearhop, S., Vales, D. G., Silva, L., Zenteno, L.,
+Tavares, M., Crespo, E. A., \& Cardona, L. (2015). Latitudinal changes
+in the structure of marine food webs in the {Southwestern Atlantic
+Ocean}. \emph{Marine Ecology Progress Series}, \emph{538}, 23--34.
+\url{https://doi.org/10.3354/meps11464}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Schejter2019}{}}%
+Schejter, L., \& Bremec, C. S. (2019). Stony corals ({Anthozoa}:
+{Scleractinia}) of {Burdwood Bank} and neighbouring areas, {SW Atlantic
+Ocean}. \emph{Scientia Marina}, \emph{83}(3), 247--260.
+\url{https://doi.org/10.3989/scimar.04863.10A}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Schejter2020}{}}%
+Schejter, L., Genzano, G., Gaitán, E., Perez, C. D., \& Bremec, C. S.
+(2020). Benthic communities in the {Southwest Atlantic Ocean}:
+{Conservation} value of animal forests at the {Burdwood Bank} slope.
+\emph{Aquatic Conservation: Marine and Freshwater Ecosystems},
+\emph{30}(3), 426--439. \url{https://doi.org/10.1002/aqc.3265}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Schejter2016}{}}%
 Schejter, L., Rimondino, C., Chiesa, I., Díaz de Astarloa, J. M., Doti,
-B., Elías, R., \ldots{} Bremec, C. S. (2016). Namuncurá {Marine
-Protected Area}: An oceanic hot spot of benthic biodiversity at
-{Burdwood Bank}, {Argentina}. \emph{Polar Biology}, \emph{39}(12),
-2373--2386. doi:
-\href{https://doi.org/10.1007/s00300-016-1913-2}{10.1007/s00300-016-1913-2}
+B., Elías, R., Escolar, M., Genzano, G., López-Gappa, J., Tatián, M.,
+Zelaya, D. G., Cristobo, J., Perez, C. D., Cordeiro, R. T., \& Bremec,
+C. S. (2016). Namuncurá {Marine Protected Area}: An oceanic hot spot of
+benthic biodiversity at {Burdwood Bank}, {Argentina}. \emph{Polar
+Biology}, \emph{39}(12), 2373--2386.
+\url{https://doi.org/10.1007/s00300-016-1913-2}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Schejter2021}{}}%
+Schejter, \& Albano. (2021). Benthic communities at the marine protected
+area {Namuncurá}/{Burdwood} bank, {SW Atlantic Ocean}: Detection of
+vulnerable marine ecosystems and contributions to the assessment of the
+rezoning process. \emph{Polar Biology}, \emph{44}(10), 2023--2037.
+\url{https://doi.org/10.1007/s00300-021-02936-y}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Scotti2010}{}}%
+Scotti, M., \& Jordán, F. (2010). Relationships between centrality
+indices and trophic levels in food webs. \emph{Community Ecology},
+\emph{11}(1), 59--67. \url{https://doi.org/10.1556/ComEc.11.2010.1.9}
+
+\leavevmode\vadjust pre{\hypertarget{ref-MartinSirito2019}{}}%
+Sirito, M. (2019). \emph{Fauna asociada a corales ({Octocorallia}) e
+hidroides ({Hydrozoa}) del {Área Marina Protegida} {``{Namuncurá}''}
+({Banco Burdwood}) y zonas profundas adyacentes} {[}PhD thesis{]}.
+Universidad Nacional de Mar del Plata.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Smith-Ramesh2017}{}}%
+Smith-Ramesh, L. M., Moore, A. C., \& Schmitz, O. J. (2017). Global
+synthesis suggests that food web connectance correlates to invasion
+resistance. \emph{Global Change Biology}, \emph{23}(2), 465--473.
+\url{https://doi.org/10.1111/gcb.13460}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sole2001}{}}%
+Solé, R. V., \& Montoya, M. (2001). Complexity and fragility in
+ecological networks. \emph{Proceedings of the Royal Society of London.
+Series B: Biological Sciences}, \emph{268}(1480), 2039--2045.
+\url{https://doi.org/10.1098/rspb.2001.1767}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Spinelli2020}{}}%
+Spinelli, M. L., Malits, A., García Alonso, V. A., Martín, J., \&
+Capitanio, F. L. (2020). Spatial gradients of spring zooplankton
+assemblages at the open ocean sub-{Antarctic Namuncurá Marine Protected
+Area}/{Burdwood Bank}, {SW Atlantic Ocean}. \emph{Journal of Marine
+Systems}, \emph{210}, 103398.
+\url{https://doi.org/10.1016/j.jmarsys.2020.103398}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Stouffer2010}{}}%
+Stouffer, D. B., \& Bascompte, J. (2010). Understanding food-web
+persistence from local to global scales. \emph{Ecology Letters},
+\emph{13}(2), 154--161.
+\url{https://doi.org/10.1111/j.1461-0248.2009.01407.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Stouffer2005}{}}%
+Stouffer, D. B., Camacho, J., Guimerà, R., Ng, C. A., \& Nunes Amaral,
+L. A. (2005). Quantitative {Patterns} in the {Structure} of {Model} and
+{Empirical Food Webs}. \emph{Ecology}, \emph{86}(5), 1301--1311.
+\url{https://doi.org/10.1890/04-0957}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Strogatz2001}{}}%
+Strogatz, S. H. (2001). Exploring complex networks. \emph{Nature},
+\emph{410}(6825), 268--276. \url{https://doi.org/10.1038/35065725}
 
@@
 Team, R. C. (2022). \emph{R: {A Language} and {Environment} for
-{Statistical Computing}}. {Vienna, Austria}: R Foundation for
-Statistical Computing.
+{Statistical Computing}}. R Foundation for Statistical Computing.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Thebault2010}{}}%
+Thébault, E., \& Fontaine, C. (2010). Stability of {Ecological
+Communities} and the {Architecture} of {Mutualistic} and {Trophic
+Networks}. \emph{Science}, \emph{329}(5993), 853--856.
+\url{https://doi.org/10.1126/science.1188321}
 
@@
 Tilman, D. (1996). Biodiversity: {Population Versus Ecosystem
-Stability}. \emph{Ecology}, \emph{77}(2), 350--363. doi:
-\href{https://doi.org/10.2307/2265614}{10.2307/2265614}
+Stability}. \emph{Ecology}, \emph{77}(2), 350--363.
+\url{https://doi.org/10.2307/2265614}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Trathan2021}{}}%
+Trathan, P. N., Fielding, S., Hollyman, P. R., Murphy, E. J.,
+Warwick-Evans, V., \& Collins, M. A. (2021). Enhancing the ecosystem
+approach for the fishery for {Antarctic} krill within the complex,
+variable, and changing ecosystem at {South Georgia}. \emph{ICES Journal
+of Marine Science}, \emph{78}(6), 2065--2081.
+\url{https://doi.org/10.1093/icesjms/fsab092}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Troccoli2020}{}}%
+Troccoli, G. H., Aguilar, E., Martínez, P. A., \& Belleggia, M. (2020).
+The diet of the {Patagonian} toothfish {Dissostichus} eleginoides, a
+deep-sea top predator off {Southwest Atlantic Ocean}. \emph{Polar
+Biology}, \emph{43}(10), 1595--1604.
+\url{https://doi.org/10.1007/s00300-020-02730-2}
 
@@
 {``small-world''} networks. \emph{Nature}, \emph{393}(6684), 440--442.
-doi: \href{https://doi.org/10.1038/30918}{10.1038/30918}
+\url{https://doi.org/10.1038/30918}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Williams2002}{}}%
+Williams, R. J., Berlow, E. L., Dunne, J. A., Barabási, A.-L., \&
+Martinez, N. D. (2002). Two degrees of separation in complex food webs.
+\emph{Proceedings of the National Academy of Sciences}, \emph{99}(20),
+12913--12916. \url{https://doi.org/10.1073/pnas.192448799}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Woodward2005}{}}%
+Woodward, G., Ebenman, B., Emmerson, M., Montoya, J. M., Olesen, J. M.,
+Valido, A., \& Warren, P. H. (2005). Body size in ecological networks.
+\emph{Trends in Ecology \& Evolution}, \emph{20}(7), 402--409.
+\url{https://doi.org/10.1016/j.tree.2005.04.005}
 

### 2023-03-28 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Continue w/Abstract

@@
 abstract: |
-  The abstract goes here.
+  Globally, the total area of the world ocean designated under marine protection has increased in the recent decades.
+The majority of these Marine Protected Areas (MPAs) focus on the presence of particularly vulnerable, keystone, or charismatic species, the presence of large numbers (or proportions) of endemic species, and/or the presence of high biodiversity across taxonomic levels.
+In the sub-Antarctic region, the level of ocean protection is mainly associated to oceanic islands, except for the MPAs Namuncurá - Banco Burdwood I and II (MPA N-BB), which are associated to a submarine plateau and its southern adjacent deep slope region, respectively.
+Here we present the first detailed analysis of the network of predator-prey interactions (food web) for the MPA N-BB ecosystem.
+We applied a network approach with the objective of characterize the food web in terms of complexity and structure, and identify the species' role in such framework.
 

### 2023-03-29 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Version sent to co-authors (?)

@@
   Globally, the total area of the world ocean designated under marine protection has increased in the recent decades.
-The majority of these Marine Protected Areas (MPAs) focus on the presence of particularly vulnerable, keystone, or charismatic species, the presence of large numbers (or proportions) of endemic species, and/or the presence of high biodiversity across taxonomic levels.
-In the sub-Antarctic region, the level of ocean protection is mainly associated to oceanic islands, except for the MPAs Namuncurá - Banco Burdwood I and II (MPA N-BB), which are associated to a submarine plateau and its southern adjacent deep slope region, respectively.
+The majority of these Marine Protected Areas (MPAs) focus on the presence of particularly vulnerable, keystone, or charismatic species, the presence of large numbers of endemic species, and/or the presence of high biodiversity across taxonomic levels.
+In the sub-Antarctic region, the level of ocean protection is mainly associated to oceanic islands, except for the MPAs Namuncurá - Banco Burdwood I and II (MPA N-BB, 53º–55ºS and 56º–62ºW), which are associated to a submarine plateau and its southern adjacent deep slope region, respectively.
 Here we present the first detailed analysis of the network of predator-prey interactions (food web) for the MPA N-BB ecosystem.
-We applied a network approach with the objective of characterize the food web in terms of complexity and structure, and identify the species' role in such framework.
+We applied a network approach with the objective of characterizing the food web in terms of complexity and structure, and identifying the species' role in such framework.
+In terms of complexity, the MPA N-BB food web consisted of 1778 predator-prey interactions and 379 species, with a link density of 4.69 and a connectance of 0.01.
+In terms of structure, almost half of the consumers were omnivores (0.48), and the network displayed a small-world pattern.
+All this suggest that the ecosystem might be fragile to external perturbations targeting highly connected species, although structural properties might provide resilience and resistance with the final outcome of a rearrange structure maintaining their functions.
+On the other hand, we identified several species as important in terms of different aspects of trophic structure and functioning, and response to perturbations.
+We suggest that generalist species, mostly fishes, play a crucial role in the ecosystem's bentho-pelagic coupling process.
+In addition, we propose that other species rather than the longtail southern cod *Patagonotothen ramsayi* and the Fueguian sprat *Sprattus fuegensis* should be considered as relevant energy transfers for the ecosystem.
+Finally, we argue that it is the diversity of species, representing the benthic and pelagic habitats, what maintains the connectivity of the food web against perturbations, therefore contributing to the structure and stability of the ecosystem.
 

### 2023-03-29 MS_ToSubmit/MS_Burdwood_foodweb.tex
Version sent to co-authors (?)

@@
   \begin{abstract}
-  The abstract goes here.
+  Globally, the total area of the world ocean designated under marine
+  protection has increased in the recent decades. The majority of these
+  Marine Protected Areas (MPAs) focus on the presence of particularly
+  vulnerable, keystone, or charismatic species, the presence of large
+  numbers of endemic species, and/or the presence of high biodiversity
+  across taxonomic levels. In the sub-Antarctic region, the level of
+  ocean protection is mainly associated to oceanic islands, except for
+  the MPAs Namuncurá - Banco Burdwood I and II (MPA N-BB, 53º--55ºS and
+  56º--62ºW), which are associated to a submarine plateau and its
+  southern adjacent deep slope region, respectively. Here we present the
+  first detailed analysis of the network of predator-prey interactions
+  (food web) for the MPA N-BB ecosystem. We applied a network approach
+  with the objective of characterizing the food web in terms of
+  complexity and structure, and identifying the species' role in such
+  framework. In terms of complexity, the MPA N-BB food web consisted of
+  1778 predator-prey interactions and 379 species, with a link density
+  of 4.69 and a connectance of 0.01. In terms of structure, almost half
+  of the consumers were omnivores (0.48), and the network displayed a
+  small-world pattern. All this suggest that the ecosystem might be
+  fragile to external perturbations targeting highly connected species,
+  although structural properties might provide resilience and resistance
+  with the final outcome of a rearrange structure maintaining their
+  functions. On the other hand, we identified several species as
+  important in terms of different aspects of trophic structure and
+  functioning, and response to perturbations. We suggest that generalist
+  species, mostly fishes, play a crucial role in the ecosystem's
+  bentho-pelagic coupling process. In addition, we propose that other
+  species rather than the longtail southern cod \emph{Patagonotothen
+  ramsayi} and the Fueguian sprat \emph{Sprattus fuegensis} should be
+  considered as relevant energy transfers for the ecosystem. Finally, we
+  argue that it is the diversity of species, representing the benthic
+  and pelagic habitats, what maintains the connectivity of the food web
+  against perturbations, therefore contributing to the structure and
+  stability of the ecosystem.
   \end{abstract}

### 2023-03-30 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Add co-authors and Acknowledgements

@@
     email: tomasimarina@gmail.com
-  - name: Irene R. Schloss^a^^,^^b^
+  - name: Irene R. Schloss^a^^,^^b^^,^^c^
   - name: Luciana Riccialdelli^a^
-  - name: To be continued(?)^c^
+  - name: Juan Martín Díaz de Astarloa^d^
+  - name: Cintia Fraysse^a^
+  - name: Gustavo A. Lovrich^a^
+  - name: Andrea Raya Rey^a^^,^^c^^,^^e^
+  - name: Mariela L. Spinelli^f^
+  - name: Diego Urteaga^g^
+
 address:
@@
   - code: 3
-    address: INIDEP, UBA-CONICET, IIMyC-CONICET, MACN-CONICET, UNC-CONICET
+    address: Instituto de Ciencias Polares, Ambiente y Recursos Naturales (ICPA), Universidad de Tierra del Fuego (UNTDF), Argentina
+  - code: 4
+    address: Instituto de Investigaciones Marinas y Costeras (IIMYC), Universidad Nacional de Mar del Plata-CONICET, Argentina
+  - code: 5
+    address: Wildlife Conservation Society, Argentina
+  - code: 6
+    address: Instituto de Biodiversidad y Biología Experimental y Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, Argentina
+  - code: 7
+    address: Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina
+
 abstract: |
@@
 
-We are indebted to all those experts of the working group 'Banco Burdwood' who humbly provided their knowledge to enhance the quality of the present research (add names if necessary), and special thanks to GA Lovrich the Scientific Coordinator of the MPA Namuncurá-Burdwood Bank and the MPA N-BB Administrators.
+We are indebted to all those experts of the working group 'Banco Burdwood' who humbly provided their knowledge to enhance the quality of the present research.
+It is worth to mention the following researchers: Daniel O.
+Bruno (CADIC-CONICET, Argentina), Sandra Gordillo (IDACOR-CONICET; Universidad Nacional de Córdoba, Argentina), Mariano I.
+Martinez (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina), Laura Schejter (INIDEP-CONICET),...
+Special thanks to G.A. Lovrich the Scientific Coordinator of the MPA Namuncurá-Burdwood Bank and the MPA N-BB Administrators.
 This study was funded by Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617), Argentina.

### 2023-03-30 MS_ToSubmit/MS_Burdwood_foodweb.tex
Add co-authors and Acknowledgements

@@
    \ead{tomasimarina@gmail.com} 
-    \author[]{Irene R. Schloss\textsuperscript{a,b}%
+    \author[]{Irene R. Schloss\textsuperscript{a,b,c}%
   %
@@
 
-    \author[]{To be continued(?)\textsuperscript{c}%
+    \author[]{Juan Martín Díaz de Astarloa\textsuperscript{d}%
+  %
+  }
+
+    \author[]{Cintia Fraysse\textsuperscript{a}%
+  %
+  }
+
+    \author[]{Gustavo A. Lovrich\textsuperscript{a}%
+  %
+  }
+
+    \author[]{Andrea Raya Rey\textsuperscript{a,c,e}%
+  %
+  }
+
+    \author[]{Mariela L. Spinelli\textsuperscript{f}%
+  %
+  }
+
+    \author[]{Diego Urteaga\textsuperscript{g}%
   %
@@
     \affiliation[2]{Instituto Antartico Argentino (IAA), Argentina}
-    \affiliation[3]{INIDEP, UBA-CONICET, IIMyC-CONICET, MACN-CONICET,
-UNC-CONICET}
+    \affiliation[3]{Instituto de Ciencias Polares, Ambiente y Recursos
+Naturales (ICPA), Universidad de Tierra del Fuego (UNTDF), Argentina}
+    \affiliation[4]{Instituto de Investigaciones Marinas y Costeras
+(IIMYC), Universidad Nacional de Mar del Plata-CONICET, Argentina}
+    \affiliation[5]{Wildlife Conservation Society, Argentina}
+    \affiliation[6]{Instituto de Biodiversidad y Biología Experimental y
+Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, Argentina}
+    \affiliation[7]{Museo Argentino de Ciencias Naturales ``Bernardino
+Rivadavia'', Argentina}
     \cortext[cor1]{Corresponding author}
@@
 Burdwood' who humbly provided their knowledge to enhance the quality of
-the present research (add names if necessary), and special thanks to GA
-Lovrich the Scientific Coordinator of the MPA Namuncurá-Burdwood Bank
-and the MPA N-BB Administrators. This study was funded by Consejo
-Nacional de Investigaciones Científicas y Técnicas (CONICET) and Agencia
-Nacional de Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617),
-Argentina. This work is contribution no. XX of the MPA Namuncurá (Law
-26.875).
+the present research. It is worth to mention the following researchers:
+Daniel O. Bruno (CADIC-CONICET, Argentina), Sandra Gordillo
+(IDACOR-CONICET; Universidad Nacional de Córdoba, Argentina), Mariano I.
+Martinez (Museo Argentino de Ciencias Naturales ``Bernardino
+Rivadavia'', Argentina), Laura Schejter (INIDEP-CONICET),\ldots{}
+Special thanks to G.A. Lovrich the Scientific Coordinator of the MPA
+Namuncurá-Burdwood Bank and the MPA N-BB Administrators. This study was
+funded by Consejo Nacional de Investigaciones Científicas y Técnicas
+(CONICET) and Agencia Nacional de Promoción Científica y Tecnológica
+(PICT 2020-SERIEA-01617), Argentina. This work is contribution no. XX of
+the MPA Namuncurá (Law 26.875).
 

### 2023-04-01 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Add co-authors

@@
   - name: Diego Urteaga^g^
+  - name: Marcos Tatián^h^^,^^i^
 
@@
     address: Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina
+  - code: 8
+    address: Instituto de Diversidad y Ecología Animal (IDEA-CONICET)
+  - code: 9
+    address: Facultad de Ciencias Exactas, Físicas y Naturales, Universidad Nacional de Córdoba (UNC), Argentina
 

### 2023-04-04 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Add co-authors

@@
   - name: Luciana Riccialdelli^a^
+  - name: Fabiana L. Capitanio^f^
+  - name: Sergio M. Delpiani^d^
   - name: Juan Martín Díaz de Astarloa^d^
@@
   - name: Marcos Tatián^h^^,^^i^
+  - name: Virginia A. García Alonso^f^
 

### 2023-04-06 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Add co-authors

@@
   - name: Virginia A. García Alonso^f^
+  - name: Claudia C. Boy^a^
+  - name: Daniel O. Bruno^a^^,^^c^
 
@@
 We are indebted to all those experts of the working group 'Banco Burdwood' who humbly provided their knowledge to enhance the quality of the present research.
-It is worth to mention the following researchers: Daniel O.
-Bruno (CADIC-CONICET, Argentina), Sandra Gordillo (IDACOR-CONICET; Universidad Nacional de Córdoba, Argentina), Mariano I.
+It is worth to mention the following researchers: Sandra Gordillo (IDACOR-CONICET; Universidad Nacional de Córdoba, Argentina), Mariano I.
 Martinez (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina), Laura Schejter (INIDEP-CONICET),...

### 2023-04-06 MS_ToSubmit/MS_Burdwood_foodweb.tex
Add co-authors

@@
 
+    \author[]{Fabiana L. Capitanio\textsuperscript{f}%
+  %
+  }
+
+    \author[]{Sergio M. Delpiani\textsuperscript{d}%
+  %
+  }
+
     \author[]{Juan Martín Díaz de Astarloa\textsuperscript{d}%
@@
     \author[]{Diego Urteaga\textsuperscript{g}%
+  %
+  }
+
+    \author[]{Marcos Tatián\textsuperscript{h,i}%
+  %
+  }
+
+    \author[]{Virginia A. García Alonso\textsuperscript{f}%
+  %
+  }
+
+    \author[]{Claudia C. Boy\textsuperscript{a}%
+  %
+  }
+
+    \author[]{Daniel O. Bruno\textsuperscript{a,c}%
   %
@@
 Rivadavia'', Argentina}
+    \affiliation[8]{Instituto de Diversidad y Ecología Animal
+(IDEA-CONICET)}
+    \affiliation[9]{Facultad de Ciencias Exactas, Físicas y Naturales,
+Universidad Nacional de Córdoba (UNC), Argentina}
     \cortext[cor1]{Corresponding author}
@@
 the present research. It is worth to mention the following researchers:
-Daniel O. Bruno (CADIC-CONICET, Argentina), Sandra Gordillo
-(IDACOR-CONICET; Universidad Nacional de Córdoba, Argentina), Mariano I.
-Martinez (Museo Argentino de Ciencias Naturales ``Bernardino
-Rivadavia'', Argentina), Laura Schejter (INIDEP-CONICET),\ldots{}
-Special thanks to G.A. Lovrich the Scientific Coordinator of the MPA
-Namuncurá-Burdwood Bank and the MPA N-BB Administrators. This study was
-funded by Consejo Nacional de Investigaciones Científicas y Técnicas
-(CONICET) and Agencia Nacional de Promoción Científica y Tecnológica
-(PICT 2020-SERIEA-01617), Argentina. This work is contribution no. XX of
-the MPA Namuncurá (Law 26.875).
+Sandra Gordillo (IDACOR-CONICET; Universidad Nacional de Córdoba,
+Argentina), Mariano I. Martinez (Museo Argentino de Ciencias Naturales
+``Bernardino Rivadavia'', Argentina), Laura Schejter
+(INIDEP-CONICET),\ldots{} Special thanks to G.A. Lovrich the Scientific
+Coordinator of the MPA Namuncurá-Burdwood Bank and the MPA N-BB
+Administrators. This study was funded by Consejo Nacional de
+Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de
+Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617), Argentina.
+This work is contribution no. XX of the MPA Namuncurá (Law 26.875).
 

### 2023-04-21 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Added Schejter, Astarloa & Capitanio

@@
 ---
-title: The complex network of trophic interactions in a subAntarctic Marine Protected
+title: The complex network of trophic interactions in a subAntarctic oceanic Marine Protected
   Area
@@
 Interestingly, the case of the MPAs Namuncurá - Banco Burdwood I and II (MPA N-BB), which is the focus of this work, is unique since these MPAs are associated to a submarine plateau and its southern adjacent deep slope region, respectively [@Falabella2017].
-Added to this, such MPAs are part of a network of protected areas in the sub-Antarctic (jointly with MPA Yaganes), that aims to protect and strengthen the functioning of this southern region to maintain global ocean health.
+In addition, such MPAs are part of a network of protected areas in the sub-Antarctic (jointly with MPA Yaganes), that aims to protect and strengthen the functioning of this southern region to maintain global ocean health.
 
@@
 Indeed, the MPA N-BB was created to protect a sensitive and biodiverse benthic habitat that was barely known [@Schejter2016; @Falabella2017].
-The benthic community is featured by a high biomass of vulnerable and fragile species (mainly Poriferaand Cnidaria) that meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResources2009].
-Also, it provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge and nursery area [@GarciaAlonso2018; @Delpiani2020; @Troccoli2020].
+The benthic community is featured by a high biomass of vulnerable and fragile species (mainly Porifera and Cnidaria) that meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResources2009].
+Also, it provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge and nursery area [@GarciaAlonso2018; @Delpiani2020; @Troccoli2020; @CovattiAle2022; @Fischer2022; @Florencia2023].
 The maintenance of this singular community is related to local and regional oceanographic processes, including the circulation of the rich Malvinas (Falkland) current in the area [@Piola1989; @Guerrero1999] and the upwelling and mixing phenomena [@Matano2019].
@@
 High-latitude marine ecosystems, such as the MPA N-BB, are characterized by an unexpected complexity in terms of biodiversity and ecological interactions [@Day2013; @Kortsch2019; @Cordone2020; @Trathan2021].
-Although there is a robust knowledge about the complexity considering the richness of the benthic and plankton communities in the MPA N-BB ecosystem [@Schejter2016; @Guinder2020; @Schejter2020; @APN2022], there is a need for a better understanding of species interactions' complexity and structure.
+Although there is a robust knowledge about the complexity considering the richness of the benthic and plankton communities in the MPA N-BB ecosystem [@Schejter2016; @Guinder2020; @Schejter2020; @APN2022], a better understanding of species interactions' complexity and structure is needed.
 This aspect can be tackled by analyzing one of the most-frequent relationships occurring between species: the predator-prey interaction [@Bascompte2009].
@@
 
-In order to build the network of predator-prey interactions we reviewed more than 150 references considering published articles, databases and doctoral theses.
+In order to build the network of predator-prey interactions we reviewed more than 150 references considering published articles, Ph.D.
+theses, public databases, and reports belonging to xx research cruises conducted in the MPAs N-BB I and II.
+Here it is important to note that the sampling effort was greater in the MPA N-BB I.
 Furthermore, we took into account personal communications from experts belonging to the working group of the study area (https://www.pampazul.gob.ar/tag/banco-burdwood/).
-The diversity of the expertise of the authors contributing to the present study was a key factor in enhancing the quality of the network, and inherently improved the network representation.
+The diversity of the authors' expertise contributing to the present study was a key factor in enhancing the quality of the network, and inherently improved the network representation.
 A list of the references used to build the network is presented in Supplementary Material (Table S1).
@@
 In some cases, we collapsed species when taxa shared the same set of predators and prey (trophic similarity, @Martinez1991), one of the aggregation methods that better preserves food web functional properties [@Gauzens2013].
+In addition, for endemic species (e.g.
+bryozoan *Burdwoodipora paguricola*) and other species with no trophic studies so far, we inferred their feeding interactions applying a conservative approach that assumes that the set of prey and predators are at some point preserved in time.
+In those cases we gathered information from upper taxonomic levels (i.e.
+Genus, Family, Order, Class, Phylum) as a good proxy variable [@Morales2015; @Pomeranz2018].
 Details about this can be found in Supplementary Material (Table S2).
@@
 The distribution of prey among predators showed that most of the consumers fed on a low number of prey whereas few of them had multiple preys (Figure 3B).
-These were the top-five predators in number of prey: *Patagonotothen guntheri* (Notothenioid fish, 52 prey), *Patagonotothen ramsayi* (Notothenioid fish, 50 prey), *Dissostichus eleginoides* (Notothenioid fish, 30 prey), *Bathyraja brachyurops* (Chondrichthyan, 30 prey), and *Bathyraja griseocauda* (Chondrichthyan, 28 prey).
+These were the top-five predators in number of prey: yellowfin notothen *Patagonotothen guntheri* (Notothenioid fish, 52 prey), rock cod *Patagonotothen ramsayi* (Notothenioid fish, 50 prey), Patagonian toothfish *Dissostichus eleginoides* (Notothenioid fish, 30 prey), broad nose skate *Bathyraja brachyurops* (Chondrichthyan, 30 prey), and graytail skate *Bathyraja griseocauda* (Chondrichthyan, 28 prey).
 Following the same distribution pattern, few prey presented multiple predators (Figure 3C).
@@
 The following were the five species with a network connector role: Detritus, Diatoms (benthic, centric and pennate), and *Patagonotothen ramsayi*.
-The 35 species with a module connector role represent these functional groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Cnidaria, Cumacea, Decapoda, Detritus, Diatoms, Dinoflagellates, Echinodermata, Fish (bentho-pelagic, demersal, chondrichthyes), Foraminifera, Polychaeta, Porifera, Pycnogonida, Sea birds, and Zooplankton (see Supplementary Material Table S3 for the identity of the species).
+The 35 species with a module connector role represent these functional groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Cnidaria, Cumacea, Decapoda, Detritus, Diatoms, Dinoflagellates, Echinodermata, Fish (bentho-pelagic, demersal, Chondrichthyes), Foraminifera, Polychaeta, Porifera, Pycnogonida, Sea birds, and Zooplankton (see Supplementary Material Table S3 for the identity of the species).
 
@@
 The food web of the MPA Namuncurá - Banco Burdwood ecosystem analysed in this study is one of the most highly-resolved networks of trophic interactions ever studied not only for a high-latitude marine ecosystem but also for a marine protected area worldwide.
-It is of paramount importance to consider the complexity of species interactions in order to gain insights into the structure and functioning of the ecosystem, since the aggregation of species might mask food web properties and/or produce type II errors (false positive) [@Martinez1993; @Gauzens2013].
+It is of paramount importance to consider the complexity of species interactions in order to gain insights into the structure and functioning of the ecosystem, since the aggregation of species might mask food web properties and produce type II errors (false positive) [@Martinez1993; @Gauzens2013].
 
@@
 In this sense, empirical analyses support the notion that highly-connected ecological networks are robust against external perturbations such as the introduction of new (e.g., invasive) species [@Smith-Ramesh2017] as well as species removal (e.g., local extinction) [@Dunne2002; @Montoya2003].
-The connectance of the food web of the MPA Namuncurá - Banco Burdwood (0.01) is one of the lowest reported so far for these regions; in particular, it appears to be five times lower than that of Beagle Channel, an adjacent area [@Rodriguez2022].
+The connectance of the food web of the MPA Namuncurá - Banco Burdwood (0.01) is one of the lowest reported so far for these regions; in particular, it appears to be five times lower than that of Beagle Channel, an adjacent coastal area [@Rodriguez2022].
 
@@
 This is based on the fact that omnivores are species able to adapt faster and to a wider range of environmental conditions by changing their foraging habits to feed on the most abundant prey [@Fagan1997].
-Furthermore, omnivory can be analysed from the interaction point of view: theoretical studies have identified omnivorous interactions as a possible candidate for a keystone interaction, sensu @Kadoya2018, highlighting the importance of omnivory inn stabilizing food web dynamics [@McCann1997; @Neutel2002].
+Furthermore, omnivory can be analysed from the interaction point of view: theoretical studies have identified omnivorous interactions as a possible candidate for a keystone interaction, sensu @Kadoya2018, highlighting the importance of omnivory in stabilizing food web dynamics [@McCann1997; @Neutel2002].
 The high proportion of omnivory in the food web of the MPA N-BB suggests that the network might be robust to variations in prey abundances, which could increase food web's persistence and stability [@Stouffer2010].
 
-To resume, the food web of the MPA Namuncurá - Banco Burdwood presents a combination of network properties that make it unique in terms of network resolution, complexity, and structural pattern.
-All this suggest that the ecosystem might be fragile to external perturbations targeting highly connected species.
+In summary, the food web of the MPA Namuncurá - Banco Burdwood presents a combination of network properties that make it unique in terms of network resolution, complexity, and structural pattern.
+All this suggests that the ecosystem might be fragile to external perturbations targeting highly connected species.
 However, structural properties might provide resilience and resistance with the final outcome of a rearrange structure maintaining their functions.
@@
 We have identified that the majority of the consumers in the food web of the MPA N-BB either has a narrow diet or are specialists, while few present a broad diet.
-The most evident generalist species are *Patagonotothen guntheri*, *P.
-ramsayi*, *Dissostichus eleginoides*, *Bathyraja brachyurops*, and *B.
-griseocauda*, with more than 25 potential prey.
+The most evident generalist species are *Patagonotothen guntheri* [@CovattiAle2022], *P.
+ramsayi* [@Fischer2022], *Dissostichus eleginoides* [@Troccoli2020], *Bathyraja brachyurops* [@Bellegia2008], and *B.
+griseocauda* [@Bellegia2014], with more than 25 potential prey.
 Since these species present mid-trophic positions in the food web (3-4), acting as predator and prey, they might be important links between lower and higher trophic levels.
-This is in agreement with the sole analysis, using stable isotopes, that exists so far for the trophic structure of the MPA N-BB [@Riccialdelli2020], and resembles other high-latitude marine systems of the Southwest Atlantic and Arctic regions [@Arkhipkin2013; @Kortsch2019].
+This is in agreement with the sole analysis, using stable isotopes, that exists so far for the trophic structure of the MPA N-BB [@Riccialdelli2020], and resembles other high-latitude marine systems of the Southwest Atlantic and Antarctic regions [@Arkhipkin2013; @Marina2018].
 The importance of these particular generalist species also arises since they feed on the benthic and pelagic habitats [@Troccoli2020; @CovattiAle2022; @Fischer2022], linking these realms and contributing to the vertical carbon flow.
@@
 
-In construction...
+Caveats:
+The food web studied in the present work might be more representative of the MPA Namuncurá - Banco Burdwood I ecosystem, which comprises the shallow submarine plateau called Burdwood Bank.
+This is related to the sampling effort that was conducted during the research cruises in the former MPA compared to the MPA N-BB II (i.e.
+deep flanks to the south).
+As a consequence most of the data we used to build the network comes from studies performed in the MPA N-BB I.
+Despite this fact, we decided to build the food web considering both MPAs due to the tight oceanographic and ecological connection that exists among them [references in @APN2022].
 
-Caveats:
+It's worth mentioning that we did not consider quantitative data (i.e.
+abundance, biomass) to assess the species' role in the food web.
+Although there exists such data for some species of the MPA N-BB [@Schejter2021], it would not be possible to incorporate it in the food web framework described here due to a taxonomical resolution mismatch.
+In this regard, we should mention the case of *Zygochlamys patagonica* (Bivalvia) that is highlighted by our species-level analyses though it has been found in low abundances in the area [@Schejter2021].
+
+Some species of sessile suspension feeders in high-latitude marine ecosystems, such as sponges, ascidians and octocorals, avoid predation by producing secondary metabolites that function as a chemical defense [@NunezPons2010; @Moles2015; @Prieto2022].
+Although this was not reported at the MPA N-BB, there are few studies that reported it other locations in species that were found in the MPA N-BB [@RojoDeAlmeida2010].
+Thus, the interactions that we considered between these species and their predators should be taken with caution.
 
@@
 
-Perspectives:
+These are the perspectives that we suggest should be considered to improve our knowledge regarding the structure, functioning and stability of the MPA N-BB:
 
-Incorporate habitat heterogeneity, since benthic community in the BB and deep flanks is different [@Schejter2021].
+* Incorporate habitat heterogeneity, since benthic community in the BB and deep flanks is different [@Schejter2021]. El caso de las ascidias (Tatián)
+
 This might lead to distinct food web properties, hence differences in ecosystem functioning and response to anthropogenic and environmental perturbations.
@@
 
-Simulate perturbations on food web and target species: mercury transfer, microplastic pollution, fisheries.
+* Incorporate species traits, like body size and mass, which are known to be important drivers in predator-prey interactions.
+
+* Simulate perturbations on food web and target species: mercury transfer, microplastic pollution, fisheries.
 @Cossi2021; @DiMauro2022; @Fioramonti2022
 
-Estimation of interaction strength considering species and interaction traits (i.e.
+* Estimation of interaction strength considering species and interaction traits (i.e.
 body size, body mass, interaction dimensionality) to gain insights into food web stability and response to anthropogenic and environmental perturbations.
@@
 It is worth to mention the following researchers: Sandra Gordillo (IDACOR-CONICET; Universidad Nacional de Córdoba, Argentina), Mariano I.
-Martinez (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina), Laura Schejter (INIDEP-CONICET),...
+Martinez (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina), Sofía L.
+Callá (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina),...
 Special thanks to G.A. Lovrich the Scientific Coordinator of the MPA Namuncurá-Burdwood Bank and the MPA N-BB Administrators.

### 2023-04-21 MS_ToSubmit/SupMaterial.Rmd
Version sent to co-authors (?)
Added Schejter, Astarloa & Capitanio

@@
 title: "Supplementary material for 'The complex network of trophic interactions in a subAntarctic Marine Protected Area'"
-author: "Tomás I. Marina, Irene R. Schloss and Luciana Riccialdelli"
+author: "Tomás I. Marina, Irene R. Schloss, Luciana Riccialdelli, To be continued"
 output: pdf_document
@@
 Not recorded", "Cirripedia") ~ "",
-                                 Species == "Campylaspis_spp" ~ "Aggregated: Campylaspis_frigida y Campylaspis_bacescui",
-                                 Species == "Ophiactis_sp" ~ "Aggregated: Ophiactis_asperula y Ophiactis_spp",
-                                 Species == "Brachiopoda_spp" ~ "Aggregated: Magellania_venosa, Liothyrella_uva y Terebratella_dorsata",
+                                 Species == "Campylaspis_spp" ~ "Aggregated: Campylaspis_frigida & Campylaspis_bacescui",
+                                 Species == "Ophiactis_sp" ~ "Aggregated: Ophiactis_asperula & Ophiactis_spp",
+                                 Species == "Brachiopoda_spp" ~ "Aggregated: Magellania_venosa, Liothyrella_uva & Terebratella_dorsata",
+                                 Species == "Enteroctopodidae" ~ "Aggregated: Enteroctopus_megalocyathus & Muusoctopus_longibrachus",
                                  TRUE ~ Observation),
@@
                                Species == "Campylaspis_spp" ~ "Doti_etal_2020",
-                               Species == "Brachiopoda_spp" ~ "Schejter_etal_2016", TRUE ~ Reference),
+                               Species == "Brachiopoda_spp" ~ "Schejter_etal_2016", 
+                               Species == "Salpa_thompsoni" ~ "Capitanio_pers.com.",
+                               TRUE ~ Reference),
          FunctionalGroup = case_when(Species == "Campylaspis_spp" ~ "Cumacea",
@@
                               Species %in% c("Detritus","Necromass") ~ "NA",
-                              Species %in% c("Bacteria","Foraminifera") ~ "Phylum",
-                              Species %in% c("Calcarea","Copepodite","Hexactinellida") ~ "Class",
+                              Species == "Foraminifera" ~ "Phylum",
+                              Species == "Bacteria" ~ "Domain",
+                              Species %in% c("Calcarea","Hexactinellida") ~ "Class",
                               Species %in% c("Halichondrida","Haplosclerida","Poecilosclerida","Tetractinellida") ~ "Order",
+                              Species %in% ("Copepodite","Larvae_Fish","Larvae_Nauplii","Eggs_Fish") ~ "Ontogenetic stage",
                               TRUE ~ "Other")) %>%  
@@
 # Table 2. List of species
-knitr::kable(sp_list, format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Taxonomy","Group","Reference","Link","Observation"), caption = "List of species for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
+knitr::kable(sp_list, format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Taxonomy","Group","Reference","Link","Observation"), caption = "List of species for the food web of the Marine Protected Areas Namuncurá - Banco Burdwood I and II ecosystem.
 Alphabetically ordered by species.") %>%

### 2023-04-22 MS_ToSubmit/SupMaterial.Rmd
Update functional groups

@@
                               Species %in% c("Halichondrida","Haplosclerida","Poecilosclerida","Tetractinellida") ~ "Order",
-                              Species %in% ("Copepodite","Larvae_Fish","Larvae_Nauplii","Eggs_Fish") ~ "Ontogenetic stage",
+                              Species %in% c("Copepodite","Larvae_Fish","Larvae_Nauplii","Eggs_Fish") ~ "Ontogenetic stage",
                               TRUE ~ "Other")) %>%  

### 2023-04-26 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Updates co-authors

@@
   Globally, the total area of the world ocean designated under marine protection has increased in the recent decades.
-The majority of these Marine Protected Areas (MPAs) focus on the presence of particularly vulnerable, keystone, or charismatic species, the presence of large numbers of endemic species, and/or the presence of high biodiversity across taxonomic levels.
-In the sub-Antarctic region, the level of ocean protection is mainly associated to oceanic islands, except for the MPAs Namuncurá - Banco Burdwood I and II (MPA N-BB, 53º–55ºS and 56º–62ºW), which are associated to a submarine plateau and its southern adjacent deep slope region, respectively.
-Here we present the first detailed analysis of the network of predator-prey interactions (food web) for the MPA N-BB ecosystem.
-We applied a network approach with the objective of characterizing the food web in terms of complexity and structure, and identifying the species' role in such framework.
+The majority of these Marine Protected Areas (MPAs) focus on the presence of particularly vulnerable, keystone, or charismatic species, large numbers of endemic species, and/or high biodiversity across taxonomic levels.
+In the sub-Antarctic region, the level of ocean protection is mainly associated to oceanic islands, except for the MPAs Namuncurá - Banco Burdwood I and II (MPA N-BB, 53º–55ºS and 56º–62ºW, respectively), which are associated to a submarine plateau and its southern adjacent deep slope region, respectively.
+Here, we present the first detailed analysis of the network of predator-prey interactions (food web) for the MPA N-BB ecosystem.
+We applied a network approach to characterize the food web in terms of complexity and structure, and identifying the species' role in such a framework.
 In terms of complexity, the MPA N-BB food web consisted of 1778 predator-prey interactions and 379 species, with a link density of 4.69 and a connectance of 0.01.
 In terms of structure, almost half of the consumers were omnivores (0.48), and the network displayed a small-world pattern.
-All this suggest that the ecosystem might be fragile to external perturbations targeting highly connected species, although structural properties might provide resilience and resistance with the final outcome of a rearrange structure maintaining their functions.
-On the other hand, we identified several species as important in terms of different aspects of trophic structure and functioning, and response to perturbations.
-We suggest that generalist species, mostly fishes, play a crucial role in the ecosystem's bentho-pelagic coupling process.
-In addition, we propose that other species rather than the longtail southern cod *Patagonotothen ramsayi* and the Fueguian sprat *Sprattus fuegensis* should be considered as relevant energy transfers for the ecosystem.
-Finally, we argue that it is the diversity of species, representing the benthic and pelagic habitats, what maintains the connectivity of the food web against perturbations, therefore contributing to the structure and stability of the ecosystem.
+These findings suggest that the ecosystem might be vulnerable to external perturbations targeting highly connected species, although structural properties might provide resilience and resistance, resulting in a rearranged structure that preserves its original functions.
+Furthermore, we identified several species as important in terms of different aspects of trophic structure and functioning, and response to perturbations.
+We suggest that generalist species, mainly fishes, play a crucial role in the ecosystem's bentho-pelagic coupling process.
+In addition, we propose that other species besides the longtail southern cod *Patagonotothen ramsayi* and the Fueguian sprat *Sprattus fuegensis* should be considered as relevant energy transfers for the ecosystem.
+Finally, we argue that the diversity of species, including both the benthic and pelagic habitats, is responsible for seccuring the connectivity within the food web against perturbations, therefore contributing to the structure and stability of the ecosystem.
 
@@
 The evidence of benefits provided by Marine Protected Areas (MPAs) as well as the urgent need for ocean protection have driven an unprecedented increase in the number of MPAs worldwide in recent years [@Roberts2017; @Sala2018].
-Globally, the total area of the world ocean designated under marine protection adds up to nearly 29,600,000 km^2^, distributed across nearly 18,444 MPAs and covering 8.16% of the ocean’s surface [@IUCN2023], and therefore approaching the 10% goal of the Convention of Biological Diversity [@CBD2004].
+Globally, the total area of the world ocean designated under marine protection adds up to approximately 29,600,000 km^2^, distributed across nearly 18,444 MPAs and covering 8.16% of the ocean’s surface [@IUCN2023], and therefore approaching the 10% goal of the Convention of Biological Diversity [@CBD2004].
 Despite this progress, recent reports have shown that actual protection has been overestimated because it includes areas that are not yet effectively protected (only declared) as well as areas that allow significant extractive activities [@Sala2018].
@@
 Interestingly, the case of the MPAs Namuncurá - Banco Burdwood I and II (MPA N-BB), which is the focus of this work, is unique since these MPAs are associated to a submarine plateau and its southern adjacent deep slope region, respectively [@Falabella2017].
-In addition, such MPAs are part of a network of protected areas in the sub-Antarctic (jointly with MPA Yaganes), that aims to protect and strengthen the functioning of this southern region to maintain global ocean health.
+In addition, such MPAs are part of a network of protected areas in the sub-Antarctic area (jointly with MPA Yaganes) that aims to protect and strengthen the functioning of this southern region to maintain global ocean health.
 
-Many of these MPAs focus on the presence of particularly vulnerable, keystone, or charismatic species, the presence of large numbers (or proportions) of endemic species, and/or the presence of high biodiversity across taxonomic levels [@Hogg2016].
+Many of these MPAs focus on the presence of particularly vulnerable, keystone, or charismatic species, large numbers (or proportions) of endemic species, and/or high biodiversity across taxonomic levels [@Hogg2016].
 Indeed, the MPA N-BB was created to protect a sensitive and biodiverse benthic habitat that was barely known [@Schejter2016; @Falabella2017].
-The benthic community is featured by a high biomass of vulnerable and fragile species (mainly Porifera and Cnidaria) that meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResources2009].
+The benthic community is featured by high biomass of vulnerable and fragile species (mainly Porifera and Cnidaria) that meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResources2009].
 Also, it provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge and nursery area [@GarciaAlonso2018; @Delpiani2020; @Troccoli2020; @CovattiAle2022; @Fischer2022; @Florencia2023].
 The maintenance of this singular community is related to local and regional oceanographic processes, including the circulation of the rich Malvinas (Falkland) current in the area [@Piola1989; @Guerrero1999] and the upwelling and mixing phenomena [@Matano2019].
-The input of nutrients coming from the Malvinas (Falkland) current also supports a diverse plankton community [@Guinder2020].
-Overall, 811 benthic and plankton species have been identified for the MPA N-BB ecosystem, where 349 were reported for the first time for the area [@APN2022].
-However, identifying the main species for maintenance of ecosystem services and health as well as for management and conservation is essential.
+The input of nutrients from the Malvinas (Falkland) current also supports a diverse plankton community [@Guinder2020].
+Overall, 811 benthic and plankton species have been identified for the MPA N-BB ecosystem, where 349 were reported for the first time in the area in recent years [@APN2022].
+However, identifying the main species involved in the maintenance of ecosystem services and health as well as for management and conservation is essential.
 
-Recently, the structure of the southwestern South Atlantic Ocean has been proposed to be under a 'wasp-waist' control, meaning that the structure and dynamics of the ecosystem is regulated primarily by mid-trophic level species (e.g., fishes, crustaceans) [@Padovani2012; @Saporiti2015; @Riccialdelli2020].
+Recently, the structure of the southwestern South Atlantic Ocean has been proposed to be under a 'wasp-waist' control, meaning that the structure and dynamics of the ecosystem are regulated primarily by mid-trophic level species (e.g., fishes, crustaceans) [@Padovani2012; @Saporiti2015; @Riccialdelli2020].
 In particular, the ecosystem of the MPA N-BB shows a more pronounced 'wasp-waist' structure than other sub-Antarctic areas, such as the Atlantic coast of Tierra del Fuego.
@@
 Although there is a robust knowledge about the complexity considering the richness of the benthic and plankton communities in the MPA N-BB ecosystem [@Schejter2016; @Guinder2020; @Schejter2020; @APN2022], a better understanding of species interactions' complexity and structure is needed.
-This aspect can be tackled by analyzing one of the most-frequent relationships occurring between species: the predator-prey interaction [@Bascompte2009].
-The sum of predator-prey or trophic interactions of a particular region is referred to as a food web, which represents the roadmap for matter and energy flow in an ecosystem.
+This aspect can be tackled by analyzing one of the most frequent relationships between species: the predator-prey interaction [@Bascompte2009].
+The sum of predator-prey or trophic interactions of a particular region is referred to as a food web, representing the roadmap for matter and energy flow in an ecosystem.
 In recent years, network approaches have been successfully applied to study complex high-latitude marine ecosystems, improving our knowledge on structure, functioning, and response to environmental/anthropogenic changes [@Kortsch2015; @Cordone2018; @Funes2022; @Marina2023].
-Among anthropogenic threats, it is worth mentioning that contaminants like mercury and microplastics have been recently reported as important threats for the MPA N-BB region [@Cossi2021; @DiMauro2022; @Fioramonti2022].
+Among anthropogenic threats, it is worth mentioning that contaminants like mercury and microplastics have been recently reported as important threats to the MPA N-BB region [@Cossi2021; @DiMauro2022; @Fioramonti2022].
 
-In the present work, we present the first, detailed analysis of the network of predator-prey interactions, hereafter food web, for the MPA N-BB ecosystem.
+In the present work, we present the first detailed analysis of the network of predator-prey interactions, hereafter food web, for the MPA N-BB ecosystem.
 For this, we applied a network approach to a highly resolved food web.
-The objective was twofold: characterize the food web in terms of complexity and structure, and identify the species' role in such network framework.
+The objective was twofold: characterize the food web in terms of complexity and structure, and identify the species' role in such a network framework.
 
@@
 The MPAs Namuncurá - Banco Burdwood I and II, created by National Laws 26.875 and 27.490, comprise a shallow submarine plateau called Burdwood Bank (BB) and a deep slope that reaches 4000 m in depth, N-BB I and N-BB II, respectively [@APN2023].
-They are located 150 km east of isla de los Estados and 200 km south from Malvinas/Falkland Islands (Figure 1).
+They are located 150 km east of Isla de los Estados and 200 km south of Malvinas/Falkland Islands (Figure 1).
 The MPA N-BB I comprises nearly 34,000 km^2^ circumscribed by the 200 m isobath, between 54º–55ºS and 56º–62ºW, with a slight slope extended nearly 370 km east–west.
@@
 The BB is surrounded by steep flanks of up to 4000 m depth through which strong currents circulate [@Piola1989; @Reta2014; @Matano2019].
-Such deep slope form the basis of N-BB II that protects about 32,000 km^2^.
-Intense upwelling and mixing occur over it, entraining deep nutrient-rich waters into the photic layer [@Piola2009; @Matano2019], and resulting in a fairly homogeneous water column both spatially and temporally [@Glorioso1995; @Guerrero1999; @Matano2019].
+Such deep slope forms the basis of N-BB II, protecting about 32,000 km^2^.
+Intense upwelling and mixing occur over it, entraining deep nutrient-rich waters into the photic layer [@Piola2009; @Matano2019] and resulting in a fairly homogeneous water column both spatially and temporally [@Glorioso1995; @Guerrero1999; @Matano2019].
 
 Given the evidence collected during several research cruises about the oceanographic and ecological processes connecting MPAs N-BB I and II [references in @APN2022], a joint management plan was recently proposed [@APN2022].
+This is why, the study area of the present work includes both MPAs.
 
@@
 
-In order to build the network of predator-prey interactions we reviewed more than 150 references considering published articles, Ph.D.
+In order to build the network of predator-prey interactions, we reviewed more than 150 references considering published articles, Ph.D.
 theses, public databases, and reports belonging to xx research cruises conducted in the MPAs N-BB I and II.
@@
 In most cases, we followed it when specific data on species, in the taxonomic sense, were not available.
-In some cases, we collapsed species when taxa shared the same set of predators and prey (trophic similarity, @Martinez1991), one of the aggregation methods that better preserves food web functional properties [@Gauzens2013].
+In some cases, we collapsed species when taxa shared the same set of predators and prey (trophic similarity, @Martinez1991), one of the aggregation methods that better preserve food web functional properties [@Gauzens2013].
 In addition, for endemic species (e.g.
@@
 
-With the gathered trophic data we constructed a matrix of pairwise interactions; a value of 1 or 0 was assigned to each element a_ij of the matrix depending on whether the j-species preyed or not on the i-species.
-Then we transformed such matrix into an oriented graph with L trophic interactions between S nodes or species.
+With the gathered trophic data, we constructed a matrix of pairwise interactions; a value of 1 or 0 was assigned to each element a_ij of the matrix depending on whether the j-species preyed or not on the i-species.
+Then we transformed such a matrix into an oriented graph with L trophic interactions between S nodes or species.
 The orientation or direction of the graph follows the flow of energy and matter in the network, from prey to predator.
@@
 
-The network-level analysis aims to characterizee the food web in terms of complexity and structure.
-For this we calculated several network properties commonly used to describe empirical food webs [@Pascual2005]: (1) number of species S; (2) number of interactions or links L; (3) link density L/S; (4) connectance L/S^2; (5) omnivory Omn; and (6) small-world pattern.
-In order to explore the small-world phenomenon we analyzed the  characteristic path length (CPL) and the clustering coefficient (CC).
-The CPL is defined as the average shortest path length between all pairs of nodes [@Watts1998].
+The network-level analysis aims to characterize the food web in terms of complexity and structure.
+For this, we calculated several network properties commonly used to describe empirical food webs [@Pascual2005]: (1) number of species S; (2) number of interactions or links L; (3) link density L/S; (4) connectance L/S^2; (5) omnivory Omn; and (6) small-world pattern.
+In order to explore the small-world phenomenon, we analyzed the  characteristic path length (CPL) and the clustering coefficient (CC).
+The CPL is the average shortest path length between all pairs of nodes [@Watts1998].
 Here, CPL was calculated as the average number of nodes in the shortest path $CPL_{Min} (i,j)$ between all pairs of nodes $S(i,j)$ in a network averaged over $S(S-1)/2$ nodes:
@@
 where $E_i$ is the effective number of interactions between $K_i$ nearest-neighbor nodes of node $i$ and the maximal possible number of such interactions [@Newman2003].
-With the aim of testing whether the food web presented the small-world pattern, we compared the empirical values of CPL and CC with those resulting from 1000 randomly generated networks with the same size (S) and number of interactions (L), following the method proposed by @Marina2018a.
+To test whether the food web presented the small-world pattern, we compared the empirical values of CPL and CC with those resulting from 1000 randomly generated networks with the same size (S) and number of interactions (L), following the method proposed by @Marina2018a.
 
-Also, we estimated the (7) degree distributions for the food web, for prey and predators, and for each functional group (e.g., Amphipoda, Ascidiacea, Bivalvia, Fish, Marine mammals, Sea birds, etc.).
+Also, we estimated the (7) degree distributions for the food web, prey and predators, and each functional group (e.g., Amphipoda, Ascidiacea, Bivalvia, fish, marine mammals, sea birds, among others).
 The prey and predator distributions indicate the frequency of prey among predators, and viceversa; the functional group's degree shows the distribution of interactions within groups.
@@
 For this, we considered the following properties: (1) betweenness Btw; (2) closeness Cl; (3) trophic similarity TS; (4) topological role TR; and (5) trophic level TL (Table 1).
-Topological roles refers to the fact that food webs tend to naturally organize in non-random, modular patterns, where modules are defined as a group of species that interact more frequently among themselves than with species that are not members of the module [@Guimera2005].
-Species can play different roles in this respect, according to the pattern of interactions they have within their own module and/or across modules.
-We computed the topological role for each species, classified as: module hub, species with a relatively high number of interactions, but most within its own module; module specialist, species with relatively few interactions and most within its own module; module connector, species with relatively few interactions mainly between modules; and network connector, species with high connectivity between and within modules [@Guimera2005].
+Topological roles refer to the fact that food webs tend to naturally organize in non-random, modular patterns, where modules are defined as a group of species that interact more frequently among themselves than with species that are not members of the module [@Guimera2005].
+Species can play different roles in this respect, according to the pattern of interactions within their own module and/or across modules.
+We computed the topological role for each species, classified as module hub, species with a relatively high number of interactions, but most within its own module; module specialist, species with relatively few interactions and most within its own module; module connector, species with relatively few interactions mainly between modules; and network connector, species with high connectivity between and within modules [@Guimera2005].
 
@@
 Thus, we considered the TL as the dependent variable and the given property (i.e.
-betweenness, closeness, trophic similarity) as the independent variable, and obtained the coefficients (slope and intercept) for the linear model.
+betweenness, closeness, trophic similarity) as the independent variable and obtained the coefficients (slope and intercept) for the linear model.
 Models were fitted using the least squares approach.
 We also explored the topological role categories with the species TL.
-These species-level properties provide a general appropriate description of species' role in empirical complex food webs [@Cirtwill2018].
+These species-level properties provide an appropriate description of species' role in empirical complex food webs [@Cirtwill2018].
 
@@
 
-load("../results/summary_results_jan23.rda")
+load("../results/summary_results_apr23.rda")
 
@@
 
-The degree distribution of the food web showed an asymmetric frequency in the number of interactions, where most of the species had a relatively low number of interactions and few species concentrated the majority of them (Figure 3A).
-The distribution of prey among predators showed that most of the consumers fed on a low number of prey whereas few of them had multiple preys (Figure 3B).
+The degree distribution of the food web showed an asymmetric frequency in the number of interactions, where most of the species had a relatively low number of interactions and few species concentrated most of them (Figure 3A).
+The distribution of prey among predators showed that most consumers fed on a low number of prey whereas few had multiple preys (Figure 3B).
 These were the top-five predators in number of prey: yellowfin notothen *Patagonotothen guntheri* (Notothenioid fish, 52 prey), rock cod *Patagonotothen ramsayi* (Notothenioid fish, 50 prey), Patagonian toothfish *Dissostichus eleginoides* (Notothenioid fish, 30 prey), broad nose skate *Bathyraja brachyurops* (Chondrichthyan, 30 prey), and graytail skate *Bathyraja griseocauda* (Chondrichthyan, 28 prey).
@@
 These were the top-five prey in number of predators: Detritus (Non-living, 153 predators), the three categories of Diatoms considered (benthic, centric and pennate, 72 predators on average), and species of the genus *Euphausia* (Zooplankton, 46 predators).
-Finally, taking into account the interactions within each functional group, again the majority of the interactions were concentrated in few species (Figure 3D).
+Finally, taking into account the interactions within each functional group, again most interactions were concentrated in a few species (Figure 3D).
 The most evident species were: *Themisto gaudichaudii* (Amphipoda), *Zygochlamys patagonica* (Bivalvia), *Aspidostoma giganteum* (Bryozoa), *Munida gregaria* (Decapoda), *Patagonotothen ramsayi* and *Patagonotothen guntheri* (bentho-pelagic fish), *Psychrolutes marmoratus* (demersal fish), and species of *Euphausia* (Zooplankton).
-Overall, there is an evident asymmetry in the distribution of interactions among species at different levels in the MPA Namuncurá - Banco Burdwood food web.
+Overall, there is an evident asymmetry in the distribution of interactions among species at different levels in the MPA N-BB food web.
 
@@
 
-load("../data/foodweb-data_jan23.rda")
-load("../results/summary_results_jan23.rda")
+load("../data/foodweb-data_apr23.rda")
+load("../results/summary_results_apr23.rda")
 
@@
 
-The majority of the species in the food web were consumers, 336 out of 379; the rest were primary producers, such as diatoms (phytoplankton), and non-living food sources like detritus and necromass.
+Most species in the food web were consumers, 336 out of 379; the rest were primary producers, such as diatoms (phytoplankton), and non-living food sources like detritus and necromass.
 
@@
 
-We also found a negative significant relationship between TL and closeness, however less evident, meaning that low-TL species are relatively closer to any other species in the food web (Figure 4B).
-Species of genera *Calanus* and *Euphausia*, and species of Brachiopoda, all of them with TL < 3, registered the highest values of closeness (Table S3).
+We also found a significant negative relationship between TL and closeness, however less evident, meaning that low-TL species are relatively closer to any other species in the food web (Figure 4B).
+Species of genera *Calanus* and *Euphausia*, and species of Brachiopoda, all with TL < 3, registered the highest closeness values (Table S3).
 
-It is noteworthy that the highest values of betweenness were shown by species of mid-TLs (3-4), meaning that those species participated in the highest number of shortest paths between species (Figure 4A).
+Notably, species of mid-TLs (3-4) showed the highest values of betweenness, meaning that those species participated in the highest number of shortest paths between species (Figure 4A).
 The following are the species with the highest values: *Patagonotothen ramsayi*, *Dissostichus eleginoides*, *Salilota australis* (fishes), *Doryteuthis gahi* (Cephalopoda), and *Patagonotothen guntheri* (Notothenioid fish) (Table S3).
@@
 Considering the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.77); 'module hub' was constrained to mid-TL species (2.48 - 3.92); 'module connector' from low to mid-TLs (1 - 3.86); and 'network connector', the least frequent, had all of its species in TL = 1, except for one with TL = 3.47 (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework).
-Here it is important to highlight the two latter topological roles, because they are responsible for linking modules and maintaining the connectivity of the food web: 40 species (5 network connectors + 35 module connectors) from 20 different functional groups with a TL range = 1 - 3.86.
+Here it is important to highlight the two latter topological roles because they are responsible for linking modules and maintaining the connectivity of the food web: 40 species (5 network connectors + 35 module connectors) from 20 different functional groups with a TL range = 1 - 3.86.
 The following were the five species with a network connector role: Detritus, Diatoms (benthic, centric and pennate), and *Patagonotothen ramsayi*.
-The 35 species with a module connector role represent these functional groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Cnidaria, Cumacea, Decapoda, Detritus, Diatoms, Dinoflagellates, Echinodermata, Fish (bentho-pelagic, demersal, Chondrichthyes), Foraminifera, Polychaeta, Porifera, Pycnogonida, Sea birds, and Zooplankton (see Supplementary Material Table S3 for the identity of the species).
+The 35 species with a module connector role represent these functional groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Cnidaria, Cumacea, Decapoda, detritus, Diatoms, Dinoflagellates, Echinodermata, fish (bentho-pelagic, demersal, Chondrichthyes), Foraminifera, Polychaeta, Porifera, Pycnogonida, sea birds, and zooplankton (see Supplementary Material Table S3 for the identity of the species).
 
@@
 
-The food web of the MPA Namuncurá - Banco Burdwood ecosystem analysed in this study is one of the most highly-resolved networks of trophic interactions ever studied not only for a high-latitude marine ecosystem but also for a marine protected area worldwide.
+The food web of the MPA N-BB ecosystem analysed in this study is one of the most highly-resolved networks of trophic interactions ever studied, not only for a high-latitude marine ecosystem but also for any marine protected area worldwide to our knowledge.
 It is of paramount importance to consider the complexity of species interactions in order to gain insights into the structure and functioning of the ecosystem, since the aggregation of species might mask food web properties and produce type II errors (false positive) [@Martinez1993; @Gauzens2013].
@@
 Food web connectance is a feature that resumes the complexity of the network, but more importantly, it is an emergent property of pairwise species interactions [@Poisot2014].
-It contains information regarding how interactions within an ecological network are distributed, and predicts reasonably well key dynamical properties of ecological networks [@Dunne2002a].
+It contains information regarding how interactions within an ecological network are distributed and predicts reasonably well key dynamical properties of ecological networks [@Dunne2002a].
 Complex marine food webs (i.e.
@@
 
-The degree distribution or the distribution of number of interactions per species is the core for the structure of species interactions, which influences the opportunities for multiple species to persist in the long term and, therefore, their coexistence [@Godoy2018].
+The degree distribution, the distribution of the number of interactions per species, is the core of the structure of species interactions, which influences the opportunities for multiple species to persist in the long term and, therefore, their coexistence [@Godoy2018].
 The food web for the MPA N-BB presents an asymmetric degree distribution.
@@
 
-It is suggested that the small-world pattern, i.e., a network with short path length and high clustering coefficient is not frequent in complex marine food webs, mainly due to a low clustering coefficient compared to random networks [@Dunne2002b; @Marina2018a].
+It is suggested that the small-world pattern, i.e., a network with short path length and high clustering coefficient, is not frequent in complex marine food webs, mainly due to a low clustering coefficient compared to random networks [@Dunne2002b; @Marina2018a].
 However, the food web of the MPA N-BB does display a small-world pattern.
 Consequences of this could be of great importance in recognizing evolutionary paths and the vulnerability to perturbations [@Montoya2002].
-On the one hand, a short path length implies a rapid spread of an impact (e.g., contaminant, population fluctuation, local extinction) throughout the network and, at the same time, a more potentially adaptive dynamics in face of external perturbations [@Montoya2002; @Williams2002].
+On the one hand, a short path length implies a rapid spread of an impact (e.g., contaminant, population fluctuation, local extinction) throughout the network and, at the same time, more potentially adaptive dynamics in the face of external perturbations [@Montoya2002; @Williams2002].
 On the other hand, a high clustering coefficient indicates the formation of subnetworks composed only by the neighbours of particular species.
 This translates into a greater resistance of the network due to the confinement of perturbations mainly within subnetworks and not spreading between them [@Kortsch2019; @Heer2020].
-Overall, a small-world topology provides ecological networks with a greater resilience and resistance [@Bornatowski2017; @Dormann2017].
+Overall, a small-world topology provides ecological networks with greater resilience and resistance [@Bornatowski2017; @Dormann2017].
 
-Omnivory acts as a buffer to changes as the ecosystem presents alternative energy pathways in the face of perturbations; i.e., reducing the risk of cascading extinctions following primary loss of species [@Borrvall2000].
-This is based on the fact that omnivores are species able to adapt faster and to a wider range of environmental conditions by changing their foraging habits to feed on the most abundant prey [@Fagan1997].
+Omnivory acts as a buffer to changes as the ecosystem presents alternative energy pathways in the face of perturbations, i.e., reducing the risk of cascading extinctions following the primary loss of species [@Borrvall2000].
+Omnivores are species able to adapt faster and to a broader range of environmental conditions by changing their foraging habits to feed on the most abundant prey [@Fagan1997].
 Furthermore, omnivory can be analysed from the interaction point of view: theoretical studies have identified omnivorous interactions as a possible candidate for a keystone interaction, sensu @Kadoya2018, highlighting the importance of omnivory in stabilizing food web dynamics [@McCann1997; @Neutel2002].
@@
 
-In summary, the food web of the MPA Namuncurá - Banco Burdwood presents a combination of network properties that make it unique in terms of network resolution, complexity, and structural pattern.
+In summary, the food web of the MPA N-BB presents a combination of network properties that makes it unique in terms of network resolution, complexity, and structural pattern.
 All this suggests that the ecosystem might be fragile to external perturbations targeting highly connected species.
-However, structural properties might provide resilience and resistance with the final outcome of a rearrange structure maintaining their functions.
+However, structural properties might provide resilience and resistance with the final outcome of a rearranged structure maintaining its functions.
 
@@
 Here again the longtail southern cod *Patagonotothen ramsayi* is emphasized as an influential species for the connectivity of the food web, which agrees with the suggested 'wasp-waist' control for the MPA N-BB ecosystem [@Riccialdelli2020].
-But most importantly, our results broadens this issue by pointing out that there are other species, belonging to a wide range of trophic positions (1 to 3.86) and representing 20 different functional groups, that should be considered.
+But most importantly, our results broaden this issue by pointing out that there are other species, belonging to a wide range of trophic positions (1 to 3.86) and representing 20 different functional groups, that should be considered.
 Thus, we propose that it is the diversity of species (benthic and pelagic) what maintains the connectivity of the food web, therefore contributing to the trophic structure and ecosystem's stability.
@@
 On one hand, we suggest that generalist species, mostly fishes, play a crucial role in the ecosystem's bentho-pelagic coupling process.
-At the same time, we propose that other species rather than the longtail southern cod *Patagonotothen ramsayi* and the Fueguian sprat *Sprattus fuegensis* should be considered as relevant energy transfers for the ecosystem.
+At the same time, we propose that other species besides the longtail southern cod *Patagonotothen ramsayi* and the Fueguian sprat *Sprattus fuegensis* should be considered as relevant energy transfers for the ecosystem.
 Finally, we argue that it is the diversity of species, representing the benthic and pelagic habitats, what maintains the connectivity of the food web against perturbations, therefore contributing to the structure and stability of the ecosystem.

### 2023-04-26 MS_ToSubmit/MS_Burdwood_foodweb.tex
Updates co-authors

@@
             pdfauthor={},
-            pdftitle={The complex network of trophic interactions in a subAntarctic Marine Protected Area},
+            pdftitle={The complex network of trophic interactions in a subAntarctic oceanic Marine Protected Area},
             colorlinks=false,
@@
   \title{The complex network of trophic interactions in a subAntarctic
-Marine Protected Area}
+oceanic Marine Protected Area}
     \author[]{Tomás I. Marina\textsuperscript{a}%
@@
   Marine Protected Areas (MPAs) focus on the presence of particularly
-  vulnerable, keystone, or charismatic species, the presence of large
-  numbers of endemic species, and/or the presence of high biodiversity
-  across taxonomic levels. In the sub-Antarctic region, the level of
-  ocean protection is mainly associated to oceanic islands, except for
-  the MPAs Namuncurá - Banco Burdwood I and II (MPA N-BB, 53º--55ºS and
-  56º--62ºW), which are associated to a submarine plateau and its
-  southern adjacent deep slope region, respectively. Here we present the
-  first detailed analysis of the network of predator-prey interactions
-  (food web) for the MPA N-BB ecosystem. We applied a network approach
-  with the objective of characterizing the food web in terms of
-  complexity and structure, and identifying the species' role in such
-  framework. In terms of complexity, the MPA N-BB food web consisted of
-  1778 predator-prey interactions and 379 species, with a link density
-  of 4.69 and a connectance of 0.01. In terms of structure, almost half
-  of the consumers were omnivores (0.48), and the network displayed a
-  small-world pattern. All this suggest that the ecosystem might be
-  fragile to external perturbations targeting highly connected species,
-  although structural properties might provide resilience and resistance
-  with the final outcome of a rearrange structure maintaining their
-  functions. On the other hand, we identified several species as
-  important in terms of different aspects of trophic structure and
-  functioning, and response to perturbations. We suggest that generalist
-  species, mostly fishes, play a crucial role in the ecosystem's
-  bentho-pelagic coupling process. In addition, we propose that other
-  species rather than the longtail southern cod \emph{Patagonotothen
-  ramsayi} and the Fueguian sprat \emph{Sprattus fuegensis} should be
-  considered as relevant energy transfers for the ecosystem. Finally, we
-  argue that it is the diversity of species, representing the benthic
-  and pelagic habitats, what maintains the connectivity of the food web
+  vulnerable, keystone, or charismatic species, large numbers of endemic
+  species, and/or high biodiversity across taxonomic levels. In the
+  sub-Antarctic region, the level of ocean protection is mainly
+  associated to oceanic islands, except for the MPAs Namuncurá - Banco
+  Burdwood I and II (MPA N-BB, 53º--55ºS and 56º--62ºW, respectively),
+  which are associated to a submarine plateau and its southern adjacent
+  deep slope region, respectively. Here, we present the first detailed
+  analysis of the network of predator-prey interactions (food web) for
+  the MPA N-BB ecosystem. We applied a network approach to characterize
+  the food web in terms of complexity and structure, and identifying the
+  species' role in such a framework. In terms of complexity, the MPA
+  N-BB food web consisted of 1778 predator-prey interactions and 379
+  species, with a link density of 4.69 and a connectance of 0.01. In
+  terms of structure, almost half of the consumers were omnivores
+  (0.48), and the network displayed a small-world pattern. These
+  findings suggest that the ecosystem might be vulnerable to external
+  perturbations targeting highly connected species, although structural
+  properties might provide resilience and resistance, resulting in a
+  rearranged structure that preserves its original functions.
+  Furthermore, we identified several species as important in terms of
+  different aspects of trophic structure and functioning, and response
+  to perturbations. We suggest that generalist species, mainly fishes,
+  play a crucial role in the ecosystem's bentho-pelagic coupling
+  process. In addition, we propose that other species besides the
+  longtail southern cod \emph{Patagonotothen ramsayi} and the Fueguian
+  sprat \emph{Sprattus fuegensis} should be considered as relevant
+  energy transfers for the ecosystem. Finally, we argue that the
+  diversity of species, including both the benthic and pelagic habitats,
+  is responsible for seccuring the connectivity within the food web
   against perturbations, therefore contributing to the structure and
@@
 (Roberts et al., 2017; Sala et al., 2018). Globally, the total area of
-the world ocean designated under marine protection adds up to nearly
-29,600,000 km\textsuperscript{2}, distributed across nearly 18,444 MPAs
-and covering 8.16\% of the ocean's surface (IUCN \& UNEP-WCMC, 2023),
-and therefore approaching the 10\% goal of the Convention of Biological
-Diversity (CBD, 2004). Despite this progress, recent reports have shown
-that actual protection has been overestimated because it includes areas
-that are not yet effectively protected (only declared) as well as areas
-that allow significant extractive activities (Sala et al., 2018).
+the world ocean designated under marine protection adds up to
+approximately 29,600,000 km\textsuperscript{2}, distributed across
+nearly 18,444 MPAs and covering 8.16\% of the ocean's surface (IUCN \&
+UNEP-WCMC, 2023), and therefore approaching the 10\% goal of the
+Convention of Biological Diversity (CBD, 2004). Despite this progress,
+recent reports have shown that actual protection has been overestimated
+because it includes areas that are not yet effectively protected (only
+declared) as well as areas that allow significant extractive activities
+(Sala et al., 2018).
 
@@
 since these MPAs are associated to a submarine plateau and its southern
-adjacent deep slope region, respectively (Falabella, 2017). Added to
-this, such MPAs are part of a network of protected areas in the
-sub-Antarctic (jointly with MPA Yaganes), that aims to protect and
-strengthen the functioning of this southern region to maintain global
-ocean health.
+adjacent deep slope region, respectively (Falabella, 2017). In addition,
+such MPAs are part of a network of protected areas in the sub-Antarctic
+area (jointly with MPA Yaganes) that aims to protect and strengthen the
+functioning of this southern region to maintain global ocean health.
 
 Many of these MPAs focus on the presence of particularly vulnerable,
-keystone, or charismatic species, the presence of large numbers (or
-proportions) of endemic species, and/or the presence of high
-biodiversity across taxonomic levels (Hogg et al., 2016). Indeed, the
-MPA N-BB was created to protect a sensitive and biodiverse benthic
-habitat that was barely known (Falabella, 2017; L. Schejter et al.,
-2016). The benthic community is featured by a high biomass of vulnerable
-and fragile species (mainly Poriferaand Cnidaria) that meet the
-characteristics of vulnerable marine ecosystems (Schejter \& Albano,
-2021), here defined as sites that present taxa with a minimum biomass of
-10 kg per 1200 m\textsuperscript{2} (Commission for the Conservation of
-Antarctic Marine Living Resources, 2009). Also, it provides habitat to
-several small-sized species (López-Gappa et al., 2018; L. Schejter \&
-Bremec, 2019; Sirito, 2019), and has an important role in the life
-history of fishes as a food source, refuge and nursery area (Delpiani et
-al., 2020; García Alonso et al., 2018; Troccoli et al., 2020). The
-maintenance of this singular community is related to local and regional
-oceanographic processes, including the circulation of the rich Malvinas
-(Falkland) current in the area (Guerrero et al., 1999; A. R. Piola \&
-Gordon, 1989) and the upwelling and mixing phenomena (Matano et al.,
-2019). The input of nutrients coming from the Malvinas (Falkland)
-current also supports a diverse plankton community (Guinder et al.,
-2020). Overall, 811 benthic and plankton species have been identified
-for the MPA N-BB ecosystem, where 349 were reported for the first time
-for the area (APN, 2022). However, identifying the main species for
-maintenance of ecosystem services and health as well as for management
-and conservation is essential.
+keystone, or charismatic species, large numbers (or proportions) of
+endemic species, and/or high biodiversity across taxonomic levels (Hogg
+et al., 2016). Indeed, the MPA N-BB was created to protect a sensitive
+and biodiverse benthic habitat that was barely known (Falabella, 2017;
+L. Schejter et al., 2016). The benthic community is featured by high
+biomass of vulnerable and fragile species (mainly Porifera and Cnidaria)
+that meet the characteristics of vulnerable marine ecosystems (Schejter
+\& Albano, 2021), here defined as sites that present taxa with a minimum
+biomass of 10 kg per 1200 m\textsuperscript{2} (Commission for the
+Conservation of Antarctic Marine Living Resources, 2009). Also, it
+provides habitat to several small-sized species (López-Gappa et al.,
+2018; L. Schejter \& Bremec, 2019; Sirito, 2019), and has an important
+role in the life history of fishes as a food source, refuge and nursery
+area (Covatti Ale et al., 2022; Delpiani et al., 2020; Fischer et al.,
+2022; García Alonso et al., 2018; Troccoli et al., 2020;
+\textbf{Florencia2023?}). The maintenance of this singular community is
+related to local and regional oceanographic processes, including the
+circulation of the rich Malvinas (Falkland) current in the area
+(Guerrero et al., 1999; A. R. Piola \& Gordon, 1989) and the upwelling
+and mixing phenomena (Matano et al., 2019). The input of nutrients from
+the Malvinas (Falkland) current also supports a diverse plankton
+community (Guinder et al., 2020). Overall, 811 benthic and plankton
+species have been identified for the MPA N-BB ecosystem, where 349 were
+reported for the first time in the area in recent years (APN, 2022).
+However, identifying the main species involved in the maintenance of
+ecosystem services and health as well as for management and conservation
+is essential.
 
@@
 been proposed to be under a `wasp-waist' control, meaning that the
-structure and dynamics of the ecosystem is regulated primarily by
+structure and dynamics of the ecosystem are regulated primarily by
 mid-trophic level species (e.g., fishes, crustaceans) (Padovani et al.,
@@
 communities in the MPA N-BB ecosystem (APN, 2022; Guinder et al., 2020;
-L. Schejter et al., 2016, 2020), there is a need for a better
-understanding of species interactions' complexity and structure. This
-aspect can be tackled by analyzing one of the most-frequent
-relationships occurring between species: the predator-prey interaction
-(Bascompte, 2009). The sum of predator-prey or trophic interactions of a
-particular region is referred to as a food web, which represents the
-roadmap for matter and energy flow in an ecosystem. In recent years,
-network approaches have been successfully applied to study complex
-high-latitude marine ecosystems, improving our knowledge on structure,
-functioning, and response to environmental/anthropogenic changes
-(Cordone et al., 2018; Funes et al., 2022; Kortsch et al., 2015; Marina
-et al., 2023). Among anthropogenic threats, it is worth mentioning that
-contaminants like mercury and microplastics have been recently reported
-as important threats for the MPA N-BB region (Cossi et al., 2021; Di
-Mauro et al., 2022; Fioramonti et al., 2022).
-
-In the present work, we present the first, detailed analysis of the
+L. Schejter et al., 2016, 2020), a better understanding of species
+interactions' complexity and structure is needed. This aspect can be
+tackled by analyzing one of the most frequent relationships between
+species: the predator-prey interaction (Bascompte, 2009). The sum of
+predator-prey or trophic interactions of a particular region is referred
+to as a food web, representing the roadmap for matter and energy flow in
+an ecosystem. In recent years, network approaches have been successfully
+applied to study complex high-latitude marine ecosystems, improving our
+knowledge on structure, functioning, and response to
+environmental/anthropogenic changes (Cordone et al., 2018; Funes et al.,
+2022; Kortsch et al., 2015; Marina et al., 2023). Among anthropogenic
+threats, it is worth mentioning that contaminants like mercury and
+microplastics have been recently reported as important threats to the
+MPA N-BB region (Cossi et al., 2021; Di Mauro et al., 2022; Fioramonti
+et al., 2022).
+
+In the present work, we present the first detailed analysis of the
 network of predator-prey interactions, hereafter food web, for the MPA
@@
 in terms of complexity and structure, and identify the species' role in
-such network framework.
+such a network framework.
 
@@
 Bank (BB) and a deep slope that reaches 4000 m in depth, N-BB I and N-BB
-II, respectively (APN, 2023). They are located 150 km east of isla de
-los Estados and 200 km south from Malvinas/Falkland Islands (Figure 1).
+II, respectively (APN, 2023). They are located 150 km east of Isla de
+los Estados and 200 km south of Malvinas/Falkland Islands (Figure 1).
 The MPA N-BB I comprises nearly 34,000 km\textsuperscript{2}
@@
 circulate (Matano et al., 2019; A. R. Piola \& Gordon, 1989; Reta,
-2014). Such deep slope form the basis of N-BB II that protects about
+2014). Such deep slope forms the basis of N-BB II, protecting about
 32,000 km\textsuperscript{2}. Intense upwelling and mixing occur over
 it, entraining deep nutrient-rich waters into the photic layer (Matano
-et al., 2019; A. Piola \& Falabella, 2009), and resulting in a fairly
+et al., 2019; A. Piola \& Falabella, 2009) and resulting in a fairly
 homogeneous water column both spatially and temporally (Glorioso \&
@@
 (references in APN, 2022), a joint management plan was recently proposed
-(APN, 2022).
+(APN, 2022). This is why, the study area of the present work includes
+both MPAs.
 
@@
 
-In order to build the network of predator-prey interactions we reviewed
-more than 150 references considering published articles, databases and
-doctoral theses. Furthermore, we took into account personal
-communications from experts belonging to the working group of the study
-area (https://www.pampazul.gob.ar/tag/banco-burdwood/). The diversity of
-the expertise of the authors contributing to the present study was a key
-factor in enhancing the quality of the network, and inherently improved
-the network representation. A list of the references used to build the
+In order to build the network of predator-prey interactions, we reviewed
+more than 150 references considering published articles, Ph.D.~theses,
+public databases, and reports belonging to xx research cruises conducted
+in the MPAs N-BB I and II. Here it is important to note that the
+sampling effort was greater in the MPA N-BB I. Furthermore, we took into
+account personal communications from experts belonging to the working
+group of the study area
+(https://www.pampazul.gob.ar/tag/banco-burdwood/). The diversity of the
+authors' expertise contributing to the present study was a key factor in
+enhancing the quality of the network, and inherently improved the
+network representation. A list of the references used to build the
 network is presented in Supplementary Material (Table S1).
@@
 and prey (trophic similarity, Martinez (1991)), one of the aggregation
-methods that better preserves food web functional properties (Gauzens et
-al., 2013). Details about this can be found in Supplementary Material
-(Table S2).
-
-With the gathered trophic data we constructed a matrix of pairwise
+methods that better preserve food web functional properties (Gauzens et
+al., 2013). In addition, for endemic species (e.g.~bryozoan
+\emph{Burdwoodipora paguricola}) and other species with no trophic
+studies so far, we inferred their feeding interactions applying a
+conservative approach that assumes that the set of prey and predators
+are at some point preserved in time. In those cases we gathered
+information from upper taxonomic levels (i.e.~Genus, Family, Order,
+Class, Phylum) as a good proxy variable (\textbf{Morales2015?};
+\textbf{Pomeranz2018?}). Details about this can be found in
+Supplementary Material (Table S2).
+
+With the gathered trophic data, we constructed a matrix of pairwise
 interactions; a value of 1 or 0 was assigned to each element a\_ij of
 the matrix depending on whether the j-species preyed or not on the
-i-species. Then we transformed such matrix into an oriented graph with L
-trophic interactions between S nodes or species. The orientation or
+i-species. Then we transformed such a matrix into an oriented graph with
+L trophic interactions between S nodes or species. The orientation or
 direction of the graph follows the flow of energy and matter in the
@@
 
-The network-level analysis aims to characterizee the food web in terms
-of complexity and structure. For this we calculated several network
+The network-level analysis aims to characterize the food web in terms of
+complexity and structure. For this, we calculated several network
 properties commonly used to describe empirical food webs (Pascual \&
@@
 Omn; and (6) small-world pattern. In order to explore the small-world
-phenomenon we analyzed the characteristic path length (CPL) and the
-clustering coefficient (CC). The CPL is defined as the average shortest
-path length between all pairs of nodes (Watts \& Strogatz, 1998). Here,
-CPL was calculated as the average number of nodes in the shortest path
+phenomenon, we analyzed the characteristic path length (CPL) and the
+clustering coefficient (CC). The CPL is the average shortest path length
+between all pairs of nodes (Watts \& Strogatz, 1998). Here, CPL was
+calculated as the average number of nodes in the shortest path
 \(CPL_{Min} (i,j)\) between all pairs of nodes \(S(i,j)\) in a network
@@
 nearest-neighbor nodes of node \(i\) and the maximal possible number of
-such interactions (Newman, 2003). With the aim of testing whether the
-food web presented the small-world pattern, we compared the empirical
-values of CPL and CC with those resulting from 1000 randomly generated
-networks with the same size (S) and number of interactions (L),
-following the method proposed by Marina et al. (2018).
-
-Also, we estimated the (7) degree distributions for the food web, for
-prey and predators, and for each functional group (e.g., Amphipoda,
-Ascidiacea, Bivalvia, Fish, Marine mammals, Sea birds, etc.). The prey
-and predator distributions indicate the frequency of prey among
-predators, and viceversa; the functional group's degree shows the
-distribution of interactions within groups.
+such interactions (Newman, 2003). To test whether the food web presented
+the small-world pattern, we compared the empirical values of CPL and CC
+with those resulting from 1000 randomly generated networks with the same
+size (S) and number of interactions (L), following the method proposed
+by Marina et al. (2018).
+
+Also, we estimated the (7) degree distributions for the food web, prey
+and predators, and each functional group (e.g., Amphipoda, Ascidiacea,
+Bivalvia, fish, marine mammals, sea birds, among others). The prey and
+predator distributions indicate the frequency of prey among predators,
+and viceversa; the functional group's degree shows the distribution of
+interactions within groups.
 
@@
 topological role TR; and (5) trophic level TL (Table 1). Topological
-roles refers to the fact that food webs tend to naturally organize in
+roles refer to the fact that food webs tend to naturally organize in
 non-random, modular patterns, where modules are defined as a group of
@@
 Species can play different roles in this respect, according to the
-pattern of interactions they have within their own module and/or across
-modules. We computed the topological role for each species, classified
-as: module hub, species with a relatively high number of interactions,
-but most within its own module; module specialist, species with
-relatively few interactions and most within its own module; module
-connector, species with relatively few interactions mainly between
-modules; and network connector, species with high connectivity between
-and within modules (Guimerà \& Nunes Amaral, 2005).
+pattern of interactions within their own module and/or across modules.
+We computed the topological role for each species, classified as module
+hub, species with a relatively high number of interactions, but most
+within its own module; module specialist, species with relatively few
+interactions and most within its own module; module connector, species
+with relatively few interactions mainly between modules; and network
+connector, species with high connectivity between and within modules
+(Guimerà \& Nunes Amaral, 2005).
 
@@
 (i.e.~betweenness, closeness, trophic similarity) as the independent
-variable, and obtained the coefficients (slope and intercept) for the
+variable and obtained the coefficients (slope and intercept) for the
 linear model. Models were fitted using the least squares approach. We
 also explored the topological role categories with the species TL. These
-species-level properties provide a general appropriate description of
-species' role in empirical complex food webs (Cirtwill et al., 2018).
+species-level properties provide an appropriate description of species'
+role in empirical complex food webs (Cirtwill et al., 2018).
 
@@
 \hline
-379 & 1778 & 4.69 & 0.01 & 0.48 & 2.99 & 0.08 & True\\
+380 & 1785 & 4.7 & 0.01 & 0.48 & 2.99 & 0.08 & True\\
 \hline
@@
 in the number of interactions, where most of the species had a
-relatively low number of interactions and few species concentrated the
-majority of them (Figure 3A). The distribution of prey among predators
-showed that most of the consumers fed on a low number of prey whereas
-few of them had multiple preys (Figure 3B). These were the top-five
-predators in number of prey: \emph{Patagonotothen guntheri}
-(Notothenioid fish, 52 prey), \emph{Patagonotothen ramsayi}
-(Notothenioid fish, 50 prey), \emph{Dissostichus eleginoides}
-(Notothenioid fish, 30 prey), \emph{Bathyraja brachyurops}
-(Chondrichthyan, 30 prey), and \emph{Bathyraja griseocauda}
-(Chondrichthyan, 28 prey). Following the same distribution pattern, few
-prey presented multiple predators (Figure 3C). These were the top-five
-prey in number of predators: Detritus (Non-living, 153 predators), the
-three categories of Diatoms considered (benthic, centric and pennate, 72
-predators on average), and species of the genus \emph{Euphausia}
-(Zooplankton, 46 predators). Finally, taking into account the
-interactions within each functional group, again the majority of the
-interactions were concentrated in few species (Figure 3D). The most
+relatively low number of interactions and few species concentrated most
+of them (Figure 3A). The distribution of prey among predators showed
+that most consumers fed on a low number of prey whereas few had multiple
+preys (Figure 3B). These were the top-five predators in number of prey:
+yellowfin notothen \emph{Patagonotothen guntheri} (Notothenioid fish, 52
+prey), rock cod \emph{Patagonotothen ramsayi} (Notothenioid fish, 50
+prey), Patagonian toothfish \emph{Dissostichus eleginoides}
+(Notothenioid fish, 30 prey), broad nose skate \emph{Bathyraja
+brachyurops} (Chondrichthyan, 30 prey), and graytail skate
+\emph{Bathyraja griseocauda} (Chondrichthyan, 28 prey). Following the
+same distribution pattern, few prey presented multiple predators (Figure
+3C). These were the top-five prey in number of predators: Detritus
+(Non-living, 153 predators), the three categories of Diatoms considered
+(benthic, centric and pennate, 72 predators on average), and species of
+the genus \emph{Euphausia} (Zooplankton, 46 predators). Finally, taking
+into account the interactions within each functional group, again most
+interactions were concentrated in a few species (Figure 3D). The most
 evident species were: \emph{Themisto gaudichaudii} (Amphipoda),
@@
 in the distribution of interactions among species at different levels in
-the MPA Namuncurá - Banco Burdwood food web.
+the MPA N-BB food web.
 
@@
 
-The majority of the species in the food web were consumers, 336 out of
-379; the rest were primary producers, such as diatoms (phytoplankton),
-and non-living food sources like detritus and necromass.
+Most species in the food web were consumers, 336 out of 379; the rest
+were primary producers, such as diatoms (phytoplankton), and non-living
+food sources like detritus and necromass.
 
@@
 
-We also found a negative significant relationship between TL and
+We also found a significant negative relationship between TL and
 closeness, however less evident, meaning that low-TL species are
@@
 Species of genera \emph{Calanus} and \emph{Euphausia}, and species of
-Brachiopoda, all of them with TL \textless{} 3, registered the highest
-values of closeness (Table S3).
-
-It is noteworthy that the highest values of betweenness were shown by
-species of mid-TLs (3-4), meaning that those species participated in the
-highest number of shortest paths between species (Figure 4A). The
-following are the species with the highest values: \emph{Patagonotothen
-ramsayi}, \emph{Dissostichus eleginoides}, \emph{Salilota australis}
-(fishes), \emph{Doryteuthis gahi} (Cephalopoda), and
-\emph{Patagonotothen guntheri} (Notothenioid fish) (Table S3).
+Brachiopoda, all with TL \textless{} 3, registered the highest closeness
+values (Table S3).
+
+Notably, species of mid-TLs (3-4) showed the highest values of
+betweenness, meaning that those species participated in the highest
+number of shortest paths between species (Figure 4A). The following are
+the species with the highest values: \emph{Patagonotothen ramsayi},
+\emph{Dissostichus eleginoides}, \emph{Salilota australis} (fishes),
+\emph{Doryteuthis gahi} (Cephalopoda), and \emph{Patagonotothen
+guntheri} (Notothenioid fish) (Table S3).
 
@@
 framework). Here it is important to highlight the two latter topological
-roles, because they are responsible for linking modules and maintaining
+roles because they are responsible for linking modules and maintaining
 the connectivity of the food web: 40 species (5 network connectors + 35
@@
 role represent these functional groups: Amphipoda, Bivalvia,
-Brachiopoda, Bryozoa, Cnidaria, Cumacea, Decapoda, Detritus, Diatoms,
-Dinoflagellates, Echinodermata, Fish (bentho-pelagic, demersal,
-chondrichthyes), Foraminifera, Polychaeta, Porifera, Pycnogonida, Sea
-birds, and Zooplankton (see Supplementary Material Table S3 for the
+Brachiopoda, Bryozoa, Cnidaria, Cumacea, Decapoda, detritus, Diatoms,
+Dinoflagellates, Echinodermata, fish (bentho-pelagic, demersal,
+Chondrichthyes), Foraminifera, Polychaeta, Porifera, Pycnogonida, sea
+birds, and zooplankton (see Supplementary Material Table S3 for the
 identity of the species).
@@
 
-The food web of the MPA Namuncurá - Banco Burdwood ecosystem analysed in
-this study is one of the most highly-resolved networks of trophic
-interactions ever studied not only for a high-latitude marine ecosystem
-but also for a marine protected area worldwide. It is of paramount
-importance to consider the complexity of species interactions in order
-to gain insights into the structure and functioning of the ecosystem,
-since the aggregation of species might mask food web properties and/or
-produce type II errors (false positive) (Gauzens et al., 2013; Martinez,
-1993).
+The food web of the MPA N-BB ecosystem analysed in this study is one of
+the most highly-resolved networks of trophic interactions ever studied,
+not only for a high-latitude marine ecosystem but also for any marine
+protected area worldwide to our knowledge. It is of paramount importance
+to consider the complexity of species interactions in order to gain
+insights into the structure and functioning of the ecosystem, since the
+aggregation of species might mask food web properties and produce type
+II errors (false positive) (Gauzens et al., 2013; Martinez, 1993).
 
@@
 species interactions (Poisot \& Gravel, 2014). It contains information
-regarding how interactions within an ecological network are distributed,
+regarding how interactions within an ecological network are distributed
 and predicts reasonably well key dynamical properties of ecological
@@
 it appears to be five times lower than that of Beagle Channel, an
-adjacent area (Rodriguez et al., 2022).
-
-The degree distribution or the distribution of number of interactions
-per species is the core for the structure of species interactions, which
+adjacent coastal area (Rodriguez et al., 2022).
+
+The degree distribution, the distribution of the number of interactions
+per species, is the core of the structure of species interactions, which
 influences the opportunities for multiple species to persist in the long
@@
 It is suggested that the small-world pattern, i.e., a network with short
-path length and high clustering coefficient is not frequent in complex
+path length and high clustering coefficient, is not frequent in complex
 marine food webs, mainly due to a low clustering coefficient compared to
@@
 of an impact (e.g., contaminant, population fluctuation, local
-extinction) throughout the network and, at the same time, a more
-potentially adaptive dynamics in face of external perturbations (Montoya
-\& Solé, 2002; Williams et al., 2002). On the other hand, a high
-clustering coefficient indicates the formation of subnetworks composed
-only by the neighbours of particular species. This translates into a
-greater resistance of the network due to the confinement of
+extinction) throughout the network and, at the same time, more
+potentially adaptive dynamics in the face of external perturbations
+(Montoya \& Solé, 2002; Williams et al., 2002). On the other hand, a
+high clustering coefficient indicates the formation of subnetworks
+composed only by the neighbours of particular species. This translates
+into a greater resistance of the network due to the confinement of
 perturbations mainly within subnetworks and not spreading between them
 (Heer et al., 2020; Kortsch et al., 2019). Overall, a small-world
-topology provides ecological networks with a greater resilience and
+topology provides ecological networks with greater resilience and
 resistance (Bornatowski et al., 2017; Dormann et al., 2017).
@@
 Omnivory acts as a buffer to changes as the ecosystem presents
-alternative energy pathways in the face of perturbations; i.e., reducing
-the risk of cascading extinctions following primary loss of species
-(Borrvall et al., 2000). This is based on the fact that omnivores are
-species able to adapt faster and to a wider range of environmental
-conditions by changing their foraging habits to feed on the most
-abundant prey (Fagan, 1997). Furthermore, omnivory can be analysed from
-the interaction point of view: theoretical studies have identified
-omnivorous interactions as a possible candidate for a keystone
-interaction, sensu Kadoya et al. (2018), highlighting the importance of
-omnivory inn stabilizing food web dynamics (McCann \& Hastings, 1997;
-Neutel et al., 2002). The high proportion of omnivory in the food web of
-the MPA N-BB suggests that the network might be robust to variations in
-prey abundances, which could increase food web's persistence and
-stability (Stouffer \& Bascompte, 2010).
-
-To resume, the food web of the MPA Namuncurá - Banco Burdwood presents a
-combination of network properties that make it unique in terms of
-network resolution, complexity, and structural pattern. All this suggest
-that the ecosystem might be fragile to external perturbations targeting
-highly connected species. However, structural properties might provide
-resilience and resistance with the final outcome of a rearrange
-structure maintaining their functions.
+alternative energy pathways in the face of perturbations, i.e., reducing
+the risk of cascading extinctions following the primary loss of species
+(Borrvall et al., 2000). Omnivores are species able to adapt faster and
+to a broader range of environmental conditions by changing their
+foraging habits to feed on the most abundant prey (Fagan, 1997).
+Furthermore, omnivory can be analysed from the interaction point of
+view: theoretical studies have identified omnivorous interactions as a
+possible candidate for a keystone interaction, sensu Kadoya et al.
+(2018), highlighting the importance of omnivory in stabilizing food web
+dynamics (McCann \& Hastings, 1997; Neutel et al., 2002). The high
+proportion of omnivory in the food web of the MPA N-BB suggests that the
+network might be robust to variations in prey abundances, which could
+increase food web's persistence and stability (Stouffer \& Bascompte,
+2010).
+
+In summary, the food web of the MPA N-BB presents a combination of
+network properties that makes it unique in terms of network resolution,
+complexity, and structural pattern. All this suggests that the ecosystem
+might be fragile to external perturbations targeting highly connected
+species. However, structural properties might provide resilience and
+resistance with the final outcome of a rearranged structure maintaining
+its functions.
 
@@
 present a broad diet. The most evident generalist species are
-\emph{Patagonotothen guntheri}, \emph{P. ramsayi}, \emph{Dissostichus
-eleginoides}, \emph{Bathyraja brachyurops}, and \emph{B. griseocauda},
-with more than 25 potential prey. Since these species present
-mid-trophic positions in the food web (3-4), acting as predator and
-prey, they might be important links between lower and higher trophic
-levels. This is in agreement with the sole analysis, using stable
-isotopes, that exists so far for the trophic structure of the MPA N-BB
-(Riccialdelli et al., 2020), and resembles other high-latitude marine
-systems of the Southwest Atlantic and Arctic regions (Arkhipkin \&
-Laptikhovsky, 2013; Kortsch et al., 2019). The importance of these
-particular generalist species also arises since they feed on the benthic
-and pelagic habitats (Covatti Ale et al., 2022; Fischer et al., 2022;
-Troccoli et al., 2020), linking these realms and contributing to the
-vertical carbon flow.
+\emph{Patagonotothen guntheri} (Covatti Ale et al., 2022), \emph{P.
+ramsayi} (Fischer et al., 2022), \emph{Dissostichus eleginoides}
+(Troccoli et al., 2020), \emph{Bathyraja brachyurops}
+(\textbf{Bellegia2008?}), and \emph{B. griseocauda}
+(\textbf{Bellegia2014?}), with more than 25 potential prey. Since these
+species present mid-trophic positions in the food web (3-4), acting as
+predator and prey, they might be important links between lower and
+higher trophic levels. This is in agreement with the sole analysis,
+using stable isotopes, that exists so far for the trophic structure of
+the MPA N-BB (Riccialdelli et al., 2020), and resembles other
+high-latitude marine systems of the Southwest Atlantic and Antarctic
+regions (Arkhipkin \& Laptikhovsky, 2013; \textbf{Marina2018?}). The
+importance of these particular generalist species also arises since they
+feed on the benthic and pelagic habitats (Covatti Ale et al., 2022;
+Fischer et al., 2022; Troccoli et al., 2020), linking these realms and
+contributing to the vertical carbon flow.
 
@@
 N-BB ecosystem (Riccialdelli et al., 2020). But most importantly, our
-results broadens this issue by pointing out that there are other
-species, belonging to a wide range of trophic positions (1 to 3.86) and
+results broaden this issue by pointing out that there are other species,
+belonging to a wide range of trophic positions (1 to 3.86) and
 representing 20 different functional groups, that should be considered.
@@
 
-In construction\ldots{}
-
-Caveats:
+Caveats: The food web studied in the present work might be more
+representative of the MPA Namuncurá - Banco Burdwood I ecosystem, which
+comprises the shallow submarine plateau called Burdwood Bank. This is
+related to the sampling effort that was conducted during the research
+cruises in the former MPA compared to the MPA N-BB II (i.e.~deep flanks
+to the south). As a consequence most of the data we used to build the
+network comes from studies performed in the MPA N-BB I. Despite this
+fact, we decided to build the food web considering both MPAs due to the
+tight oceanographic and ecological connection that exists among them
+(references in APN, 2022).
+
+It's worth mentioning that we did not consider quantitative data
+(i.e.~abundance, biomass) to assess the species' role in the food web.
+Although there exists such data for some species of the MPA N-BB
+(Schejter \& Albano, 2021), it would not be possible to incorporate it
+in the food web framework described here due to a taxonomical resolution
+mismatch. In this regard, we should mention the case of
+\emph{Zygochlamys patagonica} (Bivalvia) that is highlighted by our
+species-level analyses though it has been found in low abundances in the
+area (Schejter \& Albano, 2021).
+
+Some species of sessile suspension feeders in high-latitude marine
+ecosystems, such as sponges, ascidians and octocorals, avoid predation
+by producing secondary metabolites that function as a chemical defense
+(\textbf{NunezPons2010?}; \textbf{Moles2015?}; \textbf{Prieto2022?}).
+Although this was not reported at the MPA N-BB, there are few studies
+that reported it other locations in species that were found in the MPA
+N-BB (\textbf{RojoDeAlmeida2010?}). Thus, the interactions that we
+considered between these species and their predators should be taken
+with caution.
 
@@
 
-Perspectives:
-
-Incorporate habitat heterogeneity, since benthic community in the BB and
-deep flanks is different (Schejter \& Albano, 2021). This might lead to
-distinct food web properties, hence differences in ecosystem functioning
-and response to anthropogenic and environmental perturbations. Cordone
-et al. (2020)
-
-Simulate perturbations on food web and target species: mercury transfer,
-microplastic pollution, fisheries. Cossi et al. (2021); Di Mauro et al.
-(2022); Fioramonti et al. (2022)
-
+These are the perspectives that we suggest should be considered to
+improve our knowledge regarding the structure, functioning and stability
+of the MPA N-BB:
+
+\begin{itemize}
+\tightlist
+\item
+  Incorporate habitat heterogeneity, since benthic community in the BB
+  and deep flanks is different (Schejter \& Albano, 2021). El caso de
+  las ascidias (Tatián)
+\end{itemize}
+
+This might lead to distinct food web properties, hence differences in
+ecosystem functioning and response to anthropogenic and environmental
+perturbations. Cordone et al. (2020)
+
+\begin{itemize}
+\item
+  Incorporate species traits, like body size and mass, which are known
+  to be important drivers in predator-prey interactions.
+\item
+  Simulate perturbations on food web and target species: mercury
+  transfer, microplastic pollution, fisheries. Cossi et al. (2021); Di
+  Mauro et al. (2022); Fioramonti et al. (2022)
+\item
   Estimation of interaction strength considering species and interaction
@@
   (2018); Kortsch et al. (2021)
+\end{itemize}
 
@@
 ecosystem's bentho-pelagic coupling process. At the same time, we
-propose that other species rather than the longtail southern cod
+propose that other species besides the longtail southern cod
 \emph{Patagonotothen ramsayi} and the Fueguian sprat \emph{Sprattus
@@
 Argentina), Mariano I. Martinez (Museo Argentino de Ciencias Naturales
-``Bernardino Rivadavia'', Argentina), Laura Schejter
-(INIDEP-CONICET),\ldots{} Special thanks to G.A. Lovrich the Scientific
-Coordinator of the MPA Namuncurá-Burdwood Bank and the MPA N-BB
-Administrators. This study was funded by Consejo Nacional de
-Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de
-Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617), Argentina.
-This work is contribution no. XX of the MPA Namuncurá (Law 26.875).
+``Bernardino Rivadavia'', Argentina), Sofía L. Callá (Museo Argentino de
+Ciencias Naturales ``Bernardino Rivadavia'', Argentina),\ldots{} Special
+thanks to G.A. Lovrich the Scientific Coordinator of the MPA
+Namuncurá-Burdwood Bank and the MPA N-BB Administrators. This study was
+funded by Consejo Nacional de Investigaciones Científicas y Técnicas
+(CONICET) and Agencia Nacional de Promoción Científica y Tecnológica
+(PICT 2020-SERIEA-01617), Argentina. This work is contribution no. XX of
+the MPA Namuncurá (Law 26.875).
 

### 2023-04-26 MS_ToSubmit/SupMaterial.Rmd
Updates co-authors

@@
 # Load data
-load("../data/cleaned-data_jan23.rda")
+load("../data/cleaned-data_apr23.rda")
 
@@
 library(kableExtra)
+library(stringr)
 
 # Load data
-load("../data/cleaned-data_jan23.rda")
-load("../data/foodweb-data_jan23.rda")
+load("../data/cleaned-data_apr23.rda")
+load("../data/foodweb-data_apr23.rda")
 
@@
 # Load data
-load("../results/summary_results_jan23.rda")
+load("../results/summary_results_apr23.rda")
 

### 2023-04-26 R/1_datawrangling.R

@@ -17,7 +17,7 @@ ipak(packages)
 
 ## Lista de Especies ----
 
-sp_raw <- read.csv("data/ListaEspecies_AMPNBB_jan23.csv")
+sp_raw <- read.csv("data/ListaEspecies_AMPNBB_apr23.csv")
 colnames(sp_raw)
 sp_raw <- sp_raw %>% 
   add_count(FunctionalGroup, name = "Richness") %>% 
@@ -26,7 +26,7 @@ sp_raw <- sp_raw %>%
 
 ## Lista de Interacciones ----
 
-int_raw <- read.csv("data/ListaInteracciones_AMPNBB_jan23.csv")
+int_raw <- read.csv("data/ListaInteracciones_AMPNBB_apr23.csv")
 
 int_raw <- int_raw %>% 
   # low-resolved Phytoplankton
@@ -107,42 +107,42 @@ int_raw <- subset(int_raw, !(Prey %in% "Demospongiae *"))  # exclude rows with P
 
 # Check ----
 
-int_good_res <- int_raw %>% 
-  filter(!str_detect(Prey, "\\*$")) %>% 
-  filter(!str_detect(Predator, "\\*$")) %>% 
-  dplyr::select(Prey, Predator, PreyGroup, PredGroup, PredStrategy, FoodSource) %>% 
-  distinct(Prey, Predator, .keep_all = TRUE)
-
-library(igraph)
-g <- graph_from_edgelist(as.matrix(int_good_res[,1:2]), directed = TRUE)
-sp_raw_fg <- sp_raw[,c("TrophicSpecies", "FunctionalGroup", "Zone")] %>% 
-  mutate(across(where(is.factor), as.character)) %>% 
-  relocate(any_of(c("FunctionalGroup", "Zone", "TrophicSpecies"))) %>% rename(id = TrophicSpecies)
-df_g <- igraph::as_data_frame(g, 'both')
-df_g$vertices <- df_g$vertices %>% 
-  left_join(sp_raw_fg, c('name' = 'id'))
-g <- graph_from_data_frame(df_g$edges, directed = TRUE, vertices = df_g$vertices)
-
-library(NetIndices)
-adj_mat <- as_adjacency_matrix(g, sparse = TRUE)
-tl <- round(TrophInd(as.matrix(adj_mat)), digits = 3)
-V(g)$TL <- tl$TL
-V(g)$Omn <- tl$OI
-
[…]

### 2023-04-26 R/2_dataexploring.R

@@ -17,7 +17,7 @@ ipak(packages)
 
 # Cargar datos ----
 
-load("data/cleaned-data_jan23.rda")
+load("data/cleaned-data_apr23.rda")
 
 
 # Lista de Especies ----
@@ -325,79 +325,79 @@ num_int_prey <- sum(int_need_prey$n)
 num_int_pred <- sum(int_need_pred$n)
 
 
-## Guardar listas grupo funcional ----
-
-sort(unique(int_raw$PredGroup))
-sort(unique(int_raw$PreyGroup))
-
-IntList_prey <- split(int_raw, f = int_raw$PreyGroup)
-IntList_pred <- split(int_raw, f = int_raw$PredGroup)
-# keys <- unique(c(names(IntList_prey), names(IntList_pred)))
-# IntList_all <- setNames(mapply(c, IntList_prey[keys], IntList_pred[keys]), keys)
-
-# Interaction lists
-Amphipoda <- bind_rows(IntList_prey[["Amphipoda"]], IntList_pred[["Amphipoda"]])
-Ascidiacea <- bind_rows(IntList_prey[["Ascidiacea"]], IntList_pred[["Ascidiacea"]])
-Bacillariophyceae <- bind_rows(IntList_prey[["Bacillariophyceae"]], IntList_pred[["Bacillariophyceae"]])
-Bacteria <- bind_rows(IntList_prey[["Bacteria"]], IntList_pred[["Bacteria"]])
-Benthos_Misc <- bind_rows(IntList_prey[["Benthos_Misc"]], IntList_pred[["Benthos_Misc"]])
-Bivalvia <- bind_rows(IntList_prey[["Bivalvia"]], IntList_pred[["Bivalvia"]])
-Brachiopoda <- bind_rows(IntList_prey[["Brachiopoda"]], IntList_pred[["Brachiopoda"]])
-Bryozoa <- bind_rows(IntList_prey[["Bryozoa"]], IntList_pred[["Bryozoa"]])
-Cephalopoda <- bind_rows(IntList_prey[["Cephalopoda"]], IntList_pred[["Cephalopoda"]])
-Ciliates <- bind_rows(IntList_prey[["Ciliates"]], IntList_pred[["Ciliates"]])
-Cnidaria <- bind_rows(IntList_prey[["Cnidaria"]], IntList_pred[["Cnidaria"]])
-Coccolithophorids <- bind_rows(IntList_prey[["Coccolithophorids"]], IntList_pred[["Coccolithophorids"]])
[…]

### 2023-04-26 R/3_foodwebexploring.R

@@ -17,7 +17,7 @@ ipak(packages)
 
 # Cargar datos ----
 
-load("data/cleaned-data_jan23.rda")
+load("data/cleaned-data_apr23.rda")
 
 
 # Red trófica ----
@@ -114,4 +114,4 @@ plotTrophLevel(g, ylab = "Trophic level")
 # Save data ----
 
 save(g, int_need_res, int_good_res,
-     file = "data/foodweb-data_jan23.rda")
+     file = "data/foodweb-data_apr23.rda")

### 2023-04-26 R/4_foodwebanalysis.R

@@ -18,8 +18,8 @@ ipak(packages)
 
 # Cargar datos ----
 
-load("data/cleaned-data_jan23.rda")
-load("data/foodweb-data_jan23.rda")
+load("data/cleaned-data_apr23.rda")
+load("data/foodweb-data_apr23.rda")
 
 
 # Análisis ----
@@ -171,7 +171,7 @@ spp_total <- spp_total %>%
                              FunctionalGroup %in% c("Fish_Demersal") ~ "Demersal"))
 
 
-write_csv(spp_total, file = "results/spp_prop_jan23.csv")
+write_csv(spp_total, file = "results/spp_prop_apr23.csv")
 
 
 # Resolución de la red ----
@@ -186,4 +186,4 @@ sp_prop <- sp_count/vcount(g_up)
 # Guardar datos ----
 
 save(g_up, g, deg_dist_fit, prop_topol, spp_total, top.role, top.role.df,
-     file = "results/summary_results_jan23.rda")
+     file = "results/summary_results_apr23.rda")

### 2023-04-26 R/5_regressionanalyses.R

@@ -16,7 +16,7 @@ ipak(packages)
 
 
 # Datos ----
-load("results/summary_results_jan23.rda")
+load("results/summary_results_aor23.rda")
 
 
 # Linear Regression ----

### 2023-04-28 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Updates Cintia Fraysse

@@
 In those cases we gathered information from upper taxonomic levels (i.e.
-Genus, Family, Order, Class, Phylum) as a good proxy variable [@Morales2015; @Pomeranz2018].
+Genus, Family, Order, Class, Phylum) as a good proxy variable [@Morales-Castilla2015; @Pomeranz2019].
 Details about this can be found in Supplementary Material (Table S2).
@@
 
-The degree distribution allows to identify important species, such as potential keystone species [@Sole2001; @Dunne2002], generalist/specialist species, and dominant food sources [@Kondoh2010].
+The degree distribution allows identifying important species, such as potential keystone species [@Sole2001; @Dunne2002], generalist/specialist species, and dominant food sources [@Kondoh2010].
 
-We have identified that the majority of the consumers in the food web of the MPA N-BB either has a narrow diet or are specialists, while few present a broad diet.
+We have identified that most of the consumers in the food web of the MPA N-BB either has a narrow diet or are specialists, while few present a broad diet.
 The most evident generalist species are *Patagonotothen guntheri* [@CovattiAle2022], *P.
-ramsayi* [@Fischer2022], *Dissostichus eleginoides* [@Troccoli2020], *Bathyraja brachyurops* [@Bellegia2008], and *B.
+ramsayi* [@Fischer2022], *Dissostichus eleginoides* [@Troccoli2020], *Bathyraja brachyurops* [@Belleggia2008a], and *B.
 griseocauda* [@Bellegia2014], with more than 25 potential prey.
 Since these species present mid-trophic positions in the food web (3-4), acting as predator and prey, they might be important links between lower and higher trophic levels.
-This is in agreement with the sole analysis, using stable isotopes, that exists so far for the trophic structure of the MPA N-BB [@Riccialdelli2020], and resembles other high-latitude marine systems of the Southwest Atlantic and Antarctic regions [@Arkhipkin2013; @Marina2018].
+This result is in agreement with the sole analysis, using stable isotopes, that exists so far for the trophic structure of the MPA N-BB [@Riccialdelli2020], and resembles other high-latitude marine systems of the Southwest Atlantic and Antarctic regions [@Arkhipkin2013; @Marina2018].
 The importance of these particular generalist species also arises since they feed on the benthic and pelagic habitats [@Troccoli2020; @CovattiAle2022; @Fischer2022], linking these realms and contributing to the vertical carbon flow.
 
-On the other hand, few prey are consumed by many predators in the food web of the MPA N-BB.
-This suggests that there are dominant food sources from which most consumers depend on, and from where the ecosystem energy is being transferred to the upper trophic levels.
+On the other hand, a low number of prey are consumed by many predators in the food web of the MPA N-BB.
+This suggests that there are dominant food sources from which most consumers depend on and from where the ecosystem energy is being transferred to the upper trophic levels.
 The most demanded source we identified in this study (i.e.
@@
 
-Describing species’ roles in food webs provides a toolbox with which to assess the significance of species in terms of community's functioning and overall stability [@Thebault2010; @Cirtwill2018].
+Describing species’ roles in food webs provides a toolbox to assess the significance of species in terms of community's functioning and overall stability [@Thebault2010; @Cirtwill2018].
 We used a range of descriptors to characterise the dynamic and multifaceted nature of the species forming the MPA N-BB food web.
 
-Closeness and betweenness are defined as "meso-scale" properties because they consider direct and indirect interactions, therefore describing the focal species’ ability to influence the rest of the species of the food web [@Lai2012].
+Closeness and betweenness are defined as "mesoscale" properties because they consider direct and indirect interactions, therefore describing the focal species’ ability to influence the rest of the species of the food web [@Lai2012].
 Closeness quantifies how many steps away species $i$ is from all other species in the food web, and is proportional to how rapidly the indirect effects of the focal species can spread to other species in the network [@Scotti2010].
@@
 
-Ecosystems with a pronounced 'wasp-waist' structure are suggested to present a high trophic redundancy, since a large proportion of species would show similar trophic habits [@Cury2000].
-The significant negative relationship we found between trophic similarity and trophic level enhances the hypothesis of functional redundancy at low and mid-TL species compared to higher TL species for the MPA N-BB food web [@Riccialdelli2020].
-At the same time, our results highlight the uniqueness in terms of trophic role for high-TL predators.
+Ecosystems with a pronounced 'wasp-waist' structure are suggested to present a high trophic redundancy, since many species would show similar trophic habits [@Cury2000].
+The significant negative relationship between trophic similarity and trophic level enhances the hypothesis of functional redundancy at low and mid-TL species compared to higher TL species for the MPA N-BB food web [@Riccialdelli2020].
+At the same time, our results highlight the uniqueness in terms of the trophic role of high-TL predators.
 Here, not only the expected pelagic animals such as marine mammals and sea birds arise as relevant, but also benthic vertebrate (chondrichthyans *Bathyraja macloviana* and *Squalus acanthias*) and invertebrate species (echinoderms *Diplopteraster clarki* and *Pteraster sp*) are noteworthy.
@@
 
-Species' role can be also assessed in a module-based context.
+Species' role can also be assessed in a module-based context.
 Among the varying numbers of topological roles in which species can be divided, two are remarkable: 'module connector' and 'network connector'.
-Here again the longtail southern cod *Patagonotothen ramsayi* is emphasized as an influential species for the connectivity of the food web, which agrees with the suggested 'wasp-waist' control for the MPA N-BB ecosystem [@Riccialdelli2020].
+Here again, the longtail southern cod *Patagonotothen ramsayi* is emphasized as an influential species for the connectivity of the food web, which agrees with the suggested 'wasp-waist' control for the MPA N-BB ecosystem [@Riccialdelli2020].
 But most importantly, our results broaden this issue by pointing out that there are other species, belonging to a wide range of trophic positions (1 to 3.86) and representing 20 different functional groups, that should be considered.
-Thus, we propose that it is the diversity of species (benthic and pelagic) what maintains the connectivity of the food web, therefore contributing to the trophic structure and ecosystem's stability.
+Thus, we propose that the diversity of species (benthic and pelagic) maintains the connectivity of the food web, therefore contributing to the trophic structure and ecosystem's stability.
 
@@
 
-Some species of sessile suspension feeders in high-latitude marine ecosystems, such as sponges, ascidians and octocorals, avoid predation by producing secondary metabolites that function as a chemical defense [@NunezPons2010; @Moles2015; @Prieto2022].
-Although this was not reported at the MPA N-BB, there are few studies that reported it other locations in species that were found in the MPA N-BB [@RojoDeAlmeida2010].
+Some species of sessile suspension feeders in high-latitude marine ecosystems, such as sponges, ascidians and octocorals, avoid predation by producing secondary metabolites that function as a chemical defense [@Nunez-Pons2010; @Moles2015; @Prieto2022].
+Although this was not reported at the MPA N-BB, there are few studies that reported it other locations in species that were found in the MPA N-BB [@RojodeAlmeida2010].
 Thus, the interactions that we considered between these species and their predators should be taken with caution.
@@
 Spatial variation of study area: Banco Burdwood west-east gradient.
-In the oceanic BB area, complex oceanographic conditions generate an internal spatial heterogeneity, mainly along its longitudinal axis [@Matano2019], and consequently plankton communities respond with different spatial distributions [@Spinelli2020].
+In the oceanic BB area, complex oceanographic conditions generate an internal spatial heterogeneity, mainly along its longitudinal axis [@Matano2019], and consequently, plankton communities respond with different spatial distributions [@Spinelli2020].
 @Kortsch2019
@@
 
-* Incorporate habitat heterogeneity, since benthic community in the BB and deep flanks is different [@Schejter2021]. El caso de las ascidias (Tatián)
-
-This might lead to distinct food web properties, hence differences in ecosystem functioning and response to anthropogenic and environmental perturbations.
-@Cordone2020
+* Incorporate habitat heterogeneity, since the benthic community in the BB and deep flanks differs [@Schejter2021].
+This heterogeneity might lead to distinct food web properties, hence differences in ecosystem functioning and response to anthropogenic and environmental perturbations [@Cordone2020].
+El caso de las ascidias (Tatián)
 
@@
 We compiled information on the species and trophic diversity of the Marine Protected Area Namuncurá - Banco Burdwood, generating an unprecedented, well-resolved network of trophic interactions for a sub-Antarctic ecosystem, identifying the complexity and structure of the system, and the main species role in a network framework.
-Particular properties at the network level allowed us to identify ecosystem's vulnerability and potential response to perturbations in the presence of highly-connected species, with a rearrange structure maintaining their functions due to its potential resilience and resistance.
+Particular properties at the network level allowed us to identify the ecosystem's vulnerability and potential response to perturbations in the presence of highly-connected species, with a rearranged structure maintaining their functions due to its potential resilience and resistance.
 
-We identified several species as important in terms of different aspects of trophic structure and functioning, and response to perturbations (i.e.
+We identified several species as important regarding different aspects of trophic structure and functioning, and response to perturbations (i.e.
 environmental/anthropogenic changes).
-On one hand, we suggest that generalist species, mostly fishes, play a crucial role in the ecosystem's bentho-pelagic coupling process.
-At the same time, we propose that other species besides the longtail southern cod *Patagonotothen ramsayi* and the Fueguian sprat *Sprattus fuegensis* should be considered as relevant energy transfers for the ecosystem.
-Finally, we argue that it is the diversity of species, representing the benthic and pelagic habitats, what maintains the connectivity of the food web against perturbations, therefore contributing to the structure and stability of the ecosystem.
+On the one hand, we suggest that generalist species, mainly fishes, play a crucial role in the ecosystem's bentho-pelagic coupling process.
+At the same time, we propose that other species besides the longtail southern cod *Patagonotothen ramsayi* and the Fueguian sprat *Sprattus fuegensis* should be considered relevant energy transfers for the ecosystem.
+Finally, we argue that it is the diversity of species, representing the benthic and pelagic habitats, that maintains the connectivity of the food web against perturbations, therefore contributing to the structure and stability of the ecosystem.
 

### 2023-04-28 MS_ToSubmit/MS_Burdwood_foodweb.tex
Updates Cintia Fraysse

@@
 area (Covatti Ale et al., 2022; Delpiani et al., 2020; Fischer et al.,
-2022; García Alonso et al., 2018; Troccoli et al., 2020;
-\textbf{Florencia2023?}). The maintenance of this singular community is
-related to local and regional oceanographic processes, including the
-circulation of the rich Malvinas (Falkland) current in the area
-(Guerrero et al., 1999; A. R. Piola \& Gordon, 1989) and the upwelling
-and mixing phenomena (Matano et al., 2019). The input of nutrients from
-the Malvinas (Falkland) current also supports a diverse plankton
-community (Guinder et al., 2020). Overall, 811 benthic and plankton
-species have been identified for the MPA N-BB ecosystem, where 349 were
-reported for the first time in the area in recent years (APN, 2022).
-However, identifying the main species involved in the maintenance of
-ecosystem services and health as well as for management and conservation
-is essential.
+2022; Florencia et al., 2023; García Alonso et al., 2018; Troccoli et
+al., 2020). The maintenance of this singular community is related to
+local and regional oceanographic processes, including the circulation of
+the rich Malvinas (Falkland) current in the area (Guerrero et al., 1999;
+A. R. Piola \& Gordon, 1989) and the upwelling and mixing phenomena
+(Matano et al., 2019). The input of nutrients from the Malvinas
+(Falkland) current also supports a diverse plankton community (Guinder
+et al., 2020). Overall, 811 benthic and plankton species have been
+identified for the MPA N-BB ecosystem, where 349 were reported for the
+first time in the area in recent years (APN, 2022). However, identifying
+the main species involved in the maintenance of ecosystem services and
+health as well as for management and conservation is essential.
 
@@
 information from upper taxonomic levels (i.e.~Genus, Family, Order,
-Class, Phylum) as a good proxy variable (\textbf{Morales2015?};
-\textbf{Pomeranz2018?}). Details about this can be found in
-Supplementary Material (Table S2).
+Class, Phylum) as a good proxy variable (Morales-Castilla et al., 2015;
+Pomeranz et al., 2019). Details about this can be found in Supplementary
+Material (Table S2).
 
@@
 size (S) and number of interactions (L), following the method proposed
-by Marina et al. (2018).
+by Marina, Saravia, et al. (2018).
 
@@
 than 25 trophic species) show connectance values ranging from 0.01 -
-0.27 (Marina et al., 2018). In particular, food webs from high-latitude
-regions tend to exhibit a connectance closer to the minimum (between
-0.01 and 0.05) (Kortsch et al., 2015; Rodriguez et al., 2022; Santana et
-al., 2013). Whether food webs display a low or a high connectance helps
-to better comprehend ecosystem's synthetic properties like robustness.
-In this sense, empirical analyses support the notion that
-highly-connected ecological networks are robust against external
+0.27 (Marina, Saravia, et al., 2018). In particular, food webs from
+high-latitude regions tend to exhibit a connectance closer to the
+minimum (between 0.01 and 0.05) (Kortsch et al., 2015; Rodriguez et al.,
+2022; Santana et al., 2013). Whether food webs display a low or a high
+connectance helps to better comprehend ecosystem's synthetic properties
+like robustness. In this sense, empirical analyses support the notion
+that highly-connected ecological networks are robust against external
 perturbations such as the introduction of new (e.g., invasive) species
@@
 marine food webs, mainly due to a low clustering coefficient compared to
-random networks (Dunne et al., 2002c; Marina et al., 2018). However, the
-food web of the MPA N-BB does display a small-world pattern.
-Consequences of this could be of great importance in recognizing
-evolutionary paths and the vulnerability to perturbations (Montoya \&
-Solé, 2002). On the one hand, a short path length implies a rapid spread
-of an impact (e.g., contaminant, population fluctuation, local
-extinction) throughout the network and, at the same time, more
+random networks (Dunne et al., 2002c; Marina, Saravia, et al., 2018).
+However, the food web of the MPA N-BB does display a small-world
+pattern. Consequences of this could be of great importance in
+recognizing evolutionary paths and the vulnerability to perturbations
+(Montoya \& Solé, 2002). On the one hand, a short path length implies a
+rapid spread of an impact (e.g., contaminant, population fluctuation,
+local extinction) throughout the network and, at the same time, more
 potentially adaptive dynamics in the face of external perturbations
@@
 
-The degree distribution allows to identify important species, such as
+The degree distribution allows identifying important species, such as
 potential keystone species (Dunne et al., 2002b; Solé \& Montoya, 2001),
@@
 
-We have identified that the majority of the consumers in the food web of
-the MPA N-BB either has a narrow diet or are specialists, while few
-present a broad diet. The most evident generalist species are
-\emph{Patagonotothen guntheri} (Covatti Ale et al., 2022), \emph{P.
-ramsayi} (Fischer et al., 2022), \emph{Dissostichus eleginoides}
-(Troccoli et al., 2020), \emph{Bathyraja brachyurops}
-(\textbf{Bellegia2008?}), and \emph{B. griseocauda}
-(\textbf{Bellegia2014?}), with more than 25 potential prey. Since these
-species present mid-trophic positions in the food web (3-4), acting as
-predator and prey, they might be important links between lower and
-higher trophic levels. This is in agreement with the sole analysis,
-using stable isotopes, that exists so far for the trophic structure of
-the MPA N-BB (Riccialdelli et al., 2020), and resembles other
-high-latitude marine systems of the Southwest Atlantic and Antarctic
-regions (Arkhipkin \& Laptikhovsky, 2013; \textbf{Marina2018?}). The
-importance of these particular generalist species also arises since they
-feed on the benthic and pelagic habitats (Covatti Ale et al., 2022;
-Fischer et al., 2022; Troccoli et al., 2020), linking these realms and
-contributing to the vertical carbon flow.
-
-On the other hand, few prey are consumed by many predators in the food
-web of the MPA N-BB. This suggests that there are dominant food sources
-from which most consumers depend on, and from where the ecosystem energy
-is being transferred to the upper trophic levels. The most demanded
-source we identified in this study (i.e.~detritus) supports the abundant
-benthic community of filter-feeders (L. Schejter et al., 2016).
-Furthermore, we found that the second and third-most consumed prey were
-diatoms and species of \emph{Euphausia}, respectively, which are
-essential sources for the diverse zooplankton community (Spinelli et
-al., 2020), mid-TL consumers like the Fuegian sprat \emph{Sprattus
-fuegensis} (Padovani et al., 2021) and \emph{Patagonotothen ramsayi}
-(Fischer et al., 2022), and top predators (Raya Rey, 2022; Riccialdelli,
-2022).
+We have identified that most of the consumers in the food web of the MPA
+N-BB either has a narrow diet or are specialists, while few present a
+broad diet. The most evident generalist species are \emph{Patagonotothen
+guntheri} (Covatti Ale et al., 2022), \emph{P. ramsayi} (Fischer et al.,
+2022), \emph{Dissostichus eleginoides} (Troccoli et al., 2020),
+\emph{Bathyraja brachyurops} (Belleggia et al., 2008), and \emph{B.
+griseocauda} (Bellegia et al., 2014), with more than 25 potential prey.
+Since these species present mid-trophic positions in the food web (3-4),
+acting as predator and prey, they might be important links between lower
+and higher trophic levels. This result is in agreement with the sole
+analysis, using stable isotopes, that exists so far for the trophic
+structure of the MPA N-BB (Riccialdelli et al., 2020), and resembles
+other high-latitude marine systems of the Southwest Atlantic and
+Antarctic regions (Arkhipkin \& Laptikhovsky, 2013; Marina, Salinas, et
+al., 2018). The importance of these particular generalist species also
+arises since they feed on the benthic and pelagic habitats (Covatti Ale
+et al., 2022; Fischer et al., 2022; Troccoli et al., 2020), linking
+these realms and contributing to the vertical carbon flow.
+
+On the other hand, a low number of prey are consumed by many predators
+in the food web of the MPA N-BB. This suggests that there are dominant
+food sources from which most consumers depend on and from where the
+ecosystem energy is being transferred to the upper trophic levels. The
+most demanded source we identified in this study (i.e.~detritus)
+supports the abundant benthic community of filter-feeders (L. Schejter
+et al., 2016). Furthermore, we found that the second and third-most
+consumed prey were diatoms and species of \emph{Euphausia},
+respectively, which are essential sources for the diverse zooplankton
+community (Spinelli et al., 2020), mid-TL consumers like the Fuegian
+sprat \emph{Sprattus fuegensis} (Padovani et al., 2021) and
+\emph{Patagonotothen ramsayi} (Fischer et al., 2022), and top predators
+(Raya Rey, 2022; Riccialdelli, 2022).
 
@@
 
-Describing species' roles in food webs provides a toolbox with which to
-assess the significance of species in terms of community's functioning
-and overall stability (Cirtwill et al., 2018; Thébault \& Fontaine,
-2010). We used a range of descriptors to characterise the dynamic and
-multifaceted nature of the species forming the MPA N-BB food web.
-
-Closeness and betweenness are defined as ``meso-scale'' properties
+Describing species' roles in food webs provides a toolbox to assess the
+significance of species in terms of community's functioning and overall
+stability (Cirtwill et al., 2018; Thébault \& Fontaine, 2010). We used a
+range of descriptors to characterise the dynamic and multifaceted nature
+of the species forming the MPA N-BB food web.
+
+Closeness and betweenness are defined as ``mesoscale'' properties
 because they consider direct and indirect interactions, therefore
@@
 Ecosystems with a pronounced `wasp-waist' structure are suggested to
-present a high trophic redundancy, since a large proportion of species
-would show similar trophic habits (Cury et al., 2000). The significant
-negative relationship we found between trophic similarity and trophic
-level enhances the hypothesis of functional redundancy at low and mid-TL
-species compared to higher TL species for the MPA N-BB food web
-(Riccialdelli et al., 2020). At the same time, our results highlight the
-uniqueness in terms of trophic role for high-TL predators. Here, not
-only the expected pelagic animals such as marine mammals and sea birds
-arise as relevant, but also benthic vertebrate (chondrichthyans
-\emph{Bathyraja macloviana} and \emph{Squalus acanthias}) and
-invertebrate species (echinoderms \emph{Diplopteraster clarki} and
-\emph{Pteraster sp}) are noteworthy. The role that such species play in
-the MPA N-BB ecosystem is unique and perturbations on them might result
-in unprecedented changes at the trophic structure and functioning level.
-
-Species' role can be also assessed in a module-based context. Among the
+present a high trophic redundancy, since many species would show similar
+trophic habits (Cury et al., 2000). The significant negative
+relationship between trophic similarity and trophic level enhances the
+hypothesis of functional redundancy at low and mid-TL species compared
+to higher TL species for the MPA N-BB food web (Riccialdelli et al.,
+2020). At the same time, our results highlight the uniqueness in terms
+of the trophic role of high-TL predators. Here, not only the expected
+pelagic animals such as marine mammals and sea birds arise as relevant,
+but also benthic vertebrate (chondrichthyans \emph{Bathyraja macloviana}
+and \emph{Squalus acanthias}) and invertebrate species (echinoderms
+\emph{Diplopteraster clarki} and \emph{Pteraster sp}) are noteworthy.
+The role that such species play in the MPA N-BB ecosystem is unique and
+perturbations on them might result in unprecedented changes at the
+trophic structure and functioning level.
+
+Species' role can also be assessed in a module-based context. Among the
 varying numbers of topological roles in which species can be divided,
 two are remarkable: `module connector' and `network connector'. Here
-again the longtail southern cod \emph{Patagonotothen ramsayi} is
+again, the longtail southern cod \emph{Patagonotothen ramsayi} is
 emphasized as an influential species for the connectivity of the food
@@
 representing 20 different functional groups, that should be considered.
-Thus, we propose that it is the diversity of species (benthic and
-pelagic) what maintains the connectivity of the food web, therefore
-contributing to the trophic structure and ecosystem's stability.
+Thus, we propose that the diversity of species (benthic and pelagic)
+maintains the connectivity of the food web, therefore contributing to
+the trophic structure and ecosystem's stability.
 
@@
 by producing secondary metabolites that function as a chemical defense
-(\textbf{NunezPons2010?}; \textbf{Moles2015?}; \textbf{Prieto2022?}).
+(Moles et al., 2015; Núñez-Pons et al., 2010; Prieto et al., 2022).
 Although this was not reported at the MPA N-BB, there are few studies
 that reported it other locations in species that were found in the MPA
-N-BB (\textbf{RojoDeAlmeida2010?}). Thus, the interactions that we
+N-BB (Rojo de Almeida et al., 2010). Thus, the interactions that we
 considered between these species and their predators should be taken
@@
 internal spatial heterogeneity, mainly along its longitudinal axis
-(Matano et al., 2019), and consequently plankton communities respond
+(Matano et al., 2019), and consequently, plankton communities respond
 with different spatial distributions (Spinelli et al., 2020). Kortsch et
@@
 \begin{itemize}
-\tightlist
 \item
-  Incorporate habitat heterogeneity, since benthic community in the BB
-  and deep flanks is different (Schejter \& Albano, 2021). El caso de
-  las ascidias (Tatián)
-\end{itemize}
-
-This might lead to distinct food web properties, hence differences in
-ecosystem functioning and response to anthropogenic and environmental
-perturbations. Cordone et al. (2020)
-
-\begin{itemize}
+  Incorporate habitat heterogeneity, since the benthic community in the
+  BB and deep flanks differs (Schejter \& Albano, 2021). This
+  heterogeneity might lead to distinct food web properties, hence
+  differences in ecosystem functioning and response to anthropogenic and
+  environmental perturbations (Cordone et al., 2020). El caso de las
+  ascidias (Tatián)
 \item
@@
 system, and the main species role in a network framework. Particular
-properties at the network level allowed us to identify ecosystem's
+properties at the network level allowed us to identify the ecosystem's
 vulnerability and potential response to perturbations in the presence of
-highly-connected species, with a rearrange structure maintaining their
+highly-connected species, with a rearranged structure maintaining their
 functions due to its potential resilience and resistance.
 
-We identified several species as important in terms of different aspects
+We identified several species as important regarding different aspects
 of trophic structure and functioning, and response to perturbations
-(i.e.~environmental/anthropogenic changes). On one hand, we suggest that
-generalist species, mostly fishes, play a crucial role in the
+(i.e.~environmental/anthropogenic changes). On the one hand, we suggest
+that generalist species, mainly fishes, play a crucial role in the
 ecosystem's bentho-pelagic coupling process. At the same time, we
@@
 \emph{Patagonotothen ramsayi} and the Fueguian sprat \emph{Sprattus
-fuegensis} should be considered as relevant energy transfers for the
+fuegensis} should be considered relevant energy transfers for the
 ecosystem. Finally, we argue that it is the diversity of species,
-representing the benthic and pelagic habitats, what maintains the
+representing the benthic and pelagic habitats, that maintains the
 connectivity of the food web against perturbations, therefore
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Belleggia2019}{}}%
+Belleggia, M., Battagliotti, C., Cortés, F., \& Colonello, J. H. (2019).
+Feeding together: A global diet analysis of twenty-three species of
+chondrichthyes on a feeding ground area. \emph{Hydrobiologia},
+\emph{842}(1), 77--99. \url{https://doi.org/10.1007/s10750-019-04027-w}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Belleggia2008a}{}}%
+Belleggia, M., Mabragaña, E., Figueroa, D. E., Scenna, L. B., Barbini,
+S. A., \& Astarloa, J. M. D. de. (2008). Food habits of the broad nose
+skate, {\emph{Bathyraja}}{ \emph{Brachyurops}} ({Chondrichthyes},
+{Rajidae}), in the south-west {Atlantic}. \emph{Scientia Marina},
+\emph{72}(4), 701--710.
+\url{https://doi.org/10.3989/scimar.2008.72n4701}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bellegia2014}{}}%
+Bellegia, M., Scenna, L., Barbini, S. A., Figueroa, D. E., \& Díaz de
+Astarloa, J. M. (2014). \emph{The diets of four {Bathyraja} skates
+({Elasmobranchii}, {Arhynchobatidae}) from the {Southwest Atlantic}}.
+\url{https://doi.org/10.26028/CYBIUM/2014-384-012}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Bergagna2019}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-AlvarezColombo2018}{}}%
+Colombo, G. Álvarez. (2018). \emph{{Informe de Campaña Namuncurá-Banco
+Burdwood: \textquestiondown Area de cría de peces australes?}} (p. 83)
+{[}\{Field campaign Report\}{]}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-CommissionfortheConservationofAntarcticMarineLivingResources2009}{}}%
@@
 147--165. \url{https://doi.org/10.1016/j.csr.2013.02.002}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Dellabianca2015}{}}%
+Dellabianca, N. A. (2015). \emph{{Informe de Campaña {``Namuncurá-Banco
+Burdwood''}}} (p. 48) {[}\{Field campaign Report\}{]}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Dellabianca2018}{}}%
+Dellabianca, N. A. (2018). \emph{{Informe de Campaña AMP Namuncurá
+\textendash{} Banco Burdwood: Comprendiendo la bomba biológica de
+carbono}} (p. 101) {[}\{Field campaign Report\}{]}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Florencia2023}{}}%
+Florencia, M., Vazquez, D. M., Gabbanelli, V., Díaz de Astarloa, J. M.,
+\& Mabragaña, E. (2023). Chondrichthyans from the southern tip of {South
+America} with emphasis on the marine protected area {Namuncurá-Burdwood
+Bank}: Exploring egg nursery grounds. \emph{Polar Biology}.
+\url{https://doi.org/10.1007/s00300-023-03128-6}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Franco2020}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Giberto2017}{}}%
+Giberto, D. A., Belleggia, M., \& Bremec, C. S. (2017). \emph{El bentos
+como alimento de peces comerciales.} {Instituto Nacional de
+Investigación y Desarrollo Pesquero (INIDEP)}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Glorioso1995}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Kreps2016}{}}%
+Kreps, G. (2016). \emph{{Informe de Campaña AMP Namuncurá - Banco
+Burdwood: Primavera 2016}} (p. 103) {[}\{Field campaign Report\}{]}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Lai2012}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Marina2018}{}}%
+Marina, T. I., Salinas, V., Cordone, G., Campana, G., Moreira, E.,
+Deregibus, D., Torre, L., Sahade, R., Tatián, M., Barrera Oro, E., De
+Troch, M., Doyle, S., Quartino, M. L., Saravia, L. A., \& Momo, F. R.
+(2018). The {Food Web} of {Potter Cove} ({Antarctica}): Complexity,
+structure and function. \emph{Estuarine, Coastal and Shelf Science},
+\emph{200}, 141--151. \url{https://doi.org/10.1016/j.ecss.2017.10.015}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Marina2018a}{}}%
@@
 \url{https://doi.org/10.5194/egusphere-2022-1518}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Martin2015}{}}%
+Martin, J. (2015). \emph{{Informe de Campaña Banco Burdwood/Namuncurá
+\textendash{} Tierra del Fuego}} (p. 78) {[}\{Field campaign
+Report\}{]}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Moles2015}{}}%
+Moles, J., Núñez-Pons, L., Taboada, S., Figuerola, B., Cristobo, J., \&
+Avila, C. (2015). Anti-predatory chemical defences in {Antarctic}
+benthic fauna. \emph{Marine Biology}, \emph{162}(9), 1813--1821.
+\url{https://doi.org/10.1007/s00227-015-2714-9}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Montoya2002}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Morales-Castilla2015}{}}%
+Morales-Castilla, I., Matias, M. G., Gravel, D., \& Araújo, M. B.
+(2015). Inferring biotic interactions from proxies. \emph{Trends in
+Ecology \& Evolution}, \emph{30}(6), 347--356.
+\url{https://doi.org/10.1016/j.tree.2015.03.014}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Neutel2002}{}}%
@@
 \url{https://doi.org/10.1007/s12080-015-0282-8}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Nunez-Pons2010}{}}%
+Núñez-Pons, L., Forestieri, R., Nieto, R. M., Varela, M., Nappo, M.,
+Rodríguez, J., Jiménez, C., Castelluccio, F., Carbone, M., Ramos-Espla,
+A., Gavagnin, M., \& Avila, C. (2010). Chemical defenses of tunicates of
+the genus {Aplidium} from the {Weddell Sea} ({Antarctica}). \emph{Polar
+Biology}, \emph{33}(10), 1319--1329.
+\url{https://doi.org/10.1007/s00300-010-0819-7}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Ospina-Alvarez2020}{}}%
+Ospina-Alvarez, A., de Juan, S., Alós, J., Basterretxea, G.,
+Alonso-Fernández, A., Follana-Berná, G., Palmer, M., \& Catalán, I.
+(2020). {MPA} network design based on graph theory and emergent
+properties of larval dispersal. \emph{Marine Ecology Progress Series},
+\emph{650}, 309--326. \url{https://doi.org/10.3354/meps13399}
 
@@
 \url{https://doi.org/10.7717/peerj.251}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Pomeranz2019}{}}%
+Pomeranz, J. P. F., Thompson, R. M., Poisot, T., \& Harding, J. S.
+(2019). Inferring predator\textendash prey interactions in food webs.
+\emph{Methods in Ecology and Evolution}, \emph{10}(3), 356--367.
+\url{https://doi.org/10.1111/2041-210X.13125}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Prieto2022}{}}%
+Prieto, I. M., Paola, A., Pérez, M., García, M., Blustein, G., Schejter,
+L., \& Palermo, J. A. (2022). Antifouling {Diterpenoids} from the
+{Sponge} {\emph{Dendrilla}}{ \emph{Antarctica}}. \emph{Chemistry \&
+Biodiversity}, \emph{19}(2).
+\url{https://doi.org/10.1002/cbdv.202100618}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-RojodeAlmeida2010}{}}%
+Rojo de Almeida, M. T., Siless, G. E., Perez, C. D., Veloso, M. J.,
+Schejter, L., Puricelli, L., \& Palermo, J. A. (2010). Dolabellane
+{Diterpenoids} from the {South Atlantic Gorgonian} {\emph{Convexella}}{
+\emph{Magelhaenica}}. \emph{Journal of Natural Products}, \emph{73}(10),
+1714--1717. \url{https://doi.org/10.1021/np100337j}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Sala2018}{}}%
@@
 including multiplex networks}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Schejter2017}{}}%
+Schejter, L. (2017). \emph{{Informe de Campaña Banco Burdwood}} (p. 296)
+{[}\{Field campaign Report\}{]}.
 

### 2023-04-30 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Update

@@
 Ecosystems with a pronounced 'wasp-waist' structure are suggested to present a high trophic redundancy, since many species would show similar trophic habits [@Cury2000].
-The significant negative relationship between trophic similarity and trophic level enhances the hypothesis of functional redundancy at low and mid-TL species compared to higher TL species for the MPA N-BB food web [@Riccialdelli2020].
+The significant negative relationship between trophic similarity and trophic level enhances the hypothesis of functional similarity at low and mid-TL species compared to higher TL species for the MPA N-BB food web [@Riccialdelli2020].
 At the same time, our results highlight the uniqueness in terms of the trophic role of high-TL predators.

### 2023-05-01 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Updates Claudia Boy

@@
 In the sub-Antarctic region, the level of ocean protection is mainly associated to oceanic islands, such as the South Georgia and South Sandwich, Bouvet, Prince Edward, and Macquarie islands [@IUCN2023].
-Interestingly, the case of the MPAs Namuncurá - Banco Burdwood I and II (MPA N-BB), which is the focus of this work, is unique since these MPAs are associated to a submarine plateau and its southern adjacent deep slope region, respectively [@Falabella2017].
+Interestingly, the case of the MPAs Namuncurá - Banco Burdwood I and II (MPA N-BB, 53º–55ºS 56º–62ºW), which is the focus of this work, is unique since these MPAs are associated to a submarine plateau and its southern adjacent deep slope region, respectively [@Falabella2017].
 In addition, such MPAs are part of a network of protected areas in the sub-Antarctic area (jointly with MPA Yaganes) that aims to protect and strengthen the functioning of this southern region to maintain global ocean health.
@@
 Recently, the structure of the southwestern South Atlantic Ocean has been proposed to be under a 'wasp-waist' control, meaning that the structure and dynamics of the ecosystem are regulated primarily by mid-trophic level species (e.g., fishes, crustaceans) [@Padovani2012; @Saporiti2015; @Riccialdelli2020].
-In particular, the ecosystem of the MPA N-BB shows a more pronounced 'wasp-waist' structure than other sub-Antarctic areas, such as the Atlantic coast of Tierra del Fuego.
+In particular, the ecosystem of the MPA N-BB shows a more pronounced 'wasp-waist' structure, meaning a shorter food-chain length and a greater trophic overlap and redundancy, than other sub-Antarctic areas, such as the Atlantic coast of Tierra del Fuego.
 The Fuegian sprat *Sprattus fuegensis* and longtail southern cod *Patagonotothen ramsayi* are considered the most plausible 'wasp-waist' species [@Riccialdelli2020].
 
-High-latitude marine ecosystems, such as the MPA N-BB, are characterized by an unexpected complexity in terms of biodiversity and ecological interactions [@Day2013; @Kortsch2019; @Cordone2020; @Trathan2021].
+High-latitude marine ecosystems, such as the MPA N-BB, are considered complex systems in terms of biodiversity and ecological interactions [@Day2013; @Kortsch2019; @Cordone2020; @Trathan2021].
 Although there is a robust knowledge about the complexity considering the richness of the benthic and plankton communities in the MPA N-BB ecosystem [@Schejter2016; @Guinder2020; @Schejter2020; @APN2022], a better understanding of species interactions' complexity and structure is needed.
@@
 
-The MPAs Namuncurá - Banco Burdwood I and II, created by National Laws 26.875 and 27.490, comprise a shallow submarine plateau called Burdwood Bank (BB) and a deep slope that reaches 4000 m in depth, N-BB I and N-BB II, respectively [@APN2023].
-They are located 150 km east of Isla de los Estados and 200 km south of Malvinas/Falkland Islands (Figure 1).
+The MPAs Namuncurá - Banco Burdwood I and II, created by National Laws 26.875 and 27.490, comprise a shallow submarine plateau called Burdwood Bank (BB) and a deep slope that reaches 4000 m in depth, N-BB I and N-BB II, respectively [@APN2023] (Figure 1).
+They are located 150 km east of Isla de los Estados and 200 km south of Malvinas/Falkland Islands.
 The MPA N-BB I comprises nearly 34,000 km^2^ circumscribed by the 200 m isobath, between 54º–55ºS and 56º–62ºW, with a slight slope extended nearly 370 km east–west.
@@
 In order to build the network of predator-prey interactions, we reviewed more than 150 references considering published articles, Ph.D.
-theses, public databases, and reports belonging to xx research cruises conducted in the MPAs N-BB I and II.
+theses, public databases, and reports belonging to 16 research cruises conducted in the MPAs N-BB I and II during 2014-2019.
 Here it is important to note that the sampling effort was greater in the MPA N-BB I.
@@
 The distribution of prey among predators showed that most consumers fed on a low number of prey whereas few had multiple preys (Figure 3B).
-These were the top-five predators in number of prey: yellowfin notothen *Patagonotothen guntheri* (Notothenioid fish, 52 prey), rock cod *Patagonotothen ramsayi* (Notothenioid fish, 50 prey), Patagonian toothfish *Dissostichus eleginoides* (Notothenioid fish, 30 prey), broad nose skate *Bathyraja brachyurops* (Chondrichthyan, 30 prey), and graytail skate *Bathyraja griseocauda* (Chondrichthyan, 28 prey).
+The top-five predators in number of prey were: yellowfin notothen *Patagonotothen guntheri* (Notothenioid fish, 52 prey), rock cod *Patagonotothen ramsayi* (Notothenioid fish, 50 prey), Patagonian toothfish *Dissostichus eleginoides* (Notothenioid fish, 30 prey), broad nose skate *Bathyraja brachyurops* (Chondrichthyan, 30 prey), and graytail skate *Bathyraja griseocauda* (Chondrichthyan, 28 prey).
 Following the same distribution pattern, few prey presented multiple predators (Figure 3C).
-These were the top-five prey in number of predators: Detritus (Non-living, 153 predators), the three categories of Diatoms considered (benthic, centric and pennate, 72 predators on average), and species of the genus *Euphausia* (Zooplankton, 46 predators).
-Finally, taking into account the interactions within each functional group, again most interactions were concentrated in a few species (Figure 3D).
+The top-five prey in number of predators were: Detritus (Non-living, 153 predators), the three categories of Diatoms considered (benthic, centric and pennate, 72 predators on average), and species of the genus *Euphausia* (Zooplankton, 46 predators).
+Finally, taking into account the interactions within each functional group, most interactions were concentrated in a few species (Figure 3D).
 The most evident species were: *Themisto gaudichaudii* (Amphipoda), *Zygochlamys patagonica* (Bivalvia), *Aspidostoma giganteum* (Bryozoa), *Munida gregaria* (Decapoda), *Patagonotothen ramsayi* and *Patagonotothen guntheri* (bentho-pelagic fish), *Psychrolutes marmoratus* (demersal fish), and species of *Euphausia* (Zooplankton).
@@
 the higher the species' TL, the lower the trophic similarity or the higher the uniqueness in terms of trophic role (Figure 4C).
-Here it is noteworthy to highlight those high-trophic level species with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster sp* (echinoderms), *Phalacrocorax_atriceps* and *Eudyptes chrysocome* (sea birds), and *Lagenorhynchus cruciger* and *Mesoplodon bowdoini* (marine mammals) (Table S3).
+Here it is noteworthy to highlight those high-trophic level species with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster sp* (echinoderms), *Phalacrocorax atriceps* and *Eudyptes chrysocome* (sea birds), and *Lagenorhynchus cruciger* and *Mesoplodon bowdoini* (marine mammals) (Table S3).
 
@@
 The following were the five species with a network connector role: Detritus, Diatoms (benthic, centric and pennate), and *Patagonotothen ramsayi*.
-The 35 species with a module connector role represent these functional groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Cnidaria, Cumacea, Decapoda, detritus, Diatoms, Dinoflagellates, Echinodermata, fish (bentho-pelagic, demersal, Chondrichthyes), Foraminifera, Polychaeta, Porifera, Pycnogonida, sea birds, and zooplankton (see Supplementary Material Table S3 for the identity of the species).
+The 35 species with a module connector role represent these functional groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Cnidaria, Cumacea, Decapoda, detritus, Diatoms, Dinoflagellates, Echinodermata, fish (bentho-pelagic and demersal Osteichthyes, and Chondrychthyes), Foraminifera, Polychaeta, Porifera, Pycnogonida, sea birds, and zooplankton (see Supplementary Material Table S3 for the identity of the species).
 
@@
 Each point represents a species.
-Linear regressions for betweenness ($y = 72.48x - 111.98, R^2 = 0.04, p-value < 3.38e-05$), closeness ($y = 5.78e-06x - 9.37e-04, R^2 = -0.0005, p-value = 0.37$) and trophic similarity ($y = -0.01x - 0.11, R^2 = 0.07, p-value = 6.76e-08$).
-Note that for A, B and C panels only species with TLs equal or greater than 2 were considered."}
+Linear regressions for betweenness ($y = x - , R^2 = , p-value < $), closeness ($y = x - , R^2 = , p-value = $) and trophic similarity ($y = x - , R^2 = , p-value = $).
+Note that for panels A, B and C only species with TLs equal or greater than 2 were considered."}
 # Betweenness, Closeness, Trophic similarity & Topological role by Trophic level
@@
   geom_point(size=0.3) +
+  xlim(2, 5) +
   geom_smooth(method = "lm") +
@@
   scale_fill_manual(values=cols) +
+  ylim(1, 5) +
   labs(x = "Topological role", y = "Trophic level") +
@@
 Such asymmetry is a well-known feature in empirical complex food webs in particular [@Dunne2002a; @Montoya2003; @Stouffer2005], and has received great attention in complex networks in general [@Albert2002; @Newman2003].
-The degree distribution affects the resilience of complex food webs against random failures and intentional attacks: food webs showing right-skewed distributions, like the one described in this study, are more vulnerable to the removal of the most connected species or hubs, with the potential of producing secondary extinctions and a catastrophic fragmentation of the network [@Albert2000; @Dunne2002; @Eklof2006].
+The degree distribution affects the resilience of complex food webs against random failures and pressure on a particular component of the web: food webs showing right-skewed distributions, like the one described in this study, are more vulnerable to the removal of the most connected species or hubs, with the potential of producing secondary extinctions and a catastrophic fragmentation of the network [@Albert2000; @Dunne2002; @Eklof2006].
 
@@
 We have identified the longtail southern cod *Patagonotothen ramsayi* as the most important species in this sense.
-Moreover, in light of our analysis, other species like the Patagonian toothfish *Dissostichus eleginoides*, the Patagonian cod *Salilota australis*, the yellowfin notothen *Patagonotothen guntheri*, and the Patagonian longfin squid *Doryteuthis gahi* should be considered as relevant in the energy transfer in the ecosystem.
+Moreover, in light of our analysis, other species like the Patagonian toothfish *Dissostichus eleginoides*, the Patagonian cod *Salilota australis*, the yellowfin notothenioid *Patagonotothen guntheri*, and the Patagonian longfin squid *Doryteuthis gahi* should be considered as relevant in the energy transfer in the ecosystem.
 All these species have a mid-trophic position in the food web, supporting the 'wasp-waist' control hypothesis for the MPA N-BB [@Riccialdelli2020].
@@
 
-Caveats:
 The food web studied in the present work might be more representative of the MPA Namuncurá - Banco Burdwood I ecosystem, which comprises the shallow submarine plateau called Burdwood Bank.
@@
 deep flanks to the south).
-As a consequence most of the data we used to build the network comes from studies performed in the MPA N-BB I.
+As a consequence most of the data we used to build the network come from studies performed in the MPA N-BB I.
 Despite this fact, we decided to build the food web considering both MPAs due to the tight oceanographic and ecological connection that exists among them [references in @APN2022].
@@
 abundance, biomass) to assess the species' role in the food web.
-Although there exists such data for some species of the MPA N-BB [@Schejter2021], it would not be possible to incorporate it in the food web framework described here due to a taxonomical resolution mismatch.
+Although there exists such data for some species [@Schejter2021], it would not be possible to include it in the food web framework described here due to a taxonomical resolution mismatch.
 In this regard, we should mention the case of *Zygochlamys patagonica* (Bivalvia) that is highlighted by our species-level analyses though it has been found in low abundances in the area [@Schejter2021].
@@
 Some species of sessile suspension feeders in high-latitude marine ecosystems, such as sponges, ascidians and octocorals, avoid predation by producing secondary metabolites that function as a chemical defense [@Nunez-Pons2010; @Moles2015; @Prieto2022].
-Although this was not reported at the MPA N-BB, there are few studies that reported it other locations in species that were found in the MPA N-BB [@RojodeAlmeida2010].
-Thus, the interactions that we considered between these species and their predators should be taken with caution.
+Although this was not yet recorded at the MPA N-BB, there are a few studies that reported it in other locations in species that inhabit the MPA N-BB [@RojodeAlmeida2010].
 
-Seasonal variation in predators' diet due to food source availability.
-@Brose2019
-
-Spatial variation of study area: Banco Burdwood west-east gradient.
-In the oceanic BB area, complex oceanographic conditions generate an internal spatial heterogeneity, mainly along its longitudinal axis [@Matano2019], and consequently, plankton communities respond with different spatial distributions [@Spinelli2020].
-@Kortsch2019
+The MPA N-BB I presents complex oceanographic conditions that generate an internal spatial heterogeneity, mainly along its longitudinal axis [@Matano2019].
+Up to date this heterogeneity has been reflected in phytoplankton and zooplankton communities [@Bertola2018; @GarciaAlonso2020; @Spinelli2020], and in fish assemblages [@Delpiani2020].
+Moreover, seasonal variations also occur in some physical and biological aspects of the MPA N-BB I [@GarciaAlonso2018; @Matano2019].
+Although we were aware of it, we decided to characterize a food web representing the whole MPA N-BB I year round since this is the first study of its type in the area.
 
@@
 
-* Incorporate habitat heterogeneity, since the benthic community in the BB and deep flanks differs [@Schejter2021].
-This heterogeneity might lead to distinct food web properties, hence differences in ecosystem functioning and response to anthropogenic and environmental perturbations [@Cordone2020].
+Incorporate habitat heterogeneity, since the benthic community in the BB and deep flanks differs [; @Schejter2021].
+This heterogeneity might lead to distinct food web properties, hence differences in ecosystem functioning and response to anthropogenic and environmental perturbations [@Kortsch2019; @Cordone2020].
 El caso de las ascidias (Tatián)
 
-* Incorporate species traits, like body size and mass, which are known to be important drivers in predator-prey interactions.
+Incorporate species traits, like body size and mass, which are known to be important drivers in predator-prey interactions. @LaMesa2016
 
-* Simulate perturbations on food web and target species: mercury transfer, microplastic pollution, fisheries.
+Simulate perturbations on food web and target species: mercury transfer, microplastic pollution, fisheries.
 @Cossi2021; @DiMauro2022; @Fioramonti2022
 
-* Estimation of interaction strength considering species and interaction traits (i.e.
+Estimation of interaction strength considering species and interaction traits (i.e.
 body size, body mass, interaction dimensionality) to gain insights into food web stability and response to anthropogenic and environmental perturbations.

### 2023-05-01 MS_ToSubmit/MS_Burdwood_foodweb.tex
Updates Claudia Boy

@@
 UNEP-WCMC, 2023). Interestingly, the case of the MPAs Namuncurá - Banco
-Burdwood I and II (MPA N-BB), which is the focus of this work, is unique
-since these MPAs are associated to a submarine plateau and its southern
-adjacent deep slope region, respectively (Falabella, 2017). In addition,
-such MPAs are part of a network of protected areas in the sub-Antarctic
-area (jointly with MPA Yaganes) that aims to protect and strengthen the
-functioning of this southern region to maintain global ocean health.
+Burdwood I and II (MPA N-BB, 53º--55ºS 56º--62ºW), which is the focus of
+this work, is unique since these MPAs are associated to a submarine
+plateau and its southern adjacent deep slope region, respectively
+(Falabella, 2017). In addition, such MPAs are part of a network of
+protected areas in the sub-Antarctic area (jointly with MPA Yaganes)
+that aims to protect and strengthen the functioning of this southern
+region to maintain global ocean health.
 
@@
 and biodiverse benthic habitat that was barely known (Falabella, 2017;
-L. Schejter et al., 2016). The benthic community is featured by high
+Schejter et al., 2016). The benthic community is featured by high
 biomass of vulnerable and fragile species (mainly Porifera and Cnidaria)
@@
 provides habitat to several small-sized species (López-Gappa et al.,
-2018; L. Schejter \& Bremec, 2019; Sirito, 2019), and has an important
-role in the life history of fishes as a food source, refuge and nursery
-area (Covatti Ale et al., 2022; Delpiani et al., 2020; Fischer et al.,
-2022; Florencia et al., 2023; García Alonso et al., 2018; Troccoli et
-al., 2020). The maintenance of this singular community is related to
-local and regional oceanographic processes, including the circulation of
-the rich Malvinas (Falkland) current in the area (Guerrero et al., 1999;
-A. R. Piola \& Gordon, 1989) and the upwelling and mixing phenomena
-(Matano et al., 2019). The input of nutrients from the Malvinas
-(Falkland) current also supports a diverse plankton community (Guinder
-et al., 2020). Overall, 811 benthic and plankton species have been
-identified for the MPA N-BB ecosystem, where 349 were reported for the
-first time in the area in recent years (APN, 2022). However, identifying
-the main species involved in the maintenance of ecosystem services and
-health as well as for management and conservation is essential.
+2018; Schejter \& Bremec, 2019; Sirito, 2019), and has an important role
+in the life history of fishes as a food source, refuge and nursery area
+(Covatti Ale et al., 2022; Delpiani et al., 2020; Fischer et al., 2022;
+Florencia et al., 2023; García Alonso et al., 2018; Troccoli et al.,
+2020). The maintenance of this singular community is related to local
+and regional oceanographic processes, including the circulation of the
+rich Malvinas (Falkland) current in the area (Guerrero et al., 1999; A.
+R. Piola \& Gordon, 1989) and the upwelling and mixing phenomena (Matano
+et al., 2019). The input of nutrients from the Malvinas (Falkland)
+current also supports a diverse plankton community (Guinder et al.,
+2020). Overall, 811 benthic and plankton species have been identified
+for the MPA N-BB ecosystem, where 349 were reported for the first time
+in the area in recent years (APN, 2022). However, identifying the main
+species involved in the maintenance of ecosystem services and health as
+well as for management and conservation is essential.
 
@@
 the ecosystem of the MPA N-BB shows a more pronounced `wasp-waist'
-structure than other sub-Antarctic areas, such as the Atlantic coast of
-Tierra del Fuego. The Fuegian sprat \emph{Sprattus fuegensis} and
-longtail southern cod \emph{Patagonotothen ramsayi} are considered the
-most plausible `wasp-waist' species (Riccialdelli et al., 2020).
-
-High-latitude marine ecosystems, such as the MPA N-BB, are characterized
-by an unexpected complexity in terms of biodiversity and ecological
-interactions (Cordone et al., 2020; Day et al., 2013; Kortsch et al.,
-2019; Trathan et al., 2021). Although there is a robust knowledge about
-the complexity considering the richness of the benthic and plankton
-communities in the MPA N-BB ecosystem (APN, 2022; Guinder et al., 2020;
-L. Schejter et al., 2016, 2020), a better understanding of species
-interactions' complexity and structure is needed. This aspect can be
-tackled by analyzing one of the most frequent relationships between
-species: the predator-prey interaction (Bascompte, 2009). The sum of
-predator-prey or trophic interactions of a particular region is referred
-to as a food web, representing the roadmap for matter and energy flow in
-an ecosystem. In recent years, network approaches have been successfully
-applied to study complex high-latitude marine ecosystems, improving our
-knowledge on structure, functioning, and response to
-environmental/anthropogenic changes (Cordone et al., 2018; Funes et al.,
-2022; Kortsch et al., 2015; Marina et al., 2023). Among anthropogenic
-threats, it is worth mentioning that contaminants like mercury and
-microplastics have been recently reported as important threats to the
-MPA N-BB region (Cossi et al., 2021; Di Mauro et al., 2022; Fioramonti
-et al., 2022).
+structure, meaning a shorter food-chain length and a greater trophic
+overlap and redundancy, than other sub-Antarctic areas, such as the
+Atlantic coast of Tierra del Fuego. The Fuegian sprat \emph{Sprattus
+fuegensis} and longtail southern cod \emph{Patagonotothen ramsayi} are
+considered the most plausible `wasp-waist' species (Riccialdelli et al.,
+2020).
+
+High-latitude marine ecosystems, such as the MPA N-BB, are considered
+complex systems in terms of biodiversity and ecological interactions
+(Cordone et al., 2020; Day et al., 2013; Kortsch et al., 2019; Trathan
+et al., 2021). Although there is a robust knowledge about the complexity
+considering the richness of the benthic and plankton communities in the
+MPA N-BB ecosystem (APN, 2022; Guinder et al., 2020; Schejter et al.,
+2016, 2020), a better understanding of species interactions' complexity
+and structure is needed. This aspect can be tackled by analyzing one of
+the most frequent relationships between species: the predator-prey
+interaction (Bascompte, 2009). The sum of predator-prey or trophic
+interactions of a particular region is referred to as a food web,
+representing the roadmap for matter and energy flow in an ecosystem. In
+recent years, network approaches have been successfully applied to study
+complex high-latitude marine ecosystems, improving our knowledge on
+structure, functioning, and response to environmental/anthropogenic
+changes (Cordone et al., 2018; Funes et al., 2022; Kortsch et al., 2015;
+Marina et al., 2023). Among anthropogenic threats, it is worth
+mentioning that contaminants like mercury and microplastics have been
+recently reported as important threats to the MPA N-BB region (Cossi et
+al., 2021; Di Mauro et al., 2022; Fioramonti et al., 2022).
 
@@
 Bank (BB) and a deep slope that reaches 4000 m in depth, N-BB I and N-BB
-II, respectively (APN, 2023). They are located 150 km east of Isla de
-los Estados and 200 km south of Malvinas/Falkland Islands (Figure 1).
-The MPA N-BB I comprises nearly 34,000 km\textsuperscript{2}
-circumscribed by the 200 m isobath, between 54º--55ºS and 56º--62ºW,
-with a slight slope extended nearly 370 km east--west. Physical features
-in the BB are fairly stable, with salinity averaging 34 all year round
-and temperature ranging between 4 and 8ºC (Acha et al., 2004; Guerrero
-et al., 1999; A. Piola \& Falabella, 2009). The BB is surrounded by
-steep flanks of up to 4000 m depth through which strong currents
-circulate (Matano et al., 2019; A. R. Piola \& Gordon, 1989; Reta,
-2014). Such deep slope forms the basis of N-BB II, protecting about
-32,000 km\textsuperscript{2}. Intense upwelling and mixing occur over
-it, entraining deep nutrient-rich waters into the photic layer (Matano
-et al., 2019; A. Piola \& Falabella, 2009) and resulting in a fairly
-homogeneous water column both spatially and temporally (Glorioso \&
-Flather, 1995; Guerrero et al., 1999; Matano et al., 2019).
+II, respectively (APN, 2023) (Figure 1). They are located 150 km east of
+Isla de los Estados and 200 km south of Malvinas/Falkland Islands. The
+MPA N-BB I comprises nearly 34,000 km\textsuperscript{2} circumscribed
+by the 200 m isobath, between 54º--55ºS and 56º--62ºW, with a slight
+slope extended nearly 370 km east--west. Physical features in the BB are
+fairly stable, with salinity averaging 34 all year round and temperature
+ranging between 4 and 8ºC (Acha et al., 2004; Guerrero et al., 1999; A.
+Piola \& Falabella, 2009). The BB is surrounded by steep flanks of up to
+4000 m depth through which strong currents circulate (Matano et al.,
+2019; A. R. Piola \& Gordon, 1989; Reta, 2014). Such deep slope forms
+the basis of N-BB II, protecting about 32,000 km\textsuperscript{2}.
+Intense upwelling and mixing occur over it, entraining deep
+nutrient-rich waters into the photic layer (Matano et al., 2019; A.
+Piola \& Falabella, 2009) and resulting in a fairly homogeneous water
+column both spatially and temporally (Glorioso \& Flather, 1995;
+Guerrero et al., 1999; Matano et al., 2019).
 
@@
 more than 150 references considering published articles, Ph.D.~theses,
-public databases, and reports belonging to xx research cruises conducted
-in the MPAs N-BB I and II. Here it is important to note that the
-sampling effort was greater in the MPA N-BB I. Furthermore, we took into
-account personal communications from experts belonging to the working
-group of the study area
+public databases, and reports belonging to 16 research cruises conducted
+in the MPAs N-BB I and II during 2014-2019. Here it is important to note
+that the sampling effort was greater in the MPA N-BB I. Furthermore, we
+took into account personal communications from experts belonging to the
+working group of the study area
 (https://www.pampazul.gob.ar/tag/banco-burdwood/). The diversity of the
@@
 that most consumers fed on a low number of prey whereas few had multiple
-preys (Figure 3B). These were the top-five predators in number of prey:
+preys (Figure 3B). The top-five predators in number of prey were:
 yellowfin notothen \emph{Patagonotothen guntheri} (Notothenioid fish, 52
@@
 same distribution pattern, few prey presented multiple predators (Figure
-3C). These were the top-five prey in number of predators: Detritus
+3C). The top-five prey in number of predators were: Detritus
 (Non-living, 153 predators), the three categories of Diatoms considered
@@
 the genus \emph{Euphausia} (Zooplankton, 46 predators). Finally, taking
-into account the interactions within each functional group, again most
+into account the interactions within each functional group, most
 interactions were concentrated in a few species (Figure 3D). The most
@@
 acanthias} (Chondrichthyans), \emph{Diplopteraster clarki} and
-\emph{Pteraster sp} (echinoderms), \emph{Phalacrocorax\_atriceps} and
+\emph{Pteraster sp} (echinoderms), \emph{Phalacrocorax atriceps} and
 \emph{Eudyptes chrysocome} (sea birds), and \emph{Lagenorhynchus
@@
 Brachiopoda, Bryozoa, Cnidaria, Cumacea, Decapoda, detritus, Diatoms,
-Dinoflagellates, Echinodermata, fish (bentho-pelagic, demersal,
-Chondrichthyes), Foraminifera, Polychaeta, Porifera, Pycnogonida, sea
-birds, and zooplankton (see Supplementary Material Table S3 for the
-identity of the species).
+Dinoflagellates, Echinodermata, fish (bentho-pelagic and demersal
+Osteichthyes, and Chondrychthyes), Foraminifera, Polychaeta, Porifera,
+Pycnogonida, sea birds, and zooplankton (see Supplementary Material
+Table S3 for the identity of the species).
 
@@
 Each point represents a species.
-Linear regressions for betweenness ($y = 72.48x - 111.98, R^2 = 0.04, p-value < 3.38e-05$), closeness ($y = 5.78e-06x - 9.37e-04, R^2 = -0.0005, p-value = 0.37$) and trophic similarity ($y = -0.01x - 0.11, R^2 = 0.07, p-value = 6.76e-08$).
-Note that for A, B and C panels only species with TLs equal or greater than 2 were considered.}\label{fig:figure4}
+Linear regressions for betweenness ($y = x - , R^2 = , p-value < $), closeness ($y = x - , R^2 = , p-value = $) and trophic similarity ($y = x - , R^2 = , p-value = $).
+Note that for panels A, B and C only species with TLs equal or greater than 2 were considered.}\label{fig:figure4}
 \end{figure}
@@
 2002; Newman, 2003). The degree distribution affects the resilience of
-complex food webs against random failures and intentional attacks: food
-webs showing right-skewed distributions, like the one described in this
-study, are more vulnerable to the removal of the most connected species
-or hubs, with the potential of producing secondary extinctions and a
-catastrophic fragmentation of the network (Albert et al., 2000; Dunne et
-al., 2002b; Eklöf \& Ebenman, 2006).
+complex food webs against random failures and pressure on a particular
+component of the web: food webs showing right-skewed distributions, like
+the one described in this study, are more vulnerable to the removal of
+the most connected species or hubs, with the potential of producing
+secondary extinctions and a catastrophic fragmentation of the network
+(Albert et al., 2000; Dunne et al., 2002b; Eklöf \& Ebenman, 2006).
 
@@
 most demanded source we identified in this study (i.e.~detritus)
-supports the abundant benthic community of filter-feeders (L. Schejter
-et al., 2016). Furthermore, we found that the second and third-most
+supports the abundant benthic community of filter-feeders (Schejter et
+al., 2016). Furthermore, we found that the second and third-most
 consumed prey were diatoms and species of \emph{Euphausia},
@@
 eleginoides}, the Patagonian cod \emph{Salilota australis}, the
-yellowfin notothen \emph{Patagonotothen guntheri}, and the Patagonian
-longfin squid \emph{Doryteuthis gahi} should be considered as relevant
-in the energy transfer in the ecosystem. All these species have a
-mid-trophic position in the food web, supporting the `wasp-waist'
+yellowfin notothenioid \emph{Patagonotothen guntheri}, and the
+Patagonian longfin squid \emph{Doryteuthis gahi} should be considered as
+relevant in the energy transfer in the ecosystem. All these species have
+a mid-trophic position in the food web, supporting the `wasp-waist'
 control hypothesis for the MPA N-BB (Riccialdelli et al., 2020).
@@
 relationship between trophic similarity and trophic level enhances the
-hypothesis of functional redundancy at low and mid-TL species compared
+hypothesis of functional similarity at low and mid-TL species compared
 to higher TL species for the MPA N-BB food web (Riccialdelli et al.,
@@
 
-Caveats: The food web studied in the present work might be more
-representative of the MPA Namuncurá - Banco Burdwood I ecosystem, which
-comprises the shallow submarine plateau called Burdwood Bank. This is
-related to the sampling effort that was conducted during the research
-cruises in the former MPA compared to the MPA N-BB II (i.e.~deep flanks
-to the south). As a consequence most of the data we used to build the
-network comes from studies performed in the MPA N-BB I. Despite this
-fact, we decided to build the food web considering both MPAs due to the
-tight oceanographic and ecological connection that exists among them
-(references in APN, 2022).
+The food web studied in the present work might be more representative of
+the MPA Namuncurá - Banco Burdwood I ecosystem, which comprises the
+shallow submarine plateau called Burdwood Bank. This is related to the
+sampling effort that was conducted during the research cruises in the
+former MPA compared to the MPA N-BB II (i.e.~deep flanks to the south).
+As a consequence most of the data we used to build the network come from
+studies performed in the MPA N-BB I. Despite this fact, we decided to
+build the food web considering both MPAs due to the tight oceanographic
+and ecological connection that exists among them (references in APN,
+2022).
 
@@
 (i.e.~abundance, biomass) to assess the species' role in the food web.
-Although there exists such data for some species of the MPA N-BB
-(Schejter \& Albano, 2021), it would not be possible to incorporate it
-in the food web framework described here due to a taxonomical resolution
-mismatch. In this regard, we should mention the case of
-\emph{Zygochlamys patagonica} (Bivalvia) that is highlighted by our
-species-level analyses though it has been found in low abundances in the
-area (Schejter \& Albano, 2021).
+Although there exists such data for some species (Schejter \& Albano,
+2021), it would not be possible to include it in the food web framework
+described here due to a taxonomical resolution mismatch. In this regard,
+we should mention the case of \emph{Zygochlamys patagonica} (Bivalvia)
+that is highlighted by our species-level analyses though it has been
+found in low abundances in the area (Schejter \& Albano, 2021).
 
@@
 (Moles et al., 2015; Núñez-Pons et al., 2010; Prieto et al., 2022).
-Although this was not reported at the MPA N-BB, there are few studies
-that reported it other locations in species that were found in the MPA
-N-BB (Rojo de Almeida et al., 2010). Thus, the interactions that we
-considered between these species and their predators should be taken
-with caution.
-
-Seasonal variation in predators' diet due to food source availability.
-Brose et al. (2019)
-
-Spatial variation of study area: Banco Burdwood west-east gradient. In
-the oceanic BB area, complex oceanographic conditions generate an
-internal spatial heterogeneity, mainly along its longitudinal axis
-(Matano et al., 2019), and consequently, plankton communities respond
-with different spatial distributions (Spinelli et al., 2020). Kortsch et
-al. (2019)
+Although this was not yet recorded at the MPA N-BB, there are a few
+studies that reported it in other locations in species that inhabit the
+MPA N-BB (Rojo de Almeida et al., 2010).
+
+The MPA N-BB I presents complex oceanographic conditions that generate
+an internal spatial heterogeneity, mainly along its longitudinal axis
+(Matano et al., 2019). Up to date this heterogeneity has been reflected
+in phytoplankton and zooplankton communities (Bértola et al., 2018;
+García Alonso et al., 2020; Spinelli et al., 2020), and in fish
+assemblages (Delpiani et al., 2020). Moreover, seasonal variations also
+occur in some physical and biological aspects of the MPA N-BB I (García
+Alonso et al., 2018; Matano et al., 2019). Although we were aware of it,
+we decided to characterize a food web representing the whole MPA N-BB I
+year round since this is the first study of its type in the area.
 
@@
 
-\begin{itemize}
-\item
-  Incorporate habitat heterogeneity, since the benthic community in the
-  BB and deep flanks differs (Schejter \& Albano, 2021). This
+Incorporate habitat heterogeneity, since the benthic community in the BB
+and deep flanks differs {[}; Schejter \& Albano (2021){]}. This
 heterogeneity might lead to distinct food web properties, hence
 differences in ecosystem functioning and response to anthropogenic and
-  environmental perturbations (Cordone et al., 2020). El caso de las
-  ascidias (Tatián)
-\item
-  Incorporate species traits, like body size and mass, which are known
-  to be important drivers in predator-prey interactions.
-\item
-  Simulate perturbations on food web and target species: mercury
-  transfer, microplastic pollution, fisheries. Cossi et al. (2021); Di
-  Mauro et al. (2022); Fioramonti et al. (2022)
-\item
+environmental perturbations (Cordone et al., 2020; Kortsch et al.,
+2019). El caso de las ascidias (Tatián)
+
+Incorporate species traits, like body size and mass, which are known to
+be important drivers in predator-prey interactions. La Mesa et al.
+(2016)
+
+Simulate perturbations on food web and target species: mercury transfer,
+microplastic pollution, fisheries. Cossi et al. (2021); Di Mauro et al.
+(2022); Fioramonti et al. (2022)
+
 Estimation of interaction strength considering species and interaction
@@
 (2018); Kortsch et al. (2021)
-\end{itemize}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Bertola2018}{}}%
+Bértola, G., Olguín Salinas, H., \& Alder, V. A. (2018). Distribución
+espacial de {Rhizosolenia} crassa, \textquestiondown especie clave del
+banco burdwood? \emph{Libro de Resúmenes {X Jornadas Nacionales} de
+{Ciencias} Del {Mar}}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Bornatowski2017}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-GarciaAlonso2020}{}}%
+García Alonso, V. A., Brown, D. R., Pájaro, M., \& Capitanio, F. L.
+(2020). Growing {Up Down South}: {Spatial} and {Temporal Variability} in
+{Early Growth} of {Fuegian Sprat Sprattus} fuegensis {From} the
+{Southwest Atlantic Ocean}. \emph{Frontiers in Marine Science},
+\emph{7}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-GarciaAlonso2018}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-LaMesa2016}{}}%
+La Mesa, M., Riginella, E., Melli, V., Bartolini, F., \& Mazzoldi, C.
+(2016). Biological traits of a sub-{Antarctic} nototheniid,
+{Patagonotothen} ramsayi, from the {Burdwood Bank}. \emph{Polar
+Biology}, \emph{39}(1), 103--111.
+\url{https://doi.org/10.1007/s00300-015-1663-6}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Lai2012}{}}%
@@
 {[}\{Field campaign Report\}{]}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Schejter2021}{}}%
+Schejter, L., \& Albano, M. (2021). Benthic communities at the marine
+protected area {Namuncurá}/{Burdwood} bank, {SW Atlantic Ocean}:
+Detection of vulnerable marine ecosystems and contributions to the
+assessment of the rezoning process. \emph{Polar Biology}, \emph{44}(10),
+2023--2037. \url{https://doi.org/10.1007/s00300-021-02936-y}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Schejter2021}{}}%
-Schejter, \& Albano. (2021). Benthic communities at the marine protected
-area {Namuncurá}/{Burdwood} bank, {SW Atlantic Ocean}: Detection of
-vulnerable marine ecosystems and contributions to the assessment of the
-rezoning process. \emph{Polar Biology}, \emph{44}(10), 2023--2037.
-\url{https://doi.org/10.1007/s00300-021-02936-y}
-
 \leavevmode\vadjust pre{\hypertarget{ref-Scotti2010}{}}%

### 2023-05-05 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Urteaga & Bruno suggs

@@
 Furthermore, we identified several species as important in terms of different aspects of trophic structure and functioning, and response to perturbations.
-We suggest that generalist species, mainly fishes, play a crucial role in the ecosystem's bentho-pelagic coupling process.
-In addition, we propose that other species besides the longtail southern cod *Patagonotothen ramsayi* and the Fueguian sprat *Sprattus fuegensis* should be considered as relevant energy transfers for the ecosystem.
+We suggest that generalist species, mainly fishes, play a crucial role in the ecosystem's bentho-pelagic coupling process and that other species, besides the longtail southern cod *Patagonotothen ramsayi* and the Fueguian sprat *Sprattus fuegensis*, should be considered as relevant energy transfers for the ecosystem.
 Finally, we argue that the diversity of species, including both the benthic and pelagic habitats, is responsible for seccuring the connectivity within the food web against perturbations, therefore contributing to the structure and stability of the ecosystem.
@@
 
-load("../results/summary_results_apr23.rda")
+load("../results/summary_results_may23.rda")
 
@@
 The degree distribution of the food web showed an asymmetric frequency in the number of interactions, where most of the species had a relatively low number of interactions and few species concentrated most of them (Figure 3A).
-The distribution of prey among predators showed that most consumers fed on a low number of prey whereas few had multiple preys (Figure 3B).
+The distribution of prey among predators showed that most consumers fed on a low number of prey whereas few had multiple prey (Figure 3B).
 The top-five predators in number of prey were: yellowfin notothen *Patagonotothen guntheri* (Notothenioid fish, 52 prey), rock cod *Patagonotothen ramsayi* (Notothenioid fish, 50 prey), Patagonian toothfish *Dissostichus eleginoides* (Notothenioid fish, 30 prey), broad nose skate *Bathyraja brachyurops* (Chondrichthyan, 30 prey), and graytail skate *Bathyraja griseocauda* (Chondrichthyan, 28 prey).
@@
 # Group Degree
-un.prey <- as.data.frame(unique(int_good_res$PreyGroup))  # prey groups
-un.pred <- as.data.frame(unique(int_good_res$PredGroup))  # pred groups
-colnames(un.prey) <- "Group"
-colnames(un.pred) <- "Group"
-unique_FG <- unique(bind_rows(un.pred, un.prey))  # 35 groups
-
-col_palette <- scales::hue_pal()(nrow(unique_FG))
-FGColors <- setNames(col_palette, levels(unique_FG$Group))
-unique_FG <- cbind(unique_FG, as.data.frame(FGColors))
-colnames(unique_FG) <- c("FunctionalGroup", "FGColor")
-
+# RColorBrewer::brewer.pal(11, "RdYlGn")
+# "#A50026" "#D73027" "#F46D43" "#FDAE61" "#FEE08B" "#FFFFBF" "#D9EF8B" "#A6D96A" "#66BD63" "#1A9850" "#006837"
 plot_grpdeg <- spp_total %>% 
@@
     mutate(TL_fg = mean(TL)) %>% 
-    ggplot(., aes(x = TotalDegree, y = reorder(FunctionalGroup, TL_fg), fill = FunctionalGroup)) + 
-    geom_joy(scale = 3.75) +
-    scale_fill_manual(values = FGColors) +
+    mutate(color = case_when(TL_fg <= 1 ~ "#006837",
+                           between(TL_fg, 1.1, 1.95) ~ "#1A9850",
+                           between(TL_fg, 1.98, 2.05) ~ "#66BD63",
+                           between(TL_fg, 2.06, 2.25) ~ "#A6D96A",
+                           between(TL_fg, 2.26, 2.5) ~ "#D9EF8B",
+                           between(TL_fg, 2.51, 3.0) ~ "#FFFFBF",
+                           between(TL_fg, 3.001, 3.25) ~ "#FEE08B",
+                           between(TL_fg, 3.001, 3.25) ~ "#FDAE61",
+                           between(TL_fg, 3.51, 4.0) ~ "#F46D43",
+                           between(TL_fg, 4.01, 4.49) ~ "#D73027",
+                           TL_fg >= 4.5 ~ "#A50026")) %>% 
+    ggplot(., aes(x = TotalDegree, y = reorder(FunctionalGroup, TL_fg))) + 
+    geom_joy(aes(scale = 3.75, fill = color)) +
+    scale_fill_identity() +
     labs(x = "Number of interactions", y = "Functional group", tag="D") +
@@
 figure_3
-
-# # Create layout : nrow = 2, ncol = 2
-# pushViewport(viewport(layout = grid.layout(3, 2)))
-# # A helper function to define a region on the layout
-# define_region <- function(row, col){
-#   viewport(layout.pos.row = row, layout.pos.col = col)
-# } 
-# # Arrange the plots
-# print(a, vp = define_region(1, 1:2))
-# print(b, vp = define_region(2, 1))
-# print(c, vp = define_region(2, 2))
-# print(d, vp = define_region(3, 1:2))
 

### 2023-05-05 R/1_datawrangling.R

@@ -17,7 +17,7 @@ ipak(packages)
 
 ## Lista de Especies ----
 
-sp_raw <- read.csv("data/ListaEspecies_AMPNBB_apr23.csv")
+sp_raw <- read.csv("data/ListaEspecies_AMPNBB_may23.csv")
 colnames(sp_raw)
 sp_raw <- sp_raw %>% 
   add_count(FunctionalGroup, name = "Richness") %>% 
@@ -26,7 +26,7 @@ sp_raw <- sp_raw %>%
 
 ## Lista de Interacciones ----
 
-int_raw <- read.csv("data/ListaInteracciones_AMPNBB_apr23.csv")
+int_raw <- read.csv("data/ListaInteracciones_AMPNBB_may23.csv")
 
 int_raw <- int_raw %>% 
   # low-resolved Phytoplankton
@@ -145,4 +145,4 @@ int_raw <- subset(int_raw, !(Prey %in% "Demospongiae *"))  # exclude rows with P
 ## Save data ----
 
 save(sp_raw, int_raw,
-     file = "data/cleaned-data_apr23.rda")
+     file = "data/cleaned-data_may23.rda")

### 2023-05-05 R/3_foodwebexploring.R

@@ -17,7 +17,7 @@ ipak(packages)
 
 # Cargar datos ----
 
-load("data/cleaned-data_apr23.rda")
+load("data/cleaned-data_may23.rda")
 
 
 # Red trófica ----
@@ -114,4 +114,4 @@ plotTrophLevel(g, ylab = "Trophic level")
 # Save data ----
 
 save(g, int_need_res, int_good_res,
-     file = "data/foodweb-data_apr23.rda")
+     file = "data/foodweb-data_may23.rda")

### 2023-05-05 R/4_foodwebanalysis.R

@@ -18,8 +18,8 @@ ipak(packages)
 
 # Cargar datos ----
 
-load("data/cleaned-data_apr23.rda")
-load("data/foodweb-data_apr23.rda")
+load("data/cleaned-data_may23.rda")
+load("data/foodweb-data_may23.rda")
 
 
 # Análisis ----

### 2023-05-06 R/4_foodwebanalysis.R
Updated results may23

@@ -171,7 +171,7 @@ spp_total <- spp_total %>%
                              FunctionalGroup %in% c("Fish_Demersal") ~ "Demersal"))
 
 
-write_csv(spp_total, file = "results/spp_prop_apr23.csv")
+write_csv(spp_total, file = "results/spp_prop_may23.csv")
 
 
 # Resolución de la red ----
@@ -186,4 +186,4 @@ sp_prop <- sp_count/vcount(g_up)
 # Guardar datos ----
 
 save(g_up, g, deg_dist_fit, prop_topol, spp_total, top.role, top.role.df,
-     file = "results/summary_results_apr23.rda")
+     file = "results/summary_results_may23.rda")

### 2023-05-06 R/5_regressionanalyses.R

@@ -16,7 +16,7 @@ ipak(packages)
 
 
 # Datos ----
-load("results/summary_results_aor23.rda")
+load("results/summary_results_may23.rda")
 
 
 # Linear Regression ----

### 2023-05-07 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Update top roles may23

@@
 
-In terms of complexity, the MPA Namuncurá - Banco Burdwood food web (N-BB I and II) consisted of 1778 predator-prey interactions and 379 species, where 93% of them were defined at the species taxonomical level (Figure 2, Table S2).
-The food web presented a link density (e.g., the average number of interactions per species) of 4.69, and a connectance of 0.01.
+In terms of complexity, the MPA Namuncurá - Banco Burdwood food web (N-BB I and II) consisted of 1796 predator-prey interactions and 380 species, where 93% of them were defined at the species taxonomical level (Figure 2, Table S2).
+The food web presented a link density (e.g., the average number of interactions per species) of 4.73, and a connectance of 0.01.
 Almost half of the consumers were omnivores (0.48), feeding on sources at different trophic levels.
@@
 The distribution of prey among predators showed that most consumers fed on a low number of prey whereas few had multiple prey (Figure 3B).
-The top-five predators in number of prey were: yellowfin notothen *Patagonotothen guntheri* (Notothenioid fish, 52 prey), rock cod *Patagonotothen ramsayi* (Notothenioid fish, 50 prey), Patagonian toothfish *Dissostichus eleginoides* (Notothenioid fish, 30 prey), broad nose skate *Bathyraja brachyurops* (Chondrichthyan, 30 prey), and graytail skate *Bathyraja griseocauda* (Chondrichthyan, 28 prey).
+The top-five predators in number of prey were: yellowfin notothen *Patagonotothen guntheri* (Notothenioid fish, 50 prey), rock cod *Patagonotothen ramsayi* (Notothenioid fish, 49 prey), broad nose skate *Bathyraja brachyurops* (Chondrichthyan, 33 prey), Patagonian toothfish *Dissostichus eleginoides* (Notothenioid fish, 30 prey), and graytail skate *Bathyraja griseocauda* (Chondrichthyan, 28 prey).
 Following the same distribution pattern, few prey presented multiple predators (Figure 3C).
-The top-five prey in number of predators were: Detritus (Non-living, 153 predators), the three categories of Diatoms considered (benthic, centric and pennate, 72 predators on average), and species of the genus *Euphausia* (Zooplankton, 46 predators).
+The top-five prey in number of predators were: Detritus (Non-living, 155 predators), the three categories of Diatoms considered (benthic, centric and pennate, 75 predators on average), and species of the genus *Euphausia* (Zooplankton, 47 predators).
 Finally, taking into account the interactions within each functional group, most interactions were concentrated in a few species (Figure 3D).
-The most evident species were: *Themisto gaudichaudii* (Amphipoda), *Zygochlamys patagonica* (Bivalvia), *Aspidostoma giganteum* (Bryozoa), *Munida gregaria* (Decapoda), *Patagonotothen ramsayi* and *Patagonotothen guntheri* (bentho-pelagic fish), *Psychrolutes marmoratus* (demersal fish), and species of *Euphausia* (Zooplankton).
+The most evident species were: *Doryteuthis gahi* (Cephalopoda), *Grimothea gregaria* (Decapoda), *Patagonotothen ramsayi*, *Patagonotothen guntheri* and *Dissostichus eleginoides* (bentho-pelagic fish), *Sprattus fuegensis* and *Micromesistius australis* (pelagic fish), and species of *Euphausia* and *Themisto gaudichaudii* (Zooplankton).
 Overall, there is an evident asymmetry in the distribution of interactions among species at different levels in the MPA N-BB food web.
@@
 
-load("../data/foodweb-data_apr23.rda")
-load("../results/summary_results_apr23.rda")
+load("../data/foodweb-data_may23.rda")
+load("../results/summary_results_may23.rda")
 
@@
 
-Most species in the food web were consumers, 336 out of 379; the rest were primary producers, such as diatoms (phytoplankton), and non-living food sources like detritus and necromass.
+Most species in the food web were consumers, 339 out of 379; the rest were primary producers, such as diatoms (phytoplankton), and non-living food sources like detritus and necromass.
 
@@
 the higher the species' TL, the lower the trophic similarity or the higher the uniqueness in terms of trophic role (Figure 4C).
-Here it is noteworthy to highlight those high-trophic level species with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster sp* (echinoderms), *Phalacrocorax atriceps* and *Eudyptes chrysocome* (sea birds), and *Lagenorhynchus cruciger* and *Mesoplodon bowdoini* (marine mammals) (Table S3).
+Here it is noteworthy to highlight those high-trophic level species (TL > 3.1) with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster sp* (echinoderms), *Phalacrocorax atriceps* and *Eudyptes chrysocome* (sea birds), and *Lagenorhynchus cruciger* (marine mammals) (Table S3).
 

### 2023-05-07 R/4_foodwebanalysis.R

@@ -176,11 +176,19 @@ write_csv(spp_total, file = "results/spp_prop_may23.csv")
 
 # Resolución de la red ----
 
-res_sp <- as.data.frame(V(g_up)$name)
+res_sp <- as.data.frame(V(g)$name)
 good_res_sp <- sum(str_detect(res_sp[,1], "_"))
-gen_count <- sum(str_detect(res_sp[,1], "_sp"))
-sp_count <- good_res_sp - gen_count
-sp_prop <- sp_count/vcount(g_up)
+#gen_count <- sum(str_detect(res_sp[,1], "_sp"))
+#agr_count <- sum(str_detect(res_sp[,1], "_spp"))
+sp_prop <- good_res_sp/vcount(g)
+
+
+# Especie más conectada por Grupo Funcional ---
+int_grp <- spp_total %>% 
+  dplyr::select(TrophicSpecies, FunctionalGroup, TotalDegree) %>% 
+  group_by(FunctionalGroup, TotalDegree, TrophicSpecies) %>% 
+  summarise() %>% 
+  arrange(FunctionalGroup, TotalDegree)
 
 
 # Guardar datos ----

### 2023-05-08 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
2nd version w/ coauthors suggs

@@
   - code: 6
-    address: Instituto de Biodiversidad y Biología Experimental y Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, Argentina
+    address: Instituto de Biodiversidad y Biologia Experimental y Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, Argentina
   - code: 7
@@
   - code: 8
-    address: Instituto de Diversidad y Ecología Animal (IDEA-CONICET)
+    address: Instituto de Diversidad y Ecologia Animal (IDEA-CONICET)
   - code: 9
-    address: Facultad de Ciencias Exactas, Físicas y Naturales, Universidad Nacional de Córdoba (UNC), Argentina
+    address: Facultad de Ciencias Exactas, Fisicas y Naturales, Universidad Nacional de Cordoba (UNC), Argentina
 
@@
 Here, we present the first detailed analysis of the network of predator-prey interactions (food web) for the MPA N-BB ecosystem.
-We applied a network approach to characterize the food web in terms of complexity and structure, and identifying the species' role in such a framework.
-In terms of complexity, the MPA N-BB food web consisted of 1778 predator-prey interactions and 379 species, with a link density of 4.69 and a connectance of 0.01.
+We applied a network approach to characterise the food web in terms of complexity and structure, and identifying the species' role in such a framework.
+In terms of complexity, the MPA N-BB food web consisted of 1780 predator-prey interactions and 375 species, with a link density of 4.75 and a connectance of 0.01.
 In terms of structure, almost half of the consumers were omnivores (0.48), and the network displayed a small-world pattern.
@@
 Although there is a robust knowledge about the complexity considering the richness of the benthic and plankton communities in the MPA N-BB ecosystem [@Schejter2016; @Guinder2020; @Schejter2020; @APN2022], a better understanding of species interactions' complexity and structure is needed.
-This aspect can be tackled by analyzing one of the most frequent relationships between species: the predator-prey interaction [@Bascompte2009].
+This aspect can be tackled by analysing one of the most frequent relationships between species: the predator-prey interaction [@Bascompte2009].
 The sum of predator-prey or trophic interactions of a particular region is referred to as a food web, representing the roadmap for matter and energy flow in an ecosystem.
@@
 For this, we applied a network approach to a highly resolved food web.
-The objective was twofold: characterize the food web in terms of complexity and structure, and identify the species' role in such a network framework.
+The objective was twofold: characterise the food web in terms of complexity and structure, and identify the species' role in such a network framework.
 
@@
 
-We analyzed the MPA N-BB network of trophic interactions, or food web, at two levels: A) network, considering species and interactions of the whole network; and B) species, considering interactions and species related to a particular species (Table 1).
+We analysed the MPA N-BB network of trophic interactions, or food web, at two levels: A) network, considering species and interactions of the whole network; and B) species, considering interactions and species related to a particular species (Table 1).
 
-The network-level analysis aims to characterize the food web in terms of complexity and structure.
+The network-level analysis aims to characterise the food web in terms of complexity and structure.
 For this, we calculated several network properties commonly used to describe empirical food webs [@Pascual2005]: (1) number of species S; (2) number of interactions or links L; (3) link density L/S; (4) connectance L/S^2; (5) omnivory Omn; and (6) small-world pattern.
-In order to explore the small-world phenomenon, we analyzed the  characteristic path length (CPL) and the clustering coefficient (CC).
+In order to explore the small-world phenomenon, we analysed the  characteristic path length (CPL) and the clustering coefficient (CC).
 The CPL is the average shortest path length between all pairs of nodes [@Watts1998].
@@
 
-Also, we estimated the (7) degree distributions for the food web, prey and predators, and each functional group (e.g., Amphipoda, Ascidiacea, Bivalvia, fish, marine mammals, sea birds, among others).
+Also, we estimated the (7) degree distributions for the food web, prey and predators, and each functional group (e.g., Amphipoda, Ascidiacea, Bivalvia, fish, marine mammals, seabirds, among others).
 The prey and predator distributions indicate the frequency of prey among predators, and viceversa; the functional group's degree shows the distribution of interactions within groups.
@@
 
-In terms of complexity, the MPA Namuncurá - Banco Burdwood food web (N-BB I and II) consisted of 1796 predator-prey interactions and 380 species, where 93% of them were defined at the species taxonomical level (Figure 2, Table S2).
-The food web presented a link density (e.g., the average number of interactions per species) of 4.73, and a connectance of 0.01.
+In terms of complexity, the MPA Namuncurá - Banco Burdwood food web (N-BB I and II) consisted of 1780 predator-prey interactions and 375 species, where 93% of them were defined at the species taxonomical level (Figure 2, Table S2).
+The food web presented a link density (e.g., the average number of interactions per species) of 4.75, and a connectance of 0.01.
 Almost half of the consumers were omnivores (0.48), feeding on sources at different trophic levels.
@@
 ```{r figure3, echo=FALSE, fig.width = 6.5, fig.height = 9, fig.align='center', fig.cap="Degree distributions for the (A) food web, for (B) prey among predators, (C) predators among prey, and (D) for each functional group.
-Groups are vertically ordered by increasing trophic level; groups with less than 3 species were not plotted (e.g., pelagic fish)."}
+Groups are vertically ordered by increasing trophic level (following coloration of figure 2); groups with less than 3 species were not plotted (e.g., pelagic fish).
+All functional groups and the species that comprise them are shown in Supplementary Material (Table S3)."}
 # Degree distributions: network, predator, prey & group
@@
 
-Most species in the food web were consumers, 339 out of 379; the rest were primary producers, such as diatoms (phytoplankton), and non-living food sources like detritus and necromass.
-
 We found different relationships between the species trophic level (TL) and the rest of the analysed species-level properties (Figure 4A-D).
@@
 the higher the species' TL, the lower the trophic similarity or the higher the uniqueness in terms of trophic role (Figure 4C).
-Here it is noteworthy to highlight those high-trophic level species (TL > 3.1) with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster sp* (echinoderms), *Phalacrocorax atriceps* and *Eudyptes chrysocome* (sea birds), and *Lagenorhynchus cruciger* (marine mammals) (Table S3).
+Here it is noteworthy to highlight those high-trophic level species (TL > 3.1) with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster sp* (echinoderms), *Phalacrocorax atriceps* and *Eudyptes chrysocome* (seabirds), and *Lagenorhynchus cruciger* (marine mammals) (Table S3).
 
 We also found a significant negative relationship between TL and closeness, however less evident, meaning that low-TL species are relatively closer to any other species in the food web (Figure 4B).
-Species of genera *Calanus* and *Euphausia*, and species of Brachiopoda, all with TL < 3, registered the highest closeness values (Table S3).
+Detritus, species of genera *Calanus* and *Euphausia*, and Foraminifera, all with TL < 3, registered the highest closeness values (Table S3).
 
-Notably, species of mid-TLs (3-4) showed the highest values of betweenness, meaning that those species participated in the highest number of shortest paths between species (Figure 4A).
-The following are the species with the highest values: *Patagonotothen ramsayi*, *Dissostichus eleginoides*, *Salilota australis* (fishes), *Doryteuthis gahi* (Cephalopoda), and *Patagonotothen guntheri* (Notothenioid fish) (Table S3).
+Notably, species of mid-TLs (3-4.2) showed the highest values of betweenness, meaning that those species participated in the highest number of shortest paths between species (Figure 4A).
+The following are the species with the highest values: *Patagonotothen ramsayi*, *Salilota australis*, *Dissostichus eleginoides* (fishes), *Doryteuthis gahi* (Cephalopoda), and *Patagonotothen guntheri* (Notothenioid fish) (Table S3).
 
-Considering the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.77); 'module hub' was constrained to mid-TL species (2.48 - 3.92); 'module connector' from low to mid-TLs (1 - 3.86); and 'network connector', the least frequent, had all of its species in TL = 1, except for one with TL = 3.47 (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework).
-Here it is important to highlight the two latter topological roles because they are responsible for linking modules and maintaining the connectivity of the food web: 40 species (5 network connectors + 35 module connectors) from 20 different functional groups with a TL range = 1 - 3.86.
-The following were the five species with a network connector role: Detritus, Diatoms (benthic, centric and pennate), and *Patagonotothen ramsayi*.
-The 35 species with a module connector role represent these functional groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Cnidaria, Cumacea, Decapoda, detritus, Diatoms, Dinoflagellates, Echinodermata, fish (bentho-pelagic and demersal Osteichthyes, and Chondrychthyes), Foraminifera, Polychaeta, Porifera, Pycnogonida, sea birds, and zooplankton (see Supplementary Material Table S3 for the identity of the species).
+Considering the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.7), as well as 'module hub' species (TL = 1 - 4); 'module connector' was constrained to mid-TLs (2 - 3.86); and 'network connector', the least frequent, had all of its species in low-TLs (1 - 2), except for one with TL = 3.48 (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework).
+Here it is important to highlight the two latter topological roles because they are responsible for linking modules and maintaining the connectivity of the food web: 41 species (4 network connectors + 37 module connectors) from 19 different functional groups with a TL range = 1 - 3.86.
+The following were the four species with a network connector role: detritus, benthic diatoms, Foraminifera and *Patagonotothen ramsayi*.
+The 37 species with a module connector role represented these functional groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Hydrozoa (as 'Cnidaria_benthic'), Copepoda, Cumacea, Decapoda, diatoms, Echinodermata, fish (bentho-pelagic and demersal Osteichthyes, and Chondrychthyes), Polychaeta, Porifera, Pycnogonida (as 'Benthos_Misc') and zooplankton (see Supplementary Material Table S3 for the identity of the species).
 
@@
 Each point represents a species.
-Linear regressions for betweenness ($y = x - , R^2 = , p-value < $), closeness ($y = x - , R^2 = , p-value = $) and trophic similarity ($y = x - , R^2 = , p-value = $).
+Linear regressions for betweenness ($y = 74.96x - 121.71, R^2 = 0.05, p-value < 0.01$), closeness ($y = 1.01e-05x - 9.48e-4, R^2 = 0.003, p-value = 0.14$) and trophic similarity ($y = -0.02x + 0.11 , R^2 = 0.08, p-value < 0.01$).
 Note that for panels A, B and C only species with TLs equal or greater than 2 were considered."}
@@
 Consequences of this could be of great importance in recognizing evolutionary paths and the vulnerability to perturbations [@Montoya2002].
-On the one hand, a short path length implies a rapid spread of an impact (e.g., contaminant, population fluctuation, local extinction) throughout the network and, at the same time, more potentially adaptive dynamics in the face of external perturbations [@Montoya2002; @Williams2002].
+On the one hand, a short path length implies a rapid spread of an impact (e.g., contaminant, population fluctuation, local extinction) throughout the network but, at the same time, more potentially adaptive dynamics in the face of external perturbations [@Montoya2002; @Williams2002].
 On the other hand, a high clustering coefficient indicates the formation of subnetworks composed only by the neighbours of particular species.
@@
 
-We have identified that most of the consumers in the food web of the MPA N-BB either has a narrow diet or are specialists, while few present a broad diet.
+We have identified that most of the consumers in the food web of the MPA N-BB either have a narrow diet or are specialists, while few present a broad diet.
 The most evident generalist species are *Patagonotothen guntheri* [@CovattiAle2022], *P.
@@
 detritus) supports the abundant benthic community of filter-feeders [@Schejter2016].
-Furthermore, we found that the second and third-most consumed prey were diatoms and species of *Euphausia*, respectively, which are essential sources for the diverse zooplankton community [@Spinelli2020], mid-TL consumers like the Fuegian sprat *Sprattus fuegensis* [@Padovani2021] and *Patagonotothen ramsayi* [@Fischer2022], and top predators [@RayaRey2022; @Riccialdelli2022].
+Furthermore, we found that the second and third-most consumed prey were diatoms and species of *Euphausia*, respectively, which are essential sources for the diverse zooplankton community [@Spinelli2020], mid-TL consumers like the Fuegian sprat *Sprattus fuegensis* [@Padovani2021] and *Patagonotothen ramsayi* [@Fischer2022], and top predators such as the black-browed and grey-headed albatrosses (*Thalassarche melanophris* and *Thalassarche chrysostoma*, respectively) [@Catry2004], and baleen whales (species of the genera Balaenoptera and Eubalaena) [@Valenzuela2018].
 
@@
 At the same time, our results highlight the uniqueness in terms of the trophic role of high-TL predators.
-Here, not only the expected pelagic animals such as marine mammals and sea birds arise as relevant, but also benthic vertebrate (chondrichthyans *Bathyraja macloviana* and *Squalus acanthias*) and invertebrate species (echinoderms *Diplopteraster clarki* and *Pteraster sp*) are noteworthy.
+Here, not only the expected pelagic animals such as marine mammals and seabirds arise as relevant, but also benthic vertebrate (chondrichthyans *Bathyraja macloviana* and *Squalus acanthias*) and invertebrate species (echinoderms *Diplopteraster clarki* and *Pteraster sp*) are noteworthy.
 The role that such species play in the MPA N-BB ecosystem is unique and perturbations on them might result in unprecedented changes at the trophic structure and functioning level.
@@
 deep flanks to the south).
-As a consequence most of the data we used to build the network come from studies performed in the MPA N-BB I.
-Despite this fact, we decided to build the food web considering both MPAs due to the tight oceanographic and ecological connection that exists among them [references in @APN2022].
+As a consequence, most of the data we used to build the network come from studies performed in the MPA N-BB I.
+Despite this fact, we decided to build the food web considering both MPAs due to the tight oceanographic and ecological connection that exists among them [@APN2022 and references therein].
 
@@
 Moreover, seasonal variations also occur in some physical and biological aspects of the MPA N-BB I [@GarciaAlonso2018; @Matano2019].
-Although we were aware of it, we decided to characterize a food web representing the whole MPA N-BB I year round since this is the first study of its type in the area.
+Considering both MPAs (N-BB I and II), a seasonal variation in the community composition of marine mammals and seabirds was recorded recently [@Dellabianca2023].
+The spatial and seasonal variations in the plankton community might affect the energy and matter flow to higher levels of the food web.
+This has been recently studied in the vicinity of the MPA N-BB I, in the Beagle Channel, where a differential energy flow pattern of the plankton community has been recognised in two micro-basins of the Channel separated by a sill, each with different physicochemical properties [@Giesecke2021], nutrient concentration [@Latorre2023] as well as in the dominant component of the plankton community [@Bruno2023a; @Presta2023].
+Although we were aware of the above, we decided to characterise a food web representing the whole MPA N-BB I year round since this is the first study of its type in the area.
 
-These are the perspectives that we suggest should be considered to improve our knowledge regarding the structure, functioning and stability of the MPA N-BB:
-
-Incorporate habitat heterogeneity, since the benthic community in the BB and deep flanks differs [; @Schejter2021].
-This heterogeneity might lead to distinct food web properties, hence differences in ecosystem functioning and response to anthropogenic and environmental perturbations [@Kortsch2019; @Cordone2020].
-El caso de las ascidias (Tatián)
-
-Incorporate species traits, like body size and mass, which are known to be important drivers in predator-prey interactions. @LaMesa2016
-
-Simulate perturbations on food web and target species: mercury transfer, microplastic pollution, fisheries.
-@Cossi2021; @DiMauro2022; @Fioramonti2022
-
-Estimation of interaction strength considering species and interaction traits (i.e.
-body size, body mass, interaction dimensionality) to gain insights into food web stability and response to anthropogenic and environmental perturbations.
-@Nilsson2016; @Cirtwill2018; @Kortsch2021
+Taking into account the mentioned caveats, and with the aim of improving the knowledge regarding the structure, functioning and stability of the MPA N-BB, we suggest that the future perspectives should: 1) incorporate spatial heterogeneity among MPA N-BB I and II [@Schejter2021], which might lead to distinct food web properties in terms of structure and functioning [@Kortsch2019; @Cordone2020]; 2) include species traits, like body size and mass, since they are known to be important drivers in predator-prey interactions [@Brose2019]; 3) simulate the anthropogenic impacts already present in the MPA N-BB ecosystem (e.g.
+microplastics, mercury) [@Cossi2021; @DiMauro2022; @Fioramonti2022] as perturbations within the framework of the described complex food web; and 4) estimate the interaction strength of each predator-prey relationship in the food web considering species and interaction traits (i.e.
+body size, body mass, interaction dimensionality), and species density data [@Nilsson2016; @Pawar2012].
 

### 2023-05-08 MS_ToSubmit/MS_Burdwood_foodweb.tex
2nd version w/ coauthors suggs

@@
     \affiliation[5]{Wildlife Conservation Society, Argentina}
-    \affiliation[6]{Instituto de Biodiversidad y Biología Experimental y
+    \affiliation[6]{Instituto de Biodiversidad y Biologia Experimental y
 Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, Argentina}
@@
 Rivadavia'', Argentina}
-    \affiliation[8]{Instituto de Diversidad y Ecología Animal
+    \affiliation[8]{Instituto de Diversidad y Ecologia Animal
 (IDEA-CONICET)}
-    \affiliation[9]{Facultad de Ciencias Exactas, Físicas y Naturales,
-Universidad Nacional de Córdoba (UNC), Argentina}
+    \affiliation[9]{Facultad de Ciencias Exactas, Fisicas y Naturales,
+Universidad Nacional de Cordoba (UNC), Argentina}
     \cortext[cor1]{Corresponding author}
@@
   analysis of the network of predator-prey interactions (food web) for
-  the MPA N-BB ecosystem. We applied a network approach to characterize
+  the MPA N-BB ecosystem. We applied a network approach to characterise
   the food web in terms of complexity and structure, and identifying the
   species' role in such a framework. In terms of complexity, the MPA
-  N-BB food web consisted of 1778 predator-prey interactions and 379
-  species, with a link density of 4.69 and a connectance of 0.01. In
+  N-BB food web consisted of 1780 predator-prey interactions and 375
+  species, with a link density of 4.75 and a connectance of 0.01. In
   terms of structure, almost half of the consumers were omnivores
@@
   to perturbations. We suggest that generalist species, mainly fishes,
-  play a crucial role in the ecosystem's bentho-pelagic coupling
-  process. In addition, we propose that other species besides the
-  longtail southern cod \emph{Patagonotothen ramsayi} and the Fueguian
-  sprat \emph{Sprattus fuegensis} should be considered as relevant
-  energy transfers for the ecosystem. Finally, we argue that the
-  diversity of species, including both the benthic and pelagic habitats,
-  is responsible for seccuring the connectivity within the food web
-  against perturbations, therefore contributing to the structure and
-  stability of the ecosystem.
+  play a crucial role in the ecosystem's bentho-pelagic coupling process
+  and that other species, besides the longtail southern cod
+  \emph{Patagonotothen ramsayi} and the Fueguian sprat \emph{Sprattus
+  fuegensis}, should be considered as relevant energy transfers for the
+  ecosystem. Finally, we argue that the diversity of species, including
+  both the benthic and pelagic habitats, is responsible for seccuring
+  the connectivity within the food web against perturbations, therefore
+  contributing to the structure and stability of the ecosystem.
   \end{abstract}
@@
 2016, 2020), a better understanding of species interactions' complexity
-and structure is needed. This aspect can be tackled by analyzing one of
+and structure is needed. This aspect can be tackled by analysing one of
 the most frequent relationships between species: the predator-prey
@@
 N-BB ecosystem. For this, we applied a network approach to a highly
-resolved food web. The objective was twofold: characterize the food web
+resolved food web. The objective was twofold: characterise the food web
 in terms of complexity and structure, and identify the species' role in
@@
 
-We analyzed the MPA N-BB network of trophic interactions, or food web,
+We analysed the MPA N-BB network of trophic interactions, or food web,
 at two levels: A) network, considering species and interactions of the
@@
 
-The network-level analysis aims to characterize the food web in terms of
+The network-level analysis aims to characterise the food web in terms of
 complexity and structure. For this, we calculated several network
@@
 Omn; and (6) small-world pattern. In order to explore the small-world
-phenomenon, we analyzed the characteristic path length (CPL) and the
+phenomenon, we analysed the characteristic path length (CPL) and the
 clustering coefficient (CC). The CPL is the average shortest path length
@@
 and predators, and each functional group (e.g., Amphipoda, Ascidiacea,
-Bivalvia, fish, marine mammals, sea birds, among others). The prey and
+Bivalvia, fish, marine mammals, seabirds, among others). The prey and
 predator distributions indicate the frequency of prey among predators,
@@
 In terms of complexity, the MPA Namuncurá - Banco Burdwood food web
-(N-BB I and II) consisted of 1778 predator-prey interactions and 379
+(N-BB I and II) consisted of 1780 predator-prey interactions and 375
 species, where 93\% of them were defined at the species taxonomical
 level (Figure 2, Table S2). The food web presented a link density (e.g.,
-the average number of interactions per species) of 4.69, and a
+the average number of interactions per species) of 4.75, and a
 connectance of 0.01. Almost half of the consumers were omnivores (0.48),
@@
 \hline
-380 & 1785 & 4.7 & 0.01 & 0.48 & 2.99 & 0.08 & True\\
+375 & 1780 & 4.75 & 0.01 & 0.48 & 2.96 & 0.08 & True\\
 \hline
@@
 that most consumers fed on a low number of prey whereas few had multiple
-preys (Figure 3B). The top-five predators in number of prey were:
-yellowfin notothen \emph{Patagonotothen guntheri} (Notothenioid fish, 52
-prey), rock cod \emph{Patagonotothen ramsayi} (Notothenioid fish, 50
+prey (Figure 3B). The top-five predators in number of prey were:
+yellowfin notothen \emph{Patagonotothen guntheri} (Notothenioid fish, 50
+prey), rock cod \emph{Patagonotothen ramsayi} (Notothenioid fish, 49
+prey), broad nose skate \emph{Bathyraja brachyurops} (Chondrichthyan, 33
 prey), Patagonian toothfish \emph{Dissostichus eleginoides}
-(Notothenioid fish, 30 prey), broad nose skate \emph{Bathyraja
-brachyurops} (Chondrichthyan, 30 prey), and graytail skate
-\emph{Bathyraja griseocauda} (Chondrichthyan, 28 prey). Following the
-same distribution pattern, few prey presented multiple predators (Figure
-3C). The top-five prey in number of predators were: Detritus
-(Non-living, 153 predators), the three categories of Diatoms considered
-(benthic, centric and pennate, 72 predators on average), and species of
-the genus \emph{Euphausia} (Zooplankton, 46 predators). Finally, taking
-into account the interactions within each functional group, most
-interactions were concentrated in a few species (Figure 3D). The most
-evident species were: \emph{Themisto gaudichaudii} (Amphipoda),
-\emph{Zygochlamys patagonica} (Bivalvia), \emph{Aspidostoma giganteum}
-(Bryozoa), \emph{Munida gregaria} (Decapoda), \emph{Patagonotothen
-ramsayi} and \emph{Patagonotothen guntheri} (bentho-pelagic fish),
-\emph{Psychrolutes marmoratus} (demersal fish), and species of
-\emph{Euphausia} (Zooplankton). Overall, there is an evident asymmetry
-in the distribution of interactions among species at different levels in
-the MPA N-BB food web.
+(Notothenioid fish, 30 prey), and graytail skate \emph{Bathyraja
+griseocauda} (Chondrichthyan, 28 prey). Following the same distribution
+pattern, few prey presented multiple predators (Figure 3C). The top-five
+prey in number of predators were: Detritus (Non-living, 155 predators),
+the three categories of Diatoms considered (benthic, centric and
+pennate, 75 predators on average), and species of the genus
+\emph{Euphausia} (Zooplankton, 47 predators). Finally, taking into
+account the interactions within each functional group, most interactions
+were concentrated in a few species (Figure 3D). The most evident species
+were: \emph{Doryteuthis gahi} (Cephalopoda), \emph{Grimothea gregaria}
+(Decapoda), \emph{Patagonotothen ramsayi}, \emph{Patagonotothen
+guntheri} and \emph{Dissostichus eleginoides} (bentho-pelagic fish),
+\emph{Sprattus fuegensis} and \emph{Micromesistius australis} (pelagic
+fish), and species of \emph{Euphausia} and \emph{Themisto gaudichaudii}
+(Zooplankton). Overall, there is an evident asymmetry in the
+distribution of interactions among species at different levels in the
+MPA N-BB food web.
 
@@
 \caption{Degree distributions for the (A) food web, for (B) prey among predators, (C) predators among prey, and (D) for each functional group.
-Groups are vertically ordered by increasing trophic level; groups with less than 3 species were not plotted (e.g., pelagic fish).}\label{fig:figure3}
+Groups are vertically ordered by increasing trophic level (following coloration of figure 2); groups with less than 3 species were not plotted (e.g., pelagic fish).
+All functional groups and the species that comprise them are shown in Supplementary Material (Table S3).}\label{fig:figure3}
 \end{figure}
@@
 \subsection{Species-level properties}\label{species-level-properties}}
-
-Most species in the food web were consumers, 336 out of 379; the rest
-were primary producers, such as diatoms (phytoplankton), and non-living
-food sources like detritus and necromass.
 
@@
 higher the uniqueness in terms of trophic role (Figure 4C). Here it is
-noteworthy to highlight those high-trophic level species with low values
-of trophic similarity: \emph{Bathyraja macloviana} and \emph{Squalus
-acanthias} (Chondrichthyans), \emph{Diplopteraster clarki} and
-\emph{Pteraster sp} (echinoderms), \emph{Phalacrocorax atriceps} and
-\emph{Eudyptes chrysocome} (sea birds), and \emph{Lagenorhynchus
-cruciger} and \emph{Mesoplodon bowdoini} (marine mammals) (Table S3).
+noteworthy to highlight those high-trophic level species (TL
+\textgreater{} 3.1) with low values of trophic similarity:
+\emph{Bathyraja macloviana} and \emph{Squalus acanthias}
+(Chondrichthyans), \emph{Diplopteraster clarki} and \emph{Pteraster sp}
+(echinoderms), \emph{Phalacrocorax atriceps} and \emph{Eudyptes
+chrysocome} (seabirds), and \emph{Lagenorhynchus cruciger} (marine
+mammals) (Table S3).
 
@@
 relatively closer to any other species in the food web (Figure 4B).
-Species of genera \emph{Calanus} and \emph{Euphausia}, and species of
-Brachiopoda, all with TL \textless{} 3, registered the highest closeness
-values (Table S3).
-
-Notably, species of mid-TLs (3-4) showed the highest values of
+Detritus, species of genera \emph{Calanus} and \emph{Euphausia}, and
+Foraminifera, all with TL \textless{} 3, registered the highest
+closeness values (Table S3).
+
+Notably, species of mid-TLs (3-4.2) showed the highest values of
 betweenness, meaning that those species participated in the highest
@@
 the species with the highest values: \emph{Patagonotothen ramsayi},
-\emph{Dissostichus eleginoides}, \emph{Salilota australis} (fishes),
+\emph{Salilota australis}, \emph{Dissostichus eleginoides} (fishes),
 \emph{Doryteuthis gahi} (Cephalopoda), and \emph{Patagonotothen
@@
 Considering the topological role, `module specialist' species were the
-most frequent and presented a wide TL range (1 - 4.77); `module hub' was
-constrained to mid-TL species (2.48 - 3.92); `module connector' from low
-to mid-TLs (1 - 3.86); and `network connector', the least frequent, had
-all of its species in TL = 1, except for one with TL = 3.47 (Figure 4D,
-see Figure S2 for species' topological roles in a food web graph
+most frequent and presented a wide TL range (1 - 4.7), as well as
+`module hub' species (TL = 1 - 4); `module connector' was constrained to
+mid-TLs (2 - 3.86); and `network connector', the least frequent, had all
+of its species in low-TLs (1 - 2), except for one with TL = 3.48 (Figure
+4D, see Figure S2 for species' topological roles in a food web graph
 framework). Here it is important to highlight the two latter topological
 roles because they are responsible for linking modules and maintaining
-the connectivity of the food web: 40 species (5 network connectors + 35
-module connectors) from 20 different functional groups with a TL range =
-1 - 3.86. The following were the five species with a network connector
-role: Detritus, Diatoms (benthic, centric and pennate), and
-\emph{Patagonotothen ramsayi}. The 35 species with a module connector
-role represent these functional groups: Amphipoda, Bivalvia,
-Brachiopoda, Bryozoa, Cnidaria, Cumacea, Decapoda, detritus, Diatoms,
-Dinoflagellates, Echinodermata, fish (bentho-pelagic and demersal
-Osteichthyes, and Chondrychthyes), Foraminifera, Polychaeta, Porifera,
-Pycnogonida, sea birds, and zooplankton (see Supplementary Material
-Table S3 for the identity of the species).
+the connectivity of the food web: 41 species (4 network connectors + 37
+module connectors) from 19 different functional groups with a TL range =
+1 - 3.86. The following were the four species with a network connector
+role: detritus, benthic diatoms, Foraminifera and \emph{Patagonotothen
+ramsayi}. The 37 species with a module connector role represented these
+functional groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Hydrozoa
+(as `Cnidaria\_benthic'), Copepoda, Cumacea, Decapoda, diatoms,
+Echinodermata, fish (bentho-pelagic and demersal Osteichthyes, and
+Chondrychthyes), Polychaeta, Porifera, Pycnogonida (as `Benthos\_Misc')
+and zooplankton (see Supplementary Material Table S3 for the identity of
+the species).
 
@@
 Each point represents a species.
-Linear regressions for betweenness ($y = x - , R^2 = , p-value < $), closeness ($y = x - , R^2 = , p-value = $) and trophic similarity ($y = x - , R^2 = , p-value = $).
+Linear regressions for betweenness ($y = 74.96x - 121.71, R^2 = 0.05, p-value < 0.01$), closeness ($y = 1.01e-05x - 9.48e-4, R^2 = 0.003, p-value = 0.14$) and trophic similarity ($y = -0.02x + 0.11 , R^2 = 0.08, p-value < 0.01$).
 Note that for panels A, B and C only species with TLs equal or greater than 2 were considered.}\label{fig:figure4}
@@
 rapid spread of an impact (e.g., contaminant, population fluctuation,
-local extinction) throughout the network and, at the same time, more
+local extinction) throughout the network but, at the same time, more
 potentially adaptive dynamics in the face of external perturbations
@@
 We have identified that most of the consumers in the food web of the MPA
-N-BB either has a narrow diet or are specialists, while few present a
+N-BB either have a narrow diet or are specialists, while few present a
 broad diet. The most evident generalist species are \emph{Patagonotothen
@@
 \emph{Patagonotothen ramsayi} (Fischer et al., 2022), and top predators
-(Raya Rey, 2022; Riccialdelli, 2022).
+such as the black-browed and grey-headed albatrosses (\emph{Thalassarche
+melanophris} and \emph{Thalassarche chrysostoma}, respectively) (Catry
+et al., 2004), and baleen whales (species of the genera Balaenoptera and
+Eubalaena) (Valenzuela et al., 2018).
 
@@
 of the trophic role of high-TL predators. Here, not only the expected
-pelagic animals such as marine mammals and sea birds arise as relevant,
+pelagic animals such as marine mammals and seabirds arise as relevant,
 but also benthic vertebrate (chondrichthyans \emph{Bathyraja macloviana}
@@
 former MPA compared to the MPA N-BB II (i.e.~deep flanks to the south).
-As a consequence most of the data we used to build the network come from
-studies performed in the MPA N-BB I. Despite this fact, we decided to
-build the food web considering both MPAs due to the tight oceanographic
-and ecological connection that exists among them (references in APN,
-2022).
+As a consequence, most of the data we used to build the network come
+from studies performed in the MPA N-BB I. Despite this fact, we decided
+to build the food web considering both MPAs due to the tight
+oceanographic and ecological connection that exists among them (APN,
+2022 and references therein).
 
@@
 occur in some physical and biological aspects of the MPA N-BB I (García
-Alonso et al., 2018; Matano et al., 2019). Although we were aware of it,
-we decided to characterize a food web representing the whole MPA N-BB I
+Alonso et al., 2018; Matano et al., 2019). Considering both MPAs (N-BB I
+and II), a seasonal variation in the community composition of marine
+mammals and seabirds was recorded recently (Dellabianca et al., 2023).
+The spatial and seasonal variations in the plankton community might
+affect the energy and matter flow to higher levels of the food web. This
+has been recently studied in the vicinity of the MPA N-BB I, in the
+Beagle Channel, where a differential energy flow pattern of the plankton
+community has been recognised in two micro-basins of the Channel
+separated by a sill, each with different physicochemical properties
+(Giesecke et al., 2021), nutrient concentration (Latorre et al., 2023)
+as well as in the dominant component of the plankton community (Bruno et
+al., 2023; Presta et al., 2023). Although we were aware of the above, we
+decided to characterise a food web representing the whole MPA N-BB I
 year round since this is the first study of its type in the area.
 
-These are the perspectives that we suggest should be considered to
-improve our knowledge regarding the structure, functioning and stability
-of the MPA N-BB:
-
-Incorporate habitat heterogeneity, since the benthic community in the BB
-and deep flanks differs {[}; Schejter \& Albano (2021){]}. This
-heterogeneity might lead to distinct food web properties, hence
-differences in ecosystem functioning and response to anthropogenic and
-environmental perturbations (Cordone et al., 2020; Kortsch et al.,
-2019). El caso de las ascidias (Tatián)
-
-Incorporate species traits, like body size and mass, which are known to
-be important drivers in predator-prey interactions. La Mesa et al.
-(2016)
-
-Simulate perturbations on food web and target species: mercury transfer,
-microplastic pollution, fisheries. Cossi et al. (2021); Di Mauro et al.
-(2022); Fioramonti et al. (2022)
-
-Estimation of interaction strength considering species and interaction
-traits (i.e.~body size, body mass, interaction dimensionality) to gain
-insights into food web stability and response to anthropogenic and
-environmental perturbations. Nilsson \& McCann (2016); Cirtwill et al.
-(2018); Kortsch et al. (2021)
+Taking into account the mentioned caveats, and with the aim of improving
+the knowledge regarding the structure, functioning and stability of the
+MPA N-BB, we suggest that the future perspectives should: 1) incorporate
+spatial heterogeneity among MPA N-BB I and II (Schejter \& Albano,
+2021), which might lead to distinct food web properties in terms of
+structure and functioning (Cordone et al., 2020; Kortsch et al., 2019);
+2) include species traits, like body size and mass, since they are known
+to be important drivers in predator-prey interactions (Brose et al.,
+2019); 3) simulate the anthropogenic impacts already present in the MPA
+N-BB ecosystem (e.g.~microplastics, mercury) (Cossi et al., 2021; Di
+Mauro et al., 2022; Fioramonti et al., 2022) as perturbations within the
+framework of the described complex food web; and 4) estimate the
+interaction strength of each predator-prey relationship in the food web
+considering species and interaction traits (i.e.~body size, body mass,
+interaction dimensionality), and species density data (Nilsson \&
+McCann, 2016; Pawar et al., 2012).
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Bruno2023a}{}}%
+Bruno, D. O., Valencia-Carrasco, C., Paci, M. A., Leonarduzzi, E.,
+Castro, L., Riccialdelli, L., Iachetti, C. M., Cadaillon, A., Giesecke,
+R., Schloss, I. R., Berghoff, C. F., Martín, J., Diez, M., Cabreira, A.,
+Presta, M. L., Capitanio, F. L., \& Boy, C. C. (2023). Spring plankton
+energy content by size classes in two contrasting environments of a high
+latitude ecosystem: {The Beagle Channel}. \emph{Journal of Marine
+Systems}, \emph{240}, 103876.
+\url{https://doi.org/10.1016/j.jmarsys.2023.103876}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Catry2004}{}}%
+Catry, P., Phillips, R. A., Phalan, B., Silk, J. R. D., \& Croxall, J.
+P. (2004). Foraging strategies of grey-headed albatrosses {Thalassarche}
+chrysostoma: Integration of movements, activity and feeding events.
+\emph{Marine Ecology Progress Series}, \emph{280}, 261--273.
+\url{https://doi.org/10.3354/meps280261}
+
 \leavevmode\vadjust pre{\hypertarget{ref-CBD2004}{}}%
@@
 carbono}} (p. 101) {[}\{Field campaign Report\}{]}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Dellabianca2023}{}}%
+Dellabianca, N. A., Torres, M. A., Ordoñez, C., Fioramonti, N., \& Raya
+Rey, A. (2023). Marine protected areas in the southern south-west
+{Atlantic}: {Insights} from marine top predator communities.
+\emph{Aquatic Conservation: Marine and Freshwater Ecosystems},
+\emph{33}(5), 472--487. \url{https://doi.org/10.1002/aqc.3935}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Giesecke2021}{}}%
+Giesecke, R., Martín, J., Piñones, A., Höfer, J., Garcés-Vargas, J.,
+Flores-Melo, X., Alarcón, E., Durrieu de Madron, X., Bourrin, F., \&
+González, H. E. (2021). General {Hydrography} of the {Beagle Channel}, a
+{Subantarctic Interoceanic Passage} at the {Southern Tip} of {South
+America}. \emph{Frontiers in Marine Science}, \emph{8}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Glorioso1995}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Latorre2023}{}}%
+Latorre, M. P., Berghoff, C. F., Giesecke, R., Malits, A., Pizarro, G.,
+Iachetti, C. M., Martin, J., Flores-Melo, X., Gil, M. N., Iriarte, J.
+L., \& Schloss, I. R. (2023). Plankton metabolic balance in the eastern
+{Beagle Channel} during spring. \emph{Journal of Marine Systems},
+\emph{240}, 103882. \url{https://doi.org/10.1016/j.jmarsys.2023.103882}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Lopez-Gappa2018}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Presta2023}{}}%
+Presta, M. L., Riccialdelli, L., Bruno, D. O., Castro, L. R.,
+Fioramonti, N. E., Florentín, O. V., Berghoff, C. F., Capitanio, F. L.,
+\& Lovrich, G. A. (2023). Mesozooplankton community structure and
+trophic relationships in an austral high-latitude ecosystem ({Beagle
+Channel}): {The} role of bottom-up and top-down forces during
+springtime. \emph{Journal of Marine Systems}, \emph{240}, 103881.
+\url{https://doi.org/10.1016/j.jmarsys.2023.103881}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Prieto2022}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RayaRey2022}{}}%
-Raya Rey, A. (2022). \emph{Food items of sea birds of the {Marine
-Protected Area Namuncurá} - {Banco Burdwood}}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-Reta2014}{}}%
@@
 Actual} del {Conocimiento} y {Perspectivas}}. {INIDEP}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Riccialdelli2022}{}}%
-Riccialdelli, L. (2022). \emph{Feeding items of marine mammals of the
-{Marine Protected Area Namuncurá} - {Banco Burdwood}}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Valenzuela2018}{}}%
+Valenzuela, L. O., Rowntree, V. J., Sironi, M., \& Seger, J. (2018).
+Stable isotopes ({\(\delta\)15N}, {\(\delta\)13C}, {\(\delta\)34S}) in
+skin reveal diverse food sources used by southern right whales
+{Eubalaena} australis. \emph{Marine Ecology Progress Series},
+\emph{603}, 243--255. \url{https://doi.org/10.3354/meps12722}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Watts1998}{}}%

### 2023-05-08 MS_ToSubmit/SupMaterial.Rmd
2nd version w/ coauthors suggs

@@
 ---
-title: "Supplementary material for 'The complex network of trophic interactions in a subAntarctic Marine Protected Area'"
-author: "Tomás I. Marina, Irene R. Schloss, Luciana Riccialdelli, To be continued"
+title: "Supplementary Material for 'The complex network of trophic interactions in
+  a subAntarctic oceanic Marine Protected Area'"
+author:
+  - Tomás I. Marina
+  - Irene R. Schloss
+  - Luciana Riccialdelli
+  - Fabiana L. Capitanio
+  - Sergio M. Delpiani
+  - Juan Martín Díaz de Astarloa
+  - Cintia Fraysse
+  - Gustavo A. Lovrich
+  - Andrea Raya Rey
+  - Mariela L. Spinelli
+  - Diego Urteaga
+  - Marcos Tatián
+  - Virginia A. García Alonso
+  - Claudia C. Boy
+  - Daniel O. Bruno
+bibliography: AMPBancoBurdwood.bib
 output: pdf_document
-bibliography: "AMPBancoBurdwood.bib"
 ---
@@
 
-The following figure and tables summarize the data we used to build the network of trophic (predator-prey) interactions for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
+The following figure and tables summarise the data we used to build the network of trophic (predator-prey) interactions for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
 Figure 1 resumes the type and number of references reviewed.
@@
 # Load data
-load("../data/cleaned-data_apr23.rda")
+load("../data/cleaned-data_may23.rda")
 
@@
 # Load data
-load("../data/cleaned-data_apr23.rda")
-load("../data/foodweb-data_apr23.rda")
+load("../data/cleaned-data_may23.rda")
+load("../data/foodweb-data_may23.rda")
 
@@
 Species, represented by circles, are coloured by role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green).
-Network connector = 5 species; module connector = 35 species; module hub = 7 species; and module specialist = 332 species.
+Network connector = 4 species; module connector = 37 species; module hub = 8 species; and module specialist = 326 species.
 
-```{r toprole_graph, echo=FALSE, fig.width = 20, fig.height=20, fig.cap="Graph of the food web showing species coloured by topological role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green)."}
+```{r toprole_graph, echo=FALSE, fig.width = 20, fig.height=20, fig.cap="Graph of the food web showing species coloured by topological role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green).
+Circle diameter is relative to the number of interactions."}
 
@@
 # Load data
-load("../results/summary_results_apr23.rda")
+load("../results/summary_results_may23.rda")
 

### 2023-05-08 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
2nd version w/ coauthors suggs

@@
 the higher the species' TL, the lower the trophic similarity or the higher the uniqueness in terms of trophic role (Figure 4C).
-Here it is noteworthy to highlight those high-trophic level species (TL > 3.1) with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster sp* (echinoderms), *Phalacrocorax atriceps* and *Eudyptes chrysocome* (seabirds), and *Lagenorhynchus cruciger* (marine mammals) (Table S3).
+Here it is noteworthy to highlight those high-trophic level species (TL > 3.1) with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster sp* (echinoderms), *Daption capense* and *Eudyptes chrysocome* (seabirds), Ziphiidae and *Lagenorhynchus cruciger* (marine mammals) (Table S3).
 
@@
 We are indebted to all those experts of the working group 'Banco Burdwood' who humbly provided their knowledge to enhance the quality of the present research.
-It is worth to mention the following researchers: Sandra Gordillo (IDACOR-CONICET; Universidad Nacional de Córdoba, Argentina), Mariano I.
-Martinez (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina), Sofía L.
-Callá (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina),...
+It is worth to mention the following researchers: Brenda L.
+Doti (IBBEA, CONICET-UBA; Universidad de Buenos Aires, Argentina), Sofía L.
+Callá (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina), Sandra Gordillo (IDACOR-CONICET; Universidad Nacional de Córdoba, Argentina), Mariano I.
+Martinez (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina) and Luciano Padovani (Instituto Nacional de Investigación y Desarrollo Pesquero, INIDEP, Argentina).
 Special thanks to G.A. Lovrich the Scientific Coordinator of the MPA Namuncurá-Burdwood Bank and the MPA N-BB Administrators.

### 2023-05-08 MS_ToSubmit/MS_Burdwood_foodweb.tex
2nd version w/ coauthors suggs

@@
 (Chondrichthyans), \emph{Diplopteraster clarki} and \emph{Pteraster sp}
-(echinoderms), \emph{Phalacrocorax atriceps} and \emph{Eudyptes
-chrysocome} (seabirds), and \emph{Lagenorhynchus cruciger} (marine
+(echinoderms), \emph{Daption capense} and \emph{Eudyptes chrysocome}
+(seabirds), Ziphiidae and \emph{Lagenorhynchus cruciger} (marine
 mammals) (Table S3).
@@
 the present research. It is worth to mention the following researchers:
-Sandra Gordillo (IDACOR-CONICET; Universidad Nacional de Córdoba,
-Argentina), Mariano I. Martinez (Museo Argentino de Ciencias Naturales
-``Bernardino Rivadavia'', Argentina), Sofía L. Callá (Museo Argentino de
-Ciencias Naturales ``Bernardino Rivadavia'', Argentina),\ldots{} Special
-thanks to G.A. Lovrich the Scientific Coordinator of the MPA
-Namuncurá-Burdwood Bank and the MPA N-BB Administrators. This study was
-funded by Consejo Nacional de Investigaciones Científicas y Técnicas
-(CONICET) and Agencia Nacional de Promoción Científica y Tecnológica
-(PICT 2020-SERIEA-01617), Argentina. This work is contribution no. XX of
-the MPA Namuncurá (Law 26.875).
+Brenda L. Doti (IBBEA, CONICET-UBA; Universidad de Buenos Aires,
+Argentina), Sofía L. Callá (Museo Argentino de Ciencias Naturales
+``Bernardino Rivadavia'', Argentina), Sandra Gordillo (IDACOR-CONICET;
+Universidad Nacional de Córdoba, Argentina), Mariano I. Martinez (Museo
+Argentino de Ciencias Naturales ``Bernardino Rivadavia'', Argentina) and
+Luciano Padovani (Instituto Nacional de Investigación y Desarrollo
+Pesquero, INIDEP, Argentina). Special thanks to G.A. Lovrich the
+Scientific Coordinator of the MPA Namuncurá-Burdwood Bank and the MPA
+N-BB Administrators. This study was funded by Consejo Nacional de
+Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de
+Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617), Argentina.
+This work is contribution no. XX of the MPA Namuncurá (Law 26.875).
 

### 2023-05-09 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Co-authors order

@@
   - name: Irene R. Schloss^a^^,^^b^^,^^c^
-  - name: Luciana Riccialdelli^a^
+  - name: Gustavo A. Lovrich^a^
+  - name: Claudia C. Boy^a^
+  - name: Daniel O. Bruno^a^^,^^c^
   - name: Fabiana L. Capitanio^f^
@@
   - name: Cintia Fraysse^a^
-  - name: Gustavo A. Lovrich^a^
+  - name: Virginia A. García Alonso^f^  
   - name: Andrea Raya Rey^a^^,^^c^^,^^e^
   - name: Mariela L. Spinelli^f^
+  - name: Marcos Tatián^h^^,^^i^
   - name: Diego Urteaga^g^
-  - name: Marcos Tatián^h^^,^^i^
-  - name: Virginia A. García Alonso^f^
-  - name: Claudia C. Boy^a^
-  - name: Daniel O. Bruno^a^^,^^c^
+  - name: Luciana Riccialdelli^a^
 

### 2023-05-09 MS_ToSubmit/SupMaterial.Rmd
Co-authors order

@@
   - Irene R. Schloss
-  - Luciana Riccialdelli
+  - Gustavo A. Lovrich
+  - Claudia C. Boy
+  - Daniel O. Bruno  
   - Fabiana L. Capitanio
@@
   - Cintia Fraysse
-  - Gustavo A. Lovrich
+  - Virginia A. García Alonso
   - Andrea Raya Rey
   - Mariela L. Spinelli
+  - Marcos Tatián
   - Diego Urteaga
-  - Marcos Tatián
-  - Virginia A. García Alonso
-  - Claudia C. Boy
-  - Daniel O. Bruno
+  - Luciana Riccialdelli
 bibliography: AMPBancoBurdwood.bib

### 2023-05-14 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Lovrich & Delpiani suggs

@@
   - name: Daniel O. Bruno^a^^,^^c^
-  - name: Fabiana L. Capitanio^f^
-  - name: Sergio M. Delpiani^d^
-  - name: Juan Martín Díaz de Astarloa^d^
+  - name: Fabiana L. Capitanio^d^^,^^e^
+  - name: Sergio M. Delpiani^f^
+  - name: Juan Martín Díaz de Astarloa^e^
   - name: Cintia Fraysse^a^
-  - name: Virginia A. García Alonso^f^  
-  - name: Andrea Raya Rey^a^^,^^c^^,^^e^
-  - name: Mariela L. Spinelli^f^
+  - name: Virginia A. García Alonso^d^^,^^e^
+  - name: Andrea Raya Rey^a^^,^^c^^,^^g^
+  - name: Mariela L. Spinelli^d^^,^^e^
   - name: Marcos Tatián^h^^,^^i^
-  - name: Diego Urteaga^g^
+  - name: Diego Urteaga^j^
   - name: Luciana Riccialdelli^a^
@@
   - code: 4
+    address: Facultad de Ciencias Exactas y Naturales, Universidad de Buenos Aires (UBA), Argentina
+  - code: 5
+    address: Instituto de Biodiversidad y Biologia Experimental y Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, Argentina
+  - code: 6
     address: Instituto de Investigaciones Marinas y Costeras (IIMYC), Universidad Nacional de Mar del Plata-CONICET, Argentina
-  - code: 5
+  - code: 7
     address: Wildlife Conservation Society, Argentina
-  - code: 6
-    address: Instituto de Biodiversidad y Biologia Experimental y Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, Argentina
-  - code: 7
+  - code: 8
+    address: Facultad de Ciencias Exactas, Fisicas y Naturales, Universidad Nacional de Cordoba (UNC), Argentina
+  - code: 9
+    address: Instituto de Diversidad y Ecologia Animal (IDEA-CONICET)
+  - code: 10
     address: Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina
-  - code: 8
-    address: Instituto de Diversidad y Ecologia Animal (IDEA-CONICET)
-  - code: 9
-    address: Facultad de Ciencias Exactas, Fisicas y Naturales, Universidad Nacional de Cordoba (UNC), Argentina
 
@@
 The majority of these Marine Protected Areas (MPAs) focus on the presence of particularly vulnerable, keystone, or charismatic species, large numbers of endemic species, and/or high biodiversity across taxonomic levels.
-In the sub-Antarctic region, the level of ocean protection is mainly associated to oceanic islands, except for the MPAs Namuncurá - Banco Burdwood I and II (MPA N-BB, 53º–55ºS and 56º–62ºW, respectively), which are associated to a submarine plateau and its southern adjacent deep slope region, respectively.
+In the sub-Antarctic region, the level of ocean protection is mainly associated to oceanic islands, except for the MPAs Namuncurá - Burdwood Bank I and II (MPA N-BB, 53º–55ºS and 56º–62ºW, respectively), which are associated to a submarine plateau and its southern adjacent deep slope region, respectively.
 Here, we present the first detailed analysis of the network of predator-prey interactions (food web) for the MPA N-BB ecosystem.
@@
   - Structure
-  - Marine Protected Area
+  - Burdwood Bank
   - Southwest Atlantic
@@
 In the sub-Antarctic region, the level of ocean protection is mainly associated to oceanic islands, such as the South Georgia and South Sandwich, Bouvet, Prince Edward, and Macquarie islands [@IUCN2023].
-Interestingly, the case of the MPAs Namuncurá - Banco Burdwood I and II (MPA N-BB, 53º–55ºS 56º–62ºW), which is the focus of this work, is unique since these MPAs are associated to a submarine plateau and its southern adjacent deep slope region, respectively [@Falabella2017].
+Interestingly, the case of the MPAs Namuncurá - Burdwood Bank I and II (MPA N-BB, 53º–55ºS 56º–62ºW), which is the focus of this work, is unique since these MPAs are associated to a submarine plateau and its southern adjacent deep slope region, respectively [@Falabella2017].
 In addition, such MPAs are part of a network of protected areas in the sub-Antarctic area (jointly with MPA Yaganes) that aims to protect and strengthen the functioning of this southern region to maintain global ocean health.
@@
 The benthic community is featured by high biomass of vulnerable and fragile species (mainly Porifera and Cnidaria) that meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResources2009].
-Also, it provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge and nursery area [@GarciaAlonso2018; @Delpiani2020; @Troccoli2020; @CovattiAle2022; @Fischer2022; @Florencia2023].
+Also, it provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge and nursery area [@GarciaAlonso2018; @Vazquez2018; @Delpiani2020; @Troccoli2020; @CovattiAle2022; @Fischer2022; @Florencia2023].
 The maintenance of this singular community is related to local and regional oceanographic processes, including the circulation of the rich Malvinas (Falkland) current in the area [@Piola1989; @Guerrero1999] and the upwelling and mixing phenomena [@Matano2019].
 The input of nutrients from the Malvinas (Falkland) current also supports a diverse plankton community [@Guinder2020].
-Overall, 811 benthic and plankton species have been identified for the MPA N-BB ecosystem, where 349 were reported for the first time in the area in recent years [@APN2022].
+Overall, 811 benthic and plankton species have been identified for the MPA N-BB ecosystem, where 349 were reported for the first time in the area in recent years [@AdministraciondeParquesNacionales2022].
 However, identifying the main species involved in the maintenance of ecosystem services and health as well as for management and conservation is essential.
@@
 Recently, the structure of the southwestern South Atlantic Ocean has been proposed to be under a 'wasp-waist' control, meaning that the structure and dynamics of the ecosystem are regulated primarily by mid-trophic level species (e.g., fishes, crustaceans) [@Padovani2012; @Saporiti2015; @Riccialdelli2020].
-In particular, the ecosystem of the MPA N-BB shows a more pronounced 'wasp-waist' structure, meaning a shorter food-chain length and a greater trophic overlap and redundancy, than other sub-Antarctic areas, such as the Atlantic coast of Tierra del Fuego.
+In particular, the ecosystem of the MPA N-BB shows a more pronounced 'wasp-waist' structure, meaning a shorter food-chain length and a greater trophic overlap and redundancy, than other sub-Antarctic areas, such as the continental shelf off Tierra del Fuego.
 The Fuegian sprat *Sprattus fuegensis* and longtail southern cod *Patagonotothen ramsayi* are considered the most plausible 'wasp-waist' species [@Riccialdelli2020].
@@
 High-latitude marine ecosystems, such as the MPA N-BB, are considered complex systems in terms of biodiversity and ecological interactions [@Day2013; @Kortsch2019; @Cordone2020; @Trathan2021].
-Although there is a robust knowledge about the complexity considering the richness of the benthic and plankton communities in the MPA N-BB ecosystem [@Schejter2016; @Guinder2020; @Schejter2020; @APN2022], a better understanding of species interactions' complexity and structure is needed.
+Although there is a robust knowledge about the complexity considering the richness of the benthic and plankton communities in the MPA N-BB ecosystem [@Schejter2016; @Guinder2020; @Schejter2020; @AdministraciondeParquesNacionales2022], a better understanding of species interactions' complexity and structure is needed.
 This aspect can be tackled by analysing one of the most frequent relationships between species: the predator-prey interaction [@Bascompte2009].
@@
 In recent years, network approaches have been successfully applied to study complex high-latitude marine ecosystems, improving our knowledge on structure, functioning, and response to environmental/anthropogenic changes [@Kortsch2015; @Cordone2018; @Funes2022; @Marina2023].
-Among anthropogenic threats, it is worth mentioning that contaminants like mercury and microplastics have been recently reported as important threats to the MPA N-BB region [@Cossi2021; @DiMauro2022; @Fioramonti2022].
+Among anthropogenic threats, it is worth mentioning that contaminants like mercury and microplastics have been recently reported as important threats to the MPA N-BB region [@Cossi2021; @DiMauro2022; @Fioramonti2022]; also fishing vessels are allowed to operate in the western section of the MPA N-BB (i.e.
+Marine National Reserve category), altering the stocks of commercially important fish species [@Martinez2021; @AdministraciondeParquesNacionales2022].
+Moreover, there is a potential hazard related to the effects of offshore activities (exploration and explotation) to the west of the MPA N-BB [@AdministraciondeParquesNacionales2022].
 
@@
 
-The MPAs Namuncurá - Banco Burdwood I and II, created by National Laws 26.875 and 27.490, comprise a shallow submarine plateau called Burdwood Bank (BB) and a deep slope that reaches 4000 m in depth, N-BB I and N-BB II, respectively [@APN2023] (Figure 1).
+The MPAs Namuncurá - Burdwood Bank I and II, created by National Laws 26.875 in 2013 and 27.490 in 2017, comprise a shallow submarine plateau called Burdwood Bank (BB) and a deep slope that reaches 4000 m in depth, N-BB I and N-BB II, respectively [@Tombesi2020; @AdministraciondeParquesNacionales2023] (Figure 1).
 They are located 150 km east of Isla de los Estados and 200 km south of Malvinas/Falkland Islands.
@@
 The BB is surrounded by steep flanks of up to 4000 m depth through which strong currents circulate [@Piola1989; @Reta2014; @Matano2019].
-Such deep slope forms the basis of N-BB II, protecting about 32,000 km^2^.
+The N-BB II includes such a deep slope, protecting about 32,000 km^2^.
 Intense upwelling and mixing occur over it, entraining deep nutrient-rich waters into the photic layer [@Piola2009; @Matano2019] and resulting in a fairly homogeneous water column both spatially and temporally [@Glorioso1995; @Guerrero1999; @Matano2019].
 
-Given the evidence collected during several research cruises about the oceanographic and ecological processes connecting MPAs N-BB I and II [references in @APN2022], a joint management plan was recently proposed [@APN2022].
+Given the evidence collected during several research cruises about the oceanographic and ecological processes connecting MPAs N-BB I and II [references in @AdministraciondeParquesNacionales2022], a joint management plan was recently proposed [@AdministraciondeParquesNacionales2022].
 This is why, the study area of the present work includes both MPAs.
 
-```{r figure1, echo=FALSE, fig.width = 5, fig.height = 10, out.width = '100%', fig.cap="Marine Protected Areas Namuncurá - Banco Burdwood I (MNR and MNP, northern section) and II (MNR and SMNR, southern section).
+```{r figure1, echo=FALSE, fig.width = 5, fig.height = 10, out.width = '100%', fig.cap="Marine Protected Areas Namuncurá - Burdwood Bank I (MNR and MNP, northern section) and II (MNR and SMNR, southern section).
 Acronyms indicate categories according to the management plan: MNR - Marine National Reserve, MNP - Marine National Park and RMNR - Restricted Marine National Reserve."}
@@
 theses, public databases, and reports belonging to 16 research cruises conducted in the MPAs N-BB I and II during 2014-2019.
-Here it is important to note that the sampling effort was greater in the MPA N-BB I.
+It is noteworthy that the sampling effort was greater in the MPA N-BB I.
 Furthermore, we took into account personal communications from experts belonging to the working group of the study area (https://www.pampazul.gob.ar/tag/banco-burdwood/).
@@
 $$
-where $E_i$ is the effective number of interactions between $K_i$ nearest-neighbor nodes of node $i$ and the maximal possible number of such interactions [@Newman2003].
+where $E_i$ is the effective number of interactions between $K_i$ nearest-neighbour nodes of node $i$ and the maximal possible number of such interactions [@Newman2003].
 To test whether the food web presented the small-world pattern, we compared the empirical values of CPL and CC with those resulting from 1000 randomly generated networks with the same size (S) and number of interactions (L), following the method proposed by @Marina2018a.
@@
 
-In terms of complexity, the MPA Namuncurá - Banco Burdwood food web (N-BB I and II) consisted of 1780 predator-prey interactions and 375 species, where 93% of them were defined at the species taxonomical level (Figure 2, Table S2).
+In terms of complexity, the MPA Namuncurá - Burdwood Bank food web (N-BB I and II) consisted of 1780 predator-prey interactions and 375 species, where 93% of them were defined at the species taxonomical level (Figure 2, Table S2).
 The food web presented a link density (e.g., the average number of interactions per species) of 4.75, and a connectance of 0.01.
@@
 
-```{r figure2, echo=FALSE, fig.width = 5.5, fig.height = 10, fig.align='center', fig.cap="Graph of the food web for the MPA Namuncurá - Banco Burdwood.
+```{r figure2, echo=FALSE, fig.width = 5.5, fig.height = 10, fig.align='center', fig.cap="Graph of the food web for the MPA Namuncurá - Burdwood Bank.
 Circles represent species and arrows trophic interactions.
@@
 knitr::kable(round(prop_topol,2) %>% dplyr::select(Size, Links, LD, Connectance, Omnivory, PathLength, Clustering) %>% mutate(SW = "True"), col.names = c("Species","Interactions","Density","Connectance","Omnivory","CPL", "CC", "SW"),
-                      caption = "Network-level properties of the MPA Namuncurá - Banco Burdwood food web.
+                      caption = "Network-level properties of the MPA Namuncurá - Burdwood Bank food web.
 CPL: Characteristic Path Length; CC: Clustering Coefficient; SW: Small-World pattern.
@@
 
-## The food web of the MPA Namuncurá - Banco Burdwood ecosystem
+## The food web of the MPA Namuncurá - Burdwood Bank ecosystem
 
@@
 In this sense, empirical analyses support the notion that highly-connected ecological networks are robust against external perturbations such as the introduction of new (e.g., invasive) species [@Smith-Ramesh2017] as well as species removal (e.g., local extinction) [@Dunne2002; @Montoya2003].
-The connectance of the food web of the MPA Namuncurá - Banco Burdwood (0.01) is one of the lowest reported so far for these regions; in particular, it appears to be five times lower than that of Beagle Channel, an adjacent coastal area [@Rodriguez2022].
+The connectance of the food web of the MPA Namuncurá - Burdwood Bank (0.01) is one of the lowest reported so far for these regions; in particular, it appears to much lower than that of Beagle Channel (0.05), an adjacent coastal area [@Rodriguez2022].
 
@@
 In summary, the food web of the MPA N-BB presents a combination of network properties that makes it unique in terms of network resolution, complexity, and structural pattern.
-All this suggests that the ecosystem might be fragile to external perturbations targeting highly connected species.
+All this suggests that the ecosystem might be fragile to external perturbations targeting highly connected species, which in turn coincides to be commercial exploited species as fishes [@Martinez2015].
 However, structural properties might provide resilience and resistance with the final outcome of a rearranged structure maintaining its functions.
@@
 This result is in agreement with the sole analysis, using stable isotopes, that exists so far for the trophic structure of the MPA N-BB [@Riccialdelli2020], and resembles other high-latitude marine systems of the Southwest Atlantic and Antarctic regions [@Arkhipkin2013; @Marina2018].
-The importance of these particular generalist species also arises since they feed on the benthic and pelagic habitats [@Troccoli2020; @CovattiAle2022; @Fischer2022], linking these realms and contributing to the vertical carbon flow.
+The importance of these particular generalist species also arises since they feed in the benthic and pelagic habitats [@Troccoli2020; @CovattiAle2022; @Fischer2022], linking these realms and contributing to the vertical carbon flow.
 
@@
 The most demanded source we identified in this study (i.e.
-detritus) supports the abundant benthic community of filter-feeders [@Schejter2016].
+detritus) supports the abundant benthic community of filter-feeders [@Schejter2016], likely feeding on detritus that is constantly resuspended from the bottom [@Martin2021].
 Furthermore, we found that the second and third-most consumed prey were diatoms and species of *Euphausia*, respectively, which are essential sources for the diverse zooplankton community [@Spinelli2020], mid-TL consumers like the Fuegian sprat *Sprattus fuegensis* [@Padovani2021] and *Patagonotothen ramsayi* [@Fischer2022], and top predators such as the black-browed and grey-headed albatrosses (*Thalassarche melanophris* and *Thalassarche chrysostoma*, respectively) [@Catry2004], and baleen whales (species of the genera Balaenoptera and Eubalaena) [@Valenzuela2018].
@@
 At the same time, our results highlight the uniqueness in terms of the trophic role of high-TL predators.
-Here, not only the expected pelagic animals such as marine mammals and seabirds arise as relevant, but also benthic vertebrate (chondrichthyans *Bathyraja macloviana* and *Squalus acanthias*) and invertebrate species (echinoderms *Diplopteraster clarki* and *Pteraster sp*) are noteworthy.
+Here, not only the expected pelagic animals such as marine mammals and seabirds arise as relevant, but also demersal vertebrate (chondrichthyans *Bathyraja macloviana* and *Squalus acanthias*) and benthic invertebrate species (echinoderms *Diplopteraster clarki* and *Pteraster sp*) are noteworthy.
 The role that such species play in the MPA N-BB ecosystem is unique and perturbations on them might result in unprecedented changes at the trophic structure and functioning level.
+In this regard, we should mention the potential threat of the fisheries operating in the western section of the MPA N-BB, where this activity is allowed and mostly focuses on the Patagonian toothfish *Dissostichus eleginoides* and the southern blue whiting *Micromesistius australis* [@Martinez2015].
+Although the fishing effort is concentrated outside the limits of the MPA N-BB, the impact on the MPA ecosystem should not be neglected [@Martinez2021].
 
@@
 
-The food web studied in the present work might be more representative of the MPA Namuncurá - Banco Burdwood I ecosystem, which comprises the shallow submarine plateau called Burdwood Bank.
+The food web studied in the present work might be more representative of the shallow ecosystem of the submarine plateau called Burdwood Bank, on which most of the research was focused as the MPA N-BB I was first created.
 This is related to the sampling effort that was conducted during the research cruises in the former MPA compared to the MPA N-BB II (i.e.
@@
 As a consequence, most of the data we used to build the network come from studies performed in the MPA N-BB I.
-Despite this fact, we decided to build the food web considering both MPAs due to the tight oceanographic and ecological connection that exists among them [@APN2022 and references therein].
+Despite this fact, we decided to build the food web considering both MPAs due to the tight oceanographic and ecological connection that exists among them [@AdministraciondeParquesNacionales2022 and references therein].
 
-It's worth mentioning that we did not consider quantitative data (i.e.
+It's important to mark that we did not consider quantitative data (i.e.
 abundance, biomass) to assess the species' role in the food web.
@@
 The MPA N-BB I presents complex oceanographic conditions that generate an internal spatial heterogeneity, mainly along its longitudinal axis [@Matano2019].
-Up to date this heterogeneity has been reflected in phytoplankton and zooplankton communities [@Bertola2018; @GarciaAlonso2020; @Spinelli2020], and in fish assemblages [@Delpiani2020].
+So far this heterogeneity has been reflected in phytoplankton and zooplankton communities [@Bertola2018; @GarciaAlonso2020; @Spinelli2020], and in fish assemblages [@Delpiani2020].
 Moreover, seasonal variations also occur in some physical and biological aspects of the MPA N-BB I [@GarciaAlonso2018; @Matano2019].
@@
 
-We compiled information on the species and trophic diversity of the Marine Protected Area Namuncurá - Banco Burdwood, generating an unprecedented, well-resolved network of trophic interactions for a sub-Antarctic ecosystem, identifying the complexity and structure of the system, and the main species role in a network framework.
+We compiled information on the species and trophic diversity of the Marine Protected Area Namuncurá - Burdwood Bank, generating an unprecedented, well-resolved network of trophic interactions for a sub-Antarctic ecosystem, identifying the complexity and structure of the system, and the main species role in a network framework.
 Particular properties at the network level allowed us to identify the ecosystem's vulnerability and potential response to perturbations in the presence of highly-connected species, with a rearranged structure maintaining their functions due to its potential resilience and resistance.
@@
 Martinez (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina) and Luciano Padovani (Instituto Nacional de Investigación y Desarrollo Pesquero, INIDEP, Argentina).
-Special thanks to G.A. Lovrich the Scientific Coordinator of the MPA Namuncurá-Burdwood Bank and the MPA N-BB Administrators.
+Research cruises were funded by national funds by the Law 26.875.
 This study was funded by Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617), Argentina.

### 2023-05-14 MS_ToSubmit/MS_Burdwood_foodweb.tex
Co-authors order
Lovrich & Delpiani suggs

@@
 
-    \author[]{Luciana Riccialdelli\textsuperscript{a}%
+    \author[]{Gustavo A. Lovrich\textsuperscript{a}%
   %
@@
 
-    \author[]{Fabiana L. Capitanio\textsuperscript{f}%
+    \author[]{Claudia C. Boy\textsuperscript{a}%
   %
@@
 
-    \author[]{Sergio M. Delpiani\textsuperscript{d}%
+    \author[]{Daniel O. Bruno\textsuperscript{a,c}%
   %
@@
 
-    \author[]{Juan Martín Díaz de Astarloa\textsuperscript{d}%
+    \author[]{Fabiana L. Capitanio\textsuperscript{d,e}%
+  %
+  }
+
+    \author[]{Sergio M. Delpiani\textsuperscript{f}%
+  %
+  }
+
+    \author[]{Juan Martín Díaz de Astarloa\textsuperscript{e}%
   %
@@
 
-    \author[]{Gustavo A. Lovrich\textsuperscript{a}%
+    \author[]{Virginia A. García Alonso\textsuperscript{d,e}%
   %
@@
 
-    \author[]{Andrea Raya Rey\textsuperscript{a,c,e}%
+    \author[]{Andrea Raya Rey\textsuperscript{a,c,g}%
   %
@@
 
-    \author[]{Mariela L. Spinelli\textsuperscript{f}%
-  %
-  }
-
-    \author[]{Diego Urteaga\textsuperscript{g}%
+    \author[]{Mariela L. Spinelli\textsuperscript{d,e}%
   %
@@
 
-    \author[]{Virginia A. García Alonso\textsuperscript{f}%
+    \author[]{Diego Urteaga\textsuperscript{j}%
   %
@@
 
-    \author[]{Claudia C. Boy\textsuperscript{a}%
-  %
-  }
-
-    \author[]{Daniel O. Bruno\textsuperscript{a,c}%
+    \author[]{Luciana Riccialdelli\textsuperscript{a}%
   %
@@
 Naturales (ICPA), Universidad de Tierra del Fuego (UNTDF), Argentina}
-    \affiliation[4]{Instituto de Investigaciones Marinas y Costeras
+    \affiliation[4]{Facultad de Ciencias Exactas y Naturales,
+Universidad de Buenos Aires (UBA), Argentina}
+    \affiliation[5]{Instituto de Biodiversidad y Biologia Experimental y
+Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, Argentina}
+    \affiliation[6]{Instituto de Investigaciones Marinas y Costeras
 (IIMYC), Universidad Nacional de Mar del Plata-CONICET, Argentina}
-    \affiliation[5]{Wildlife Conservation Society, Argentina}
-    \affiliation[6]{Instituto de Biodiversidad y Biologia Experimental y
-Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, Argentina}
-    \affiliation[7]{Museo Argentino de Ciencias Naturales ``Bernardino
+    \affiliation[7]{Wildlife Conservation Society, Argentina}
+    \affiliation[8]{Facultad de Ciencias Exactas, Fisicas y Naturales,
+Universidad Nacional de Cordoba (UNC), Argentina}
+    \affiliation[9]{Instituto de Diversidad y Ecologia Animal
+(IDEA-CONICET)}
+    \affiliation[10]{Museo Argentino de Ciencias Naturales ``Bernardino
 Rivadavia'', Argentina}
-    \affiliation[8]{Instituto de Diversidad y Ecologia Animal
-(IDEA-CONICET)}
-    \affiliation[9]{Facultad de Ciencias Exactas, Fisicas y Naturales,
-Universidad Nacional de Cordoba (UNC), Argentina}
     \cortext[cor1]{Corresponding author}
@@
   sub-Antarctic region, the level of ocean protection is mainly
-  associated to oceanic islands, except for the MPAs Namuncurá - Banco
-  Burdwood I and II (MPA N-BB, 53º--55ºS and 56º--62ºW, respectively),
-  which are associated to a submarine plateau and its southern adjacent
-  deep slope region, respectively. Here, we present the first detailed
-  analysis of the network of predator-prey interactions (food web) for
-  the MPA N-BB ecosystem. We applied a network approach to characterise
-  the food web in terms of complexity and structure, and identifying the
-  species' role in such a framework. In terms of complexity, the MPA
-  N-BB food web consisted of 1780 predator-prey interactions and 375
-  species, with a link density of 4.75 and a connectance of 0.01. In
-  terms of structure, almost half of the consumers were omnivores
-  (0.48), and the network displayed a small-world pattern. These
-  findings suggest that the ecosystem might be vulnerable to external
-  perturbations targeting highly connected species, although structural
-  properties might provide resilience and resistance, resulting in a
-  rearranged structure that preserves its original functions.
-  Furthermore, we identified several species as important in terms of
-  different aspects of trophic structure and functioning, and response
-  to perturbations. We suggest that generalist species, mainly fishes,
-  play a crucial role in the ecosystem's bentho-pelagic coupling process
-  and that other species, besides the longtail southern cod
-  \emph{Patagonotothen ramsayi} and the Fueguian sprat \emph{Sprattus
-  fuegensis}, should be considered as relevant energy transfers for the
-  ecosystem. Finally, we argue that the diversity of species, including
-  both the benthic and pelagic habitats, is responsible for seccuring
-  the connectivity within the food web against perturbations, therefore
-  contributing to the structure and stability of the ecosystem.
+  associated to oceanic islands, except for the MPAs Namuncurá -
+  Burdwood Bank I and II (MPA N-BB, 53º--55ºS and 56º--62ºW,
+  respectively), which are associated to a submarine plateau and its
+  southern adjacent deep slope region, respectively. Here, we present
+  the first detailed analysis of the network of predator-prey
+  interactions (food web) for the MPA N-BB ecosystem. We applied a
+  network approach to characterise the food web in terms of complexity
+  and structure, and identifying the species' role in such a framework.
+  In terms of complexity, the MPA N-BB food web consisted of 1780
+  predator-prey interactions and 375 species, with a link density of
+  4.75 and a connectance of 0.01. In terms of structure, almost half of
+  the consumers were omnivores (0.48), and the network displayed a
+  small-world pattern. These findings suggest that the ecosystem might
+  be vulnerable to external perturbations targeting highly connected
+  species, although structural properties might provide resilience and
+  resistance, resulting in a rearranged structure that preserves its
+  original functions. Furthermore, we identified several species as
+  important in terms of different aspects of trophic structure and
+  functioning, and response to perturbations. We suggest that generalist
+  species, mainly fishes, play a crucial role in the ecosystem's
+  bentho-pelagic coupling process and that other species, besides the
+  longtail southern cod \emph{Patagonotothen ramsayi} and the Fueguian
+  sprat \emph{Sprattus fuegensis}, should be considered as relevant
+  energy transfers for the ecosystem. Finally, we argue that the
+  diversity of species, including both the benthic and pelagic habitats,
+  is responsible for seccuring the connectivity within the food web
+  against perturbations, therefore contributing to the structure and
+  stability of the ecosystem.
   \end{abstract}
     \begin{keyword}
-    Food web \sep Complexity \sep Structure \sep Marine Protected
-Area \sep 
+    Food web \sep Complexity \sep Structure \sep Burdwood Bank \sep 
     Southwest Atlantic
@@
 Sandwich, Bouvet, Prince Edward, and Macquarie islands (IUCN \&
-UNEP-WCMC, 2023). Interestingly, the case of the MPAs Namuncurá - Banco
-Burdwood I and II (MPA N-BB, 53º--55ºS 56º--62ºW), which is the focus of
-this work, is unique since these MPAs are associated to a submarine
-plateau and its southern adjacent deep slope region, respectively
-(Falabella, 2017). In addition, such MPAs are part of a network of
-protected areas in the sub-Antarctic area (jointly with MPA Yaganes)
-that aims to protect and strengthen the functioning of this southern
-region to maintain global ocean health.
+UNEP-WCMC, 2023). Interestingly, the case of the MPAs Namuncurá -
+Burdwood Bank I and II (MPA N-BB, 53º--55ºS 56º--62ºW), which is the
+focus of this work, is unique since these MPAs are associated to a
+submarine plateau and its southern adjacent deep slope region,
+respectively (Falabella, 2017). In addition, such MPAs are part of a
+network of protected areas in the sub-Antarctic area (jointly with MPA
+Yaganes) that aims to protect and strengthen the functioning of this
+southern region to maintain global ocean health.
 
@@
 Florencia et al., 2023; García Alonso et al., 2018; Troccoli et al.,
-2020). The maintenance of this singular community is related to local
-and regional oceanographic processes, including the circulation of the
-rich Malvinas (Falkland) current in the area (Guerrero et al., 1999; A.
-R. Piola \& Gordon, 1989) and the upwelling and mixing phenomena (Matano
-et al., 2019). The input of nutrients from the Malvinas (Falkland)
-current also supports a diverse plankton community (Guinder et al.,
-2020). Overall, 811 benthic and plankton species have been identified
-for the MPA N-BB ecosystem, where 349 were reported for the first time
-in the area in recent years (APN, 2022). However, identifying the main
-species involved in the maintenance of ecosystem services and health as
-well as for management and conservation is essential.
+2020; Vazquez et al., 2018). The maintenance of this singular community
+is related to local and regional oceanographic processes, including the
+circulation of the rich Malvinas (Falkland) current in the area
+(Guerrero et al., 1999; Piola \& Gordon, 1989) and the upwelling and
+mixing phenomena (Matano et al., 2019). The input of nutrients from the
+Malvinas (Falkland) current also supports a diverse plankton community
+(Guinder et al., 2020). Overall, 811 benthic and plankton species have
+been identified for the MPA N-BB ecosystem, where 349 were reported for
+the first time in the area in recent years (Administracion de Parques
+Nacionales, 2022). However, identifying the main species involved in the
+maintenance of ecosystem services and health as well as for management
+and conservation is essential.
 
@@
 overlap and redundancy, than other sub-Antarctic areas, such as the
-Atlantic coast of Tierra del Fuego. The Fuegian sprat \emph{Sprattus
+continental shelf off Tierra del Fuego. The Fuegian sprat \emph{Sprattus
 fuegensis} and longtail southern cod \emph{Patagonotothen ramsayi} are
@@
 considering the richness of the benthic and plankton communities in the
-MPA N-BB ecosystem (APN, 2022; Guinder et al., 2020; Schejter et al.,
-2016, 2020), a better understanding of species interactions' complexity
-and structure is needed. This aspect can be tackled by analysing one of
-the most frequent relationships between species: the predator-prey
-interaction (Bascompte, 2009). The sum of predator-prey or trophic
-interactions of a particular region is referred to as a food web,
-representing the roadmap for matter and energy flow in an ecosystem. In
-recent years, network approaches have been successfully applied to study
-complex high-latitude marine ecosystems, improving our knowledge on
-structure, functioning, and response to environmental/anthropogenic
-changes (Cordone et al., 2018; Funes et al., 2022; Kortsch et al., 2015;
-Marina et al., 2023). Among anthropogenic threats, it is worth
-mentioning that contaminants like mercury and microplastics have been
-recently reported as important threats to the MPA N-BB region (Cossi et
-al., 2021; Di Mauro et al., 2022; Fioramonti et al., 2022).
+MPA N-BB ecosystem (Administracion de Parques Nacionales, 2022; Guinder
+et al., 2020; Schejter et al., 2016, 2020), a better understanding of
+species interactions' complexity and structure is needed. This aspect
+can be tackled by analysing one of the most frequent relationships
+between species: the predator-prey interaction (Bascompte, 2009). The
+sum of predator-prey or trophic interactions of a particular region is
+referred to as a food web, representing the roadmap for matter and
+energy flow in an ecosystem. In recent years, network approaches have
+been successfully applied to study complex high-latitude marine
+ecosystems, improving our knowledge on structure, functioning, and
+response to environmental/anthropogenic changes (Cordone et al., 2018;
+Funes et al., 2022; Kortsch et al., 2015; Marina et al., 2023). Among
+anthropogenic threats, it is worth mentioning that contaminants like
+mercury and microplastics have been recently reported as important
+threats to the MPA N-BB region (Cossi et al., 2021; Di Mauro et al.,
+2022; Fioramonti et al., 2022); also fishing vessels are allowed to
+operate in the western section of the MPA N-BB (i.e.~Marine National
+Reserve category), altering the stocks of commercially important fish
+species (Administracion de Parques Nacionales, 2022; Martínez et al.,
+2021). Moreover, there is a potential hazard related to the effects of
+offshore activities (exploration and explotation) to the west of the MPA
+N-BB (Administracion de Parques Nacionales, 2022).
 
@@
 
-The MPAs Namuncurá - Banco Burdwood I and II, created by National Laws
-26.875 and 27.490, comprise a shallow submarine plateau called Burdwood
-Bank (BB) and a deep slope that reaches 4000 m in depth, N-BB I and N-BB
-II, respectively (APN, 2023) (Figure 1). They are located 150 km east of
+The MPAs Namuncurá - Burdwood Bank I and II, created by National Laws
+26.875 in 2013 and 27.490 in 2017, comprise a shallow submarine plateau
+called Burdwood Bank (BB) and a deep slope that reaches 4000 m in depth,
+N-BB I and N-BB II, respectively (Administracion de Parques Nacionales,
+2023; Tombesi et al., 2020) (Figure 1). They are located 150 km east of
 Isla de los Estados and 200 km south of Malvinas/Falkland Islands. The
@@
 fairly stable, with salinity averaging 34 all year round and temperature
-ranging between 4 and 8ºC (Acha et al., 2004; Guerrero et al., 1999; A.
+ranging between 4 and 8ºC (Acha et al., 2004; Guerrero et al., 1999;
 Piola \& Falabella, 2009). The BB is surrounded by steep flanks of up to
 4000 m depth through which strong currents circulate (Matano et al.,
-2019; A. R. Piola \& Gordon, 1989; Reta, 2014). Such deep slope forms
-the basis of N-BB II, protecting about 32,000 km\textsuperscript{2}.
-Intense upwelling and mixing occur over it, entraining deep
-nutrient-rich waters into the photic layer (Matano et al., 2019; A.
-Piola \& Falabella, 2009) and resulting in a fairly homogeneous water
-column both spatially and temporally (Glorioso \& Flather, 1995;
-Guerrero et al., 1999; Matano et al., 2019).
+2019; Piola \& Gordon, 1989; Reta, 2014). The N-BB II includes such a
+deep slope, protecting about 32,000 km\textsuperscript{2}. Intense
+upwelling and mixing occur over it, entraining deep nutrient-rich waters
+into the photic layer (Matano et al., 2019; Piola \& Falabella, 2009)
+and resulting in a fairly homogeneous water column both spatially and
+temporally (Glorioso \& Flather, 1995; Guerrero et al., 1999; Matano et
+al., 2019).
 
@@
 oceanographic and ecological processes connecting MPAs N-BB I and II
-(references in APN, 2022), a joint management plan was recently proposed
-(APN, 2022). This is why, the study area of the present work includes
-both MPAs.
+(references in Administracion de Parques Nacionales, 2022), a joint
+management plan was recently proposed (Administracion de Parques
+Nacionales, 2022). This is why, the study area of the present work
+includes both MPAs.
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{MPABurdwood_map} \caption{Marine Protected Areas Namuncurá - Banco Burdwood I (MNR and MNP, northern section) and II (MNR and SMNR, southern section).
+\includegraphics[width=1\linewidth]{MPABurdwood_map} \caption{Marine Protected Areas Namuncurá - Burdwood Bank I (MNR and MNP, northern section) and II (MNR and SMNR, southern section).
 Acronyms indicate categories according to the management plan: MNR - Marine National Reserve, MNP - Marine National Park and RMNR - Restricted Marine National Reserve.}\label{fig:figure1}
@@
 public databases, and reports belonging to 16 research cruises conducted
-in the MPAs N-BB I and II during 2014-2019. Here it is important to note
-that the sampling effort was greater in the MPA N-BB I. Furthermore, we
-took into account personal communications from experts belonging to the
-working group of the study area
+in the MPAs N-BB I and II during 2014-2019. It is noteworthy that the
+sampling effort was greater in the MPA N-BB I. Furthermore, we took into
+account personal communications from experts belonging to the working
+group of the study area
 (https://www.pampazul.gob.ar/tag/banco-burdwood/). The diversity of the
@@
 \] where \(E_i\) is the effective number of interactions between \(K_i\)
-nearest-neighbor nodes of node \(i\) and the maximal possible number of
+nearest-neighbour nodes of node \(i\) and the maximal possible number of
 such interactions (Newman, 2003). To test whether the food web presented
@@
 
-In terms of complexity, the MPA Namuncurá - Banco Burdwood food web
-(N-BB I and II) consisted of 1780 predator-prey interactions and 375
-species, where 93\% of them were defined at the species taxonomical
-level (Figure 2, Table S2). The food web presented a link density (e.g.,
-the average number of interactions per species) of 4.75, and a
-connectance of 0.01. Almost half of the consumers were omnivores (0.48),
-feeding on sources at different trophic levels. The food web displayed a
-small-world pattern, meaning that the path length was lower and the
-clustering coefficient higher than the random networks (Table 2).
+In terms of complexity, the MPA Namuncurá - Burdwood Bank food web (N-BB
+I and II) consisted of 1780 predator-prey interactions and 375 species,
+where 93\% of them were defined at the species taxonomical level (Figure
+2, Table S2). The food web presented a link density (e.g., the average
+number of interactions per species) of 4.75, and a connectance of 0.01.
+Almost half of the consumers were omnivores (0.48), feeding on sources
+at different trophic levels. The food web displayed a small-world
+pattern, meaning that the path length was lower and the clustering
+coefficient higher than the random networks (Table 2).
 
@@
 
-\caption{Graph of the food web for the MPA Namuncurá - Banco Burdwood.
+\caption{Graph of the food web for the MPA Namuncurá - Burdwood Bank.
 Circles represent species and arrows trophic interactions.
@@
 
-\caption{\label{tab:table2}Network-level properties of the MPA Namuncurá - Banco Burdwood food web.
+\caption{\label{tab:table2}Network-level properties of the MPA Namuncurá - Burdwood Bank food web.
 CPL: Characteristic Path Length; CC: Clustering Coefficient; SW: Small-World pattern.
@@
 
-\hypertarget{the-food-web-of-the-mpa-namuncuruxe1---banco-burdwood-ecosystem}{%
-\subsection{The food web of the MPA Namuncurá - Banco Burdwood
-ecosystem}\label{the-food-web-of-the-mpa-namuncuruxe1---banco-burdwood-ecosystem}}
+\hypertarget{the-food-web-of-the-mpa-namuncuruxe1---burdwood-bank-ecosystem}{%
+\subsection{The food web of the MPA Namuncurá - Burdwood Bank
+ecosystem}\label{the-food-web-of-the-mpa-namuncuruxe1---burdwood-bank-ecosystem}}
 
@@
 extinction) (Dunne et al., 2002b; Montoya \& Solé, 2003). The
-connectance of the food web of the MPA Namuncurá - Banco Burdwood (0.01)
+connectance of the food web of the MPA Namuncurá - Burdwood Bank (0.01)
 is one of the lowest reported so far for these regions; in particular,
-it appears to be five times lower than that of Beagle Channel, an
-adjacent coastal area (Rodriguez et al., 2022).
+it appears to much lower than that of Beagle Channel (0.05), an adjacent
+coastal area (Rodriguez et al., 2022).
 
@@
 might be fragile to external perturbations targeting highly connected
-species. However, structural properties might provide resilience and
-resistance with the final outcome of a rearranged structure maintaining
-its functions.
+species, which in turn coincides to be commercial exploited species as
+fishes (Martínez et al., 2015). However, structural properties might
+provide resilience and resistance with the final outcome of a rearranged
+structure maintaining its functions.
 
@@
 al., 2018). The importance of these particular generalist species also
-arises since they feed on the benthic and pelagic habitats (Covatti Ale
+arises since they feed in the benthic and pelagic habitats (Covatti Ale
 et al., 2022; Fischer et al., 2022; Troccoli et al., 2020), linking
@@
 supports the abundant benthic community of filter-feeders (Schejter et
-al., 2016). Furthermore, we found that the second and third-most
-consumed prey were diatoms and species of \emph{Euphausia},
-respectively, which are essential sources for the diverse zooplankton
-community (Spinelli et al., 2020), mid-TL consumers like the Fuegian
-sprat \emph{Sprattus fuegensis} (Padovani et al., 2021) and
-\emph{Patagonotothen ramsayi} (Fischer et al., 2022), and top predators
-such as the black-browed and grey-headed albatrosses (\emph{Thalassarche
-melanophris} and \emph{Thalassarche chrysostoma}, respectively) (Catry
-et al., 2004), and baleen whales (species of the genera Balaenoptera and
-Eubalaena) (Valenzuela et al., 2018).
+al., 2016), likely feeding on detritus that is constantly resuspended
+from the bottom (Martin \& Flores Melo, 2021). Furthermore, we found
+that the second and third-most consumed prey were diatoms and species of
+\emph{Euphausia}, respectively, which are essential sources for the
+diverse zooplankton community (Spinelli et al., 2020), mid-TL consumers
+like the Fuegian sprat \emph{Sprattus fuegensis} (Padovani et al., 2021)
+and \emph{Patagonotothen ramsayi} (Fischer et al., 2022), and top
+predators such as the black-browed and grey-headed albatrosses
+(\emph{Thalassarche melanophris} and \emph{Thalassarche chrysostoma},
+respectively) (Catry et al., 2004), and baleen whales (species of the
+genera Balaenoptera and Eubalaena) (Valenzuela et al., 2018).
 
@@
 pelagic animals such as marine mammals and seabirds arise as relevant,
-but also benthic vertebrate (chondrichthyans \emph{Bathyraja macloviana}
-and \emph{Squalus acanthias}) and invertebrate species (echinoderms
-\emph{Diplopteraster clarki} and \emph{Pteraster sp}) are noteworthy.
-The role that such species play in the MPA N-BB ecosystem is unique and
-perturbations on them might result in unprecedented changes at the
-trophic structure and functioning level.
+but also demersal vertebrate (chondrichthyans \emph{Bathyraja
+macloviana} and \emph{Squalus acanthias}) and benthic invertebrate
+species (echinoderms \emph{Diplopteraster clarki} and \emph{Pteraster
+sp}) are noteworthy. The role that such species play in the MPA N-BB
+ecosystem is unique and perturbations on them might result in
+unprecedented changes at the trophic structure and functioning level. In
+this regard, we should mention the potential threat of the fisheries
+operating in the western section of the MPA N-BB, where this activity is
+allowed and mostly focuses on the Patagonian toothfish
+\emph{Dissostichus eleginoides} and the southern blue whiting
+\emph{Micromesistius australis} (Martínez et al., 2015). Although the
+fishing effort is concentrated outside the limits of the MPA N-BB, the
+impact on the MPA ecosystem should not be neglected (Martínez et al.,
+2021).
 
@@
 The food web studied in the present work might be more representative of
-the MPA Namuncurá - Banco Burdwood I ecosystem, which comprises the
-shallow submarine plateau called Burdwood Bank. This is related to the
-sampling effort that was conducted during the research cruises in the
-former MPA compared to the MPA N-BB II (i.e.~deep flanks to the south).
-As a consequence, most of the data we used to build the network come
-from studies performed in the MPA N-BB I. Despite this fact, we decided
-to build the food web considering both MPAs due to the tight
-oceanographic and ecological connection that exists among them (APN,
-2022 and references therein).
-
-It's worth mentioning that we did not consider quantitative data
+the shallow ecosystem of the submarine plateau called Burdwood Bank, on
+which most of the research was focused as the MPA N-BB I was first
+created. This is related to the sampling effort that was conducted
+during the research cruises in the former MPA compared to the MPA N-BB
+II (i.e.~deep flanks to the south). As a consequence, most of the data
+we used to build the network come from studies performed in the MPA N-BB
+I. Despite this fact, we decided to build the food web considering both
+MPAs due to the tight oceanographic and ecological connection that
+exists among them (Administracion de Parques Nacionales, 2022 and
+references therein).
+
+It's important to mark that we did not consider quantitative data
 (i.e.~abundance, biomass) to assess the species' role in the food web.
@@
 an internal spatial heterogeneity, mainly along its longitudinal axis
-(Matano et al., 2019). Up to date this heterogeneity has been reflected
-in phytoplankton and zooplankton communities (Bértola et al., 2018;
-García Alonso et al., 2020; Spinelli et al., 2020), and in fish
-assemblages (Delpiani et al., 2020). Moreover, seasonal variations also
-occur in some physical and biological aspects of the MPA N-BB I (García
-Alonso et al., 2018; Matano et al., 2019). Considering both MPAs (N-BB I
-and II), a seasonal variation in the community composition of marine
-mammals and seabirds was recorded recently (Dellabianca et al., 2023).
-The spatial and seasonal variations in the plankton community might
-affect the energy and matter flow to higher levels of the food web. This
-has been recently studied in the vicinity of the MPA N-BB I, in the
-Beagle Channel, where a differential energy flow pattern of the plankton
+(Matano et al., 2019). So far this heterogeneity has been reflected in
+phytoplankton and zooplankton communities (Bértola et al., 2018; García
+Alonso et al., 2020; Spinelli et al., 2020), and in fish assemblages
+(Delpiani et al., 2020). Moreover, seasonal variations also occur in
+some physical and biological aspects of the MPA N-BB I (García Alonso et
+al., 2018; Matano et al., 2019). Considering both MPAs (N-BB I and II),
+a seasonal variation in the community composition of marine mammals and
+seabirds was recorded recently (Dellabianca et al., 2023). The spatial
+and seasonal variations in the plankton community might affect the
+energy and matter flow to higher levels of the food web. This has been
+recently studied in the vicinity of the MPA N-BB I, in the Beagle
+Channel, where a differential energy flow pattern of the plankton
 community has been recognised in two micro-basins of the Channel
@@
 We compiled information on the species and trophic diversity of the
-Marine Protected Area Namuncurá - Banco Burdwood, generating an
+Marine Protected Area Namuncurá - Burdwood Bank, generating an
 unprecedented, well-resolved network of trophic interactions for a
@@
 Luciano Padovani (Instituto Nacional de Investigación y Desarrollo
-Pesquero, INIDEP, Argentina). Special thanks to G.A. Lovrich the
-Scientific Coordinator of the MPA Namuncurá-Burdwood Bank and the MPA
-N-BB Administrators. This study was funded by Consejo Nacional de
+Pesquero, INIDEP, Argentina). Research cruises were funded by national
+funds by the Law 26.875. This study was funded by Consejo Nacional de
 Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-AdministraciondeParquesNacionales2022}{}}%
+Administracion de Parques Nacionales. (2022). \emph{Plan de gestión {AMP
+Namuncurá Banco Burdwood}}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-AdministraciondeParquesNacionales2023}{}}%
+Administracion de Parques Nacionales. (2023). \emph{Área {Marina
+Protegida Namuncurá Banco Burdwood}}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Albert2002}{}}%
@@
 378--382. \url{https://doi.org/10.1038/35019019}
-
-\leavevmode\vadjust pre{\hypertarget{ref-APN2022}{}}%
-APN. (2022). \emph{Plan de gestión {AMP Namuncurá Banco Burdwood}}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-APN2023}{}}%
-APN. (2023). \emph{Área {Marina Protegida Namuncurá Banco Burdwood}}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Martin2021}{}}%
+Martin, J., \& Flores Melo, X. (2021). \emph{{Área Marina Protegida
+Namuncurá Banco Burdwood: Aspectos físicos y biogeoquímicos}}.
+{Administración de Parques Nacionales}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Martinez1992}{}}%
@@
 \url{https://doi.org/10.2307/3544934}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Martinez2021}{}}%
+Martínez, P. A., Wöhler, O. C., Troccoli, G. H., \& Di Marco, E. J.
+(2021). \emph{{Análisis del impacto potencial provocado por el
+establecimiento de las áreas marinas protegidas Namuncurá-Banco Burdwood
+I, II y Yaganes en la pesquería argentina de merluza negra (Dissostichus
+eleginoides)}} (\{Technical report\} No. 23/2021; p. 17). {Instituto
+Nacional de Investigación y Desarrollo Pesquero (INIDEP)}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Martinez2015}{}}%
+Martínez, P. A., Wöhler, O. G., \& Troccoli, G. H. (2015). \emph{{La
+evolución de la pesquería de merluza negra (Dissostichus eleginoides) en
+el espacio marítimo argentino. Periodo 2003- 2014}} (\{Technical
+report\} No. 11/15; p. 12). {Instituto Nacional de Investigación y
+Desarrollo Pesquero (INIDEP)}.
 
@@
 de la sardina fueguina ({Sprattus} fuegensis) en la región patagónica
-austral durante la época reproductiva}. {INIDEP}.
+austral durante la época reproductiva} {[}Technical Report{]}.
+{Instituto Nacional de Investigación y Desarrollo Pesquero (INIDEP)}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Piola2009}{}}%
+Piola, A. R., \& Falabella, V. (2009). {El mar Patagónico}. In
+\emph{{Atlas del Mar Patagónico. Especies y Espacios}} (Falabella, V.,
+Campagna, C. y Croxall, J. Ed., pp. 54--75). {Wildlife Conservation
+Society y Birdlife Internacional}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Piola1989}{}}%
@@
 \url{https://doi.org/10.1016/0198-0149(89)90015-0}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Piola2009}{}}%
-Piola, A., \& Falabella, V. (2009). \emph{El mar {Patagónico}}.
-{Wildlife Conservation Society y Birdlife Internacional}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Tombesi2020}{}}%
+Tombesi, M. L., Rabufetti, F., \& Lovrich, G. A. (2020). Las áreas
+marinas protegidas en la {Argentina}. \emph{La Lupa. Colección Fueguina
+De Divulgación Científica}, \emph{16}, 2--7.
+https://doi.org/\url{https://www.coleccionlalupa.com.ar/index.php/lalupa/article/view/79}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Trathan2021}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Vazquez2018}{}}%
+Vazquez, D. M., Belleggia, M., Schejter, L., \& Mabragaña, E. (2018).
+Avoiding being dragged away: Finding egg cases of {Schroederichthys}
+bivius ({Chondrichthyes}: {Scyliorhinidae}) associated with benthic
+invertebrates. \emph{Journal of Fish Biology}, \emph{92}(1), 248--253.
+\url{https://doi.org/10.1111/jfb.13490}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Watts1998}{}}%

### 2023-05-15 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
References tidying

@@
 bibliography: AMPBancoBurdwood.bib
-nocite: '@*'
+#nocite: '@*' cites all references in .bib file
 linenumbers: true
@@
 The evidence of benefits provided by Marine Protected Areas (MPAs) as well as the urgent need for ocean protection have driven an unprecedented increase in the number of MPAs worldwide in recent years [@Roberts2017; @Sala2018].
-Globally, the total area of the world ocean designated under marine protection adds up to approximately 29,600,000 km^2^, distributed across nearly 18,444 MPAs and covering 8.16% of the ocean’s surface [@IUCN2023], and therefore approaching the 10% goal of the Convention of Biological Diversity [@CBD2004].
+Globally, the total area of the world ocean designated under marine protection adds up to approximately 29,600,000 km^2^, distributed across nearly 18,444 MPAs and covering 8.16% of the ocean’s surface [@IUCN2023], and therefore approaching the 10% goal of the Convention of Biological Diversity [@Secretariatoftheconventiononbiologicaldiversity2004].
 Despite this progress, recent reports have shown that actual protection has been overestimated because it includes areas that are not yet effectively protected (only declared) as well as areas that allow significant extractive activities [@Sala2018].
@@
 Indeed, the MPA N-BB was created to protect a sensitive and biodiverse benthic habitat that was barely known [@Schejter2016; @Falabella2017].
-The benthic community is featured by high biomass of vulnerable and fragile species (mainly Porifera and Cnidaria) that meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResources2009].
+The benthic community is featured by high biomass of vulnerable and fragile species (mainly Porifera and Cnidaria) that meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResourcesCCAMLR2009].
 Also, it provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge and nursery area [@GarciaAlonso2018; @Vazquez2018; @Delpiani2020; @Troccoli2020; @CovattiAle2022; @Fischer2022; @Florencia2023].
@@
 
-The MPAs Namuncurá - Burdwood Bank I and II, created by National Laws 26.875 in 2013 and 27.490 in 2017, comprise a shallow submarine plateau called Burdwood Bank (BB) and a deep slope that reaches 4000 m in depth, N-BB I and N-BB II, respectively [@Tombesi2020; @AdministraciondeParquesNacionales2023] (Figure 1).
+The MPAs Namuncurá - Burdwood Bank I and II, created by National Laws 26.875 in 2013 and 27.490 in 2017, comprise a shallow submarine plateau called Burdwood Bank (BB) and a deep slope that reaches 4000 m in depth, N-BB I and N-BB II, respectively [@Tombesi2020; @AdministraciondeParquesNacionales2022] (Figure 1).
 They are located 150 km east of Isla de los Estados and 200 km south of Malvinas/Falkland Islands.

### 2023-05-15 MS_ToSubmit/MS_Burdwood_foodweb.tex
References tidying

@@
 UNEP-WCMC, 2023), and therefore approaching the 10\% goal of the
-Convention of Biological Diversity (CBD, 2004). Despite this progress,
-recent reports have shown that actual protection has been overestimated
-because it includes areas that are not yet effectively protected (only
-declared) as well as areas that allow significant extractive activities
-(Sala et al., 2018).
+Convention of Biological Diversity (Secretariat of the convention on
+biological diversity, 2004). Despite this progress, recent reports have
+shown that actual protection has been overestimated because it includes
+areas that are not yet effectively protected (only declared) as well as
+areas that allow significant extractive activities (Sala et al., 2018).
 
@@
 biomass of 10 kg per 1200 m\textsuperscript{2} (Commission for the
-Conservation of Antarctic Marine Living Resources, 2009). Also, it
-provides habitat to several small-sized species (López-Gappa et al.,
-2018; Schejter \& Bremec, 2019; Sirito, 2019), and has an important role
-in the life history of fishes as a food source, refuge and nursery area
-(Covatti Ale et al., 2022; Delpiani et al., 2020; Fischer et al., 2022;
-Florencia et al., 2023; García Alonso et al., 2018; Troccoli et al.,
-2020; Vazquez et al., 2018). The maintenance of this singular community
-is related to local and regional oceanographic processes, including the
-circulation of the rich Malvinas (Falkland) current in the area
-(Guerrero et al., 1999; Piola \& Gordon, 1989) and the upwelling and
-mixing phenomena (Matano et al., 2019). The input of nutrients from the
-Malvinas (Falkland) current also supports a diverse plankton community
-(Guinder et al., 2020). Overall, 811 benthic and plankton species have
-been identified for the MPA N-BB ecosystem, where 349 were reported for
-the first time in the area in recent years (Administracion de Parques
-Nacionales, 2022). However, identifying the main species involved in the
-maintenance of ecosystem services and health as well as for management
-and conservation is essential.
+Conservation of Antarctic Marine Living Resources (CCAMLR), 2009). Also,
+it provides habitat to several small-sized species (López-Gappa et al.,
+2018; Martin Sirito, 2019; Schejter \& Bremec, 2019), and has an
+important role in the life history of fishes as a food source, refuge
+and nursery area (Covatti Ale et al., 2022; Delpiani et al., 2020;
+Fischer et al., 2022; Florencia et al., 2023; García Alonso et al.,
+2018; Troccoli et al., 2020; Vazquez et al., 2018). The maintenance of
+this singular community is related to local and regional oceanographic
+processes, including the circulation of the rich Malvinas (Falkland)
+current in the area (Guerrero et al., 1999; Piola \& Gordon, 1989) and
+the upwelling and mixing phenomena (Matano et al., 2019). The input of
+nutrients from the Malvinas (Falkland) current also supports a diverse
+plankton community (Guinder et al., 2020). Overall, 811 benthic and
+plankton species have been identified for the MPA N-BB ecosystem, where
+349 were reported for the first time in the area in recent years
+(Administración de Parques Nacionales, 2022). However, identifying the
+main species involved in the maintenance of ecosystem services and
+health as well as for management and conservation is essential.
 
@@
 considering the richness of the benthic and plankton communities in the
-MPA N-BB ecosystem (Administracion de Parques Nacionales, 2022; Guinder
+MPA N-BB ecosystem (Administración de Parques Nacionales, 2022; Guinder
 et al., 2020; Schejter et al., 2016, 2020), a better understanding of
@@
 Reserve category), altering the stocks of commercially important fish
-species (Administracion de Parques Nacionales, 2022; Martínez et al.,
+species (Administración de Parques Nacionales, 2022; Martínez et al.,
 2021). Moreover, there is a potential hazard related to the effects of
 offshore activities (exploration and explotation) to the west of the MPA
-N-BB (Administracion de Parques Nacionales, 2022).
+N-BB (Administración de Parques Nacionales, 2022).
 
@@
 called Burdwood Bank (BB) and a deep slope that reaches 4000 m in depth,
-N-BB I and N-BB II, respectively (Administracion de Parques Nacionales,
-2023; Tombesi et al., 2020) (Figure 1). They are located 150 km east of
+N-BB I and N-BB II, respectively (Administración de Parques Nacionales,
+2022; Tombesi et al., 2020) (Figure 1). They are located 150 km east of
 Isla de los Estados and 200 km south of Malvinas/Falkland Islands. The
@@
 oceanographic and ecological processes connecting MPAs N-BB I and II
-(references in Administracion de Parques Nacionales, 2022), a joint
-management plan was recently proposed (Administracion de Parques
+(references in Administración de Parques Nacionales, 2022), a joint
+management plan was recently proposed (Administración de Parques
 Nacionales, 2022). This is why, the study area of the present work
@@
 MPAs due to the tight oceanographic and ecological connection that
-exists among them (Administracion de Parques Nacionales, 2022 and
+exists among them (Administración de Parques Nacionales, 2022 and
 references therein).
@@
 \leavevmode\vadjust pre{\hypertarget{ref-AdministraciondeParquesNacionales2022}{}}%
-Administracion de Parques Nacionales. (2022). \emph{Plan de gestión {AMP
-Namuncurá Banco Burdwood}}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-AdministraciondeParquesNacionales2023}{}}%
-Administracion de Parques Nacionales. (2023). \emph{Área {Marina
-Protegida Namuncurá Banco Burdwood}}.
+Administración de Parques Nacionales. (2022). \emph{{Plan de gestión AMP
+Namuncurá Banco Burdwood}}. {Dirección Nacional de Áreas Marinas
+Protegidas (DNAMP), Argentina}.
 
@@
 \url{https://doi.org/10.1126/science.1170749}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Belleggia2019}{}}%
-Belleggia, M., Battagliotti, C., Cortés, F., \& Colonello, J. H. (2019).
-Feeding together: A global diet analysis of twenty-three species of
-chondrichthyes on a feeding ground area. \emph{Hydrobiologia},
-\emph{842}(1), 77--99. \url{https://doi.org/10.1007/s10750-019-04027-w}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Bergagna2019}{}}%
-Bergagna, L. (2019). \emph{{Descripción de los ensambles bentónicos del
-AMP Namuncurá-Banco Burdwood y estimación del contenido de carbono
--orgánico e inorgánico- allí presente.}} {[}\{Bachelor Thesis\}{]}.
-Universidad Nacional de Córdoba.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bergagna2020}{}}%
-Bergagna, L., Chiesa, I., Álvarez, Y. P., Ceballos, S. G., Boy, C. C.,
-Riccialdelli, L., \& Lovrich, G. A. (2020). {En el fondo el Banco es
-bueno}. \emph{La Lupa. Colección Fueguina de Divulgación Científica},
-\emph{16}, 20--24.
-
 \leavevmode\vadjust pre{\hypertarget{ref-Bertola2018}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Borrelli2014}{}}%
-Borrelli, J. J., \& Ginzburg, L. R. (2014). Why there are so few trophic
-levels: {Selection} against instability explains the pattern. \emph{Food
-Webs}, \emph{1}(1), 10--17.
-\url{https://doi.org/10.1016/j.fooweb.2014.11.002}
-
 \leavevmode\vadjust pre{\hypertarget{ref-Borrvall2000}{}}%
@@
 \url{https://doi.org/10.1046/j.1461-0248.2000.00130.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Brickle2009}{}}%
-Brickle, P., Arkhipkin, A. I., Laptikhovsky, V., Stocks, A., \& Taylor,
-A. (2009). Resource partitioning by two large planktivorous fishes
-{Micromesistius} australis and {Macruronus} magellanicus in the
-{Southwest Atlantic}. \emph{Estuarine, Coastal and Shelf Science},
-\emph{84}(1), 91--98. \url{https://doi.org/10.1016/j.ecss.2009.06.007}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-CBD2004}{}}%
-CBD. (2004). \emph{Secretariat of the convention on biological
-diversity: {Technical} advice on the establishment and management of a
-national system of marine and coastal protected areas, {Technical
-Series} number 13.}
-
 \leavevmode\vadjust pre{\hypertarget{ref-Cirtwill2018}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-AlvarezColombo2018}{}}%
-Colombo, G. Álvarez. (2018). \emph{{Informe de Campaña Namuncurá-Banco
-Burdwood: \textquestiondown Area de cría de peces australes?}} (p. 83)
-{[}\{Field campaign Report\}{]}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-CommissionfortheConservationofAntarcticMarineLivingResources2009}{}}%
-Commission for the Conservation of Antarctic Marine Living Resources.
-(2009). \emph{Vulnerable {Marine Ecosystem} taxa identification guide}.
+\leavevmode\vadjust pre{\hypertarget{ref-CommissionfortheConservationofAntarcticMarineLivingResourcesCCAMLR2009}{}}%
+Commission for the Conservation of Antarctic Marine Living Resources
+(CCAMLR). (2009). \emph{Vulnerable {Marine Ecosystem} taxa
+identification guide}. {Commission for the Conservation of Antarctic
+Marine Living Resources}.
 
@@
 147--165. \url{https://doi.org/10.1016/j.csr.2013.02.002}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Dellabianca2015}{}}%
-Dellabianca, N. A. (2015). \emph{{Informe de Campaña {``Namuncurá-Banco
-Burdwood''}}} (p. 48) {[}\{Field campaign Report\}{]}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Dellabianca2018}{}}%
-Dellabianca, N. A. (2018). \emph{{Informe de Campaña AMP Namuncurá
-\textendash{} Banco Burdwood: Comprendiendo la bomba biológica de
-carbono}} (p. 101) {[}\{Field campaign Report\}{]}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Estrada2007}{}}%
-Estrada, E. (2007). Food webs robustness to biodiversity loss: {The}
-roles of connectance, expansibility and degree distribution.
-\emph{Journal of Theoretical Biology}, \emph{244}(2), 296--307.
-\url{https://doi.org/10.1016/j.jtbi.2006.08.002}
-
 \leavevmode\vadjust pre{\hypertarget{ref-Fagan1997}{}}%
@@
 Burdwood}. {Contribuciones} para la línea de base y el plan de manejo}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fernandez2021}{}}%
-Fernández, M., Rodríguez-Ruiz, M., Gelcich, S., Hiriart-Bertrand, L., \&
-Castilla, J. C. (2021). Advances and challenges in marine conservation
-in {Chile}: {A} regional and global comparison. \emph{Aquatic
-Conservation: Marine and Freshwater Ecosystems}, \emph{31}(7),
-1760--1771. \url{https://doi.org/10.1002/aqc.3570}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Franco2020}{}}%
-Franco, B. C., Defeo, O., Piola, A. R., Barreiro, M., Yang, H., Ortega,
-L., Gianelli, I., Castello, J. P., Vera, C., Buratti, C., Pájaro, M.,
-Pezzi, L. P., \& Möller, O. O. (2020). Climate change impacts on the
-atmospheric circulation, ocean, and fisheries in the southwest {South
-Atlantic Ocean}: A review. \emph{Climatic Change}, \emph{162}(4),
-2359--2377. \url{https://doi.org/10.1007/s10584-020-02783-6}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Freeman1978}{}}%
-Freeman, L. C. (1978). Centrality in social networks conceptual
-clarification. \emph{Social Networks}, \emph{1}(3), 215--239.
-\url{https://doi.org/10.1016/0378-8733(78)90021-7}
-
 \leavevmode\vadjust pre{\hypertarget{ref-Funes2022}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Giberto2017}{}}%
-Giberto, D. A., Belleggia, M., \& Bremec, C. S. (2017). \emph{El bentos
-como alimento de peces comerciales.} {Instituto Nacional de
-Investigación y Desarrollo Pesquero (INIDEP)}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-Giesecke2021}{}}%
@@
 \url{https://doi.org/10.1016/j.tree.2018.01.007}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Grilli2016}{}}%
-Grilli, J., Rogers, T., \& Allesina, S. (2016). Modularity and stability
-in ecological communities. \emph{Nature Communications}, \emph{7}(1),
-12031. \url{https://doi.org/10.1038/ncomms12031}
 
@@
 IUCN, \& UNEP-WCMC. (2023). \emph{The world database on protected areas
-({WDPA})}.
+({WDPA})}. {Protected Planet}.
 
@@
 \url{https://doi.org/10.1890/09-2219.1}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kortsch2021}{}}%
-Kortsch, S., Frelat, R., Pecuchet, L., Olivier, P., Putnis, I.,
-Bonsdorff, E., Ojaveer, H., Jurgensone, I., Strāķe, S., Rubene, G.,
-Krūze, Ē., \& Nordström, M. C. (2021). Disentangling temporal food web
-dynamics facilitates understanding of ecosystem functioning.
-\emph{Journal of Animal Ecology}, \emph{90}(5), 1205--1216.
-\url{https://doi.org/10.1111/1365-2656.13447}
 
@@
 \url{https://doi.org/10.1098/rspb.2015.1546}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kreps2016}{}}%
-Kreps, G. (2016). \emph{{Informe de Campaña AMP Namuncurá - Banco
-Burdwood: Primavera 2016}} (p. 103) {[}\{Field campaign Report\}{]}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-LaMesa2016}{}}%
-La Mesa, M., Riginella, E., Melli, V., Bartolini, F., \& Mazzoldi, C.
-(2016). Biological traits of a sub-{Antarctic} nototheniid,
-{Patagonotothen} ramsayi, from the {Burdwood Bank}. \emph{Polar
-Biology}, \emph{39}(1), 103--111.
-\url{https://doi.org/10.1007/s00300-015-1663-6}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Martin2015}{}}%
-Martin, J. (2015). \emph{{Informe de Campaña Banco Burdwood/Namuncurá
-\textendash{} Tierra del Fuego}} (p. 78) {[}\{Field campaign
-Report\}{]}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-Martin2021}{}}%
 Martin, J., \& Flores Melo, X. (2021). \emph{{Área Marina Protegida
-Namuncurá Banco Burdwood: Aspectos físicos y biogeoquímicos}}.
-{Administración de Parques Nacionales}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Martinez1992}{}}%
-Martinez, N. D. (1992). Constant {Connectance} in {Community Food Webs}.
-\emph{The American Naturalist}, \emph{139}(6), 1208--1218.
-\url{https://doi.org/10.1086/285382}
+Namuncurá Banco Burdwood: Aspectos físicos y biogeoquímicos}}. {Tercer
+taller científico sobre el Área Marina Protegida Namuncurá Banco
+Burdwood. Administración de Parques Nacionales (APN), Argentina}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-MartinSirito2019}{}}%
+Martin Sirito, S. (2019). \emph{{Fauna asociada a corales (Octocorallia)
+e hidroides (Hydrozoa) del Área Marina Protegida {``Namuncurá''} (Banco
+Burdwood) y zonas profundas adyacentes}} {[}PhD thesis{]}. Universidad
+Nacional de Mar del Plata (UNMdP), Argentina.
 
@@
 eleginoides)}} (\{Technical report\} No. 23/2021; p. 17). {Instituto
-Nacional de Investigación y Desarrollo Pesquero (INIDEP)}.
+Nacional de Investigación y Desarrollo Pesquero (INIDEP), Argentina}.
 
@@
 report\} No. 11/15; p. 12). {Instituto Nacional de Investigación y
-Desarrollo Pesquero (INIDEP)}.
+Desarrollo Pesquero (INIDEP), Argentina}.
 
@@
 \emph{124}(10), 6904--6926. \url{https://doi.org/10.1029/2019JC015001}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Matusevich2022}{}}%
-Matusevich. (2022). \emph{Chondrichthyan fauna from the {Marine
-Protected Area Namuncurá} at {Burdwood Bank}: Exploring egg nursery
-grounds}. https://www.researchsquare.com.
-\url{https://doi.org/10.21203/rs.3.rs-2247873/v1}
-
-\leavevmode\vadjust pre{\hypertarget{ref-May1973}{}}%
-May, R. (1973). \emph{Stability and complexity in model ecosystems}.
-{Princeton University Press}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ospina-Alvarez2020}{}}%
-Ospina-Alvarez, A., de Juan, S., Alós, J., Basterretxea, G.,
-Alonso-Fernández, A., Follana-Berná, G., Palmer, M., \& Catalán, I.
-(2020). {MPA} network design based on graph theory and emergent
-properties of larval dispersal. \emph{Marine Ecology Progress Series},
-\emph{650}, 309--326. \url{https://doi.org/10.3354/meps13399}
-
 \leavevmode\vadjust pre{\hypertarget{ref-Padovani2021}{}}%
@@
 Press}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Pastorino2019}{}}%
-Pastorino, G. (2019). A new deep water gastropod of the genus
-{Parabuccinum} ({Neogastropoda}: {Buccinulidae}) from southwestern
-{Atlantic} waters with new data on the distribution of all species.
-\emph{Marine Biodiversity}, \emph{49}(2), 913--922.
-\url{https://doi.org/10.1007/s12526-018-0876-7}
 
@@
 Reta, R. (2014). \emph{Oceanografía del {Banco Burdwood}: {Estado
-Actual} del {Conocimiento} y {Perspectivas}}. {INIDEP}.
+Actual} del {Conocimiento} y {Perspectivas}}. {Instituto Nacional de
+Investigación y Desarrollo Pesquero (INIDEP), Argentina}.
 
@@
 including multiplex networks}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Schejter2017}{}}%
-Schejter, L. (2017). \emph{{Informe de Campaña Banco Burdwood}} (p. 296)
-{[}\{Field campaign Report\}{]}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-MartinSirito2019}{}}%
-Sirito, M. (2019). \emph{Fauna asociada a corales ({Octocorallia}) e
-hidroides ({Hydrozoa}) del {Área Marina Protegida} {``{Namuncurá}''}
-({Banco Burdwood}) y zonas profundas adyacentes} {[}PhD thesis{]}.
-Universidad Nacional de Mar del Plata.
+\leavevmode\vadjust pre{\hypertarget{ref-Secretariatoftheconventiononbiologicaldiversity2004}{}}%
+Secretariat of the convention on biological diversity. (2004).
+\emph{Technical advice on the establishment and management of a national
+system of marine and coastal protected areas} (Technical Report No. 13).
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Strogatz2001}{}}%
-Strogatz, S. H. (2001). Exploring complex networks. \emph{Nature},
-\emph{410}(6825), 268--276. \url{https://doi.org/10.1038/35065725}
-
 \leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam2022}{}}%
@@
 \url{https://doi.org/10.1126/science.1188321}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Tilman1996}{}}%
-Tilman, D. (1996). Biodiversity: {Population Versus Ecosystem
-Stability}. \emph{Ecology}, \emph{77}(2), 350--363.
-\url{https://doi.org/10.2307/2265614}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Woodward2005}{}}%
-Woodward, G., Ebenman, B., Emmerson, M., Montoya, J. M., Olesen, J. M.,
-Valido, A., \& Warren, P. H. (2005). Body size in ecological networks.
-\emph{Trends in Ecology \& Evolution}, \emph{20}(7), 402--409.
-\url{https://doi.org/10.1016/j.tree.2005.04.005}
-
 \end{CSLReferences}

### 2023-05-17 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Minor changes

@@
 Notably, species of mid-TLs (3-4.2) showed the highest values of betweenness, meaning that those species participated in the highest number of shortest paths between species (Figure 4A).
-The following are the species with the highest values: *Patagonotothen ramsayi*, *Salilota australis*, *Dissostichus eleginoides* (fishes), *Doryteuthis gahi* (Cephalopoda), and *Patagonotothen guntheri* (Notothenioid fish) (Table S3).
+The following are the species with the highest values (descending order): *Patagonotothen ramsayi*, *Salilota australis*, *Dissostichus eleginoides* (fishes), *Doryteuthis gahi* (Cephalopoda), and *Patagonotothen guntheri* (Notothenioid fish) (Table S3).
 

### 2023-06-29 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Changes on Acanthoserolis & Aega sp

@@
   - name: Andrea Raya Rey^a^^,^^c^^,^^g^
+  - name: Laura Schejter^h^
   - name: Mariela L. Spinelli^d^^,^^e^
-  - name: Marcos Tatián^h^^,^^i^
-  - name: Diego Urteaga^j^
+  - name: Marcos Tatián^i^^,^^j^
+  - name: Diego Urteaga^k^
   - name: Luciana Riccialdelli^a^
@@
   - code: 8
+    address: Instituto Nacional de Investigacion y Desarrollo Pesquero (INIDEP), Consejo Nacional de Investigaciones Cientificas y Tecnicas (CONICET), Argentina
+  - code: 9
     address: Facultad de Ciencias Exactas, Fisicas y Naturales, Universidad Nacional de Cordoba (UNC), Argentina
-  - code: 9
+  - code: 10
     address: Instituto de Diversidad y Ecologia Animal (IDEA-CONICET)
-  - code: 10
+  - code: 11
     address: Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina
@@
 We applied a network approach to characterise the food web in terms of complexity and structure, and identifying the species' role in such a framework.
-In terms of complexity, the MPA N-BB food web consisted of 1780 predator-prey interactions and 375 species, with a link density of 4.75 and a connectance of 0.01.
+In terms of complexity, the MPA N-BB food web consisted of 1788 predator-prey interactions and 380 species, with a link density of 4.70 and a connectance of 0.01.
 In terms of structure, almost half of the consumers were omnivores (0.48), and the network displayed a small-world pattern.
@@
 
-In terms of complexity, the MPA Namuncurá - Burdwood Bank food web (N-BB I and II) consisted of 1780 predator-prey interactions and 375 species, where 93% of them were defined at the species taxonomical level (Figure 2, Table S2).
-The food web presented a link density (e.g., the average number of interactions per species) of 4.75, and a connectance of 0.01.
+In terms of complexity, the MPA Namuncurá - Burdwood Bank food web (N-BB I and II) consisted of 1788 predator-prey interactions and 380 species, where 93% of them were defined at the species taxonomical level (Figure 2, Table S2).
+The food web presented a link density (e.g., the average number of interactions per species) of 4.70, and a connectance of 0.01.
 Almost half of the consumers were omnivores (0.48), feeding on sources at different trophic levels.
@@
 
-load("../results/summary_results_may23.rda")
+load("../results/summary_results_jun23.rda")
 
@@
 Following the same distribution pattern, few prey presented multiple predators (Figure 3C).
-The top-five prey in number of predators were: Detritus (Non-living, 155 predators), the three categories of Diatoms considered (benthic, centric and pennate, 75 predators on average), and species of the genus *Euphausia* (Zooplankton, 47 predators).
+The top-five prey in number of predators were: Detritus (Non-living, 153 predators), the three categories of Diatoms considered (benthic, centric and pennate, 72.5 predators on average), and species of the genus *Euphausia* (Zooplankton, 46 predators).
 Finally, taking into account the interactions within each functional group, most interactions were concentrated in a few species (Figure 3D).
@@
 
-load("../data/foodweb-data_may23.rda")
-load("../results/summary_results_may23.rda")
+load("../data/foodweb-data_jun23.rda")
+load("../results/summary_results_jun23.rda")
 
@@
 
-Considering the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.7), as well as 'module hub' species (TL = 1 - 4); 'module connector' was constrained to mid-TLs (2 - 3.86); and 'network connector', the least frequent, had all of its species in low-TLs (1 - 2), except for one with TL = 3.48 (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework).
-Here it is important to highlight the two latter topological roles because they are responsible for linking modules and maintaining the connectivity of the food web: 41 species (4 network connectors + 37 module connectors) from 19 different functional groups with a TL range = 1 - 3.86.
-The following were the four species with a network connector role: detritus, benthic diatoms, Foraminifera and *Patagonotothen ramsayi*.
-The 37 species with a module connector role represented these functional groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Hydrozoa (as 'Cnidaria_benthic'), Copepoda, Cumacea, Decapoda, diatoms, Echinodermata, fish (bentho-pelagic and demersal Osteichthyes, and Chondrychthyes), Polychaeta, Porifera, Pycnogonida (as 'Benthos_Misc') and zooplankton (see Supplementary Material Table S3 for the identity of the species).
+Considering the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.78), as well as 'module hub' species (TL = 1 - 3.9); 'module connector' was constrained to mid-TLs (2 - 3.86); and 'network connector', was represented by only one trophic species: detritus (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework).
+Here it is important to highlight the two latter topological roles because they are responsible for linking modules and maintaining the connectivity of the food web: 42 species (1 network connector + 41 module connectors) from 19 different functional groups with a TL range = 1 - 3.86.
+The 41 species with a module connector role represented these functional groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Hydrozoa (as 'Cnidaria_benthic'), Copepoda, Cumacea, Decapoda, Echinodermata, fish (bentho-pelagic and demersal Osteichthyes, and Chondrychthyes), Foraminifera, Polychaeta, Porifera, Pycnogonida (as 'Benthos_Misc') and zooplankton (see Supplementary Material Table S3 for the identity of the species).
 
@@
 Each point represents a species.
-Linear regressions for betweenness ($y = 74.96x - 121.71, R^2 = 0.05, p-value < 0.01$), closeness ($y = 1.01e-05x - 9.48e-4, R^2 = 0.003, p-value = 0.14$) and trophic similarity ($y = -0.02x + 0.11 , R^2 = 0.08, p-value < 0.01$).
+Linear regressions for betweenness ($y = 74.82x - 116.82, R^2 = 0.05, p-value < 0.01$), closeness ($y = 1.04e-05x - 9.25e-4, R^2 = 0.004, p-value = 0.11$) and trophic similarity ($y = -0.02x + 0.1 , R^2 = 0.07, p-value < 0.01$).
 Note that for panels A, B and C only species with TLs equal or greater than 2 were considered."}
@@
 Among the varying numbers of topological roles in which species can be divided, two are remarkable: 'module connector' and 'network connector'.
-Here again, the longtail southern cod *Patagonotothen ramsayi* is emphasized as an influential species for the connectivity of the food web, which agrees with the suggested 'wasp-waist' control for the MPA N-BB ecosystem [@Riccialdelli2020].
-But most importantly, our results broaden this issue by pointing out that there are other species, belonging to a wide range of trophic positions (1 to 3.86) and representing 20 different functional groups, that should be considered.
+Here, our results point out that there are several species, belonging to a wide range of trophic positions (1 to 3.86) and representing 17 different functional groups, that should be considered as influential species for the connectivity of the food web.
 Thus, we propose that the diversity of species (benthic and pelagic) maintains the connectivity of the food web, therefore contributing to the trophic structure and ecosystem's stability.

### 2023-06-29 MS_ToSubmit/MS_Burdwood_foodweb.tex
Changes on Acanthoserolis & Aega sp

@@
 
-\usepackage{lineno} % add
-  \linenumbers % turns line numbering on
-
 \usepackage{graphicx}
@@
 \usepackage{amssymb,amsmath}
+% TODO: Currently lineno needs to be loaded after amsmath because of conflict
+% https://github.com/latex-lineno/lineno/issues/5
+\usepackage{lineno} % add
+  \linenumbers % turns line numbering on
 \usepackage{ifxetex,ifluatex}
@@
 
+    \author[]{Laura Schejter\textsuperscript{h}%
+  %
+  }
+
     \author[]{Mariela L. Spinelli\textsuperscript{d,e}%
@@
 
-    \author[]{Marcos Tatián\textsuperscript{h,i}%
+    \author[]{Marcos Tatián\textsuperscript{i,j}%
   %
@@
 
-    \author[]{Diego Urteaga\textsuperscript{j}%
+    \author[]{Diego Urteaga\textsuperscript{k}%
   %
@@
     \affiliation[7]{Wildlife Conservation Society, Argentina}
-    \affiliation[8]{Facultad de Ciencias Exactas, Fisicas y Naturales,
+    \affiliation[8]{Instituto Nacional de Investigacion y Desarrollo
+Pesquero (INIDEP), Consejo Nacional de Investigaciones Cientificas y
+Tecnicas (CONICET), Argentina}
+    \affiliation[9]{Facultad de Ciencias Exactas, Fisicas y Naturales,
 Universidad Nacional de Cordoba (UNC), Argentina}
-    \affiliation[9]{Instituto de Diversidad y Ecologia Animal
+    \affiliation[10]{Instituto de Diversidad y Ecologia Animal
 (IDEA-CONICET)}
-    \affiliation[10]{Museo Argentino de Ciencias Naturales ``Bernardino
+    \affiliation[11]{Museo Argentino de Ciencias Naturales ``Bernardino
 Rivadavia'', Argentina}
@@
   and structure, and identifying the species' role in such a framework.
-  In terms of complexity, the MPA N-BB food web consisted of 1780
-  predator-prey interactions and 375 species, with a link density of
-  4.75 and a connectance of 0.01. In terms of structure, almost half of
+  In terms of complexity, the MPA N-BB food web consisted of 1788
+  predator-prey interactions and 380 species, with a link density of
+  4.70 and a connectance of 0.01. In terms of structure, almost half of
   the consumers were omnivores (0.48), and the network displayed a
@@
 complexity and structure.}\tabularnewline
-\toprule()
+\toprule\noalign{}
 \begin{minipage}[b]{\linewidth}\raggedright
@@
 \end{minipage} \\
-\midrule()
+\midrule\noalign{}
 \endfirsthead
-\toprule()
+\toprule\noalign{}
 \begin{minipage}[b]{\linewidth}\raggedright
@@
 \end{minipage} \\
-\midrule()
+\midrule\noalign{}
 \endhead
+\bottomrule\noalign{}
+\endlastfoot
 \textbf{Number of species} & Number of trophic species in a food web. &
@@
 connectivity of the food web. & Guimera \& Nunes Amaral 2005 \\
-\bottomrule()
 \end{longtable}
@@
 In terms of complexity, the MPA Namuncurá - Burdwood Bank food web (N-BB
-I and II) consisted of 1780 predator-prey interactions and 375 species,
+I and II) consisted of 1788 predator-prey interactions and 380 species,
 where 93\% of them were defined at the species taxonomical level (Figure
 2, Table S2). The food web presented a link density (e.g., the average
-number of interactions per species) of 4.75, and a connectance of 0.01.
+number of interactions per species) of 4.70, and a connectance of 0.01.
 Almost half of the consumers were omnivores (0.48), feeding on sources
@@
 \hline
-375 & 1780 & 4.75 & 0.01 & 0.48 & 2.96 & 0.08 & True\\
+380 & 1788 & 4.71 & 0.01 & 0.48 & 2.99 & 0.08 & True\\
 \hline
@@
 pattern, few prey presented multiple predators (Figure 3C). The top-five
-prey in number of predators were: Detritus (Non-living, 155 predators),
+prey in number of predators were: Detritus (Non-living, 153 predators),
 the three categories of Diatoms considered (benthic, centric and
-pennate, 75 predators on average), and species of the genus
-\emph{Euphausia} (Zooplankton, 47 predators). Finally, taking into
+pennate, 72.5 predators on average), and species of the genus
+\emph{Euphausia} (Zooplankton, 46 predators). Finally, taking into
 account the interactions within each functional group, most interactions
@@
 number of shortest paths between species (Figure 4A). The following are
-the species with the highest values: \emph{Patagonotothen ramsayi},
-\emph{Salilota australis}, \emph{Dissostichus eleginoides} (fishes),
-\emph{Doryteuthis gahi} (Cephalopoda), and \emph{Patagonotothen
-guntheri} (Notothenioid fish) (Table S3).
+the species with the highest values (descending order):
+\emph{Patagonotothen ramsayi}, \emph{Salilota australis},
+\emph{Dissostichus eleginoides} (fishes), \emph{Doryteuthis gahi}
+(Cephalopoda), and \emph{Patagonotothen guntheri} (Notothenioid fish)
+(Table S3).
 
 Considering the topological role, `module specialist' species were the
-most frequent and presented a wide TL range (1 - 4.7), as well as
-`module hub' species (TL = 1 - 4); `module connector' was constrained to
-mid-TLs (2 - 3.86); and `network connector', the least frequent, had all
-of its species in low-TLs (1 - 2), except for one with TL = 3.48 (Figure
-4D, see Figure S2 for species' topological roles in a food web graph
-framework). Here it is important to highlight the two latter topological
-roles because they are responsible for linking modules and maintaining
-the connectivity of the food web: 41 species (4 network connectors + 37
-module connectors) from 19 different functional groups with a TL range =
-1 - 3.86. The following were the four species with a network connector
-role: detritus, benthic diatoms, Foraminifera and \emph{Patagonotothen
-ramsayi}. The 37 species with a module connector role represented these
-functional groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Hydrozoa
-(as `Cnidaria\_benthic'), Copepoda, Cumacea, Decapoda, diatoms,
-Echinodermata, fish (bentho-pelagic and demersal Osteichthyes, and
-Chondrychthyes), Polychaeta, Porifera, Pycnogonida (as `Benthos\_Misc')
-and zooplankton (see Supplementary Material Table S3 for the identity of
-the species).
+most frequent and presented a wide TL range (1 - 4.78), as well as
+`module hub' species (TL = 1 - 3.9); `module connector' was constrained
+to mid-TLs (2 - 3.86); and `network connector', was represented by only
+one trophic species: detritus (Figure 4D, see Figure S2 for species'
+topological roles in a food web graph framework). Here it is important
+to highlight the two latter topological roles because they are
+responsible for linking modules and maintaining the connectivity of the
+food web: 42 species (1 network connector + 41 module connectors) from
+19 different functional groups with a TL range = 1 - 3.86. The 41
+species with a module connector role represented these functional
+groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Hydrozoa (as
+`Cnidaria\_benthic'), Copepoda, Cumacea, Decapoda, Echinodermata, fish
+(bentho-pelagic and demersal Osteichthyes, and Chondrychthyes),
+Foraminifera, Polychaeta, Porifera, Pycnogonida (as `Benthos\_Misc') and
+zooplankton (see Supplementary Material Table S3 for the identity of the
+species).
 
@@
 Each point represents a species.
-Linear regressions for betweenness ($y = 74.96x - 121.71, R^2 = 0.05, p-value < 0.01$), closeness ($y = 1.01e-05x - 9.48e-4, R^2 = 0.003, p-value = 0.14$) and trophic similarity ($y = -0.02x + 0.11 , R^2 = 0.08, p-value < 0.01$).
+Linear regressions for betweenness ($y = 74.82x - 116.82, R^2 = 0.05, p-value < 0.01$), closeness ($y = 1.04e-05x - 9.25e-4, R^2 = 0.004, p-value = 0.11$) and trophic similarity ($y = -0.02x + 0.1 , R^2 = 0.07, p-value < 0.01$).
 Note that for panels A, B and C only species with TLs equal or greater than 2 were considered.}\label{fig:figure4}
@@
 and predicts reasonably well key dynamical properties of ecological
-networks (Dunne et al., 2002a). Complex marine food webs (i.e.~with more
+networks (Dunne et al., 2002c). Complex marine food webs (i.e.~with more
 than 25 trophic species) show connectance values ranging from 0.01 -
@@
 (Smith-Ramesh et al., 2017) as well as species removal (e.g., local
-extinction) (Dunne et al., 2002b; Montoya \& Solé, 2003). The
+extinction) (Dunne et al., 2002a; Montoya \& Solé, 2003). The
 connectance of the food web of the MPA Namuncurá - Burdwood Bank (0.01)
@@
 feature in empirical complex food webs in particular (Dunne et al.,
-2002a; Montoya \& Solé, 2003; Stouffer et al., 2005), and has received
+2002c; Montoya \& Solé, 2003; Stouffer et al., 2005), and has received
 great attention in complex networks in general (Albert \& Barabási,
@@
 secondary extinctions and a catastrophic fragmentation of the network
-(Albert et al., 2000; Dunne et al., 2002b; Eklöf \& Ebenman, 2006).
+(Albert et al., 2000; Dunne et al., 2002a; Eklöf \& Ebenman, 2006).
 
@@
 marine food webs, mainly due to a low clustering coefficient compared to
-random networks (Dunne et al., 2002c; Marina, Saravia, et al., 2018).
+random networks (Dunne et al., 2002b; Marina, Saravia, et al., 2018).
 However, the food web of the MPA N-BB does display a small-world
@@
 The degree distribution allows identifying important species, such as
-potential keystone species (Dunne et al., 2002b; Solé \& Montoya, 2001),
+potential keystone species (Dunne et al., 2002a; Solé \& Montoya, 2001),
 generalist/specialist species, and dominant food sources (Kondoh et al.,
@@
 varying numbers of topological roles in which species can be divided,
-two are remarkable: `module connector' and `network connector'. Here
-again, the longtail southern cod \emph{Patagonotothen ramsayi} is
-emphasized as an influential species for the connectivity of the food
-web, which agrees with the suggested `wasp-waist' control for the MPA
-N-BB ecosystem (Riccialdelli et al., 2020). But most importantly, our
-results broaden this issue by pointing out that there are other species,
-belonging to a wide range of trophic positions (1 to 3.86) and
-representing 20 different functional groups, that should be considered.
-Thus, we propose that the diversity of species (benthic and pelagic)
-maintains the connectivity of the food web, therefore contributing to
-the trophic structure and ecosystem's stability.
+two are remarkable: `module connector' and `network connector'. Here,
+our results point out that there are several species, belonging to a
+wide range of trophic positions (1 to 3.86) and representing 17
+different functional groups, that should be considered as influential
+species for the connectivity of the food web. Thus, we propose that the
+diversity of species (benthic and pelagic) maintains the connectivity of
+the food web, therefore contributing to the trophic structure and
+ecosystem's stability.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002}{}}%
+Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002a). Network
+structure and biodiversity loss in food webs: Robustness increases with
+connectance. \emph{Ecology Letters}, \emph{5}(4), 558--567.
+\url{https://doi.org/10.1046/j.1461-0248.2002.00354.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002b}{}}%
+Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002b). \emph{Small
+{Networks} but not {Small Worlds}: {Unique Aspects} of {Food Web
+Structure}}. {Santa Fe Institute}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Dunne2002a}{}}%
-Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002a). Food-web
+Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002c). Food-web
 structure and network theory: {The} role of connectance and size.
@@
 12917--12922. \url{https://doi.org/10.1073/pnas.192407699}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002}{}}%
-Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002b). Network
-structure and biodiversity loss in food webs: Robustness increases with
-connectance. \emph{Ecology Letters}, \emph{5}(4), 558--567.
-\url{https://doi.org/10.1046/j.1461-0248.2002.00354.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002b}{}}%
-Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002c). \emph{Small
-{Networks} but not {Small Worlds}: {Unique Aspects} of {Food Web
-Structure}}. {Santa Fe Institute}.
 

### 2023-06-29 MS_ToSubmit/SupMaterial.Rmd
Changes on Acanthoserolis & Aega sp

@@
   - Andrea Raya Rey
+  - Laura Schejter
   - Mariela L. Spinelli
@@
 # Load data
-load("../data/cleaned-data_may23.rda")
+load("../data/cleaned-data_jun23.rda")
 
@@
 # Load data
-load("../data/cleaned-data_may23.rda")
-load("../data/foodweb-data_may23.rda")
+load("../data/cleaned-data_jun23.rda")
+load("../data/foodweb-data_jun23.rda")
 
@@
 Species, represented by circles, are coloured by role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green).
-Network connector = 4 species; module connector = 37 species; module hub = 8 species; and module specialist = 326 species.
+Network connector = 1 species; module connector = 41 species; module hub = 10 species; and module specialist = 328 species.
 
@@
 # Load data
-load("../results/summary_results_may23.rda")
+load("../results/summary_results_jun23.rda")
 

### 2023-06-29 R/1_datawrangling.R

@@ -26,7 +26,7 @@ sp_raw <- sp_raw %>%
 
 ## Lista de Interacciones ----
 
-int_raw <- read.csv("data/ListaInteracciones_AMPNBB_may23.csv")
+int_raw <- read.csv("data/ListaInteracciones_AMPNBB_jun23.csv")
 
 int_raw <- int_raw %>% 
   # low-resolved Phytoplankton
@@ -145,4 +145,4 @@ int_raw <- subset(int_raw, !(Prey %in% "Demospongiae *"))  # exclude rows with P
 ## Save data ----
 
 save(sp_raw, int_raw,
-     file = "data/cleaned-data_may23.rda")
+     file = "data/cleaned-data_jun23.rda")

### 2023-06-29 R/2_dataexploring.R

@@ -17,7 +17,7 @@ ipak(packages)
 
 # Cargar datos ----
 
-load("data/cleaned-data_apr23.rda")
+load("data/cleaned-data_jun23.rda")
 
 
 # Lista de Especies ----

### 2023-06-29 R/3_foodwebexploring.R

@@ -17,7 +17,7 @@ ipak(packages)
 
 # Cargar datos ----
 
-load("data/cleaned-data_may23.rda")
+load("data/cleaned-data_jun23.rda")
 
 
 # Red trófica ----
@@ -114,4 +114,4 @@ plotTrophLevel(g, ylab = "Trophic level")
 # Save data ----
 
 save(g, int_need_res, int_good_res,
-     file = "data/foodweb-data_may23.rda")
+     file = "data/foodweb-data_jun23.rda")

### 2023-06-29 R/4_foodwebanalysis.R

@@ -18,8 +18,8 @@ ipak(packages)
 
 # Cargar datos ----
 
-load("data/cleaned-data_may23.rda")
-load("data/foodweb-data_may23.rda")
+load("data/cleaned-data_jun23.rda")
+load("data/foodweb-data_jun23.rda")
 
 
 # Análisis ----
@@ -171,7 +171,7 @@ spp_total <- spp_total %>%
                              FunctionalGroup %in% c("Fish_Demersal") ~ "Demersal"))
 
 
-write_csv(spp_total, file = "results/spp_prop_may23.csv")
+write_csv(spp_total, file = "results/spp_prop_jun23.csv")
 
 
 # Resolución de la red ----
@@ -194,4 +194,4 @@ int_grp <- spp_total %>%
 # Guardar datos ----
 
 save(g_up, g, deg_dist_fit, prop_topol, spp_total, top.role, top.role.df,
-     file = "results/summary_results_may23.rda")
+     file = "results/summary_results_jun23.rda")

### 2023-06-29 R/5_regressionanalyses.R

@@ -16,7 +16,7 @@ ipak(packages)
 
 
 # Datos ----
-load("results/summary_results_may23.rda")
+load("results/summary_results_jun23.rda")
 
 
 # Linear Regression ----

### 2023-06-29 R/6_figures.R

@@ -18,7 +18,7 @@ ipak(packages)
 
 # Cargar datos ----
 
-load("results/summary_results_jan23.rda")
+load("results/summary_results_jun23.rda")
 
 
 # Figuras ----
@@ -79,7 +79,7 @@ gen_vul_plot
 
 # Distribución interacciones por GF
 
-load("data/foodweb-data_jan23.rda")
+load("data/foodweb-data_jun23.rda")
 
 # Definir colores para cada GF
 un.prey <- as.data.frame(unique(int_good_res$PreyGroup))  # prey groups

### 2023-07-04 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Schloss & Riccialdelli sug.

@@
 In terms of structure, almost half of the consumers were omnivores (0.48), and the network displayed a small-world pattern.
-These findings suggest that the ecosystem might be vulnerable to external perturbations targeting highly connected species, although structural properties might provide resilience and resistance, resulting in a rearranged structure that preserves its original functions.
+These findings suggest that the ecosystem might be vulnerable to external perturbations targeting highly connected species, although other properties might provide resilience and resistance, resulting in a rearranged structure that preserves its original functions.
 Furthermore, we identified several species as important in terms of different aspects of trophic structure and functioning, and response to perturbations.
@@
 Interestingly, the case of the MPAs Namuncurá - Burdwood Bank I and II (MPA N-BB, 53º–55ºS 56º–62ºW), which is the focus of this work, is unique since these MPAs are associated to a submarine plateau and its southern adjacent deep slope region, respectively [@Falabella2017].
-In addition, such MPAs are part of a network of protected areas in the sub-Antarctic area (jointly with MPA Yaganes) that aims to protect and strengthen the functioning of this southern region to maintain global ocean health.
+In addition, such MPAs are part of a network of protected areas in the sub-Antarctic area (jointly with MPA Yaganes) that aims to protect this southern region in order to contribute to global ocean health.
 
 Many of these MPAs focus on the presence of particularly vulnerable, keystone, or charismatic species, large numbers (or proportions) of endemic species, and/or high biodiversity across taxonomic levels [@Hogg2016].
-Indeed, the MPA N-BB was created to protect a sensitive and biodiverse benthic habitat that was barely known [@Schejter2016; @Falabella2017].
-The benthic community is featured by high biomass of vulnerable and fragile species (mainly Porifera and Cnidaria) that meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResourcesCCAMLR2009].
-Also, it provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge and nursery area [@GarciaAlonso2018; @Vazquez2018; @Delpiani2020; @Troccoli2020; @CovattiAle2022; @Fischer2022; @Florencia2023].
+Indeed, the MPA N-BB was created to protect a potentially sensitive and biodiverse benthic habitat that was only barely known [@Schejter2016; @Falabella2017].
+The benthic community is featured by high biomass of vulnerable and fragile species (mainly Porifera, Bryozoa and Cnidaria) that considered with their environment meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResourcesCCAMLR2009].
+Also, the benthic realm provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge and nursery area [@GarciaAlonso2018; @Vazquez2018; @Delpiani2020; @Troccoli2020; @CovattiAle2022; @Fischer2022; @Matusevich2022; @Florencia2023].
 The maintenance of this singular community is related to local and regional oceanographic processes, including the circulation of the rich Malvinas (Falkland) current in the area [@Piola1989; @Guerrero1999] and the upwelling and mixing phenomena [@Matano2019].
 The input of nutrients from the Malvinas (Falkland) current also supports a diverse plankton community [@Guinder2020].
+
 Overall, 811 benthic and plankton species have been identified for the MPA N-BB ecosystem, where 349 were reported for the first time in the area in recent years [@AdministraciondeParquesNacionales2022].
-However, identifying the main species involved in the maintenance of ecosystem services and health as well as for management and conservation is essential.
-
+Identifying the main species involved in the maintenance of ecosystem services and health as well as for management and conservation is essential.
 Recently, the structure of the southwestern South Atlantic Ocean has been proposed to be under a 'wasp-waist' control, meaning that the structure and dynamics of the ecosystem are regulated primarily by mid-trophic level species (e.g., fishes, crustaceans) [@Padovani2012; @Saporiti2015; @Riccialdelli2020].
-In particular, the ecosystem of the MPA N-BB shows a more pronounced 'wasp-waist' structure, meaning a shorter food-chain length and a greater trophic overlap and redundancy, than other sub-Antarctic areas, such as the continental shelf off Tierra del Fuego.
+In particular, the ecosystem of the MPA N-BB shows a more pronounced 'wasp-waist' structure, meaning a shorter food chain and a greater trophic overlap and redundancy, than other sub-Antarctic areas, such as the continental shelf off Tierra del Fuego.
 The Fuegian sprat *Sprattus fuegensis* and longtail southern cod *Patagonotothen ramsayi* are considered the most plausible 'wasp-waist' species [@Riccialdelli2020].
 
-High-latitude marine ecosystems, such as the MPA N-BB, are considered complex systems in terms of biodiversity and ecological interactions [@Day2013; @Kortsch2019; @Cordone2020; @Trathan2021].
+High-latitude marine ecosystems, such as the MPA N-BB, are complex systems in terms of biodiversity and ecological interactions [@Day2013; @Kortsch2019; @Cordone2020; @Trathan2021].
 Although there is a robust knowledge about the complexity considering the richness of the benthic and plankton communities in the MPA N-BB ecosystem [@Schejter2016; @Guinder2020; @Schejter2020; @AdministraciondeParquesNacionales2022], a better understanding of species interactions' complexity and structure is needed.
@@
 For this, we applied a network approach to a highly resolved food web.
-The objective was twofold: characterise the food web in terms of complexity and structure, and identify the species' role in such a network framework.
+The objective was twofold: characterise the food web in terms of complexity and structure, and identify the species' role in the network.
 
@@
 The N-BB II includes such a deep slope, protecting about 32,000 km^2^.
-Intense upwelling and mixing occur over it, entraining deep nutrient-rich waters into the photic layer [@Piola2009; @Matano2019] and resulting in a fairly homogeneous water column both spatially and temporally [@Glorioso1995; @Guerrero1999; @Matano2019].
+Intense upwelling and mixing occur in relation with the slope, entraining deep nutrient-rich waters into the photic layer [@Piola2009; @Matano2019] and resulting in a fairly homogeneous water column both spatially and temporally [@Glorioso1995; @Guerrero1999; @Matano2019].
 
@@
 
-In order to build the network of predator-prey interactions, we reviewed more than 150 references considering published articles, Ph.D.
+In order to build the network of predator-prey interactions, we reviewed more than 170 references considering published articles, Ph.D.
 theses, public databases, and reports belonging to 16 research cruises conducted in the MPAs N-BB I and II during 2014-2019.
@@
 
-Due to a lack of trophic data resolution for some species inhabiting the study area, we followed the concept of trophic species, here defined as aggregated groups of taxa.
-In most cases, we followed it when specific data on species, in the taxonomic sense, were not available.
+Due to a lack of trophic data resolution for some species inhabiting the study area, we followed the concept of trophic species, here defined as follows: taxa collapsed into a single node in the network.
+In most cases, we followed this concept when specific data on species, in the taxonomic sense, were not available.
 In some cases, we collapsed species when taxa shared the same set of predators and prey (trophic similarity, @Martinez1991), one of the aggregation methods that better preserve food web functional properties [@Gauzens2013].
@@
 Details about this can be found in Supplementary Material (Table S2).
+Furthermore, we considered non-living food sources, such as detritus and necromass, as prey species in the food web context.
 
@@
 The species-level analysis aims to describe the species' role in the food web.
-For this, we considered the following properties: (1) betweenness Btw; (2) closeness Cl; (3) trophic similarity TS; (4) topological role TR; and (5) trophic level TL (Table 1).
+For this, we considered the following properties: betweenness Btw, closeness Cl, trophic similarity TS, topological role TR, and trophic level TL (Table 1).
 Topological roles refer to the fact that food webs tend to naturally organize in non-random, modular patterns, where modules are defined as a group of species that interact more frequently among themselves than with species that are not members of the module [@Guimera2005].
@@
 
-In terms of complexity, the MPA Namuncurá - Burdwood Bank food web (N-BB I and II) consisted of 1788 predator-prey interactions and 380 species, where 93% of them were defined at the species taxonomical level (Figure 2, Table S2).
+In terms of complexity, the MPA Namuncurá - Burdwood Bank food web consisted of 1788 predator-prey interactions and 380 species, where 93% of them were defined at the species taxonomical level (Figure 2, Table S2).
 The food web presented a link density (e.g., the average number of interactions per species) of 4.70, and a connectance of 0.01.
@@
 Following the same distribution pattern, few prey presented multiple predators (Figure 3C).
-The top-five prey in number of predators were: Detritus (Non-living, 153 predators), the three categories of Diatoms considered (benthic, centric and pennate, 72.5 predators on average), and species of the genus *Euphausia* (Zooplankton, 46 predators).
+The top-five prey (or food sources) in number of predators were: Detritus (Non-living, 153 predators), the three categories of Diatoms considered (benthic, centric and pennate, 72.5 predators on average), and species of the genus *Euphausia* (Zooplankton, 46 predators).
 Finally, taking into account the interactions within each functional group, most interactions were concentrated in a few species (Figure 3D).
-The most evident species were: *Doryteuthis gahi* (Cephalopoda), *Grimothea gregaria* (Decapoda), *Patagonotothen ramsayi*, *Patagonotothen guntheri* and *Dissostichus eleginoides* (bentho-pelagic fish), *Sprattus fuegensis* and *Micromesistius australis* (pelagic fish), and species of *Euphausia* and *Themisto gaudichaudii* (Zooplankton).
+The most evident species were: *Doryteuthis gahi* (Cephalopoda), *Grimothea (=Munida) gregaria* (Decapoda), *Patagonotothen ramsayi*, *Patagonotothen guntheri* and *Dissostichus eleginoides* (bentho-pelagic fish), *Sprattus fuegensis* and *Micromesistius australis* (pelagic fish), and species of *Euphausia* and *Themisto gaudichaudii* (Zooplankton).
 Overall, there is an evident asymmetry in the distribution of interactions among species at different levels in the MPA N-BB food web.
@@
 
-The food web of the MPA N-BB ecosystem analysed in this study is one of the most highly-resolved networks of trophic interactions ever studied, not only for a high-latitude marine ecosystem but also for any marine protected area worldwide to our knowledge.
-It is of paramount importance to consider the complexity of species interactions in order to gain insights into the structure and functioning of the ecosystem, since the aggregation of species might mask food web properties and produce type II errors (false positive) [@Martinez1993; @Gauzens2013].
+The food web of the MPA N-BB ecosystem analysed in this study is one of the most highly-resolved networks of trophic interactions ever studied, not only for a high-latitude open-ocean ecosystem but also for any marine protected area worldwide to our knowledge.
+It is of paramount importance to consider the complexity of species interactions in order to gain insights into the structure and functioning of the ecosystem, since the aggregation of species might mask food web properties and produce type II errors (false positives) [@Martinez1993; @Gauzens2013].
 
@@
 In this sense, empirical analyses support the notion that highly-connected ecological networks are robust against external perturbations such as the introduction of new (e.g., invasive) species [@Smith-Ramesh2017] as well as species removal (e.g., local extinction) [@Dunne2002; @Montoya2003].
-The connectance of the food web of the MPA Namuncurá - Burdwood Bank (0.01) is one of the lowest reported so far for these regions; in particular, it appears to much lower than that of Beagle Channel (0.05), an adjacent coastal area [@Rodriguez2022].
+The connectance of the food web of the MPA Namuncurá - Burdwood Bank (0.01) is one of the lowest reported so far for these regions; in particular, it appears to be much lower than that of Beagle Channel (0.05), an adjacent coastal area [@Rodriguez2022].
 
@@
 However, the food web of the MPA N-BB does display a small-world pattern.
-Consequences of this could be of great importance in recognizing evolutionary paths and the vulnerability to perturbations [@Montoya2002].
+Consequences of this could be of great importance in recognizing species evolutionary paths and the vulnerability to perturbations [@Montoya2002].
 On the one hand, a short path length implies a rapid spread of an impact (e.g., contaminant, population fluctuation, local extinction) throughout the network but, at the same time, more potentially adaptive dynamics in the face of external perturbations [@Montoya2002; @Williams2002].
@@
 In summary, the food web of the MPA N-BB presents a combination of network properties that makes it unique in terms of network resolution, complexity, and structural pattern.
-All this suggests that the ecosystem might be fragile to external perturbations targeting highly connected species, which in turn coincides to be commercial exploited species as fishes [@Martinez2015].
+All this suggests that the food web might be fragile to external perturbations targeting highly connected species, which in turn coincides to be commercial exploited species as fishes [@Laptikhovsky2013; @Martinez2015; @Winter2023].
 However, structural properties might provide resilience and resistance with the final outcome of a rearranged structure maintaining its functions.
@@
 
-The degree distribution allows identifying important species, such as potential keystone species [@Sole2001; @Dunne2002], generalist/specialist species, and dominant food sources [@Kondoh2010].
+The degree distribution allows identifying important species, such as potential keystone species (i.e.
+highly connected) [@Sole2001; @Dunne2002], generalist/specialist species, and dominant food sources [@Kondoh2010].
 
-We have identified that most of the consumers in the food web of the MPA N-BB either have a narrow diet or are specialists, while few present a broad diet.
+We have identified that most of the consumers in the food web of the MPA N-BB either have a narrow diet or are specialists, while few present a broad or generalist diet.
 The most evident generalist species are *Patagonotothen guntheri* [@CovattiAle2022], *P.
@@
 On the other hand, a low number of prey are consumed by many predators in the food web of the MPA N-BB.
-This suggests that there are dominant food sources from which most consumers depend on and from where the ecosystem energy is being transferred to the upper trophic levels.
+This suggests that there are dominant food sources on which most consumers depend and from where the ecosystem energy is being transferred to the upper trophic levels.
 The most demanded source we identified in this study (i.e.
@@
 In the food web of the MPA N-BB, low-TL consumers arise as important in this regard: species of the zooplankton community, *Calanus* and *Euphausia*, and Brachiopoda.
-Any perturbation affecting these species, such as the recently confirmed contaminants mercury [@Fioramonti2022] and microplastics [@Cossi2021; @DiMauro2022] for the area, should be of concern since it might reach many other species in the food web.
+Any perturbation affecting these species, such as the recently confirmed contaminants mercury [@Fioramonti2022] and microplastics [@Cossi2021; @DiMauro2022], should be of concern since it might reach many other species in the food web.
 Otherwise, betweenness measures the number of shortest paths between species, providing information on the importance of species as “bridges” for energy transfer: a species with high betweenness takes part in more food chains and therefore affects more energy flows [@Scotti2010].
@@
 
-We compiled information on the species and trophic diversity of the Marine Protected Area Namuncurá - Burdwood Bank, generating an unprecedented, well-resolved network of trophic interactions for a sub-Antarctic ecosystem, identifying the complexity and structure of the system, and the main species role in a network framework.
+We compiled information on the species and trophic diversity of the oceanic Marine Protected Area Namuncurá - Burdwood Bank, generating an unprecedented, well-resolved network of trophic interactions for a sub-Antarctic ecosystem, identifying the complexity and structure of the system, and the main species role in a network framework.
 Particular properties at the network level allowed us to identify the ecosystem's vulnerability and potential response to perturbations in the presence of highly-connected species, with a rearranged structure maintaining their functions due to its potential resilience and resistance.
@@
 We are indebted to all those experts of the working group 'Banco Burdwood' who humbly provided their knowledge to enhance the quality of the present research.
-It is worth to mention the following researchers: Brenda L.
+Although most of them are authors of the present work, it is worth to mention the following researchers: Brenda L.
 Doti (IBBEA, CONICET-UBA; Universidad de Buenos Aires, Argentina), Sofía L.
@@
 Martinez (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina) and Luciano Padovani (Instituto Nacional de Investigación y Desarrollo Pesquero, INIDEP, Argentina).
+We thank the MPA Namuncurá − Burdwood Bank administration.
 Research cruises were funded by national funds by the Law 26.875.

### 2023-07-11 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Schejter suggs.

@@
 The majority of these Marine Protected Areas (MPAs) focus on the presence of particularly vulnerable, keystone, or charismatic species, large numbers of endemic species, and/or high biodiversity across taxonomic levels.
-In the sub-Antarctic region, the level of ocean protection is mainly associated to oceanic islands, except for the MPAs Namuncurá - Burdwood Bank I and II (MPA N-BB, 53º–55ºS and 56º–62ºW, respectively), which are associated to a submarine plateau and its southern adjacent deep slope region, respectively.
+In the sub-Antarctic region, the level of ocean protection is mainly associated to oceanic islands, except for the MPAs Namuncurá - Burdwood Bank I and II (MPA N-BB, ~53º–55ºS and ~56º–62ºW), which are associated to a submarine plateau and its southern adjacent deep slope region, respectively.
 Here, we present the first detailed analysis of the network of predator-prey interactions (food web) for the MPA N-BB ecosystem.
@@
 
-In the sub-Antarctic region, the level of ocean protection is mainly associated to oceanic islands, such as the South Georgia and South Sandwich, Bouvet, Prince Edward, and Macquarie islands [@IUCN2023].
-Interestingly, the case of the MPAs Namuncurá - Burdwood Bank I and II (MPA N-BB, 53º–55ºS 56º–62ºW), which is the focus of this work, is unique since these MPAs are associated to a submarine plateau and its southern adjacent deep slope region, respectively [@Falabella2017].
+In the sub-Antarctic region, the level of ocean protection is mainly associated to oceanic islands, such as the South Georgias and South Sandwich, Bouvet, Prince Edward, and Macquarie islands [@IUCN2023].
+Interestingly, the case of the MPAs Namuncurá - Burdwood Bank I and II (MPA N-BB, ~53º–55ºS ~56º–62ºW), which is the focus of this work, is unique since these MPAs are associated to a submarine plateau and its southern adjacent deep slope region, respectively [@Falabella2017; @Schejter2020].
 In addition, such MPAs are part of a network of protected areas in the sub-Antarctic area (jointly with MPA Yaganes) that aims to protect this southern region in order to contribute to global ocean health.
@@
 Indeed, the MPA N-BB was created to protect a potentially sensitive and biodiverse benthic habitat that was only barely known [@Schejter2016; @Falabella2017].
-The benthic community is featured by high biomass of vulnerable and fragile species (mainly Porifera, Bryozoa and Cnidaria) that considered with their environment meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResourcesCCAMLR2009].
+The benthic community is featured by high biomass of vulnerable and fragile species (mainly Porifera, Bryozoa and Cnidaria) that considered with their environment meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present densities of Indicator Taxa of > 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResourcesCCAMLR2009].
 Also, the benthic realm provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge and nursery area [@GarciaAlonso2018; @Vazquez2018; @Delpiani2020; @Troccoli2020; @CovattiAle2022; @Fischer2022; @Matusevich2022; @Florencia2023].
@@
 They are located 150 km east of Isla de los Estados and 200 km south of Malvinas/Falkland Islands.
-The MPA N-BB I comprises nearly 34,000 km^2^ circumscribed by the 200 m isobath, between 54º–55ºS and 56º–62ºW, with a slight slope extended nearly 370 km east–west.
+The MPA N-BB I comprises nearly 28,900 km^2^ circumscribed by the 200 m isobath, between ~54º–55ºS and ~56º–62ºW, with a slight slope extended nearly 370 km east–west.
 Physical features in the BB are fairly stable, with salinity averaging 34 all year round and temperature ranging between 4 and 8ºC [@Guerrero1999; @Acha2004; @Piola2009].
 The BB is surrounded by steep flanks of up to 4000 m depth through which strong currents circulate [@Piola1989; @Reta2014; @Matano2019].
-The N-BB II includes such a deep slope, protecting about 32,000 km^2^.
+The N-BB II includes such a deep slope, protecting about 32,000 km^2^ (~55º-56ºS, ~58º-62ºW).
 Intense upwelling and mixing occur in relation with the slope, entraining deep nutrient-rich waters into the photic layer [@Piola2009; @Matano2019] and resulting in a fairly homogeneous water column both spatially and temporally [@Glorioso1995; @Guerrero1999; @Matano2019].
@@
 
-load("../results/summary_results_jun23.rda")
+load("../results/summary_results_jul23.rda")
 
@@
 
-load("../data/foodweb-data_jun23.rda")
-load("../results/summary_results_jun23.rda")
+load("../data/foodweb-data_jul23.rda")
+load("../results/summary_results_jul23.rda")
 
@@
 the higher the species' TL, the lower the trophic similarity or the higher the uniqueness in terms of trophic role (Figure 4C).
-Here it is noteworthy to highlight those high-trophic level species (TL > 3.1) with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster sp* (echinoderms), *Daption capense* and *Eudyptes chrysocome* (seabirds), Ziphiidae and *Lagenorhynchus cruciger* (marine mammals) (Table S3).
+Here it is noteworthy to highlight those high-trophic level species (TL > 3.1) with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster* sp.
+(echinoderms), *Daption capense* and *Eudyptes chrysocome* (seabirds), Ziphiidae and *Lagenorhynchus cruciger* (marine mammals) (Table S3).
 
@@
 The most evident generalist species are *Patagonotothen guntheri* [@CovattiAle2022], *P.
-ramsayi* [@Fischer2022], *Dissostichus eleginoides* [@Troccoli2020], *Bathyraja brachyurops* [@Belleggia2008a], and *B.
+ramsayi* [@Fischer2022], juveniles of *Dissostichus eleginoides* [@Troccoli2020], *Bathyraja brachyurops* [@Belleggia2008a], and *B.
 griseocauda* [@Bellegia2014], with more than 25 potential prey.
-Since these species present mid-trophic positions in the food web (3-4), acting as predator and prey, they might be important links between lower and higher trophic levels.
+Since these species present mid-trophic positions in the food web (with the exception of adults of *Dissostichus eleginoides* that are top predators), acting as predator and prey, they might be important links between lower and higher trophic levels.
 This result is in agreement with the sole analysis, using stable isotopes, that exists so far for the trophic structure of the MPA N-BB [@Riccialdelli2020], and resembles other high-latitude marine systems of the Southwest Atlantic and Antarctic regions [@Arkhipkin2013; @Marina2018].
@@
 The most demanded source we identified in this study (i.e.
-detritus) supports the abundant benthic community of filter-feeders [@Schejter2016], likely feeding on detritus that is constantly resuspended from the bottom [@Martin2021].
-Furthermore, we found that the second and third-most consumed prey were diatoms and species of *Euphausia*, respectively, which are essential sources for the diverse zooplankton community [@Spinelli2020], mid-TL consumers like the Fuegian sprat *Sprattus fuegensis* [@Padovani2021] and *Patagonotothen ramsayi* [@Fischer2022], and top predators such as the black-browed and grey-headed albatrosses (*Thalassarche melanophris* and *Thalassarche chrysostoma*, respectively) [@Catry2004], and baleen whales (species of the genera Balaenoptera and Eubalaena) [@Valenzuela2018].
+detritus) supports the abundant benthic community of filter-feeders [@Schejter2016], components of the animal forest [@Schejter2020], likely feeding on detritus that is constantly resuspended from the bottom [@Martin2021].
+Furthermore, we found that the second and third-most consumed prey were diatoms and species of *Euphausia*, respectively, which are essential sources for the diverse zooplankton community [@Spinelli2020], mid-TL consumers like the Fuegian sprat *Sprattus fuegensis* [@Padovani2021] and *Patagonotothen ramsayi* [@Fischer2022], and top predators such as the black-browed and grey-headed albatrosses (*Thalassarche melanophris* and *Thalassarche chrysostoma*, respectively) [@Catry2004], and baleen whales (species of the genera *Balaenoptera* and *Eubalaena*) [@Valenzuela2018].
 
@@
 Closeness quantifies how many steps away species $i$ is from all other species in the food web, and is proportional to how rapidly the indirect effects of the focal species can spread to other species in the network [@Scotti2010].
-In the food web of the MPA N-BB, low-TL consumers arise as important in this regard: species of the zooplankton community, *Calanus* and *Euphausia*, and Brachiopoda.
+In the food web of the MPA N-BB, low-TL consumers arise as important in this regard: species of the zooplankton community, *Calanus* and *Euphausia*, *Zygochlamys patagonica* (Bivalvia), and Brachiopoda.
 Any perturbation affecting these species, such as the recently confirmed contaminants mercury [@Fioramonti2022] and microplastics [@Cossi2021; @DiMauro2022], should be of concern since it might reach many other species in the food web.
@@
 We have identified the longtail southern cod *Patagonotothen ramsayi* as the most important species in this sense.
-Moreover, in light of our analysis, other species like the Patagonian toothfish *Dissostichus eleginoides*, the Patagonian cod *Salilota australis*, the yellowfin notothenioid *Patagonotothen guntheri*, and the Patagonian longfin squid *Doryteuthis gahi* should be considered as relevant in the energy transfer in the ecosystem.
+Moreover, in light of our analysis, other species like the Patagonian toothfish *Dissostichus eleginoides* (juveniles), the Patagonian cod *Salilota australis*, the yellowfin notothenioid *Patagonotothen guntheri*, and the Patagonian longfin squid *Doryteuthis gahi* should be considered as relevant in the energy transfer in the ecosystem.
 All these species have a mid-trophic position in the food web, supporting the 'wasp-waist' control hypothesis for the MPA N-BB [@Riccialdelli2020].
@@
 At the same time, our results highlight the uniqueness in terms of the trophic role of high-TL predators.
-Here, not only the expected pelagic animals such as marine mammals and seabirds arise as relevant, but also demersal vertebrate (chondrichthyans *Bathyraja macloviana* and *Squalus acanthias*) and benthic invertebrate species (echinoderms *Diplopteraster clarki* and *Pteraster sp*) are noteworthy.
+Here, not only the expected pelagic animals such as marine mammals and seabirds arise as relevant, but also demersal vertebrate (chondrichthyans *Bathyraja macloviana* and *Squalus acanthias*) and benthic invertebrate species (echinoderms *Diplopteraster clarki* and *Pteraster* sp.) are noteworthy.
 The role that such species play in the MPA N-BB ecosystem is unique and perturbations on them might result in unprecedented changes at the trophic structure and functioning level.
@@
 Although there exists such data for some species [@Schejter2021], it would not be possible to include it in the food web framework described here due to a taxonomical resolution mismatch.
-In this regard, we should mention the case of *Zygochlamys patagonica* (Bivalvia) that is highlighted by our species-level analyses though it has been found in low abundances in the area [@Schejter2021].
+In this regard, we should mention the case of *Zygochlamys patagonica* (Bivalvia) and Brachiopoda that are highlighted by our species-level analyses though they have been found in low abundances in the area [@Schejter2021].
 

### 2023-07-11 MS_ToSubmit/SupMaterial.Rmd
Schejter suggs.

@@
   filter(!str_detect(Predator, "\\*$")) %>% 
+  mutate(Prey = case_when(Prey == "Brachiopoda_spp" ~ "Brachiopoda", TRUE ~ "Other")) %>%
   dplyr::select(Prey, Predator, Reference, Reference_link) %>% 

### 2023-07-11 R/1_datawrangling.R

@@ -26,7 +26,7 @@ sp_raw <- sp_raw %>%
 
 ## Lista de Interacciones ----
 
-int_raw <- read.csv("data/ListaInteracciones_AMPNBB_jun23.csv")
+int_raw <- read.csv("data/ListaInteracciones_AMPNBB_jul23.csv")
 
 int_raw <- int_raw %>% 
   # low-resolved Phytoplankton
@@ -145,4 +145,4 @@ int_raw <- subset(int_raw, !(Prey %in% "Demospongiae *"))  # exclude rows with P
 ## Save data ----
 
 save(sp_raw, int_raw,
-     file = "data/cleaned-data_jun23.rda")
+     file = "data/cleaned-data_jul23.rda")

### 2023-07-11 R/2_dataexploring.R

@@ -17,7 +17,7 @@ ipak(packages)
 
 # Cargar datos ----
 
-load("data/cleaned-data_jun23.rda")
+load("data/cleaned-data_jul23.rda")
 
 
 # Lista de Especies ----
@@ -38,7 +38,7 @@ group_count <- sp_raw %>%
 sum(group_count$n)
 
 # Definir colores para cada GF
-col_palette <- scales::hue_pal()(35)
+col_palette <- scales::hue_pal()(38)
 FGColors <- setNames(col_palette, levels(sp_raw$FunctionalGroup))
 
 (plot_grupos <- ggplot(group_count, aes(x = FunctionalGroup, y = n, fill = FunctionalGroup)) + 

### 2023-07-11 R/3_foodwebexploring.R

@@ -17,7 +17,7 @@ ipak(packages)
 
 # Cargar datos ----
 
-load("data/cleaned-data_jun23.rda")
+load("data/cleaned-data_jul23.rda")
 
 
 # Red trófica ----
@@ -114,4 +114,4 @@ plotTrophLevel(g, ylab = "Trophic level")
 # Save data ----
 
 save(g, int_need_res, int_good_res,
-     file = "data/foodweb-data_jun23.rda")
+     file = "data/foodweb-data_jul23.rda")

### 2023-07-11 R/4_foodwebanalysis.R

@@ -18,8 +18,8 @@ ipak(packages)
 
 # Cargar datos ----
 
-load("data/cleaned-data_jun23.rda")
-load("data/foodweb-data_jun23.rda")
+load("data/cleaned-data_jul23.rda")
+load("data/foodweb-data_jul23.rda")
 
 
 # Análisis ----
@@ -171,7 +171,7 @@ spp_total <- spp_total %>%
                              FunctionalGroup %in% c("Fish_Demersal") ~ "Demersal"))
 
 
-write_csv(spp_total, file = "results/spp_prop_jun23.csv")
+write_csv(spp_total, file = "results/spp_prop_jul23.csv")
 
 
 # Resolución de la red ----
@@ -193,5 +193,5 @@ int_grp <- spp_total %>%
 
 # Guardar datos ----
 
-save(g_up, g, deg_dist_fit, prop_topol, spp_total, top.role, top.role.df,
-     file = "results/summary_results_jun23.rda")
+save(g_up, g, deg_dist_fit, prop_topol, spp_total, top.role, top.role.df, int_grp,
+     file = "results/summary_results_jul23.rda")

### 2023-07-11 R/5_regressionanalyses.R

@@ -16,7 +16,7 @@ ipak(packages)
 
 
 # Datos ----
-load("results/summary_results_jun23.rda")
+load("results/summary_results_jul23.rda")
 
 
 # Linear Regression ----
@@ -80,4 +80,3 @@ ts_reg <- lm(meanTrophicSimil ~ TL, data = spp_total)
 summary(ts_reg)
 ols_test_normality(ts_reg)  # check normality of residuals
 ols_plot_resid_qq(ts_reg)  # Q-Q plot
-

### 2023-07-11 R/6_figures.R

@@ -18,7 +18,7 @@ ipak(packages)
 
 # Cargar datos ----
 
-load("results/summary_results_jun23.rda")
+load("results/summary_results_jul23.rda")
 
 
 # Figuras ----
@@ -253,6 +253,3 @@ plot_sp_tr <- data_TRColor %>%
         axis.text.y = element_text(size = 15),
         legend.position = "none")
 plot_sp_tr
-
-
-

### 2023-07-12 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Schejter suggs.

@@
 We applied a network approach to characterise the food web in terms of complexity and structure, and identifying the species' role in such a framework.
-In terms of complexity, the MPA N-BB food web consisted of 1788 predator-prey interactions and 380 species, with a link density of 4.70 and a connectance of 0.01.
+In terms of complexity, the MPA N-BB food web consisted of 1788 predator-prey interactions and 379 species, with a link density of 4.72 and a connectance of 0.01.
 In terms of structure, almost half of the consumers were omnivores (0.48), and the network displayed a small-world pattern.
@@
 
-In terms of complexity, the MPA Namuncurá - Burdwood Bank food web consisted of 1788 predator-prey interactions and 380 species, where 93% of them were defined at the species taxonomical level (Figure 2, Table S2).
-The food web presented a link density (e.g., the average number of interactions per species) of 4.70, and a connectance of 0.01.
+In terms of complexity, the MPA Namuncurá - Burdwood Bank food web consisted of 1788 predator-prey interactions and 379 species, where 93% of them were defined at the species taxonomical level (Figure 2, Table S2).
+The food web presented a link density (e.g., the average number of interactions per species) of 4.72, and a connectance of 0.01.
 Almost half of the consumers were omnivores (0.48), feeding on sources at different trophic levels.
@@
 
-Considering the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.78), as well as 'module hub' species (TL = 1 - 3.9); 'module connector' was constrained to mid-TLs (2 - 3.86); and 'network connector', was represented by only one trophic species: detritus (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework).
+Considering the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.78), as well as 'module hub' species (TL = 1 - 3.92); 'module connector' was constrained to mid-TLs (2 - 3.86); and 'network connector', was represented by only one trophic species: detritus (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework).
 Here it is important to highlight the two latter topological roles because they are responsible for linking modules and maintaining the connectivity of the food web: 42 species (1 network connector + 41 module connectors) from 19 different functional groups with a TL range = 1 - 3.86.
@@
 Each point represents a species.
-Linear regressions for betweenness ($y = 74.82x - 116.82, R^2 = 0.05, p-value < 0.01$), closeness ($y = 1.04e-05x - 9.25e-4, R^2 = 0.004, p-value = 0.11$) and trophic similarity ($y = -0.02x + 0.1 , R^2 = 0.07, p-value < 0.01$).
+Linear regressions for betweenness ($y = 74.97x - 117.35, R^2 = 0.05, p-value < 0.01$), closeness ($y = 9.33e-06x - 9.31e-4, R^2 = 0.003, p-value = 0.15$) and trophic similarity ($y = -0.02x + 0.11 , R^2 = 0.07, p-value < 0.01$).
 Note that for panels A, B and C only species with TLs equal or greater than 2 were considered."}

### 2023-07-12 MS_ToSubmit/MS_Burdwood_foodweb.tex
Schejter suggs.

@@
   associated to oceanic islands, except for the MPAs Namuncurá -
-  Burdwood Bank I and II (MPA N-BB, 53º--55ºS and 56º--62ºW,
-  respectively), which are associated to a submarine plateau and its
-  southern adjacent deep slope region, respectively. Here, we present
-  the first detailed analysis of the network of predator-prey
+  Burdwood Bank I and II (MPA N-BB, \textasciitilde53º--55ºS and
+  \textasciitilde56º--62ºW), which are associated to a submarine plateau
+  and its southern adjacent deep slope region, respectively. Here, we
+  present the first detailed analysis of the network of predator-prey
   interactions (food web) for the MPA N-BB ecosystem. We applied a
@@
   In terms of complexity, the MPA N-BB food web consisted of 1788
-  predator-prey interactions and 380 species, with a link density of
-  4.70 and a connectance of 0.01. In terms of structure, almost half of
+  predator-prey interactions and 379 species, with a link density of
+  4.72 and a connectance of 0.01. In terms of structure, almost half of
   the consumers were omnivores (0.48), and the network displayed a
@@
   be vulnerable to external perturbations targeting highly connected
-  species, although structural properties might provide resilience and
+  species, although other properties might provide resilience and
   resistance, resulting in a rearranged structure that preserves its
@@
 In the sub-Antarctic region, the level of ocean protection is mainly
-associated to oceanic islands, such as the South Georgia and South
+associated to oceanic islands, such as the South Georgias and South
 Sandwich, Bouvet, Prince Edward, and Macquarie islands (IUCN \&
 UNEP-WCMC, 2023). Interestingly, the case of the MPAs Namuncurá -
-Burdwood Bank I and II (MPA N-BB, 53º--55ºS 56º--62ºW), which is the
-focus of this work, is unique since these MPAs are associated to a
-submarine plateau and its southern adjacent deep slope region,
-respectively (Falabella, 2017). In addition, such MPAs are part of a
-network of protected areas in the sub-Antarctic area (jointly with MPA
-Yaganes) that aims to protect and strengthen the functioning of this
-southern region to maintain global ocean health.
+Burdwood Bank I and II (MPA N-BB, \textasciitilde53º--55ºS
+\textasciitilde56º--62ºW), which is the focus of this work, is unique
+since these MPAs are associated to a submarine plateau and its southern
+adjacent deep slope region, respectively (Falabella, 2017; Schejter et
+al., 2020). In addition, such MPAs are part of a network of protected
+areas in the sub-Antarctic area (jointly with MPA Yaganes) that aims to
+protect this southern region in order to contribute to global ocean
+health.
 
@@
 endemic species, and/or high biodiversity across taxonomic levels (Hogg
-et al., 2016). Indeed, the MPA N-BB was created to protect a sensitive
-and biodiverse benthic habitat that was barely known (Falabella, 2017;
-Schejter et al., 2016). The benthic community is featured by high
-biomass of vulnerable and fragile species (mainly Porifera and Cnidaria)
-that meet the characteristics of vulnerable marine ecosystems (Schejter
-\& Albano, 2021), here defined as sites that present taxa with a minimum
-biomass of 10 kg per 1200 m\textsuperscript{2} (Commission for the
-Conservation of Antarctic Marine Living Resources (CCAMLR), 2009). Also,
-it provides habitat to several small-sized species (López-Gappa et al.,
-2018; Martin Sirito, 2019; Schejter \& Bremec, 2019), and has an
-important role in the life history of fishes as a food source, refuge
-and nursery area (Covatti Ale et al., 2022; Delpiani et al., 2020;
-Fischer et al., 2022; Florencia et al., 2023; García Alonso et al.,
-2018; Troccoli et al., 2020; Vazquez et al., 2018). The maintenance of
-this singular community is related to local and regional oceanographic
-processes, including the circulation of the rich Malvinas (Falkland)
-current in the area (Guerrero et al., 1999; Piola \& Gordon, 1989) and
-the upwelling and mixing phenomena (Matano et al., 2019). The input of
-nutrients from the Malvinas (Falkland) current also supports a diverse
-plankton community (Guinder et al., 2020). Overall, 811 benthic and
-plankton species have been identified for the MPA N-BB ecosystem, where
-349 were reported for the first time in the area in recent years
-(Administración de Parques Nacionales, 2022). However, identifying the
-main species involved in the maintenance of ecosystem services and
-health as well as for management and conservation is essential.
-
-Recently, the structure of the southwestern South Atlantic Ocean has
-been proposed to be under a `wasp-waist' control, meaning that the
-structure and dynamics of the ecosystem are regulated primarily by
+et al., 2016). Indeed, the MPA N-BB was created to protect a potentially
+sensitive and biodiverse benthic habitat that was only barely known
+(Falabella, 2017; Schejter et al., 2016). The benthic community is
+featured by high biomass of vulnerable and fragile species (mainly
+Porifera, Bryozoa and Cnidaria) that considered with their environment
+meet the characteristics of vulnerable marine ecosystems (Schejter \&
+Albano, 2021), here defined as sites that present densities of Indicator
+Taxa of \textgreater{} 10 kg per 1200 m\textsuperscript{2} (Commission
+for the Conservation of Antarctic Marine Living Resources (CCAMLR),
+2009). Also, the benthic realm provides habitat to several small-sized
+species (López-Gappa et al., 2018; Martin Sirito, 2019; Schejter \&
+Bremec, 2019), and has an important role in the life history of fishes
+as a food source, refuge and nursery area (Covatti Ale et al., 2022;
+Delpiani et al., 2020; Fischer et al., 2022; Florencia et al., 2023;
+García Alonso et al., 2018; Matusevich, 2022; Troccoli et al., 2020;
+Vazquez et al., 2018). The maintenance of this singular community is
+related to local and regional oceanographic processes, including the
+circulation of the rich Malvinas (Falkland) current in the area
+(Guerrero et al., 1999; Piola \& Gordon, 1989) and the upwelling and
+mixing phenomena (Matano et al., 2019). The input of nutrients from the
+Malvinas (Falkland) current also supports a diverse plankton community
+(Guinder et al., 2020).
+
+Overall, 811 benthic and plankton species have been identified for the
+MPA N-BB ecosystem, where 349 were reported for the first time in the
+area in recent years (Administración de Parques Nacionales, 2022).
+Identifying the main species involved in the maintenance of ecosystem
+services and health as well as for management and conservation is
+essential. Recently, the structure of the southwestern South Atlantic
+Ocean has been proposed to be under a `wasp-waist' control, meaning that
+the structure and dynamics of the ecosystem are regulated primarily by
 mid-trophic level species (e.g., fishes, crustaceans) (Padovani et al.,
@@
 the ecosystem of the MPA N-BB shows a more pronounced `wasp-waist'
-structure, meaning a shorter food-chain length and a greater trophic
-overlap and redundancy, than other sub-Antarctic areas, such as the
-continental shelf off Tierra del Fuego. The Fuegian sprat \emph{Sprattus
-fuegensis} and longtail southern cod \emph{Patagonotothen ramsayi} are
-considered the most plausible `wasp-waist' species (Riccialdelli et al.,
-2020).
-
-High-latitude marine ecosystems, such as the MPA N-BB, are considered
-complex systems in terms of biodiversity and ecological interactions
-(Cordone et al., 2020; Day et al., 2013; Kortsch et al., 2019; Trathan
-et al., 2021). Although there is a robust knowledge about the complexity
+structure, meaning a shorter food chain and a greater trophic overlap
+and redundancy, than other sub-Antarctic areas, such as the continental
+shelf off Tierra del Fuego. The Fuegian sprat \emph{Sprattus fuegensis}
+and longtail southern cod \emph{Patagonotothen ramsayi} are considered
+the most plausible `wasp-waist' species (Riccialdelli et al., 2020).
+
+High-latitude marine ecosystems, such as the MPA N-BB, are complex
+systems in terms of biodiversity and ecological interactions (Cordone et
+al., 2020; Day et al., 2013; Kortsch et al., 2019; Trathan et al.,
+2021). Although there is a robust knowledge about the complexity
 considering the richness of the benthic and plankton communities in the
@@
 in terms of complexity and structure, and identify the species' role in
-such a network framework.
+the network.
 
@@
 Isla de los Estados and 200 km south of Malvinas/Falkland Islands. The
-MPA N-BB I comprises nearly 34,000 km\textsuperscript{2} circumscribed
-by the 200 m isobath, between 54º--55ºS and 56º--62ºW, with a slight
-slope extended nearly 370 km east--west. Physical features in the BB are
-fairly stable, with salinity averaging 34 all year round and temperature
-ranging between 4 and 8ºC (Acha et al., 2004; Guerrero et al., 1999;
-Piola \& Falabella, 2009). The BB is surrounded by steep flanks of up to
-4000 m depth through which strong currents circulate (Matano et al.,
-2019; Piola \& Gordon, 1989; Reta, 2014). The N-BB II includes such a
-deep slope, protecting about 32,000 km\textsuperscript{2}. Intense
-upwelling and mixing occur over it, entraining deep nutrient-rich waters
-into the photic layer (Matano et al., 2019; Piola \& Falabella, 2009)
-and resulting in a fairly homogeneous water column both spatially and
-temporally (Glorioso \& Flather, 1995; Guerrero et al., 1999; Matano et
-al., 2019).
+MPA N-BB I comprises nearly 28,900 km\textsuperscript{2} circumscribed
+by the 200 m isobath, between \textasciitilde54º--55ºS and
+\textasciitilde56º--62ºW, with a slight slope extended nearly 370 km
+east--west. Physical features in the BB are fairly stable, with salinity
+averaging 34 all year round and temperature ranging between 4 and 8ºC
+(Acha et al., 2004; Guerrero et al., 1999; Piola \& Falabella, 2009).
+The BB is surrounded by steep flanks of up to 4000 m depth through which
+strong currents circulate (Matano et al., 2019; Piola \& Gordon, 1989;
+Reta, 2014). The N-BB II includes such a deep slope, protecting about
+32,000 km\textsuperscript{2} (\textasciitilde55º-56ºS,
+\textasciitilde58º-62ºW). Intense upwelling and mixing occur in relation
+with the slope, entraining deep nutrient-rich waters into the photic
+layer (Matano et al., 2019; Piola \& Falabella, 2009) and resulting in a
+fairly homogeneous water column both spatially and temporally (Glorioso
+\& Flather, 1995; Guerrero et al., 1999; Matano et al., 2019).
 
@@
 In order to build the network of predator-prey interactions, we reviewed
-more than 150 references considering published articles, Ph.D.~theses,
+more than 170 references considering published articles, Ph.D.~theses,
 public databases, and reports belonging to 16 research cruises conducted
@@
 study area, we followed the concept of trophic species, here defined as
-aggregated groups of taxa. In most cases, we followed it when specific
-data on species, in the taxonomic sense, were not available. In some
-cases, we collapsed species when taxa shared the same set of predators
-and prey (trophic similarity, Martinez (1991)), one of the aggregation
-methods that better preserve food web functional properties (Gauzens et
-al., 2013). In addition, for endemic species (e.g.~bryozoan
-\emph{Burdwoodipora paguricola}) and other species with no trophic
-studies so far, we inferred their feeding interactions applying a
-conservative approach that assumes that the set of prey and predators
-are at some point preserved in time. In those cases we gathered
-information from upper taxonomic levels (i.e.~Genus, Family, Order,
-Class, Phylum) as a good proxy variable (Morales-Castilla et al., 2015;
-Pomeranz et al., 2019). Details about this can be found in Supplementary
-Material (Table S2).
+follows: taxa collapsed into a single node in the network. In most
+cases, we followed this concept when specific data on species, in the
+taxonomic sense, were not available. In some cases, we collapsed species
+when taxa shared the same set of predators and prey (trophic similarity,
+Martinez (1991)), one of the aggregation methods that better preserve
+food web functional properties (Gauzens et al., 2013). In addition, for
+endemic species (e.g.~bryozoan \emph{Burdwoodipora paguricola}) and
+other species with no trophic studies so far, we inferred their feeding
+interactions applying a conservative approach that assumes that the set
+of prey and predators are at some point preserved in time. In those
+cases we gathered information from upper taxonomic levels (i.e.~Genus,
+Family, Order, Class, Phylum) as a good proxy variable (Morales-Castilla
+et al., 2015; Pomeranz et al., 2019). Details about this can be found in
+Supplementary Material (Table S2). Furthermore, we considered non-living
+food sources, such as detritus and necromass, as prey species in the
+food web context.
 
@@
 The species-level analysis aims to describe the species' role in the
-food web. For this, we considered the following properties: (1)
-betweenness Btw; (2) closeness Cl; (3) trophic similarity TS; (4)
-topological role TR; and (5) trophic level TL (Table 1). Topological
-roles refer to the fact that food webs tend to naturally organize in
-non-random, modular patterns, where modules are defined as a group of
-species that interact more frequently among themselves than with species
-that are not members of the module (Guimerà \& Nunes Amaral, 2005).
-Species can play different roles in this respect, according to the
-pattern of interactions within their own module and/or across modules.
-We computed the topological role for each species, classified as module
-hub, species with a relatively high number of interactions, but most
-within its own module; module specialist, species with relatively few
-interactions and most within its own module; module connector, species
-with relatively few interactions mainly between modules; and network
-connector, species with high connectivity between and within modules
-(Guimerà \& Nunes Amaral, 2005).
+food web. For this, we considered the following properties: betweenness
+Btw, closeness Cl, trophic similarity TS, topological role TR, and
+trophic level TL (Table 1). Topological roles refer to the fact that
+food webs tend to naturally organize in non-random, modular patterns,
+where modules are defined as a group of species that interact more
+frequently among themselves than with species that are not members of
+the module (Guimerà \& Nunes Amaral, 2005). Species can play different
+roles in this respect, according to the pattern of interactions within
+their own module and/or across modules. We computed the topological role
+for each species, classified as module hub, species with a relatively
+high number of interactions, but most within its own module; module
+specialist, species with relatively few interactions and most within its
+own module; module connector, species with relatively few interactions
+mainly between modules; and network connector, species with high
+connectivity between and within modules (Guimerà \& Nunes Amaral, 2005).
 
@@
 
-In terms of complexity, the MPA Namuncurá - Burdwood Bank food web (N-BB
-I and II) consisted of 1788 predator-prey interactions and 380 species,
-where 93\% of them were defined at the species taxonomical level (Figure
-2, Table S2). The food web presented a link density (e.g., the average
-number of interactions per species) of 4.70, and a connectance of 0.01.
-Almost half of the consumers were omnivores (0.48), feeding on sources
-at different trophic levels. The food web displayed a small-world
-pattern, meaning that the path length was lower and the clustering
-coefficient higher than the random networks (Table 2).
+In terms of complexity, the MPA Namuncurá - Burdwood Bank food web
+consisted of 1788 predator-prey interactions and 379 species, where 93\%
+of them were defined at the species taxonomical level (Figure 2, Table
+S2). The food web presented a link density (e.g., the average number of
+interactions per species) of 4.72, and a connectance of 0.01. Almost
+half of the consumers were omnivores (0.48), feeding on sources at
+different trophic levels. The food web displayed a small-world pattern,
+meaning that the path length was lower and the clustering coefficient
+higher than the random networks (Table 2).
 
@@
 \hline
-380 & 1788 & 4.71 & 0.01 & 0.48 & 2.99 & 0.08 & True\\
+379 & 1788 & 4.72 & 0.01 & 0.49 & 2.99 & 0.08 & True\\
 \hline
@@
 pattern, few prey presented multiple predators (Figure 3C). The top-five
-prey in number of predators were: Detritus (Non-living, 153 predators),
-the three categories of Diatoms considered (benthic, centric and
-pennate, 72.5 predators on average), and species of the genus
-\emph{Euphausia} (Zooplankton, 46 predators). Finally, taking into
-account the interactions within each functional group, most interactions
-were concentrated in a few species (Figure 3D). The most evident species
-were: \emph{Doryteuthis gahi} (Cephalopoda), \emph{Grimothea gregaria}
-(Decapoda), \emph{Patagonotothen ramsayi}, \emph{Patagonotothen
-guntheri} and \emph{Dissostichus eleginoides} (bentho-pelagic fish),
-\emph{Sprattus fuegensis} and \emph{Micromesistius australis} (pelagic
-fish), and species of \emph{Euphausia} and \emph{Themisto gaudichaudii}
-(Zooplankton). Overall, there is an evident asymmetry in the
-distribution of interactions among species at different levels in the
-MPA N-BB food web.
+prey (or food sources) in number of predators were: Detritus
+(Non-living, 153 predators), the three categories of Diatoms considered
+(benthic, centric and pennate, 72.5 predators on average), and species
+of the genus \emph{Euphausia} (Zooplankton, 46 predators). Finally,
+taking into account the interactions within each functional group, most
+interactions were concentrated in a few species (Figure 3D). The most
+evident species were: \emph{Doryteuthis gahi} (Cephalopoda),
+\emph{Grimothea (=Munida) gregaria} (Decapoda), \emph{Patagonotothen
+ramsayi}, \emph{Patagonotothen guntheri} and \emph{Dissostichus
+eleginoides} (bentho-pelagic fish), \emph{Sprattus fuegensis} and
+\emph{Micromesistius australis} (pelagic fish), and species of
+\emph{Euphausia} and \emph{Themisto gaudichaudii} (Zooplankton).
+Overall, there is an evident asymmetry in the distribution of
+interactions among species at different levels in the MPA N-BB food web.
 
@@
 \emph{Bathyraja macloviana} and \emph{Squalus acanthias}
-(Chondrichthyans), \emph{Diplopteraster clarki} and \emph{Pteraster sp}
+(Chondrichthyans), \emph{Diplopteraster clarki} and \emph{Pteraster} sp.
 (echinoderms), \emph{Daption capense} and \emph{Eudyptes chrysocome}
@@
 most frequent and presented a wide TL range (1 - 4.78), as well as
-`module hub' species (TL = 1 - 3.9); `module connector' was constrained
+`module hub' species (TL = 1 - 3.92); `module connector' was constrained
 to mid-TLs (2 - 3.86); and `network connector', was represented by only
@@
 Each point represents a species.
-Linear regressions for betweenness ($y = 74.82x - 116.82, R^2 = 0.05, p-value < 0.01$), closeness ($y = 1.04e-05x - 9.25e-4, R^2 = 0.004, p-value = 0.11$) and trophic similarity ($y = -0.02x + 0.1 , R^2 = 0.07, p-value < 0.01$).
+Linear regressions for betweenness ($y = 74.97x - 117.35, R^2 = 0.05, p-value < 0.01$), closeness ($y = 9.33e-06x - 9.31e-4, R^2 = 0.003, p-value = 0.15$) and trophic similarity ($y = -0.02x + 0.11 , R^2 = 0.07, p-value < 0.01$).
 Note that for panels A, B and C only species with TLs equal or greater than 2 were considered.}\label{fig:figure4}
@@
 the most highly-resolved networks of trophic interactions ever studied,
-not only for a high-latitude marine ecosystem but also for any marine
-protected area worldwide to our knowledge. It is of paramount importance
-to consider the complexity of species interactions in order to gain
-insights into the structure and functioning of the ecosystem, since the
-aggregation of species might mask food web properties and produce type
-II errors (false positive) (Gauzens et al., 2013; Martinez, 1993).
+not only for a high-latitude open-ocean ecosystem but also for any
+marine protected area worldwide to our knowledge. It is of paramount
+importance to consider the complexity of species interactions in order
+to gain insights into the structure and functioning of the ecosystem,
+since the aggregation of species might mask food web properties and
+produce type II errors (false positives) (Gauzens et al., 2013;
+Martinez, 1993).
 
@@
 is one of the lowest reported so far for these regions; in particular,
-it appears to much lower than that of Beagle Channel (0.05), an adjacent
-coastal area (Rodriguez et al., 2022).
+it appears to be much lower than that of Beagle Channel (0.05), an
+adjacent coastal area (Rodriguez et al., 2022).
 
@@
 pattern. Consequences of this could be of great importance in
-recognizing evolutionary paths and the vulnerability to perturbations
-(Montoya \& Solé, 2002). On the one hand, a short path length implies a
-rapid spread of an impact (e.g., contaminant, population fluctuation,
-local extinction) throughout the network but, at the same time, more
-potentially adaptive dynamics in the face of external perturbations
-(Montoya \& Solé, 2002; Williams et al., 2002). On the other hand, a
-high clustering coefficient indicates the formation of subnetworks
-composed only by the neighbours of particular species. This translates
-into a greater resistance of the network due to the confinement of
-perturbations mainly within subnetworks and not spreading between them
-(Heer et al., 2020; Kortsch et al., 2019). Overall, a small-world
-topology provides ecological networks with greater resilience and
-resistance (Bornatowski et al., 2017; Dormann et al., 2017).
+recognizing species evolutionary paths and the vulnerability to
+perturbations (Montoya \& Solé, 2002). On the one hand, a short path
+length implies a rapid spread of an impact (e.g., contaminant,
+population fluctuation, local extinction) throughout the network but, at
+the same time, more potentially adaptive dynamics in the face of
+external perturbations (Montoya \& Solé, 2002; Williams et al., 2002).
+On the other hand, a high clustering coefficient indicates the formation
+of subnetworks composed only by the neighbours of particular species.
+This translates into a greater resistance of the network due to the
+confinement of perturbations mainly within subnetworks and not spreading
+between them (Heer et al., 2020; Kortsch et al., 2019). Overall, a
+small-world topology provides ecological networks with greater
+resilience and resistance (Bornatowski et al., 2017; Dormann et al.,
+2017).
 
@@
 network properties that makes it unique in terms of network resolution,
-complexity, and structural pattern. All this suggests that the ecosystem
+complexity, and structural pattern. All this suggests that the food web
 might be fragile to external perturbations targeting highly connected
 species, which in turn coincides to be commercial exploited species as
-fishes (Martínez et al., 2015). However, structural properties might
-provide resilience and resistance with the final outcome of a rearranged
+fishes (Laptikhovsky et al., 2013; Martínez et al., 2015; Winter \&
+Arkhipkin, 2023). However, structural properties might provide
+resilience and resistance with the final outcome of a rearranged
 structure maintaining its functions.
@@
 The degree distribution allows identifying important species, such as
-potential keystone species (Dunne et al., 2002a; Solé \& Montoya, 2001),
-generalist/specialist species, and dominant food sources (Kondoh et al.,
-2010).
+potential keystone species (i.e.~highly connected) (Dunne et al., 2002a;
+Solé \& Montoya, 2001), generalist/specialist species, and dominant food
+sources (Kondoh et al., 2010).
 
@@
 N-BB either have a narrow diet or are specialists, while few present a
-broad diet. The most evident generalist species are \emph{Patagonotothen
-guntheri} (Covatti Ale et al., 2022), \emph{P. ramsayi} (Fischer et al.,
-2022), \emph{Dissostichus eleginoides} (Troccoli et al., 2020),
-\emph{Bathyraja brachyurops} (Belleggia et al., 2008), and \emph{B.
-griseocauda} (Bellegia et al., 2014), with more than 25 potential prey.
-Since these species present mid-trophic positions in the food web (3-4),
-acting as predator and prey, they might be important links between lower
-and higher trophic levels. This result is in agreement with the sole
+broad or generalist diet. The most evident generalist species are
+\emph{Patagonotothen guntheri} (Covatti Ale et al., 2022), \emph{P.
+ramsayi} (Fischer et al., 2022), juveniles of \emph{Dissostichus
+eleginoides} (Troccoli et al., 2020), \emph{Bathyraja brachyurops}
+(Belleggia et al., 2008), and \emph{B. griseocauda} (Bellegia et al.,
+2014), with more than 25 potential prey. Since these species present
+mid-trophic positions in the food web (with the exception of adults of
+\emph{Dissostichus eleginoides} that are top predators), acting as
+predator and prey, they might be important links between lower and
+higher trophic levels. This result is in agreement with the sole
 analysis, using stable isotopes, that exists so far for the trophic
@@
 in the food web of the MPA N-BB. This suggests that there are dominant
-food sources from which most consumers depend on and from where the
-ecosystem energy is being transferred to the upper trophic levels. The
-most demanded source we identified in this study (i.e.~detritus)
-supports the abundant benthic community of filter-feeders (Schejter et
-al., 2016), likely feeding on detritus that is constantly resuspended
-from the bottom (Martin \& Flores Melo, 2021). Furthermore, we found
-that the second and third-most consumed prey were diatoms and species of
-\emph{Euphausia}, respectively, which are essential sources for the
-diverse zooplankton community (Spinelli et al., 2020), mid-TL consumers
-like the Fuegian sprat \emph{Sprattus fuegensis} (Padovani et al., 2021)
-and \emph{Patagonotothen ramsayi} (Fischer et al., 2022), and top
-predators such as the black-browed and grey-headed albatrosses
-(\emph{Thalassarche melanophris} and \emph{Thalassarche chrysostoma},
-respectively) (Catry et al., 2004), and baleen whales (species of the
-genera Balaenoptera and Eubalaena) (Valenzuela et al., 2018).
+food sources on which most consumers depend and from where the ecosystem
+energy is being transferred to the upper trophic levels. The most
+demanded source we identified in this study (i.e.~detritus) supports the
+abundant benthic community of filter-feeders (Schejter et al., 2016),
+components of the animal forest (Schejter et al., 2020), likely feeding
+on detritus that is constantly resuspended from the bottom (Martin \&
+Flores Melo, 2021). Furthermore, we found that the second and third-most
+consumed prey were diatoms and species of \emph{Euphausia},
+respectively, which are essential sources for the diverse zooplankton
+community (Spinelli et al., 2020), mid-TL consumers like the Fuegian
+sprat \emph{Sprattus fuegensis} (Padovani et al., 2021) and
+\emph{Patagonotothen ramsayi} (Fischer et al., 2022), and top predators
+such as the black-browed and grey-headed albatrosses (\emph{Thalassarche
+melanophris} and \emph{Thalassarche chrysostoma}, respectively) (Catry
+et al., 2004), and baleen whales (species of the genera
+\emph{Balaenoptera} and \emph{Eubalaena}) (Valenzuela et al., 2018).
 
@@
 important in this regard: species of the zooplankton community,
-\emph{Calanus} and \emph{Euphausia}, and Brachiopoda. Any perturbation
-affecting these species, such as the recently confirmed contaminants
-mercury (Fioramonti et al., 2022) and microplastics (Cossi et al., 2021;
-Di Mauro et al., 2022) for the area, should be of concern since it might
-reach many other species in the food web. Otherwise, betweenness
-measures the number of shortest paths between species, providing
-information on the importance of species as ``bridges'' for energy
-transfer: a species with high betweenness takes part in more food chains
-and therefore affects more energy flows (Scotti \& Jordán, 2010). We
-have identified the longtail southern cod \emph{Patagonotothen ramsayi}
-as the most important species in this sense. Moreover, in light of our
-analysis, other species like the Patagonian toothfish \emph{Dissostichus
-eleginoides}, the Patagonian cod \emph{Salilota australis}, the
-yellowfin notothenioid \emph{Patagonotothen guntheri}, and the
-Patagonian longfin squid \emph{Doryteuthis gahi} should be considered as
-relevant in the energy transfer in the ecosystem. All these species have
-a mid-trophic position in the food web, supporting the `wasp-waist'
-control hypothesis for the MPA N-BB (Riccialdelli et al., 2020).
+\emph{Calanus} and \emph{Euphausia}, \emph{Zygochlamys patagonica}
+(Bivalvia), and Brachiopoda. Any perturbation affecting these species,
+such as the recently confirmed contaminants mercury (Fioramonti et al.,
+2022) and microplastics (Cossi et al., 2021; Di Mauro et al., 2022),
+should be of concern since it might reach many other species in the food
+web. Otherwise, betweenness measures the number of shortest paths
+between species, providing information on the importance of species as
+``bridges'' for energy transfer: a species with high betweenness takes
+part in more food chains and therefore affects more energy flows (Scotti
+\& Jordán, 2010). We have identified the longtail southern cod
+\emph{Patagonotothen ramsayi} as the most important species in this
+sense. Moreover, in light of our analysis, other species like the
+Patagonian toothfish \emph{Dissostichus eleginoides} (juveniles), the
+Patagonian cod \emph{Salilota australis}, the yellowfin notothenioid
+\emph{Patagonotothen guntheri}, and the Patagonian longfin squid
+\emph{Doryteuthis gahi} should be considered as relevant in the energy
+transfer in the ecosystem. All these species have a mid-trophic position
+in the food web, supporting the `wasp-waist' control hypothesis for the
+MPA N-BB (Riccialdelli et al., 2020).
 
@@
 macloviana} and \emph{Squalus acanthias}) and benthic invertebrate
-species (echinoderms \emph{Diplopteraster clarki} and \emph{Pteraster
-sp}) are noteworthy. The role that such species play in the MPA N-BB
+species (echinoderms \emph{Diplopteraster clarki} and \emph{Pteraster}
+sp.) are noteworthy. The role that such species play in the MPA N-BB
 ecosystem is unique and perturbations on them might result in
@@
 we should mention the case of \emph{Zygochlamys patagonica} (Bivalvia)
-that is highlighted by our species-level analyses though it has been
-found in low abundances in the area (Schejter \& Albano, 2021).
+and Brachiopoda that are highlighted by our species-level analyses
+though they have been found in low abundances in the area (Schejter \&
+Albano, 2021).
 
@@
 We compiled information on the species and trophic diversity of the
-Marine Protected Area Namuncurá - Burdwood Bank, generating an
+oceanic Marine Protected Area Namuncurá - Burdwood Bank, generating an
 unprecedented, well-resolved network of trophic interactions for a
@@
 Burdwood' who humbly provided their knowledge to enhance the quality of
-the present research. It is worth to mention the following researchers:
-Brenda L. Doti (IBBEA, CONICET-UBA; Universidad de Buenos Aires,
-Argentina), Sofía L. Callá (Museo Argentino de Ciencias Naturales
-``Bernardino Rivadavia'', Argentina), Sandra Gordillo (IDACOR-CONICET;
-Universidad Nacional de Córdoba, Argentina), Mariano I. Martinez (Museo
-Argentino de Ciencias Naturales ``Bernardino Rivadavia'', Argentina) and
-Luciano Padovani (Instituto Nacional de Investigación y Desarrollo
-Pesquero, INIDEP, Argentina). Research cruises were funded by national
-funds by the Law 26.875. This study was funded by Consejo Nacional de
-Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de
-Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617), Argentina.
-This work is contribution no. XX of the MPA Namuncurá (Law 26.875).
+the present research. Although most of them are authors of the present
+work, it is worth to mention the following researchers: Brenda L. Doti
+(IBBEA, CONICET-UBA; Universidad de Buenos Aires, Argentina), Sofía L.
+Callá (Museo Argentino de Ciencias Naturales ``Bernardino Rivadavia'',
+Argentina), Sandra Gordillo (IDACOR-CONICET; Universidad Nacional de
+Córdoba, Argentina), Mariano I. Martinez (Museo Argentino de Ciencias
+Naturales ``Bernardino Rivadavia'', Argentina) and Luciano Padovani
+(Instituto Nacional de Investigación y Desarrollo Pesquero, INIDEP,
+Argentina). We thank the MPA Namuncurá − Burdwood Bank administration.
+Research cruises were funded by national funds by the Law 26.875. This
+study was funded by Consejo Nacional de Investigaciones Científicas y
+Técnicas (CONICET) and Agencia Nacional de Promoción Científica y
+Tecnológica (PICT 2020-SERIEA-01617), Argentina. This work is
+contribution no. XX of the MPA Namuncurá (Law 26.875).
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Laptikhovsky2013}{}}%
+Laptikhovsky, V., Arkhipkin, A., \& Brickle, P. (2013). From small
+bycatch to main commercial species: {Explosion} of stocks of rock cod
+{Patagonotothen} ramsayi ({Regan}) in the {Southwest Atlantic}.
+\emph{Fisheries Research}, \emph{147}, 399--403.
+\url{https://doi.org/10.1016/j.fishres.2013.05.006}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Latorre2023}{}}%
@@
 \emph{124}(10), 6904--6926. \url{https://doi.org/10.1029/2019JC015001}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Matusevich2022}{}}%
+Matusevich. (2022). \emph{Chondrichthyan fauna from the {Marine
+Protected Area Namuncurá} at {Burdwood Bank}: Exploring egg nursery
+grounds}. https://www.researchsquare.com.
+\url{https://doi.org/10.21203/rs.3.rs-2247873/v1}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Winter2023}{}}%
+Winter, A., \& Arkhipkin, A. (2023). Opportunistic {Survey Analyses
+Reveal} a {Recent Decline} of {Skate} ({Rajiformes}) {Biomass} in
+{Falkland Islands Waters}. \emph{Fishes}, \emph{8}(1), 24.
+\url{https://doi.org/10.3390/fishes8010024}
+
 \end{CSLReferences}

### 2023-07-12 MS_ToSubmit/SupMaterial.Rmd
Schejter suggs.

@@
 # Load data
-load("../data/cleaned-data_jun23.rda")
+load("../data/cleaned-data_jul23.rda")
 
@@
 # Load data
-load("../data/cleaned-data_jun23.rda")
-load("../data/foodweb-data_jun23.rda")
+load("../data/cleaned-data_jul23.rda")
+load("../data/foodweb-data_jul23.rda")
 
@@
 # Load data
-load("../results/summary_results_jun23.rda")
+load("../results/summary_results_jul23.rda")
 

### 2023-07-17 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
MEPS format

@@
 ---
-title: The complex network of trophic interactions in a subAntarctic oceanic Marine Protected
-  Area
+title: The complex network of trophic interactions in a subAntarctic oceanic Marine Protected Area
 author:
@@
     email: tomasimarina@gmail.com
+    correspondingauthor: true
   - name: Irene R. Schloss^a^^,^^b^^,^^c^
@@
   - name: Sergio M. Delpiani^f^
-  - name: Juan Martín Díaz de Astarloa^e^
+  - name: Juan Martín Díaz de Astarloa^f^
   - name: Cintia Fraysse^a^
@@
   - code: 1
-    address: Centro Austral de Investigaciones Cientificas (CADIC-CONICET), Argentina
+    address: Centro Austral de Investigaciones Científicas (CADIC-CONICET), Ushuaia, Argentina
   - code: 2
-    address: Instituto Antartico Argentino (IAA), Argentina
+    address: Instituto Antártico Argentino (IAA), CABA, Argentina
   - code: 3
-    address: Instituto de Ciencias Polares, Ambiente y Recursos Naturales (ICPA), Universidad de Tierra del Fuego (UNTDF), Argentina
+    address: Instituto de Ciencias Polares, Ambiente y Recursos Naturales (ICPA), Universidad de Tierra del Fuego (UNTDF), Ushuaia, Argentina
   - code: 4
-    address: Facultad de Ciencias Exactas y Naturales, Universidad de Buenos Aires (UBA), Argentina
+    address: Facultad de Ciencias Exactas y Naturales, Universidad de Buenos Aires (UBA), CABA, Argentina
   - code: 5
-    address: Instituto de Biodiversidad y Biologia Experimental y Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, Argentina
+    address: Instituto de Biodiversidad y Biología Experimental y Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, CABA, Argentina
   - code: 6
-    address: Instituto de Investigaciones Marinas y Costeras (IIMYC), Universidad Nacional de Mar del Plata-CONICET, Argentina
+    address: Instituto de Investigaciones Marinas y Costeras (IIMYC), Universidad Nacional de Mar del Plata-CONICET, Mar del Plata, Argentina
   - code: 7
@@
   - code: 8
-    address: Instituto Nacional de Investigacion y Desarrollo Pesquero (INIDEP), Consejo Nacional de Investigaciones Cientificas y Tecnicas (CONICET), Argentina
+    address: Instituto Nacional de Investigación y Desarrollo Pesquero (INIDEP), Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET), Mar del Plata, Argentina
   - code: 9
-    address: Facultad de Ciencias Exactas, Fisicas y Naturales, Universidad Nacional de Cordoba (UNC), Argentina
+    address: Facultad de Ciencias Exactas, Físicas y Naturales, Universidad Nacional de Córdoba (UNC), Córdoba, Argentina
   - code: 10
-    address: Instituto de Diversidad y Ecologia Animal (IDEA-CONICET)
+    address: Instituto de Diversidad y Ecología Animal (IDEA-CONICET), Córdoba, Argentina
   - code: 11
-    address: Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina
-
+    address: Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, CABA, Argentina
 abstract: |
-  Globally, the total area of the world ocean designated under marine protection has increased in the recent decades.
-The majority of these Marine Protected Areas (MPAs) focus on the presence of particularly vulnerable, keystone, or charismatic species, large numbers of endemic species, and/or high biodiversity across taxonomic levels.
-In the sub-Antarctic region, the level of ocean protection is mainly associated to oceanic islands, except for the MPAs Namuncurá - Burdwood Bank I and II (MPA N-BB, ~53º–55ºS and ~56º–62ºW), which are associated to a submarine plateau and its southern adjacent deep slope region, respectively.
-Here, we present the first detailed analysis of the network of predator-prey interactions (food web) for the MPA N-BB ecosystem.
-We applied a network approach to characterise the food web in terms of complexity and structure, and identifying the species' role in such a framework.
-In terms of complexity, the MPA N-BB food web consisted of 1788 predator-prey interactions and 379 species, with a link density of 4.72 and a connectance of 0.01.
-In terms of structure, almost half of the consumers were omnivores (0.48), and the network displayed a small-world pattern.
-These findings suggest that the ecosystem might be vulnerable to external perturbations targeting highly connected species, although other properties might provide resilience and resistance, resulting in a rearranged structure that preserves its original functions.
-Furthermore, we identified several species as important in terms of different aspects of trophic structure and functioning, and response to perturbations.
-We suggest that generalist species, mainly fishes, play a crucial role in the ecosystem's bentho-pelagic coupling process and that other species, besides the longtail southern cod *Patagonotothen ramsayi* and the Fueguian sprat *Sprattus fuegensis*, should be considered as relevant energy transfers for the ecosystem.
-Finally, we argue that the diversity of species, including both the benthic and pelagic habitats, is responsible for seccuring the connectivity within the food web against perturbations, therefore contributing to the structure and stability of the ecosystem.
-
+  Abstract: The total area of the world ocean designated under marine protection has increased recently.
+Most Marine Protected Areas (MPAs) target vulnerable, keystone, charismatic and or endemic species.
+In the sub-Antarctic, ocean protection is associated to oceanic islands,except for MPAs Namuncurá - Burdwood Bank I and II (MPA N-BB, ~53º–55ºS and ~56º–62ºW), which are associated to a submarine plateau and its southern adjacent deep slope, respectively.
+Here, we present the first analysis of the network of predator-prey interactions for the MPA N-BB.
+We applied a network approach to characterise the complexity and structure of the food web, and identify the species' role in such a framework.
+The MPA N-BB food web consisted of 1788 interactions and 379 species, with a connectance of 0.01.
+Almost half of the consumers were omnivores (0.48), and the network displayed a small-world pattern.
+These suggest that the ecosystem might be vulnerable to perturbations targeting highly connected species, although other properties might provide resilience and resistance, resulting in a rearranged structure that preserves its original functions.
+Several species arose as important in terms of different aspects of trophic structure and functioning, and response to perturbations.
+Generalist species, mainly fishes, play a crucial role in the ecosystem's benthopelagic coupling and should be considered as relevant energy transfers for the ecosystem.
+We argue that the diversity of species, including both the benthic and pelagic habitats, is responsible for securing the connectivity within the food web against perturbations, therefore contributing to the structure and stability of the ecosystem.
 keywords: 
-  - Food web
+  - Food Web
   - Complexity
@@
   - Southwest Atlantic
-journal: "MEPS, Oikos, Ecological Applications, J of Applied Ecology (?)"
-date: "`r Sys.Date()`"
 classoption: preprint, 3p, authoryear
 bibliography: AMPBancoBurdwood.bib
-#nocite: '@*' cites all references in .bib file
 linenumbers: true
@@
 # Use a CSL with `citation_package = "default"`
-csl: "apa.csl"
+csl: "elsevier-harvard2.csl"
 output: 
   rticles::elsevier_article:
+    latex_engine: xelatex
     keep_tex: true
@@
 
-# References
+# Literature Cited

### 2023-07-17 MS_ToSubmit/MS_Burdwood_foodweb.tex
MEPS format

@@
 \usepackage[hyphens]{url}
-
-  \journal{MEPS, Oikos, Ecological Applications, J of Applied Ecology
-(?)} % Sets Journal name
 
@@
     \author[]{Tomás I. Marina\textsuperscript{a}%
-  %
+  \corref{cor1}%
   }
@@
 
-    \author[]{Juan Martín Díaz de Astarloa\textsuperscript{e}%
+    \author[]{Juan Martín Díaz de Astarloa\textsuperscript{f}%
   %
@@
 
-      \affiliation[1]{Centro Austral de Investigaciones Cientificas
-(CADIC-CONICET), Argentina}
-    \affiliation[2]{Instituto Antartico Argentino (IAA), Argentina}
+      \affiliation[1]{Centro Austral de Investigaciones Científicas
+(CADIC-CONICET), Ushuaia, Argentina}
+    \affiliation[2]{Instituto Antártico Argentino (IAA), CABA,
+Argentina}
     \affiliation[3]{Instituto de Ciencias Polares, Ambiente y Recursos
-Naturales (ICPA), Universidad de Tierra del Fuego (UNTDF), Argentina}
+Naturales (ICPA), Universidad de Tierra del Fuego (UNTDF), Ushuaia,
+Argentina}
     \affiliation[4]{Facultad de Ciencias Exactas y Naturales,
-Universidad de Buenos Aires (UBA), Argentina}
-    \affiliation[5]{Instituto de Biodiversidad y Biologia Experimental y
-Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, Argentina}
+Universidad de Buenos Aires (UBA), CABA, Argentina}
+    \affiliation[5]{Instituto de Biodiversidad y Biología Experimental y
+Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, CABA, Argentina}
     \affiliation[6]{Instituto de Investigaciones Marinas y Costeras
-(IIMYC), Universidad Nacional de Mar del Plata-CONICET, Argentina}
+(IIMYC), Universidad Nacional de Mar del Plata-CONICET, Mar del Plata,
+Argentina}
     \affiliation[7]{Wildlife Conservation Society, Argentina}
-    \affiliation[8]{Instituto Nacional de Investigacion y Desarrollo
-Pesquero (INIDEP), Consejo Nacional de Investigaciones Cientificas y
-Tecnicas (CONICET), Argentina}
-    \affiliation[9]{Facultad de Ciencias Exactas, Fisicas y Naturales,
-Universidad Nacional de Cordoba (UNC), Argentina}
-    \affiliation[10]{Instituto de Diversidad y Ecologia Animal
-(IDEA-CONICET)}
+    \affiliation[8]{Instituto Nacional de Investigación y Desarrollo
+Pesquero (INIDEP), Consejo Nacional de Investigaciones Científicas y
+Técnicas (CONICET), Mar del Plata, Argentina}
+    \affiliation[9]{Facultad de Ciencias Exactas, Físicas y Naturales,
+Universidad Nacional de Córdoba (UNC), Córdoba, Argentina}
+    \affiliation[10]{Instituto de Diversidad y Ecología Animal
+(IDEA-CONICET), Córdoba, Argentina}
     \affiliation[11]{Museo Argentino de Ciencias Naturales ``Bernardino
-Rivadavia'', Argentina}
+Rivadavia'', CABA, Argentina}
     \cortext[cor1]{Corresponding author}
@@
   \begin{abstract}
-  Globally, the total area of the world ocean designated under marine
-  protection has increased in the recent decades. The majority of these
-  Marine Protected Areas (MPAs) focus on the presence of particularly
-  vulnerable, keystone, or charismatic species, large numbers of endemic
-  species, and/or high biodiversity across taxonomic levels. In the
-  sub-Antarctic region, the level of ocean protection is mainly
-  associated to oceanic islands, except for the MPAs Namuncurá -
-  Burdwood Bank I and II (MPA N-BB, \textasciitilde53º--55ºS and
-  \textasciitilde56º--62ºW), which are associated to a submarine plateau
-  and its southern adjacent deep slope region, respectively. Here, we
-  present the first detailed analysis of the network of predator-prey
-  interactions (food web) for the MPA N-BB ecosystem. We applied a
-  network approach to characterise the food web in terms of complexity
-  and structure, and identifying the species' role in such a framework.
-  In terms of complexity, the MPA N-BB food web consisted of 1788
-  predator-prey interactions and 379 species, with a link density of
-  4.72 and a connectance of 0.01. In terms of structure, almost half of
-  the consumers were omnivores (0.48), and the network displayed a
-  small-world pattern. These findings suggest that the ecosystem might
-  be vulnerable to external perturbations targeting highly connected
-  species, although other properties might provide resilience and
-  resistance, resulting in a rearranged structure that preserves its
-  original functions. Furthermore, we identified several species as
-  important in terms of different aspects of trophic structure and
-  functioning, and response to perturbations. We suggest that generalist
-  species, mainly fishes, play a crucial role in the ecosystem's
-  bentho-pelagic coupling process and that other species, besides the
-  longtail southern cod \emph{Patagonotothen ramsayi} and the Fueguian
-  sprat \emph{Sprattus fuegensis}, should be considered as relevant
-  energy transfers for the ecosystem. Finally, we argue that the
-  diversity of species, including both the benthic and pelagic habitats,
-  is responsible for seccuring the connectivity within the food web
-  against perturbations, therefore contributing to the structure and
+  Abstract: The total area of the world ocean designated under marine
+  protection has increased recently. Most Marine Protected Areas (MPAs)
+  target vulnerable, keystone, charismatic and or endemic species. In
+  the sub-Antarctic, ocean protection is associated to oceanic
+  islands,except for MPAs Namuncurá - Burdwood Bank I and II (MPA N-BB,
+  \textasciitilde53º--55ºS and \textasciitilde56º--62ºW), which are
+  associated to a submarine plateau and its southern adjacent deep
+  slope, respectively. Here, we present the first analysis of the
+  network of predator-prey interactions for the MPA N-BB. We applied a
+  network approach to characterise the complexity and structure of the
+  food web, and identify the species' role in such a framework. The MPA
+  N-BB food web consisted of 1788 interactions and 379 species, with a
+  connectance of 0.01. Almost half of the consumers were omnivores
+  (0.48), and the network displayed a small-world pattern. These suggest
+  that the ecosystem might be vulnerable to perturbations targeting
+  highly connected species, although other properties might provide
+  resilience and resistance, resulting in a rearranged structure that
+  preserves its original functions. Several species arose as important
+  in terms of different aspects of trophic structure and functioning,
+  and response to perturbations. Generalist species, mainly fishes, play
+  a crucial role in the ecosystem's benthopelagic coupling and should be
+  considered as relevant energy transfers for the ecosystem. We argue
+  that the diversity of species, including both the benthic and pelagic
+  habitats, is responsible for securing the connectivity within the food
+  web against perturbations, therefore contributing to the structure and
   stability of the ecosystem.
@@
     \begin{keyword}
-    Food web \sep Complexity \sep Structure \sep Burdwood Bank \sep 
+    Food Web \sep Complexity \sep Structure \sep Burdwood Bank \sep 
     Southwest Atlantic
@@
 approximately 29,600,000 km\textsuperscript{2}, distributed across
-nearly 18,444 MPAs and covering 8.16\% of the ocean's surface (IUCN \&
+nearly 18,444 MPAs and covering 8.16\% of the ocean's surface (IUCN and
 UNEP-WCMC, 2023), and therefore approaching the 10\% goal of the
@@
 associated to oceanic islands, such as the South Georgias and South
-Sandwich, Bouvet, Prince Edward, and Macquarie islands (IUCN \&
+Sandwich, Bouvet, Prince Edward, and Macquarie islands (IUCN and
 UNEP-WCMC, 2023). Interestingly, the case of the MPAs Namuncurá -
@@
 Porifera, Bryozoa and Cnidaria) that considered with their environment
-meet the characteristics of vulnerable marine ecosystems (Schejter \&
+meet the characteristics of vulnerable marine ecosystems (Schejter and
 Albano, 2021), here defined as sites that present densities of Indicator
@@
 2009). Also, the benthic realm provides habitat to several small-sized
-species (López-Gappa et al., 2018; Martin Sirito, 2019; Schejter \&
+species (López-Gappa et al., 2018; Martin Sirito, 2019; Schejter and
 Bremec, 2019), and has an important role in the life history of fishes
@@
 circulation of the rich Malvinas (Falkland) current in the area
-(Guerrero et al., 1999; Piola \& Gordon, 1989) and the upwelling and
+(Guerrero et al., 1999; Piola and Gordon, 1989) and the upwelling and
 mixing phenomena (Matano et al., 2019). The input of nutrients from the
@@
 MPA N-BB ecosystem (Administración de Parques Nacionales, 2022; Guinder
-et al., 2020; Schejter et al., 2016, 2020), a better understanding of
+et al., 2020; Schejter et al., 2020, 2016), a better understanding of
 species interactions' complexity and structure is needed. This aspect
@@
 averaging 34 all year round and temperature ranging between 4 and 8ºC
-(Acha et al., 2004; Guerrero et al., 1999; Piola \& Falabella, 2009).
+(Acha et al., 2004; Guerrero et al., 1999; Piola and Falabella, 2009).
 The BB is surrounded by steep flanks of up to 4000 m depth through which
-strong currents circulate (Matano et al., 2019; Piola \& Gordon, 1989;
+strong currents circulate (Matano et al., 2019; Piola and Gordon, 1989;
 Reta, 2014). The N-BB II includes such a deep slope, protecting about
@@
 with the slope, entraining deep nutrient-rich waters into the photic
-layer (Matano et al., 2019; Piola \& Falabella, 2009) and resulting in a
-fairly homogeneous water column both spatially and temporally (Glorioso
-\& Flather, 1995; Guerrero et al., 1999; Matano et al., 2019).
+layer (Matano et al., 2019; Piola and Falabella, 2009) and resulting in
+a fairly homogeneous water column both spatially and temporally
+(Glorioso and Flather, 1995; Guerrero et al., 1999; Matano et al.,
+2019).
 
@@
 complexity and structure. For this, we calculated several network
-properties commonly used to describe empirical food webs (Pascual \&
+properties commonly used to describe empirical food webs (Pascual and
 Dunne, 2005): (1) number of species S; (2) number of interactions or
@@
 clustering coefficient (CC). The CPL is the average shortest path length
-between all pairs of nodes (Watts \& Strogatz, 1998). Here, CPL was
+between all pairs of nodes (Watts and Strogatz, 1998). Here, CPL was
 calculated as the average number of nodes in the shortest path
@@
 size (S) and number of interactions (L), following the method proposed
-by Marina, Saravia, et al. (2018).
+by Marina et al. (2018b).
 
@@
 frequently among themselves than with species that are not members of
-the module (Guimerà \& Nunes Amaral, 2005). Species can play different
+the module (Guimerà and Nunes Amaral, 2005). Species can play different
 roles in this respect, according to the pattern of interactions within
@@
 mainly between modules; and network connector, species with high
-connectivity between and within modules (Guimerà \& Nunes Amaral, 2005).
+connectivity between and within modules (Guimerà and Nunes Amaral,
+2005).
 
@@
 All network analyses and graphs were performed in R version 4.2.2 (Team,
-2022), mainly using `igraph' (Csardi \& Nepusz, 2006) and `multiweb'
+2022), mainly using `igraph' (Csardi and Nepusz, 2006) and `multiweb'
 (Saravia, 2022) packages. The source code and data are available at
@@
 network, but more importantly, it is an emergent property of pairwise
-species interactions (Poisot \& Gravel, 2014). It contains information
+species interactions (Poisot and Gravel, 2014). It contains information
 regarding how interactions within an ecological network are distributed
 and predicts reasonably well key dynamical properties of ecological
-networks (Dunne et al., 2002c). Complex marine food webs (i.e.~with more
-than 25 trophic species) show connectance values ranging from 0.01 -
-0.27 (Marina, Saravia, et al., 2018). In particular, food webs from
+networks (Jennifer A. Dunne et al., 2002a). Complex marine food webs
+(i.e.~with more than 25 trophic species) show connectance values ranging
+from 0.01 - 0.27 (Marina et al., 2018b). In particular, food webs from
 high-latitude regions tend to exhibit a connectance closer to the
@@
 (Smith-Ramesh et al., 2017) as well as species removal (e.g., local
-extinction) (Dunne et al., 2002a; Montoya \& Solé, 2003). The
-connectance of the food web of the MPA Namuncurá - Burdwood Bank (0.01)
-is one of the lowest reported so far for these regions; in particular,
-it appears to be much lower than that of Beagle Channel (0.05), an
-adjacent coastal area (Rodriguez et al., 2022).
+extinction) (Jennifer A. Dunne et al., 2002b; Montoya and Solé, 2003).
+The connectance of the food web of the MPA Namuncurá - Burdwood Bank
+(0.01) is one of the lowest reported so far for these regions; in
+particular, it appears to be much lower than that of Beagle Channel
+(0.05), an adjacent coastal area (Rodriguez et al., 2022).
 
@@
 predator, prey, and functional group. Such asymmetry is a well-known
-feature in empirical complex food webs in particular (Dunne et al.,
-2002c; Montoya \& Solé, 2003; Stouffer et al., 2005), and has received
-great attention in complex networks in general (Albert \& Barabási,
-2002; Newman, 2003). The degree distribution affects the resilience of
-complex food webs against random failures and pressure on a particular
-component of the web: food webs showing right-skewed distributions, like
-the one described in this study, are more vulnerable to the removal of
-the most connected species or hubs, with the potential of producing
-secondary extinctions and a catastrophic fragmentation of the network
-(Albert et al., 2000; Dunne et al., 2002a; Eklöf \& Ebenman, 2006).
+feature in empirical complex food webs in particular (Jennifer A. Dunne
+et al., 2002a; Montoya and Solé, 2003; Stouffer et al., 2005), and has
+received great attention in complex networks in general (Albert and
+Barabási, 2002; Newman, 2003). The degree distribution affects the
+resilience of complex food webs against random failures and pressure on
+a particular component of the web: food webs showing right-skewed
+distributions, like the one described in this study, are more vulnerable
+to the removal of the most connected species or hubs, with the potential
+of producing secondary extinctions and a catastrophic fragmentation of
+the network (Albert et al., 2000; Jennifer A. Dunne et al., 2002b; Eklöf
+and Ebenman, 2006).
 
@@
 marine food webs, mainly due to a low clustering coefficient compared to
-random networks (Dunne et al., 2002b; Marina, Saravia, et al., 2018).
+random networks (Jennifer A. Dunne et al., 2002c; Marina et al., 2018b).
 However, the food web of the MPA N-BB does display a small-world
@@
 recognizing species evolutionary paths and the vulnerability to
-perturbations (Montoya \& Solé, 2002). On the one hand, a short path
+perturbations (Montoya and Solé, 2002). On the one hand, a short path
 length implies a rapid spread of an impact (e.g., contaminant,
@@
 the same time, more potentially adaptive dynamics in the face of
-external perturbations (Montoya \& Solé, 2002; Williams et al., 2002).
+external perturbations (Montoya and Solé, 2002; Williams et al., 2002).
 On the other hand, a high clustering coefficient indicates the formation
@@
 (2018), highlighting the importance of omnivory in stabilizing food web
-dynamics (McCann \& Hastings, 1997; Neutel et al., 2002). The high
+dynamics (McCann and Hastings, 1997; Neutel et al., 2002). The high
 proportion of omnivory in the food web of the MPA N-BB suggests that the
 network might be robust to variations in prey abundances, which could
-increase food web's persistence and stability (Stouffer \& Bascompte,
+increase food web's persistence and stability (Stouffer and Bascompte,
 2010).
@@
 species, which in turn coincides to be commercial exploited species as
-fishes (Laptikhovsky et al., 2013; Martínez et al., 2015; Winter \&
+fishes (Laptikhovsky et al., 2013; Martínez et al., 2015; Winter and
 Arkhipkin, 2023). However, structural properties might provide
@@
 The degree distribution allows identifying important species, such as
-potential keystone species (i.e.~highly connected) (Dunne et al., 2002a;
-Solé \& Montoya, 2001), generalist/specialist species, and dominant food
-sources (Kondoh et al., 2010).
+potential keystone species (i.e.~highly connected) (Jennifer A. Dunne et
+al., 2002b; Solé and Montoya, 2001), generalist/specialist species, and
+dominant food sources (Kondoh et al., 2010).
 
@@
 other high-latitude marine systems of the Southwest Atlantic and
-Antarctic regions (Arkhipkin \& Laptikhovsky, 2013; Marina, Salinas, et
-al., 2018). The importance of these particular generalist species also
+Antarctic regions (Arkhipkin and Laptikhovsky, 2013; Marina et al.,
+2018a). The importance of these particular generalist species also
 arises since they feed in the benthic and pelagic habitats (Covatti Ale
@@
 components of the animal forest (Schejter et al., 2020), likely feeding
-on detritus that is constantly resuspended from the bottom (Martin \&
+on detritus that is constantly resuspended from the bottom (Martin and
 Flores Melo, 2021). Furthermore, we found that the second and third-most
@@
 significance of species in terms of community's functioning and overall
-stability (Cirtwill et al., 2018; Thébault \& Fontaine, 2010). We used a
-range of descriptors to characterise the dynamic and multifaceted nature
-of the species forming the MPA N-BB food web.
+stability (Cirtwill et al., 2018; Thébault and Fontaine, 2010). We used
+a range of descriptors to characterise the dynamic and multifaceted
+nature of the species forming the MPA N-BB food web.
 
@@
 and is proportional to how rapidly the indirect effects of the focal
-species can spread to other species in the network (Scotti \& Jordán,
+species can spread to other species in the network (Scotti and Jordán,
 2010). In the food web of the MPA N-BB, low-TL consumers arise as
@@
 part in more food chains and therefore affects more energy flows (Scotti
-\& Jordán, 2010). We have identified the longtail southern cod
+and Jordán, 2010). We have identified the longtail southern cod
 \emph{Patagonotothen ramsayi} as the most important species in this
@@
 (i.e.~abundance, biomass) to assess the species' role in the food web.
-Although there exists such data for some species (Schejter \& Albano,
+Although there exists such data for some species (Schejter and Albano,
 2021), it would not be possible to include it in the food web framework
@@
 and Brachiopoda that are highlighted by our species-level analyses
-though they have been found in low abundances in the area (Schejter \&
+though they have been found in low abundances in the area (Schejter and
 Albano, 2021).
@@
 MPA N-BB, we suggest that the future perspectives should: 1) incorporate
-spatial heterogeneity among MPA N-BB I and II (Schejter \& Albano,
+spatial heterogeneity among MPA N-BB I and II (Schejter and Albano,
 2021), which might lead to distinct food web properties in terms of
@@
 considering species and interaction traits (i.e.~body size, body mass,
-interaction dimensionality), and species density data (Nilsson \&
+interaction dimensionality), and species density data (Nilsson and
 McCann, 2016; Pawar et al., 2012).
@@
 
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
+\hypertarget{literature-cited}{%
+\section*{Literature Cited}\label{literature-cited}}
+\addcontentsline{toc}{section}{Literature Cited}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Acha2004}{}}%
-Acha, E. M., Mianzan, H. W., Guerrero, R. A., Favero, M., \& Bava, J.
-(2004). Marine fronts at the continental shelves of austral {South
-America}: {Physical} and ecological processes. \emph{Journal of Marine
-Systems}, \emph{44}(1), 83--105.
-\url{https://doi.org/10.1016/j.jmarsys.2003.09.005}
+Acha, E.M., Mianzan, H.W., Guerrero, R.A., Favero, M., Bava, J., 2004.
+\href{https://doi.org/10.1016/j.jmarsys.2003.09.005}{Marine fronts at
+the continental shelves of austral {South America}: {Physical} and
+ecological processes}. Journal of Marine Systems 44, 83--105.
 
 \leavevmode\vadjust pre{\hypertarget{ref-AdministraciondeParquesNacionales2022}{}}%
-Administración de Parques Nacionales. (2022). \emph{{Plan de gestión AMP
-Namuncurá Banco Burdwood}}. {Dirección Nacional de Áreas Marinas
-Protegidas (DNAMP), Argentina}.
+Administración de Parques Nacionales, 2022. {Plan de gestión AMP
+Namuncurá Banco Burdwood}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Albert2002}{}}%
-Albert, R., \& Barabási, A.-L. (2002). Statistical mechanics of complex
-networks. \emph{Reviews of Modern Physics}, \emph{74}(1), 47--97.
-\url{https://doi.org/10.1103/RevModPhys.74.47}
+Albert, R., Barabási, A.-L., 2002.
+\href{https://doi.org/10.1103/RevModPhys.74.47}{Statistical mechanics of
+complex networks}. Reviews of Modern Physics 74, 47--97.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Albert2000}{}}%
-Albert, R., Jeong, H., \& Barabási, A.-L. (2000). Error and attack
-tolerance of complex networks. \emph{Nature}, \emph{406}(6794),
-378--382. \url{https://doi.org/10.1038/35019019}
+Albert, R., Jeong, H., Barabási, A.-L., 2000.
+\href{https://doi.org/10.1038/35019019}{Error and attack tolerance of
+complex networks}. Nature 406, 378--382.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Arkhipkin2013}{}}%
-Arkhipkin, A., \& Laptikhovsky, V. (2013). From gelatinous to muscle
-food chain: Rock cod {Patagonotothen} ramsayi recycles coelenterate and
-tunicate resources on the {Patagonian Shelf}. \emph{Journal of Fish
-Biology}, \emph{83}(5), 1210--1220.
-\url{https://doi.org/10.1111/jfb.12217}
+Arkhipkin, A., Laptikhovsky, V., 2013.
+\href{https://doi.org/10.1111/jfb.12217}{From gelatinous to muscle food
+chain: Rock cod {Patagonotothen} ramsayi recycles coelenterate and
+tunicate resources on the {Patagonian Shelf}}. Journal of Fish Biology
+83, 1210--1220.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Bascompte2009}{}}%
-Bascompte, J. (2009). Disentangling the {Web} of {Life}. \emph{Science},
-\emph{325}(5939), 416--419.
-\url{https://doi.org/10.1126/science.1170749}
+Bascompte, J., 2009.
+\href{https://doi.org/10.1126/science.1170749}{Disentangling the {Web}
+of {Life}}. Science 325, 416--419.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Belleggia2008a}{}}%
-Belleggia, M., Mabragaña, E., Figueroa, D. E., Scenna, L. B., Barbini,
-S. A., \& Astarloa, J. M. D. de. (2008). Food habits of the broad nose
-skate, {\emph{Bathyraja}}{ \emph{Brachyurops}} ({Chondrichthyes},
-{Rajidae}), in the south-west {Atlantic}. \emph{Scientia Marina},
-\emph{72}(4), 701--710.
-\url{https://doi.org/10.3989/scimar.2008.72n4701}
+Belleggia, M., Mabragaña, E., Figueroa, D.E., Scenna, L.B., Barbini,
+S.A., Astarloa, J.M.D. de, 2008.
+\href{https://doi.org/10.3989/scimar.2008.72n4701}{Food habits of the
+broad nose skate, {\emph{Bathyraja}}{ \emph{Brachyurops}}
+({Chondrichthyes}, {Rajidae}), in the south-west {Atlantic}}. Scientia
+Marina 72, 701--710.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Bellegia2014}{}}%
-Bellegia, M., Scenna, L., Barbini, S. A., Figueroa, D. E., \& Díaz de
-Astarloa, J. M. (2014). \emph{The diets of four {Bathyraja} skates
-({Elasmobranchii}, {Arhynchobatidae}) from the {Southwest Atlantic}}.
-\url{https://doi.org/10.26028/CYBIUM/2014-384-012}
+Bellegia, M., Scenna, L., Barbini, S.A., Figueroa, D.E., Díaz de
+Astarloa, J.M., 2014.
+\href{https://doi.org/10.26028/CYBIUM/2014-384-012}{The diets of four
+{Bathyraja} skates ({Elasmobranchii}, {Arhynchobatidae}) from the
+{Southwest Atlantic}}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Bertola2018}{}}%
-Bértola, G., Olguín Salinas, H., \& Alder, V. A. (2018). Distribución
+Bértola, G., Olguín Salinas, H., Alder, V.A., 2018. Distribución
 espacial de {Rhizosolenia} crassa, \textquestiondown especie clave del
-banco burdwood? \emph{Libro de Resúmenes {X Jornadas Nacionales} de
-{Ciencias} Del {Mar}}.
+banco burdwood? In: Libro de Resúmenes {X Jornadas Nacionales} de
+{Ciencias} Del {Mar}. {Ciudad Autónoma de Buenos Aires, Argentina}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Bornatowski2017}{}}%
-Bornatowski, H., Barreto, R., Navia, A. F., \& de Amorim, A. F. (2017).
-Topological redundancy and {``small-world''} patterns in a food web in a
-subtropical ecosystem of {Brazil}. \emph{Marine Ecology}, \emph{38}(2),
-e12407. \url{https://doi.org/10.1111/maec.12407}
+Bornatowski, H., Barreto, R., Navia, A.F., de Amorim, A.F., 2017.
+\href{https://doi.org/10.1111/maec.12407}{Topological redundancy and
+{``small-world''} patterns in a food web in a subtropical ecosystem of
+{Brazil}}. Marine Ecology 38, e12407.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Borrvall2000}{}}%
-Borrvall, C., Ebenman, B., \& Tomas Jonsson, T. J. (2000). Biodiversity
-lessens the risk of cascading extinction in model food webs.
-\emph{Ecology Letters}, \emph{3}(2), 131--136.
-\url{https://doi.org/10.1046/j.1461-0248.2000.00130.x}
+Borrvall, C., Ebenman, B., Tomas Jonsson, T.J., 2000.
+\href{https://doi.org/10.1046/j.1461-0248.2000.00130.x}{Biodiversity
+lessens the risk of cascading extinction in model food webs}. Ecology
+Letters 3, 131--136.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Brose2019}{}}%
-Brose, U., Archambault, P., Barnes, A. D., Bersier, L.-F., Boy, T.,
+Brose, U., Archambault, P., Barnes, A.D., Bersier, L.-F., Boy, T.,
 Canning-Clode, J., Conti, E., Dias, M., Digel, C., Dissanayake, A.,
-Flores, A. A. V., Fussmann, K., Gauzens, B., Gray, C., Häussler, J.,
-Hirt, M. R., Jacob, U., Jochum, M., Kéfi, S., \ldots{} Iles, A. C.
-(2019). Predator traits determine food-web architecture across
-ecosystems. \emph{Nature Ecology \& Evolution}, \emph{3}(6), 919--927.
-\url{https://doi.org/10.1038/s41559-019-0899-x}
+Flores, A.A.V., Fussmann, K., Gauzens, B., Gray, C., Häussler, J., Hirt,
+M.R., Jacob, U., Jochum, M., Kéfi, S., McLaughlin, O., MacPherson, M.M.,
+Latz, E., Layer-Dobra, K., Legagneux, P., Li, Y., Madeira, C., Martinez,
+N.D., Mendonça, V., Mulder, C., Navarrete, S.A., O'Gorman, E.J., Ott,
+D., Paula, J., Perkins, D., Piechnik, D., Pokrovsky, I., Raffaelli, D.,
+Rall, B.C., Rosenbaum, B., Ryser, R., Silva, A., Sohlström, E.H.,
+Sokolova, N., Thompson, M.S.A., Thompson, R.M., Vermandele, F., Vinagre,
+C., Wang, S., Wefer, J.M., Williams, R.J., Wieters, E., Woodward, G.,
+Iles, A.C., 2019.
+\href{https://doi.org/10.1038/s41559-019-0899-x}{Predator traits
+determine food-web architecture across ecosystems}. Nature Ecology \&
+Evolution 3, 919--927.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Bruno2023a}{}}%
-Bruno, D. O., Valencia-Carrasco, C., Paci, M. A., Leonarduzzi, E.,
-Castro, L., Riccialdelli, L., Iachetti, C. M., Cadaillon, A., Giesecke,
-R., Schloss, I. R., Berghoff, C. F., Martín, J., Diez, M., Cabreira, A.,
-Presta, M. L., Capitanio, F. L., \& Boy, C. C. (2023). Spring plankton
+Bruno, D.O., Valencia-Carrasco, C., Paci, M.A., Leonarduzzi, E., Castro,
+L., Riccialdelli, L., Iachetti, C.M., Cadaillon, A., Giesecke, R.,
+Schloss, I.R., Berghoff, C.F., Martín, J., Diez, M., Cabreira, A.,
+Presta, M.L., Capitanio, F.L., Boy, C.C., 2023.
+\href{https://doi.org/10.1016/j.jmarsys.2023.103876}{Spring plankton
 energy content by size classes in two contrasting environments of a high
-latitude ecosystem: {The Beagle Channel}. \emph{Journal of Marine
-Systems}, \emph{240}, 103876.
-\url{https://doi.org/10.1016/j.jmarsys.2023.103876}
+latitude ecosystem: {The Beagle Channel}}. Journal of Marine Systems
+240, 103876.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Catry2004}{}}%
-Catry, P., Phillips, R. A., Phalan, B., Silk, J. R. D., \& Croxall, J.
-P. (2004). Foraging strategies of grey-headed albatrosses {Thalassarche}
-chrysostoma: Integration of movements, activity and feeding events.
-\emph{Marine Ecology Progress Series}, \emph{280}, 261--273.
-\url{https://doi.org/10.3354/meps280261}
+Catry, P., Phillips, R.A., Phalan, B., Silk, J.R.D., Croxall, J.P.,
+2004. \href{https://doi.org/10.3354/meps280261}{Foraging strategies of
+grey-headed albatrosses {Thalassarche} chrysostoma: Integration of
+movements, activity and feeding events}. Marine Ecology Progress Series
+280, 261--273.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Cirtwill2018}{}}%
-Cirtwill, A. R., Dalla Riva, G. V., Gaiarsa, M. P., Bimler, M. D.,
-Cagua, E. F., Coux, C., \& Dehling, D. M. (2018). A review of species
-role concepts in food webs. \emph{Food Webs}, \emph{16}, e00093.
-\url{https://doi.org/10.1016/j.fooweb.2018.e00093}
+Cirtwill, A.R., Dalla Riva, G.V., Gaiarsa, M.P., Bimler, M.D., Cagua,
+E.F., Coux, C., Dehling, D.M., 2018.
+\href{https://doi.org/10.1016/j.fooweb.2018.e00093}{A review of species
+role concepts in food webs}. Food Webs 16, e00093.
 
@@
 Commission for the Conservation of Antarctic Marine Living Resources
-(CCAMLR). (2009). \emph{Vulnerable {Marine Ecosystem} taxa
-identification guide}. {Commission for the Conservation of Antarctic
-Marine Living Resources}.
+(CCAMLR), 2009. Vulnerable {Marine Ecosystem} taxa identification guide.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Cordone2018}{}}%
-Cordone, G., Marina, T. I., Salinas, V., Doyle, S. R., Saravia, L. A.,
-\& Momo, F. R. (2018). Effects of macroalgae loss in an {Antarctic}
-marine food web: Applying extinction thresholds to food web studies.
-\emph{PeerJ}, \emph{6}, e5531. \url{https://doi.org/10.7717/peerj.5531}
+Cordone, G., Marina, T.I., Salinas, V., Doyle, S.R., Saravia, L.A.,
+Momo, F.R., 2018. \href{https://doi.org/10.7717/peerj.5531}{Effects of
+macroalgae loss in an {Antarctic} marine food web: Applying extinction
+thresholds to food web studies}. PeerJ 6, e5531.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Cordone2020}{}}%
-Cordone, G., Salinas, V., Marina, T. I., Doyle, S. R., Pasotti, F.,
-Saravia, L. A., \& Momo, F. R. (2020). Green vs brown food web:
-{Effects} of habitat type on multidimensional stability proxies for a
-highly-resolved {Antarctic} food web. \emph{Food Webs}, \emph{25},
-e00166. \url{https://doi.org/10.1016/j.fooweb.2020.e00166}
+Cordone, G., Salinas, V., Marina, T.I., Doyle, S.R., Pasotti, F.,
+Saravia, L.A., Momo, F.R., 2020.
+\href{https://doi.org/10.1016/j.fooweb.2020.e00166}{Green vs brown food
+web: {Effects} of habitat type on multidimensional stability proxies for
+a highly-resolved {Antarctic} food web}. Food Webs 25, e00166.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Cossi2021}{}}%
-Cossi, P. F., Ojeda, M., Chiesa, I. L., Rimondino, G. N., Fraysse, C.,
-Calcagno, J., \& Pérez, A. F. (2021). First evidence of microplastics in
-the {Marine Protected Area Namuncurá} at {Burdwood Bank}, {Argentina}: A
-study on {Henricia} obesa and {Odontaster} penicillatus
-({Echinodermata}: {Asteroidea}). \emph{Polar Biology}, \emph{44}(12),
-2277--2287. \url{https://doi.org/10.1007/s00300-021-02959-5}
+Cossi, P.F., Ojeda, M., Chiesa, I.L., Rimondino, G.N., Fraysse, C.,
+Calcagno, J., Pérez, A.F., 2021.
+\href{https://doi.org/10.1007/s00300-021-02959-5}{First evidence of
+microplastics in the {Marine Protected Area Namuncurá} at {Burdwood
+Bank}, {Argentina}: A study on {Henricia} obesa and {Odontaster}
+penicillatus ({Echinodermata}: {Asteroidea})}. Polar Biology 44,
+2277--2287.
 
 \leavevmode\vadjust pre{\hypertarget{ref-CovattiAle2022}{}}%
-Covatti Ale, M., Fischer, L., Deli Antoni, M., Diaz de Astarloa, J. M.,
-\& Delpiani, G. (2022). Trophic ecology of the yellowfin notothen,
-{Patagonotothen} guntheri ({Norman}, 1937) at the {Marine Protected Area
-Namuncurá-Burdwood Bank}, {Argentina}. \emph{Polar Biology},
-\emph{45}(4), 549--558. \url{https://doi.org/10.1007/s00300-022-03011-w}
+Covatti Ale, M., Fischer, L., Deli Antoni, M., Diaz de Astarloa, J.M.,
+Delpiani, G., 2022.
+\href{https://doi.org/10.1007/s00300-022-03011-w}{Trophic ecology of the
+yellowfin notothen, {Patagonotothen} guntheri ({Norman}, 1937) at the
+{Marine Protected Area Namuncurá-Burdwood Bank}, {Argentina}}. Polar
+Biology 45, 549--558.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Csardi2006}{}}%
-Csardi, \& Nepusz. (2006). \emph{The igraph software package for complex
-network research}.
+Csardi, Nepusz, 2006. The igraph software package for complex network
+research.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Cury2000}{}}%
-Cury, P., Bakun, A., Crawford, R. J. M., Jarre, A., Quiñones, R. A.,
-Shannon, L. J., \& Verheye, H. M. (2000). Small pelagics in upwelling
-systems: Patterns of interaction and structural changes in
-{``wasp-waist''} ecosystems. \emph{ICES Journal of Marine Science},
-\emph{57}(3), 603--618. \url{https://doi.org/10.1006/jmsc.2000.0712}
+Cury, P., Bakun, A., Crawford, R.J.M., Jarre, A., Quiñones, R.A.,
+Shannon, L.J., Verheye, H.M., 2000.
+\href{https://doi.org/10.1006/jmsc.2000.0712}{Small pelagics in
+upwelling systems: Patterns of interaction and structural changes in
+{``wasp-waist''} ecosystems}. ICES Journal of Marine Science 57,
+603--618.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Day2013}{}}%
-Day, R. H., Weingartner, T. J., Hopcroft, R. R., Aerts, L. A. M.,
-Blanchard, A. L., Gall, A. E., Gallaway, B. J., Hannay, D. E., Holladay,
-B. A., Mathis, J. T., Norcross, B. L., Questel, J. M., \& Wisdom, S. S.
-(2013). The offshore northeastern {Chukchi Sea}, {Alaska}: {A} complex
-high-latitude ecosystem. \emph{Continental Shelf Research}, \emph{67},
-147--165. \url{https://doi.org/10.1016/j.csr.2013.02.002}
+Day, R.H., Weingartner, T.J., Hopcroft, R.R., Aerts, L.A.M., Blanchard,
+A.L., Gall, A.E., Gallaway, B.J., Hannay, D.E., Holladay, B.A., Mathis,
+J.T., Norcross, B.L., Questel, J.M., Wisdom, S.S., 2013.
+\href{https://doi.org/10.1016/j.csr.2013.02.002}{The offshore
+northeastern {Chukchi Sea}, {Alaska}: {A} complex high-latitude
+ecosystem}. Continental Shelf Research, Seasonal and interannual
+dynamics of the northeastern {Chukchi Sea Ecosystem} 67, 147--165.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Dellabianca2023}{}}%
-Dellabianca, N. A., Torres, M. A., Ordoñez, C., Fioramonti, N., \& Raya
-Rey, A. (2023). Marine protected areas in the southern south-west
-{Atlantic}: {Insights} from marine top predator communities.
-\emph{Aquatic Conservation: Marine and Freshwater Ecosystems},
-\emph{33}(5), 472--487. \url{https://doi.org/10.1002/aqc.3935}
+Dellabianca, N.A., Torres, M.A., Ordoñez, C., Fioramonti, N., Raya Rey,
+A., 2023. \href{https://doi.org/10.1002/aqc.3935}{Marine protected areas
+in the southern south-west {Atlantic}: {Insights} from marine top
+predator communities}. Aquatic Conservation: Marine and Freshwater
+Ecosystems 33, 472--487.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Delpiani2020}{}}%
-Delpiani, S. M., Bruno, D. O., Vazquez, D. M., Llompart, F., Delpiani,
-G. E., Fernández, D. A., Rosso, J. J., Mabragaña, E., \& Díaz de
-Astarloa, J. M. (2020). Structure and distribution of fish assemblages
-at {Burdwood Bank}, the first {Sub-Antarctic Marine Protected Area}
-{``{Namuncurá}''} in {Argentina} ({Southwestern Atlantic Ocean}).
-\emph{Polar Biology}, \emph{43}(11), 1783--1793.
-\url{https://doi.org/10.1007/s00300-020-02744-w}
+Delpiani, S.M., Bruno, D.O., Vazquez, D.M., Llompart, F., Delpiani,
+G.E., Fernández, D.A., Rosso, J.J., Mabragaña, E., Díaz de Astarloa,
+J.M., 2020. \href{https://doi.org/10.1007/s00300-020-02744-w}{Structure
+and distribution of fish assemblages at {Burdwood Bank}, the first
+{Sub-Antarctic Marine Protected Area} {``{Namuncurá}''} in {Argentina}
+({Southwestern Atlantic Ocean})}. Polar Biology 43, 1783--1793.
 
 \leavevmode\vadjust pre{\hypertarget{ref-DiMauro2022}{}}%
-Di Mauro, R., Castillo, S., Pérez, A., Iachetti, C. M., Silva, L.,
-Tomba, J. P., \& Chiesa, I. L. (2022). Anthropogenic microfibers are
-highly abundant at the {Burdwood Bank} seamount, a protected
-sub-{Antarctic} environment in the {Southwestern Atlantic Ocean}.
-\emph{Environmental Pollution}, \emph{306}, 119364.
-\url{https://doi.org/10.1016/j.envpol.2022.119364}
+Di Mauro, R., Castillo, S., Pérez, A., Iachetti, C.M., Silva, L., Tomba,
+J.P., Chiesa, I.L., 2022.
+\href{https://doi.org/10.1016/j.envpol.2022.119364}{Anthropogenic
+microfibers are highly abundant at the {Burdwood Bank} seamount, a
+protected sub-{Antarctic} environment in the {Southwestern Atlantic
+Ocean}}. Environmental Pollution 306, 119364.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Dormann2017}{}}%
-Dormann, C. F., Fründ, J., \& Schaefer, H. M. (2017). Identifying
+Dormann, C.F., Fründ, J., Schaefer, H.M., 2017.
+\href{https://doi.org/10.1146/annurev-ecolsys-110316-022928}{Identifying
 {Causes} of {Patterns} in {Ecological Networks}: {Opportunities} and
-{Limitations}. \emph{Annual Review of Ecology, Evolution, and
-Systematics}, \emph{48}, 559--584.
-\url{https://doi.org/10.1146/annurev-ecolsys-110316-022928}
+{Limitations}}. Annual Review of Ecology, Evolution, and Systematics 48,
+559--584.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Dunne2002}{}}%
-Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002a). Network
+Dunne, Jennifer A., Williams, R.J., Martinez, N.D., 2002b.
+\href{https://doi.org/10.1046/j.1461-0248.2002.00354.x}{Network
 structure and biodiversity loss in food webs: Robustness increases with
-connectance. \emph{Ecology Letters}, \emph{5}(4), 558--567.
-\url{https://doi.org/10.1046/j.1461-0248.2002.00354.x}
+connectance}. Ecology Letters 5, 558--567.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002a}{}}%
+Dunne, Jennifer A., Williams, R.J., Martinez, N.D., 2002a.
+\href{https://doi.org/10.1073/pnas.192407699}{Food-web structure and
+network theory: {The} role of connectance and size}. Proceedings of the
+National Academy of Sciences 99, 12917--12922.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Dunne2002b}{}}%
-Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002b). \emph{Small
+Dunne, Jennifer A., Williams, R.J., Martinez, N.D., 2002c. Small
 {Networks} but not {Small Worlds}: {Unique Aspects} of {Food Web
-Structure}}. {Santa Fe Institute}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002a}{}}%
-Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002c). Food-web
-structure and network theory: {The} role of connectance and size.
-\emph{Proceedings of the National Academy of Sciences}, \emph{99}(20),
-12917--12922. \url{https://doi.org/10.1073/pnas.192407699}
+Structure}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Eklof2006}{}}%
-Eklöf, A., \& Ebenman, B. (2006). Species loss and secondary extinctions
-in simple and complex model communities. \emph{Journal of Animal
-Ecology}, \emph{75}(1), 239--246.
-\url{https://doi.org/10.1111/j.1365-2656.2006.01041.x}
+Eklöf, A., Ebenman, B., 2006.
+\href{https://doi.org/10.1111/j.1365-2656.2006.01041.x}{Species loss and
+secondary extinctions in simple and complex model communities}. Journal
+of Animal Ecology 75, 239--246.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Fagan1997}{}}%
-Fagan, W. F. (1997). Omnivory as a {Stabilizing Feature} of {Natural
-Communities}. \emph{The American Naturalist}, \emph{150}(5), 554--567.
-\url{https://doi.org/10.1086/286081}
+Fagan, W.F., 1997. \href{https://doi.org/10.1086/286081}{Omnivory as a
+{Stabilizing Feature} of {Natural Communities}}. The American Naturalist
+150, 554--567.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Falabella2017}{}}%
-Falabella, V. (2017). \emph{Área {Marina Protegida Namuncurá-Banco
-Burdwood}. {Contribuciones} para la línea de base y el plan de manejo}.
+Falabella, V., 2017. Área {Marina Protegida Namuncurá-Banco Burdwood}.
+{Contribuciones} para la línea de base y el plan de manejo.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Fioramonti2022}{}}%
-Fioramonti, N. E., Ribeiro Guevara, S., Becker, Y. A., \& Riccialdelli,
-L. (2022). Mercury transfer in coastal and oceanic food webs from the
-{Southwest Atlantic Ocean}. \emph{Marine Pollution Bulletin},
-\emph{175}, 113365.
-\url{https://doi.org/10.1016/j.marpolbul.2022.113365}
+Fioramonti, N.E., Ribeiro Guevara, S., Becker, Y.A., Riccialdelli, L.,
+2022. \href{https://doi.org/10.1016/j.marpolbul.2022.113365}{Mercury
+transfer in coastal and oceanic food webs from the {Southwest Atlantic
+Ocean}}. Marine Pollution Bulletin 175, 113365.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Fischer2022}{}}%
-Fischer, L., Covatti Ale, M., Deli Antoni, M., Díaz de Astarloa, J. M.,
-\& Delpiani, G. (2022). Feeding ecology of the longtail southern cod,
-{Patagonotothen} ramsayi ({Regan}, 1913) ({Notothenioidei}) in the
-{Marine Protected Area Namuncurá-Burdwood Bank}, {Argentina}.
-\emph{Polar Biology}, \emph{45}(9), 1483--1494.
-\url{https://doi.org/10.1007/s00300-022-03082-9}
+Fischer, L., Covatti Ale, M., Deli Antoni, M., Díaz de Astarloa, J.M.,
+Delpiani, G., 2022.
+\href{https://doi.org/10.1007/s00300-022-03082-9}{Feeding ecology of the
+longtail southern cod, {Patagonotothen} ramsayi ({Regan}, 1913)
+({Notothenioidei}) in the {Marine Protected Area Namuncurá-Burdwood
+Bank}, {Argentina}}. Polar Biology 45, 1483--1494.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Florencia2023}{}}%
-Florencia, M., Vazquez, D. M., Gabbanelli, V., Díaz de Astarloa, J. M.,
-\& Mabragaña, E. (2023). Chondrichthyans from the southern tip of {South
-America} with emphasis on the marine protected area {Namuncurá-Burdwood
-Bank}: Exploring egg nursery grounds. \emph{Polar Biology}.
-\url{https://doi.org/10.1007/s00300-023-03128-6}
+Florencia, M., Vazquez, D.M., Gabbanelli, V., Díaz de Astarloa, J.M.,
+Mabragaña, E., 2023.
+\href{https://doi.org/10.1007/s00300-023-03128-6}{Chondrichthyans from
+the southern tip of {South America} with emphasis on the marine
+protected area {Namuncurá-Burdwood Bank}: Exploring egg nursery
+grounds}. Polar Biology.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Funes2022}{}}%
-Funes, M., Saravia, L. A., Cordone, G., Iribarne, O. O., \& Galván, D.
-E. (2022). Network analysis suggests changes in food web stability
-produced by bottom trawl fishery in {Patagonia}. \emph{Scientific
-Reports}, \emph{12}(1), 10876.
-\url{https://doi.org/10.1038/s41598-022-14363-y}
+Funes, M., Saravia, L.A., Cordone, G., Iribarne, O.O., Galván, D.E.,
+2022. \href{https://doi.org/10.1038/s41598-022-14363-y}{Network analysis
+suggests changes in food web stability produced by bottom trawl fishery
+in {Patagonia}}. Scientific Reports 12, 10876.
+
+\leavevmode\vadjust pre{\hypertarget{ref-GarciaAlonso2018}{}}%
+García Alonso, V.A., Brown, D., Martín, J., Pájaro, M., Capitanio, F.L.,
+2018. \href{https://doi.org/10.1007/s00300-018-2352-z}{Seasonal patterns
+of {Patagonian} sprat {Sprattus} fuegensis early life stages in an open
+sea {Sub-Antarctic Marine Protected Area}}. Polar Biology 41,
+2167--2179.
 
 \leavevmode\vadjust pre{\hypertarget{ref-GarciaAlonso2020}{}}%
-García Alonso, V. A., Brown, D. R., Pájaro, M., \& Capitanio, F. L.
-(2020). Growing {Up Down South}: {Spatial} and {Temporal Variability} in
-{Early Growth} of {Fuegian Sprat Sprattus} fuegensis {From} the
-{Southwest Atlantic Ocean}. \emph{Frontiers in Marine Science},
-\emph{7}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-GarciaAlonso2018}{}}%
-García Alonso, V. A., Brown, D., Martín, J., Pájaro, M., \& Capitanio,
-F. L. (2018). Seasonal patterns of {Patagonian} sprat {Sprattus}
-fuegensis early life stages in an open sea {Sub-Antarctic Marine
-Protected Area}. \emph{Polar Biology}, \emph{41}(11), 2167--2179.
-\url{https://doi.org/10.1007/s00300-018-2352-z}
+García Alonso, V.A., Brown, D.R., Pájaro, M., Capitanio, F.L., 2020.
+Growing {Up Down South}: {Spatial} and {Temporal Variability} in {Early
+Growth} of {Fuegian Sprat Sprattus} fuegensis {From} the {Southwest
+Atlantic Ocean}. Frontiers in Marine Science 7.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Gauzens2013}{}}%
-Gauzens, B., Legendre, S., Lazzaro, X., \& Lacroix, G. (2013). Food-web
-aggregation, methodological and functional issues. \emph{Oikos},
-\emph{122}(11), 1606--1615.
-\url{https://doi.org/10.1111/j.1600-0706.2013.00266.x}
+Gauzens, B., Legendre, S., Lazzaro, X., Lacroix, G., 2013.
+\href{https://doi.org/10.1111/j.1600-0706.2013.00266.x}{Food-web
+aggregation, methodological and functional issues}. Oikos 122,
+1606--1615.
 
@@
 Giesecke, R., Martín, J., Piñones, A., Höfer, J., Garcés-Vargas, J.,
-Flores-Melo, X., Alarcón, E., Durrieu de Madron, X., Bourrin, F., \&
-González, H. E. (2021). General {Hydrography} of the {Beagle Channel}, a
+Flores-Melo, X., Alarcón, E., Durrieu de Madron, X., Bourrin, F.,
+González, H.E., 2021. General {Hydrography} of the {Beagle Channel}, a
 {Subantarctic Interoceanic Passage} at the {Southern Tip} of {South
-America}. \emph{Frontiers in Marine Science}, \emph{8}.
+America}. Frontiers in Marine Science 8.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Glorioso1995}{}}%
-Glorioso, P. D., \& Flather, R. A. (1995). A barotropic model of the
-currents off {SE South America}. \emph{Journal of Geophysical Research:
-Oceans}, \emph{100}(C7), 13427--13440.
-\url{https://doi.org/10.1029/95JC00942}
+Glorioso, P.D., Flather, R.A., 1995.
+\href{https://doi.org/10.1029/95JC00942}{A barotropic model of the
+currents off {SE South America}}. Journal of Geophysical Research:
+Oceans 100, 13427--13440.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Godoy2018}{}}%
-Godoy, O., Bartomeus, I., Rohr, R. P., \& Saavedra, S. (2018). Towards
-the {Integration} of {Niche} and {Network Theories}. \emph{Trends in
-Ecology \& Evolution}, \emph{33}(4), 287--300.
-\url{https://doi.org/10.1016/j.tree.2018.01.007}
+Godoy, O., Bartomeus, I., Rohr, R.P., Saavedra, S., 2018.
+\href{https://doi.org/10.1016/j.tree.2018.01.007}{Towards the
+{Integration} of {Niche} and {Network Theories}}. Trends in Ecology \&
+Evolution 33, 287--300.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Guerrero1999}{}}%
-Guerrero, R. A., Baldoni, A. G., \& Benavides, H. R. (1999).
-\emph{Oceanographic conditions at the southern end of the argentine
-continental slope}.
-https://doi.org/\url{http://10.0.64.26/handle/inidep/247}
+Guerrero, R.A., Baldoni, A.G., Benavides, H.R., 1999.
+\href{http://10.0.64.26/handle/inidep/247}{Oceanographic conditions at
+the southern end of the argentine continental slope}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Guimera2005}{}}%
-Guimerà, R., \& Nunes Amaral, L. A. (2005). Functional cartography of
-complex metabolic networks. \emph{Nature}, \emph{433}(7028), 895--900.
-\url{https://doi.org/10.1038/nature03288}
+Guimerà, R., Nunes Amaral, L.A., 2005.
+\href{https://doi.org/10.1038/nature03288}{Functional cartography of
+complex metabolic networks}. Nature 433, 895--900.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Guinder2020}{}}%
-Guinder, V. A., Malits, A., Ferronato, C., Krock, B., Garzón-Cardona,
-J., \& Martínez, A. (2020). Microbial plankton configuration in the
-epipelagic realm from the {Beagle Channel} to the {Burdwood Bank}, a
-{Marine Protected Area} in {Sub-Antarctic} waters. \emph{PLOS ONE},
-\emph{15}(5), e0233156.
-\url{https://doi.org/10.1371/journal.pone.0233156}
+Guinder, V.A., Malits, A., Ferronato, C., Krock, B., Garzón-Cardona, J.,
+Martínez, A., 2020.
+\href{https://doi.org/10.1371/journal.pone.0233156}{Microbial plankton
+configuration in the epipelagic realm from the {Beagle Channel} to the
+{Burdwood Bank}, a {Marine Protected Area} in {Sub-Antarctic} waters}.
+PLOS ONE 15, e0233156.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Heer2020}{}}%
-Heer, H., Streib, L., Schäfer, R. B., \& Ruzika, S. (2020). Maximising
-the clustering coefficient of networks and the effects on habitat
-network robustness. \emph{PLOS ONE}, \emph{15}(10), e0240940.
-\url{https://doi.org/10.1371/journal.pone.0240940}
+Heer, H., Streib, L., Schäfer, R.B., Ruzika, S., 2020.
+\href{https://doi.org/10.1371/journal.pone.0240940}{Maximising the
+clustering coefficient of networks and the effects on habitat network
+robustness}. PLOS ONE 15, e0240940.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Hogg2016}{}}%
-Hogg, O. T., Huvenne, V. A. I., Griffiths, H. J., Dorschel, B., \&
-Linse, K. (2016). Landscape mapping at sub-{Antarctic South Georgia}
-provides a protocol for underpinning large-scale marine protected areas.
-\emph{Scientific Reports}, \emph{6}(1), 33163.
-\url{https://doi.org/10.1038/srep33163}
+Hogg, O.T., Huvenne, V.A.I., Griffiths, H.J., Dorschel, B., Linse, K.,
+2016. \href{https://doi.org/10.1038/srep33163}{Landscape mapping at
+sub-{Antarctic South Georgia} provides a protocol for underpinning
+large-scale marine protected areas}. Scientific Reports 6, 33163.
 
 \leavevmode\vadjust pre{\hypertarget{ref-IUCN2023}{}}%
-IUCN, \& UNEP-WCMC. (2023). \emph{The world database on protected areas
-({WDPA})}. {Protected Planet}.
+IUCN, UNEP-WCMC, 2023. The world database on protected areas ({WDPA}).
 
 \leavevmode\vadjust pre{\hypertarget{ref-Kadoya2018}{}}%
-Kadoya, T., Gellner, G., \& McCann, K. S. (2018). Potential oscillators
-and keystone modules in food webs. \emph{Ecology Letters}, \emph{21}(9),
-1330--1340. \url{https://doi.org/10.1111/ele.13099}
+Kadoya, T., Gellner, G., McCann, K.S., 2018.
+\href{https://doi.org/10.1111/ele.13099}{Potential oscillators and
+keystone modules in food webs}. Ecology Letters 21, 1330--1340.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Kondoh2010}{}}%
-Kondoh, M., Kato, S., \& Sakato, Y. (2010). Food webs are built up with
-nested subwebs. \emph{Ecology}, \emph{91}(11), 3123--3130.
-\url{https://doi.org/10.1890/09-2219.1}
+Kondoh, M., Kato, S., Sakato, Y., 2010.
+\href{https://doi.org/10.1890/09-2219.1}{Food webs are built up with
+nested subwebs}. Ecology 91, 3123--3130.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Kortsch2019}{}}%
-Kortsch, S., Primicerio, R., Aschan, M., Lind, S., Dolgov, A. V., \&
-Planque, B. (2019). Food-web structure varies along environmental
-gradients in a high-latitude marine ecosystem. \emph{Ecography},
-\emph{42}(2), 295--308. \url{https://doi.org/10.1111/ecog.03443}
+Kortsch, S., Primicerio, R., Aschan, M., Lind, S., Dolgov, A.V.,
+Planque, B., 2019. \href{https://doi.org/10.1111/ecog.03443}{Food-web
+structure varies along environmental gradients in a high-latitude marine
+ecosystem}. Ecography 42, 295--308.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Kortsch2015}{}}%
-Kortsch, S., Primicerio, R., Fossheim, M., Dolgov, A. V., \& Aschan, M.
-(2015). Climate change alters the structure of arctic marine food webs
-due to poleward shifts of boreal generalists. \emph{Proceedings of the
-Royal Society B: Biological Sciences}, \emph{282}(1814), 20151546.
-\url{https://doi.org/10.1098/rspb.2015.1546}
+Kortsch, S., Primicerio, R., Fossheim, M., Dolgov, A.V., Aschan, M.,
+2015. \href{https://doi.org/10.1098/rspb.2015.1546}{Climate change
+alters the structure of arctic marine food webs due to poleward shifts
+of boreal generalists}. Proceedings of the Royal Society B: Biological
+Sciences 282, 20151546.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Lai2012}{}}%
-Lai, S.-M., Liu, W.-C., \& Jordán, F. (2012). On the centrality and
-uniqueness of species from the network perspective. \emph{Biology
-Letters}, \emph{8}(4), 570--573.
-\url{https://doi.org/10.1098/rsbl.2011.1167}
+Lai, S.-M., Liu, W.-C., Jordán, F., 2012.
+\href{https://doi.org/10.1098/rsbl.2011.1167}{On the centrality and
+uniqueness of species from the network perspective}. Biology Letters 8,
+570--573.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Laptikhovsky2013}{}}%
-Laptikhovsky, V., Arkhipkin, A., \& Brickle, P. (2013). From small
-bycatch to main commercial species: {Explosion} of stocks of rock cod
-{Patagonotothen} ramsayi ({Regan}) in the {Southwest Atlantic}.
-\emph{Fisheries Research}, \emph{147}, 399--403.
-\url{https://doi.org/10.1016/j.fishres.2013.05.006}
+Laptikhovsky, V., Arkhipkin, A., Brickle, P., 2013.
+\href{https://doi.org/10.1016/j.fishres.2013.05.006}{From small bycatch
+to main commercial species: {Explosion} of stocks of rock cod
+{Patagonotothen} ramsayi ({Regan}) in the {Southwest Atlantic}}.
+Fisheries Research 147, 399--403.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Latorre2023}{}}%
-Latorre, M. P., Berghoff, C. F., Giesecke, R., Malits, A., Pizarro, G.,
-Iachetti, C. M., Martin, J., Flores-Melo, X., Gil, M. N., Iriarte, J.
-L., \& Schloss, I. R. (2023). Plankton metabolic balance in the eastern
-{Beagle Channel} during spring. \emph{Journal of Marine Systems},
-\emph{240}, 103882. \url{https://doi.org/10.1016/j.jmarsys.2023.103882}
+Latorre, M.P., Berghoff, C.F., Giesecke, R., Malits, A., Pizarro, G.,
+Iachetti, C.M., Martin, J., Flores-Melo, X., Gil, M.N., Iriarte, J.L.,
+Schloss, I.R., 2023.
+\href{https://doi.org/10.1016/j.jmarsys.2023.103882}{Plankton metabolic
+balance in the eastern {Beagle Channel} during spring}. Journal of
+Marine Systems 240, 103882.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Lopez-Gappa2018}{}}%
-López-Gappa, J., Liuzzi, M. G., \& Zelaya, D. G. (2018). A new genus and
-species of cheilostome bryozoan associated with hermit crabs in the
-subantarctic {Southwest Atlantic}. \emph{Polar Biology}, \emph{41}(4),
-733--741. \url{https://doi.org/10.1007/s00300-017-2234-9}
+López-Gappa, J., Liuzzi, M.G., Zelaya, D.G., 2018.
+\href{https://doi.org/10.1007/s00300-017-2234-9}{A new genus and species
+of cheilostome bryozoan associated with hermit crabs in the subantarctic
+{Southwest Atlantic}}. Polar Biology 41, 733--741.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Marina2018}{}}%
-Marina, T. I., Salinas, V., Cordone, G., Campana, G., Moreira, E.,
+Marina, T.I., Salinas, V., Cordone, Georgina, Campana, G., Moreira, E.,
 Deregibus, D., Torre, L., Sahade, R., Tatián, M., Barrera Oro, E., De
-Troch, M., Doyle, S., Quartino, M. L., Saravia, L. A., \& Momo, F. R.
-(2018). The {Food Web} of {Potter Cove} ({Antarctica}): Complexity,
-structure and function. \emph{Estuarine, Coastal and Shelf Science},
-\emph{200}, 141--151. \url{https://doi.org/10.1016/j.ecss.2017.10.015}
+Troch, M., Doyle, S., Quartino, M.L., Saravia, L.A., Momo, F.R., 2018a.
+\href{https://doi.org/10.1016/j.ecss.2017.10.015}{The {Food Web} of
+{Potter Cove} ({Antarctica}): Complexity, structure and function}.
+Estuarine, Coastal and Shelf Science 200, 141--151.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Marina2018a}{}}%
-Marina, T. I., Saravia, L. A., Cordone, G., Salinas, V., Doyle, S. R.,
-\& Momo, F. R. (2018). Architecture of marine food webs: {To} be or not
-be a {``small-world.''} \emph{PLOS ONE}, \emph{13}(5), e0198217.
-\url{https://doi.org/10.1371/journal.pone.0198217}
+Marina, T.I., Saravia, L.A., Cordone, G., Salinas, V., Doyle, S.R.,
+Momo, F.R., 2018b.
+\href{https://doi.org/10.1371/journal.pone.0198217}{Architecture of
+marine food webs: {To} be or not be a {``small-world''}}. PLOS ONE 13,
+e0198217.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Marina2023}{}}%
-Marina, T. I., Saravia, L. A., \& Kortsch, S. (2023). \emph{New insights
-into the {Weddell Sea} ecosystem applying a quantitative network
-approach}. {EGUsphere preprint}.
-\url{https://doi.org/10.5194/egusphere-2022-1518}
+Marina, T.I., Saravia, L.A., Kortsch, S., 2023.
+\href{https://doi.org/10.5194/egusphere-2022-1518}{New insights into the
+{Weddell Sea} ecosystem applying a quantitative network approach}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Martin2021}{}}%
-Martin, J., \& Flores Melo, X. (2021). \emph{{Área Marina Protegida
-Namuncurá Banco Burdwood: Aspectos físicos y biogeoquímicos}}. {Tercer
-taller científico sobre el Área Marina Protegida Namuncurá Banco
-Burdwood. Administración de Parques Nacionales (APN), Argentina}.
+Martin, J., Flores Melo, X., 2021. {Área Marina Protegida Namuncurá
+Banco Burdwood: Aspectos físicos y biogeoquímicos}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-MartinSirito2019}{}}%
-Martin Sirito, S. (2019). \emph{{Fauna asociada a corales (Octocorallia)
-e hidroides (Hydrozoa) del Área Marina Protegida {``Namuncurá''} (Banco
-Burdwood) y zonas profundas adyacentes}} {[}PhD thesis{]}. Universidad
-Nacional de Mar del Plata (UNMdP), Argentina.
+Martin Sirito, S., 2019. {Fauna asociada a corales (Octocorallia) e
+hidroides (Hydrozoa) del Área Marina Protegida {``Namuncurá''} (Banco
+Burdwood) y zonas profundas adyacentes} (PhD thesis). Universidad
+Nacional de Mar del Plata (UNMdP), Argentina, {Argentina}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Martinez1991}{}}%
-Martinez, N. D. (1991). Artifacts or {Attributes}? {Effects} of
-{Resolution} on the {Little Rock Lake Food Web}. \emph{Ecological
-Monographs}, \emph{61}(4), 367--392.
-\url{https://doi.org/10.2307/2937047}
+Martinez, N.D., 1991. \href{https://doi.org/10.2307/2937047}{Artifacts
+or {Attributes}? {Effects} of {Resolution} on the {Little Rock Lake Food
+Web}}. Ecological Monographs 61, 367--392.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Martinez1993}{}}%
-Martinez, N. D. (1993). Effects of {Resolution} on {Food Web Structure}.
-\emph{Oikos}, \emph{66}(3), 403--412.
-\url{https://doi.org/10.2307/3544934}
+Martinez, N.D., 1993. \href{https://doi.org/10.2307/3544934}{Effects of
+{Resolution} on {Food Web Structure}}. Oikos 66, 403--412.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Martinez2021}{}}%
-Martínez, P. A., Wöhler, O. C., Troccoli, G. H., \& Di Marco, E. J.
-(2021). \emph{{Análisis del impacto potencial provocado por el
-establecimiento de las áreas marinas protegidas Namuncurá-Banco Burdwood
-I, II y Yaganes en la pesquería argentina de merluza negra (Dissostichus
-eleginoides)}} (\{Technical report\} No. 23/2021; p. 17). {Instituto
-Nacional de Investigación y Desarrollo Pesquero (INIDEP), Argentina}.
+Martínez, P.A., Wöhler, O.C., Troccoli, G.H., Di Marco, E.J., 2021.
+{Análisis del impacto potencial provocado por el establecimiento de las
+áreas marinas protegidas Namuncurá-Banco Burdwood I, II y Yaganes en la
+pesquería argentina de merluza negra (Dissostichus eleginoides)}
+(\{Technical report\} No. 23/2021). {Instituto Nacional de Investigación
+y Desarrollo Pesquero (INIDEP), Argentina}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Martinez2015}{}}%
-Martínez, P. A., Wöhler, O. G., \& Troccoli, G. H. (2015). \emph{{La
-evolución de la pesquería de merluza negra (Dissostichus eleginoides) en
-el espacio marítimo argentino. Periodo 2003- 2014}} (\{Technical
-report\} No. 11/15; p. 12). {Instituto Nacional de Investigación y
-Desarrollo Pesquero (INIDEP), Argentina}.
+Martínez, P.A., Wöhler, O.G., Troccoli, G.H., 2015. {La evolución de la
+pesquería de merluza negra (Dissostichus eleginoides) en el espacio
+marítimo argentino. Periodo 2003- 2014} (\{Technical report\} No.
+11/15). {Instituto Nacional de Investigación y Desarrollo Pesquero
+(INIDEP), Argentina}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Matano2019}{}}%
-Matano, R. P., Palma, E. D., \& Combes, V. (2019). The {Burdwood Bank
-Circulation}. \emph{Journal of Geophysical Research: Oceans},
-\emph{124}(10), 6904--6926. \url{https://doi.org/10.1029/2019JC015001}
+Matano, R.P., Palma, E.D., Combes, V., 2019.
+\href{https://doi.org/10.1029/2019JC015001}{The {Burdwood Bank
+Circulation}}. Journal of Geophysical Research: Oceans 124, 6904--6926.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Matusevich2022}{}}%
-Matusevich. (2022). \emph{Chondrichthyan fauna from the {Marine
-Protected Area Namuncurá} at {Burdwood Bank}: Exploring egg nursery
-grounds}. https://www.researchsquare.com.
-\url{https://doi.org/10.21203/rs.3.rs-2247873/v1}
+Matusevich, 2022.
+\href{https://doi.org/10.21203/rs.3.rs-2247873/v1}{Chondrichthyan fauna
+from the {Marine Protected Area Namuncurá} at {Burdwood Bank}: Exploring
+egg nursery grounds}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-McCann1997}{}}%
-McCann, K., \& Hastings, A. (1997). Re\textendash evaluating the
-omnivory\textendash stability relationship in food webs.
-\emph{Proceedings of the Royal Society of London. Series B: Biological
-Sciences}, \emph{264}(1385), 1249--1254.
-\url{https://doi.org/10.1098/rspb.1997.0172}
+McCann, K., Hastings, A., 1997.
+\href{https://doi.org/10.1098/rspb.1997.0172}{Re\textendash evaluating
+the omnivory\textendash stability relationship in food webs}.
+Proceedings of the Royal Society of London. Series B: Biological
+Sciences 264, 1249--1254.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Moles2015}{}}%
-Moles, J., Núñez-Pons, L., Taboada, S., Figuerola, B., Cristobo, J., \&
-Avila, C. (2015). Anti-predatory chemical defences in {Antarctic}
-benthic fauna. \emph{Marine Biology}, \emph{162}(9), 1813--1821.
-\url{https://doi.org/10.1007/s00227-015-2714-9}
+Moles, J., Núñez-Pons, L., Taboada, S., Figuerola, B., Cristobo, J.,
+Avila, C., 2015.
+\href{https://doi.org/10.1007/s00227-015-2714-9}{Anti-predatory chemical
+defences in {Antarctic} benthic fauna}. Marine Biology 162, 1813--1821.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Montoya2002}{}}%
-Montoya, J. M., \& Solé, R. V. (2002). Small {World Patterns} in {Food
-Webs}. \emph{Journal of Theoretical Biology}, \emph{214}(3), 405--412.
-\url{https://doi.org/10.1006/jtbi.2001.2460}
+Montoya, J.M., Solé, R.V., 2002.
+\href{https://doi.org/10.1006/jtbi.2001.2460}{Small {World Patterns} in
+{Food Webs}}. Journal of Theoretical Biology 214, 405--412.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Montoya2003}{}}%
-Montoya, J. M., \& Solé, R. V. (2003). Topological properties of food
-webs: From real data to community assembly models. \emph{Oikos},
-\emph{102}(3), 614--622.
-\url{https://doi.org/10.1034/j.1600-0706.2003.12031.x}
+Montoya, J.M., Solé, R.V., 2003.
+\href{https://doi.org/10.1034/j.1600-0706.2003.12031.x}{Topological
+properties of food webs: From real data to community assembly models}.
+Oikos 102, 614--622.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Morales-Castilla2015}{}}%
-Morales-Castilla, I., Matias, M. G., Gravel, D., \& Araújo, M. B.
-(2015). Inferring biotic interactions from proxies. \emph{Trends in
-Ecology \& Evolution}, \emph{30}(6), 347--356.
-\url{https://doi.org/10.1016/j.tree.2015.03.014}
+Morales-Castilla, I., Matias, M.G., Gravel, D., Araújo, M.B., 2015.
+\href{https://doi.org/10.1016/j.tree.2015.03.014}{Inferring biotic
+interactions from proxies}. Trends in Ecology \& Evolution 30, 347--356.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Neutel2002}{}}%
-Neutel, A.-M., Heesterbeek, J. A. P., \& de Ruiter, P. C. (2002).
-Stability in {Real Food Webs}: {Weak Links} in {Long Loops}.
-\emph{Science}, \emph{296}(5570), 1120--1123.
-\url{https://doi.org/10.1126/science.1068326}
+Neutel, A.-M., Heesterbeek, J.A.P., de Ruiter, P.C., 2002.
+\href{https://doi.org/10.1126/science.1068326}{Stability in {Real Food
+Webs}: {Weak Links} in {Long Loops}}. Science 296, 1120--1123.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Newman2003}{}}%
-Newman, M. E. J. (2003). The {Structure} and {Function} of {Complex
-Networks}. \emph{SIAM Review}, \emph{45}(2), 167--256.
-\url{https://doi.org/10.1137/S003614450342480}
+Newman, M.E.J., 2003.
+\href{https://doi.org/10.1137/S003614450342480}{The {Structure} and
+{Function} of {Complex Networks}}. SIAM Review 45, 167--256.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Nilsson2016}{}}%
-Nilsson, K. A., \& McCann, K. S. (2016). Interaction strength
+Nilsson, K.A., McCann, K.S., 2016.
+\href{https://doi.org/10.1007/s12080-015-0282-8}{Interaction strength
 revisited\textemdash clarifying the role of energy flux for food web
-stability. \emph{Theoretical Ecology}, \emph{9}(1), 59--71.
-\url{https://doi.org/10.1007/s12080-015-0282-8}
+stability}. Theoretical Ecology 9, 59--71.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Nunez-Pons2010}{}}%
-Núñez-Pons, L., Forestieri, R., Nieto, R. M., Varela, M., Nappo, M.,
+Núñez-Pons, L., Forestieri, R., Nieto, R.M., Varela, M., Nappo, M.,
 Rodríguez, J., Jiménez, C., Castelluccio, F., Carbone, M., Ramos-Espla,
-A., Gavagnin, M., \& Avila, C. (2010). Chemical defenses of tunicates of
-the genus {Aplidium} from the {Weddell Sea} ({Antarctica}). \emph{Polar
-Biology}, \emph{33}(10), 1319--1329.
-\url{https://doi.org/10.1007/s00300-010-0819-7}
+A., Gavagnin, M., Avila, C., 2010.
+\href{https://doi.org/10.1007/s00300-010-0819-7}{Chemical defenses of
+tunicates of the genus {Aplidium} from the {Weddell Sea}
+({Antarctica})}. Polar Biology 33, 1319--1329.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Padovani2021}{}}%
-Padovani, L. N., Álvarez, N., \& Farías, A. (2021). \emph{Alimentación
-de la sardina fueguina ({Sprattus} fuegensis) en la región patagónica
-austral durante la época reproductiva} {[}Technical Report{]}.
-{Instituto Nacional de Investigación y Desarrollo Pesquero (INIDEP)}.
+Padovani, L.N., Álvarez, N., Farías, A., 2021. Alimentación de la
+sardina fueguina ({Sprattus} fuegensis) en la región patagónica austral
+durante la época reproductiva (Technical Report). {Instituto Nacional de
+Investigación y Desarrollo Pesquero (INIDEP)}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Padovani2012}{}}%
-Padovani, L. N., Viñas, M. D., Sánchez, F., \& Mianzan, H. (2012).
-Amphipod-supported food web: {Themisto} gaudichaudii, a key food
-resource for fishes in the southern {Patagonian Shelf}. \emph{Journal of
-Sea Research}, \emph{67}(1), 85--90.
-\url{https://doi.org/10.1016/j.seares.2011.10.007}
+Padovani, L.N., Viñas, M.D., Sánchez, F., Mianzan, H., 2012.
+\href{https://doi.org/10.1016/j.seares.2011.10.007}{Amphipod-supported
+food web: {Themisto} gaudichaudii, a key food resource for fishes in the
+southern {Patagonian Shelf}}. Journal of Sea Research 67, 85--90.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Pascual2005}{}}%
-Pascual, M., \& Dunne, J. A. (2005). \emph{Ecological {Networks}:
-{Linking Structure} to {Dynamics} in {Food Webs}}. {Oxford University
-Press}.
+Pascual, M., Dunne, J.A., 2005. Ecological {Networks}: {Linking
+Structure} to {Dynamics} in {Food Webs}. {Oxford University Press}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Pawar2012}{}}%
-Pawar, S., Dell, A. I., \& Van M. Savage. (2012). Dimensionality of
-consumer search space drives trophic interaction strengths.
-\emph{Nature}, \emph{486}, 485.
-\url{https://doi.org/10.1038/nature11131}
+Pawar, S., Dell, A.I., Van M. Savage, 2012.
+\href{https://doi.org/10.1038/nature11131}{Dimensionality of consumer
+search space drives trophic interaction strengths}. Nature 486, 485.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Piola2009}{}}%
-Piola, A. R., \& Falabella, V. (2009). {El mar Patagónico}. In
-\emph{{Atlas del Mar Patagónico. Especies y Espacios}} (Falabella, V.,
-Campagna, C. y Croxall, J. Ed., pp. 54--75). {Wildlife Conservation
-Society y Birdlife Internacional}.
+Piola, A.R., Falabella, V., 2009. {El mar Patagónico}. In: {Atlas del
+Mar Patagónico. Especies y Espacios}. {Wildlife Conservation Society y
+Birdlife Internacional}, {Buenos Aires, Argentina}, pp. 54--75.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Piola1989}{}}%
-Piola, A. R., \& Gordon, A. L. (1989). Intermediate waters in the
-southwest {South Atlantic}. \emph{Deep Sea Research Part A.
-Oceanographic Research Papers}, \emph{36}(1), 1--16.
-\url{https://doi.org/10.1016/0198-0149(89)90015-0}
+Piola, A.R., Gordon, A.L., 1989.
+\href{https://doi.org/10.1016/0198-0149(89)90015-0}{Intermediate waters
+in the southwest {South Atlantic}}. Deep Sea Research Part A.
+Oceanographic Research Papers 36, 1--16.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Poisot2014}{}}%
-Poisot, T., \& Gravel, D. (2014). When is an ecological network complex?
-{Connectance} drives degree distribution and emerging network
-properties. \emph{PeerJ}, \emph{2}, e251.
-\url{https://doi.org/10.7717/peerj.251}
+Poisot, T., Gravel, D., 2014.
+\href{https://doi.org/10.7717/peerj.251}{When is an ecological network
+complex? {Connectance} drives degree distribution and emerging network
+properties}. PeerJ 2, e251.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Pomeranz2019}{}}%
-Pomeranz, J. P. F., Thompson, R. M., Poisot, T., \& Harding, J. S.
-(2019). Inferring predator\textendash prey interactions in food webs.
-\emph{Methods in Ecology and Evolution}, \emph{10}(3), 356--367.
-\url{https://doi.org/10.1111/2041-210X.13125}
+Pomeranz, J.P.F., Thompson, R.M., Poisot, T., Harding, J.S., 2019.
+\href{https://doi.org/10.1111/2041-210X.13125}{Inferring
+predator\textendash prey interactions in food webs}. Methods in Ecology
+and Evolution 10, 356--367.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Presta2023}{}}%
-Presta, M. L., Riccialdelli, L., Bruno, D. O., Castro, L. R.,
-Fioramonti, N. E., Florentín, O. V., Berghoff, C. F., Capitanio, F. L.,
-\& Lovrich, G. A. (2023). Mesozooplankton community structure and
-trophic relationships in an austral high-latitude ecosystem ({Beagle
-Channel}): {The} role of bottom-up and top-down forces during
-springtime. \emph{Journal of Marine Systems}, \emph{240}, 103881.
-\url{https://doi.org/10.1016/j.jmarsys.2023.103881}
+Presta, M.L., Riccialdelli, L., Bruno, D.O., Castro, L.R., Fioramonti,
+N.E., Florentín, O.V., Berghoff, C.F., Capitanio, F.L., Lovrich, G.A.,
+2023.
+\href{https://doi.org/10.1016/j.jmarsys.2023.103881}{Mesozooplankton
+community structure and trophic relationships in an austral
+high-latitude ecosystem ({Beagle Channel}): {The} role of bottom-up and
+top-down forces during springtime}. Journal of Marine Systems 240,
+103881.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Prieto2022}{}}%
-Prieto, I. M., Paola, A., Pérez, M., García, M., Blustein, G., Schejter,
-L., \& Palermo, J. A. (2022). Antifouling {Diterpenoids} from the
-{Sponge} {\emph{Dendrilla}}{ \emph{Antarctica}}. \emph{Chemistry \&
-Biodiversity}, \emph{19}(2).
-\url{https://doi.org/10.1002/cbdv.202100618}
+Prieto, I.M., Paola, A., Pérez, M., García, M., Blustein, G., Schejter,
+L., Palermo, J.A., 2022.
+\href{https://doi.org/10.1002/cbdv.202100618}{Antifouling {Diterpenoids}
+from the {Sponge} {\emph{Dendrilla}}{ \emph{Antarctica}}}. Chemistry \&
+Biodiversity 19.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Reta2014}{}}%
-Reta, R. (2014). \emph{Oceanografía del {Banco Burdwood}: {Estado
-Actual} del {Conocimiento} y {Perspectivas}}. {Instituto Nacional de
-Investigación y Desarrollo Pesquero (INIDEP), Argentina}.
+Reta, R., 2014. Oceanografía del {Banco Burdwood}: {Estado Actual} del
+{Conocimiento} y {Perspectivas}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Riccialdelli2020}{}}%
-Riccialdelli, L., Becker, Y. A., Fioramonti, N. E., Torres, M., Bruno,
-D. O., Rey, A. R., \& Fernández, D. A. (2020). Trophic structure of
-southern marine ecosystems: A comparative isotopic analysis from the
-{Beagle Channel} to the oceanic {Burdwood Bank} area under a wasp-waist
-assumption. \emph{Marine Ecology Progress Series}, \emph{655}, 1--27.
-\url{https://doi.org/10.3354/meps13524}
+Riccialdelli, L., Becker, Y.A., Fioramonti, N.E., Torres, M., Bruno,
+D.O., Rey, A.R., Fernández, D.A., 2020.
+\href{https://doi.org/10.3354/meps13524}{Trophic structure of southern
+marine ecosystems: A comparative isotopic analysis from the {Beagle
+Channel} to the oceanic {Burdwood Bank} area under a wasp-waist
+assumption}. Marine Ecology Progress Series 655, 1--27.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Roberts2017}{}}%
-Roberts, C. M., O'Leary, B. C., McCauley, D. J., Cury, P. M., Duarte, C.
-M., Lubchenco, J., Pauly, D., Sáenz-Arroyo, A., Sumaila, U. R., Wilson,
-R. W., Worm, B., \& Castilla, J. C. (2017). Marine reserves can mitigate
-and promote adaptation to climate change. \emph{Proceedings of the
-National Academy of Sciences}, \emph{114}(24), 6167--6175.
-\url{https://doi.org/10.1073/pnas.1701262114}
+Roberts, C.M., O'Leary, B.C., McCauley, D.J., Cury, P.M., Duarte, C.M.,
+Lubchenco, J., Pauly, D., Sáenz-Arroyo, A., Sumaila, U.R., Wilson, R.W.,
+Worm, B., Castilla, J.C., 2017.
+\href{https://doi.org/10.1073/pnas.1701262114}{Marine reserves can
+mitigate and promote adaptation to climate change}. Proceedings of the
+National Academy of Sciences 114, 6167--6175.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Rodriguez2022}{}}%
-Rodriguez, I. D., Marina, T. I., Schloss, I. R., \& Saravia, L. A.
-(2022). Marine food webs are more complex but less stable in
-sub-{Antarctic} ({Beagle Channel}, {Argentina}) than in {Antarctic}
-({Potter Cove}, {Antarctic Peninsula}) regions. \emph{Marine
-Environmental Research}, \emph{174}, 105561.
-\url{https://doi.org/10.1016/j.marenvres.2022.105561}
+Rodriguez, I.D., Marina, T.I., Schloss, I.R., Saravia, L.A., 2022.
+\href{https://doi.org/10.1016/j.marenvres.2022.105561}{Marine food webs
+are more complex but less stable in sub-{Antarctic} ({Beagle Channel},
+{Argentina}) than in {Antarctic} ({Potter Cove}, {Antarctic Peninsula})
+regions}. Marine Environmental Research 174, 105561.
 
 \leavevmode\vadjust pre{\hypertarget{ref-RojodeAlmeida2010}{}}%
-Rojo de Almeida, M. T., Siless, G. E., Perez, C. D., Veloso, M. J.,
-Schejter, L., Puricelli, L., \& Palermo, J. A. (2010). Dolabellane
-{Diterpenoids} from the {South Atlantic Gorgonian} {\emph{Convexella}}{
-\emph{Magelhaenica}}. \emph{Journal of Natural Products}, \emph{73}(10),
-1714--1717. \url{https://doi.org/10.1021/np100337j}
+Rojo de Almeida, M.T., Siless, G.E., Perez, C.D., Veloso, M.J.,
+Schejter, L., Puricelli, L., Palermo, J.A., 2010.
+\href{https://doi.org/10.1021/np100337j}{Dolabellane {Diterpenoids} from
+the {South Atlantic Gorgonian} {\emph{Convexella}}{
+\emph{Magelhaenica}}}. Journal of Natural Products 73, 1714--1717.
 
@@
 Sala, E., Lubchenco, J., Grorud-Colvert, K., Novelli, C., Roberts, C.,
-\& Sumaila, U. R. (2018). Assessing real progress towards effective
-ocean protection. \emph{Marine Policy}, \emph{91}, 11--13.
-\url{https://doi.org/10.1016/j.marpol.2018.02.004}
+Sumaila, U.R., 2018.
+\href{https://doi.org/10.1016/j.marpol.2018.02.004}{Assessing real
+progress towards effective ocean protection}. Marine Policy 91, 11--13.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Santana2013}{}}%
-Santana, C. N. de, Rozenfeld, A. F., Marquet, P. A., \& Duarte, C. M.
-(2013). Topological properties of polar food webs. \emph{Marine Ecology
-Progress Series}, \emph{474}, 15--26.
-\url{https://doi.org/10.3354/meps10073}
+Santana, C.N. de, Rozenfeld, A.F., Marquet, P.A., Duarte, C.M., 2013.
+\href{https://doi.org/10.3354/meps10073}{Topological properties of polar
+food webs}. Marine Ecology Progress Series 474, 15--26.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Saporiti2015}{}}%
-Saporiti, F., Bearhop, S., Vales, D. G., Silva, L., Zenteno, L.,
-Tavares, M., Crespo, E. A., \& Cardona, L. (2015). Latitudinal changes
-in the structure of marine food webs in the {Southwestern Atlantic
-Ocean}. \emph{Marine Ecology Progress Series}, \emph{538}, 23--34.
-\url{https://doi.org/10.3354/meps11464}
+Saporiti, F., Bearhop, S., Vales, D.G., Silva, L., Zenteno, L., Tavares,
+M., Crespo, E.A., Cardona, L., 2015.
+\href{https://doi.org/10.3354/meps11464}{Latitudinal changes in the
+structure of marine food webs in the {Southwestern Atlantic Ocean}}.
+Marine Ecology Progress Series 538, 23--34.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Saravia2022a}{}}%
-Saravia, L. A. (2022). \emph{Multiweb: {Ecological} network analyses
-including multiplex networks}.
+Saravia, L.A., 2022. Multiweb: {Ecological} network analyses including
+multiplex networks.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Schejter2021}{}}%
-Schejter, L., \& Albano, M. (2021). Benthic communities at the marine
-protected area {Namuncurá}/{Burdwood} bank, {SW Atlantic Ocean}:
-Detection of vulnerable marine ecosystems and contributions to the
-assessment of the rezoning process. \emph{Polar Biology}, \emph{44}(10),
-2023--2037. \url{https://doi.org/10.1007/s00300-021-02936-y}
+Schejter, L., Albano, M., 2021.
+\href{https://doi.org/10.1007/s00300-021-02936-y}{Benthic communities at
+the marine protected area {Namuncurá}/{Burdwood} bank, {SW Atlantic
+Ocean}: Detection of vulnerable marine ecosystems and contributions to
+the assessment of the rezoning process}. Polar Biology 44, 2023--2037.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Schejter2019}{}}%
-Schejter, L., \& Bremec, C. S. (2019). Stony corals ({Anthozoa}:
-{Scleractinia}) of {Burdwood Bank} and neighbouring areas, {SW Atlantic
-Ocean}. \emph{Scientia Marina}, \emph{83}(3), 247--260.
-\url{https://doi.org/10.3989/scimar.04863.10A}
+Schejter, L., Bremec, C.S., 2019.
+\href{https://doi.org/10.3989/scimar.04863.10A}{Stony corals
+({Anthozoa}: {Scleractinia}) of {Burdwood Bank} and neighbouring areas,
+{SW Atlantic Ocean}}. Scientia Marina 83, 247--260.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Schejter2020}{}}%
-Schejter, L., Genzano, G., Gaitán, E., Perez, C. D., \& Bremec, C. S.
-(2020). Benthic communities in the {Southwest Atlantic Ocean}:
-{Conservation} value of animal forests at the {Burdwood Bank} slope.
-\emph{Aquatic Conservation: Marine and Freshwater Ecosystems},
-\emph{30}(3), 426--439. \url{https://doi.org/10.1002/aqc.3265}
+Schejter, L., Genzano, G., Gaitán, E., Perez, C.D., Bremec, C.S., 2020.
+\href{https://doi.org/10.1002/aqc.3265}{Benthic communities in the
+{Southwest Atlantic Ocean}: {Conservation} value of animal forests at
+the {Burdwood Bank} slope}. Aquatic Conservation: Marine and Freshwater
+Ecosystems 30, 426--439.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Schejter2016}{}}%
-Schejter, L., Rimondino, C., Chiesa, I., Díaz de Astarloa, J. M., Doti,
+Schejter, L., Rimondino, C., Chiesa, I., Díaz de Astarloa, J.M., Doti,
 B., Elías, R., Escolar, M., Genzano, G., López-Gappa, J., Tatián, M.,
-Zelaya, D. G., Cristobo, J., Perez, C. D., Cordeiro, R. T., \& Bremec,
-C. S. (2016). Namuncurá {Marine Protected Area}: An oceanic hot spot of
-benthic biodiversity at {Burdwood Bank}, {Argentina}. \emph{Polar
-Biology}, \emph{39}(12), 2373--2386.
-\url{https://doi.org/10.1007/s00300-016-1913-2}
+Zelaya, D.G., Cristobo, J., Perez, C.D., Cordeiro, R.T., Bremec, C.S.,
+2016. \href{https://doi.org/10.1007/s00300-016-1913-2}{Namuncurá {Marine
+Protected Area}: An oceanic hot spot of benthic biodiversity at
+{Burdwood Bank}, {Argentina}}. Polar Biology 39, 2373--2386.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Scotti2010}{}}%
-Scotti, M., \& Jordán, F. (2010). Relationships between centrality
-indices and trophic levels in food webs. \emph{Community Ecology},
-\emph{11}(1), 59--67. \url{https://doi.org/10.1556/ComEc.11.2010.1.9}
+Scotti, M., Jordán, F., 2010.
+\href{https://doi.org/10.1556/ComEc.11.2010.1.9}{Relationships between
+centrality indices and trophic levels in food webs}. Community Ecology
+11, 59--67.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Secretariatoftheconventiononbiologicaldiversity2004}{}}%
-Secretariat of the convention on biological diversity. (2004).
-\emph{Technical advice on the establishment and management of a national
-system of marine and coastal protected areas} (Technical Report No. 13).
+Secretariat of the convention on biological diversity, 2004. Technical
+advice on the establishment and management of a national system of
+marine and coastal protected areas (Technical Report No. 13).
 
 \leavevmode\vadjust pre{\hypertarget{ref-Smith-Ramesh2017}{}}%
-Smith-Ramesh, L. M., Moore, A. C., \& Schmitz, O. J. (2017). Global
-synthesis suggests that food web connectance correlates to invasion
-resistance. \emph{Global Change Biology}, \emph{23}(2), 465--473.
-\url{https://doi.org/10.1111/gcb.13460}
+Smith-Ramesh, L.M., Moore, A.C., Schmitz, O.J., 2017.
+\href{https://doi.org/10.1111/gcb.13460}{Global synthesis suggests that
+food web connectance correlates to invasion resistance}. Global Change
+Biology 23, 465--473.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Sole2001}{}}%
-Solé, R. V., \& Montoya, M. (2001). Complexity and fragility in
-ecological networks. \emph{Proceedings of the Royal Society of London.
-Series B: Biological Sciences}, \emph{268}(1480), 2039--2045.
-\url{https://doi.org/10.1098/rspb.2001.1767}
+Solé, R.V., Montoya, M., 2001.
+\href{https://doi.org/10.1098/rspb.2001.1767}{Complexity and fragility
+in ecological networks}. Proceedings of the Royal Society of London.
+Series B: Biological Sciences 268, 2039--2045.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Spinelli2020}{}}%
-Spinelli, M. L., Malits, A., García Alonso, V. A., Martín, J., \&
-Capitanio, F. L. (2020). Spatial gradients of spring zooplankton
-assemblages at the open ocean sub-{Antarctic Namuncurá Marine Protected
-Area}/{Burdwood Bank}, {SW Atlantic Ocean}. \emph{Journal of Marine
-Systems}, \emph{210}, 103398.
-\url{https://doi.org/10.1016/j.jmarsys.2020.103398}
+Spinelli, M.L., Malits, A., García Alonso, V.A., Martín, J., Capitanio,
+F.L., 2020. \href{https://doi.org/10.1016/j.jmarsys.2020.103398}{Spatial
+gradients of spring zooplankton assemblages at the open ocean
+sub-{Antarctic Namuncurá Marine Protected Area}/{Burdwood Bank}, {SW
+Atlantic Ocean}}. Journal of Marine Systems 210, 103398.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Stouffer2010}{}}%
-Stouffer, D. B., \& Bascompte, J. (2010). Understanding food-web
-persistence from local to global scales. \emph{Ecology Letters},
-\emph{13}(2), 154--161.
-\url{https://doi.org/10.1111/j.1461-0248.2009.01407.x}
+Stouffer, D.B., Bascompte, J., 2010.
+\href{https://doi.org/10.1111/j.1461-0248.2009.01407.x}{Understanding
+food-web persistence from local to global scales}. Ecology Letters 13,
+154--161.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Stouffer2005}{}}%
-Stouffer, D. B., Camacho, J., Guimerà, R., Ng, C. A., \& Nunes Amaral,
-L. A. (2005). Quantitative {Patterns} in the {Structure} of {Model} and
-{Empirical Food Webs}. \emph{Ecology}, \emph{86}(5), 1301--1311.
-\url{https://doi.org/10.1890/04-0957}
+Stouffer, D.B., Camacho, J., Guimerà, R., Ng, C.A., Nunes Amaral, L.A.,
+2005. \href{https://doi.org/10.1890/04-0957}{Quantitative {Patterns} in
+the {Structure} of {Model} and {Empirical Food Webs}}. Ecology 86,
+1301--1311.
 
 \leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam2022}{}}%
-Team, R. C. (2022). \emph{R: {A Language} and {Environment} for
-{Statistical Computing}}. R Foundation for Statistical Computing.
+Team, R.C., 2022. R: {A Language} and {Environment} for {Statistical
+Computing}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Thebault2010}{}}%
-Thébault, E., \& Fontaine, C. (2010). Stability of {Ecological
+Thébault, E., Fontaine, C., 2010.
+\href{https://doi.org/10.1126/science.1188321}{Stability of {Ecological
 Communities} and the {Architecture} of {Mutualistic} and {Trophic
-Networks}. \emph{Science}, \emph{329}(5993), 853--856.
-\url{https://doi.org/10.1126/science.1188321}
+Networks}}. Science 329, 853--856.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Tombesi2020}{}}%
-Tombesi, M. L., Rabufetti, F., \& Lovrich, G. A. (2020). Las áreas
-marinas protegidas en la {Argentina}. \emph{La Lupa. Colección Fueguina
-De Divulgación Científica}, \emph{16}, 2--7.
-https://doi.org/\url{https://www.coleccionlalupa.com.ar/index.php/lalupa/article/view/79}
+Tombesi, M.L., Rabufetti, F., Lovrich, G.A., 2020.
+\href{https://www.coleccionlalupa.com.ar/index.php/lalupa/article/view/79}{Las
+áreas marinas protegidas en la {Argentina}}. La Lupa. Colección Fueguina
+De divulgación científica 16, 2--7.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Trathan2021}{}}%
-Trathan, P. N., Fielding, S., Hollyman, P. R., Murphy, E. J.,
-Warwick-Evans, V., \& Collins, M. A. (2021). Enhancing the ecosystem
+Trathan, P.N., Fielding, S., Hollyman, P.R., Murphy, E.J.,
+Warwick-Evans, V., Collins, M.A., 2021.
+\href{https://doi.org/10.1093/icesjms/fsab092}{Enhancing the ecosystem
 approach for the fishery for {Antarctic} krill within the complex,
-variable, and changing ecosystem at {South Georgia}. \emph{ICES Journal
-of Marine Science}, \emph{78}(6), 2065--2081.
-\url{https://doi.org/10.1093/icesjms/fsab092}
+variable, and changing ecosystem at {South Georgia}}. ICES Journal of
+Marine Science 78, 2065--2081.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Troccoli2020}{}}%
-Troccoli, G. H., Aguilar, E., Martínez, P. A., \& Belleggia, M. (2020).
-The diet of the {Patagonian} toothfish {Dissostichus} eleginoides, a
-deep-sea top predator off {Southwest Atlantic Ocean}. \emph{Polar
-Biology}, \emph{43}(10), 1595--1604.
-\url{https://doi.org/10.1007/s00300-020-02730-2}
+Troccoli, G.H., Aguilar, E., Martínez, P.A., Belleggia, M., 2020.
+\href{https://doi.org/10.1007/s00300-020-02730-2}{The diet of the
+{Patagonian} toothfish {Dissostichus} eleginoides, a deep-sea top
+predator off {Southwest Atlantic Ocean}}. Polar Biology 43, 1595--1604.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Valenzuela2018}{}}%
-Valenzuela, L. O., Rowntree, V. J., Sironi, M., \& Seger, J. (2018).
-Stable isotopes ({\(\delta\)15N}, {\(\delta\)13C}, {\(\delta\)34S}) in
-skin reveal diverse food sources used by southern right whales
-{Eubalaena} australis. \emph{Marine Ecology Progress Series},
-\emph{603}, 243--255. \url{https://doi.org/10.3354/meps12722}
+Valenzuela, L.O., Rowntree, V.J., Sironi, M., Seger, J., 2018.
+\href{https://doi.org/10.3354/meps12722}{Stable isotopes
+({\(\delta\)15N}, {\(\delta\)13C}, {\(\delta\)34S}) in skin reveal
+diverse food sources used by southern right whales {Eubalaena}
+australis}. Marine Ecology Progress Series 603, 243--255.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Vazquez2018}{}}%
-Vazquez, D. M., Belleggia, M., Schejter, L., \& Mabragaña, E. (2018).
-Avoiding being dragged away: Finding egg cases of {Schroederichthys}
-bivius ({Chondrichthyes}: {Scyliorhinidae}) associated with benthic
-invertebrates. \emph{Journal of Fish Biology}, \emph{92}(1), 248--253.
-\url{https://doi.org/10.1111/jfb.13490}
+Vazquez, D.M., Belleggia, M., Schejter, L., Mabragaña, E., 2018.
+\href{https://doi.org/10.1111/jfb.13490}{Avoiding being dragged away:
+Finding egg cases of {Schroederichthys} bivius ({Chondrichthyes}:
+{Scyliorhinidae}) associated with benthic invertebrates}. Journal of
+Fish Biology 92, 248--253.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Watts1998}{}}%
-Watts, D. J., \& Strogatz, S. H. (1998). Collective dynamics of
-{``small-world''} networks. \emph{Nature}, \emph{393}(6684), 440--442.
-\url{https://doi.org/10.1038/30918}
+Watts, D.J., Strogatz, S.H., 1998.
+\href{https://doi.org/10.1038/30918}{Collective dynamics of
+{``small-world''} networks}. Nature 393, 440--442.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Williams2002}{}}%
-Williams, R. J., Berlow, E. L., Dunne, J. A., Barabási, A.-L., \&
-Martinez, N. D. (2002). Two degrees of separation in complex food webs.
-\emph{Proceedings of the National Academy of Sciences}, \emph{99}(20),
-12913--12916. \url{https://doi.org/10.1073/pnas.192448799}
+Williams, R.J., Berlow, E.L., Dunne, J.A., Barabási, A.-L., Martinez,
+N.D., 2002. \href{https://doi.org/10.1073/pnas.192448799}{Two degrees of
+separation in complex food webs}. Proceedings of the National Academy of
+Sciences 99, 12913--12916.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Winter2023}{}}%
-Winter, A., \& Arkhipkin, A. (2023). Opportunistic {Survey Analyses
-Reveal} a {Recent Decline} of {Skate} ({Rajiformes}) {Biomass} in
-{Falkland Islands Waters}. \emph{Fishes}, \emph{8}(1), 24.
-\url{https://doi.org/10.3390/fishes8010024}
+Winter, A., Arkhipkin, A., 2023.
+\href{https://doi.org/10.3390/fishes8010024}{Opportunistic {Survey
+Analyses Reveal} a {Recent Decline} of {Skate} ({Rajiformes}) {Biomass}
+in {Falkland Islands Waters}}. Fishes 8, 24.
 

### 2024-01-11 MS_ToSubmit/SupMaterial.Rmd
Fix table format

@@
 ---
-title: "Supplementary Material for 'The complex network of trophic interactions in
-  a subAntarctic oceanic Marine Protected Area'"
-author:
-  - Tomás I. Marina
-  - Irene R. Schloss
-  - Gustavo A. Lovrich
-  - Claudia C. Boy
-  - Daniel O. Bruno  
-  - Fabiana L. Capitanio
-  - Sergio M. Delpiani
-  - Juan Martín Díaz de Astarloa
-  - Cintia Fraysse
-  - Virginia A. García Alonso
-  - Andrea Raya Rey
-  - Laura Schejter
-  - Mariela L. Spinelli
-  - Marcos Tatián
-  - Diego Urteaga
-  - Luciana Riccialdelli
+output:
+  pdf_document:
+    latex_engine: xelatex
+    keep_tex: yes
+  word_document: default
+# classoption: landscape
 bibliography: AMPBancoBurdwood.bib
-output: pdf_document
+csl: "elsevier-harvard2.csl"
+documentclass: article
+geometry:
+- vmargin=1in
+- hmargin=1in
+header-includes:
+- \usepackage{amsmath}
+- \usepackage{pdflscape,booktabs}
+- \usepackage{lscape}
+- \newcommand{\blandscape}{\begin{landscape}}
+- \newcommand{\elandscape}{\end{landscape}}
+- \usepackage[running]{lineno}
+- \linenumbers
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
-```
+# Supplementary Material for 'The complex network of trophic interactions in a subAntarctic oceanic Marine Protected Area'
 
@@
 
-```{r ref_plot, echo=FALSE, fig.cap="Summary of references used to build the network of trophic (predator-prey) interactions for the MPAN-BB ecosystem."}
+```{r ref_plot, echo=FALSE, message=FALSE, fig.cap="Summary of references used to build the network of trophic (predator-prey) interactions for the MPAN-BB ecosystem."}
 
@@
 \newpage
+\blandscape
 
-```{r tableS1, echo=FALSE, results='asis'}
+```{r tableS1, echo=FALSE, message=FALSE, results='asis'}
 
 # Load packages
-library(knitr)
-library(dplyr)
-library(kableExtra)
-library(pander)
+require(tidyverse)
+require(knitr)
+require(dplyr)
+require(kableExtra)
+require(pander)
 
@@
 int_good_res <- int_raw %>% 
-  filter(!str_detect(Prey, "\\*$")) %>% 
-  filter(!str_detect(Predator, "\\*$")) %>% 
-  mutate(Prey = case_when(Prey == "Brachiopoda_spp" ~ "Brachiopoda", TRUE ~ "Other")) %>%
+  dplyr::filter(!str_detect(Prey, "\\*$")) %>% 
+  dplyr::filter(!str_detect(Predator, "\\*$")) %>% 
+  mutate(Prey = case_when(Prey == "Brachiopoda_spp" ~ "Brachiopoda", TRUE ~ Prey)) %>%
   dplyr::select(Prey, Predator, Reference, Reference_link) %>% 
@@
 # Table 1. List of interactions
-knitr::kable(int_good_res %>% arrange(., (Predator)), booktabs = TRUE, format = "latex", longtable = T, col.names = c("Prey","Predator","Reference", "Link"), caption = "List of predator-prey (trophic) interactions for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
+# landscape(knitr::kable(int_good_res %>% arrange(., (Predator), booktabs = TRUE, format = "latex", longtable = T, col.names = c("Prey","Predator","Reference", "Link"), caption = "List of predator-prey (trophic) interactions for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
 Alphabetically ordered by predator.") %>%
-  column_spec(1:3, width="2cm") %>% 
-  column_spec(4, width="14cm") %>% 
-  kable_styling(latex_options = c("hold_position","repeat_header"), font_size = 4) %>% 
-  landscape()
+#              column_spec(1:3, width="2cm") %>% 
+#              column_spec(4, width="14cm") %>% 
+#              kable_styling(latex_options = c("hold_position","repeat_header"), font_size = 4))
 
-# pandoc.table(int_good_res %>% arrange(., (Predator)) %>% mutate(Reference_link = paste('\\tiny', Reference_link)) %>% rename("Link"="Reference_link"), style="multiline", split.tables = Inf, justify = c("left","left","left","right"),
-#              caption = "List of predator-prey (trophic) interactions used to build the network for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).")
+pandoc.table(int_good_res %>% arrange(., (Predator)) %>% mutate(Prey = paste('\\tiny', Prey), Predator = paste('\\tiny', Predator), Reference = paste('\\tiny', Reference), Reference_link = paste('\\tiny', Reference_link)) %>% rename("Link"="Reference_link"), style="multiline", split.tables = Inf, justify = c("left","left","left","right"),
+             caption = "List of predator-prey (trophic) interactions used to build the network for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).")
 
@@
 
-```{r tableS2, echo=FALSE, results='asis'}
+```{r tableS2, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
 # Load packages
-library(knitr)
-library(dplyr)
-library(kableExtra)
-library(stringr)
+# library(knitr)
+# library(dplyr)
+# library(kableExtra)
+# library(stringr)
 
@@
 # Table 2. List of species
-knitr::kable(sp_list, format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Taxonomy","Group","Reference","Link","Observation"), caption = "List of species for the food web of the Marine Protected Areas Namuncurá - Banco Burdwood I and II ecosystem.
+# knitr::kable(sp_list, format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Taxonomy","Group","Reference","Link","Observation"), caption = "List of species for the food web of the Marine Protected Areas Namuncurá - Banco Burdwood I and II ecosystem.
 Alphabetically ordered by species.") %>%
-  column_spec(1:3, width="2cm") %>%
-  column_spec(4, width="3cm") %>% 
-  column_spec(5:6, width="5cm") %>% 
-  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 4) %>% 
-  landscape()
+#   column_spec(1:3, width="2cm") %>%
+#   column_spec(4, width="3cm") %>% 
+#   column_spec(5:6, width="5cm") %>% 
+#   kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 4) %>% 
+#   landscape()
+
+pandoc.table(sp_list %>% arrange(., (Species)) %>% mutate(Species = paste('\\tiny', Species), TaxLevel = paste('\\tiny', TaxLevel), FunctionalGroup = paste('\\tiny', FunctionalGroup), Reference = paste('\\tiny', Reference), Reference_pres_link = paste('\\tiny', Reference_pres_link), Observation = paste('\\tiny', Observation)) %>% rename("Taxonomy"="TaxLevel", "Group"="FunctionalGroup", "Link"="Reference_pres_link"), style="multiline", split.tables = Inf, justify = c("left","left","left","right","right","left"),
+             caption = "List of species for the food web of the Marine Protected Areas Namuncurá - Banco Burdwood I and II ecosystem. Alphabetically ordered by species.")
 
@@
 
-```{r tableS3, echo=FALSE}
+```{r tableS3, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
@@
 
-# Table 2. List of species
-knitr::kable(spp_total %>% 
-               mutate(TopRole = case_when(TopRole == "hubcon" ~ "netcon",
-                                          TRUE ~ TopRole)) %>% 
+# Table 3. List of species
+tbl_3 <- spp_total %>% 
+  mutate(TopRole = case_when(TopRole == "hubcon" ~ "netcon", TRUE ~ TopRole)) %>% 
   dplyr::select(TrophicSpecies, FunctionalGroup, TotalDegree, NumPrey, NumPred, Between, Close, TL, meanTrophicSimil, TopRole) %>% 
@@
                                      TrophicSpecies == "Campylaspis_spp" ~ "Cumacea",
-                                                  TRUE ~ FunctionalGroup)), 
-             format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Group","Degree","NumPrey","NumPred","Between","Close","TL","TS","TR"), align = "llcccccccc", caption = "Species-level properties for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
+                                     TRUE ~ FunctionalGroup))
+# tbl_31 <- kableExtra::kbl(tbl_3, format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Group","Degree","NumPrey","NumPred","Between","Close","TL","TS","TR"), align = "llcccccccc", caption = "Species-level properties for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
 Ordered by degree (total number of interactions).
-Between: betweenness; Close: closeness; TL: trophic level; TS: trophic similarity; TR: topological role (netcon = network connector, modcon = module connector, modhub = module hub, modspe = module specialist).") %>%
-  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 4.5)
+Between: betweenness; Close: closeness; TL: trophic level; TS: trophic similarity; TR: topological role (netcon = network connector, modcon = module connector, modhub = module hub, modspe = module specialist).")
+# tbl_32 <- kableExtra::kable_styling(tbl_31, latex_options = c("hold_position", "repeat_header"), font_size = 4.5)
+
+pandoc.table(tbl_3 %>% arrange(., (TotalDegree)) %>% rename("Species"="TrophicSpecies", "Group"="FunctionalGroup", "Degree"="TotalDegree", "TS"="meanTrophicSimil", "TR"="TopRole"), style="multiline", split.tables = Inf, justify = c("left","left","center","left","left","left","left","left","left","left"),
+             caption = "Species-level properties for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
+Ordered by degree (total number of interactions).
+Between: betweenness; Close: closeness; TL: trophic level; TS: trophic similarity; TR: topological role (netcon = network connector, modcon = module connector, modhub = module hub, modspe = module specialist).")
 
@@
 
+\elandscape
 \newpage
@@
 
-```{r toprole_graph, echo=FALSE, fig.width = 20, fig.height=20, fig.cap="Graph of the food web showing species coloured by topological role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green).
+```{r toprole_graph, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 20, fig.height=20, fig.cap="Graph of the food web showing species coloured by topological role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green).
 Circle diameter is relative to the number of interactions."}

### 2024-01-11 R/6_figures.R
Tidy script

@@ -1,12 +1,12 @@
-## FIGURES: RED TRÓFICA AMP NAMUNCURÁ-BANCO BURDWOOD
-# Autor: Tomás Ignacio Marina
-# Fecha: 18/08/2022
+## FIGURES: FOOD WEB AMP NAMUNCURÁ-BANCO BURDWOOD
+# Author: Tomás Ignacio Marina
+# Date: 18/08/2022 - 14/11/2023
 
 
-# Paquetes ----
+# Load packages ----------------------------------------------------------------
 
 packages <- c("tidyverse", "ggplot2", "ggjoy", "ggpubr", "scales", 
-              "multiweb", "igraph")
+              "multiweb", "igraph", "grid")
 ipak <- function(pkg){
   new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
   if (length(new.pkg))
@@ -16,100 +16,195 @@ ipak <- function(pkg){
 ipak(packages)
 
 
-# Cargar datos ----
+# Load previous results ---------------------------------------------------
 
 load("results/summary_results_jul23.rda")
+load("data/foodweb-data_jul23.rda")
 
 
-# Figuras ----
+# Figures -----------------------------------------------------------------
 
-## Escala global ----
+## Figure 2 ----
 
-# Red trófica por degree
-plot_troph_level(g_up, ylab = "Trophic level")
+par(cex.axis=0.8, cex.lab=0.8)
+figure_2 <- plot_troph_level(g, vertexLabel = F, modules = F, ylab = "Trophic level",
+                             tk = T)
 
-# Distribución de grado
-# Histograma
+## Figure 3 ----
+
+### Network degree ----
 degree <- as.data.frame(degree(g, mode = "total"))
-(plot_distdegree <- ggplot(degree, aes(degree[,1])) +
-    geom_histogram(bins = 100, alpha = 0.3, color = "black") +
-    labs(x = "Degree", y = "Frequency") +
-    theme_bw() +
-    theme(legend.position = "none",
-          axis.text.x = element_text(size = 14),
-          axis.text.y = element_text(size = 14),
-          axis.title.x = element_text(face = "bold", size = 16),
-          axis.title.y = element_text(face = "bold", size = 16)))
+plot_totdeg <- ggplot(degree, aes(degree[,1])) +
+  geom_histogram(bins = 100, alpha = 0.3, color = "black") +
+  labs(x = "Degree (total interactions)", y = "Frequency") +
+  theme_bw() +
[…]

### 2024-01-11 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Minor changes

@@
 # Arrange figure
-figure_ab <- ggarrange(plot_sp_bt + rremove("xlab"), plot_sp_cl + rremove("xlab"),
+figure_ab <- ggarrange(plot_sp_ts + rremove("xlab"), plot_sp_cl + rremove("xlab"),
                       labels = c("A","B"), ncol=2,
@@
 figure_4 <- ggarrange(figure_ab,                                                                                         # First row
-          ggarrange(plot_sp_ts, plot_sp_tr, ncol = 2, labels = c("C", "D"), font.label=list(color="black",size=10)),                                            
+          ggarrange(plot_sp_bt, plot_sp_tr, ncol = 2, labels = c("C", "D"), font.label=list(color="black",size=10)),                                            
           nrow = 2)

### 2024-01-11 MS_ToSubmit/OriginallySubmittedVersion.Rmd
Fix format

--- 2024-01-11 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
@@
 ---
-title: The complex network of trophic interactions in a subAntarctic oceanic Marine Protected Area
-author:
-  - name: Tomás I. Marina^a^
-    email: tomasimarina@gmail.com
-    correspondingauthor: true
-  - name: Irene R. Schloss^a^^,^^b^^,^^c^
-  - name: Gustavo A. Lovrich^a^
-  - name: Claudia C. Boy^a^
-  - name: Daniel O. Bruno^a^^,^^c^
-  - name: Fabiana L. Capitanio^d^^,^^e^
-  - name: Sergio M. Delpiani^f^
-  - name: Juan Martín Díaz de Astarloa^f^
-  - name: Cintia Fraysse^a^
-  - name: Virginia A. García Alonso^d^^,^^e^
-  - name: Andrea Raya Rey^a^^,^^c^^,^^g^
-  - name: Laura Schejter^h^
-  - name: Mariela L. Spinelli^d^^,^^e^
-  - name: Marcos Tatián^i^^,^^j^
-  - name: Diego Urteaga^k^
-  - name: Luciana Riccialdelli^a^
+output:
+  pdf_document:
+    latex_engine: xelatex
+    keep_tex: yes
+  word_document: default
+bibliography: AMPBancoBurdwood.bib
+csl: "elsevier-harvard2.csl"
+documentclass: article
+geometry:
+- vmargin=1in
+- hmargin=1in
+header-includes:
+- \usepackage{amsmath}
+- \usepackage{pdflscape,booktabs}
+- \newcommand{\blandscape}{\begin{landscape}}
+- \newcommand{\elandscape}{\end{landscape}}
+- \usepackage[running]{lineno}
+- \linenumbers
+---
 
-address:
-  - code: 1
-    address: Centro Austral de Investigaciones Científicas (CADIC-CONICET), Ushuaia, Argentina
-  - code: 2
-    address: Instituto Antártico Argentino (IAA), CABA, Argentina
-  - code: 3
-    address: Instituto de Ciencias Polares, Ambiente y Recursos Naturales (ICPA), Universidad de Tierra del Fuego (UNTDF), Ushuaia, Argentina
-  - code: 4
-    address: Facultad de Ciencias Exactas y Naturales, Universidad de Buenos Aires (UBA), CABA, Argentina
-  - code: 5
-    address: Instituto de Biodiversidad y Biología Experimental y Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, CABA, Argentina
-  - code: 6
-    address: Instituto de Investigaciones Marinas y Costeras (IIMYC), Universidad Nacional de Mar del Plata-CONICET, Mar del Plata, Argentina
-  - code: 7
-    address: Wildlife Conservation Society, Argentina
-  - code: 8
-    address: Instituto Nacional de Investigación y Desarrollo Pesquero (INIDEP), Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET), Mar del Plata, Argentina
-  - code: 9
-    address: Facultad de Ciencias Exactas, Físicas y Naturales, Universidad Nacional de Córdoba (UNC), Córdoba, Argentina
-  - code: 10
-    address: Instituto de Diversidad y Ecología Animal (IDEA-CONICET), Córdoba, Argentina
-  - code: 11
-    address: Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, CABA, Argentina
-abstract: |
-  Abstract: The total area of the world ocean designated under marine protection has increased recently.
+# The complex network of trophic interactions in a subAntarctic oceanic Marine Protected Area
+
+## Abstract
+
+The total area of the world ocean designated under marine protection has increased recently.
 Most Marine Protected Areas (MPAs) target vulnerable, keystone, charismatic and or endemic species.
@@
 We argue that the diversity of species, including both the benthic and pelagic habitats, is responsible for securing the connectivity within the food web against perturbations, therefore contributing to the structure and stability of the ecosystem.
-keywords: 
-  - Food Web
-  - Complexity
-  - Structure
-  - Burdwood Bank
-  - Southwest Atlantic
-classoption: preprint, 3p, authoryear
-bibliography: AMPBancoBurdwood.bib
-linenumbers: true
-numbersections: true
-# Use a CSL with `citation_package = "default"`
-csl: "elsevier-harvard2.csl"
-output: 
-  rticles::elsevier_article:
-    latex_engine: xelatex
-    keep_tex: true
-    citation_package: "default"
----
 
-```{r setup, include=FALSE, echo=FALSE}
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+Keywords: Food Web, Complexity, Structure, Burdwood Bank, Southwest Atlantic
 
-library(knitr)
-library(tidyverse)
-library(pander)
-library(ggplot2)
-library(kableExtra)
-library(multiweb)
-library(ggjoy)
-library(ggpubr)
-library(igraph)
-library(gridExtra)
-library(grid)
-
-```
-
-# Introduction
+## 1. Introduction
 
@@
 
-# Methodology
+## 2. Methodology
 
-## Study area
+### 2.1. Study area
 
@@
 
-```{r figure1, echo=FALSE, fig.width = 5, fig.height = 10, out.width = '100%', fig.cap="Marine Protected Areas Namuncurá - Burdwood Bank I (MNR and MNP, northern section) and II (MNR and SMNR, southern section).
-Acronyms indicate categories according to the management plan: MNR - Marine National Reserve, MNP - Marine National Park and RMNR - Restricted Marine National Reserve."}
-
-knitr::include_graphics("MPABurdwood_map.jpg")
-
-```
-
-## Network construction
+### 2.2. Network construction
 
@@
 
-## Network analysis
+### 2.3. Network analysis
 
@@
 
-```{r table1, echo=FALSE, results='asis'}
+## 3. Results
+
+### 3.1. Network-level properties
+
+In terms of complexity, the MPA Namuncurá - Burdwood Bank food web consisted of 1788 predator-prey interactions and 379 species, where 93% of them were defined at the species taxonomical level (Figure 2, Table S2).
+The food web presented a link density (e.g., the average number of interactions per species) of 4.72, and a connectance of 0.01.
+Almost half of the consumers were omnivores (0.48), feeding on sources at different trophic levels.
+The food web displayed a small-world pattern, meaning that the path length was lower and the clustering coefficient higher than the random networks (Table 2).
+
+The degree distribution of the food web showed an asymmetric frequency in the number of interactions, where most of the species had a relatively low number of interactions and few species concentrated most of them (Figure 3A).
+The distribution of prey among predators showed that most consumers fed on a low number of prey whereas few had multiple prey (Figure 3B).
+The top-five predators in number of prey were: yellowfin notothen *Patagonotothen guntheri* (Notothenioid fish, 50 prey), rock cod *Patagonotothen ramsayi* (Notothenioid fish, 49 prey), broad nose skate *Bathyraja brachyurops* (Chondrichthyan, 33 prey), Patagonian toothfish *Dissostichus eleginoides* (Notothenioid fish, 30 prey), and graytail skate *Bathyraja griseocauda* (Chondrichthyan, 28 prey).
+Following the same distribution pattern, few prey presented multiple predators (Figure 3C).
+The top-five prey (or food sources) in number of predators were: Detritus (Non-living, 153 predators), the three categories of Diatoms considered (benthic, centric and pennate, 72.5 predators on average), and species of the genus *Euphausia* (Zooplankton, 46 predators).
+Finally, taking into account the interactions within each functional group, most interactions were concentrated in a few species (Figure 3D).
+The most evident species were: *Doryteuthis gahi* (Cephalopoda), *Grimothea (=Munida) gregaria* (Decapoda), *Patagonotothen ramsayi*, *Patagonotothen guntheri* and *Dissostichus eleginoides* (bentho-pelagic fish), *Sprattus fuegensis* and *Micromesistius australis* (pelagic fish), and species of *Euphausia* and *Themisto gaudichaudii* (Zooplankton).
+Overall, there is an evident asymmetry in the distribution of interactions among species at different levels in the MPA N-BB food web.
+
+A list of the distribution of interactions per species is presented in Supplementary Material (Table S3).
+
+### 3.2. Species-level properties
+
+We found different relationships between the species trophic level (TL) and the rest of the analysed species-level properties (Figure 4A-D).
+The most evident significant relationship was with trophic similarity, i.e.
+the higher the species' TL, the lower the trophic similarity or the higher the uniqueness in terms of trophic role (Figure 4C).
+Here it is noteworthy to highlight those high-trophic level species (TL > 3.1) with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster* sp.
+(echinoderms), *Daption capense* and *Eudyptes chrysocome* (seabirds), Ziphiidae and *Lagenorhynchus cruciger* (marine mammals) (Table S3).
+
+We also found a significant negative relationship between TL and closeness, however less evident, meaning that low-TL species are relatively closer to any other species in the food web (Figure 4B).
+Detritus, species of genera *Calanus* and *Euphausia*, and Foraminifera, all with TL < 3, registered the highest closeness values (Table S3).
+
+Notably, species of mid-TLs (3-4.2) showed the highest values of betweenness, meaning that those species participated in the highest number of shortest paths between species (Figure 4A).
+The following are the species with the highest values (descending order): *Patagonotothen ramsayi*, *Salilota australis*, *Dissostichus eleginoides* (fishes), *Doryteuthis gahi* (Cephalopoda), and *Patagonotothen guntheri* (Notothenioid fish) (Table S3).
+
+Considering the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.78), as well as 'module hub' species (TL = 1 - 3.92); 'module connector' was constrained to mid-TLs (2 - 3.86); and 'network connector', was represented by only one trophic species: detritus (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework).
+Here it is important to highlight the two latter topological roles because they are responsible for linking modules and maintaining the connectivity of the food web: 42 species (1 network connector + 41 module connectors) from 19 different functional groups with a TL range = 1 - 3.86.
+The 41 species with a module connector role represented these functional groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Hydrozoa (as 'Cnidaria_benthic'), Copepoda, Cumacea, Decapoda, Echinodermata, fish (bentho-pelagic and demersal Osteichthyes, and Chondrychthyes), Foraminifera, Polychaeta, Porifera, Pycnogonida (as 'Benthos_Misc') and zooplankton (see Supplementary Material Table S3 for the identity of the species).
+
+An exhaustive list of the species-level properties is presented in Supplementary Material (Table S3).
+
+## 4. Discussion
+
+### 4.1. The food web of the MPA Namuncurá - Burdwood Bank ecosystem
+
+The food web of the MPA N-BB ecosystem analysed in this study is one of the most highly-resolved networks of trophic interactions ever studied, not only for a high-latitude open-ocean ecosystem but also for any marine protected area worldwide to our knowledge.
+It is of paramount importance to consider the complexity of species interactions in order to gain insights into the structure and functioning of the ecosystem, since the aggregation of species might mask food web properties and produce type II errors (false positives) [@Martinez1993; @Gauzens2013].
+
+Food web connectance is a feature that resumes the complexity of the network, but more importantly, it is an emergent property of pairwise species interactions [@Poisot2014].
+It contains information regarding how interactions within an ecological network are distributed and predicts reasonably well key dynamical properties of ecological networks [@Dunne2002a].
+Complex marine food webs (i.e.
+with more than 25 trophic species) show connectance values ranging from 0.01 - 0.27 [@Marina2018a].
+In particular, food webs from high-latitude regions tend to exhibit a connectance closer to the minimum (between 0.01 and 0.05) [@Santana2013; @Kortsch2015; @Rodriguez2022].
+Whether food webs display a low or a high connectance helps to better comprehend ecosystem's synthetic properties like robustness.
+In this sense, empirical analyses support the notion that highly-connected ecological networks are robust against external perturbations such as the introduction of new (e.g., invasive) species [@Smith-Ramesh2017] as well as species removal (e.g., local extinction) [@Dunne2002; @Montoya2003].
+The connectance of the food web of the MPA Namuncurá - Burdwood Bank (0.01) is one of the lowest reported so far for these regions; in particular, it appears to be much lower than that of Beagle Channel (0.05), an adjacent coastal area [@Rodriguez2022].
+
+The degree distribution, the distribution of the number of interactions per species, is the core of the structure of species interactions, which influences the opportunities for multiple species to persist in the long term and, therefore, their coexistence [@Godoy2018].
+The food web for the MPA N-BB presents an asymmetric degree distribution.
+This pattern was identified at different levels of analysis: food web, predator, prey, and functional group.
+Such asymmetry is a well-known feature in empirical complex food webs in particular [@Dunne2002a; @Montoya2003; @Stouffer2005], and has received great attention in complex networks in general [@Albert2002; @Newman2003].
+The degree distribution affects the resilience of complex food webs against random failures and pressure on a particular component of the web: food webs showing right-skewed distributions, like the one described in this study, are more vulnerable to the removal of the most connected species or hubs, with the potential of producing secondary extinctions and a catastrophic fragmentation of the network [@Albert2000; @Dunne2002; @Eklof2006].
+
+It is suggested that the small-world pattern, i.e., a network with short path length and high clustering coefficient, is not frequent in complex marine food webs, mainly due to a low clustering coefficient compared to random networks [@Dunne2002b; @Marina2018a].
+However, the food web of the MPA N-BB does display a small-world pattern.
+Consequences of this could be of great importance in recognizing species evolutionary paths and the vulnerability to perturbations [@Montoya2002].
+On the one hand, a short path length implies a rapid spread of an impact (e.g., contaminant, population fluctuation, local extinction) throughout the network but, at the same time, more potentially adaptive dynamics in the face of external perturbations [@Montoya2002; @Williams2002].
+On the other hand, a high clustering coefficient indicates the formation of subnetworks composed only by the neighbours of particular species.
+This translates into a greater resistance of the network due to the confinement of perturbations mainly within subnetworks and not spreading between them [@Kortsch2019; @Heer2020].
+Overall, a small-world topology provides ecological networks with greater resilience and resistance [@Bornatowski2017; @Dormann2017].
+
+Omnivory acts as a buffer to changes as the ecosystem presents alternative energy pathways in the face of perturbations, i.e., reducing the risk of cascading extinctions following the primary loss of species [@Borrvall2000].
+Omnivores are species able to adapt faster and to a broader range of environmental conditions by changing their foraging habits to feed on the most abundant prey [@Fagan1997].
+Furthermore, omnivory can be analysed from the interaction point of view: theoretical studies have identified omnivorous interactions as a possible candidate for a keystone interaction, sensu @Kadoya2018, highlighting the importance of omnivory in stabilizing food web dynamics [@McCann1997; @Neutel2002].
+The high proportion of omnivory in the food web of the MPA N-BB suggests that the network might be robust to variations in prey abundances, which could increase food web's persistence and stability [@Stouffer2010].
+
+In summary, the food web of the MPA N-BB presents a combination of network properties that makes it unique in terms of network resolution, complexity, and structural pattern.
+All this suggests that the food web might be fragile to external perturbations targeting highly connected species, which in turn coincides to be commercial exploited species as fishes [@Laptikhovsky2013; @Martinez2015; @Winter2023].
+However, structural properties might provide resilience and resistance with the final outcome of a rearranged structure maintaining its functions.
+
+### 4.2. Dominant consumers and food sources
+
+The degree distribution allows identifying important species, such as potential keystone species (i.e.
+highly connected) [@Sole2001; @Dunne2002], generalist/specialist species, and dominant food sources [@Kondoh2010].
+
+We have identified that most of the consumers in the food web of the MPA N-BB either have a narrow diet or are specialists, while few present a broad or generalist diet.
+The most evident generalist species are *Patagonotothen guntheri* [@CovattiAle2022], *P.
+ramsayi* [@Fischer2022], juveniles of *Dissostichus eleginoides* [@Troccoli2020], *Bathyraja brachyurops* [@Belleggia2008a], and *B.
+griseocauda* [@Bellegia2014], with more than 25 potential prey.
+Since these species present mid-trophic positions in the food web (with the exception of adults of *Dissostichus eleginoides* that are top predators), acting as predator and prey, they might be important links between lower and higher trophic levels.
+This result is in agreement with the sole analysis, using stable isotopes, that exists so far for the trophic structure of the MPA N-BB [@Riccialdelli2020], and resembles other high-latitude marine systems of the Southwest Atlantic and Antarctic regions [@Arkhipkin2013; @Marina2018].
+The importance of these particular generalist species also arises since they feed in the benthic and pelagic habitats [@Troccoli2020; @CovattiAle2022; @Fischer2022], linking these realms and contributing to the vertical carbon flow.
+
+On the other hand, a low number of prey are consumed by many predators in the food web of the MPA N-BB.
+This suggests that there are dominant food sources on which most consumers depend and from where the ecosystem energy is being transferred to the upper trophic levels.
+The most demanded source we identified in this study (i.e.
+detritus) supports the abundant benthic community of filter-feeders [@Schejter2016], components of the animal forest [@Schejter2020], likely feeding on detritus that is constantly resuspended from the bottom [@Martin2021].
+Furthermore, we found that the second and third-most consumed prey were diatoms and species of *Euphausia*, respectively, which are essential sources for the diverse zooplankton community [@Spinelli2020], mid-TL consumers like the Fuegian sprat *Sprattus fuegensis* [@Padovani2021] and *Patagonotothen ramsayi* [@Fischer2022], and top predators such as the black-browed and grey-headed albatrosses (*Thalassarche melanophris* and *Thalassarche chrysostoma*, respectively) [@Catry2004], and baleen whales (species of the genera *Balaenoptera* and *Eubalaena*) [@Valenzuela2018].
+
+### 4.3. Species' role related to their trophic level
+
+Describing species’ roles in food webs provides a toolbox to assess the significance of species in terms of community's functioning and overall stability [@Thebault2010; @Cirtwill2018].
+We used a range of descriptors to characterise the dynamic and multifaceted nature of the species forming the MPA N-BB food web.
+
+Closeness and betweenness are defined as "mesoscale" properties because they consider direct and indirect interactions, therefore describing the focal species’ ability to influence the rest of the species of the food web [@Lai2012].
+Closeness quantifies how many steps away species $i$ is from all other species in the food web, and is proportional to how rapidly the indirect effects of the focal species can spread to other species in the network [@Scotti2010].
+In the food web of the MPA N-BB, low-TL consumers arise as important in this regard: species of the zooplankton community, *Calanus* and *Euphausia*, *Zygochlamys patagonica* (Bivalvia), and Brachiopoda.
+Any perturbation affecting these species, such as the recently confirmed contaminants mercury [@Fioramonti2022] and microplastics [@Cossi2021; @DiMauro2022], should be of concern since it might reach many other species in the food web.
+Otherwise, betweenness measures the number of shortest paths between species, providing information on the importance of species as “bridges” for energy transfer: a species with high betweenness takes part in more food chains and therefore affects more energy flows [@Scotti2010].
+We have identified the longtail southern cod *Patagonotothen ramsayi* as the most important species in this sense.
+Moreover, in light of our analysis, other species like the Patagonian toothfish *Dissostichus eleginoides* (juveniles), the Patagonian cod *Salilota australis*, the yellowfin notothenioid *Patagonotothen guntheri*, and the Patagonian longfin squid *Doryteuthis gahi* should be considered as relevant in the energy transfer in the ecosystem.
+All these species have a mid-trophic position in the food web, supporting the 'wasp-waist' control hypothesis for the MPA N-BB [@Riccialdelli2020].
+
+Ecosystems with a pronounced 'wasp-waist' structure are suggested to present a high trophic redundancy, since many species would show similar trophic habits [@Cury2000].
+The significant negative relationship between trophic similarity and trophic level enhances the hypothesis of functional similarity at low and mid-TL species compared to higher TL species for the MPA N-BB food web [@Riccialdelli2020].
+At the same time, our results highlight the uniqueness in terms of the trophic role of high-TL predators.
+Here, not only the expected pelagic animals such as marine mammals and seabirds arise as relevant, but also demersal vertebrate (chondrichthyans *Bathyraja macloviana* and *Squalus acanthias*) and benthic invertebrate species (echinoderms *Diplopteraster clarki* and *Pteraster* sp.) are noteworthy.
+The role that such species play in the MPA N-BB ecosystem is unique and perturbations on them might result in unprecedented changes at the trophic structure and functioning level.
+In this regard, we should mention the potential threat of the fisheries operating in the western section of the MPA N-BB, where this activity is allowed and mostly focuses on the Patagonian toothfish *Dissostichus eleginoides* and the southern blue whiting *Micromesistius australis* [@Martinez2015].
+Although the fishing effort is concentrated outside the limits of the MPA N-BB, the impact on the MPA ecosystem should not be neglected [@Martinez2021].
+
+Species' role can also be assessed in a module-based context.
+Among the varying numbers of topological roles in which species can be divided, two are remarkable: 'module connector' and 'network connector'.
+Here, our results point out that there are several species, belonging to a wide range of trophic positions (1 to 3.86) and representing 17 different functional groups, that should be considered as influential species for the connectivity of the food web.
+Thus, we propose that the diversity of species (benthic and pelagic) maintains the connectivity of the food web, therefore contributing to the trophic structure and ecosystem's stability.
+
+### 4.4. Caveats and future perspectives
+
+The food web studied in the present work might be more representative of the shallow ecosystem of the submarine plateau called Burdwood Bank, on which most of the research was focused as the MPA N-BB I was first created.
+This is related to the sampling effort that was conducted during the research cruises in the former MPA compared to the MPA N-BB II (i.e.
+deep flanks to the south).
+As a consequence, most of the data we used to build the network come from studies performed in the MPA N-BB I.
+Despite this fact, we decided to build the food web considering both MPAs due to the tight oceanographic and ecological connection that exists among them [@AdministraciondeParquesNacionales2022 and references therein].
+
+It's important to mark that we did not consider quantitative data (i.e.
+abundance, biomass) to assess the species' role in the food web.
+Although there exists such data for some species [@Schejter2021], it would not be possible to include it in the food web framework described here due to a taxonomical resolution mismatch.
+In this regard, we should mention the case of *Zygochlamys patagonica* (Bivalvia) and Brachiopoda that are highlighted by our species-level analyses though they have been found in low abundances in the area [@Schejter2021].
+
+Some species of sessile suspension feeders in high-latitude marine ecosystems, such as sponges, ascidians and octocorals, avoid predation by producing secondary metabolites that function as a chemical defense [@Nunez-Pons2010; @Moles2015; @Prieto2022].
+Although this was not yet recorded at the MPA N-BB, there are a few studies that reported it in other locations in species that inhabit the MPA N-BB [@RojodeAlmeida2010].
+
+The MPA N-BB I presents complex oceanographic conditions that generate an internal spatial heterogeneity, mainly along its longitudinal axis [@Matano2019].
+So far this heterogeneity has been reflected in phytoplankton and zooplankton communities [@Bertola2018; @GarciaAlonso2020; @Spinelli2020], and in fish assemblages [@Delpiani2020].
+Moreover, seasonal variations also occur in some physical and biological aspects of the MPA N-BB I [@GarciaAlonso2018; @Matano2019].
+Considering both MPAs (N-BB I and II), a seasonal variation in the community composition of marine mammals and seabirds was recorded recently [@Dellabianca2023].
+The spatial and seasonal variations in the plankton community might affect the energy and matter flow to higher levels of the food web.
+This has been recently studied in the vicinity of the MPA N-BB I, in the Beagle Channel, where a differential energy flow pattern of the plankton community has been recognised in two micro-basins of the Channel separated by a sill, each with different physicochemical properties [@Giesecke2021], nutrient concentration [@Latorre2023] as well as in the dominant component of the plankton community [@Bruno2023a; @Presta2023].
+Although we were aware of the above, we decided to characterise a food web representing the whole MPA N-BB I year round since this is the first study of its type in the area.
+
+Taking into account the mentioned caveats, and with the aim of improving the knowledge regarding the structure, functioning and stability of the MPA N-BB, we suggest that the future perspectives should: 1) incorporate spatial heterogeneity among MPA N-BB I and II [@Schejter2021], which might lead to distinct food web properties in terms of structure and functioning [@Kortsch2019; @Cordone2020]; 2) include species traits, like body size and mass, since they are known to be important drivers in predator-prey interactions [@Brose2019]; 3) simulate the anthropogenic impacts already present in the MPA N-BB ecosystem (e.g.
+microplastics, mercury) [@Cossi2021; @DiMauro2022; @Fioramonti2022] as perturbations within the framework of the described complex food web; and 4) estimate the interaction strength of each predator-prey relationship in the food web considering species and interaction traits (i.e.
+body size, body mass, interaction dimensionality), and species density data [@Nilsson2016; @Pawar2012].
+
+## 5. Conclusion
+
+We compiled information on the species and trophic diversity of the oceanic Marine Protected Area Namuncurá - Burdwood Bank, generating an unprecedented, well-resolved network of trophic interactions for a sub-Antarctic ecosystem, identifying the complexity and structure of the system, and the main species role in a network framework.
+Particular properties at the network level allowed us to identify the ecosystem's vulnerability and potential response to perturbations in the presence of highly-connected species, with a rearranged structure maintaining their functions due to its potential resilience and resistance.
+
+We identified several species as important regarding different aspects of trophic structure and functioning, and response to perturbations (i.e.
+environmental/anthropogenic changes).
+On the one hand, we suggest that generalist species, mainly fishes, play a crucial role in the ecosystem's bentho-pelagic coupling process.
+At the same time, we propose that other species besides the longtail southern cod *Patagonotothen ramsayi* and the Fueguian sprat *Sprattus fuegensis* should be considered relevant energy transfers for the ecosystem.
+Finally, we argue that it is the diversity of species, representing the benthic and pelagic habitats, that maintains the connectivity of the food web against perturbations, therefore contributing to the structure and stability of the ecosystem.
+
+## Acknowledgements
+
+We are indebted to all those experts of the working group 'Banco Burdwood' who humbly provided their knowledge to enhance the quality of the present research.
+Although most of them are authors of the present work, it is worth to mention the following researchers: Brenda L.
+Doti (IBBEA, CONICET-UBA; Universidad de Buenos Aires, Argentina), Sofía L.
+Callá (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina), Sandra Gordillo (IDACOR-CONICET; Universidad Nacional de Córdoba, Argentina), Mariano I.
+Martinez (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina) and Luciano Padovani (Instituto Nacional de Investigación y Desarrollo Pesquero, INIDEP, Argentina).
+We thank the MPA Namuncurá - Burdwood Bank administration.
+Research cruises were funded by national funds by the Law 26.875.
+This study was funded by Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de Promoción Científica y Tecnológica (PICT 2020 SERIEA 01617), Argentina.
+This work is contribution no.
+XX of the MPA Namuncurá (Law 26.875).
+
+## Tables
+
+```{r table1, echo=FALSE, message=FALSE, results='asis'}
+
+require(tidyverse)
+require(pander)
 
@@
 
-# Results
+```{r tableS2, echo=FALSE, message=FALSE, results='asis'}
+require(pander)
+require(tidyverse)
 
-## Network-level properties
+load("../results/summary_results_jul23.rda")
 
-In terms of complexity, the MPA Namuncurá - Burdwood Bank food web consisted of 1788 predator-prey interactions and 379 species, where 93% of them were defined at the species taxonomical level (Figure 2, Table S2).
-The food web presented a link density (e.g., the average number of interactions per species) of 4.72, and a connectance of 0.01.
-Almost half of the consumers were omnivores (0.48), feeding on sources at different trophic levels.
-The food web displayed a small-world pattern, meaning that the path length was lower and the clustering coefficient higher than the random networks (Table 2).
+pandoc.table(round(prop_topol,2) %>% dplyr::select(Size, Links, LD, Connectance, Omnivory, PathLength, Clustering) %>% mutate(SW = "True"), col.names = c("Species","Interactions","Density","Connectance","Omnivory","CPL", "CC", "SW"), split.cells = c(1,1,1,1,1,1,1,1),
+                      caption = "Network-level properties of the MPA Namuncurá - Burdwood Bank food web.
+CPL: Characteristic Path Length; CC: Clustering Coefficient; SW: Small-World pattern.
+See table 1 for definitions and ecological relevance.")
 
-\newpage
+```
 
-```{r figure2, echo=FALSE, fig.width = 5.5, fig.height = 10, fig.align='center', fig.cap="Graph of the food web for the MPA Namuncurá - Burdwood Bank.
+## Figures
+
+```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 5, fig.height = 10, out.width = '100%', fig.cap="Marine Protected Areas Namuncurá - Burdwood Bank I (MNR and MNP, northern section) and II (MNR and SMNR, southern section).
+Acronyms indicate categories according to the management plan: MNR - Marine National Reserve, MNP - Marine National Park and RMNR - Restricted Marine National Reserve."}
+
+knitr::include_graphics("MPABurdwood_map.jpg")
+
+```
+
+```{r figure2, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 5.5, fig.height = 10, fig.align='center', fig.cap="Graph of the food web for the MPA Namuncurá - Burdwood Bank.
 Circles represent species and arrows trophic interactions.
@@
 
+# Packages
+require(multiweb)
+
+# Data
 load("../results/summary_results_jul23.rda")
@@
 
-```{r table2, echo=FALSE}
-
-load("../results/summary_results_jul23.rda")
-
-knitr::kable(round(prop_topol,2) %>% dplyr::select(Size, Links, LD, Connectance, Omnivory, PathLength, Clustering) %>% mutate(SW = "True"), col.names = c("Species","Interactions","Density","Connectance","Omnivory","CPL", "CC", "SW"),
-                      caption = "Network-level properties of the MPA Namuncurá - Burdwood Bank food web.
-CPL: Characteristic Path Length; CC: Clustering Coefficient; SW: Small-World pattern.
-See table 1 for definitions and ecological relevance.") %>% row_spec(0,bold=TRUE)
-
-```
-
-The degree distribution of the food web showed an asymmetric frequency in the number of interactions, where most of the species had a relatively low number of interactions and few species concentrated most of them (Figure 3A).
-The distribution of prey among predators showed that most consumers fed on a low number of prey whereas few had multiple prey (Figure 3B).
-The top-five predators in number of prey were: yellowfin notothen *Patagonotothen guntheri* (Notothenioid fish, 50 prey), rock cod *Patagonotothen ramsayi* (Notothenioid fish, 49 prey), broad nose skate *Bathyraja brachyurops* (Chondrichthyan, 33 prey), Patagonian toothfish *Dissostichus eleginoides* (Notothenioid fish, 30 prey), and graytail skate *Bathyraja griseocauda* (Chondrichthyan, 28 prey).
-Following the same distribution pattern, few prey presented multiple predators (Figure 3C).
-The top-five prey (or food sources) in number of predators were: Detritus (Non-living, 153 predators), the three categories of Diatoms considered (benthic, centric and pennate, 72.5 predators on average), and species of the genus *Euphausia* (Zooplankton, 46 predators).
-Finally, taking into account the interactions within each functional group, most interactions were concentrated in a few species (Figure 3D).
-The most evident species were: *Doryteuthis gahi* (Cephalopoda), *Grimothea (=Munida) gregaria* (Decapoda), *Patagonotothen ramsayi*, *Patagonotothen guntheri* and *Dissostichus eleginoides* (bentho-pelagic fish), *Sprattus fuegensis* and *Micromesistius australis* (pelagic fish), and species of *Euphausia* and *Themisto gaudichaudii* (Zooplankton).
-Overall, there is an evident asymmetry in the distribution of interactions among species at different levels in the MPA N-BB food web.
-
-A list of the distribution of interactions per species is presented in Supplementary Material (Table S3).
-
-```{r figure3, echo=FALSE, fig.width = 6.5, fig.height = 9, fig.align='center', fig.cap="Degree distributions for the (A) food web, for (B) prey among predators, (C) predators among prey, and (D) for each functional group.
+```{r figure3, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 6.5, fig.height = 9, fig.align='center', fig.cap="Degree distributions for the (A) food web, for (B) prey among predators, (C) predators among prey, and (D) for each functional group.
 Groups are vertically ordered by increasing trophic level (following coloration of figure 2); groups with less than 3 species were not plotted (e.g., pelagic fish).
@@
 # above row (network, prey, predator), below row (group)
+
+# Packages
+require(tidyverse)
+require(igraph)
+require(grid)
+require(ggpubr)
+require(ggplot2)
+require(ggjoy)
 
@@
 figure_3
-
 ```
 
-## Species-level properties
-
-We found different relationships between the species trophic level (TL) and the rest of the analysed species-level properties (Figure 4A-D).
-The most evident significant relationship was with trophic similarity, i.e.
-the higher the species' TL, the lower the trophic similarity or the higher the uniqueness in terms of trophic role (Figure 4C).
-Here it is noteworthy to highlight those high-trophic level species (TL > 3.1) with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster* sp.
-(echinoderms), *Daption capense* and *Eudyptes chrysocome* (seabirds), Ziphiidae and *Lagenorhynchus cruciger* (marine mammals) (Table S3).
-
-We also found a significant negative relationship between TL and closeness, however less evident, meaning that low-TL species are relatively closer to any other species in the food web (Figure 4B).
-Detritus, species of genera *Calanus* and *Euphausia*, and Foraminifera, all with TL < 3, registered the highest closeness values (Table S3).
-
-Notably, species of mid-TLs (3-4.2) showed the highest values of betweenness, meaning that those species participated in the highest number of shortest paths between species (Figure 4A).
-The following are the species with the highest values (descending order): *Patagonotothen ramsayi*, *Salilota australis*, *Dissostichus eleginoides* (fishes), *Doryteuthis gahi* (Cephalopoda), and *Patagonotothen guntheri* (Notothenioid fish) (Table S3).
-
-Considering the topological role, 'module specialist' species were the most frequent and presented a wide TL range (1 - 4.78), as well as 'module hub' species (TL = 1 - 3.92); 'module connector' was constrained to mid-TLs (2 - 3.86); and 'network connector', was represented by only one trophic species: detritus (Figure 4D, see Figure S2 for species' topological roles in a food web graph framework).
-Here it is important to highlight the two latter topological roles because they are responsible for linking modules and maintaining the connectivity of the food web: 42 species (1 network connector + 41 module connectors) from 19 different functional groups with a TL range = 1 - 3.86.
-The 41 species with a module connector role represented these functional groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Hydrozoa (as 'Cnidaria_benthic'), Copepoda, Cumacea, Decapoda, Echinodermata, fish (bentho-pelagic and demersal Osteichthyes, and Chondrychthyes), Foraminifera, Polychaeta, Porifera, Pycnogonida (as 'Benthos_Misc') and zooplankton (see Supplementary Material Table S3 for the identity of the species).
-
-An exhaustive list of the species-level properties is presented in Supplementary Material (Table S3).
-
-```{r figure4, echo=FALSE, fig.width = 6.5, fig.height = 6.5, fig.align='center', fig.cap="Species-level properties by trophic level: (A) betweenness, (B) closeness, (C) trophic similarity, and (D) topological role.
+```{r figure4, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 6.5, fig.height = 6.5, fig.align='center', fig.cap="Species-level properties by trophic level: (A) trophic similarity, (B) closeness, (C) betweenness, and (D) topological role.
 Each point represents a species.
@@
 # Betweenness, Closeness, Trophic similarity & Topological role by Trophic level
+require(tidyverse)
+require(igraph)
+require(grid)
+require(ggpubr)
 
@@
 # Arrange figure
-figure_ab <- ggarrange(plot_sp_ts + rremove("xlab"), plot_sp_cl + rremove("xlab"),
+figure_ab <- ggarrange(plot_sp_bt + rremove("xlab"), plot_sp_cl + rremove("xlab"),
                       labels = c("A","B"), ncol=2,
@@
 figure_4 <- ggarrange(figure_ab,                                                                                         # First row
-          ggarrange(plot_sp_bt, plot_sp_tr, ncol = 2, labels = c("C", "D"), font.label=list(color="black",size=10)),                                            
+          ggarrange(plot_sp_ts, plot_sp_tr, ncol = 2, labels = c("C", "D"), font.label=list(color="black",size=10)),                                            
           nrow = 2)
 figure_4
-
 ```
 
-# Discussion
+\newpage
 
-## The food web of the MPA Namuncurá - Burdwood Bank ecosystem
-
-The food web of the MPA N-BB ecosystem analysed in this study is one of the most highly-resolved networks of trophic interactions ever studied, not only for a high-latitude open-ocean ecosystem but also for any marine protected area worldwide to our knowledge.
-It is of paramount importance to consider the complexity of species interactions in order to gain insights into the structure and functioning of the ecosystem, since the aggregation of species might mask food web properties and produce type II errors (false positives) [@Martinez1993; @Gauzens2013].
-
-Food web connectance is a feature that resumes the complexity of the network, but more importantly, it is an emergent property of pairwise species interactions [@Poisot2014].
-It contains information regarding how interactions within an ecological network are distributed and predicts reasonably well key dynamical properties of ecological networks [@Dunne2002a].
-Complex marine food webs (i.e.
-with more than 25 trophic species) show connectance values ranging from 0.01 - 0.27 [@Marina2018a].
-In particular, food webs from high-latitude regions tend to exhibit a connectance closer to the minimum (between 0.01 and 0.05) [@Santana2013; @Kortsch2015; @Rodriguez2022].
-Whether food webs display a low or a high connectance helps to better comprehend ecosystem's synthetic properties like robustness.
-In this sense, empirical analyses support the notion that highly-connected ecological networks are robust against external perturbations such as the introduction of new (e.g., invasive) species [@Smith-Ramesh2017] as well as species removal (e.g., local extinction) [@Dunne2002; @Montoya2003].
-The connectance of the food web of the MPA Namuncurá - Burdwood Bank (0.01) is one of the lowest reported so far for these regions; in particular, it appears to be much lower than that of Beagle Channel (0.05), an adjacent coastal area [@Rodriguez2022].
-
-The degree distribution, the distribution of the number of interactions per species, is the core of the structure of species interactions, which influences the opportunities for multiple species to persist in the long term and, therefore, their coexistence [@Godoy2018].
-The food web for the MPA N-BB presents an asymmetric degree distribution.
-This pattern was identified at different levels of analysis: food web, predator, prey, and functional group.
-Such asymmetry is a well-known feature in empirical complex food webs in particular [@Dunne2002a; @Montoya2003; @Stouffer2005], and has received great attention in complex networks in general [@Albert2002; @Newman2003].
-The degree distribution affects the resilience of complex food webs against random failures and pressure on a particular component of the web: food webs showing right-skewed distributions, like the one described in this study, are more vulnerable to the removal of the most connected species or hubs, with the potential of producing secondary extinctions and a catastrophic fragmentation of the network [@Albert2000; @Dunne2002; @Eklof2006].
-
-It is suggested that the small-world pattern, i.e., a network with short path length and high clustering coefficient, is not frequent in complex marine food webs, mainly due to a low clustering coefficient compared to random networks [@Dunne2002b; @Marina2018a].
-However, the food web of the MPA N-BB does display a small-world pattern.
-Consequences of this could be of great importance in recognizing species evolutionary paths and the vulnerability to perturbations [@Montoya2002].
-On the one hand, a short path length implies a rapid spread of an impact (e.g., contaminant, population fluctuation, local extinction) throughout the network but, at the same time, more potentially adaptive dynamics in the face of external perturbations [@Montoya2002; @Williams2002].
-On the other hand, a high clustering coefficient indicates the formation of subnetworks composed only by the neighbours of particular species.
-This translates into a greater resistance of the network due to the confinement of perturbations mainly within subnetworks and not spreading between them [@Kortsch2019; @Heer2020].
-Overall, a small-world topology provides ecological networks with greater resilience and resistance [@Bornatowski2017; @Dormann2017].
-
-Omnivory acts as a buffer to changes as the ecosystem presents alternative energy pathways in the face of perturbations, i.e., reducing the risk of cascading extinctions following the primary loss of species [@Borrvall2000].
-Omnivores are species able to adapt faster and to a broader range of environmental conditions by changing their foraging habits to feed on the most abundant prey [@Fagan1997].
-Furthermore, omnivory can be analysed from the interaction point of view: theoretical studies have identified omnivorous interactions as a possible candidate for a keystone interaction, sensu @Kadoya2018, highlighting the importance of omnivory in stabilizing food web dynamics [@McCann1997; @Neutel2002].
-The high proportion of omnivory in the food web of the MPA N-BB suggests that the network might be robust to variations in prey abundances, which could increase food web's persistence and stability [@Stouffer2010].
-
-In summary, the food web of the MPA N-BB presents a combination of network properties that makes it unique in terms of network resolution, complexity, and structural pattern.
-All this suggests that the food web might be fragile to external perturbations targeting highly connected species, which in turn coincides to be commercial exploited species as fishes [@Laptikhovsky2013; @Martinez2015; @Winter2023].
-However, structural properties might provide resilience and resistance with the final outcome of a rearranged structure maintaining its functions.
-
-## Dominant consumers and food sources
-
-The degree distribution allows identifying important species, such as potential keystone species (i.e.
-highly connected) [@Sole2001; @Dunne2002], generalist/specialist species, and dominant food sources [@Kondoh2010].
-
-We have identified that most of the consumers in the food web of the MPA N-BB either have a narrow diet or are specialists, while few present a broad or generalist diet.
-The most evident generalist species are *Patagonotothen guntheri* [@CovattiAle2022], *P.
-ramsayi* [@Fischer2022], juveniles of *Dissostichus eleginoides* [@Troccoli2020], *Bathyraja brachyurops* [@Belleggia2008a], and *B.
-griseocauda* [@Bellegia2014], with more than 25 potential prey.
-Since these species present mid-trophic positions in the food web (with the exception of adults of *Dissostichus eleginoides* that are top predators), acting as predator and prey, they might be important links between lower and higher trophic levels.
-This result is in agreement with the sole analysis, using stable isotopes, that exists so far for the trophic structure of the MPA N-BB [@Riccialdelli2020], and resembles other high-latitude marine systems of the Southwest Atlantic and Antarctic regions [@Arkhipkin2013; @Marina2018].
-The importance of these particular generalist species also arises since they feed in the benthic and pelagic habitats [@Troccoli2020; @CovattiAle2022; @Fischer2022], linking these realms and contributing to the vertical carbon flow.
-
-On the other hand, a low number of prey are consumed by many predators in the food web of the MPA N-BB.
-This suggests that there are dominant food sources on which most consumers depend and from where the ecosystem energy is being transferred to the upper trophic levels.
-The most demanded source we identified in this study (i.e.
-detritus) supports the abundant benthic community of filter-feeders [@Schejter2016], components of the animal forest [@Schejter2020], likely feeding on detritus that is constantly resuspended from the bottom [@Martin2021].
-Furthermore, we found that the second and third-most consumed prey were diatoms and species of *Euphausia*, respectively, which are essential sources for the diverse zooplankton community [@Spinelli2020], mid-TL consumers like the Fuegian sprat *Sprattus fuegensis* [@Padovani2021] and *Patagonotothen ramsayi* [@Fischer2022], and top predators such as the black-browed and grey-headed albatrosses (*Thalassarche melanophris* and *Thalassarche chrysostoma*, respectively) [@Catry2004], and baleen whales (species of the genera *Balaenoptera* and *Eubalaena*) [@Valenzuela2018].
-
-## Species' role related to their trophic level
-
-Describing species’ roles in food webs provides a toolbox to assess the significance of species in terms of community's functioning and overall stability [@Thebault2010; @Cirtwill2018].
-We used a range of descriptors to characterise the dynamic and multifaceted nature of the species forming the MPA N-BB food web.
-
-Closeness and betweenness are defined as "mesoscale" properties because they consider direct and indirect interactions, therefore describing the focal species’ ability to influence the rest of the species of the food web [@Lai2012].
-Closeness quantifies how many steps away species $i$ is from all other species in the food web, and is proportional to how rapidly the indirect effects of the focal species can spread to other species in the network [@Scotti2010].
-In the food web of the MPA N-BB, low-TL consumers arise as important in this regard: species of the zooplankton community, *Calanus* and *Euphausia*, *Zygochlamys patagonica* (Bivalvia), and Brachiopoda.
-Any perturbation affecting these species, such as the recently confirmed contaminants mercury [@Fioramonti2022] and microplastics [@Cossi2021; @DiMauro2022], should be of concern since it might reach many other species in the food web.
-Otherwise, betweenness measures the number of shortest paths between species, providing information on the importance of species as “bridges” for energy transfer: a species with high betweenness takes part in more food chains and therefore affects more energy flows [@Scotti2010].
-We have identified the longtail southern cod *Patagonotothen ramsayi* as the most important species in this sense.
-Moreover, in light of our analysis, other species like the Patagonian toothfish *Dissostichus eleginoides* (juveniles), the Patagonian cod *Salilota australis*, the yellowfin notothenioid *Patagonotothen guntheri*, and the Patagonian longfin squid *Doryteuthis gahi* should be considered as relevant in the energy transfer in the ecosystem.
-All these species have a mid-trophic position in the food web, supporting the 'wasp-waist' control hypothesis for the MPA N-BB [@Riccialdelli2020].
-
-Ecosystems with a pronounced 'wasp-waist' structure are suggested to present a high trophic redundancy, since many species would show similar trophic habits [@Cury2000].
-The significant negative relationship between trophic similarity and trophic level enhances the hypothesis of functional similarity at low and mid-TL species compared to higher TL species for the MPA N-BB food web [@Riccialdelli2020].
-At the same time, our results highlight the uniqueness in terms of the trophic role of high-TL predators.
-Here, not only the expected pelagic animals such as marine mammals and seabirds arise as relevant, but also demersal vertebrate (chondrichthyans *Bathyraja macloviana* and *Squalus acanthias*) and benthic invertebrate species (echinoderms *Diplopteraster clarki* and *Pteraster* sp.) are noteworthy.
-The role that such species play in the MPA N-BB ecosystem is unique and perturbations on them might result in unprecedented changes at the trophic structure and functioning level.
-In this regard, we should mention the potential threat of the fisheries operating in the western section of the MPA N-BB, where this activity is allowed and mostly focuses on the Patagonian toothfish *Dissostichus eleginoides* and the southern blue whiting *Micromesistius australis* [@Martinez2015].
-Although the fishing effort is concentrated outside the limits of the MPA N-BB, the impact on the MPA ecosystem should not be neglected [@Martinez2021].
-
-Species' role can also be assessed in a module-based context.
-Among the varying numbers of topological roles in which species can be divided, two are remarkable: 'module connector' and 'network connector'.
-Here, our results point out that there are several species, belonging to a wide range of trophic positions (1 to 3.86) and representing 17 different functional groups, that should be considered as influential species for the connectivity of the food web.
-Thus, we propose that the diversity of species (benthic and pelagic) maintains the connectivity of the food web, therefore contributing to the trophic structure and ecosystem's stability.
-
-## Caveats and future perspectives
-
-The food web studied in the present work might be more representative of the shallow ecosystem of the submarine plateau called Burdwood Bank, on which most of the research was focused as the MPA N-BB I was first created.
-This is related to the sampling effort that was conducted during the research cruises in the former MPA compared to the MPA N-BB II (i.e.
-deep flanks to the south).
-As a consequence, most of the data we used to build the network come from studies performed in the MPA N-BB I.
-Despite this fact, we decided to build the food web considering both MPAs due to the tight oceanographic and ecological connection that exists among them [@AdministraciondeParquesNacionales2022 and references therein].
-
-It's important to mark that we did not consider quantitative data (i.e.
-abundance, biomass) to assess the species' role in the food web.
-Although there exists such data for some species [@Schejter2021], it would not be possible to include it in the food web framework described here due to a taxonomical resolution mismatch.
-In this regard, we should mention the case of *Zygochlamys patagonica* (Bivalvia) and Brachiopoda that are highlighted by our species-level analyses though they have been found in low abundances in the area [@Schejter2021].
-
-Some species of sessile suspension feeders in high-latitude marine ecosystems, such as sponges, ascidians and octocorals, avoid predation by producing secondary metabolites that function as a chemical defense [@Nunez-Pons2010; @Moles2015; @Prieto2022].
-Although this was not yet recorded at the MPA N-BB, there are a few studies that reported it in other locations in species that inhabit the MPA N-BB [@RojodeAlmeida2010].
-
-The MPA N-BB I presents complex oceanographic conditions that generate an internal spatial heterogeneity, mainly along its longitudinal axis [@Matano2019].
-So far this heterogeneity has been reflected in phytoplankton and zooplankton communities [@Bertola2018; @GarciaAlonso2020; @Spinelli2020], and in fish assemblages [@Delpiani2020].
-Moreover, seasonal variations also occur in some physical and biological aspects of the MPA N-BB I [@GarciaAlonso2018; @Matano2019].
-Considering both MPAs (N-BB I and II), a seasonal variation in the community composition of marine mammals and seabirds was recorded recently [@Dellabianca2023].
-The spatial and seasonal variations in the plankton community might affect the energy and matter flow to higher levels of the food web.
-This has been recently studied in the vicinity of the MPA N-BB I, in the Beagle Channel, where a differential energy flow pattern of the plankton community has been recognised in two micro-basins of the Channel separated by a sill, each with different physicochemical properties [@Giesecke2021], nutrient concentration [@Latorre2023] as well as in the dominant component of the plankton community [@Bruno2023a; @Presta2023].
-Although we were aware of the above, we decided to characterise a food web representing the whole MPA N-BB I year round since this is the first study of its type in the area.
-
-Taking into account the mentioned caveats, and with the aim of improving the knowledge regarding the structure, functioning and stability of the MPA N-BB, we suggest that the future perspectives should: 1) incorporate spatial heterogeneity among MPA N-BB I and II [@Schejter2021], which might lead to distinct food web properties in terms of structure and functioning [@Kortsch2019; @Cordone2020]; 2) include species traits, like body size and mass, since they are known to be important drivers in predator-prey interactions [@Brose2019]; 3) simulate the anthropogenic impacts already present in the MPA N-BB ecosystem (e.g.
-microplastics, mercury) [@Cossi2021; @DiMauro2022; @Fioramonti2022] as perturbations within the framework of the described complex food web; and 4) estimate the interaction strength of each predator-prey relationship in the food web considering species and interaction traits (i.e.
-body size, body mass, interaction dimensionality), and species density data [@Nilsson2016; @Pawar2012].
-
-# Conclusion
-
-We compiled information on the species and trophic diversity of the oceanic Marine Protected Area Namuncurá - Burdwood Bank, generating an unprecedented, well-resolved network of trophic interactions for a sub-Antarctic ecosystem, identifying the complexity and structure of the system, and the main species role in a network framework.
-Particular properties at the network level allowed us to identify the ecosystem's vulnerability and potential response to perturbations in the presence of highly-connected species, with a rearranged structure maintaining their functions due to its potential resilience and resistance.
-
-We identified several species as important regarding different aspects of trophic structure and functioning, and response to perturbations (i.e.
-environmental/anthropogenic changes).
-On the one hand, we suggest that generalist species, mainly fishes, play a crucial role in the ecosystem's bentho-pelagic coupling process.
-At the same time, we propose that other species besides the longtail southern cod *Patagonotothen ramsayi* and the Fueguian sprat *Sprattus fuegensis* should be considered relevant energy transfers for the ecosystem.
-Finally, we argue that it is the diversity of species, representing the benthic and pelagic habitats, that maintains the connectivity of the food web against perturbations, therefore contributing to the structure and stability of the ecosystem.
-
-# Acknowledgements
-
-We are indebted to all those experts of the working group 'Banco Burdwood' who humbly provided their knowledge to enhance the quality of the present research.
-Although most of them are authors of the present work, it is worth to mention the following researchers: Brenda L.
-Doti (IBBEA, CONICET-UBA; Universidad de Buenos Aires, Argentina), Sofía L.
-Callá (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina), Sandra Gordillo (IDACOR-CONICET; Universidad Nacional de Córdoba, Argentina), Mariano I.
-Martinez (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina) and Luciano Padovani (Instituto Nacional de Investigación y Desarrollo Pesquero, INIDEP, Argentina).
-We thank the MPA Namuncurá − Burdwood Bank administration.
-Research cruises were funded by national funds by the Law 26.875.
-This study was funded by Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617), Argentina.
-This work is contribution no.
-XX of the MPA Namuncurá (Law 26.875).
-
-# Literature Cited
+## References

### 2024-01-11 MS_ToSubmit/RevisedSupMaterial.Rmd
Revised Sup Mat

--- 2024-01-11 MS_ToSubmit/SupMaterial.Rmd
@@
 The following figure and tables summarise the data we used to build the network of trophic (predator-prey) interactions for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
-Figure 1 resumes the type and number of references reviewed.
+Figure 2 resumes the type and number of references reviewed.
 Table 1 is the complete list of trophic interactions and references that confirm each of them.
@@
 
-```{r ref_plot, echo=FALSE, message=FALSE, fig.cap="Summary of references used to build the network of trophic (predator-prey) interactions for the MPAN-BB ecosystem."}
+With the gathered trophic data, we constructed a matrix of pairwise interactions; a value of 1 or 0 was assigned to each element a_ij of the matrix depending on whether the predator j preyed or not on the prey i.
+Then we transformed such a matrix into an oriented graph with L trophic interactions between S nodes or species (Figure 1).
 
-# Load packages
-library(tidyverse)
-library(ggplot2)
+```{r, out.width = "12cm", echo = FALSE, message=FALSE, fig.align = 'center', fig.cap = "Matrix of pairwise interactions and the oriented graph (food web) derived from it.
+Number of species S = 9, number of interactions (L) = 15."}
+library(knitr)
+knitr::include_graphics("FigS1.png")
+```
 
-# Load data
-load("../data/cleaned-data_jul23.rda")
+### Network analysis
 
-# Discard low resolution interactions
-int_good_res <- int_raw %>% 
-  filter(!str_detect(Prey, "\\*$")) %>% 
-  filter(!str_detect(Predator, "\\*$")) %>% 
-  dplyr::select(Prey, Predator, PreyGroup, PredGroup, Reference) %>% 
-  distinct(Prey, Predator, .keep_all = TRUE)
+Trophic level
 
-# Figure 1. Plot resuming references
-biblio <- data.frame(unique(int_good_res$Reference))
-colnames(biblio) <- "Reference"
-biblio <- biblio %>% 
-  mutate(Type = case_when(str_detect(Reference, "pers.com.") ~ "PersComm",
-                          str_detect(Reference, "etal") ~ "Article",
-                          str_detect(Reference, "&") ~ "Article",
-                          str_detect(Reference, "Encyclopedia of Life") ~ "DataBase",
-                          str_detect(Reference, "GloBI") ~ "DataBase",
-                          str_detect(Reference, "GATEWAy") ~ "DataBase",
-                          str_detect(Reference, "PhDTesis") ~ "Thesis",
-                          TRUE ~ "Article"))
-ggplot(biblio) +
-  geom_bar(aes(x = Type, fill = Type)) +
-  theme_bw() +
-  labs(x = "Reference", y = "Count") +
-  annotate("text", x = Inf, y = Inf, label = paste("Total = ", nrow(biblio), sep = ""), vjust=1, hjust=1)
+Trophic levels (TL) of species were calculated using the shortweighted TL formula of @Williams2004.
+Shortweighted trophic level is defined as the average of the shortest TL and prey-averaged TL.
+Shortest TL of a consumer in a food web is equal to 1 + the shortest chain length from this consumer to any basal species [@Williams2004].
+Prey averaged TL is equal to 1 + the mean TL of all consumer's trophic resources, calculated as:
 
-```
+\begin{equation}
+TL_j = 1 + \sum_{i = 1}^{S} l_{ij} \frac{TL_i}{n_j}
+\end{equation}
+
+where $TL_j$ is the trophic level of species $j$; $S$ is the number of species in the food web; $l_{ij}$ is the connection matrix with $S$ rows and $S$ columns, in which for column $j$ and row $i$, $l_{ij}$ = 1 if species $j$ consumes species $i$ and $l_{ij}$ = 0 if not; and $n_j$ is the number of prey species in the diet of species $j$.
+For basal species TL = 1 given that they have no prey.
+
+Topological roles
+
+Beforehand, we need to calculate modularity.
+Modularity was calculated as the difference between realized and expected within-modules interactions, divided by the total number of interactions.
+We used a stochastic algorithm called “simulated annealing” [@Guimera2005], that assumes that the nodes of the same module have more links than one would expect in a random network.
+The modules are obtained from dividing all the nodes in the network to maximize modularity.
+In this way, the modularity index is defined as:
+
+\begin{equation}
+M = \sum_{s} (\frac{I_s}{L} - (\frac{d_s}{2L})^2)
+\end{equation}
+
+where $s$ is the number of modules or compartments, $I_s$ is the number of links between species in the modules, $d_s$ is the sum of degrees for all species in module $s$ and $L$ is the total number of links.
+
+Species topological roles were calculated using the method of functional cartography [@Guimera2005]. Roles are determined according to two parameters:
+
+a) the standardized within-module degree (dz), a z-score that reflects how well a species is connected to other species inside the module, relative to other species within its own module:
+
+\begin{equation}
+dz_i = \frac{k_{is}-k_s} {ks}
+\end{equation}
+
+where $k_{is}$ is the number of links of species $i$ within its own module $s$, and $ks$ are the average and standard deviation of $k_{is}$ over all species in $s$, respectively.
+
+b) the participation coefficient $PC$, estimates the links distribution of species $i$ among modules:
+
+\begin{equation}
+PC_i = 1 - \sum_{S} \frac{k_{is}}{k_i}
+\end{equation}
+
+where $k_i$ is the total number of links of species $i$ and $k_{is}$ is the number of links of species $i$ to species in module $s$.
+To determine the role of each species, the $dz$ − $PC$ parameters space was divided into four regions [@Kortsch2015], with two threshold values: $dz$ = 2.5 and $PC$ = 0.625.
+Thus, the species were classified as follows:
+
+* Module hub ($dz$ ≥ 2.5, $PC$ < 0.625): The species has a relatively high number of links, but at least 60% within its own module.
+
+* Module specialist ($dz$ < 2.5, $PC$ < 0.625): The species has relatively few links and most within its own module.
+
+* Module connector ($dz$ < 2.5, $PC$ ≥ 0.625): The species has relatively few links and most between modules.
+
+* Network connector ($dz$ ≥ 2.5, $PC$ ≥ 0.625): The species has a high connectivity between and within the modules.
 
@@
 
-```{r tableS1, echo=FALSE, message=FALSE, results='asis'}
+```{r tableS1, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 
@@
 
-# Table 1. List of interactions
-# landscape(knitr::kable(int_good_res %>% arrange(., (Predator), booktabs = TRUE, format = "latex", longtable = T, col.names = c("Prey","Predator","Reference", "Link"), caption = "List of predator-prey (trophic) interactions for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
+# Table S1. List of interactions
+# knitr::kable(int_good_res %>% arrange(., (Predator)), booktabs = TRUE, format = "latex", col.names = c("Prey","Predator","Reference", "Link"), caption = "List of predator-prey (trophic) interactions for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
 Alphabetically ordered by predator.") %>%
@@
 #    column_spec(4, width="14cm") %>%
-#              kable_styling(latex_options = c("hold_position","repeat_header"), font_size = 4))
+#    kableExtra::kable_styling(latex_options = c("hold_position","repeat_header"), font_size = 4) %>%
+#    kableExtra::landscape()
 
-pandoc.table(int_good_res %>% arrange(., (Predator)) %>% mutate(Prey = paste('\\tiny', Prey), Predator = paste('\\tiny', Predator), Reference = paste('\\tiny', Reference), Reference_link = paste('\\tiny', Reference_link)) %>% rename("Link"="Reference_link"), style="multiline", split.tables = Inf, justify = c("left","left","left","right"),
+pandoc.table(int_good_res %>% arrange(., (Predator)) %>% mutate(Reference_link = paste('\\tiny', Reference_link), Reference = paste('\\tiny', Reference), Prey = paste('\\tiny', Prey), Predator = paste('\\tiny', Predator)) %>% rename("Link"="Reference_link"), style="multiline", split.tables = Inf, justify = c("left","left","center","right"),
              caption = "List of predator-prey (trophic) interactions used to build the network for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).")
@@
 
-pandoc.table(sp_list %>% arrange(., (Species)) %>% mutate(Species = paste('\\tiny', Species), TaxLevel = paste('\\tiny', TaxLevel), FunctionalGroup = paste('\\tiny', FunctionalGroup), Reference = paste('\\tiny', Reference), Reference_pres_link = paste('\\tiny', Reference_pres_link), Observation = paste('\\tiny', Observation)) %>% rename("Taxonomy"="TaxLevel", "Group"="FunctionalGroup", "Link"="Reference_pres_link"), style="multiline", split.tables = Inf, justify = c("left","left","left","right","right","left"),
+pandoc.table(sp_list %>% arrange(., (Species)) %>% mutate(Species = paste('\\tiny', Species), TaxLevel = paste('\\tiny', TaxLevel), FunctionalGroup = paste('\\tiny', FunctionalGroup), Reference = paste('\\tiny', Reference), Reference_pres_link = paste('\\tiny', Reference_pres_link), Observation = paste('\\tiny', Observation)) %>% rename("Taxonomy"="TaxLevel", "Group"="FunctionalGroup", "Link"="Reference_pres_link"), style="multiline", split.tables = Inf, justify = c("left","left","left","left","left","left"),
              caption = "List of species for the food web of the Marine Protected Areas Namuncurá - Banco Burdwood I and II ecosystem. Alphabetically ordered by species.")
@@
 ```{r tableS3, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+require(kableExtra)
 
@@
                                      TRUE ~ FunctionalGroup))
-# tbl_31 <- kableExtra::kbl(tbl_3, format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Group","Degree","NumPrey","NumPred","Between","Close","TL","TS","TR"), align = "llcccccccc", caption = "Species-level properties for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
-Ordered by degree (total number of interactions).
-Between: betweenness; Close: closeness; TL: trophic level; TS: trophic similarity; TR: topological role (netcon = network connector, modcon = module connector, modhub = module hub, modspe = module specialist).")
-# tbl_32 <- kableExtra::kable_styling(tbl_31, latex_options = c("hold_position", "repeat_header"), font_size = 4.5)
 
@@
 ```
+
+\newpage
+
+## References

### 2024-01-11 MS_ToSubmit/RevisedVersion.Rmd
Revised MS

--- 2024-01-11 MS_ToSubmit/OriginallySubmittedVersion.Rmd
@@
 Most Marine Protected Areas (MPAs) target vulnerable, keystone, charismatic and or endemic species.
-In the sub-Antarctic, ocean protection is associated to oceanic islands,except for MPAs Namuncurá - Burdwood Bank I and II (MPA N-BB, ~53º–55ºS and ~56º–62ºW), which are associated to a submarine plateau and its southern adjacent deep slope, respectively.
+In the sub-Antarctic, ocean protection is associated to oceanic islands, except for MPAs Namuncurá - Burdwood Bank I and II (MPA N-BB, ~53º–55ºS and ~56º–62ºW), which are associated to a submarine plateau and its southern adjacent deep slope, respectively.
 Here, we present the first analysis of the network of predator-prey interactions for the MPA N-BB.
-We applied a network approach to characterise the complexity and structure of the food web, and identify the species' role in such a framework.
+We applied a topological network approach to characterise the complexity and structure of the food web, and identify the species' role in such a framework.
 The MPA N-BB food web consisted of 1788 interactions and 379 species, with a connectance of 0.01.
-Almost half of the consumers were omnivores (0.48), and the network displayed a small-world pattern.
-These suggest that the ecosystem might be vulnerable to perturbations targeting highly connected species, although other properties might provide resilience and resistance, resulting in a rearranged structure that preserves its original functions.
+Almost half of the consumers were omnivores or feeding at more than one trophic level (0.48), and the network displayed a small-world pattern (short path length, high clustering of compartments).
+This network pattern suggests that the ecosystem might be vulnerable to perturbations targeting highly connected species, although some properties might provide resilience and resistance, resulting in a rearranged structure that preserves its original functions.
 Several species arose as important in terms of different aspects of trophic structure and functioning, and response to perturbations.
@@
 
-The evidence of benefits provided by Marine Protected Areas (MPAs) as well as the urgent need for ocean protection have driven an unprecedented increase in the number of MPAs worldwide in recent years [@Roberts2017; @Sala2018].
+In recent years, there has been an unprecedented rise in the number of Marine Protected Areas (MPAs) worldwide, driven by both the compelling evidence of their benefits and the pressing need for ocean protection [@Roberts2017; @Sala2018].
 Globally, the total area of the world ocean designated under marine protection adds up to approximately 29,600,000 km^2^, distributed across nearly 18,444 MPAs and covering 8.16% of the ocean’s surface [@IUCN2023], and therefore approaching the 10% goal of the Convention of Biological Diversity [@Secretariatoftheconventiononbiologicaldiversity2004].
-Despite this progress, recent reports have shown that actual protection has been overestimated because it includes areas that are not yet effectively protected (only declared) as well as areas that allow significant extractive activities [@Sala2018].
+Although some progress has been made, it has become apparent that the level of protection has been inflated due to the inclusion of regions that have only been declared as protected, as well as areas where significant extractive operations are allowed [@Sala2018].
 
 In the sub-Antarctic region, the level of ocean protection is mainly associated to oceanic islands, such as the South Georgias and South Sandwich, Bouvet, Prince Edward, and Macquarie islands [@IUCN2023].
-Interestingly, the case of the MPAs Namuncurá - Burdwood Bank I and II (MPA N-BB, ~53º–55ºS ~56º–62ºW), which is the focus of this work, is unique since these MPAs are associated to a submarine plateau and its southern adjacent deep slope region, respectively [@Falabella2017; @Schejter2020].
+Interestingly, the case of the Argentine MPAs Namuncurá - Burdwood Bank I and II (MPA N-BB, ~53º–55ºS ~56º–62ºW), which is the focus of this work, is unique since these MPAs are associated to a submarine plateau and its southern adjacent deep slope region, respectively [@Falabella2017; @Schejter2020].
 In addition, such MPAs are part of a network of protected areas in the sub-Antarctic area (jointly with MPA Yaganes) that aims to protect this southern region in order to contribute to global ocean health.
@@
 Indeed, the MPA N-BB was created to protect a potentially sensitive and biodiverse benthic habitat that was only barely known [@Schejter2016; @Falabella2017].
-The benthic community is featured by high biomass of vulnerable and fragile species (mainly Porifera, Bryozoa and Cnidaria) that considered with their environment meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present densities of Indicator Taxa of > 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResourcesCCAMLR2009].
+The benthic community is featured by high biomass of vulnerable and fragile species (mainly Porifera, Bryozoa and Cnidaria) that, considered with their environment, meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present densities of Indicator Taxa of > 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResourcesCCAMLR2009].
 Also, the benthic realm provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge and nursery area [@GarciaAlonso2018; @Vazquez2018; @Delpiani2020; @Troccoli2020; @CovattiAle2022; @Fischer2022; @Matusevich2022; @Florencia2023].
-The maintenance of this singular community is related to local and regional oceanographic processes, including the circulation of the rich Malvinas (Falkland) current in the area [@Piola1989; @Guerrero1999] and the upwelling and mixing phenomena [@Matano2019].
-The input of nutrients from the Malvinas (Falkland) current also supports a diverse plankton community [@Guinder2020].
+The maintenance of this singular community is related to local and regional oceanographic processes, including the circulation of the rich Malvinas current in the area [@Piola1989; @Guerrero1999] and the upwelling and mixing phenomena [@Matano2019].
+The input of nutrients from the Malvinas current also supports a diverse plankton community [@Guinder2020].
+Given the cooling trend of this current in a warming regional context (i.e.
+adjacent waters of the Patagonian shelf and Southwest Atlantic Ocean) [@Franco2022], the MPA N-BB might play an essential role as a refuge maintaining not only the biodiversity but also the fisheries' populations of the region [@Franco2020].
 
-Overall, 811 benthic and plankton species have been identified for the MPA N-BB ecosystem, where 349 were reported for the first time in the area in recent years [@AdministraciondeParquesNacionales2022].
 Identifying the main species involved in the maintenance of ecosystem services and health as well as for management and conservation is essential.
-Recently, the structure of the southwestern South Atlantic Ocean has been proposed to be under a 'wasp-waist' control, meaning that the structure and dynamics of the ecosystem are regulated primarily by mid-trophic level species (e.g., fishes, crustaceans) [@Padovani2012; @Saporiti2015; @Riccialdelli2020].
-In particular, the ecosystem of the MPA N-BB shows a more pronounced 'wasp-waist' structure, meaning a shorter food chain and a greater trophic overlap and redundancy, than other sub-Antarctic areas, such as the continental shelf off Tierra del Fuego.
-The Fuegian sprat *Sprattus fuegensis* and longtail southern cod *Patagonotothen ramsayi* are considered the most plausible 'wasp-waist' species [@Riccialdelli2020].
+In this regard, @Bergagna2020 have identified the principal ecosystem services that are provided by species inhabiting the MPA N-BB; for instance, nursery and feeding areas for commercially important fishes (e.g.
+Patagonian grenadier *Macruronus magellanicus*, Patagonian toothfish *Dissostichus eleginoides*), water purification by filter feeders (e.g.
+sponges), among others.
+These species are part of a complex system in terms of biodiversity.
+There is robust knowledge on the complexity considering the richness of the benthic and plankton communities in the MPA N-BB ecosystem [@Schejter2016; @Guinder2020; @Schejter2020; @AdministraciondeParquesNacionales2022].
+Overall, 811 benthic and plankton species have been identified in the MPA N-BB ecosystem, where 349 were reported for the first time in the area in recent years [@AdministraciondeParquesNacionales2022].
+Recently, the structure of the southwestern South Atlantic Ocean has been hypothesised to be under a 'wasp-waist' control, meaning that the structure and dynamics of the ecosystem are regulated primarily by mid-trophic level species (e.g., fishes, crustaceans) [@Padovani2012; @Saporiti2015; @Riccialdelli2020].
+In particular, the ecosystem of the MPA N-BB shows a more pronounced 'wasp-waist' structure, meaning a shorter average food chain and a greater trophic overlap and redundancy, than other sub-Antarctic areas such as the continental shelf off Tierra del Fuego.
+It is the high abundance of few prey species at this mid-trophic level of the food web which imposes a certain feeding dependence to high-trophic level predators, shortens food-web length and increases the trophic overlap and redundancy of the overall food web.
+The Fuegian sprat *Sprattus fuegensis* and longtail southern cod Patagonotothen ramsayi are considered the most plausible 'wasp-waist' species, since they are species with high regional abundances [@Madirolas2000; @Arkhipkin2013], occupy mid-trophic levels [@Riccialdelli2010; @Riccialdelli2020], many predators feed on them [@Riccialdelli2020], and the population dynamics of these species appear to depend on the environment (e.g.
+climatic variations) [@Diez2018].
+These recent efforts have increased our understanding of the biological communities and their complexity, but an understanding of species interactions’ complexity and structure is lacking.
+Such understanding will provide a more complete picture of the ecosystem, generate a baseline to comprehend climate change effects for the region [@Franco2020] and serve as an input to decision makers on conservation actions [@AdministraciondeParquesNacionales2022].
 
-High-latitude marine ecosystems, such as the MPA N-BB, are complex systems in terms of biodiversity and ecological interactions [@Day2013; @Kortsch2019; @Cordone2020; @Trathan2021].
-Although there is a robust knowledge about the complexity considering the richness of the benthic and plankton communities in the MPA N-BB ecosystem [@Schejter2016; @Guinder2020; @Schejter2020; @AdministraciondeParquesNacionales2022], a better understanding of species interactions' complexity and structure is needed.
 This aspect can be tackled by analysing one of the most frequent relationships between species: the predator-prey interaction [@Bascompte2009].
-The sum of predator-prey or trophic interactions of a particular region is referred to as a food web, representing the roadmap for matter and energy flow in an ecosystem.
-In recent years, network approaches have been successfully applied to study complex high-latitude marine ecosystems, improving our knowledge on structure, functioning, and response to environmental/anthropogenic changes [@Kortsch2015; @Cordone2018; @Funes2022; @Marina2023].
+The sum of these interactions in a particular region is referred to as a food web, representing the roadmap for matter and energy flow in an ecosystem.
+In recent years, topological network approaches have been successfully applied to study complex high-latitude marine ecosystems, improving our knowledge on structure, functioning, and response to environmental/anthropogenic changes [@Kortsch2015; @Cordone2018; @Funes2022; @Marina2023].
 Among anthropogenic threats, it is worth mentioning that contaminants like mercury and microplastics have been recently reported as important threats to the MPA N-BB region [@Cossi2021; @DiMauro2022; @Fioramonti2022]; also fishing vessels are allowed to operate in the western section of the MPA N-BB (i.e.
 Marine National Reserve category), altering the stocks of commercially important fish species [@Martinez2021; @AdministraciondeParquesNacionales2022].
-Moreover, there is a potential hazard related to the effects of offshore activities (exploration and explotation) to the west of the MPA N-BB [@AdministraciondeParquesNacionales2022].
+Moreover, there is a potential hazard related to the effects of offshore activities (exploration and exploitation of gas and oil) to the west of the MPA N-BB [@AdministraciondeParquesNacionales2022].
 
-In the present work, we present the first detailed analysis of the network of predator-prey interactions, hereafter food web, for the MPA N-BB ecosystem.
-For this, we applied a network approach to a highly resolved food web.
+In this work, we present the first detailed analysis of the network of predator-prey interactions, hereafter food web, for the MPA N-BB ecosystem.
+For this, we applied a topological network approach to a highly resolved food web.
 The objective was twofold: characterise the food web in terms of complexity and structure, and identify the species' role in the network.
+For the former, we considered all species and interactions in the food web, and calculated the number of species (S), number of interactions (L), link density (L/S), connectance (L/S^2), proportion of omnivorous, and assessed the small-world pattern.
+For the latter objective, we considered interactions and species related to a particular species and analyse the following properties: betweenness, closeness, trophic similarity, topological role and trophic level.
 
@@
 
-The MPAs Namuncurá - Burdwood Bank I and II, created by National Laws 26.875 in 2013 and 27.490 in 2017, comprise a shallow submarine plateau called Burdwood Bank (BB) and a deep slope that reaches 4000 m in depth, N-BB I and N-BB II, respectively [@Tombesi2020; @AdministraciondeParquesNacionales2022] (Figure 1).
+The MPAs Namuncurá - Burdwood Bank I and II, created by Argentine National Laws 26.875 in 2013 and 27.490 in 2017, comprise a shallow submarine plateau called Burdwood Bank (BB) and a deep slope to the south that reaches 4000 m in depth, N-BB I and N-BB II, respectively [@Tombesi2020; @AdministraciondeParquesNacionales2022] (Figure 1).
 They are located 150 km east of Isla de los Estados and 200 km south of Malvinas/Falkland Islands.
-The MPA N-BB I comprises nearly 28,900 km^2^ circumscribed by the 200 m isobath, between ~54º–55ºS and ~56º–62ºW, with a slight slope extended nearly 370 km east–west.
-Physical features in the BB are fairly stable, with salinity averaging 34 all year round and temperature ranging between 4 and 8ºC [@Guerrero1999; @Acha2004; @Piola2009].
-The BB is surrounded by steep flanks of up to 4000 m depth through which strong currents circulate [@Piola1989; @Reta2014; @Matano2019].
+The MPA N-BB I comprises nearly 28,900 km^2^ circumscribed by the 200 m isobath, between ~54º–55ºS and ~56º–62ºW, with a slight slope extending nearly 370 km east–west.
+The physical characteristics of the BB's deep waters are relatively stable, with a consistent salinity of 34 psu throughout the year and a temperature range of 4 to 8ºC [@Guerrero1999; @Acha2004; @Piola2009].
+The BB is enclosed by high, steep slopes that plunge to depths of up to 4000 m, where powerful currents flow [@Piola1989; @Reta2014; @Matano2019].
 The N-BB II includes such a deep slope, protecting about 32,000 km^2^ (~55º-56ºS, ~58º-62ºW).
-Intense upwelling and mixing occur in relation with the slope, entraining deep nutrient-rich waters into the photic layer [@Piola2009; @Matano2019] and resulting in a fairly homogeneous water column both spatially and temporally [@Glorioso1995; @Guerrero1999; @Matano2019].
+Intense upwelling and mixing take place in connection with the slope, bringing deep, nutrient-rich waters into the photic layer [@Piola2009; @Matano2019] and resulting in a relatively uniform water column both horizontally and vertically, both in space and time [@Glorioso1995; @Guerrero1999; @Matano2019].
 
@@
 
-In order to build the network of predator-prey interactions, we reviewed more than 170 references considering published articles, Ph.D.
+In order to build the network of predator-prey interactions, we started by searching trophic information for the species reported by @Schejter2016 and @Falabella2017.
+Subsequently, we performed a literature search using the name of the species in question and the keywords 'diet', 'prey', 'predator', 'feeding ecology' and 'trophic ecology' in Google Scholar and Scopus.
+This process identified more than 170 references including peer-reviewed published articles, Ph.D.
 theses, public databases, and reports belonging to 16 research cruises conducted in the MPAs N-BB I and II during 2014-2019.
-It is noteworthy that the sampling effort was greater in the MPA N-BB I.
-Furthermore, we took into account personal communications from experts belonging to the working group of the study area (https://www.pampazul.gob.ar/tag/banco-burdwood/).
+We considered that one reference showing evidence of a predator-prey relationship was enough to add that interaction to the network.
+Finally, we consulted with experts belonging to the working group of the study area (https://www.pampazul.gob.ar/tag/banco-burdwood/) that filtered the list of trophic interactions and discarded those unlikely to occur in the MPAs N-BB I and II.
 The diversity of the authors' expertise contributing to the present study was a key factor in enhancing the quality of the network, and inherently improved the network representation.
@@
 
-With the gathered trophic data, we constructed a matrix of pairwise interactions; a value of 1 or 0 was assigned to each element a_ij of the matrix depending on whether the j-species preyed or not on the i-species.
-Then we transformed such a matrix into an oriented graph with L trophic interactions between S nodes or species.
-The orientation or direction of the graph follows the flow of energy and matter in the network, from prey to predator.
+With the gathered trophic data, we constructed a matrix of pairwise interactions; a value of 1 or 0 was assigned to each element a_ij of the matrix depending on whether the predator j preyed or not on the prey i.
+Then we transformed such a matrix into an directed graph with L trophic interactions between S nodes or species (Supplementary Material, Figure S1).
+The direction of the interaction within the graph follows the flow of energy and matter in the network, from prey to predator.
 
@@
 The network-level analysis aims to characterise the food web in terms of complexity and structure.
-For this, we calculated several network properties commonly used to describe empirical food webs [@Pascual2005]: (1) number of species S; (2) number of interactions or links L; (3) link density L/S; (4) connectance L/S^2; (5) omnivory Omn; and (6) small-world pattern.
-In order to explore the small-world phenomenon, we analysed the  characteristic path length (CPL) and the clustering coefficient (CC).
-The CPL is the average shortest path length between all pairs of nodes [@Watts1998].
-Here, CPL was calculated as the average number of nodes in the shortest path $CPL_{Min} (i,j)$ between all pairs of nodes $S(i,j)$ in a network averaged over $S(S-1)/2$ nodes:
+For this, we calculated several network properties commonly used to describe empirical food webs [@Pascual2005]: (1) number of species $S$; (2) number of interactions or links $L$; (3) link density $L/S$; (4) connectance $L/S^2$; (5) omnivory $Omn$; and (6) small-world pattern.
+In order to explore the small-world phenomenon, we analysed the  characteristic path length ($CPL$) and the clustering coefficient ($CC$).
+The $CPL$ is the average shortest path length between all pairs of nodes [@Watts1998].
+Here, $CPL$ was calculated as the average number of nodes in the shortest path $CPL_{Min} (i,j)$ between all pairs of nodes $S(i,j)$ in a network averaged over $S(S-1)/2$ nodes:
 
-$$
-CPL = \frac{2}{S(S-1)} \sum_{i = 1}^{S} \sum_{i = 1}^{S} {CPL_{Min}(i,j)}
-$$
-The CC quantifies the local interconnectedness of the network and it is defined as the fraction of the number of existing links between neighbours of node $i$ among all possible links between these neighbours.
-In this study, the CC was determined as the average of the individual clustering coefficients $CC_i$ of all the nodes in the network.
+\begin{align}
+CPL = \frac{2}{S(S-1)} \sum_{i = 1}^{S} \sum_{ij = 1}^{S} {CPL_{Min}(i,j)}
+\end{align}
+
+The $CC$ quantifies the local interconnectedness of the network and it is defined as the fraction of the number of existing links between neighbours of node $i$ among all possible links between these neighbours.
+In this study, the $CC$ was determined as the average of the individual clustering coefficients $CC_i$ of all the nodes in the network.
 Individual $CC_i$ were determined as follows:
 
-$$
+\begin{align}
 CC_i = \frac{2E_i}{K_i(K_i-1)}
-$$
+\end{align}
+
 where $E_i$ is the effective number of interactions between $K_i$ nearest-neighbour nodes of node $i$ and the maximal possible number of such interactions [@Newman2003].
-To test whether the food web presented the small-world pattern, we compared the empirical values of CPL and CC with those resulting from 1000 randomly generated networks with the same size (S) and number of interactions (L), following the method proposed by @Marina2018a.
+To test whether the food web presented the small-world pattern, we compared the empirical values of $CPL$ and $CC$ with those resulting from 1000 randomly generated networks with the same size ($S$) and number of interactions ($L$).
+Random webs were created using the Erdös-Rényi model, where links are added to the complete set of nodes ($S$) and chosen uniformly randomly from the set of all possible links [@Erdos1959].
+The rigurosity of our method lies in the use of confidence intervals (CI 99%) for the empirical-random comparison of the $CPL$ and $CC$ properties.
+If the empirical value is positioned within or to the left (= lower than) the CI 99% of the random CPL, and to the right (= higher than) the CI 99% of the CC, then the food web is considered to present the SW topology [@Marina2018a].
 
@@
 The species-level analysis aims to describe the species' role in the food web.
-For this, we considered the following properties: betweenness Btw, closeness Cl, trophic similarity TS, topological role TR, and trophic level TL (Table 1).
+For this, we considered the following properties: betweenness $Btw$, closeness $Cl$, trophic similarity $TS$, topological role $TR$, and trophic level $TL$ (Table 1).
 Topological roles refer to the fact that food webs tend to naturally organize in non-random, modular patterns, where modules are defined as a group of species that interact more frequently among themselves than with species that are not members of the module [@Guimera2005].
+This means that groups of prey and predators interact more strongly with each other, than with species belonging to other groups.
+Modularity measures how strongly these subgroups of species, called modules, interact with each other compared to species from other modules.
 Species can play different roles in this respect, according to the pattern of interactions within their own module and/or across modules.
 We computed the topological role for each species, classified as module hub, species with a relatively high number of interactions, but most within its own module; module specialist, species with relatively few interactions and most within its own module; module connector, species with relatively few interactions mainly between modules; and network connector, species with high connectivity between and within modules [@Guimera2005].
+Refer to the Supplementary Material for the equations used to calculate the species-level properties.
 
-We also studied the relationship between species TL and the other species properties by performing linear regression analyses.
-Thus, we considered the TL as the dependent variable and the given property (i.e.
-betweenness, closeness, trophic similarity) as the independent variable and obtained the coefficients (slope and intercept) for the linear model.
-Models were fitted using the least squares approach.
-We also explored the topological role categories with the species TL.
+We also studied the relationship between species $TL$ and the other species properties by fitting analyses.
+Thus, we considered the $TL$ as the dependent variable and the given property (i.e.
+betweenness, closeness, trophic similarity) as the independent variable.
+Fitting was done locally, meaning that for the fit at point *x*, the fit is made using points in a neighborhood of *x*, weighted by their distance from *x* [@Cleveland1992].
+We also explored the topological role categories with the species $TL$.
 These species-level properties provide an appropriate description of species' role in empirical complex food webs [@Cirtwill2018].
 
-All network analyses and graphs were performed in R version 4.2.2 [@RCoreTeam2022], mainly using 'igraph' [@Csardi2006] and ‘multiweb’ [@Saravia2022a] packages.
+All network analyses and graphs were performed in R version 4.3.1 [@RCoreTeam2023], mainly using 'igraph' [@Csardi2006] and ‘multiweb’ [@Saravia2022a] packages.
+Fitting between species $TL$ and the other species properties was performed using *loess* function from 'stats' package [@RCoreTeam2023].
 The source code and data are available at https://github.com/TomasMarina/Banco-Burdwood.
@@
 
-In terms of complexity, the MPA Namuncurá - Burdwood Bank food web consisted of 1788 predator-prey interactions and 379 species, where 93% of them were defined at the species taxonomical level (Figure 2, Table S2).
+In terms of complexity, the MPA N-BB food web consisted of 1788 predator-prey interactions and 379 species, where 93% of them were defined at the species taxonomical level (Figure 2, Table S2).
 The food web presented a link density (e.g., the average number of interactions per species) of 4.72, and a connectance of 0.01.
@@
 The top-five prey (or food sources) in number of predators were: Detritus (Non-living, 153 predators), the three categories of Diatoms considered (benthic, centric and pennate, 72.5 predators on average), and species of the genus *Euphausia* (Zooplankton, 46 predators).
-Finally, taking into account the interactions within each functional group, most interactions were concentrated in a few species (Figure 3D).
+Finally, aggregating the interactions by functional group (Figure 3D), most interactions were concentrated in a few species.
 The most evident species were: *Doryteuthis gahi* (Cephalopoda), *Grimothea (=Munida) gregaria* (Decapoda), *Patagonotothen ramsayi*, *Patagonotothen guntheri* and *Dissostichus eleginoides* (bentho-pelagic fish), *Sprattus fuegensis* and *Micromesistius australis* (pelagic fish), and species of *Euphausia* and *Themisto gaudichaudii* (Zooplankton).
-Overall, there is an evident asymmetry in the distribution of interactions among species at different levels in the MPA N-BB food web.
-
+Overall, there is an evident asymmetry in the distribution of interactions among species at different levels (i.e.
+considering the entire food web, gathered by prey, predator and functional group) in the MPA N-BB food web.
 A list of the distribution of interactions per species is presented in Supplementary Material (Table S3).
@@
 We found different relationships between the species trophic level (TL) and the rest of the analysed species-level properties (Figure 4A-D).
-The most evident significant relationship was with trophic similarity, i.e.
-the higher the species' TL, the lower the trophic similarity or the higher the uniqueness in terms of trophic role (Figure 4C).
+The most evident relationship was with trophic similarity, which described an exponential-like decline; i.e.
+the higher the species' TL, the lower the trophic similarity or the higher the uniqueness in terms of trophic role (Figure 4A).
 Here it is noteworthy to highlight those high-trophic level species (TL > 3.1) with low values of trophic similarity: *Bathyraja macloviana* and *Squalus acanthias* (Chondrichthyans), *Diplopteraster clarki* and *Pteraster* sp.
@@
 
-We also found a significant negative relationship between TL and closeness, however less evident, meaning that low-TL species are relatively closer to any other species in the food web (Figure 4B).
+We also found a general negative relationship between TL and closeness, meaning that species with relatively low-TLs are closer to any other species in the food web (Figure 4B).
+Specifically, species in the range 2 - 3 showed a hump-shaped distribution, while for TL > 3 closeness decreased consistently.
 Detritus, species of genera *Calanus* and *Euphausia*, and Foraminifera, all with TL < 3, registered the highest closeness values (Table S3).
 
-Notably, species of mid-TLs (3-4.2) showed the highest values of betweenness, meaning that those species participated in the highest number of shortest paths between species (Figure 4A).
+Regarding betweenness, as expected species of mid-TLs (3-4.2) showed the highest values, meaning that those species participated in the highest number of shortest paths between species (Figure 4C).
 The following are the species with the highest values (descending order): *Patagonotothen ramsayi*, *Salilota australis*, *Dissostichus eleginoides* (fishes), *Doryteuthis gahi* (Cephalopoda), and *Patagonotothen guntheri* (Notothenioid fish) (Table S3).
+Here we should note that species with highest TLs (> 4.2, top predators) show values equal to zero since no "betweenness" role is possible for them.
 
@@
 The 41 species with a module connector role represented these functional groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Hydrozoa (as 'Cnidaria_benthic'), Copepoda, Cumacea, Decapoda, Echinodermata, fish (bentho-pelagic and demersal Osteichthyes, and Chondrychthyes), Foraminifera, Polychaeta, Porifera, Pycnogonida (as 'Benthos_Misc') and zooplankton (see Supplementary Material Table S3 for the identity of the species).
-
 An exhaustive list of the species-level properties is presented in Supplementary Material (Table S3).
@@
 The food web of the MPA N-BB ecosystem analysed in this study is one of the most highly-resolved networks of trophic interactions ever studied, not only for a high-latitude open-ocean ecosystem but also for any marine protected area worldwide to our knowledge.
-It is of paramount importance to consider the complexity of species interactions in order to gain insights into the structure and functioning of the ecosystem, since the aggregation of species might mask food web properties and produce type II errors (false positives) [@Martinez1993; @Gauzens2013].
+It is of paramount importance to consider the complexity of species interactions in order to gain insights into the structure and functioning of the ecosystem, since some aggregation criteria (i.e.
+body size) might mask food web properties and produce type II errors (false negatives, e.g.
+when an effect is not significant before aggregation but significant after considering a particular food web property) [@Martinez1993; @Gauzens2013].
 
@@
 In particular, food webs from high-latitude regions tend to exhibit a connectance closer to the minimum (between 0.01 and 0.05) [@Santana2013; @Kortsch2015; @Rodriguez2022].
+The connectance of the food web of the MPA N-BB (0.01) is one of the lowest reported so far for these regions; in particular, it appears to be much lower than that of Beagle Channel (0.05), an adjacent coastal area [@Rodriguez2022].
 Whether food webs display a low or a high connectance helps to better comprehend ecosystem's synthetic properties like robustness.
-In this sense, empirical analyses support the notion that highly-connected ecological networks are robust against external perturbations such as the introduction of new (e.g., invasive) species [@Smith-Ramesh2017] as well as species removal (e.g., local extinction) [@Dunne2002; @Montoya2003].
-The connectance of the food web of the MPA Namuncurá - Burdwood Bank (0.01) is one of the lowest reported so far for these regions; in particular, it appears to be much lower than that of Beagle Channel (0.05), an adjacent coastal area [@Rodriguez2022].
+Empirical research indicates that ecological networks with high connectance are resilient to external perturbations, including the introduction of new species like invasive ones [@Smith-Ramesh2017], as well as the removal of species due to local extinction [@Dunne2002; @Montoya2003].
 
-The degree distribution, the distribution of the number of interactions per species, is the core of the structure of species interactions, which influences the opportunities for multiple species to persist in the long term and, therefore, their coexistence [@Godoy2018].
+The degree distribution, the frequency distribution of the number of interactions per species, is the core of the structure of species interactions, which influences the opportunities for multiple species to persist in the long term and, therefore, their coexistence [@Godoy2018].
 The food web for the MPA N-BB presents an asymmetric degree distribution.
@@
 Omnivory acts as a buffer to changes as the ecosystem presents alternative energy pathways in the face of perturbations, i.e., reducing the risk of cascading extinctions following the primary loss of species [@Borrvall2000].
-Omnivores are species able to adapt faster and to a broader range of environmental conditions by changing their foraging habits to feed on the most abundant prey [@Fagan1997].
+This is supported by the fact that omnivorous adapt at a faster rate and to a wide range of environmental conditions due to its flexibility to feed on the most abundant prey [@Fagan1997].
 Furthermore, omnivory can be analysed from the interaction point of view: theoretical studies have identified omnivorous interactions as a possible candidate for a keystone interaction, sensu @Kadoya2018, highlighting the importance of omnivory in stabilizing food web dynamics [@McCann1997; @Neutel2002].
@@
 In summary, the food web of the MPA N-BB presents a combination of network properties that makes it unique in terms of network resolution, complexity, and structural pattern.
-All this suggests that the food web might be fragile to external perturbations targeting highly connected species, which in turn coincides to be commercial exploited species as fishes [@Laptikhovsky2013; @Martinez2015; @Winter2023].
+All this suggests that the food web might be fragile to external perturbations targeting highly connected species, which in this case are commercially exploited fishes [@Laptikhovsky2013; @Martinez2015; @Winter2023].
 However, structural properties might provide resilience and resistance with the final outcome of a rearranged structure maintaining its functions.
@@
 This result is in agreement with the sole analysis, using stable isotopes, that exists so far for the trophic structure of the MPA N-BB [@Riccialdelli2020], and resembles other high-latitude marine systems of the Southwest Atlantic and Antarctic regions [@Arkhipkin2013; @Marina2018].
-The importance of these particular generalist species also arises since they feed in the benthic and pelagic habitats [@Troccoli2020; @CovattiAle2022; @Fischer2022], linking these realms and contributing to the vertical carbon flow.
+The importance of these particular generalist species also arises since they feed in the benthic and pelagic habitats [@Troccoli2020; @CovattiAle2022; @Fischer2022], enhancing the bentho-pelagic coupling and contributing to the vertical carbon flow.
 
@@
 Describing species’ roles in food webs provides a toolbox to assess the significance of species in terms of community's functioning and overall stability [@Thebault2010; @Cirtwill2018].
-We used a range of descriptors to characterise the dynamic and multifaceted nature of the species forming the MPA N-BB food web.
 
@@
 Closeness quantifies how many steps away species $i$ is from all other species in the food web, and is proportional to how rapidly the indirect effects of the focal species can spread to other species in the network [@Scotti2010].
-In the food web of the MPA N-BB, low-TL consumers arise as important in this regard: species of the zooplankton community, *Calanus* and *Euphausia*, *Zygochlamys patagonica* (Bivalvia), and Brachiopoda.
-Any perturbation affecting these species, such as the recently confirmed contaminants mercury [@Fioramonti2022] and microplastics [@Cossi2021; @DiMauro2022], should be of concern since it might reach many other species in the food web.
+Considering the relationship between this property and TL in the food web of the MPA N-BB, it is worth to highlight that species with the highest closeness values are low-TL consumers (TL = 2 - 3): species of the zooplankton community, *Calanus* and *Euphausia*, *Zygochlamys patagonica* (Bivalvia), and Brachiopoda.
+Any perturbation affecting these species, such as the recently confirmed contaminants mercury [@Fioramonti2022] and microplastics [@Cossi2021; @DiMauro2022], and the warming trend reported for the surface and subsurface waters in the Southwest Atlantic Ocean [@Franco2020a; @Galvan2022a], should be of concern since it might reach many other species in the food web.
 Otherwise, betweenness measures the number of shortest paths between species, providing information on the importance of species as “bridges” for energy transfer: a species with high betweenness takes part in more food chains and therefore affects more energy flows [@Scotti2010].
@@
 Ecosystems with a pronounced 'wasp-waist' structure are suggested to present a high trophic redundancy, since many species would show similar trophic habits [@Cury2000].
-The significant negative relationship between trophic similarity and trophic level enhances the hypothesis of functional similarity at low and mid-TL species compared to higher TL species for the MPA N-BB food web [@Riccialdelli2020].
-At the same time, our results highlight the uniqueness in terms of the trophic role of high-TL predators.
-Here, not only the expected pelagic animals such as marine mammals and seabirds arise as relevant, but also demersal vertebrate (chondrichthyans *Bathyraja macloviana* and *Squalus acanthias*) and benthic invertebrate species (echinoderms *Diplopteraster clarki* and *Pteraster* sp.) are noteworthy.
+Such trophic redundancy is expected to be greater for species in TLs above the waist (mid-TL) that depend on a very few species at the waist.
+However, our results show an exponential-like negative relationship between trophic similarity (or redundancy) and trophic level, indicating functional similarity at low and mid-TL species compared to higher TL species for the MPA N-BB food web.
+This contradiction might be reflecting the potential discrepancy that could arise between qualitative (this study) and quantitative food web studies.
+Here it is important to note that our analyses considered all potential predator-prey interactions in the food web giving equal importance to them.
+Although this could be a disadvantage when inferring on energy flows, one of the main advantages of qualitative food web studies is that it considers the diversity of the communities inhabiting a particular study area, therefore providing a more representative picture of all components (species) acting on the ecosystem.
+In this sense, our study highlights the uniqueness in terms of the trophic role of high-TL predators.
+Not only the expected pelagic animals such as marine mammals and seabirds arise as relevant, but also demersal vertebrate (chondrichthyans *Bathyraja macloviana* and *Squalus acanthias*) and benthic invertebrate species (echinoderms *Diplopteraster clarki* and *Pteraster* sp.) are noteworthy.
 The role that such species play in the MPA N-BB ecosystem is unique and perturbations on them might result in unprecedented changes at the trophic structure and functioning level.
@@
 
-It's important to mark that we did not consider quantitative data (i.e.
-abundance, biomass) to assess the species' role in the food web.
-Although there exists such data for some species [@Schejter2021], it would not be possible to include it in the food web framework described here due to a taxonomical resolution mismatch.
-In this regard, we should mention the case of *Zygochlamys patagonica* (Bivalvia) and Brachiopoda that are highlighted by our species-level analyses though they have been found in low abundances in the area [@Schejter2021].
-
-Some species of sessile suspension feeders in high-latitude marine ecosystems, such as sponges, ascidians and octocorals, avoid predation by producing secondary metabolites that function as a chemical defense [@Nunez-Pons2010; @Moles2015; @Prieto2022].
-Although this was not yet recorded at the MPA N-BB, there are a few studies that reported it in other locations in species that inhabit the MPA N-BB [@RojodeAlmeida2010].
-
 The MPA N-BB I presents complex oceanographic conditions that generate an internal spatial heterogeneity, mainly along its longitudinal axis [@Matano2019].
@@
 
+It's important to mark that we did not consider quantitative data (i.e.
+abundance, biomass) to assess the species' role in the food web.
+Although there exists such data for some species [@Schejter2021], it would not be possible to include it in the food web framework described here due to a taxonomical resolution mismatch.
+In this regard, we should mention the case of *Zygochlamys patagonica* (Bivalvia) and Brachiopoda that are highlighted by our species-level analyses though they have been found in low abundances in the area [@Schejter2021].
+
 Taking into account the mentioned caveats, and with the aim of improving the knowledge regarding the structure, functioning and stability of the MPA N-BB, we suggest that the future perspectives should: 1) incorporate spatial heterogeneity among MPA N-BB I and II [@Schejter2021], which might lead to distinct food web properties in terms of structure and functioning [@Kortsch2019; @Cordone2020]; 2) include species traits, like body size and mass, since they are known to be important drivers in predator-prey interactions [@Brose2019]; 3) simulate the anthropogenic impacts already present in the MPA N-BB ecosystem (e.g.
 microplastics, mercury) [@Cossi2021; @DiMauro2022; @Fioramonti2022] as perturbations within the framework of the described complex food web; and 4) estimate the interaction strength of each predator-prey relationship in the food web considering species and interaction traits (i.e.
-body size, body mass, interaction dimensionality), and species density data [@Nilsson2016; @Pawar2012].
+diet preference, body size, body mass, interaction dimensionality or if the predator-prey relationship occurs in a 2 or 3 dimension space), and species density data [@Nilsson2016; @Pawar2012].
 
@@
 
-We compiled information on the species and trophic diversity of the oceanic Marine Protected Area Namuncurá - Burdwood Bank, generating an unprecedented, well-resolved network of trophic interactions for a sub-Antarctic ecosystem, identifying the complexity and structure of the system, and the main species role in a network framework.
+We compiled information on the species and trophic diversity of the oceanic Marine Protected Area Namuncurá - Burdwood Bank, generating an unprecedented, well-resolved network of trophic interactions for a sub-Antarctic ecosystem, identifying the complexity and structure of the system, and the main species' role in a network framework.
 Particular properties at the network level allowed us to identify the ecosystem's vulnerability and potential response to perturbations in the presence of highly-connected species, with a rearranged structure maintaining their functions due to its potential resilience and resistance.
@@
 Finally, we argue that it is the diversity of species, representing the benthic and pelagic habitats, that maintains the connectivity of the food web against perturbations, therefore contributing to the structure and stability of the ecosystem.
+
+Our work provides valuable information for supporting the management of the MPA N-BB in the sense that it disentangles the multiple ecosystem players and their roles.
+Moreover, by building the network of predator-prey interactions we have set the baseline to model the environmental and anthropogenic perturbations affecting the MPA ecosystem.
+This knowledge becomes of importance at the regional scale given that the MPA ecosystem is a known spawning ground for many species of commercial interest [@AdministraciondeParquesNacionales2022] and a potential area of high carbon storage and sequestration due to the characteristics of the benthic community [@Bax2022; @Bergagnainrev].
 
@@
 
+table1 <- add_row(table1, Name="Trophic level", Definition="Trophic Level (TL) is an indicator of the position a species occupies in a food web resuming the distance of each species to the source of matter and energy", Implications="Low values of mean TL indicate efficient energy transfer from basal assemblage to top predators.
+It contributes to food web stability.", Reference = "Lindeman 1942, Borrelli & Ginzburg 2014")
+
 table1 <- add_row(table1, Name="Omnivory", Definition="Species feeding on prey from more than one trophic level.", Implications="It influences food web's stability; intermediate levels of omnivory may stabilize it and may diffuse top-down effects thus reduce the probability of trophic cascades.", Reference = "McCann & Hastings 1997")
@@
 
-pandoc.table(round(prop_topol,2) %>% dplyr::select(Size, Links, LD, Connectance, Omnivory, PathLength, Clustering) %>% mutate(SW = "True"), col.names = c("Species","Interactions","Density","Connectance","Omnivory","CPL", "CC", "SW"), split.cells = c(1,1,1,1,1,1,1,1),
+pandoc.table(round(prop_topol,2) %>% dplyr::select(Size, Links, LD, Connectance, Omnivory, PathLength, Clustering) %>% mutate(SW = "True"), col.names = c("Species","Number of interactions","Link density","Connectance","Omn","CPL", "CC", "SW"), split.cells = c(1,1,1,1,1,1,1,1),
                       caption = "Network-level properties of the MPA Namuncurá - Burdwood Bank food web.
-CPL: Characteristic Path Length; CC: Clustering Coefficient; SW: Small-World pattern.
-See table 1 for definitions and ecological relevance.")
+Omn: Fraction of omnivorous groups; CPL: Characteristic Path Length; CC: Clustering Coefficient; SW: Small-World pattern.")
 
@@
 
-```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 5, fig.height = 10, out.width = '100%', fig.cap="Marine Protected Areas Namuncurá - Burdwood Bank I (MNR and MNP, northern section) and II (MNR and SMNR, southern section).
+```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 5, fig.height = 10, out.width = '100%', fig.cap="Marine Protected Areas Namuncurá - Burdwood Bank I (MNR and MNP, northern section) and II (MNR and RMNR, southern section).
 Acronyms indicate categories according to the management plan: MNR - Marine National Reserve, MNP - Marine National Park and RMNR - Restricted Marine National Reserve."}
@@
 
-```{r figure2, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 5.5, fig.height = 10, fig.align='center', fig.cap="Graph of the food web for the MPA Namuncurá - Burdwood Bank.
-Circles represent species and arrows trophic interactions.
-Circle diameter is relative to the number of interactions.
+```{r figure2, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 5.5, fig.height = 5, fig.align='center', fig.cap="Graph of the food web for the MPA Namuncurá - Burdwood Bank.
+Circles represent trophic species and arrows trophic interactions.
+Circle diameter is relative to the number of interactions (see legend).
 Colour gradient indicates the trophic level."}
@@
 
-# Packages
-require(multiweb)
-
-# Data
-load("../results/summary_results_jul23.rda")
-
-par(cex.axis=0.8, cex.lab=0.8)
-figure_2 <- plot_troph_level(g, vertexLabel = F, modules = F, ylab = "Trophic level")
+knitr::include_graphics("figure2_ok.pdf")
 
@@
 
+# Data
 load("../data/foodweb-data_jul23.rda")
@@
 
-```{r figure4, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 6.5, fig.height = 6.5, fig.align='center', fig.cap="Species-level properties by trophic level: (A) trophic similarity, (B) closeness, (C) betweenness, and (D) topological role.
+\newpage
+
+```{r figure4, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 6.5, fig.height = 6.5, fig.align='center', fig.cap="Species-level properties by trophic level: (A) betweenness, (B) closeness, (C) trophic similarity, and (D) topological role.
 Each point represents a species.
-Linear regressions for betweenness ($y = 74.97x - 117.35, R^2 = 0.05, p-value < 0.01$), closeness ($y = 9.33e-06x - 9.31e-4, R^2 = 0.003, p-value = 0.15$) and trophic similarity ($y = -0.02x + 0.11 , R^2 = 0.07, p-value < 0.01$).
-Note that for panels A, B and C only species with TLs equal or greater than 2 were considered."}
-# Betweenness, Closeness, Trophic similarity & Topological role by Trophic level
-require(tidyverse)
-require(igraph)
-require(grid)
-require(ggpubr)
+Note that for panels A, B and C only species with TLs equal or greater than 2 were considered.
+In the boxplot (D), the horizontal line in the middle of each box represents the median of the data, the colored box represents the interquartile range (range between the 1st, or 25th percentile, and 3rd, or 75th percentile, quartile), containing the middle 50% of data points."}
+# Trophic similarity, Closeness, Betweenness & Topological role by Trophic level
 
+# Data
 load("../results/summary_results_jul23.rda")
 
-# Betweenness
+### Betweenness ----
+scientific_10 <- function(x) {
+  parse(text=gsub("e", " %*% 10^", scales::scientific_format()(x)))
+}
 plot_sp_bt <- spp_total %>% 
@@
   geom_point(size=0.3) +
+  scale_y_log10(label = scientific_10) +
+  #scale_y_continuous(label = scientific_10)
   xlim(2, 5) +
-  geom_smooth(method = "lm") +
+  geom_smooth(method = "loess") +
   labs(x = "Trophic level", y = "Betweenness") +
@@
 
-# Closeness
+### Closeness ----
 plot_sp_cl <- spp_total %>% 
@@
   xlim(2, 5) +
-  geom_smooth(method = "lm") +
+  geom_smooth(method = "loess") +
   labs(x = "Trophic level", y = "Closeness") +
@@
 
-# Trophic similarity
+### Trophic similarity ----
 plot_sp_ts <- spp_total %>% 
@@
   xlim(2, 5) +
-  geom_smooth(method = "lm") +
+  geom_smooth(method = "loess") +
   labs(x = "Trophic level", y = "Trophic similarity") +
@@
 
-# Topological role
+### Topological role ----
 top.role.col <- hcl.colors(4, palette = "Purple-Green")
@@
 # Arrange figure
-figure_ab <- ggarrange(plot_sp_bt + rremove("xlab"), plot_sp_cl + rremove("xlab"),
+figure_ab <- ggarrange(plot_sp_ts + rremove("xlab"), plot_sp_cl + rremove("xlab"),
                        labels = c("A","B"), ncol=2,
@@
 figure_4 <- ggarrange(figure_ab,                                                                                         # First row
-          ggarrange(plot_sp_ts, plot_sp_tr, ncol = 2, labels = c("C", "D"), font.label=list(color="black",size=10)),                                            
+                      ggarrange(plot_sp_bt, plot_sp_tr, ncol = 2, labels = c("C", "D"), font.label=list(color="black",size=10)),                                            
                       nrow = 2)

### 2024-01-11 R/5_TLrelation.R
Loess fit

@@ -1,0 +1,102 @@
+## FOOD WEB ANALYSIS: RED TRÓFICA AMP NAMUNCURÁ-BANCO BURDWOOD
+# Autor: Tomás Ignacio Marina
+# Fecha: 24/01/2023, 8/01/2024 (update)
+
+
+# Paquetes ----
+
+packages <- c("dplyr", "ggplot2", "olsrr")
+ipak <- function(pkg){
+  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
+  if (length(new.pkg))
+    install.packages(new.pkg, dependencies = TRUE)
+  sapply(pkg, require, character.only = TRUE)
+}
+ipak(packages)
+
+
+# Datos ----
+load("results/summary_results_jul23.rda")
+
+
+# Data fit ----
+
+## Betweenness ----
+# Check linear regression assumptions
+lm.btw <- lm(Between ~ TL, data=spp_total)
+ols_test_normality(lm.btw)
+btw.res.hist <- ols_plot_resid_hist(lm.btw)
+btw.res.fit <- ols_plot_resid_fit(lm.btw)
+btw.res.qq <- ols_plot_resid_qq(lm.btw)
+figure_btw <- ggarrange(btw.res.hist, btw.res.fit, btw.res.qq,
+                       ncol=2, nrow=2,
+                       font.label = list(size = 10, color = "black"))
+annotate_figure(figure_btw,
+                top = text_grob("Betweenness ~ TL model assumptions", color = "red", face = "bold", size = 14))
+
+# Log y axis to see better the trend. highest TLs (top predators) show btw=0 due to methodology
+plot_sp_bt <- spp_total %>% 
+  filter(TL >= 2) %>% 
+  ggplot(., aes(x = TL, y = Between)) +
+  geom_point() +
+  scale_y_log10(label = scientific_10) +
+  geom_smooth(method = "loess") +
+  #geom_smooth(method = "glm", method.args = list(family = "Gamma"), se = FALSE) +
+  #geom_vline(xintercept = c(spp_nt_12+1, spp_nt_12+spp_nt_13+1, spp_nt_14+1), linetype = "longdash", colour = "red") +
+  labs(x = "Trophic level", y = "Betweenness") +
+  theme_bw() +
+  theme(panel.grid = element_blank(),
+        axis.text.x = element_text(size = 26),
+        axis.text.y = element_text(size = 26),
+        axis.title = element_text(size = 26, face = "bold"))
+
+## Closeness ----
[…]

### 2024-01-17 MS_ToSubmit/RevisedVersion.Rmd
Add Freeman 1978

@@
 
-Closeness and betweenness are defined as "mesoscale" properties because they consider direct and indirect interactions, therefore describing the focal species’ ability to influence the rest of the species of the food web [@Lai2012].
+Closeness and betweenness are defined as "mesoscale" properties because they consider direct and indirect interactions, therefore describing the focal species’ ability to influence the rest of the species of the food web [@Freeman1978; @Lai2012].
 Closeness quantifies how many steps away species $i$ is from all other species in the food web, and is proportional to how rapidly the indirect effects of the focal species can spread to other species in the network [@Scotti2010].

### 2024-03-27 MS_ToSubmit/RevisedVersion_1.Rmd
Revised version 1

--- 2024-01-17 MS_ToSubmit/RevisedVersion.Rmd
@@
 output:
+  word_document: default
   pdf_document:
@@
     keep_tex: yes
-  word_document: default
 bibliography: AMPBancoBurdwood.bib
@@
 
-The total area of the world ocean designated under marine protection has increased recently.
+The world’s oceans designated under marine protection have increased recently.
 Most Marine Protected Areas (MPAs) target vulnerable, keystone, charismatic and or endemic species.
-In the sub-Antarctic, ocean protection is associated to oceanic islands, except for MPAs Namuncurá - Burdwood Bank I and II (MPA N-BB, ~53º–55ºS and ~56º–62ºW), which are associated to a submarine plateau and its southern adjacent deep slope, respectively.
-Here, we present the first analysis of the network of predator-prey interactions for the MPA N-BB.
-We applied a topological network approach to characterise the complexity and structure of the food web, and identify the species' role in such a framework.
+In the sub-Antarctic, ocean protection is associated to oceanic islands, except for MPAs Namuncurá - Burdwood Bank I and II (MPA N-BB, ~53º–55ºS and ~56º–62ºW), which are associated to a submarine plateau and a southern deep slope, respectively.
+Here, we present the first analysis of the predator-prey network for the MPA N-BB.
+We applied a topological network approach to characterise the complexity and structure of the food web, and identify the species’ role in such a framework.
 The MPA N-BB food web consisted of 1788 interactions and 379 species, with a connectance of 0.01.
-Almost half of the consumers were omnivores or feeding at more than one trophic level (0.48), and the network displayed a small-world pattern (short path length, high clustering of compartments).
+Almost half of the consumers feed at more than one trophic level (0.48), and the network displayed a small-world pattern (short path length, high clustering of compartments).
 This network pattern suggests that the ecosystem might be vulnerable to perturbations targeting highly connected species, although some properties might provide resilience and resistance, resulting in a rearranged structure that preserves its original functions.
-Several species arose as important in terms of different aspects of trophic structure and functioning, and response to perturbations.
-Generalist species, mainly fishes, play a crucial role in the ecosystem's benthopelagic coupling and should be considered as relevant energy transfers for the ecosystem.
+Several species arose as important for the trophic structure and functioning, and response to perturbations.
+Generalist species, mainly fishes, play a crucial role in the benthopelagic coupling and should be considered as relevant energy transfers for the ecosystem.
 We argue that the diversity of species, including both the benthic and pelagic habitats, is responsible for securing the connectivity within the food web against perturbations, therefore contributing to the structure and stability of the ecosystem.
@@
 
-Identifying the main species involved in the maintenance of ecosystem services and health as well as for management and conservation is essential.
+Maintaining ocean ecosystem services relies on a healthy ocean, and biological species play a key role in this process.
+It is essential to identify the main species involved in sustaining this health for effective management and conservation purposes.
 In this regard, @Bergagna2020 have identified the principal ecosystem services that are provided by species inhabiting the MPA N-BB; for instance, nursery and feeding areas for commercially important fishes (e.g.
@@
 Recently, the structure of the southwestern South Atlantic Ocean has been hypothesised to be under a 'wasp-waist' control, meaning that the structure and dynamics of the ecosystem are regulated primarily by mid-trophic level species (e.g., fishes, crustaceans) [@Padovani2012; @Saporiti2015; @Riccialdelli2020].
-In particular, the ecosystem of the MPA N-BB shows a more pronounced 'wasp-waist' structure, meaning a shorter average food chain and a greater trophic overlap and redundancy, than other sub-Antarctic areas such as the continental shelf off Tierra del Fuego.
-It is the high abundance of few prey species at this mid-trophic level of the food web which imposes a certain feeding dependence to high-trophic level predators, shortens food-web length and increases the trophic overlap and redundancy of the overall food web.
-The Fuegian sprat *Sprattus fuegensis* and longtail southern cod Patagonotothen ramsayi are considered the most plausible 'wasp-waist' species, since they are species with high regional abundances [@Madirolas2000; @Arkhipkin2013], occupy mid-trophic levels [@Riccialdelli2010; @Riccialdelli2020], many predators feed on them [@Riccialdelli2020], and the population dynamics of these species appear to depend on the environment (e.g.
+In particular, the ecosystem of the MPA N-BB shows a more pronounced 'wasp-waist' structure, meaning a shorter average food chain and a greater trophic overlap and redundancy, respect to other sub-Antarctic areas such as the continental shelf off Tierra del Fuego.
+The high abundance of a limited number of prey species at the intermediate trophic level of the food web which leads to a specific feeding reliance among high-trophic level predators.
+This phenomenon shortens food-web length while simultaneously amplifying trophic overlap and redundancy within the overall food web.
+The Fuegian sprat *Sprattus fuegensis* and longtail southern cod *Patagonotothen ramsayi* has been considered the most plausible 'wasp-waist' species for the MPA N-BB [@Riccialdelli2020], since they are species with high regional abundances [@Madirolas2000; @Arkhipkin2013], they occupy mid-trophic levels [@Riccialdelli2010; @Riccialdelli2020], many predators feed on them [@Riccialdelli2020], and their population dynamics appear to depend on the environment (e.g.
 climatic variations) [@Diez2018].
 These recent efforts have increased our understanding of the biological communities and their complexity, but an understanding of species interactions’ complexity and structure is lacking.
-Such understanding will provide a more complete picture of the ecosystem, generate a baseline to comprehend climate change effects for the region [@Franco2020] and serve as an input to decision makers on conservation actions [@AdministraciondeParquesNacionales2022].
+Such understanding will provide a more complete picture of the ecosystem, generate a baseline to comprehend climate change effects [@Franco2020] and serve as an input to decision makers on conservation actions [@AdministraciondeParquesNacionales2022].
 
 This aspect can be tackled by analysing one of the most frequent relationships between species: the predator-prey interaction [@Bascompte2009].
-The sum of these interactions in a particular region is referred to as a food web, representing the roadmap for matter and energy flow in an ecosystem.
+The assembly of these interactions in a particular region is referred to as a food web, representing the roadmap for matter and energy flow in an ecosystem.
 In recent years, topological network approaches have been successfully applied to study complex high-latitude marine ecosystems, improving our knowledge on structure, functioning, and response to environmental/anthropogenic changes [@Kortsch2015; @Cordone2018; @Funes2022; @Marina2023].
@@
 Random webs were created using the Erdös-Rényi model, where links are added to the complete set of nodes ($S$) and chosen uniformly randomly from the set of all possible links [@Erdos1959].
-The rigurosity of our method lies in the use of confidence intervals (CI 99%) for the empirical-random comparison of the $CPL$ and $CC$ properties.
+The preciseness of our method lies in the use of confidence intervals (CI 99%) for the empirical-random comparison of the $CPL$ and $CC$ properties.
 If the empirical value is positioned within or to the left (= lower than) the CI 99% of the random CPL, and to the right (= higher than) the CI 99% of the CC, then the food web is considered to present the SW topology [@Marina2018a].
@@
 For this, we considered the following properties: betweenness $Btw$, closeness $Cl$, trophic similarity $TS$, topological role $TR$, and trophic level $TL$ (Table 1).
-Topological roles refer to the fact that food webs tend to naturally organize in non-random, modular patterns, where modules are defined as a group of species that interact more frequently among themselves than with species that are not members of the module [@Guimera2005].
+Topological roles refer to the fact that food webs tend to naturally organise in non-random, modular patterns, where modules are defined as a group of species that interact more frequently among themselves than with species that are not members of the module [@Guimera2005].
 This means that groups of prey and predators interact more strongly with each other, than with species belonging to other groups.
-Modularity measures how strongly these subgroups of species, called modules, interact with each other compared to species from other modules.
+Consequently, modularity measures how strongly these modules interact with each other compared to their interaction with species from other modules.
 Species can play different roles in this respect, according to the pattern of interactions within their own module and/or across modules.
-We computed the topological role for each species, classified as module hub, species with a relatively high number of interactions, but most within its own module; module specialist, species with relatively few interactions and most within its own module; module connector, species with relatively few interactions mainly between modules; and network connector, species with high connectivity between and within modules [@Guimera2005].
+We computed the topological role for each species, classified as “module hub”, species with a relatively high number of interactions, but most within its own module; “module specialist”, species with relatively few interactions and most within its own module; “module connector”, species with relatively few interactions mainly between modules; and “network connector”, species with high connectivity between and within modules [@Guimera2005].
 Refer to the Supplementary Material for the equations used to calculate the species-level properties.
@@
 The top-five predators in number of prey were: yellowfin notothen *Patagonotothen guntheri* (Notothenioid fish, 50 prey), rock cod *Patagonotothen ramsayi* (Notothenioid fish, 49 prey), broad nose skate *Bathyraja brachyurops* (Chondrichthyan, 33 prey), Patagonian toothfish *Dissostichus eleginoides* (Notothenioid fish, 30 prey), and graytail skate *Bathyraja griseocauda* (Chondrichthyan, 28 prey).
-Following the same distribution pattern, few prey presented multiple predators (Figure 3C).
+Following the same distribution pattern, few prey were targeted by multiple predators (Figure 3C).
 The top-five prey (or food sources) in number of predators were: Detritus (Non-living, 153 predators), the three categories of Diatoms considered (benthic, centric and pennate, 72.5 predators on average), and species of the genus *Euphausia* (Zooplankton, 46 predators).
@@
 
-Food web connectance is a feature that resumes the complexity of the network, but more importantly, it is an emergent property of pairwise species interactions [@Poisot2014].
+Food web connectance is a feature that summarises the complexity of the network, but more importantly, it is an emergent property of pairwise species interactions [@Poisot2014].
 It contains information regarding how interactions within an ecological network are distributed and predicts reasonably well key dynamical properties of ecological networks [@Dunne2002a].
@@
 Closeness quantifies how many steps away species $i$ is from all other species in the food web, and is proportional to how rapidly the indirect effects of the focal species can spread to other species in the network [@Scotti2010].
-Considering the relationship between this property and TL in the food web of the MPA N-BB, it is worth to highlight that species with the highest closeness values are low-TL consumers (TL = 2 - 3): species of the zooplankton community, *Calanus* and *Euphausia*, *Zygochlamys patagonica* (Bivalvia), and Brachiopoda.
+Considering the relationship between this property and TL in the food web of the MPA N-BB, it is worth highlighting that species with the highest closeness values are low-TL consumers (TL = 2 - 3): species of the zooplankton community, *Calanus* and *Euphausia*, *Zygochlamys patagonica* (Bivalvia), and Brachiopoda.
 Any perturbation affecting these species, such as the recently confirmed contaminants mercury [@Fioramonti2022] and microplastics [@Cossi2021; @DiMauro2022], and the warming trend reported for the surface and subsurface waters in the Southwest Atlantic Ocean [@Franco2020a; @Galvan2022a], should be of concern since it might reach many other species in the food web.
@@
 Ecosystems with a pronounced 'wasp-waist' structure are suggested to present a high trophic redundancy, since many species would show similar trophic habits [@Cury2000].
-Such trophic redundancy is expected to be greater for species in TLs above the waist (mid-TL) that depend on a very few species at the waist.
-However, our results show an exponential-like negative relationship between trophic similarity (or redundancy) and trophic level, indicating functional similarity at low and mid-TL species compared to higher TL species for the MPA N-BB food web.
+Such trophic redundancy is expected to be greater for species in TLs above the waist that depend on a very few species at this intermediate level.
+However, our results show a negative relationship between trophic similarity (or redundancy) and trophic level, indicating functional similarity at low and mid-TL species compared to higher TL species for the MPA N-BB food web.
 This contradiction might be reflecting the potential discrepancy that could arise between qualitative (this study) and quantitative food web studies.
-Here it is important to note that our analyses considered all potential predator-prey interactions in the food web giving equal importance to them.
+Here it is important to note that our analyses considered all potential predator-prey interactions in the food web, assigning equal importance to each of them.
 Although this could be a disadvantage when inferring on energy flows, one of the main advantages of qualitative food web studies is that it considers the diversity of the communities inhabiting a particular study area, therefore providing a more representative picture of all components (species) acting on the ecosystem.
 In this sense, our study highlights the uniqueness in terms of the trophic role of high-TL predators.
-Not only the expected pelagic animals such as marine mammals and seabirds arise as relevant, but also demersal vertebrate (chondrichthyans *Bathyraja macloviana* and *Squalus acanthias*) and benthic invertebrate species (echinoderms *Diplopteraster clarki* and *Pteraster* sp.) are noteworthy.
+Not only the expected pelagic animals such as marine mammals and seabirds arise as relevant, but also demersal vertebrate (chondrichthyans *Bathyraja macloviana* and *Squalus acanthias*) and benthic invertebrate species (echinoderms *Diplopteraster clarki* and *Pteraster sp.*) are noteworthy.
 The role that such species play in the MPA N-BB ecosystem is unique and perturbations on them might result in unprecedented changes at the trophic structure and functioning level.
@@
 Although we were aware of the above, we decided to characterise a food web representing the whole MPA N-BB I year round since this is the first study of its type in the area.
+In future studies, environmental variables such as depth, current speed and/or nutrient availability should be included in food web works, as done recently [@Cordone2020].
 
@@
 On the one hand, we suggest that generalist species, mainly fishes, play a crucial role in the ecosystem's bentho-pelagic coupling process.
-At the same time, we propose that other species besides the longtail southern cod *Patagonotothen ramsayi* and the Fueguian sprat *Sprattus fuegensis* should be considered relevant energy transfers for the ecosystem.
+At the same time, we propose that other species besides the longtail southern cod *Patagonotothen ramsayi* and the Fuegian sprat *Sprattus fuegensis* should be considered relevant energy transfers for the ecosystem.
 Finally, we argue that it is the diversity of species, representing the benthic and pelagic habitats, that maintains the connectivity of the food web against perturbations, therefore contributing to the structure and stability of the ecosystem.
@@
 Our work provides valuable information for supporting the management of the MPA N-BB in the sense that it disentangles the multiple ecosystem players and their roles.
-Moreover, by building the network of predator-prey interactions we have set the baseline to model the environmental and anthropogenic perturbations affecting the MPA ecosystem.
-This knowledge becomes of importance at the regional scale given that the MPA ecosystem is a known spawning ground for many species of commercial interest [@AdministraciondeParquesNacionales2022] and a potential area of high carbon storage and sequestration due to the characteristics of the benthic community [@Bax2022; @Bergagnainrev].
+Moreover, by building the network of predator-prey interactions we have set the baseline to model the environmental and anthropogenic perturbations affecting this oceanic ecosystem.
+This knowledge becomes of importance at the regional scale given that the MPA N-BB ecosystem is a known spawning ground for many species of commercial interest [@AdministraciondeParquesNacionales2022] and a potential area of high carbon storage and sequestration due to the characteristics of the benthic community [@Bax2022; @Bergagnainrev].
 
@@
 Note that for panels A, B and C only species with TLs equal or greater than 2 were considered.
-In the boxplot (D), the horizontal line in the middle of each box represents the median of the data, the colored box represents the interquartile range (range between the 1st, or 25th percentile, and 3rd, or 75th percentile, quartile), containing the middle 50% of data points."}
+In the boxplot (D), the horizontal line in the middle of each box represents the median of the data, the coloured box represents the interquartile range (range between the 1st, or 25th percentile, and 3rd, or 75th percentile, quartile), containing the middle 50% of data points."}
 # Trophic similarity, Closeness, Betweenness & Topological role by Trophic level

### 2024-03-27 MS_ToSubmit/RevisedVersion_2.Rmd
Revised version 2

--- 2024-03-27 MS_ToSubmit/RevisedVersion_1.Rmd
@@
 Overall, 811 benthic and plankton species have been identified in the MPA N-BB ecosystem, where 349 were reported for the first time in the area in recent years [@AdministraciondeParquesNacionales2022].
-Recently, the structure of the southwestern South Atlantic Ocean has been hypothesised to be under a 'wasp-waist' control, meaning that the structure and dynamics of the ecosystem are regulated primarily by mid-trophic level species (e.g., fishes, crustaceans) [@Padovani2012; @Saporiti2015; @Riccialdelli2020].
-In particular, the ecosystem of the MPA N-BB shows a more pronounced 'wasp-waist' structure, meaning a shorter average food chain and a greater trophic overlap and redundancy, respect to other sub-Antarctic areas such as the continental shelf off Tierra del Fuego.
-The high abundance of a limited number of prey species at the intermediate trophic level of the food web which leads to a specific feeding reliance among high-trophic level predators.
-This phenomenon shortens food-web length while simultaneously amplifying trophic overlap and redundancy within the overall food web.
-The Fuegian sprat *Sprattus fuegensis* and longtail southern cod *Patagonotothen ramsayi* has been considered the most plausible 'wasp-waist' species for the MPA N-BB [@Riccialdelli2020], since they are species with high regional abundances [@Madirolas2000; @Arkhipkin2013], they occupy mid-trophic levels [@Riccialdelli2010; @Riccialdelli2020], many predators feed on them [@Riccialdelli2020], and their population dynamics appear to depend on the environment (e.g.
+Recently, the structure of the southwestern South Atlantic Ocean has been hypothesised to be under a ‘wasp-waist’ control, meaning that the structure and dynamics of the ecosystem are regulated primarily by mid-trophic level species (e.g., fishes, crustaceans) [@Padovani2012; @Saporiti2015; @Riccialdelli2020].
+In particular, the ecosystem of the MPA N-BB shows a more pronounced ‘wasp-waist’ structure, meaning a shorter average food chain and a greater trophic overlap and redundancy in high-trophic levels compared to other sub-Antarctic areas, such as the continental shelf off Tierra del Fuego [@Riccialdelli2020].
+The high abundance of a limited number of prey species at the intermediate trophic level of the food web leads to a specific feeding reliance among high-trophic level predators.
+This phenomenon shortens the length of the food web, as the diet of top predators is expected to be dominated by the mentioned intermediate-trophic level species, thus lowering their trophic position.
+Simultaneously, it amplifies trophic overlap and redundancy between such predators.
+The Fuegian sprat *Sprattus fuegensis* and longtail southern cod *Patagonotothen ramsayi* have been considered the most plausible ‘wasp-waist’ species for the MPA N-BB [@Riccialdelli2020], since they are species with high regional abundances [@Madirolas2000; @Arkhipkin2013], they occupy mid-trophic levels [@Riccialdelli2010; @Riccialdelli2020], many predators feed on them [@Riccialdelli2020], and their population dynamics appear to depend on the environment (e.g.
 climatic variations) [@Diez2018].
@@
 The assembly of these interactions in a particular region is referred to as a food web, representing the roadmap for matter and energy flow in an ecosystem.
+Here it is important to distinguish the inference power of topological food web models, which rely on presence/absence interactions among species, versus the so-called dynamic food web models that account for biomass of species, along with the magnitude and direction of energy flows among them [@Brose2009].
+While the latter might better capture the ecosystem properties given that food webs are inherently dynamical systems, the former ones are the necessary first step, providing a map of biological and ecological-constrained possibilities.
 In recent years, topological network approaches have been successfully applied to study complex high-latitude marine ecosystems, improving our knowledge on structure, functioning, and response to environmental/anthropogenic changes [@Kortsch2015; @Cordone2018; @Funes2022; @Marina2023].
-Among anthropogenic threats, it is worth mentioning that contaminants like mercury and microplastics have been recently reported as important threats to the MPA N-BB region [@Cossi2021; @DiMauro2022; @Fioramonti2022]; also fishing vessels are allowed to operate in the western section of the MPA N-BB (i.e.
+Among the anthropogenic threats reported for the MPA N-BB ecosystem, it is worth mentioning contaminants like mercury and microplastics [@Cossi2021; @DiMauro2022; @Fioramonti2022]; also fishing vessels are allowed to operate in the western section of the MPA N-BB (i.e.
 Marine National Reserve category), altering the stocks of commercially important fish species [@Martinez2021; @AdministraciondeParquesNacionales2022].
@@
 For this, we applied a topological network approach to a highly resolved food web.
-The objective was twofold: characterise the food web in terms of complexity and structure, and identify the species' role in the network.
-For the former, we considered all species and interactions in the food web, and calculated the number of species (S), number of interactions (L), link density (L/S), connectance (L/S^2), proportion of omnivorous, and assessed the small-world pattern.
+The objective was twofold: characterise the food web in terms of complexity and structure, and identify the species’ role in the network.
+For the former, we considered all species and interactions in the food web, and calculated the number of species (S), number of interactions (L), link density (L/S), connectance (L/S2), proportion of omnivorous, and assessed the small-world pattern.
 For the latter objective, we considered interactions and species related to a particular species and analyse the following properties: betweenness, closeness, trophic similarity, topological role and trophic level.
@@
 Omnivory acts as a buffer to changes as the ecosystem presents alternative energy pathways in the face of perturbations, i.e., reducing the risk of cascading extinctions following the primary loss of species [@Borrvall2000].
-This is supported by the fact that omnivorous adapt at a faster rate and to a wide range of environmental conditions due to its flexibility to feed on the most abundant prey [@Fagan1997].
+This is supported by the fact that omnivores adapt at a faster rate and to a wide range of environmental conditions due to its flexibility to feed on the most abundant prey [@Fagan1997].
 Furthermore, omnivory can be analysed from the interaction point of view: theoretical studies have identified omnivorous interactions as a possible candidate for a keystone interaction, sensu @Kadoya2018, highlighting the importance of omnivory in stabilizing food web dynamics [@McCann1997; @Neutel2002].
@@
 
-Ecosystems with a pronounced 'wasp-waist' structure are suggested to present a high trophic redundancy, since many species would show similar trophic habits [@Cury2000].
+Ecosystems with a pronounced 'wasp-waist' structure are suggested to present a high trophic redundancy, since many species feeding at intermediate trophic levels would show similar trophic habits [@Saporiti2015].
 Such trophic redundancy is expected to be greater for species in TLs above the waist that depend on a very few species at this intermediate level.

### 2024-03-27 MS_ToSubmit/RevisedVersion_1.Rmd
Update listings package

@@
 output:
-  word_document: default
   pdf_document:
@@
     keep_tex: yes
+  word_document: default
 bibliography: AMPBancoBurdwood.bib
@@
 - \usepackage[running]{lineno}
+- \usepackage{listings}
 - \linenumbers

### 2024-03-27 MS_ToSubmit/RevisedVersion_2.Rmd
Abstract length

@@
 The world’s oceans designated under marine protection have increased recently.
-Most Marine Protected Areas (MPAs) target vulnerable, keystone, charismatic and or endemic species.
-In the sub-Antarctic, ocean protection is associated to oceanic islands, except for MPAs Namuncurá - Burdwood Bank I and II (MPA N-BB, ~53º–55ºS and ~56º–62ºW), which are associated to a submarine plateau and a southern deep slope, respectively.
-Here, we present the first analysis of the predator-prey network for the MPA N-BB.
-We applied a topological network approach to characterise the complexity and structure of the food web, and identify the species’ role in such a framework.
+Most Marine Protected Areas (MPAs) target vulnerable, keystone, charismatic and/or endemic species.
+In the sub-Antarctic, ocean protection is associated to oceanic islands, except for MPAs Namuncurá - Burdwood Bank I and II (MPA N-BB, ~53º – 55ºS and ~56º – 62ºW), which are associated to a submarine plateau and a southern deep slope, respectively.
+We present the first analysis of the predator-prey network for the MPA N-BB, applying a topological network approach to characterise the complexity and structure of the food web, and identify the species’ role.
 The MPA N-BB food web consisted of 1788 interactions and 379 species, with a connectance of 0.01.

### 2024-04-12 MS_ToSubmit/RevisedVersion_3.Rmd
Final version

--- 2024-03-27 MS_ToSubmit/RevisedVersion_2.Rmd
@@
 Also, the benthic realm provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge and nursery area [@GarciaAlonso2018; @Vazquez2018; @Delpiani2020; @Troccoli2020; @CovattiAle2022; @Fischer2022; @Matusevich2022; @Florencia2023].
-The maintenance of this singular community is related to local and regional oceanographic processes, including the circulation of the rich Malvinas current in the area [@Piola1989; @Guerrero1999] and the upwelling and mixing phenomena [@Matano2019].
-The input of nutrients from the Malvinas current also supports a diverse plankton community [@Guinder2020].
+The persistence of this particular community is linked to the interplay of local and regional oceanographic dynamics, encompassing the influence of the nutrient-rich Malvinas current [@Piola1989; @Guerrero1999], and occurrences of upwelling and mixing.
+Moreover, the influx of nutrients carried by the Malvinas current fosters a varied planktonic ecosystem [@Guinder2020].
 Given the cooling trend of this current in a warming regional context (i.e.
@@
 Topological roles refer to the fact that food webs tend to naturally organise in non-random, modular patterns, where modules are defined as a group of species that interact more frequently among themselves than with species that are not members of the module [@Guimera2005].
-This means that groups of prey and predators interact more strongly with each other, than with species belonging to other groups.
-Consequently, modularity measures how strongly these modules interact with each other compared to their interaction with species from other modules.
+This implies that prey and predator groups exhibit greater interaction within their respective modules compared to interactions with species outside those modules.
+Therefore, modularity assesses the intensity of interactions among these modules relative to interactions with species from different modules.
 Species can play different roles in this respect, according to the pattern of interactions within their own module and/or across modules.
@@
 Martinez (Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina) and Luciano Padovani (Instituto Nacional de Investigación y Desarrollo Pesquero, INIDEP, Argentina).
+Part of the methodology for the network analysis performed in this work is available in the pre-print @Marina2018 on https://www.biorxiv.org/content/10.1101/094557v1.full.
 We thank the MPA Namuncurá - Burdwood Bank administration.

### 2024-05-09 R/6_figures.R
Food web colors

@@ -26,9 +26,11 @@ load("data/foodweb-data_jul23.rda")
 
 ## Figure 2 ----
 
-par(cex.axis=0.8, cex.lab=0.8)
-figure_2 <- plot_troph_level(g, vertexLabel = F, modules = F, ylab = "Trophic level",
-                             tk = T)
+col <- RColorBrewer::brewer.pal(11, "RdYlBu") # PuOr, RdBu, RdYlBu
+#par(cex.axis=0.8, cex.lab=0.8)
+figure_2 <- plot_troph_level(g, vertexLabel = F, edge.arrow.size = .1, modules = F,
+                             tk = F, bpal = col)
+
 
 ## Figure 3 ----
 

### 2024-05-09 MS_ToSubmit/RevisedSupMaterial.Rmd
Final Sup Mat

@@
     keep_tex: yes
-  word_document: default
 # classoption: landscape
@@
 library(knitr)
-knitr::include_graphics("FigS1.png")
+knitr::include_graphics("../Figures/Figure S1 final.png")
 ```
@@
   dplyr::select(Prey, Predator, Reference, Reference_link) %>% 
-  distinct(Prey, Predator, .keep_all = TRUE)
+  distinct(Prey, Predator, .keep_all = TRUE) %>% 
+  rename(., Link = Reference_link)
 
@@
 
-pandoc.table(int_good_res %>% arrange(., (Predator)) %>% mutate(Reference_link = paste('\\tiny', Reference_link), Reference = paste('\\tiny', Reference), Prey = paste('\\tiny', Prey), Predator = paste('\\tiny', Predator)) %>% rename("Link"="Reference_link"), style="multiline", split.tables = Inf, justify = c("left","left","center","right"),
+# write.csv(int_good_res %>% arrange(., (Predator)), file = "TableS1_14600.csv")
+
+pandoc.table(int_good_res %>% arrange(., (Predator)) %>% mutate(Reference_link = paste('\\tiny', Reference_link), Reference = paste('\\tiny', Reference), Prey = paste('\\tiny', Prey), Predator = paste('\\tiny', Predator)), style="multiline", split.tables = Inf, justify = c("left","left","center","right"),
              caption = "List of predator-prey (trophic) interactions used to build the network for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).")
@@
 
+# write.csv(sp_list %>% arrange(., (Species)) %>% rename("Taxonomy"="TaxLevel", "Group"="FunctionalGroup", "Link"="Reference_pres_link"), file = "TableS2_14600.csv")
+
 pandoc.table(sp_list %>% arrange(., (Species)) %>% mutate(Species = paste('\\tiny', Species), TaxLevel = paste('\\tiny', TaxLevel), FunctionalGroup = paste('\\tiny', FunctionalGroup), Reference = paste('\\tiny', Reference), Reference_pres_link = paste('\\tiny', Reference_pres_link), Observation = paste('\\tiny', Observation)) %>% rename("Taxonomy"="TaxLevel", "Group"="FunctionalGroup", "Link"="Reference_pres_link"), style="multiline", split.tables = Inf, justify = c("left","left","left","left","left","left"),
@@
                                      TRUE ~ FunctionalGroup))
+
+# write.csv(tbl_3 %>% arrange(., (TotalDegree)) %>% rename("Species"="TrophicSpecies", "Group"="FunctionalGroup", "Degree"="TotalDegree", "TS"="meanTrophicSimil", "TR"="TopRole"), file = "TableS3_14600.csv")
 

### 2024-05-15 MS_ToSubmit/RevisedSupMaterial.Rmd
Add equations

@@
 
-Trophic level
+#### Betweenness
 
-Trophic levels (TL) of species were calculated using the shortweighted TL formula of @Williams2004.
-Shortweighted trophic level is defined as the average of the shortest TL and prey-averaged TL.
-Shortest TL of a consumer in a food web is equal to 1 + the shortest chain length from this consumer to any basal species [@Williams2004].
-Prey averaged TL is equal to 1 + the mean TL of all consumer's trophic resources, calculated as:
+It is the frequency with which a node is on the shortest path between any other pair of nodes [@Freeman1978].
+A node will have high betweenness when it appears on many shortest paths between other pairs of nodes.
+It is calculated as:
 
 \begin{equation}
-TL_j = 1 + \sum_{i = 1}^{S} l_{ij} \frac{TL_i}{n_j}
+BC_i = \sum \frac{g_{vij}} {g_{vj}}
 \end{equation}
 
-where $TL_j$ is the trophic level of species $j$; $S$ is the number of species in the food web; $l_{ij}$ is the connection matrix with $S$ rows and $S$ columns, in which for column $j$ and row $i$, $l_{ij}$ = 1 if species $j$ consumes species $i$ and $l_{ij}$ = 0 if not; and $n_j$ is the number of prey species in the diet of species $j$.
-For basal species TL = 1 given that they have no prey.
+being $v \neq j, v \neq i, j \neq i$, where $BC_i$ is the betweenness for species $i$; $g_{vj}$ is the number of shortest paths between nodes $v$ and $j$; and $g_{vij}$ is the number of shortest paths which pass through node $i$.
 
-Topological roles
+#### Closeness
+
+It is the number of steps required to reach every other node from a given node in the network [@Freeman1978].
+It is calculated as the inverse of distances (number of interactions) to all other nodes in the network:
+
+\begin{equation}
+C_i = \frac{1} {\sum d_{ij}}
+\end{equation}
+
+being $i \neq j$, where $d_{ji}$ is the distance between node $j$ and $i$.
+
+#### Trophic similarity
+
+It measures the trophic overlap based on shared and unique resources (prey) and consumers (predators) of a species. It is calculated as:
+
+\begin{equation}
+TS_i = \frac{c} {(a+b+c)}
+\end{equation}
+
+where $a$ is the number of prey and predators unique to one node, $b$ is number of prey and predators unique to the other node and $c$ is the number of prey and predators common to both nodes.
+Where two nodes have exactly the same set of prey and predators, $TS$ = 1; where two nodes have no prey or predators in common, $TS$ = 0.
+
+#### Topological roles
 
@@
 
+#### Trophic level
+
+Trophic levels (TL) of species were calculated using the shortweighted TL formula of @Williams2004.
+Shortweighted trophic level is defined as the average of the shortest TL and prey-averaged TL.
+Shortest TL of a consumer in a food web is equal to 1 + the shortest chain length from this consumer to any basal species [@Williams2004].
+Prey averaged TL is equal to 1 + the mean TL of all consumer's trophic resources, calculated as:
+
+\begin{equation}
+TL_j = 1 + \sum_{i = 1}^{S} l_{ij} \frac{TL_i}{n_j}
+\end{equation}
+
+where $TL_j$ is the trophic level of species $j$; $S$ is the number of species in the food web; $l_{ij}$ is the connection matrix with $S$ rows and $S$ columns, in which for column $j$ and row $i$, $l_{ij}$ = 1 if species $j$ consumes species $i$ and $l_{ij}$ = 0 if not; and $n_j$ is the number of prey species in the diet of species $j$.
+For basal species TL = 1 given that they have no prey.
+
 \newpage
@@
 
-pandoc.table(int_good_res %>% arrange(., (Predator)) %>% mutate(Reference_link = paste('\\tiny', Reference_link), Reference = paste('\\tiny', Reference), Prey = paste('\\tiny', Prey), Predator = paste('\\tiny', Predator)), style="multiline", split.tables = Inf, justify = c("left","left","center","right"),
+pandoc.table(int_good_res %>% arrange(., (Predator)) %>% mutate(Link = paste('\\tiny', Link), Reference = paste('\\tiny', Reference), Prey = paste('\\tiny', Prey), Predator = paste('\\tiny', Predator)), style="multiline", split.tables = Inf, justify = c("left","left","center","right"),
              caption = "List of predator-prey (trophic) interactions used to build the network for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).")

### 2024-05-15 R/6_figures.R
Color food web plot

@@ -26,10 +26,10 @@ load("data/foodweb-data_jul23.rda")
 
 ## Figure 2 ----
 
-col <- RColorBrewer::brewer.pal(11, "RdYlBu") # PuOr, RdBu, RdYlBu
-#par(cex.axis=0.8, cex.lab=0.8)
+col <- RColorBrewer::brewer.pal(11, "RdYlGn") # PuOr, RdBu, RdYlBu
+par(cex.axis=0.8, cex.lab=0.8)
 figure_2 <- plot_troph_level(g, vertexLabel = F, edge.arrow.size = .1, modules = F,
-                             tk = F, bpal = col)
+                             tk = F, bpal = col, ylab = "Trophic level")
 
 
 ## Figure 3 ----
